### 2018-06-06 ANA-TOPQ-2017-07-PAPER-metadata.tex
Setup ANA-TOPQ-2017-07-PAPER repository

%-------------------------------------------------------------------------------
% This file contains the title, author and abstract.
% It also contains all relevant document numbers used by the different cover pages.
%-------------------------------------------------------------------------------

% Title
\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{1.0}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
  This is a bare bones ATLAS document. Put the abstract for the document here.
}

% Author - this does not work with revtex (add it after \begin{document})
\author{The ATLAS Collaboration}

% ATLAS reference code, to help ATLAS members to locate the paper
\AtlasRefCode{TOPQ-2017-07}

% ATLAS date - arXiv submission; usually filled in by the Physics Office
% \AtlasDate{\today}

% ATLAS heading - heading at top of title page. Set for TDR etc.
% \AtlasHeading{ATLAS ABC TDR}

 %-------------------------------------------------------------------------------
% The following information is needed for the cover page. The commands are only defined
% if you use the coverpage option in atlasdoc or use the atlascover package
%-------------------------------------------------------------------------------

 % List of supporting notes  (leave as null \AtlasCoverSupportingNote{} if you want to skip this option)
% \AtlasCoverSupportingNote{Short title note 1}{https://cds.cern.ch/record/XXXXXXX}
% \AtlasCoverSupportingNote{Short title note 2}{https://cds.cern.ch/record/YYYYYYY}
%
% OR (the 2nd option is deprecated, especially for CONF and PUB notes)
%
% Supporting material TWiki page  (leave as null \AtlasCoverTwikiURL{} if you want to skip this option)
% \AtlasCoverTwikiURL{https://twiki.cern.ch/twiki/bin/view/Atlas/WebHome}

% Comment deadline
% \AtlasCoverCommentsDeadline{DD Month 2016}

  % Analysis team members - contact editors should no longer be specified
% as there is a generic email list name for the editors
% \AtlasCoverAnalysisTeam{Peter Analyser, Susan Editor1, Jenny Editor2, Alphonse Physicien}

% Editorial Board Members - indicate the Chair by a (chair) after his/her name
% Give either all members at once (then they appear on one line), or separately
% \AtlasCoverEdBoardMember{EdBoard~Chair~(chair), EB~Member~1, EB~Member~2, EB~Member~3}

% \AtlasCoverEdBoardMember{EdBoard~Chair~(chair)}
% \AtlasCoverEdBoardMember{EB~Member~1}
% \AtlasCoverEdBoardMember{EB~Member~2}
% \AtlasCoverEdBoardMember{EB~Member~3}

   % Editors egroup
\AtlasCoverEgroupEditors{atlas-TOPQ-2017-07-editors@cern.ch}

% EdBoard egroup
\AtlasCoverEgroupEdBoard{atlas-TOPQ-2017-07-editorial-board@cern.ch}

### 2018-06-30 ANA-TOPQ-2017-07-PAPER-metadata.tex
Paper draft moved to official repository

@@
 % Title
-\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
+%\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
+\AtlasTitle{Search for top quark decays $t \to Hq$ with 36 fb$^{-1}$ of $pp$ collision data at $\sqrt{s}=13~\tev$ with the ATLAS detector}
 
@@
 % Comment or remove in final version.
-\AtlasVersion{1.0}
+\AtlasVersion{0.3}
 % Abstract - % directly after { is important for correct indentation
 \AtlasAbstract{%
-  This is a bare bones ATLAS document. Put the abstract for the document here.
+A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the 
+Standard Model Higgs boson, is presented. 
+The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
+CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
+Two analyses are performed searching for top quark pair events in which one top quark decays to $Wb$ and the other top quark decays to $Hq$,
+and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
+They exploit either the high multiplicity of $b$-quark jets, or the presence of hadronically decaying tau leptons, and employ different
+multivariate techniques to separate the signal from the background, which is dominated by $t\bar{t}$ production.
+No significant excess of events above the background expectation is found, and observed (expected) 95\% CL upper limits are derived.
+The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
+yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of 0.XX\% (0.XX\%) and 0.XX\% (0.XX\%) respectively.
+The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.XX (0.XX) and 0.XX (0.XX) respectively. 
+%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
+These are the most restrictive direct bounds on $tqH$ interactions measured so far.
 }
@@
 % ATLAS heading - heading at top of title page. Set for TDR etc.
-% \AtlasHeading{ATLAS ABC TDR}
+\AtlasHeading{ATLAS ABC TDR}
 
@@
 % List of supporting notes  (leave as null \AtlasCoverSupportingNote{} if you want to skip this option)
-% \AtlasCoverSupportingNote{Short title note 1}{https://cds.cern.ch/record/XXXXXXX}
-% \AtlasCoverSupportingNote{Short title note 2}{https://cds.cern.ch/record/YYYYYYY}
+\AtlasCoverSupportingNote{Search for $\ttbar \to WbHq$, $H \to b\bar{b}$}{https://cds.cern.ch/record/2257631}
+\AtlasCoverSupportingNote{Search for $\ttbar \to WbHq$, $H \to \tau^+\tau^-$}{https://cds.cern.ch/record/2273683}
+\AtlasCoverSupportingNote{Combination of $\ttbar \to WbHq$ searches}{https://cds.cern.ch/record/2312520/}
 %
@@
 % as there is a generic email list name for the editors
-% \AtlasCoverAnalysisTeam{Peter Analyser, Susan Editor1, Jenny Editor2, Alphonse Physicien}
+\AtlasCoverAnalysisTeam{
+$H \to b\bar{b}$: Trisha Farooque, Davide Gerbaudo, Aurelio Juste, Nicola Orlando,  \\ Cheng Peng,  Laura Pereira, 
+Yulia Rodina, Yanjun Tu,  Lo\"ic Val\'ery, \\ Tal Van Daalen, Jia-Shian Wang, Daiki Yamaguchi; \\
+$H \to \tau^+\tau^-$: Xin Chen, Antonio De Maria, Boyang Li, Ligang Xia; \\
+Combination: Peter Onyisi, Harish Potti}
 
@@
 % Give either all members at once (then they appear on one line), or separately
-% \AtlasCoverEdBoardMember{EdBoard~Chair~(chair), EB~Member~1, EB~Member~2, EB~Member~3}
+\AtlasCoverEdBoardMember{Ketevi Assamagan~(chair), Garabed Halladjian, Fabrice Hubaut, Michele Weber~(chair)}
 

### 2018-06-30 figures/Hbb/fit/base_ebv2_signal_cH_default_unblinded/Tables/Yields_postFit.tex
Paper draft moved to official repository

\documentclass[10pt]{article}
\usepackage{siunitx}
\usepackage[margin=0.1in,landscape,papersize={210mm,350mm}]{geometry}
\begin{document}
\begin{table}[htbp]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline 
 & 4jex-2bex & 4jex-3bex & 4jex-4bin & 5jex-2bex & 5jex-3bex & 5jex-4bin & 6jin-2bex & 6jin-3bex & 6jin-4bin\\
\hline 
  t#bar{t}+light   & \num[round-mode=figures,round-precision=3]{82731.6} $\pm$ \num[round-mode=figures,round-precision=3]{3743.39} & \num[round-mode=figures,round-precision=3]{4864.82} $\pm$ \num[round-mode=figures,round-precision=3]{443.353} & \num[round-mode=figures,round-precision=3]{15.3037} $\pm$ \num[round-mode=figures,round-precision=3]{11.7737} & \num[round-mode=figures,round-precision=3]{37928.2} $\pm$ \num[round-mode=figures,round-precision=3]{2705} & \num[round-mode=figures,round-precision=3]{3468.45} $\pm$ \num[round-mode=figures,round-precision=3]{385.694} & \num[round-mode=figures,round-precision=3]{15.7506} $\pm$ \num[round-mode=figures,round-precision=3]{9.31776} & \num[round-mode=figures,round-precision=3]{20031.7} $\pm$ \num[round-mode=figures,round-precision=3]{2207.33} & \num[round-mode=figures,round-precision=3]{2547.58} $\pm$ \num[round-mode=figures,round-precision=3]{415.229} & \num[round-mode=figures,round-precision=3]{20.7941} $\pm$ \num[round-mode=figures,round-precision=3]{18.6547} \\ 
  t#bar{t}+cc   & \num[round-mode=figures,round-precision=3]{11413.6} $\pm$ \num[round-mode=figures,round-precision=3]{4745.82} & \num[round-mode=figures,round-precision=3]{1354.89} $\pm$ \num[round-mode=figures,round-precision=3]{558.336} & \num[round-mode=figures,round-precision=3]{5.86827} $\pm$ \num[round-mode=figures,round-precision=3]{4.11578} & \num[round-mode=figures,round-precision=3]{8341.88} $\pm$ \num[round-mode=figures,round-precision=3]{3373.8} & \num[round-mode=figures,round-precision=3]{1996.21} $\pm$ \num[round-mode=figures,round-precision=3]{769.437} & \num[round-mode=figures,round-precision=3]{39.2465} $\pm$ \num[round-mode=figures,round-precision=3]{18.1406} & \num[round-mode=figures,round-precision=3]{7794.07} $\pm$ \num[round-mode=figures,round-precision=3]{3184.81} & \num[round-mode=figures,round-precision=3]{2975.91} $\pm$ \num[round-mode=figures,round-precision=3]{1151.64} & \num[round-mode=figures,round-precision=3]{58.5315} $\pm$ \num[round-mode=figures,round-precision=3]{25.1281} \\ 
  t#bar{t}+bb   & \num[round-mode=figures,round-precision=3]{4274.97} $\pm$ \num[round-mode=figures,round-precision=3]{586.681} & \num[round-mode=figures,round-precision=3]{3403.3} $\pm$ \num[round-mode=figures,round-precision=3]{355.431} & \num[round-mode=figures,round-precision=3]{109.855} $\pm$ \num[round-mode=figures,round-precision=3]{16.9385} & \num[round-mode=figures,round-precision=3]{3410.91} $\pm$ \num[round-mode=figures,round-precision=3]{467.915} & \num[round-mode=figures,round-precision=3]{4920.81} $\pm$ \num[round-mode=figures,round-precision=3]{465.43} & \num[round-mode=figures,round-precision=3]{355.754} $\pm$ \num[round-mode=figures,round-precision=3]{28.8725} & \num[round-mode=figures,round-precision=3]{3395.32} $\pm$ \num[round-mode=figures,round-precision=3]{488.592} & \num[round-mode=figures,round-precision=3]{7518.29} $\pm$ \num[round-mode=figures,round-precision=3]{767.709} & \num[round-mode=figures,round-precision=3]{1105.48} $\pm$ \num[round-mode=figures,round-precision=3]{81.9048} \\ 
  topEW   & \num[round-mode=figures,round-precision=3]{173.141} $\pm$ \num[round-mode=figures,round-precision=3]{27.3722} & \num[round-mode=figures,round-precision=3]{34.8919} $\pm$ \num[round-mode=figures,round-precision=3]{5.71662} & \num[round-mode=figures,round-precision=3]{2.67875} $\pm$ \num[round-mode=figures,round-precision=3]{0.540039} & \num[round-mode=figures,round-precision=3]{167.465} $\pm$ \num[round-mode=figures,round-precision=3]{25.9124} & \num[round-mode=figures,round-precision=3]{65.3104} $\pm$ \num[round-mode=figures,round-precision=3]{10.4221} & \num[round-mode=figures,round-precision=3]{8.15336} $\pm$ \num[round-mode=figures,round-precision=3]{1.43885} & \num[round-mode=figures,round-precision=3]{212.764} $\pm$ \num[round-mode=figures,round-precision=3]{33.8202} & \num[round-mode=figures,round-precision=3]{146.887} $\pm$ \num[round-mode=figures,round-precision=3]{23.862} & \num[round-mode=figures,round-precision=3]{26.9491} $\pm$ \num[round-mode=figures,round-precision=3]{4.79349} \\ 
  ttH   & \num[round-mode=figures,round-precision=3]{62.4444} $\pm$ \num[round-mode=figures,round-precision=3]{7.53342} & \num[round-mode=figures,round-precision=3]{47.1158} $\pm$ \num[round-mode=figures,round-precision=3]{6.06513} & \num[round-mode=figures,round-precision=3]{4.65928} $\pm$ \num[round-mode=figures,round-precision=3]{0.676057} & \num[round-mode=figures,round-precision=3]{81.0323} $\pm$ \num[round-mode=figures,round-precision=3]{8.86474} & \num[round-mode=figures,round-precision=3]{98.5241} $\pm$ \num[round-mode=figures,round-precision=3]{11.579} & \num[round-mode=figures,round-precision=3]{16.5515} $\pm$ \num[round-mode=figures,round-precision=3]{2.31589} & \num[round-mode=figures,round-precision=3]{134.587} $\pm$ \num[round-mode=figures,round-precision=3]{15.1851} & \num[round-mode=figures,round-precision=3]{240.518} $\pm$ \num[round-mode=figures,round-precision=3]{29.1002} & \num[round-mode=figures,round-precision=3]{61.6042} $\pm$ \num[round-mode=figures,round-precision=3]{8.77664} \\ 
  W+jetslight   & \num[round-mode=figures,round-precision=3]{6.12582} $\pm$ \num[round-mode=figures,round-precision=3]{6.30201} & \num[round-mode=figures,round-precision=3]{0.0116465} $\pm$ \num[round-mode=figures,round-precision=3]{0.0131854} & \num[round-mode=figures,round-precision=3]{4.05447e-06} $\pm$ \num[round-mode=figures,round-precision=3]{4.98735e-06} & \num[round-mode=figures,round-precision=3]{2.43672} $\pm$ \num[round-mode=figures,round-precision=3]{2.37869} & \num[round-mode=figures,round-precision=3]{0.00827649} $\pm$ \num[round-mode=figures,round-precision=3]{0.00936765} & \num[round-mode=figures,round-precision=3]{5.90829e-06} $\pm$ \num[round-mode=figures,round-precision=3]{7.22092e-06} & \num[round-mode=figures,round-precision=3]{1.14449} $\pm$ \num[round-mode=figures,round-precision=3]{1.08589} & \num[round-mode=figures,round-precision=3]{0.00749858} $\pm$ \num[round-mode=figures,round-precision=3]{0.00862511} & \num[round-mode=figures,round-precision=3]{9.96564e-06} $\pm$ \num[round-mode=figures,round-precision=3]{1.24703e-05} \\ 
  W+jetscharm   & \num[round-mode=figures,round-precision=3]{115.305} $\pm$ \num[round-mode=figures,round-precision=3]{56.3834} & \num[round-mode=figures,round-precision=3]{1.21567} $\pm$ \num[round-mode=figures,round-precision=3]{0.666388} & \num[round-mode=figures,round-precision=3]{0.00240026} $\pm$ \num[round-mode=figures,round-precision=3]{0.00148325} & \num[round-mode=figures,round-precision=3]{47.0596} $\pm$ \num[round-mode=figures,round-precision=3]{22.8395} & \num[round-mode=figures,round-precision=3]{0.71657} $\pm$ \num[round-mode=figures,round-precision=3]{0.39251} & \num[round-mode=figures,round-precision=3]{0.00222823} $\pm$ \num[round-mode=figures,round-precision=3]{0.00141395} & \num[round-mode=figures,round-precision=3]{21.4321} $\pm$ \num[round-mode=figures,round-precision=3]{10.9827} & \num[round-mode=figures,round-precision=3]{0.608391} $\pm$ \num[round-mode=figures,round-precision=3]{0.342486} & \num[round-mode=figures,round-precision=3]{0.00339913} $\pm$ \num[round-mode=figures,round-precision=3]{0.00224384} \\ 
  W+jetsbeauty   & \num[round-mode=figures,round-precision=3]{4726.45} $\pm$ \num[round-mode=figures,round-precision=3]{1836.48} & \num[round-mode=figures,round-precision=3]{260.312} $\pm$ \num[round-mode=figures,round-precision=3]{104.409} & \num[round-mode=figures,round-precision=3]{2.88562} $\pm$ \num[round-mode=figures,round-precision=3]{1.346} & \num[round-mode=figures,round-precision=3]{2051.07} $\pm$ \num[round-mode=figures,round-precision=3]{819.003} & \num[round-mode=figures,round-precision=3]{168.887} $\pm$ \num[round-mode=figures,round-precision=3]{68.0043} & \num[round-mode=figures,round-precision=3]{6.0271} $\pm$ \num[round-mode=figures,round-precision=3]{2.82667} & \num[round-mode=figures,round-precision=3]{1185.98} $\pm$ \num[round-mode=figures,round-precision=3]{472.732} & \num[round-mode=figures,round-precision=3]{183.822} $\pm$ \num[round-mode=figures,round-precision=3]{75.4584} & \num[round-mode=figures,round-precision=3]{12.5462} $\pm$ \num[round-mode=figures,round-precision=3]{5.73829} \\ 
  Z+jetslight   & \num[round-mode=figures,round-precision=3]{1.61066} $\pm$ \num[round-mode=figures,round-precision=3]{1.54715} & \num[round-mode=figures,round-precision=3]{0.00375032} $\pm$ \num[round-mode=figures,round-precision=3]{0.00414649} & \num[round-mode=figures,round-precision=3]{1.39446e-06} $\pm$ \num[round-mode=figures,round-precision=3]{1.64694e-06} & \num[round-mode=figures,round-precision=3]{0.659446} $\pm$ \num[round-mode=figures,round-precision=3]{0.630272} & \num[round-mode=figures,round-precision=3]{0.00250007} $\pm$ \num[round-mode=figures,round-precision=3]{0.00279867} & \num[round-mode=figures,round-precision=3]{1.85341e-06} $\pm$ \num[round-mode=figures,round-precision=3]{2.26403e-06} & \num[round-mode=figures,round-precision=3]{0.302002} $\pm$ \num[round-mode=figures,round-precision=3]{0.273111} & \num[round-mode=figures,round-precision=3]{0.00216257} $\pm$ \num[round-mode=figures,round-precision=3]{0.00245868} & \num[round-mode=figures,round-precision=3]{2.97446e-06} $\pm$ \num[round-mode=figures,round-precision=3]{3.69548e-06} \\ 
  Z+jetscharm   & \num[round-mode=figures,round-precision=3]{20.2778} $\pm$ \num[round-mode=figures,round-precision=3]{9.77507} & \num[round-mode=figures,round-precision=3]{0.192583} $\pm$ \num[round-mode=figures,round-precision=3]{0.105433} & \num[round-mode=figures,round-precision=3]{0.000330274} $\pm$ \num[round-mode=figures,round-precision=3]{0.000208386} & \num[round-mode=figures,round-precision=3]{8.36981} $\pm$ \num[round-mode=figures,round-precision=3]{4.04635} & \num[round-mode=figures,round-precision=3]{0.127165} $\pm$ \num[round-mode=figures,round-precision=3]{0.0699958} & \num[round-mode=figures,round-precision=3]{0.000455404} $\pm$ \num[round-mode=figures,round-precision=3]{0.000281893} & \num[round-mode=figures,round-precision=3]{4.46059} $\pm$ \num[round-mode=figures,round-precision=3]{2.19994} & \num[round-mode=figures,round-precision=3]{0.124792} $\pm$ \num[round-mode=figures,round-precision=3]{0.0687308} & \num[round-mode=figures,round-precision=3]{0.000758631} $\pm$ \num[round-mode=figures,round-precision=3]{0.00047388} \\ 
  Z+jetsbeauty   & \num[round-mode=figures,round-precision=3]{1857.53} $\pm$ \num[round-mode=figures,round-precision=3]{727.411} & \num[round-mode=figures,round-precision=3]{102.596} $\pm$ \num[round-mode=figures,round-precision=3]{41.3086} & \num[round-mode=figures,round-precision=3]{1.9331} $\pm$ \num[round-mode=figures,round-precision=3]{1.03534} & \num[round-mode=figures,round-precision=3]{698.171} $\pm$ \num[round-mode=figures,round-precision=3]{274.747} & \num[round-mode=figures,round-precision=3]{74.3953} $\pm$ \num[round-mode=figures,round-precision=3]{30.343} & \num[round-mode=figures,round-precision=3]{5.58037} $\pm$ \num[round-mode=figures,round-precision=3]{3.22145} & \num[round-mode=figures,round-precision=3]{353.402} $\pm$ \num[round-mode=figures,round-precision=3]{146.179} & \num[round-mode=figures,round-precision=3]{56.5389} $\pm$ \num[round-mode=figures,round-precision=3]{23.7814} & \num[round-mode=figures,round-precision=3]{3.53814} $\pm$ \num[round-mode=figures,round-precision=3]{2.14836} \\ 
  Single-top   & \num[round-mode=figures,round-precision=3]{6394.03} $\pm$ \num[round-mode=figures,round-precision=3]{883.786} & \num[round-mode=figures,round-precision=3]{398.806} $\pm$ \num[round-mode=figures,round-precision=3]{70.2783} & \num[round-mode=figures,round-precision=3]{8.12021} $\pm$ \num[round-mode=figures,round-precision=3]{3.29235} & \num[round-mode=figures,round-precision=3]{2586.28} $\pm$ \num[round-mode=figures,round-precision=3]{545.244} & \num[round-mode=figures,round-precision=3]{325.205} $\pm$ \num[round-mode=figures,round-precision=3]{73.1068} & \num[round-mode=figures,round-precision=3]{13.5356} $\pm$ \num[round-mode=figures,round-precision=3]{4.21865} & \num[round-mode=figures,round-precision=3]{1247.31} $\pm$ \num[round-mode=figures,round-precision=3]{360.081} & \num[round-mode=figures,round-precision=3]{321.943} $\pm$ \num[round-mode=figures,round-precision=3]{98.5638} & \num[round-mode=figures,round-precision=3]{27.8892} $\pm$ \num[round-mode=figures,round-precision=3]{10.1643} \\ 
  Dibosons   & \num[round-mode=figures,round-precision=3]{242.502} $\pm$ \num[round-mode=figures,round-precision=3]{84.0284} & \num[round-mode=figures,round-precision=3]{16.2373} $\pm$ \num[round-mode=figures,round-precision=3]{5.71578} & \num[round-mode=figures,round-precision=3]{0.494856} $\pm$ \num[round-mode=figures,round-precision=3]{0.222674} & \num[round-mode=figures,round-precision=3]{111.655} $\pm$ \num[round-mode=figures,round-precision=3]{47.8353} & \num[round-mode=figures,round-precision=3]{12.47} $\pm$ \num[round-mode=figures,round-precision=3]{5.44917} & \num[round-mode=figures,round-precision=3]{0.764199} $\pm$ \num[round-mode=figures,round-precision=3]{0.392172} & \num[round-mode=figures,round-precision=3]{82.228} $\pm$ \num[round-mode=figures,round-precision=3]{40.0442} & \num[round-mode=figures,round-precision=3]{16.7013} $\pm$ \num[round-mode=figures,round-precision=3]{8.21106} & \num[round-mode=figures,round-precision=3]{1.70033} $\pm$ \num[round-mode=figures,round-precision=3]{0.901524} \\ 
  SM-4tops   & \num[round-mode=figures,round-precision=3]{0.102052} $\pm$ \num[round-mode=figures,round-precision=3]{0.0378717} & \num[round-mode=figures,round-precision=3]{0.0964359} $\pm$ \num[round-mode=figures,round-precision=3]{0.0364277} & \num[round-mode=figures,round-precision=3]{0.00739477} $\pm$ \num[round-mode=figures,round-precision=3]{0.00590938} & \num[round-mode=figures,round-precision=3]{0.367211} $\pm$ \num[round-mode=figures,round-precision=3]{0.126578} & \num[round-mode=figures,round-precision=3]{0.491049} $\pm$ \num[round-mode=figures,round-precision=3]{0.156563} & \num[round-mode=figures,round-precision=3]{0.0540613} $\pm$ \num[round-mode=figures,round-precision=3]{0.0203091} & \num[round-mode=figures,round-precision=3]{5.14473} $\pm$ \num[round-mode=figures,round-precision=3]{1.54452} & \num[round-mode=figures,round-precision=3]{19.1387} $\pm$ \num[round-mode=figures,round-precision=3]{5.77773} & \num[round-mode=figures,round-precision=3]{4.96117} $\pm$ \num[round-mode=figures,round-precision=3]{1.54499} \\ 
  QCDE   & \num[round-mode=figures,round-precision=3]{7789.54} $\pm$ \num[round-mode=figures,round-precision=3]{3437.44} & \num[round-mode=figures,round-precision=3]{600.731} $\pm$ \num[round-mode=figures,round-precision=3]{229.327} & \num[round-mode=figures,round-precision=3]{20.0736} $\pm$ \num[round-mode=figures,round-precision=3]{14.1015} & \num[round-mode=figures,round-precision=3]{2657.64} $\pm$ \num[round-mode=figures,round-precision=3]{935.089} & \num[round-mode=figures,round-precision=3]{486.701} $\pm$ \num[round-mode=figures,round-precision=3]{221.708} & \num[round-mode=figures,round-precision=3]{3.606} $\pm$ \num[round-mode=figures,round-precision=3]{4.81275} & \num[round-mode=figures,round-precision=3]{1220.05} $\pm$ \num[round-mode=figures,round-precision=3]{500.496} & \num[round-mode=figures,round-precision=3]{747.705} $\pm$ \num[round-mode=figures,round-precision=3]{336.918} & \num[round-mode=figures,round-precision=3]{28.4241} $\pm$ \num[round-mode=figures,round-precision=3]{24.6852} \\ 
  QCDMU   & \num[round-mode=figures,round-precision=3]{1250.71} $\pm$ \num[round-mode=figures,round-precision=3]{637.813} & \num[round-mode=figures,round-precision=3]{209.581} $\pm$ \num[round-mode=figures,round-precision=3]{98.6358} & \num[round-mode=figures,round-precision=3]{9.02057} $\pm$ \num[round-mode=figures,round-precision=3]{8.46944} & \num[round-mode=figures,round-precision=3]{737.502} $\pm$ \num[round-mode=figures,round-precision=3]{369.549} & \num[round-mode=figures,round-precision=3]{71.1185} $\pm$ \num[round-mode=figures,round-precision=3]{44.7342} & \num[round-mode=figures,round-precision=3]{2e-05} $\pm$ \num[round-mode=figures,round-precision=3]{1.00366e-05} & \num[round-mode=figures,round-precision=3]{307.593} $\pm$ \num[round-mode=figures,round-precision=3]{164.21} & \num[round-mode=figures,round-precision=3]{107.547} $\pm$ \num[round-mode=figures,round-precision=3]{63.7469} & \num[round-mode=figures,round-precision=3]{8.52575} $\pm$ \num[round-mode=figures,round-precision=3]{8.0648} \\ 
\hline 
  Total  & \num[round-mode=figures,round-precision=3]{121060} $\pm$ \num[round-mode=figures,round-precision=3]{2157.23} & \num[round-mode=figures,round-precision=3]{11294.8} $\pm$ \num[round-mode=figures,round-precision=3]{284.411} & \num[round-mode=figures,round-precision=3]{180.903} $\pm$ \num[round-mode=figures,round-precision=3]{23.0855} & \num[round-mode=figures,round-precision=3]{58830.7} $\pm$ \num[round-mode=figures,round-precision=3]{1376.45} & \num[round-mode=figures,round-precision=3]{11689.4} $\pm$ \num[round-mode=figures,round-precision=3]{361.345} & \num[round-mode=figures,round-precision=3]{465.026} $\pm$ \num[round-mode=figures,round-precision=3]{29.0489} & \num[round-mode=figures,round-precision=3]{35997.5} $\pm$ \num[round-mode=figures,round-precision=3]{1273.84} & \num[round-mode=figures,round-precision=3]{14883.3} $\pm$ \num[round-mode=figures,round-precision=3]{502.308} & \num[round-mode=figures,round-precision=3]{1360.95} $\pm$ \num[round-mode=figures,round-precision=3]{71.384} \\ 
\hline 
  Data   & 120572 & 11275 & 176 & 58557 & 11707 & 466 & 35886 & 14877 & 1335 \\ 
\hline 
\end{tabular} 
\caption{Yields of the analysis} 
\end{center} 
\end{table} 
\end{document}

### 2018-06-30 figures/Hbb/fit/base_ebv2_signal_cH_default_unblinded_splusb/Tables/Yields_postFit.tex
Paper draft moved to official repository

\documentclass[10pt]{article}
\usepackage{siunitx}
\usepackage[margin=0.1in,landscape,papersize={210mm,350mm}]{geometry}
\begin{document}
\begin{table}[htbp]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline 
 & 4jex-2bex & 4jex-3bex & 4jex-4bin & 5jex-2bex & 5jex-3bex & 5jex-4bin & 6jin-2bex & 6jin-3bex & 6jin-4bin\\
\hline 
  t#bar{t}+light   & \num[round-mode=figures,round-precision=3]{82845.9} $\pm$ \num[round-mode=figures,round-precision=3]{4191.85} & \num[round-mode=figures,round-precision=3]{4876.76} $\pm$ \num[round-mode=figures,round-precision=3]{501.636} & \num[round-mode=figures,round-precision=3]{15.5023} $\pm$ \num[round-mode=figures,round-precision=3]{12.3028} & \num[round-mode=figures,round-precision=3]{38012.6} $\pm$ \num[round-mode=figures,round-precision=3]{3128.71} & \num[round-mode=figures,round-precision=3]{3483.9} $\pm$ \num[round-mode=figures,round-precision=3]{466.698} & \num[round-mode=figures,round-precision=3]{15.8022} $\pm$ \num[round-mode=figures,round-precision=3]{9.49199} & \num[round-mode=figures,round-precision=3]{20096.7} $\pm$ \num[round-mode=figures,round-precision=3]{2531.65} & \num[round-mode=figures,round-precision=3]{2562.53} $\pm$ \num[round-mode=figures,round-precision=3]{491.271} & \num[round-mode=figures,round-precision=3]{21.4468} $\pm$ \num[round-mode=figures,round-precision=3]{23.4984} \\ 
  t#bar{t}+cc   & \num[round-mode=figures,round-precision=3]{11400} $\pm$ \num[round-mode=figures,round-precision=3]{4887.9} & \num[round-mode=figures,round-precision=3]{1360.1} $\pm$ \num[round-mode=figures,round-precision=3]{565.564} & \num[round-mode=figures,round-precision=3]{5.94047} $\pm$ \num[round-mode=figures,round-precision=3]{4.25326} & \num[round-mode=figures,round-precision=3]{8311.77} $\pm$ \num[round-mode=figures,round-precision=3]{3520.68} & \num[round-mode=figures,round-precision=3]{2000.89} $\pm$ \num[round-mode=figures,round-precision=3]{780.569} & \num[round-mode=figures,round-precision=3]{39.4621} $\pm$ \num[round-mode=figures,round-precision=3]{18.4738} & \num[round-mode=figures,round-precision=3]{7750.5} $\pm$ \num[round-mode=figures,round-precision=3]{3352.71} & \num[round-mode=figures,round-precision=3]{2974.4} $\pm$ \num[round-mode=figures,round-precision=3]{1173.97} & \num[round-mode=figures,round-precision=3]{58.8447} $\pm$ \num[round-mode=figures,round-precision=3]{25.671} \\ 
  t#bar{t}+bb   & \num[round-mode=figures,round-precision=3]{4284.48} $\pm$ \num[round-mode=figures,round-precision=3]{592.115} & \num[round-mode=figures,round-precision=3]{3403.26} $\pm$ \num[round-mode=figures,round-precision=3]{353.025} & \num[round-mode=figures,round-precision=3]{109.946} $\pm$ \num[round-mode=figures,round-precision=3]{16.8869} & \num[round-mode=figures,round-precision=3]{3415.95} $\pm$ \num[round-mode=figures,round-precision=3]{467.024} & \num[round-mode=figures,round-precision=3]{4917.61} $\pm$ \num[round-mode=figures,round-precision=3]{460.154} & \num[round-mode=figures,round-precision=3]{355.879} $\pm$ \num[round-mode=figures,round-precision=3]{28.7979} & \num[round-mode=figures,round-precision=3]{3396.38} $\pm$ \num[round-mode=figures,round-precision=3]{482.853} & \num[round-mode=figures,round-precision=3]{7517.33} $\pm$ \num[round-mode=figures,round-precision=3]{766.8} & \num[round-mode=figures,round-precision=3]{1105.78} $\pm$ \num[round-mode=figures,round-precision=3]{83.3295} \\ 
  topEW   & \num[round-mode=figures,round-precision=3]{173.513} $\pm$ \num[round-mode=figures,round-precision=3]{27.6992} & \num[round-mode=figures,round-precision=3]{35.0108} $\pm$ \num[round-mode=figures,round-precision=3]{5.8841} & \num[round-mode=figures,round-precision=3]{2.68504} $\pm$ \num[round-mode=figures,round-precision=3]{0.54471} & \num[round-mode=figures,round-precision=3]{167.542} $\pm$ \num[round-mode=figures,round-precision=3]{25.9028} & \num[round-mode=figures,round-precision=3]{65.4134} $\pm$ \num[round-mode=figures,round-precision=3]{10.4831} & \num[round-mode=figures,round-precision=3]{8.1585} $\pm$ \num[round-mode=figures,round-precision=3]{1.43202} & \num[round-mode=figures,round-precision=3]{212.274} $\pm$ \num[round-mode=figures,round-precision=3]{34.0437} & \num[round-mode=figures,round-precision=3]{146.736} $\pm$ \num[round-mode=figures,round-precision=3]{23.793} & \num[round-mode=figures,round-precision=3]{26.9001} $\pm$ \num[round-mode=figures,round-precision=3]{4.77355} \\ 
  ttH   & \num[round-mode=figures,round-precision=3]{62.6374} $\pm$ \num[round-mode=figures,round-precision=3]{7.83319} & \num[round-mode=figures,round-precision=3]{47.2558} $\pm$ \num[round-mode=figures,round-precision=3]{6.24357} & \num[round-mode=figures,round-precision=3]{4.67124} $\pm$ \num[round-mode=figures,round-precision=3]{0.684293} & \num[round-mode=figures,round-precision=3]{81.125} $\pm$ \num[round-mode=figures,round-precision=3]{8.92534} & \num[round-mode=figures,round-precision=3]{98.6353} $\pm$ \num[round-mode=figures,round-precision=3]{11.6012} & \num[round-mode=figures,round-precision=3]{16.5663} $\pm$ \num[round-mode=figures,round-precision=3]{2.29956} & \num[round-mode=figures,round-precision=3]{134.283} $\pm$ \num[round-mode=figures,round-precision=3]{15.464} & \num[round-mode=figures,round-precision=3]{239.948} $\pm$ \num[round-mode=figures,round-precision=3]{29.4611} & \num[round-mode=figures,round-precision=3]{61.4684} $\pm$ \num[round-mode=figures,round-precision=3]{8.75464} \\ 
  W+jetslight   & \num[round-mode=figures,round-precision=3]{6.1336} $\pm$ \num[round-mode=figures,round-precision=3]{6.31334} & \num[round-mode=figures,round-precision=3]{0.0116485} $\pm$ \num[round-mode=figures,round-precision=3]{0.0131938} & \num[round-mode=figures,round-precision=3]{4.05355e-06} $\pm$ \num[round-mode=figures,round-precision=3]{4.99067e-06} & \num[round-mode=figures,round-precision=3]{2.43781} $\pm$ \num[round-mode=figures,round-precision=3]{2.37932} & \num[round-mode=figures,round-precision=3]{0.0082768} $\pm$ \num[round-mode=figures,round-precision=3]{0.00937337} & \num[round-mode=figures,round-precision=3]{5.90626e-06} $\pm$ \num[round-mode=figures,round-precision=3]{7.22549e-06} & \num[round-mode=figures,round-precision=3]{1.14104} $\pm$ \num[round-mode=figures,round-precision=3]{1.07961} & \num[round-mode=figures,round-precision=3]{0.00748122} $\pm$ \num[round-mode=figures,round-precision=3]{0.0085961} & \num[round-mode=figures,round-precision=3]{9.93564e-06} $\pm$ \num[round-mode=figures,round-precision=3]{1.24269e-05} \\ 
  W+jetscharm   & \num[round-mode=figures,round-precision=3]{116.205} $\pm$ \num[round-mode=figures,round-precision=3]{59.336} & \num[round-mode=figures,round-precision=3]{1.23128} $\pm$ \num[round-mode=figures,round-precision=3]{0.746056} & \num[round-mode=figures,round-precision=3]{0.0024402} $\pm$ \num[round-mode=figures,round-precision=3]{0.00177021} & \num[round-mode=figures,round-precision=3]{47.3914} $\pm$ \num[round-mode=figures,round-precision=3]{23.9413} & \num[round-mode=figures,round-precision=3]{0.724028} $\pm$ \num[round-mode=figures,round-precision=3]{0.430586} & \num[round-mode=figures,round-precision=3]{0.00225932} $\pm$ \num[round-mode=figures,round-precision=3]{0.00162516} & \num[round-mode=figures,round-precision=3]{21.4785} $\pm$ \num[round-mode=figures,round-precision=3]{11.1851} & \num[round-mode=figures,round-precision=3]{0.613245} $\pm$ \num[round-mode=figures,round-precision=3]{0.367519} & \num[round-mode=figures,round-precision=3]{0.00343852} $\pm$ \num[round-mode=figures,round-precision=3]{0.0025106} \\ 
  W+jetsbeauty   & \num[round-mode=figures,round-precision=3]{4726.21} $\pm$ \num[round-mode=figures,round-precision=3]{1836.34} & \num[round-mode=figures,round-precision=3]{260.722} $\pm$ \num[round-mode=figures,round-precision=3]{104.695} & \num[round-mode=figures,round-precision=3]{2.88981} $\pm$ \num[round-mode=figures,round-precision=3]{1.34734} & \num[round-mode=figures,round-precision=3]{2047.29} $\pm$ \num[round-mode=figures,round-precision=3]{818.158} & \num[round-mode=figures,round-precision=3]{169.025} $\pm$ \num[round-mode=figures,round-precision=3]{68.0819} & \num[round-mode=figures,round-precision=3]{6.02499} $\pm$ \num[round-mode=figures,round-precision=3]{2.82343} & \num[round-mode=figures,round-precision=3]{1182.94} $\pm$ \num[round-mode=figures,round-precision=3]{472.32} & \num[round-mode=figures,round-precision=3]{183.637} $\pm$ \num[round-mode=figures,round-precision=3]{75.3516} & \num[round-mode=figures,round-precision=3]{12.5256} $\pm$ \num[round-mode=figures,round-precision=3]{5.727} \\ 
  Z+jetslight   & \num[round-mode=figures,round-precision=3]{1.6136} $\pm$ \num[round-mode=figures,round-precision=3]{1.55208} & \num[round-mode=figures,round-precision=3]{0.00375869} $\pm$ \num[round-mode=figures,round-precision=3]{0.00416768} & \num[round-mode=figures,round-precision=3]{1.39758e-06} $\pm$ \num[round-mode=figures,round-precision=3]{1.65619e-06} & \num[round-mode=figures,round-precision=3]{0.660099} $\pm$ \num[round-mode=figures,round-precision=3]{0.631076} & \num[round-mode=figures,round-precision=3]{0.00250452} $\pm$ \num[round-mode=figures,round-precision=3]{0.00281062} & \num[round-mode=figures,round-precision=3]{1.85667e-06} $\pm$ \num[round-mode=figures,round-precision=3]{2.27538e-06} & \num[round-mode=figures,round-precision=3]{0.301938} $\pm$ \num[round-mode=figures,round-precision=3]{0.272929} & \num[round-mode=figures,round-precision=3]{0.00216152} $\pm$ \num[round-mode=figures,round-precision=3]{0.00245911} & \num[round-mode=figures,round-precision=3]{2.97083e-06} $\pm$ \num[round-mode=figures,round-precision=3]{3.69504e-06} \\ 
  Z+jetscharm   & \num[round-mode=figures,round-precision=3]{20.4352} $\pm$ \num[round-mode=figures,round-precision=3]{10.3151} & \num[round-mode=figures,round-precision=3]{0.194919} $\pm$ \num[round-mode=figures,round-precision=3]{0.117146} & \num[round-mode=figures,round-precision=3]{0.000335712} $\pm$ \num[round-mode=figures,round-precision=3]{0.000245841} & \num[round-mode=figures,round-precision=3]{8.4355} $\pm$ \num[round-mode=figures,round-precision=3]{4.26127} & \num[round-mode=figures,round-precision=3]{0.128524} $\pm$ \num[round-mode=figures,round-precision=3]{0.0768793} & \num[round-mode=figures,round-precision=3]{0.000462529} $\pm$ \num[round-mode=figures,round-precision=3]{0.000332929} & \num[round-mode=figures,round-precision=3]{4.48254} $\pm$ \num[round-mode=figures,round-precision=3]{2.27427} & \num[round-mode=figures,round-precision=3]{0.126082} $\pm$ \num[round-mode=figures,round-precision=3]{0.0751513} & \num[round-mode=figures,round-precision=3]{0.000769429} $\pm$ \num[round-mode=figures,round-precision=3]{0.000545109} \\ 
  Z+jetsbeauty   & \num[round-mode=figures,round-precision=3]{1855.81} $\pm$ \num[round-mode=figures,round-precision=3]{726.854} & \num[round-mode=figures,round-precision=3]{102.616} $\pm$ \num[round-mode=figures,round-precision=3]{41.3097} & \num[round-mode=figures,round-precision=3]{1.93486} $\pm$ \num[round-mode=figures,round-precision=3]{1.03531} & \num[round-mode=figures,round-precision=3]{697.466} $\pm$ \num[round-mode=figures,round-precision=3]{274.516} & \num[round-mode=figures,round-precision=3]{74.4819} $\pm$ \num[round-mode=figures,round-precision=3]{30.3853} & \num[round-mode=figures,round-precision=3]{5.61523} $\pm$ \num[round-mode=figures,round-precision=3]{3.25619} & \num[round-mode=figures,round-precision=3]{352.092} $\pm$ \num[round-mode=figures,round-precision=3]{146.124} & \num[round-mode=figures,round-precision=3]{56.4242} $\pm$ \num[round-mode=figures,round-precision=3]{23.7334} & \num[round-mode=figures,round-precision=3]{3.4745} $\pm$ \num[round-mode=figures,round-precision=3]{2.17451} \\ 
  Single-top   & \num[round-mode=figures,round-precision=3]{6381.22} $\pm$ \num[round-mode=figures,round-precision=3]{885.113} & \num[round-mode=figures,round-precision=3]{399.607} $\pm$ \num[round-mode=figures,round-precision=3]{71.404} & \num[round-mode=figures,round-precision=3]{8.18061} $\pm$ \num[round-mode=figures,round-precision=3]{3.39484} & \num[round-mode=figures,round-precision=3]{2576.53} $\pm$ \num[round-mode=figures,round-precision=3]{548.887} & \num[round-mode=figures,round-precision=3]{325.298} $\pm$ \num[round-mode=figures,round-precision=3]{72.9207} & \num[round-mode=figures,round-precision=3]{13.5136} $\pm$ \num[round-mode=figures,round-precision=3]{4.20447} & \num[round-mode=figures,round-precision=3]{1239.51} $\pm$ \num[round-mode=figures,round-precision=3]{364.164} & \num[round-mode=figures,round-precision=3]{320.996} $\pm$ \num[round-mode=figures,round-precision=3]{98.2455} & \num[round-mode=figures,round-precision=3]{27.779} $\pm$ \num[round-mode=figures,round-precision=3]{10.1227} \\ 
  Dibosons   & \num[round-mode=figures,round-precision=3]{241.784} $\pm$ \num[round-mode=figures,round-precision=3]{84.0429} & \num[round-mode=figures,round-precision=3]{16.2441} $\pm$ \num[round-mode=figures,round-precision=3]{5.71612} & \num[round-mode=figures,round-precision=3]{0.495344} $\pm$ \num[round-mode=figures,round-precision=3]{0.222611} & \num[round-mode=figures,round-precision=3]{111.156} $\pm$ \num[round-mode=figures,round-precision=3]{47.8556} & \num[round-mode=figures,round-precision=3]{12.4395} $\pm$ \num[round-mode=figures,round-precision=3]{5.43722} & \num[round-mode=figures,round-precision=3]{0.762558} $\pm$ \num[round-mode=figures,round-precision=3]{0.391318} & \num[round-mode=figures,round-precision=3]{81.8407} $\pm$ \num[round-mode=figures,round-precision=3]{40.0188} & \num[round-mode=figures,round-precision=3]{16.6495} $\pm$ \num[round-mode=figures,round-precision=3]{8.19213} & \num[round-mode=figures,round-precision=3]{1.69053} $\pm$ \num[round-mode=figures,round-precision=3]{0.900296} \\ 
  SM-4tops   & \num[round-mode=figures,round-precision=3]{0.102591} $\pm$ \num[round-mode=figures,round-precision=3]{0.0384966} & \num[round-mode=figures,round-precision=3]{0.0969286} $\pm$ \num[round-mode=figures,round-precision=3]{0.0370062} & \num[round-mode=figures,round-precision=3]{0.0075197} $\pm$ \num[round-mode=figures,round-precision=3]{0.00617004} & \num[round-mode=figures,round-precision=3]{0.370247} $\pm$ \num[round-mode=figures,round-precision=3]{0.131963} & \num[round-mode=figures,round-precision=3]{0.492893} $\pm$ \num[round-mode=figures,round-precision=3]{0.158354} & \num[round-mode=figures,round-precision=3]{0.0541635} $\pm$ \num[round-mode=figures,round-precision=3]{0.0203327} & \num[round-mode=figures,round-precision=3]{5.14211} $\pm$ \num[round-mode=figures,round-precision=3]{1.54412} & \num[round-mode=figures,round-precision=3]{19.1277} $\pm$ \num[round-mode=figures,round-precision=3]{5.77236} & \num[round-mode=figures,round-precision=3]{4.95833} $\pm$ \num[round-mode=figures,round-precision=3]{1.54097} \\ 
  QCDE   & \num[round-mode=figures,round-precision=3]{7764.72} $\pm$ \num[round-mode=figures,round-precision=3]{3429.04} & \num[round-mode=figures,round-precision=3]{604.567} $\pm$ \num[round-mode=figures,round-precision=3]{233.932} & \num[round-mode=figures,round-precision=3]{20.0741} $\pm$ \num[round-mode=figures,round-precision=3]{14.1034} & \num[round-mode=figures,round-precision=3]{2645.66} $\pm$ \num[round-mode=figures,round-precision=3]{942.842} & \num[round-mode=figures,round-precision=3]{488.552} $\pm$ \num[round-mode=figures,round-precision=3]{225.005} & \num[round-mode=figures,round-precision=3]{3.60926} $\pm$ \num[round-mode=figures,round-precision=3]{4.81359} & \num[round-mode=figures,round-precision=3]{1224.61} $\pm$ \num[round-mode=figures,round-precision=3]{505.51} & \num[round-mode=figures,round-precision=3]{750.291} $\pm$ \num[round-mode=figures,round-precision=3]{341.548} & \num[round-mode=figures,round-precision=3]{28.4377} $\pm$ \num[round-mode=figures,round-precision=3]{24.6942} \\ 
  QCDMU   & \num[round-mode=figures,round-precision=3]{1249.61} $\pm$ \num[round-mode=figures,round-precision=3]{635.577} & \num[round-mode=figures,round-precision=3]{211.163} $\pm$ \num[round-mode=figures,round-precision=3]{100.134} & \num[round-mode=figures,round-precision=3]{9.03359} $\pm$ \num[round-mode=figures,round-precision=3]{8.47382} & \num[round-mode=figures,round-precision=3]{736.919} $\pm$ \num[round-mode=figures,round-precision=3]{369.678} & \num[round-mode=figures,round-precision=3]{71.0056} $\pm$ \num[round-mode=figures,round-precision=3]{44.6986} & \num[round-mode=figures,round-precision=3]{2e-05} $\pm$ \num[round-mode=figures,round-precision=3]{1.00366e-05} & \num[round-mode=figures,round-precision=3]{307.769} $\pm$ \num[round-mode=figures,round-precision=3]{164.21} & \num[round-mode=figures,round-precision=3]{107.601} $\pm$ \num[round-mode=figures,round-precision=3]{63.7808} & \num[round-mode=figures,round-precision=3]{8.52704} $\pm$ \num[round-mode=figures,round-precision=3]{8.06522} \\ 
  t#rightarrow Hc   & \num[round-mode=figures,round-precision=3]{-41.3493} $\pm$ \num[round-mode=figures,round-precision=3]{2.19773} & \num[round-mode=figures,round-precision=3]{-25.154} $\pm$ \num[round-mode=figures,round-precision=3]{1.71134} & \num[round-mode=figures,round-precision=3]{-0.519194} $\pm$ \num[round-mode=figures,round-precision=3]{0.149156} & \num[round-mode=figures,round-precision=3]{-25.4783} $\pm$ \num[round-mode=figures,round-precision=3]{2.09826} & \num[round-mode=figures,round-precision=3]{-18.9684} $\pm$ \num[round-mode=figures,round-precision=3]{1.89817} & \num[round-mode=figures,round-precision=3]{-0.555763} $\pm$ \num[round-mode=figures,round-precision=3]{0.153039} & \num[round-mode=figures,round-precision=3]{-15.0656} $\pm$ \num[round-mode=figures,round-precision=3]{1.66578} & \num[round-mode=figures,round-precision=3]{-12.4407} $\pm$ \num[round-mode=figures,round-precision=3]{1.72397} & \num[round-mode=figures,round-precision=3]{-1.17541} $\pm$ \num[round-mode=figures,round-precision=3]{0.234336} \\ 
\hline 
  Total  & \num[round-mode=figures,round-precision=3]{121130} $\pm$ \num[round-mode=figures,round-precision=3]{2239.1} & \num[round-mode=figures,round-precision=3]{11318.8} $\pm$ \num[round-mode=figures,round-precision=3]{413.449} & \num[round-mode=figures,round-precision=3]{181.363} $\pm$ \num[round-mode=figures,round-precision=3]{24.0046} & \num[round-mode=figures,round-precision=3]{58863.3} $\pm$ \num[round-mode=figures,round-precision=3]{1460.61} & \num[round-mode=figures,round-precision=3]{11708.6} $\pm$ \num[round-mode=figures,round-precision=3]{438.063} & \num[round-mode=figures,round-precision=3]{465.451} $\pm$ \num[round-mode=figures,round-precision=3]{29.8603} & \num[round-mode=figures,round-precision=3]{36011.4} $\pm$ \num[round-mode=figures,round-precision=3]{1318.36} & \num[round-mode=figures,round-precision=3]{14896.4} $\pm$ \num[round-mode=figures,round-precision=3]{550.482} & \num[round-mode=figures,round-precision=3]{1361.84} $\pm$ \num[round-mode=figures,round-precision=3]{76.7609} \\ 
\hline 
  Data   & 120572 & 11275 & 176 & 58557 & 11707 & 466 & 35886 & 14877 & 1335 \\ 
\hline 
\end{tabular} 
\caption{Yields of the analysis} 
\end{center} 
\end{table} 
\end{document}

### 2018-06-30 figures/Hbb/fit/base_ebv2_signal_uH_default_unblinded/Tables/Yields_postFit.tex
Paper draft moved to official repository

\documentclass[10pt]{article}
\usepackage{siunitx}
\usepackage[margin=0.1in,landscape,papersize={210mm,350mm}]{geometry}
\begin{document}
\begin{table}[htbp]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline 
 & 4jex-2bex & 4jex-3bex & 4jex-4bin & 5jex-2bex & 5jex-3bex & 5jex-4bin & 6jin-2bex & 6jin-3bex & 6jin-4bin\\
\hline 
  t#bar{t}+light   & \num[round-mode=figures,round-precision=3]{82736.7} $\pm$ \num[round-mode=figures,round-precision=3]{3818.29} & \num[round-mode=figures,round-precision=3]{4870.48} $\pm$ \num[round-mode=figures,round-precision=3]{447.527} & \num[round-mode=figures,round-precision=3]{15.4586} $\pm$ \num[round-mode=figures,round-precision=3]{12.0169} & \num[round-mode=figures,round-precision=3]{37914.3} $\pm$ \num[round-mode=figures,round-precision=3]{2736.89} & \num[round-mode=figures,round-precision=3]{3470.01} $\pm$ \num[round-mode=figures,round-precision=3]{391.763} & \num[round-mode=figures,round-precision=3]{15.8632} $\pm$ \num[round-mode=figures,round-precision=3]{9.43766} & \num[round-mode=figures,round-precision=3]{20004.4} $\pm$ \num[round-mode=figures,round-precision=3]{2231.26} & \num[round-mode=figures,round-precision=3]{2549.13} $\pm$ \num[round-mode=figures,round-precision=3]{421.22} & \num[round-mode=figures,round-precision=3]{20.8411} $\pm$ \num[round-mode=figures,round-precision=3]{18.6847} \\ 
  t#bar{t}+cc   & \num[round-mode=figures,round-precision=3]{11455.7} $\pm$ \num[round-mode=figures,round-precision=3]{4842.46} & \num[round-mode=figures,round-precision=3]{1357.71} $\pm$ \num[round-mode=figures,round-precision=3]{568.799} & \num[round-mode=figures,round-precision=3]{5.85958} $\pm$ \num[round-mode=figures,round-precision=3]{4.13801} & \num[round-mode=figures,round-precision=3]{8375.44} $\pm$ \num[round-mode=figures,round-precision=3]{3441.7} & \num[round-mode=figures,round-precision=3]{2002.26} $\pm$ \num[round-mode=figures,round-precision=3]{785.096} & \num[round-mode=figures,round-precision=3]{39.3117} $\pm$ \num[round-mode=figures,round-precision=3]{18.3893} & \num[round-mode=figures,round-precision=3]{7831.2} $\pm$ \num[round-mode=figures,round-precision=3]{3251.3} & \num[round-mode=figures,round-precision=3]{2987.79} $\pm$ \num[round-mode=figures,round-precision=3]{1175.41} & \num[round-mode=figures,round-precision=3]{58.7913} $\pm$ \num[round-mode=figures,round-precision=3]{25.5942} \\ 
  t#bar{t}+bb   & \num[round-mode=figures,round-precision=3]{4258.72} $\pm$ \num[round-mode=figures,round-precision=3]{574.914} & \num[round-mode=figures,round-precision=3]{3395.21} $\pm$ \num[round-mode=figures,round-precision=3]{352.791} & \num[round-mode=figures,round-precision=3]{109.833} $\pm$ \num[round-mode=figures,round-precision=3]{16.9058} & \num[round-mode=figures,round-precision=3]{3399.68} $\pm$ \num[round-mode=figures,round-precision=3]{457.628} & \num[round-mode=figures,round-precision=3]{4910.58} $\pm$ \num[round-mode=figures,round-precision=3]{460.487} & \num[round-mode=figures,round-precision=3]{355.573} $\pm$ \num[round-mode=figures,round-precision=3]{28.7152} & \num[round-mode=figures,round-precision=3]{3383.78} $\pm$ \num[round-mode=figures,round-precision=3]{479.152} & \num[round-mode=figures,round-precision=3]{7504.21} $\pm$ \num[round-mode=figures,round-precision=3]{761.754} & \num[round-mode=figures,round-precision=3]{1104.67} $\pm$ \num[round-mode=figures,round-precision=3]{81.3061} \\ 
  topEW   & \num[round-mode=figures,round-precision=3]{173.264} $\pm$ \num[round-mode=figures,round-precision=3]{27.3871} & \num[round-mode=figures,round-precision=3]{34.9273} $\pm$ \num[round-mode=figures,round-precision=3]{5.71128} & \num[round-mode=figures,round-precision=3]{2.6856} $\pm$ \num[round-mode=figures,round-precision=3]{0.540473} & \num[round-mode=figures,round-precision=3]{167.597} $\pm$ \num[round-mode=figures,round-precision=3]{25.9071} & \num[round-mode=figures,round-precision=3]{65.3758} $\pm$ \num[round-mode=figures,round-precision=3]{10.4063} & \num[round-mode=figures,round-precision=3]{8.17168} $\pm$ \num[round-mode=figures,round-precision=3]{1.43466} & \num[round-mode=figures,round-precision=3]{212.973} $\pm$ \num[round-mode=figures,round-precision=3]{33.7948} & \num[round-mode=figures,round-precision=3]{147.078} $\pm$ \num[round-mode=figures,round-precision=3]{23.8292} & \num[round-mode=figures,round-precision=3]{27.0128} $\pm$ \num[round-mode=figures,round-precision=3]{4.76994} \\ 
  ttH   & \num[round-mode=figures,round-precision=3]{62.4596} $\pm$ \num[round-mode=figures,round-precision=3]{7.54464} & \num[round-mode=figures,round-precision=3]{47.1617} $\pm$ \num[round-mode=figures,round-precision=3]{6.06109} & \num[round-mode=figures,round-precision=3]{4.66843} $\pm$ \num[round-mode=figures,round-precision=3]{0.673201} & \num[round-mode=figures,round-precision=3]{81.0522} $\pm$ \num[round-mode=figures,round-precision=3]{8.86567} & \num[round-mode=figures,round-precision=3]{98.6344} $\pm$ \num[round-mode=figures,round-precision=3]{11.548} & \num[round-mode=figures,round-precision=3]{16.5886} $\pm$ \num[round-mode=figures,round-precision=3]{2.29912} & \num[round-mode=figures,round-precision=3]{134.656} $\pm$ \num[round-mode=figures,round-precision=3]{15.1917} & \num[round-mode=figures,round-precision=3]{240.832} $\pm$ \num[round-mode=figures,round-precision=3]{28.9758} & \num[round-mode=figures,round-precision=3]{61.7553} $\pm$ \num[round-mode=figures,round-precision=3]{8.68497} \\ 
  W+jetslight   & \num[round-mode=figures,round-precision=3]{6.13687} $\pm$ \num[round-mode=figures,round-precision=3]{6.3726} & \num[round-mode=figures,round-precision=3]{0.0116191} $\pm$ \num[round-mode=figures,round-precision=3]{0.0132552} & \num[round-mode=figures,round-precision=3]{4.02838e-06} $\pm$ \num[round-mode=figures,round-precision=3]{4.9843e-06} & \num[round-mode=figures,round-precision=3]{2.4412} $\pm$ \num[round-mode=figures,round-precision=3]{2.40463} & \num[round-mode=figures,round-precision=3]{0.0082668} $\pm$ \num[round-mode=figures,round-precision=3]{0.0094287} & \num[round-mode=figures,round-precision=3]{5.88125e-06} $\pm$ \num[round-mode=figures,round-precision=3]{7.23165e-06} & \num[round-mode=figures,round-precision=3]{1.14673} $\pm$ \num[round-mode=figures,round-precision=3]{1.09747} & \num[round-mode=figures,round-precision=3]{0.00749165} $\pm$ \num[round-mode=figures,round-precision=3]{0.00868194} & \num[round-mode=figures,round-precision=3]{9.92478e-06} $\pm$ \num[round-mode=figures,round-precision=3]{1.24923e-05} \\ 
  W+jetscharm   & \num[round-mode=figures,round-precision=3]{115.072} $\pm$ \num[round-mode=figures,round-precision=3]{56.4961} & \num[round-mode=figures,round-precision=3]{1.21345} $\pm$ \num[round-mode=figures,round-precision=3]{0.668815} & \num[round-mode=figures,round-precision=3]{0.00239716} $\pm$ \num[round-mode=figures,round-precision=3]{0.00149026} & \num[round-mode=figures,round-precision=3]{46.939} $\pm$ \num[round-mode=figures,round-precision=3]{22.8654} & \num[round-mode=figures,round-precision=3]{0.714879} $\pm$ \num[round-mode=figures,round-precision=3]{0.393686} & \num[round-mode=figures,round-precision=3]{0.00222412} $\pm$ \num[round-mode=figures,round-precision=3]{0.00142098} & \num[round-mode=figures,round-precision=3]{21.3729} $\pm$ \num[round-mode=figures,round-precision=3]{11.0021} & \num[round-mode=figures,round-precision=3]{0.607396} $\pm$ \num[round-mode=figures,round-precision=3]{0.344118} & \num[round-mode=figures,round-precision=3]{0.00339688} $\pm$ \num[round-mode=figures,round-precision=3]{0.00226103} \\ 
  W+jetsbeauty   & \num[round-mode=figures,round-precision=3]{4699.39} $\pm$ \num[round-mode=figures,round-precision=3]{1831.01} & \num[round-mode=figures,round-precision=3]{259.182} $\pm$ \num[round-mode=figures,round-precision=3]{104.289} & \num[round-mode=figures,round-precision=3]{2.87623} $\pm$ \num[round-mode=figures,round-precision=3]{1.34429} & \num[round-mode=figures,round-precision=3]{2039.18} $\pm$ \num[round-mode=figures,round-precision=3]{817.243} & \num[round-mode=figures,round-precision=3]{168.126} $\pm$ \num[round-mode=figures,round-precision=3]{67.9351} & \num[round-mode=figures,round-precision=3]{6.00435} $\pm$ \num[round-mode=figures,round-precision=3]{2.82184} & \num[round-mode=figures,round-precision=3]{1179.09} $\pm$ \num[round-mode=figures,round-precision=3]{471.719} & \num[round-mode=figures,round-precision=3]{182.957} $\pm$ \num[round-mode=figures,round-precision=3]{75.3672} & \num[round-mode=figures,round-precision=3]{12.5032} $\pm$ \num[round-mode=figures,round-precision=3]{5.73171} \\ 
  Z+jetslight   & \num[round-mode=figures,round-precision=3]{1.61319} $\pm$ \num[round-mode=figures,round-precision=3]{1.56458} & \num[round-mode=figures,round-precision=3]{0.00372087} $\pm$ \num[round-mode=figures,round-precision=3]{0.00409099} & \num[round-mode=figures,round-precision=3]{1.37802e-06} $\pm$ \num[round-mode=figures,round-precision=3]{1.61883e-06} & \num[round-mode=figures,round-precision=3]{0.660407} $\pm$ \num[round-mode=figures,round-precision=3]{0.636966} & \num[round-mode=figures,round-precision=3]{0.00248097} $\pm$ \num[round-mode=figures,round-precision=3]{0.00276278} & \num[round-mode=figures,round-precision=3]{1.83077e-06} $\pm$ \num[round-mode=figures,round-precision=3]{2.221e-06} & \num[round-mode=figures,round-precision=3]{0.302377} $\pm$ \num[round-mode=figures,round-precision=3]{0.275755} & \num[round-mode=figures,round-precision=3]{0.00214711} $\pm$ \num[round-mode=figures,round-precision=3]{0.0024307} & \num[round-mode=figures,round-precision=3]{2.94255e-06} $\pm$ \num[round-mode=figures,round-precision=3]{3.59597e-06} \\ 
  Z+jetscharm   & \num[round-mode=figures,round-precision=3]{20.2296} $\pm$ \num[round-mode=figures,round-precision=3]{9.78978} & \num[round-mode=figures,round-precision=3]{0.192183} $\pm$ \num[round-mode=figures,round-precision=3]{0.10577} & \num[round-mode=figures,round-precision=3]{0.000329513} $\pm$ \num[round-mode=figures,round-precision=3]{0.000209217} & \num[round-mode=figures,round-precision=3]{8.34363} $\pm$ \num[round-mode=figures,round-precision=3]{4.04684} & \num[round-mode=figures,round-precision=3]{0.12686} $\pm$ \num[round-mode=figures,round-precision=3]{0.0702107} & \num[round-mode=figures,round-precision=3]{0.000454394} $\pm$ \num[round-mode=figures,round-precision=3]{0.000283009} & \num[round-mode=figures,round-precision=3]{4.44878} $\pm$ \num[round-mode=figures,round-precision=3]{2.20319} & \num[round-mode=figures,round-precision=3]{0.124529} $\pm$ \num[round-mode=figures,round-precision=3]{0.0689165} & \num[round-mode=figures,round-precision=3]{0.000757345} $\pm$ \num[round-mode=figures,round-precision=3]{0.000476136} \\ 
  Z+jetsbeauty   & \num[round-mode=figures,round-precision=3]{1847.09} $\pm$ \num[round-mode=figures,round-precision=3]{725.378} & \num[round-mode=figures,round-precision=3]{102.151} $\pm$ \num[round-mode=figures,round-precision=3]{41.2591} & \num[round-mode=figures,round-precision=3]{1.92588} $\pm$ \num[round-mode=figures,round-precision=3]{1.03349} & \num[round-mode=figures,round-precision=3]{694.193} $\pm$ \num[round-mode=figures,round-precision=3]{274.143} & \num[round-mode=figures,round-precision=3]{73.9958} $\pm$ \num[round-mode=figures,round-precision=3]{30.2384} & \num[round-mode=figures,round-precision=3]{5.54591} $\pm$ \num[round-mode=figures,round-precision=3]{3.2085} & \num[round-mode=figures,round-precision=3]{351.493} $\pm$ \num[round-mode=figures,round-precision=3]{146.045} & \num[round-mode=figures,round-precision=3]{56.299} $\pm$ \num[round-mode=figures,round-precision=3]{23.7949} & \num[round-mode=figures,round-precision=3]{3.53004} $\pm$ \num[round-mode=figures,round-precision=3]{2.14947} \\ 
  Single-top   & \num[round-mode=figures,round-precision=3]{6405.21} $\pm$ \num[round-mode=figures,round-precision=3]{881.129} & \num[round-mode=figures,round-precision=3]{399.573} $\pm$ \num[round-mode=figures,round-precision=3]{70.1827} & \num[round-mode=figures,round-precision=3]{8.14191} $\pm$ \num[round-mode=figures,round-precision=3]{3.29931} & \num[round-mode=figures,round-precision=3]{2591.95} $\pm$ \num[round-mode=figures,round-precision=3]{545.578} & \num[round-mode=figures,round-precision=3]{326.041} $\pm$ \num[round-mode=figures,round-precision=3]{73.0191} & \num[round-mode=figures,round-precision=3]{13.575} $\pm$ \num[round-mode=figures,round-precision=3]{4.21531} & \num[round-mode=figures,round-precision=3]{1250.63} $\pm$ \num[round-mode=figures,round-precision=3]{360.943} & \num[round-mode=figures,round-precision=3]{322.922} $\pm$ \num[round-mode=figures,round-precision=3]{98.8107} & \num[round-mode=figures,round-precision=3]{28.0382} $\pm$ \num[round-mode=figures,round-precision=3]{10.1727} \\ 
  Dibosons   & \num[round-mode=figures,round-precision=3]{242.9} $\pm$ \num[round-mode=figures,round-precision=3]{84.1208} & \num[round-mode=figures,round-precision=3]{16.2734} $\pm$ \num[round-mode=figures,round-precision=3]{5.72528} & \num[round-mode=figures,round-precision=3]{0.495815} $\pm$ \num[round-mode=figures,round-precision=3]{0.222927} & \num[round-mode=figures,round-precision=3]{111.823} $\pm$ \num[round-mode=figures,round-precision=3]{47.877} & \num[round-mode=figures,round-precision=3]{12.4987} $\pm$ \num[round-mode=figures,round-precision=3]{5.45537} & \num[round-mode=figures,round-precision=3]{0.766919} $\pm$ \num[round-mode=figures,round-precision=3]{0.392579} & \num[round-mode=figures,round-precision=3]{82.3516} $\pm$ \num[round-mode=figures,round-precision=3]{40.0722} & \num[round-mode=figures,round-precision=3]{16.7367} $\pm$ \num[round-mode=figures,round-precision=3]{8.21993} & \num[round-mode=figures,round-precision=3]{1.70822} $\pm$ \num[round-mode=figures,round-precision=3]{0.904067} \\ 
  QCDE   & \num[round-mode=figures,round-precision=3]{7782.29} $\pm$ \num[round-mode=figures,round-precision=3]{3435.12} & \num[round-mode=figures,round-precision=3]{600.09} $\pm$ \num[round-mode=figures,round-precision=3]{229.152} & \num[round-mode=figures,round-precision=3]{20.0874} $\pm$ \num[round-mode=figures,round-precision=3]{14.1079} & \num[round-mode=figures,round-precision=3]{2656.51} $\pm$ \num[round-mode=figures,round-precision=3]{937.488} & \num[round-mode=figures,round-precision=3]{488.718} $\pm$ \num[round-mode=figures,round-precision=3]{223.903} & \num[round-mode=figures,round-precision=3]{3.60632} $\pm$ \num[round-mode=figures,round-precision=3]{4.81286} & \num[round-mode=figures,round-precision=3]{1225.53} $\pm$ \num[round-mode=figures,round-precision=3]{505.444} & \num[round-mode=figures,round-precision=3]{749.333} $\pm$ \num[round-mode=figures,round-precision=3]{338.803} & \num[round-mode=figures,round-precision=3]{28.4986} $\pm$ \num[round-mode=figures,round-precision=3]{24.7199} \\ 
  QCDMU   & \num[round-mode=figures,round-precision=3]{1250.34} $\pm$ \num[round-mode=figures,round-precision=3]{636.1} & \num[round-mode=figures,round-precision=3]{210.002} $\pm$ \num[round-mode=figures,round-precision=3]{98.9055} & \num[round-mode=figures,round-precision=3]{9.032} $\pm$ \num[round-mode=figures,round-precision=3]{8.47603} & \num[round-mode=figures,round-precision=3]{737.524} $\pm$ \num[round-mode=figures,round-precision=3]{369.77} & \num[round-mode=figures,round-precision=3]{71.0643} $\pm$ \num[round-mode=figures,round-precision=3]{44.7127} & \num[round-mode=figures,round-precision=3]{2e-05} $\pm$ \num[round-mode=figures,round-precision=3]{1.00366e-05} & \num[round-mode=figures,round-precision=3]{307.805} $\pm$ \num[round-mode=figures,round-precision=3]{164.154} & \num[round-mode=figures,round-precision=3]{107.192} $\pm$ \num[round-mode=figures,round-precision=3]{63.6139} & \num[round-mode=figures,round-precision=3]{8.52658} $\pm$ \num[round-mode=figures,round-precision=3]{8.06508} \\ 
  SM-4tops   & \num[round-mode=figures,round-precision=3]{0.101944} $\pm$ \num[round-mode=figures,round-precision=3]{0.0378504} & \num[round-mode=figures,round-precision=3]{0.0964923} $\pm$ \num[round-mode=figures,round-precision=3]{0.0364342} & \num[round-mode=figures,round-precision=3]{0.00741156} $\pm$ \num[round-mode=figures,round-precision=3]{0.00592196} & \num[round-mode=figures,round-precision=3]{0.367117} $\pm$ \num[round-mode=figures,round-precision=3]{0.126677} & \num[round-mode=figures,round-precision=3]{0.491372} $\pm$ \num[round-mode=figures,round-precision=3]{0.156655} & \num[round-mode=figures,round-precision=3]{0.0541694} $\pm$ \num[round-mode=figures,round-precision=3]{0.0203208} & \num[round-mode=figures,round-precision=3]{5.14482} $\pm$ \num[round-mode=figures,round-precision=3]{1.54471} & \num[round-mode=figures,round-precision=3]{19.1582} $\pm$ \num[round-mode=figures,round-precision=3]{5.78108} & \num[round-mode=figures,round-precision=3]{4.97106} $\pm$ \num[round-mode=figures,round-precision=3]{1.54508} \\ 
\hline 
  Total  & \num[round-mode=figures,round-precision=3]{121057} $\pm$ \num[round-mode=figures,round-precision=3]{2195.97} & \num[round-mode=figures,round-precision=3]{11294.3} $\pm$ \num[round-mode=figures,round-precision=3]{287.414} & \num[round-mode=figures,round-precision=3]{181.074} $\pm$ \num[round-mode=figures,round-precision=3]{23.3765} & \num[round-mode=figures,round-precision=3]{58828} $\pm$ \num[round-mode=figures,round-precision=3]{1406.91} & \num[round-mode=figures,round-precision=3]{11688.6} $\pm$ \num[round-mode=figures,round-precision=3]{368.518} & \num[round-mode=figures,round-precision=3]{465.064} $\pm$ \num[round-mode=figures,round-precision=3]{29.1391} & \num[round-mode=figures,round-precision=3]{35996.3} $\pm$ \num[round-mode=figures,round-precision=3]{1309.57} & \num[round-mode=figures,round-precision=3]{14884.4} $\pm$ \num[round-mode=figures,round-precision=3]{511.15} & \num[round-mode=figures,round-precision=3]{1360.85} $\pm$ \num[round-mode=figures,round-precision=3]{70.7275} \\ 
\hline 
  Data   & 120572 & 11275 & 176 & 58557 & 11707 & 466 & 35886 & 14877 & 1335 \\ 
\hline 
\end{tabular} 
\caption{Yields of the analysis} 
\end{center} 
\end{table} 
\end{document}

### 2018-06-30 figures/Hbb/fit/base_ebv2_signal_uH_default_unblinded_splusb/Tables/Yields_postFit.tex
Paper draft moved to official repository

\documentclass[10pt]{article}
\usepackage{siunitx}
\usepackage[margin=0.1in,landscape,papersize={210mm,350mm}]{geometry}
\begin{document}
\begin{table}[htbp]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
\hline 
 & 4jex-2bex & 4jex-3bex & 4jex-4bin & 5jex-2bex & 5jex-3bex & 5jex-4bin & 6jin-2bex & 6jin-3bex & 6jin-4bin\\
\hline 
  t#bar{t}+light   & \num[round-mode=figures,round-precision=3]{82621.5} $\pm$ \num[round-mode=figures,round-precision=3]{4264.13} & \num[round-mode=figures,round-precision=3]{4858.7} $\pm$ \num[round-mode=figures,round-precision=3]{518.823} & \num[round-mode=figures,round-precision=3]{15.3465} $\pm$ \num[round-mode=figures,round-precision=3]{12.2475} & \num[round-mode=figures,round-precision=3]{37818.5} $\pm$ \num[round-mode=figures,round-precision=3]{3238.56} & \num[round-mode=figures,round-precision=3]{3454.78} $\pm$ \num[round-mode=figures,round-precision=3]{490.283} & \num[round-mode=figures,round-precision=3]{15.7777} $\pm$ \num[round-mode=figures,round-precision=3]{9.67883} & \num[round-mode=figures,round-precision=3]{19936.5} $\pm$ \num[round-mode=figures,round-precision=3]{2589.67} & \num[round-mode=figures,round-precision=3]{2534.76} $\pm$ \num[round-mode=figures,round-precision=3]{503.364} & \num[round-mode=figures,round-precision=3]{20.2684} $\pm$ \num[round-mode=figures,round-precision=3]{22.5954} \\ 
  t#bar{t}+cc   & \num[round-mode=figures,round-precision=3]{11506.9} $\pm$ \num[round-mode=figures,round-precision=3]{4904.11} & \num[round-mode=figures,round-precision=3]{1357.86} $\pm$ \num[round-mode=figures,round-precision=3]{559.086} & \num[round-mode=figures,round-precision=3]{5.84705} $\pm$ \num[round-mode=figures,round-precision=3]{4.13245} & \num[round-mode=figures,round-precision=3]{8423.38} $\pm$ \num[round-mode=figures,round-precision=3]{3544.87} & \num[round-mode=figures,round-precision=3]{2004.02} $\pm$ \num[round-mode=figures,round-precision=3]{769.903} & \num[round-mode=figures,round-precision=3]{39.2415} $\pm$ \num[round-mode=figures,round-precision=3]{18.243} & \num[round-mode=figures,round-precision=3]{7882.2} $\pm$ \num[round-mode=figures,round-precision=3]{3382.01} & \num[round-mode=figures,round-precision=3]{2994.49} $\pm$ \num[round-mode=figures,round-precision=3]{1159.14} & \num[round-mode=figures,round-precision=3]{58.6695} $\pm$ \num[round-mode=figures,round-precision=3]{25.2641} \\ 
  t#bar{t}+bb   & \num[round-mode=figures,round-precision=3]{4251.6} $\pm$ \num[round-mode=figures,round-precision=3]{582.791} & \num[round-mode=figures,round-precision=3]{3394.36} $\pm$ \num[round-mode=figures,round-precision=3]{349.278} & \num[round-mode=figures,round-precision=3]{109.819} $\pm$ \num[round-mode=figures,round-precision=3]{16.9307} & \num[round-mode=figures,round-precision=3]{3395.16} $\pm$ \num[round-mode=figures,round-precision=3]{461.812} & \num[round-mode=figures,round-precision=3]{4910.7} $\pm$ \num[round-mode=figures,round-precision=3]{454.328} & \num[round-mode=figures,round-precision=3]{355.411} $\pm$ \num[round-mode=figures,round-precision=3]{28.7838} & \num[round-mode=figures,round-precision=3]{3382.28} $\pm$ \num[round-mode=figures,round-precision=3]{477.663} & \num[round-mode=figures,round-precision=3]{7503.07} $\pm$ \num[round-mode=figures,round-precision=3]{755.024} & \num[round-mode=figures,round-precision=3]{1104.51} $\pm$ \num[round-mode=figures,round-precision=3]{81.7063} \\ 
  topEW   & \num[round-mode=figures,round-precision=3]{173.079} $\pm$ \num[round-mode=figures,round-precision=3]{27.5058} & \num[round-mode=figures,round-precision=3]{34.8528} $\pm$ \num[round-mode=figures,round-precision=3]{5.83154} & \num[round-mode=figures,round-precision=3]{2.68137} $\pm$ \num[round-mode=figures,round-precision=3]{0.544856} & \num[round-mode=figures,round-precision=3]{167.575} $\pm$ \num[round-mode=figures,round-precision=3]{25.9057} & \num[round-mode=figures,round-precision=3]{65.3101} $\pm$ \num[round-mode=figures,round-precision=3]{10.4542} & \num[round-mode=figures,round-precision=3]{8.17101} $\pm$ \num[round-mode=figures,round-precision=3]{1.4353} & \num[round-mode=figures,round-precision=3]{213.259} $\pm$ \num[round-mode=figures,round-precision=3]{34.1966} & \num[round-mode=figures,round-precision=3]{147.122} $\pm$ \num[round-mode=figures,round-precision=3]{23.8674} & \num[round-mode=figures,round-precision=3]{27.0436} $\pm$ \num[round-mode=figures,round-precision=3]{4.81305} \\ 
  ttH   & \num[round-mode=figures,round-precision=3]{62.3644} $\pm$ \num[round-mode=figures,round-precision=3]{7.68687} & \num[round-mode=figures,round-precision=3]{47.0985} $\pm$ \num[round-mode=figures,round-precision=3]{6.12803} & \num[round-mode=figures,round-precision=3]{4.66345} $\pm$ \num[round-mode=figures,round-precision=3]{0.676345} & \num[round-mode=figures,round-precision=3]{81.0067} $\pm$ \num[round-mode=figures,round-precision=3]{8.88862} & \num[round-mode=figures,round-precision=3]{98.5882} $\pm$ \num[round-mode=figures,round-precision=3]{11.5599} & \num[round-mode=figures,round-precision=3]{16.5847} $\pm$ \num[round-mode=figures,round-precision=3]{2.30085} & \num[round-mode=figures,round-precision=3]{134.824} $\pm$ \num[round-mode=figures,round-precision=3]{15.4613} & \num[round-mode=figures,round-precision=3]{241.158} $\pm$ \num[round-mode=figures,round-precision=3]{29.5737} & \num[round-mode=figures,round-precision=3]{61.8439} $\pm$ \num[round-mode=figures,round-precision=3]{8.85361} \\ 
  W+jetslight   & \num[round-mode=figures,round-precision=3]{6.13507} $\pm$ \num[round-mode=figures,round-precision=3]{6.3893} & \num[round-mode=figures,round-precision=3]{0.0116201} $\pm$ \num[round-mode=figures,round-precision=3]{0.0132907} & \num[round-mode=figures,round-precision=3]{4.02845e-06} $\pm$ \num[round-mode=figures,round-precision=3]{4.99603e-06} & \num[round-mode=figures,round-precision=3]{2.44131} $\pm$ \num[round-mode=figures,round-precision=3]{2.40995} & \num[round-mode=figures,round-precision=3]{0.00826541} $\pm$ \num[round-mode=figures,round-precision=3]{0.00945306} & \num[round-mode=figures,round-precision=3]{5.87917e-06} $\pm$ \num[round-mode=figures,round-precision=3]{7.24772e-06} & \num[round-mode=figures,round-precision=3]{1.14915} $\pm$ \num[round-mode=figures,round-precision=3]{1.10065} & \num[round-mode=figures,round-precision=3]{0.00749934} $\pm$ \num[round-mode=figures,round-precision=3]{0.00870701} & \num[round-mode=figures,round-precision=3]{9.93406e-06} $\pm$ \num[round-mode=figures,round-precision=3]{1.25256e-05} \\ 
  W+jetscharm   & \num[round-mode=figures,round-precision=3]{114.335} $\pm$ \num[round-mode=figures,round-precision=3]{58.9381} & \num[round-mode=figures,round-precision=3]{1.2012} $\pm$ \num[round-mode=figures,round-precision=3]{0.739442} & \num[round-mode=figures,round-precision=3]{0.00236534} $\pm$ \num[round-mode=figures,round-precision=3]{0.00177045} & \num[round-mode=figures,round-precision=3]{46.6404} $\pm$ \num[round-mode=figures,round-precision=3]{23.8845} & \num[round-mode=figures,round-precision=3]{0.708481} $\pm$ \num[round-mode=figures,round-precision=3]{0.4294} & \num[round-mode=figures,round-precision=3]{0.00219848} $\pm$ \num[round-mode=figures,round-precision=3]{0.00161836} & \num[round-mode=figures,round-precision=3]{21.3067} $\pm$ \num[round-mode=figures,round-precision=3]{11.1806} & \num[round-mode=figures,round-precision=3]{0.602915} $\pm$ \num[round-mode=figures,round-precision=3]{0.367103} & \num[round-mode=figures,round-precision=3]{0.0033632} $\pm$ \num[round-mode=figures,round-precision=3]{0.00250144} \\ 
  W+jetsbeauty   & \num[round-mode=figures,round-precision=3]{4703.24} $\pm$ \num[round-mode=figures,round-precision=3]{1820.68} & \num[round-mode=figures,round-precision=3]{259.059} $\pm$ \num[round-mode=figures,round-precision=3]{103.615} & \num[round-mode=figures,round-precision=3]{2.87629} $\pm$ \num[round-mode=figures,round-precision=3]{1.33878} & \num[round-mode=figures,round-precision=3]{2041.93} $\pm$ \num[round-mode=figures,round-precision=3]{813.152} & \num[round-mode=figures,round-precision=3]{168.089} $\pm$ \num[round-mode=figures,round-precision=3]{67.4743} & \num[round-mode=figures,round-precision=3]{6.00793} $\pm$ \num[round-mode=figures,round-precision=3]{2.81029} & \num[round-mode=figures,round-precision=3]{1181.48} $\pm$ \num[round-mode=figures,round-precision=3]{470.367} & \num[round-mode=figures,round-precision=3]{183.135} $\pm$ \num[round-mode=figures,round-precision=3]{74.9288} & \num[round-mode=figures,round-precision=3]{12.5225} $\pm$ \num[round-mode=figures,round-precision=3]{5.71541} \\ 
  Z+jetslight   & \num[round-mode=figures,round-precision=3]{1.61224} $\pm$ \num[round-mode=figures,round-precision=3]{1.56826} & \num[round-mode=figures,round-precision=3]{0.00371508} $\pm$ \num[round-mode=figures,round-precision=3]{0.00410231} & \num[round-mode=figures,round-precision=3]{1.37542e-06} $\pm$ \num[round-mode=figures,round-precision=3]{1.62263e-06} & \num[round-mode=figures,round-precision=3]{0.660309} $\pm$ \num[round-mode=figures,round-precision=3]{0.638369} & \num[round-mode=figures,round-precision=3]{0.00247802} $\pm$ \num[round-mode=figures,round-precision=3]{0.00277031} & \num[round-mode=figures,round-precision=3]{1.82807e-06} $\pm$ \num[round-mode=figures,round-precision=3]{2.22597e-06} & \num[round-mode=figures,round-precision=3]{0.302496} $\pm$ \num[round-mode=figures,round-precision=3]{0.276306} & \num[round-mode=figures,round-precision=3]{0.00214612} $\pm$ \num[round-mode=figures,round-precision=3]{0.002437} & \num[round-mode=figures,round-precision=3]{2.94066e-06} $\pm$ \num[round-mode=figures,round-precision=3]{3.60504e-06} \\ 
  Z+jetscharm   & \num[round-mode=figures,round-precision=3]{20.0931} $\pm$ \num[round-mode=figures,round-precision=3]{10.2875} & \num[round-mode=figures,round-precision=3]{0.190314} $\pm$ \num[round-mode=figures,round-precision=3]{0.116286} & \num[round-mode=figures,round-precision=3]{0.000325423} $\pm$ \num[round-mode=figures,round-precision=3]{0.000242886} & \num[round-mode=figures,round-precision=3]{8.2915} $\pm$ \num[round-mode=figures,round-precision=3]{4.22279} & \num[round-mode=figures,round-precision=3]{0.125729} $\pm$ \num[round-mode=figures,round-precision=3]{0.0764736} & \num[round-mode=figures,round-precision=3]{0.000448786} $\pm$ \num[round-mode=figures,round-precision=3]{0.000331408} & \num[round-mode=figures,round-precision=3]{4.4267} $\pm$ \num[round-mode=figures,round-precision=3]{2.2708} & \num[round-mode=figures,round-precision=3]{0.123439} $\pm$ \num[round-mode=figures,round-precision=3]{0.0747982} & \num[round-mode=figures,round-precision=3]{0.000748721} $\pm$ \num[round-mode=figures,round-precision=3]{0.000541698} \\ 
  Z+jetsbeauty   & \num[round-mode=figures,round-precision=3]{1849.44} $\pm$ \num[round-mode=figures,round-precision=3]{721.993} & \num[round-mode=figures,round-precision=3]{102.175} $\pm$ \num[round-mode=figures,round-precision=3]{40.9932} & \num[round-mode=figures,round-precision=3]{1.92736} $\pm$ \num[round-mode=figures,round-precision=3]{1.03118} & \num[round-mode=figures,round-precision=3]{694.989} $\pm$ \num[round-mode=figures,round-precision=3]{272.727} & \num[round-mode=figures,round-precision=3]{74.0053} $\pm$ \num[round-mode=figures,round-precision=3]{30.064} & \num[round-mode=figures,round-precision=3]{5.52952} $\pm$ \num[round-mode=figures,round-precision=3]{3.21096} & \num[round-mode=figures,round-precision=3]{352.457} $\pm$ \num[round-mode=figures,round-precision=3]{145.98} & \num[round-mode=figures,round-precision=3]{56.3764} $\pm$ \num[round-mode=figures,round-precision=3]{23.6708} & \num[round-mode=figures,round-precision=3]{3.56573} $\pm$ \num[round-mode=figures,round-precision=3]{2.21084} \\ 
  Single-top   & \num[round-mode=figures,round-precision=3]{6413.64} $\pm$ \num[round-mode=figures,round-precision=3]{895.418} & \num[round-mode=figures,round-precision=3]{398.794} $\pm$ \num[round-mode=figures,round-precision=3]{71.5816} & \num[round-mode=figures,round-precision=3]{8.09999} $\pm$ \num[round-mode=figures,round-precision=3]{3.38477} & \num[round-mode=figures,round-precision=3]{2597.72} $\pm$ \num[round-mode=figures,round-precision=3]{555.813} & \num[round-mode=figures,round-precision=3]{325.886} $\pm$ \num[round-mode=figures,round-precision=3]{73.1366} & \num[round-mode=figures,round-precision=3]{13.5907} $\pm$ \num[round-mode=figures,round-precision=3]{4.22921} & \num[round-mode=figures,round-precision=3]{1255.17} $\pm$ \num[round-mode=figures,round-precision=3]{370.047} & \num[round-mode=figures,round-precision=3]{323.317} $\pm$ \num[round-mode=figures,round-precision=3]{99.1294} & \num[round-mode=figures,round-precision=3]{28.0955} $\pm$ \num[round-mode=figures,round-precision=3]{10.2489} \\ 
  Dibosons   & \num[round-mode=figures,round-precision=3]{243.339} $\pm$ \num[round-mode=figures,round-precision=3]{84.6212} & \num[round-mode=figures,round-precision=3]{16.2643} $\pm$ \num[round-mode=figures,round-precision=3]{5.72764} & \num[round-mode=figures,round-precision=3]{0.495776} $\pm$ \num[round-mode=figures,round-precision=3]{0.223015} & \num[round-mode=figures,round-precision=3]{112.109} $\pm$ \num[round-mode=figures,round-precision=3]{48.238} & \num[round-mode=figures,round-precision=3]{12.5143} $\pm$ \num[round-mode=figures,round-precision=3]{5.46963} & \num[round-mode=figures,round-precision=3]{0.767999} $\pm$ \num[round-mode=figures,round-precision=3]{0.393524} & \num[round-mode=figures,round-precision=3]{82.5787} $\pm$ \num[round-mode=figures,round-precision=3]{40.3695} & \num[round-mode=figures,round-precision=3]{16.7647} $\pm$ \num[round-mode=figures,round-precision=3]{8.24942} & \num[round-mode=figures,round-precision=3]{1.71383} $\pm$ \num[round-mode=figures,round-precision=3]{0.911589} \\ 
  QCDE   & \num[round-mode=figures,round-precision=3]{7788.63} $\pm$ \num[round-mode=figures,round-precision=3]{3447.93} & \num[round-mode=figures,round-precision=3]{598.103} $\pm$ \num[round-mode=figures,round-precision=3]{229.471} & \num[round-mode=figures,round-precision=3]{20.0615} $\pm$ \num[round-mode=figures,round-precision=3]{14.1004} & \num[round-mode=figures,round-precision=3]{2670.37} $\pm$ \num[round-mode=figures,round-precision=3]{964.573} & \num[round-mode=figures,round-precision=3]{487.793} $\pm$ \num[round-mode=figures,round-precision=3]{224.323} & \num[round-mode=figures,round-precision=3]{3.60627} $\pm$ \num[round-mode=figures,round-precision=3]{4.81286} & \num[round-mode=figures,round-precision=3]{1223.88} $\pm$ \num[round-mode=figures,round-precision=3]{503.911} & \num[round-mode=figures,round-precision=3]{747.718} $\pm$ \num[round-mode=figures,round-precision=3]{339.266} & \num[round-mode=figures,round-precision=3]{28.5377} $\pm$ \num[round-mode=figures,round-precision=3]{24.7368} \\ 
  QCDMU   & \num[round-mode=figures,round-precision=3]{1250.71} $\pm$ \num[round-mode=figures,round-precision=3]{636.813} & \num[round-mode=figures,round-precision=3]{208.951} $\pm$ \num[round-mode=figures,round-precision=3]{98.668} & \num[round-mode=figures,round-precision=3]{9.02458} $\pm$ \num[round-mode=figures,round-precision=3]{8.47464} & \num[round-mode=figures,round-precision=3]{738.365} $\pm$ \num[round-mode=figures,round-precision=3]{370.942} & \num[round-mode=figures,round-precision=3]{71.1194} $\pm$ \num[round-mode=figures,round-precision=3]{44.7488} & \num[round-mode=figures,round-precision=3]{2e-05} $\pm$ \num[round-mode=figures,round-precision=3]{1.00366e-05} & \num[round-mode=figures,round-precision=3]{307.735} $\pm$ \num[round-mode=figures,round-precision=3]{164.175} & \num[round-mode=figures,round-precision=3]{107.198} $\pm$ \num[round-mode=figures,round-precision=3]{63.6214} & \num[round-mode=figures,round-precision=3]{8.52622} $\pm$ \num[round-mode=figures,round-precision=3]{8.06499} \\ 
  SM-4tops   & \num[round-mode=figures,round-precision=3]{0.101669} $\pm$ \num[round-mode=figures,round-precision=3]{0.0380598} & \num[round-mode=figures,round-precision=3]{0.0962671} $\pm$ \num[round-mode=figures,round-precision=3]{0.0365775} & \num[round-mode=figures,round-precision=3]{0.00732719} $\pm$ \num[round-mode=figures,round-precision=3]{0.00611273} & \num[round-mode=figures,round-precision=3]{0.365631} $\pm$ \num[round-mode=figures,round-precision=3]{0.128712} & \num[round-mode=figures,round-precision=3]{0.490356} $\pm$ \num[round-mode=figures,round-precision=3]{0.157228} & \num[round-mode=figures,round-precision=3]{0.054148} $\pm$ \num[round-mode=figures,round-precision=3]{0.0203205} & \num[round-mode=figures,round-precision=3]{5.14698} $\pm$ \num[round-mode=figures,round-precision=3]{1.54586} & \num[round-mode=figures,round-precision=3]{19.1663} $\pm$ \num[round-mode=figures,round-precision=3]{5.78682} & \num[round-mode=figures,round-precision=3]{4.97279} $\pm$ \num[round-mode=figures,round-precision=3]{1.54702} \\ 
  t#rightarrow Hu   & \num[round-mode=figures,round-precision=3]{31.8275} $\pm$ \num[round-mode=figures,round-precision=3]{1.79374} & \num[round-mode=figures,round-precision=3]{17.2168} $\pm$ \num[round-mode=figures,round-precision=3]{1.28268} & \num[round-mode=figures,round-precision=3]{0.338133} $\pm$ \num[round-mode=figures,round-precision=3]{0.235499} & \num[round-mode=figures,round-precision=3]{18.2536} $\pm$ \num[round-mode=figures,round-precision=3]{1.69042} & \num[round-mode=figures,round-precision=3]{13.8434} $\pm$ \num[round-mode=figures,round-precision=3]{1.26685} & \num[round-mode=figures,round-precision=3]{0.348373} $\pm$ \num[round-mode=figures,round-precision=3]{0.163693} & \num[round-mode=figures,round-precision=3]{10.2895} $\pm$ \num[round-mode=figures,round-precision=3]{1.50077} & \num[round-mode=figures,round-precision=3]{8.08807} $\pm$ \num[round-mode=figures,round-precision=3]{1.21445} & \num[round-mode=figures,round-precision=3]{0.513095} $\pm$ \num[round-mode=figures,round-precision=3]{0.150948} \\ 
\hline 
  Total  & \num[round-mode=figures,round-precision=3]{121007} $\pm$ \num[round-mode=figures,round-precision=3]{2261.29} & \num[round-mode=figures,round-precision=3]{11277.7} $\pm$ \num[round-mode=figures,round-precision=3]{431.065} & \num[round-mode=figures,round-precision=3]{180.853} $\pm$ \num[round-mode=figures,round-precision=3]{23.8174} & \num[round-mode=figures,round-precision=3]{58799.5} $\pm$ \num[round-mode=figures,round-precision=3]{1465.66} & \num[round-mode=figures,round-precision=3]{11674.1} $\pm$ \num[round-mode=figures,round-precision=3]{460.406} & \num[round-mode=figures,round-precision=3]{464.746} $\pm$ \num[round-mode=figures,round-precision=3]{30.2351} & \num[round-mode=figures,round-precision=3]{35984.7} $\pm$ \num[round-mode=figures,round-precision=3]{1312.26} & \num[round-mode=figures,round-precision=3]{14875} $\pm$ \num[round-mode=figures,round-precision=3]{551.112} & \num[round-mode=figures,round-precision=3]{1360.27} $\pm$ \num[round-mode=figures,round-precision=3]{74.7837} \\ 
\hline 
  Data   & 120572 & 11275 & 176 & 58557 & 11707 & 466 & 35886 & 14877 & 1335 \\ 
\hline 
\end{tabular} 
\caption{Yields of the analysis} 
\end{center} 
\end{table} 
\end{document}

### 2018-06-30 sections/conclusion.tex
Paper draft moved to official repository

--- 2018-06-06 ANA-TOPQ-2017-07-PAPER-metadata.tex
@@
 %-------------------------------------------------------------------------------
-% This file contains the title, author and abstract.
-% It also contains all relevant document numbers used by the different cover pages.
+\section{Conclusion}
+\label{sec:conclusion}
 %-------------------------------------------------------------------------------
 
-% Title
-\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
-
-% Draft version:
-% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
-% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
-% and line numbers.
-% Comment or remove in final version.
-\AtlasVersion{1.0}
-% Abstract - % directly after { is important for correct indentation
-\AtlasAbstract{%
-  This is a bare bones ATLAS document. Put the abstract for the document here.
-}
-
-% Author - this does not work with revtex (add it after \begin{document})
-\author{The ATLAS Collaboration}
-
-% ATLAS reference code, to help ATLAS members to locate the paper
-\AtlasRefCode{TOPQ-2017-07}
-
-% ATLAS date - arXiv submission; usually filled in by the Physics Office
-% \AtlasDate{\today}
-
-% ATLAS heading - heading at top of title page. Set for TDR etc.
-% \AtlasHeading{ATLAS ABC TDR}
-
- %-------------------------------------------------------------------------------
-% The following information is needed for the cover page. The commands are only defined
-% if you use the coverpage option in atlasdoc or use the atlascover package
-%-------------------------------------------------------------------------------
-
- % List of supporting notes  (leave as null \AtlasCoverSupportingNote{} if you want to skip this option)
-% \AtlasCoverSupportingNote{Short title note 1}{https://cds.cern.ch/record/XXXXXXX}
-% \AtlasCoverSupportingNote{Short title note 2}{https://cds.cern.ch/record/YYYYYYY}
-%
-% OR (the 2nd option is deprecated, especially for CONF and PUB notes)
-%
-% Supporting material TWiki page  (leave as null \AtlasCoverTwikiURL{} if you want to skip this option)
-% \AtlasCoverTwikiURL{https://twiki.cern.ch/twiki/bin/view/Atlas/WebHome}
-
-% Comment deadline
-% \AtlasCoverCommentsDeadline{DD Month 2016}
-
-  % Analysis team members - contact editors should no longer be specified
-% as there is a generic email list name for the editors
-% \AtlasCoverAnalysisTeam{Peter Analyser, Susan Editor1, Jenny Editor2, Alphonse Physicien}
-
-% Editorial Board Members - indicate the Chair by a (chair) after his/her name
-% Give either all members at once (then they appear on one line), or separately
-% \AtlasCoverEdBoardMember{EdBoard~Chair~(chair), EB~Member~1, EB~Member~2, EB~Member~3}
-
-% \AtlasCoverEdBoardMember{EdBoard~Chair~(chair)}
-% \AtlasCoverEdBoardMember{EB~Member~1}
-% \AtlasCoverEdBoardMember{EB~Member~2}
-% \AtlasCoverEdBoardMember{EB~Member~3}
-
-   % Editors egroup
-\AtlasCoverEgroupEditors{atlas-TOPQ-2017-07-editors@cern.ch}
-
-% EdBoard egroup
-\AtlasCoverEgroupEdBoard{atlas-TOPQ-2017-07-editorial-board@cern.ch}
+A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
+The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
+CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
+Two analyses are performed searching for $\ttbar \to WbHq$ production, and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, respectively.  
+The $\Hbb$ search selects events with one isolated light lepton from the $W \to \ell\nu$ decay, and multiple jets, with several 
+of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
+The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well multiple jets. 
+Both searches employ different multivariate techniques to discriminate between the signal and the background on the basis of their kinematic differences. 
+No significant excess of events above the background expectation is found, and observed (expected) 95\% CL upper limits are derived.
+The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
+yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of 0.XX\% (0.XX\%) and 0.XX\% (0.XX\%) respectively.
+The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.XX (0.XX) and 0.XX (0.XX) respectively. 
+%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
+These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions measured so far.

### 2018-06-30 sections/data_presel.tex
Paper draft moved to official repository

%-------------------------------------------------------------------------------
\section{Data sample and event preselection}
\label{sec:data_presel}
%-------------------------------------------------------------------------------

Both searches are based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ with 25 ns bunch spacing collected 
with the ATLAS detector in 2015 and 2016, corresponding to an integrated luminosity of $36.1~\ifb$.
Only events recorded with a single-electron trigger, a single-muon trigger, or a ditau trigger under stable beam conditions 
and for which all detector subsystems were operational are considered.
The number of $pp$ interactions per bunch crossing in this dataset ranges from about 8 to 45 interactions, with an average of 24.
%The mean number of $pp$ interactions per bunch crossing in the dataset is 24.

Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers without isolation requirements to give maximum efficiency. 
For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
along with triggers with a 60~\gev\ threshold and no isolation requirement, and with a 120 (140)~\gev\ threshold with looser identification criteria.
For ditau triggers, the threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.

Events selected by the $\Hbb$ search are recorded with a single-electron or single-muon trigger and 
are required to have exactly one electron or muon that matches the lepton reconstructed by the trigger.  
Furthermore, at least four jets are required, of which at least two must be $b$-tagged.

Events selected by the $\Htautau$ search are classified into $\lephad$ and $\hadhad$ channels depending on the 
multiplicity of selected leptons. Events in the $\lephad$ channel are recorded with a single-electron or single-muon trigger 
and are required to have exactly one selected electron or muon and at least one $\tauhad$ candidate. 
The selected light lepton (electron or muon) is required to match, with $\Delta R < 0.15$, the lepton reconstructed by 
the trigger and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1--2~\gev. In addition, its electric charge is required to be of
opposite sign to that of the leading $\tauhad$ candidate.
Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
no selected light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
In addition, in both channels at least three jets and exactly one $b$-tagged jet are required.

The above requirements apply to the physics objects as defined in Section~\ref{sec:objects}.
%, which are in general different between both searches. 
These requirements are referred to as the ``preselection'' and are summarised in Table~\ref{tab:preselection}.

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\begin{center}
\begin{tabular}{l|c|cc}
\toprule\toprule
\multicolumn{4}{c}{Preselection requirements} \\      
\midrule
Requirement &  $\Hbb$ search & \multicolumn{2}{c}{$\Htautau$ search} \\      
& & $\lephad$ channel & $\hadhad$ channel \\
\midrule
Trigger & single-lepton trigger & single-lepton trigger & ditau trigger  \\
Light leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
Tau leptons & -- & $\geq$1 $\tauhad$ & $\geq$2 $\tauhad$ \\
Electric charge & -- & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &  $\geq$4 jets & $\geq$3 jets & $\geq$3 jets \\
$b$-tagging & $\geq$2 $b$-tagged jets & =1 $b$-tagged jets & =1 $b$-tagged jets  \\
\bottomrule\bottomrule
\end{tabular}
\caption{\small{Summary of preselection requirements for the $\Hbb$ and $\Htautau$ searches. 
The leading and sub-leading $\tauhad$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

### 2018-06-30 sections/detector.tex
Paper draft moved to official repository

%-------------------------------------------------------------------------------
\section{ATLAS detector}
\label{sec:detector}
%-------------------------------------------------------------------------------

The ATLAS detector~\cite{PERF-2007-01} at the LHC covers almost the entire solid angle around the collision point,\footnote{ATLAS 
uses a right-handed coordinate system with its origin at the nominal interaction point (IP) in the 
centre of the detector.  
%and the $z$-axis coinciding with the axis of the beam pipe.
The $x$-axis points from
the IP to the centre of the LHC ring, %and
the $y$-axis points upward,
and the $z$-axis coincides with the axis of the beam pipe.
Cylindrical coordinates ($r$,$\phi$) are used 
in the transverse plane, $\phi$ being the azimuthal angle around the beam pipe. The pseudorapidity is defined in 
terms of the polar angle $\theta$ as $\eta = - \ln \tan(\theta/2)$.
Angular distance is measured in units of $\Delta R\equiv \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.} and
consists of an inner tracking detector surrounded by a thin superconducting solenoid producing a
2~T axial magnetic field, electromagnetic and hadronic calorimeters, and a muon spectrometer
incorporating three large toroid magnet assemblies. The inner detector consists of a high-granularity silicon pixel detector, 
including the %newly-installed
insertable B-layer~\cite{IBL}, installed in 2014,
and a silicon microstrip tracker,
together providing a precise reconstruction of tracks of charged particles in the pseudorapidity range $|\eta|<2.5$.
The inner detector also includes a transition radiation tracker that provides tracking and electron identification information for $|\eta|<2.0$.
%The electromagnetic (EM) sampling calorimeter uses lead as the absorber material 
%and liquid-argon (LAr) as the active medium, and is divided into barrel ($|\eta|<1.475$) and end-cap ($1.375<|\eta|<3.2$) regions.  
%Hadron calorimetry is also based on the sampling technique, with either scintillator tiles or LAr as the active medium, and with 
%steel, copper, or tungsten as the absorber material. The calorimeters cover $|\eta|<4.9$. 
%Hadronic calorimetry is provided by the steel/scintillating-tile calorimeter,
%segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
%The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
%optimised for electromagnetic and hadronic measurements respectively.
The calorimeter system covers the pseudorapidity range $|\eta| < 4.9$.
Within the region $|\eta|< 3.2$, electromagnetic (EM) calorimetry is provided by barrel and 
endcap high-granularity lead/liquid-argon (LAr) electromagnetic calorimeters,
with an additional thin LAr presampler covering $|\eta| < 1.8$,
to correct for energy loss in material upstream of the calorimeters.
Hadronic calorimetry is provided by %the
a
steel/scintillator-tile calorimeter,
segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
optimised for electromagnetic and hadronic measurements, respectively.
The muon spectrometer measures the %deflection
trajectories
of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking 
chambers located in a toroidal field of approximately 0.5~T and 1~T in the central and endcap regions of ATLAS, respectively. 
The muon spectrometer is also instrumented with separate trigger chambers covering $|\eta|<2.4$.
A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based Level-1 trigger followed by 
a software-based High-Level Trigger (HLT), is used to reduce the event rate to a maximum of around 1 kHz for offline storage.

### 2018-06-30 sections/introduction.tex
Paper draft moved to official repository

%-------------------------------------------------------------------------------
\section{Introduction}
\label{sec:intro}
%-------------------------------------------------------------------------------

Following the observation of a Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties is underway.
%looking for deviations from the Standard Model (SM) predictions.  
An interesting possibility is the presence of flavour-changing neutral current (FCNC) interactions 
between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$). Since the Higgs boson is lighter than the top quark, with a 
measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, such interactions would manifest themselves as FCNC top quark decays, $t\to H q$.  
In the Standard Model (SM), such decays are extremely suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
interactions are forbidden at the tree level and even suppressed at higher-orders in the perturbative expansion due to the 
Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.  As a result, the SM predictions for the $t \to Hq$ branching 
ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
On the other hand, large enhancements in these branching ratios are possible in some beyond-SM scenarios.
Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
and of type II, such as the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk}, or supersymmetric models
with R-parity violation~\cite{Eilam:2001dh}. In these scenarios, branching ratios can be as high as $\BR(t\to Hq) \sim 10^{-5}$. 
An even larger branching ratio of  $\BR(t\to Hc) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta}. 
While other FCNC top couplings, $tq\gamma$, $tqZ$, $tqg$, are also enhanced relative to the SM prediction in these scenarios beyond the SM, 
the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling. 
See Ref.~\cite{AguilarSaavedra:2004wm} for a review.
\textbf{Update a bit above paragraph mentioning more recent models.}

Searches for $t \to Hq$ decays have been performed by the ATLAS and CMS collaborations, taking advantage of the large samples
of $\ttbar$ events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{Aaboud:2017mfd,Aaboud:2018pob,Sirunyan:2017uae} using early Run~2 data.
In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{ 
In the following $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
the SM. Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
and excellent diphoton mass re\-so\-lu\-tion. In contrast, multilepton searches are able to exploit a significantly larger branching ratio for the Higgs 
boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, and are also characterised by relatively small backgrounds.
%However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
%($\ell, \ell^\prime = e, \mu$) decay mode, which has a very small branching ratio and thus is not promising for this search.} 
%so any excess would be hard to interpret as originating from $t \to Hq$ decays.
Finally, searches have also been performed considering the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
of $\BR(H\to b\bar{b})\simeq 58\%$. Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $13~\tev$, 
as well as the larger integrated luminosity.
Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% CL of  
$\BR(t\to Hc)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, and of $\BR(t\to Hc)<0.16\%$ based on
signatures with two same-charge light leptons (electrons or muons) or three light leptons resulting from 
$H \to WW^*$, $H\to \tau\tau$ in which both leptons decay leptonically, or $H \to ZZ^*$~\cite{Aaboud:2018pob}.
These upper limits are derived under the assumption of $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ under the
assumption of $\BR(t\to Hc)=0$. On the other hand, the CMS Collaboration has performed a search using  
$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} using 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
in upper limits of $\BR(t\to Hc)<0.47\%$ and $\BR(t\to Hu)<0.47\%$, in each case neglecting the other decay mode.

%Upper limits on the branching ratios $\BR(t\to Hq)$ ($q=u,c$) can be translated to upper limits on the non-flavour-diagonal Yukawa couplings $\lamHq$ 
%appearing in the following Lagrangian~\cite{Harnik:2012pb}:
%\begin{equation}
%{\cal L}_{\rm FCNC} = -\lambda_{t_L q_R} \bar{t}_L q_R H - \lambda_{q_L t_R} \bar{q}_L t_R H  + h.c.
%\end{equation}
%The branching ratio $\BR(t\to Hq)$ is estimated as the ratio of its partial width~\cite{Zhang:2013xya} to the SM $t \to Wb$ partial width~\cite{Denner:1990ns}, 
%which is assumed to be dominant. Both predicted partial widths include next-to-leading-order (NLO) QCD corrections.
%Using the expression derived in Sect. 1.2 of Ref.~\cite{ATL-COM-PHYS-2016-1664}, the coupling $|\lamHq|$ can be extracted as $| \lamHq | = (1.92 \pm 0.02) \sqrt{\BR(t\to Hq)}$.
%The $\lamHq$ coupling corresponds to the sum in quadrature of the couplings relative to the two possible chirality combinations of the quark fields, 
%$\lamHq \equiv \sqrt{ |\lambda_{t_Lq_R}|^2 +   |\lambda_{q_L t_R}|^2 }$~\cite{Harnik:2012pb}.

The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
Therefore, they help complete the programme of searches for $t \to Hq$ decays at the ATLAS experiment based on proton-proton collision 
data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
Two analyses are performed searching for $\ttbar \to WbHq$ production, and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, 
which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
The $\Hbb$ search selects events with one isolated light lepton from the $W \to \ell\nu$ decay, and multiple jets, with several 
of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well multiple jets. 
Both searches employ different multivariate techniques to discriminate between the signal and the background on the basis of their kinematic differences. 
These two searches are combined with previous ATLAS searches in the diphoton and multilepton final states using the same dataset~\cite{Aaboud:2017mfd,Aaboud:2018pob}, 
and bounds are set on $\BR(t\to Hc)$ and $\BR(t\to Hu)$, as well as on the corresponding non-flavour-diagonal Yukawa couplings.

### 2018-06-30 sections/objects.tex
Paper draft moved to official repository

%-------------------------------------------------------------------------------
\section{Object reconstruction}
\label{sec:objects}
%-------------------------------------------------------------------------------

The event reconstruction is affected by multiple $pp$ collisions in a single bunch crossing and by collisions
in neighboring bunch crossings, referred to as ``pileup''. 
Interaction vertices from the $pp$ collisions are reconstructed from at least two tracks 
with transverse momentum ($\pt$) larger than $400~\mev$ that are consistent with originating from the 
beam collision region in the $x$--$y$ plane. If more than one primary vertex candidate is found, the
candidate whose associated tracks form the largest sum of squared $\pt$~\cite{ATL-PHYS-PUB-2015-026}
is selected as the hard-scatter primary vertex.

Electron candidates~\cite{ATLAS-CONF-2016-024,ATL-PHYS-PUB-2016-015} are reconstructed from energy 
clusters in the EM calorimeter that are matched to reconstructed tracks in the inner detector;
electron candidates in the transition region between the EM barrel and endcap calorimeters 
($1.37 < |\eta_{\textrm{cluster}}| < 1.52$) are excluded.
In the $\Hbb$ ($\Htautau$) search, electron candidates are required to have $\pt>30~(15)~\gev$ and 
$|\eta_{\textrm{cluster}}| < 2.47$, and to satisfy tight (medium) likelihood-based identification 
criteria~\cite{ATLAS-CONF-2016-024} based on calorimeter, tracking and combined variables that provide 
separation between electrons and jets. 
Muon candidates~\cite{Aad:2016jkr} are reconstructed by matching track segments in %the various
different layers of the muon spectrometer to tracks found in the inner detector;
the resulting muon candidates are refitted using the complete track information from both detector systems.
In the $\Hbb$ ($\Htautau$) search, muon candidates are required to have $\pt>30~(10)~\gev$ and $|\eta|<2.5$ 
and to satisfy medium identification criteria~\cite{Aad:2016jkr}.

Electron (muon) candidates are matched to the primary vertex by requiring that the significance of their transverse impact parameter, $d_0$, 
satisfies $|d_0/\sigma(d_0)|<5(3)$, where $\sigma(d_0)$ is the measured uncertainty in $d_0$,
and by requiring that their longitudinal impact parameter, $z_0$, satisfies $|z_0 \sin\theta|<0.5$~mm.
To further reduce the background from non-prompt leptons, photon conversions and hadrons, lepton candidates are also required to be isolated 
in the tracker and in the calorimeter.
A track-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$, where
the sum includes all tracks (excluding the lepton candidate itself) within the cone defined by $\Delta R<R_{\textrm{cut}}$ about the %axis
direction of the lepton.  The value of $R_{\textrm{cut}}$ is the smaller of $r_{\textrm{min}}$ and $10~\gev/\pt^\ell$, where
$r_{\textrm{min}}$ is set to 0.2 (0.3) for electron (muon) candidates, and $\pt^\ell$ is the lepton $\pt$. 
The $\Hbb$ search requires lepton candidates to satisfy $I_R/\pt^\ell < 0.06$, while the $\Htautau$ search 
makes $\pt$-dependent requirements on $I_R/\pt^\ell$. Additionally, the $\Htautau$ search requires leptons to
satisfy a calorimeter-based isolation criterion; a requirement is made on the sum of the transverse energy of
topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contribution
from the energy deposit of the lepton itself and correcting for pile-up effects, to be less than a $\pt$-dependent 
percentage of the lepton energy. 
%The combined efficiency of track-based and calorimeter-based isolation requirements made by the $\Htautau$ 
%search is 90\% (99\%) at $\pt=25\;(60)~\gev$.

%a Gradient isolation working points are used for both electrons and muons. The working points are based on cut maps derived from the $Z\to l^+l^-$ Monte Carlo samples. The efficiency maps are simply derived from the sum of transverse energy of the clusters deposited in the calorimeter in the given cone. The efficiency for the leptons with a certain $\pt$ is $(0.1143*\pt[\GeV]+92.14)\%*(0.1143*\pt[\GeV]+92.14)\%$.

Candidate jets are reconstructed with the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq,Cacciari:2011ma} with a
radius parameter $R=0.4$, using topological clusters~\cite{Aad:2016upy} 
built from energy deposits in the calorimeters calibrated to the electromagnetic scale. 
The reconstructed jets are then calibrated to the particle level by the application of a jet energy scale 
derived from simulation and {\textit{in situ}} corrections based on $\sqrt{s}=13~\tev$ data~\cite{Aaboud:2017jcu}.
The calibrated jets used by the $\Hbb$ search are required to have $\pt > 25~\gev$ and $|\eta| < 2.5$,
while the $\Htautau$ search uses jets with $\pt > 30~\gev$ and $|\eta| < 4.5$.
Quality criteria are imposed to reject events that contain any jets arising from non-collision sources
or detector noise~\cite{ATLAS-CONF-2015-029}.  To reduce the contamination due to jets originating from pile-up interactions,
additional requirements are made on the Jet Vertex Tagger (JVT)~\cite{Aad:2015ina} output for jets with $\pt<60~\gev$ and $|\eta| < 2.4$,
or on the forward JVT~\cite{Aaboud:2017pou} output for jets with $\pt<50~\gev$ and $|\eta| > 2.5$.

Jets containing $b$-hadrons are identified ($b$-tagged) via an algorithm~\cite{Aad:2015ydr,ATL-PHYS-PUB-2016-012} 
that uses multivariate techniques to combine information about the impact parameters of displaced tracks and the  topological properties 
of secondary and tertiary decay vertices reconstructed within the jet. For each jet, a value for the multivariate $b$-tagging discriminant is 
calculated. In the $\Htautau$ search, a jet is considered $b$-tagged if this value is above the threshold corresponding to
an average 70\% efficiency to tag a $b$-quark jet, with a light-jet\footnote{Light-jet refers to a jet originating from the hadronisation of a light quark 
($u$, $d$, $s$) or a gluon.} rejection factor of $\sim$381 and a charm-jet rejection factor of $\sim$12, as determined for jets with
$\pt >20~\gev$ and $|\eta|<2.5$ in simulated $\ttbar$ events. In contrast, the $\Hbb$ search employs a tighter $b$-tagging requirement, 
corresponding to an average efficiency of 60\% to tag a $b$-quark jet, and light-jet and charm-jet rejection factors of 1539 and 34, respectively.

Hadronically decaying $\tau$-lepton candidates ($\tauhad$) are reconstructed from clusters in the calorimeters and
associated inner detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
with a total charge of 1. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
A boosted decision tree (BDT) discriminant using calorimeter- and tracking-based variables is used to identify $\tauhad$ candidates and reject
jet backgrounds. Three working points labelled loose, medium and tight are defined, and correspond to different $\tauhad$ identification efficiency 
values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
working point for the nominal selection, while the loose working point is used for the purpose of background estimation.
The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\tauhad$ 
decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-quark/gluon jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
Electrons that are reconstructed as one-prong $\tauhad$ candidates are removed via a BDT trained to reject electrons.
Any $\tauhad$ candidate that is also $b$-tagged is rejected.

Overlaps between candidate objects are removed sequentially, following this order: muons, electron, taus (only for the $\Htautau$ search) and jets. 
In the $\Hbb$ search, firstly, electron candidates that lie within $\Delta R = 0.01$ of a muon 
candidate are removed to suppress contributions from muon bremsstrahlung.  Overlaps between electron and jet candidates are resolved 
next, and finally, overlaps between remaining jet candidates and muon candidates are removed.
Clusters from identified electrons are not excluded during jet reconstruction.
In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron is discarded. If 
the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
In the $\Htautau$ search, a fixed cone size of $\Delta R = 0.2$ is used to determine the overlap between candidate objects, and only the
highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the analysis channel, see Section~\ref{sec:data_presel}) are considered 
to resolve their overlap with jets. 
%firstly, the electron within a ${\Delta}R = 0.2$ cone of muons are excluded, then the $\tau_{had}$'s or jets within a ${\Delta}R = 0.2$ cone of an electron or muon are excluded. Finally, the jets within a ${\Delta}R = 0.2$ cone of the leading $\had$ ($\lephad$), or with the two leading $\had$’s ($\hadhad$) are excluded.

The missing transverse momentum $\mpt$ (with magnitude $\met$) is defined as the negative vector sum of the 
$\pt$ of all selected and calibrated objects in the event, including a term to account for energy from soft particles 
in the event which are not associated with any of the selected objects. 
This soft term is calculated from inner-detector tracks matched to the selected primary vertex to make it more resilient to
contamination from pile-up interactions~\cite{Aad:2016nrq,ATL-PHYS-PUB-2015-027}.

### 2018-06-30 sections/signal_background_modeling.tex
Paper draft moved to official repository

%-------------------------------------------------------------------------------
\section{Signal and background modelling}
\label{sec:signal_background_model}
%-------------------------------------------------------------------------------

Signal and most background processes are modelled using Monte Carlo (MC) simulations.
After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
Small contributions arise from single-top-quark, $W/Z$+jets, multijet and diboson ($WW,WZ,ZZ$) production, as well as from the associated 
production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
with prompt leptons, i.e. those originating from the decay of a $W$ boson, a $Z$ boson, or a tau lepton,
are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
In the simulation, the top quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
and the Higgs boson is allowed to decay into all SM particles with branching ratios calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
Backgrounds with non-prompt electrons or muons, with photons or jets misidentified as electrons, or with jets misidentified as $\tauhad$ candidates, 
generically referred to as ``fake leptons", are estimated using data-driven methods. 
The background prediction is further improved during the statistical analysis by performing a likelihood 
fit to data using several signal-depleted search regions, as discussed in Sections~\ref{sec:strategy_Hbb} and~\ref{sec:strategy_Htautau}.

%-------------------------------------------------------------------------------
\subsection{Simulated signal and background processes}
\label{sec:simulations}
%-------------------------------------------------------------------------------

Samples of simulated $\ttbar \to WbHq$ events are generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix element calculation 
is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to \textsc{Pythia} 8.212~\cite{Sjostrand:2007gs} for parton showering and fragmentation. 
The A14~\cite{ATLASUETune4} set of tuned parameters in \textsc{Pythia} controlling the description of multiparton interactions and  
initial and final state radiation, referred to as the ``tune'', is used.
The signal sample is normalised to the same cross section as used for the $t\bar{t}\to WbWb$ sample (see discussion below) and
assuming a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
The case of both top quarks decaying into $Hq$ is neglected in the analysis given existing upper limits on $\BR(t \to Hq)$ (see Section~\ref{sec:intro}).

The nominal sample used to model the $\ttbar$ background is generated with the NLO generator {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd} using the NNPDF3.0 PDF set. The {\powheg} model parameter $h_{\textrm{damp}}$, which controls 
matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, is set to 1.5 times the top quark mass. 
Parton shower and hadronisation are modelled by {\textsc Pythia}~8.2 with the A14 tune.
Alternative $\ttbar$ simulation samples used to derive systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
The generated $\ttbar$ samples are normalised to a theoretical cross section of $832^{+46}_{-51}$~pb, 
computed using \textsc{Top++}~v2.0~\cite{Czakon:2011xx} at next-to-next-to-leading order (NNLO), 
including resummation of next-to-next-to-leading logarithmic (NNLL) soft gluon 
terms~\cite{Cacciari:2011hy,Baernreuther:2012ws,Czakon:2012zr,Czakon:2012pz,Czakon:2013goa}, 
and using the MSTW 2008 NNLO~\cite{Martin:2009iq,Martin:2009bu} set of PDFs. 
The theoretical uncertainties result from variations of the factorisation and renormalisation scales, as well as from uncertainties in the
top quark mass, and in the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution to the overall theoretical uncertainty 
in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
with the MSTW 2008 68\% CL NNLO, CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3 5f FFN~\cite{Ball:2012cx} PDF sets.

The $\Hbb$ search requires a more sophisticated treatment of the $\ttbar$ background. Therefore, the simulated $\ttbar$ events are categorised depending 
on the flavour content of additional particle jets not originating from the decay of the $\ttbar$ system (see Ref.~\cite{Aaboud:2017rss} for details).
Events labelled as either \ttbin\ or \ttcin\ are generically referred to in the following as $\ttbar$+HF events, where HF stands for ``heavy flavour''.
The remaining events are labelled as $\ttbar$+light-jets events, including those with no additional jets. 
A finer categorisation of \ttbin\ events is considered for the purpose of applying further corrections and
assigning systematic uncertainties associated with the modelling of heavy-flavour production in different topologies~\cite{Aaboud:2017rss}.
In particular, the \ttbin\ events are reweighted to an NLO prediction in the four-flavour (4F) scheme 
of \ttbin\ production including parton showering~\cite{Cascioli:2013era}, based on {\ShOLlong}~\cite{Gleisberg:2008ta, Cascioli:2011va} (referred to as {\ShOL} 
in the following) using the CT10 PDF set.  This reweighting is performed in such a way that the inter-normalisations of the \ttbin\ categories are at NLO accuracy, 
while preserving the nominal \ttbin\ cross section in {\powheg}+{\pythia}. This reweighting is applied as well to the alternative $\ttbar$ samples.

Samples of single-top-quark events corresponding to the $t$-channel production mechanism are generated with the 
{\powheg}~v1~\cite{Frederix:2012dh} generator that uses the 4F scheme  for the NLO matrix element calculations
and the fixed 4F \textsc{CT10}f\textsc{4}~\cite{Lai:2010vv} PDF set.
Samples corresponding to the $Wt$- and $s$-channel production mechanisms are generated 
with {\powheg}~v1 using the CT10 PDF set. Overlaps between the $\ttbar$ and $Wt$ final states are avoided by using 
the ``diagram removal'' scheme~\cite{Frixione:2005vw}.
The parton shower, hadronisation and the underlying event are modelled using {\pythia}~6.428 with the CTEQ6L1 PDF set 
in combination with the P2012 tune.
The single-top-quark samples are normalised to the approximate NNLO theoretical cross 
sections~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.

Samples of $W/Z$+jets events are generated with the {\sherpa}~2.2.0~\cite{Gleisberg:2008ta} generator. 
The matrix element is calculated for up to two partons at NLO and up to four partons at LO using 
\textsc{Comix}~\cite{Gleisberg:2008fv} and \textsc{OpenLoops}~\cite{Cascioli:2011va}. The matrix element calculation 
is merged with the {\sherpa} parton shower~\cite{Schumann:2007mg} using the ME+PS@NLO prescription~\cite{Hoeche:2012yf}. 
The PDF set used for the matrix-element calculation is NNPDF3.0 NNLO~\cite{Ball:2014uwa} with a dedicated parton shower tuning developed for {\sherpa}. 
Separate samples are generated for different $W/Z$+jets categories using filters for a $b$-jet 
($W/Z+\geq$1$b$+jets), a $c$-jet and no $b$-jet ($W/Z+\geq$1$c$+jets), and with a veto on $b$- and $c$-jets 
($W/Z$+light-jets), which are combined into the inclusive $W/Z$+jets samples.
Both the $W$+jets and $Z$+jets samples are normalised to their respective inclusive NNLO theoretical 
cross sections in QCD calculated with \textsc{FEWZ}~\cite{Anastasiou:2003ds}.

Samples of $WW/WZ/ZZ$+jets events are generated with {\sherpa}~2.1.1 using the CT10 PDF set
and include processes containing up to four electroweak vertices. The matrix element includes zero additional partons 
at NLO and up to three partons at LO using the same procedure as for the $W/Z$+jets samples. 
The final states simulated require one of the bosons to decay leptonically and the other hadronically.
All diboson samples are normalised to their NLO theoretical cross sections provided by {\sherpa}.

Samples of $\ttbar V$ and $\ttbar H$ events are generated with {\amcatnlo}~2.3.2, using 
NLO matrix elements and the NNPDF3.0 NLO~\cite{Ball:2014uwa} PDF set. 
Showering is performed using {\pythia}~8.210 and the A14 tune.
The $\ttbar V$ samples are normalised to the NLO cross section computed with {\amcatnlo}.
The $\ttbar H$ sample is normalised using the NLO cross section~\cite{Raitio:1978pt,Beenakker:2002nc,Dawson:2003zu,Yu:2014cka,Frixione:2015zaa}  
and the Higgs boson decay branching ratios calculated using \textsc{Hdecay}.

%The production of four-top-quark events in the SM was simulated by samples generated at LO using {\amcatnlo}~2.2.2
%and the NNPDF2.3 LO PDF set, interfaced to {\pythia} 8.186 in combination with the A14 tune. 
%The sample was normalised to a cross section of 9.2 fb, computed at NLO~\cite{Alwall:2014hca}.

All simulated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
utilise \textsc{EvtGen}~v1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
To model the effects of pileup, events from minimum-bias interactions are generated using the \textsc{Pythia}~8.186~\cite{Sjostrand:2007gs} 
event generator and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
The generated events are processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
using \textsc{Geant4}~\cite{Agostinelli:2002hh}. A faster simulation, where the full \textsc{Geant4} simulation of
the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
is adopted for some of the samples used to estimate systematic uncertainties.
Simulated events are processed through the same reconstruction software as the data, and corrections are applied so that the object identification 
efficiencies, energy scales and energy resolutions match those determined from data control samples.

%-------------------------------------------------------------------------------
\subsection{Backgrounds with fake leptons}
\label{sec:fakeleptons}
%-------------------------------------------------------------------------------

\subsubsection{Fake electrons and muons}
In the $\Hbb$ search, the background from multijet production (``multijet background'' in the following) contributes to the selected 
data sample via several production and misreconstruction mechanisms.  
In the electron channel, it consists of non-prompt electrons (from semileptonic $b$- or $c$-hadron decays) as well as 
misidentified photons (e.g.~from a conversion of a photon into an $e^+e^-$ pair) or jets with a high fraction of 
their energy deposited in the EM calorimeter.  In the muon channel, the multijet background originates predominantly from 
non-prompt muons.  The multijet background normalisation and shape are estimated directly from data by using the ``matrix method''
technique~\cite{Aad:2010ey,ATLAS-CONF-2014-058}, which exploits differences in lepton identification and isolation properties between 
prompt leptons and leptons that are either non-prompt or result from the misidentification of photons or jets. 
Further details can be found in Ref.~\cite{ttbareson13TeV}.

\subsubsection{Fake taus}
\label{sec:faketaus}
In the $\Htautau$ search, the background with one or more fake $\tauhad$ candidates is mainly arising from $\ttbar$ or
multijet production, depending on the analysis channel, with $W$+jets production contributing to a lesser extent. The simulation study shows that b-jet faking rate is quite low and the fake $\tauhad$ candidates primarily result from the misidentification of light-quark jets. This background is estimated directly from data by defining control regions (CR) enriched in fake $\tauhad$ candidates via loosened $\tauhad$ requirements. These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}. The CR selection requirements are analogous to those used to define the different SRs, except that the leading (trailing) $\tauhad$ candidate 
in the $\lephad$ ($\hadhad$) channel is required to be of loose-not-medium quality, and the requirement on its charge is dropped.

The fake $\tauhad$ background events in a given SR are modeled by the fake template derived from its corresponding CR, which is a data-driven method. The fake template is defined as the data subtracted by the contributions from the simulated backgrounds with real $\tauhad$ candidates. In the $\lephad$ channel, simulation studies indicate that the fake $\tauhad$ background composition is consistent between the SR and the CR, and dominated by $\ttbar$. In this case, the fake template is simply normalised to the fake $\tauhad$ background yield in the SR and taken as the fake $\tauhad$ background. In the $\hadhad$ channel, the fake $\tauhad$ background is expected to be dominated by multijet production. However, simulation studies indicate that the fraction of $\ttbar$ yield is higher in the SR than in the CR. Therefore, an appropriate amount of simulated $\ttbar$ events with fake $\tauhad$ candidates in the CR are added to the fake template to match the fake $\tauhad$ background composition in the SR. This modified fake template is then normalised to the expected fake $\tauhad$ background yield in the SR, same as in the case of the $\lephad$ channel.

%In the $\Htautau$ search, the background events with real tau leptons are modelled by MC samples, including $t\bar{t}$, $t\bar{t}+H/V$, single top events with real taus, and $Z\to\tau\tau$+jets. The $Z\to ee,\mu\mu$ processes are included for lepton faking tau background. They are small compared to the other background components. The fake-tau background with one or more taus faked by jets consists of the top fake (with at least one fake tau from jets in the top events), QCD multijet and $W$+jets events. This background is estimated in a dedicated control region (fake-tau CR), which is shown in Fig. \ref{fig:region-definition}. The events in the fake-tau CR are required to pass mostly the same selection as fit region (FR, the region after the preselection and the cut in Eq. \ref{eq:chi2-3jet}; the tau candidates in FR are also required to have the same charge) except for the tau charge and identification requirement. The fake-tau CR consists of two kinds of events: 1. The $\tauhad$'s have medium ID and the tau candidates have the same charge; 2. The leading (sub-leading) $\tauhad$ in $\lephad$ ($\hadhad$) channel has loose ID but fails medium ID requirement and there is no charge requirement. So the fake-tau CR is orthogonal to the FR and dominated by fake $\tauhad$'s.
%
%\begin{figure}[htb]
%\centering
%\includegraphics[width=0.45\textwidth]{figures/Htautau/fakes/fake-tau-control-region.eps}
%\includegraphics[width=0.45\textwidth]{figures/Htautau/fakes/VR.eps}
%
%\caption{ The composition of the FR, fake-tau CR, and corresponding VRs defined for the analysis. The ``Loose'', ``Medium'', ``very loose'' are leading (sub-leading) tau ID in $\lephad$ ($\hadhad$) channel. OS and SS represent the charge requirements of the tau candidates, OS for opposite sign, SS for same sign.}
%\label{fig:region-definition}
%\end{figure}
%
%In the fake-tau CR, the MC contaminations from $Z$+jets, diboson, top events ($\ttbar$, single top, $\ttbar+H/V$) with two real taus are subtracted, with only the QCD, $W$+jets and top fake events left. %The fake taus are those $\tauhad$ candidates which cannot be matched to any real taus in the MC truth.
%
%In the $\lephad$ channel, the top fake is the dominant fake background, and the fractions of top fake in FR and fake-tau CR are consistent with those in FR VR and fake-tau VR. The same is true for the fractions of $W$+jets in FR and fake-tau CR. Therefore, after the subtraction, the events in fake-tau CR are transferred to FR with a transfer factor, which is defined as
%
%\begin{equation}
%f_{\text{trans}} = \frac{N_{\text{data}}^{\text{FR}} - N_{\text{non-fake}}^{\text{FR}}}{N_{\text{fake}}^{\text{fake-tau-CR}}},
%\label{eq:transfer-factor}
%\end{equation}
%
%where $N_{\text{data}}^{\text{FR}}$ and $N_{\text{non-fake}}^{\text{FR}}$ are total event yields of data and non-fake MC background in FR, $N_{\text{fake}}^{\text{fake-tau-CR}}$ is the fake events from fake-tau CR, which is data-driven. Eq. \ref{eq:transfer-factor} gives a pre-fit normalization of the fake events to demonstrate the agreement of the data and total background prediction. After the fit, $f_{\text{trans}}$ will be modified by a new multiplicative factor (freely floating in the fit) replacting the final normalization of the fake. The fit untilizes the different distribution shapes of signal and background, as well as the background-enriched region in FR to determine the fake normalization.
%
%In the $\hadhad$ channel, regarding that the QCD events have a considerable contribution to the fake-tau background and there is no guarentee that the fractions of top-fake-tau event in FR and fake-tau CR are the same. So a small amount of MC top-fake-tau events in fake-tau CR are added to the data-driven estimate to make them equal. The fractions of top-fake-tau events in both regions are simply computed by MC prediction. As a result, the fraction is also considered to have a systematic uncertainty (1-$\sigma$ deviation is around 30\%, which is measured in another top-enriched control region). So the transfer factor in the $\hadhad$ channel becomes:
%
%\begin{equation}
%f_{\text{trans}} = \frac{N_{\text{data}}^{\text{FR}} - N_{\text{non-fake}}^{\text{FR}}}{N_{\text{fake}}^{\text{fake-tau-CR}} + \epsilon N_{\text{topFake}}^{\text{fake-tau-CR}}},
%\label{eq:transfer-factor-hadhad}
%\end{equation}
%
%where $N_{\text{topFake}}^{\text{fake-tau CR}}$ is the top-fake-tau MC yield in fake-tau CR, and $\epsilon$ is a scaling factor that makes the top fake fractions equal in fake-tau CR and FR.
%
%To check if the shape of the BDT discriminant of the fake-tau events in fake-tau CR and in the FR agree with each other, independent FR and fake-tau CR validation regions (VR, as shown in Fig. \ref{fig:region-definition}) are defined. The VRs are basically the same as the nominal regions, except that
%
%\begin{itemize}
%\item The ``medium'' is downgraded to ``loose'', and ``loose'' downgraded to ``veryLoose'' for the subleading tau ID.
%\item In $\hadhad$, the ID of the leading $\tauhad$ is downgraded from ``medium'' to ``loose'' as well, in order to suppress the signal contamination.
%\end{itemize}
%
%The VRs are depleted of signals\footnote{The signal contamination is about $0.02\%$ and $0.15\%$ in the $\lephad$ 4-jet and $\hadhad$ 4-jet VRs, respectively, if assuming BR($t\to Hq$)=$1\%$.}, and the shape difference of the BDT discriminant of the fake-tau events between the FR VR and fake-tau VR (after subtracting on-fake MC backgrounds) are treated as one of the systematic uncertainty for the data-driven fake estimate.
%
%The different fractions of top fake, QCD and $W$+jets in fake-tau CR and FR can induce systematics in the fake estimation. In the $\lephad$ channel, relatively higher top fake fraction is seen in the FR than in the fake-tau CR. However, the top fake fractions in the FR and the FR VR are consistent with each other, and the same is true for the fractions in the fake-tau CR and the fake-tau VR. So the top fake fraction systematics is also covered by the VR samples comparisons.

### 2018-06-30 sections/statistical_analysis.tex
Paper draft moved to official repository

\section{Statistical analysis}
\label{sec:stat_analysis}

For each search, the final discriminant distributions across all analysis regions considered are jointly analysed to test for the 
presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a multiplicative factor to the yield for $\Hq$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$,
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties in the signal and background expectations. 
Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. With the exception of a few parameters 
that control the normalisation of the some of the background components (e.g. the \ttbin\ background in the case of the $\Hbb$ search) 
and are treated as free parameters in the fit,  all other nuisance parameters are implemented in the likelihood function 
as Gaussian or log-normal constraints.

For a given value of $\mu$, the nuisance parameters $\theta$ allow variations of the expectations for signal and background
according to the corresponding systematic uncertainties, and their fitted values result in the deviations from
the nominal expectations that globally provide the best fit to the data.
This procedure allows a reduction of the impact of systematic uncertainties on 
the search sensitivity by taking advantage of the highly populated background-dominated bins included in the likelihood fit.
To verify the improved background prediction, fits under the background-only hypothesis are performed, 
and differences between the data and the post-fit background prediction are checked 
using kinematic variables other than the ones used in the fit. 
Statistical uncertainties in each bin of the predicted final discriminant distributions due to the limited size of the simulated samples 
are taken into account by dedicated parameters in the fit.     
The best-fit $\BR(t\to Hq)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
hypothesis, i.e. maximising the likelihood function $L(\mu,\theta)$ over $\mu$ and $\theta$.

The test statistic $q_\mu$ is defined as the profile likelihood ratio: 
$q_\mu = -2\ln({\cal L}(\mu,\hat{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and $\hat{\hat{\theta}}_\mu$ are the values of the
nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
A related statistic is used to determine the probability that the observed data are compatible with the background-only hypothesis (i.e.~the discovery test)  
by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,\hat{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
The $p$-value (referred to as $p_0$) representing the probability of the data being compatible with the 
background-only hypothesis is estimated by integrating
the distribution of $q_0$ from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js,ErratumCowan:2010js}, above the observed value of $q_0$. The observed $p_0$-value is checked for each explored signal scenario.
In the absence of any significant excess above the background expectation, upper limits on $\mu$, and thus on 
$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js,ErratumCowan:2010js}, are excluded at $\geq 95\%$ CL.

### 2018-06-30 sections/strategy_Hbb.tex
Paper draft moved to official repository

\section{Strategy for the $\Hbb$ search}
\label{sec:strategy_Hbb}

This section presents an overview of the analysis strategy adopted by the $\Hbb$ search, which
follows closely that of the previous search performed on the Run 1 dataset~\cite{Aad:2015pja}.

\subsection{Event categorisation}
\label{sec:event_categorisation}

Given the choice of the $W\to\ell\nu$ and $H\to b\bar{b}$ decay modes, the $\ttbar \to WbHq$ signal 
is expected to have four jets and three $b$-quarks in the final state, which can be effectively exploited 
to suppress the background. 
Additional jets can also be present because of initial- or final-state radiation.
However, the use of the 60\% $b$-tagging operating point, characterised by a low mistag rate for
charm and light jets, make both $\Hc$ and $\Hu$ signals have a similar $b$-tag multiplicity spectrum,
with a very small fraction of events having four or more $b$-tagged jets.

In order to optimise the sensitivity of the search, the selected events are categorised into different analysis 
regions depending on the number of jets (4, 5 and $\geq$6) and on the number of $b$-tagged jets (2, 3 and $\geq$4).
Therefore, a total of nine analysis regions are considered:
(4j, 2b), (4j, 3b), (4j, 4b), (5j, 2b), (5j, 3b), (5j, $\geq$4b), ($\geq$6j, 2b), ($\geq$6j, 3b), and ($\geq$6j, $\geq$4b), 
where ($n$j, $m$b) indicates $n$ selected jets and $m$ $b$-tagged jets.

The overall rate and composition of the $\ttbar$+jets background strongly depends on the jet and $b$-tag 
multiplicities, as illustrated in Figure~\ref{fig:Hbb_Summary}.
Regions with exactly two $b$-tagged jets are dominated by $\ttbar$+light jets, while regions with 
$\geq$4 $b$-tagged jets are dominated by $\ttbb$. Intermediate compositions are found in regions with exactly three 
$b$-tagged jets.  Most of the $\ttbar$+light-jets background in the these regions have a charm jet from the hadronic $W$ boson 
decay  being $b$-tagged, in addition to the two $b$-jets from the top quark decays.

In the regions with four or five jets and exactly three $b$-tags, which dominate the sensitivity of this search, 
the selected signal events have a $H \to b\bar{b}$ decay in more than 97\% of the events.
Because of somewhat larger fraction of $\Hc$ signal in the regions with exactly three $b$-tags,
this analysis is expected to have slightly better sensitivity for $\Hc$ than for $\Hu$ signal.
The rest of the regions have significantly lower signal-to-background ratios, but they are used for the purpose of improving 
the $\ttbar$+jets background prediction and constraining the related systematic uncertainties (see Section~\ref{sec:systematics})
through a likelihood fit to data (see Section~\ref{sec:stat_analysis}).  
A table summarising the observed and expected yields before the fit to data in each of the analysis regions 
can be found in Appendix~\ref{sec:prepostfit_yields_Hbb_appendix}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
%\includegraphics[width=0.55\textwidth]{figures/Hbb/fit/base_ebv2_signal_cH_default_unblinded_splusb/Plots/Summary.png}
\includegraphics[width=0.55\textwidth]{figures/Hbb/fit/cH_plots/Summary.eps}
\caption{$\Hbb$ search: Comparison between the data and background prediction for the yields in each of the analysis regions considered 
before the fit to data (``Pre-Fit"). Backgrounds are normalised to their nominal cross sections discussed in Section~\ref{sec:simulations}.
The small contributions from $W/Z$+jets,  single top, diboson and multijet backgrounds are combined into a single background source 
referred to as ``Non-$\ttbar$''. 
The expected $\Hc$ and $\Hu$ signals (dashed histograms) are shown separately normalised to $\BR(t\to Hq)=1\%$.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
which is determined via a likelihood fit to data. \textbf{TO DO: Improve style.}} 
\label{fig:Hbb_Summary}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Likelihood discriminant}
\label{sec:likelihood_discriminant}

After event categorisation, the signal-to-background ratio is very low even in the most sensitive analysis regions, and a suitable
discriminating variable between signal and background needs to be constructed in order to improve the sensitivity of the search.
Since both signal and background result from the $\ttbar$ decay, there are few experimental handles available to discriminate
between them. The most prominent features are the different resonances present in the decay (i.e. the Higgs boson in the case 
of $\Hq$ signal and a hadronically decaying $W$ boson in the case of the $\ttbar \to WbWb$ background), and the different flavour content of the 
jets forming those resonances. However, the large number of jets in the final state causes ambiguities in the calculation 
of these kinematic variable to discriminate signal events from background events.

This search uses a similar likelihood (LH) discriminant as that developed in Ref.~\cite{Aad:2015pja}.
The LH variable for a given event is defined as:
\begin{equation}
L(\mathbf{x}) = \frac{P^\textrm{sig}(\mathbf{x}) }{P^\textrm{sig}(\mathbf{x}) +P^\textrm{bkg}(\mathbf{x}) },
\label{eq:D}
\end{equation}
where $P^\textrm{sig}(\mathbf{x}) $ and $P^\textrm{bkg}(\mathbf{x}) $ represent the probability density functions (pdf) of a given event under
the signal hypothesis ($\ttbar \to WbHq$) and under the background hypothesis ($\ttbar \to WbWb$), respectively.
Both $P^\textrm{sig}$ and $P^\textrm{bkg}$ are functions of $\mathbf{x}$, which denotes the set of two-body and three-body invariant masses 
that correspond to the expected resonances in the event (the leptonically decaying $W$ boson, the Higgs boson or the hadronically 
decaying $W$ boson, and the corresponding top quark parent particles). These invariant masses are computed from the reconstructed 
lepton, jets, and missing transverse momentum.
As in Ref.~\cite{Aad:2015pja}, $P^\textrm{sig}$ and $P^\textrm{bkg}$ are approximated as a product of one-dimensional pdfs for
each of the invariant masses considered, and averaged among all possible jet-parton matching combinations. 
Combinations are weighted using information on the per-jet multivariate $b$-tagging discriminant value to suppress the impact from 
parton-jet assignments that are inconsistent with the correct parton candidates flavour.

Two background hypotheses are considered, corresponding to the dominant backgrounds in
the analysis: $\ttbar$+light-jets and $\ttbin$. Thus, $P^\textrm{bkg}$ is computed as the average of
the pdfs for both hypotheses, weighted by their relative fractions in simulated $\ttbar$+jets events, which depend
on the analysis region considered. Furthermore, in a significant fraction of $\Hq$ simulated events (e.g. about 40--50\% in 3b regions), 
the light-quark jet from the hadronic top-quark decay is not among the selected jets.
Similarly, in about 30--40\% (50--90\%) of simulated $\ttbar$+light-jets ($\ttbin$) background events in 3b regions, 
the light-quark jet originating from the $W$ boson decay is also not selected. Thus, the calculation of $P^\textrm{sig}$ and
$P^\textrm{bkg}$ also includes an additional hypothesis to account for this topology, again weighted by the corresponding fractions. 
In this case, the invariant masses involving the missing jet are computed using the highest-$\pt$ jet not matched 
to a decay product from the $\ttbar$ system.

An example of the discrimination between signal and background that is obtained is shown in Figure~\ref{fig:LHD},
where the shape of the LH discriminant distribution is compared between the $\Hc$ and $\Hu$ signals and the 
$t\bar{t}\to WbWb$ background in each of the analysis regions considered.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[htbp]
\begin{center}
\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep4jex2bex_FcncDiscriminant.eps}} 
\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep4jex3bex_FcncDiscriminant.eps}}
\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep4jex4bin_FcncDiscriminant.eps}} \\
\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep5jex2bex_FcncDiscriminant.eps}}
\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep5jex3bex_FcncDiscriminant.eps}}
\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep5jex4bin_FcncDiscriminant.eps}} \\
\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep6jin2bex_FcncDiscriminant.eps}}
\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep6jin3bex_FcncDiscriminant.eps}}
\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep6jin4bin_FcncDiscriminant.eps}} \\
\caption{$\Hbb$ search: Comparison of the shape of the LH discriminant distribution between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
and the $t\bar{t}\to WbWb$ background (black solid) in several regions considered in the analysis:
(a) (4j, 2b), (b) (4j, 3b), (c) (4j, 4b), (d) (5j, 2b), (e) (5j, 3b), (f) (5j, $\geq$4b), (g) ($\geq$6j, 2b), 
(h) ($\geq$6j, 3b), and (i) ($\geq$6j, $\geq$4b). Due to the small signal acceptance in 4b regions,
which translates into low statistics for the simulated samples, only two bins are used for this distribution.} 
\label{fig:LHD}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-06-30 sections/strategy_Htautau.tex
Paper draft moved to official repository

%-------------------------------------------------------------------------------
\section{Strategy for the $\Htautau$ search}
\label{sec:strategy_Htautau}
%-------------------------------------------------------------------------------

The analysis strategy adopted by the $\Htautau$ search follows closely that developed in Ref.~\cite{Chen:2015nta} and is summarised in this section.

\subsection{Event categorisation and kinematic reconstruction}
\label{sec:htautau_reco_cat}

In the $\Htautau$ search, the final state signature of interest is characterised by the presence of two $\tau$-leptons from the
decay of the Higgs boson and a light-quark jet, both originating from the decay of one of the top quarks. If one of the $\tau$-leptons
decays leptonically, an isolated electron or muon and significant $\met$ would also be expected.
The other top quark decays into a $W$ boson and a $b$-quark, with the $W$ boson in turn decaying hadronically, giving 
three additional jets, one of which should be tagged as a $b$-jet. Therefore, at least four jets are typically expected in signal events.
However, in a significant fraction of the events the trailing jet from the $W$-boson decay fails the minimum $\pt$ requirement of $30~\gev$,
resulting in signal events with only three jets reconstructed.
In order to optimise the sensitivity of the search, the selected events are categorised into four search 
regions depending on the number of $\taulep$ and $\tauhad$ candidates, and on the number of jets:
($\lephad$, 3j), ($\lephad$, $\geq$4j), ($\hadhad$, 3j), and ($\hadhad$, $\geq$4j).

This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
of $\met$ in the event (larger in $\lephad$ events compared to $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
is missing or not (3j vs $\geq$4j events). This analysis adopts the event reconstruction strategy developed in Ref.~\cite{Chen:2015nta},
which is briefly summarised in the following. Events with exactly three jets that are compatible with having a fully reconstructed hadronically decaying 
top quark ($t \to Wb \to qqb$) necessarily miss the light-quark jet from the $t \to Hq$ decay and are thus rejected. 
For both 3j and $\geq$4j events, the selected jets are assigned to the different top quark decay products via a criterion based on 
minimising a sum of angular distances between objects. Finally, the four-momenta of the invisible decay products for each $\tau$-lepton decay 
are estimated by minimising a $\chi^2$ function based on the probability density functions for the angular distance of the visible and invisible
decay products in the $\tau$-lepton decay, and including Gaussian constraints on the $\tau$-lepton mass, the Higgs boson mass and the
measured $\met$. After the minimisation, an improved resolution is obtained on the determination of the Higgs boson four-momentum, and hence
its invariant mass, as well as on the four-momentum of the parent top quark. Following the event kinematic reconstruction, several kinematic variables
that discriminate between signal and background are defined. These variables are used in the multivariate analysis discussed in the next section.

%To comply with the signal topology, in each event, exactly one jet should be tagged as a $b$-jet. If all jets from the top hadronic decay and the jet from $t\to Hq$, denoted as the FCNC jet, pass the jet selection, there should be at least four jets. However, some jets have a $\pt$ less than 30 GeV and may fail to pass the jet selection. The most likely missing jet is the subleading jet from the $W$ decay. These 3-jet events are still kept if the FCNC jet can be found and matched with the Higgs to reconstruct the top. It is done as follows. In the 3-jet events, if the three jets, denoted by $j_1$, $j_2$, $b$, satisfy
%\begin{equation}
%\chi_{Wb}^2 \equiv \left(\frac{m_{j_1 j_2}-80.4}{20}\right)^2 + \left(\frac{m_{j_1 j_2 b}-172.5}{25}\right)^2 <5,
%\label{eq:chi2-3jet}
%\end{equation}
%where the mass is in GeV, the event is discarded. In these events, a good hadronic top is reconstructed, but the FCNC jet from the other top is missing.
%
%If Eq.~(\ref{eq:chi2-3jet}) is not satisfied, the FCNC jet is identified by the least sum of angular distances, $\Delta R_{3j}$, expressed as 
%\begin{equation}
%\Delta R_{3j} \equiv \Delta R(j_c ,H) + \Delta R(j_W ,b) \: ,
%\label{eq:deltaR-3jet}
%\end{equation}
%where the $j_W$ denotes the jet from the $W$ decay, and the event is kept.
%
%For the events with at least four jets (denoted as 4-jet events), the three leading ones other than the $b$-jet are considered. Out of the three possible combinations that form the two sets of top decay products, the one with the least sum of angular distances, $\Delta R_{4j}$, is chosen, which is defined as
%\begin{equation}
%\Delta R_{4j} \equiv \Delta R(j_c ,H) + \Delta R(j_{1} ,b) + \Delta R(j_{2} ,b) + \Delta R(j_{1} ,j_{2}),
%\label{eq:deltaR-4jet}
%\end{equation}
%where $j_{1,2}$ are the jets from the $W$ decay. No explicit $c$-tagging is used, and as can be seen above, the FCNC jet is found through pure kinematic criteria such as $\Delta R$.
%
%The method introduced in \cite{Chen:2015nta} is used to recontruct the ditau mass and momentum by taking the tau decay kinematics into account. To determine the 4-momenta of the invisible decay products of the tau decays, the following $\chi^2$ in Eq.~\ref{eq:tautau-chi2}, based on the probability functions above and the constraints from the tau mass, the Higgs mass and the measured $\met$, is defined,
%\begin{eqnarray}
%\begin{array}{ll}
%\chi^2 = & -2\ln \mathcal{P}_1 -2\ln \mathcal{P}_2 + \left( \frac{m_{\tau_1}^{\text{fit}} - 1.78}{\sigma_{\tau}} \right)^2 +  \left( \frac{m_{\tau_2}^{\text{fit}} - 1.78}{\sigma_{\tau}} \right)^2 +  \left( \frac{m_{H}^{\text{fit}} - 125}{\sigma_{\text{Higgs}}} \right)^2 + \\
% & \left( \frac{E_{x,\text{miss}}^{\text{fit}} - E_{x,\text{miss}}}{\sigma_{\text{miss}}} \right)^2 + \left( \frac{E_{y,\text{miss}}^{\text{fit}} - E_{y,\text{miss}}}{\sigma_{\text{miss}}} \right)^2 ,
%\end{array}
%\label{eq:tautau-chi2}
%\end{eqnarray}
%where $\mathcal{P}_i(\Delta R)$ are the probability distributions of the angular distance of the visible and invisible decay products in the tau decay, parametrized as a function of the momentum of the tau lepton. In the $\taulep$ mode where two neutrinos are present, it is extended to be the joint probability distribution of $\Delta R$ and $m_{\text{mis}}$ with $m_{\text{mis}}$ being the invariant mass of the neutrinos, denoted by $\mathcal{P}(\Delta R, m_{\text{mis}})$. These probability density functions are obtained from the MC simulation.
%
%In the Eq. \ref{eq:tautau-chi2}, the free parameters scanned are the 4-momentum components of the invisible decay products for each tau decay. In the $\tauhad$ mode, only three momentum components are scanned since a single neutrino is massless. $m_{\tau_{1,2}}^{\text{fit}}$,  $m_{H}^{\text{fit}}$ and $E_{xy,\text{miss}}^{\text{fit}}$ are the calculated tau mass, Higgs mass, and missing transverse energy with the scanned parameters. The corresponding mass resolutions, $\sigma_{\tau}$ and $\sigma_{\text{Higgs}}$, are set to 1.8~GeV and 20~GeV respectively. The $\met$ resolution is parametrized as
%\begin{equation}
%\sigma_{\text{miss}}=13.1 + 0.50\sqrt{\Sigma E_\text{T}},
%\label{eq:sigma-missing-E}
%\end{equation}
%where $\Sigma E_\text{T}$ (in GeV) is the scalar sum of transverse energy depositions of all objects and clusters. The invisible 4-momenta are obtained by minimizing the combined $\chi^2$ for each event. By adding the Higgs mass constraint term in the kinematic fit, not only is the Higgs mass resolution improved, but also the resolutions of the Higgs boson's four-momentum, and the mass of the top from which the Higgs comes.

\subsection{Multivariate discriminant}

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\begin{center}
\begin{tabular}{ccccc}
\toprule\toprule 
& \multicolumn{2}{c}{$\lephad$} & \multicolumn{2}{c}{$\hadhad$} \\
Variable & 3j & $\geq$4j & 3j & $\geq$4j  \\
\midrule
$m_{\tau\tau}^{\text{fit}}$                      	& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{Hq}$                                	& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{\text{T,lep}}$                              	& $\times$  & $\times$  &             & \\
$p_{\text{T,1}}$                             	&             &             & $\times$  & $\times$ \\
$p_{\text{T,2}}$                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
$\met$ $\phi$ centrality                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
$E_{\text{T},\parallel}^{\text{miss}}$          	& $\times$  & $\times$  & $\times$  & $\times$ \\
$E_{\text{T},\perp}^{\text{miss}}$          	& $\times$  & $\times$  &             & \\
$m_{b j_1}$                   		        & $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{\text{lep}j}$      			        & $\times$  & $\times$  &   	  & \\
$m_{\tau j}$      			        & $\times$  & $\times$  &   	  & \\
$x_1^{\text{fit}}$				& $\times$  &	$\times$  & $\times$  & $\times$ \\
$x_2^{\text{fit}}$				& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{b j_1 j_2 }$             	   		&             & $\times$  &             & $\times$ \\ \hline
\bottomrule\bottomrule
\end{tabular}
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for each search region (denoted by $\times$). 
The description of each variable is provided in the text.}}
\label{tab:mva_var}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

Boosted decision trees (BDT)~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} are used in each SR to improve the separation between signal and background. The separate training naturally exploits differences in event kinematics across SRs.  
A large set of potential variables was investigated in each SR separately, and only those variables that led to an improved discrimination
performance of the BDT were kept. In the training, only the $\Hq$ signal is used against the total SM background, including both real
and fake $\tauhad$ contributions. The BDT input variables used per SR are listed in Table~\ref{tab:mva_var} and defined in the following:

\begin{itemize}
\item $m_{\tau\tau}^{\text{fit}}$: the invariant mass of the two $\tau$-lepton candidates after the reconstruction of the neutrinos, indicating the reconstructed Higgs boson mass.
\item $m_{Hq}$: the invariant mass of the reconstructed Higgs boson and the associated light-quark jet in the $t \to Hq$ decay, corresponding to the reconstructed mass of the parent top quark.
\item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\met$ in the $\lephad$ channel.
\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\tauhad$ candidate (denoted as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\tauhad$ candidates (denoted as particles 1 and 2 respectively) in the $\hadhad$ channel.
\item $\met$ $\phi$ centrality: a variable that quantifies the relative angular position of the $\mpt$ with respect to the 
visible tau decay products in the transverse plane. The transverse plane is transformed such that the direction of the tau decay products are 
orthogonal, and that the smaller angle between the tau decay products defines the positive quadrant of the transformed plane. 
The $\met$ $\phi$ centrality is defined as the sum of the parallel ($\parallel$) and perpendicular ($\perp$) components of the $\mpt$ unit vector in this transformed plane.
\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the transverse direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
\item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically-decaying $W$ boson.
\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance with the $\tauhad$ candidate.
\item $m_{\tau j}$: the invariant mass of the  $\tauhad$ candidate and the jet that has the smallest angular distance with the $\tauhad$ candidate.
\item $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$: the momentum fractions carried by the visible decay products from the two $\tau$-lepton candidates 
(whether $\taulep$ or $\tauhad$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
\item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$-boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark. This variable is only defined for $\geq$4j events.
\end{itemize}

Among these variables, the most discriminating ones include $m_{\tau\tau}^{\text{fit}}$, $p_{\text{T},2}$, $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$. A comparison between data and background prediction 
for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:BDT_inputs_lephad} and~\ref{fig:BDT_inputs_hadhad}.
A good description of the data by the background model is observed in all cases.
The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:BDT}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most
important BDT input variables in the $\lephad$ channel. The distributions are shown for
(a) $m_{\tau\tau}^{\text{fit}}$ in the 3j region, (b) $m_{\tau\tau}^{\text{fit}}$ in the $\geq$4j region, (c) $p_{\text{T},2}$ in the 3j region,
and (d) $p_{\text{T},2}$ in the $\geq$4j region.
The expected $\Hc$ signal (dashed histogram) is shown normalised to $\BR(t\to Hc)=1\%$.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
The hashed area represents the total uncertainty of the background. \textbf{Improve style.}}
\label{fig:BDT_inputs_lephad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_hadhad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
important BDT input variables in the $\hadhad$ channel. The distributions are shown for
(a) $m_{\tau\tau}^{\text{fit}}$ in the 3j region, (b) $m_{\tau\tau}^{\text{fit}}$ in the $\geq$4j region, (c) $x_{1}^{\text{fit}}$ in the 3j region,
and (d) $x_{2}^{\text{fit}}$ in the $\geq$4j region.
The expected $\Hc$ signal (dashed histogram) is shown normalised to $\BR(t\to Hc)=1\%$.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
The hashed area represents the total uncertainty of the background. \textbf{Improve style.}} 
\label{fig:BDT_inputs_hadhad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl3j/canv_.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl4j/canv_.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh3j/canv_.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh4j/canv_.eps}} \\
\caption{$\Htautau$ search: Comparison of the shape of the BDT discriminant distribution between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
and the total background (black solid) in the different search regions considered:
(a) ($\lephad$, 3j), (b) ($\lephad$, $\geq$4j), (c) ($\hadhad$, 3j), and (d) ($\hadhad$, $\geq$4j). }
\label{fig:BDT}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-06-30 sections/systematic_uncertainties.tex
Paper draft moved to official repository

%-------------------------------------------------------------------------------
\section{Systematic uncertainties}
\label{sec:systematics}
%-------------------------------------------------------------------------------

Several sources of systematic uncertainty are considered that can affect the normalisation of signal 
and background and/or the shape of their corresponding final discriminant distributions.  
Each source of systematic uncertainty is considered to be uncorrelated with the other sources.  
Correlations of a given systematic uncertainty are maintained across processes and channels.

%Table~\ref{tab:SystSummary} presents a list of all systematic uncertainties considered in the analysis 
%and indicates whether they are taken to be normalisation-only, or to affect both shape and normalisation.
%
%%%%%%%%%%%%%%%
%\begin{table*}[htbp]
%\centering
%\begin{tabular}{lcc}
%\toprule\toprule
%Systematic uncertainty & Type  & Components \\
%\midrule
%\textbf{Luminosity}                  &  N & 1\\\midrule
%\textbf{Reconstructed Objects}                 &   & \\
%Electron                  & SN & 5 \\
%Muon                      &  SN & 6 \\
%Jet reconstruction      & SN & 1\\ 
%Jet vertex fraction         & SN    & 1\\
%Jet energy scale            & SN & 22\\
%Jet energy resolution       & SN & 1\\
%Missing transverse momentum  & SN & 2\\ 
%$b$-tagging efficiency      & SN & 6\\
%$c$-tagging efficiency      & SN & 4\\
%Light-jet tagging efficiency    & SN & 12\\ 
%High-\pt\ tagging   & SN & 1 \\ \midrule
%\textbf{Background Model}                 &   & \\
%$t\bar{t}$ cross section    &  N & 1\\
%$t\bar{t}$ modelling: $\pt$ reweighting   & SN & 9\\
%$t\bar{t}$ modelling: parton shower & SN & 3\\
%$t\bar{t}$+HF: normalisation & N & 2 \\
%$t\bar{t}$+$c\bar{c}$: $\pt$ reweighting  & SN & 2 \\
%$t\bar{t}$+$c\bar{c}$: generator & SN & 4 \\
%$t\bar{t}$+$b\bar{b}$: NLO shape & SN & 8 \\
%$W$+jets normalisation      &  N & 3\\
%$W$ $\pt$ reweighting     &  SN & 1\\
%$Z$+jets normalisation      &  N & 3\\
%$Z$ $\pt$ reweighting     &  SN & 1\\
%Single top normalisation    &  N & 3\\
%Single top model            &  SN & 1\\
%Diboson normalisation  &  N & 3\\
%$t\bar{t}V$ cross section   &  N & 1\\
%$t\bar{t}V$ model           &  SN & 1\\ 
%$t\bar{t}H$ cross section & N & 1 \\
%$t\bar{t}H$ model       & SN & 2 \\ 
%Multijet normalisation  &  N & 4\\ \midrule
%\textbf{Signal Model}                 &   & \\
%$t\bar{t}$ cross section    &  N & 1\\
%Higgs boson branching ratios & N & 3 \\
%$t\bar{t}$ modelling: $\pt$ reweighting   & SN & 9\\
%$t\bar{t}$ modelling: $\pt$ reweighting non-closure  & N & 1\\
%$t\bar{t}$ modelling: parton shower & N & 1\\
%\bottomrule\bottomrule
%\end{tabular}
%\caption{\label{tab:SystSummary} List of systematic uncertainties considered. 
%An ``N'' means that the uncertainty is taken as affecting only the normalisation for all relevant 
%processes and channels, whereas ``SN'' means that the uncertainty is 
%taken on both shape and normalisation.
%Some of the systematic uncertainties are split into several components for a more
%accurate treatment.}
%\end{table*}
%%%%%%%%%%%%%%%
%
%The leading sources of systematic uncertainty vary depending on the analysis channel considered, but they 
%typically originate from $\ttbar$+jets modelling (including $\ttbar$+HF) and $b$-tagging. 
%For example, the total systematic uncertainty  in the background normalisation in the (4 j, 4 b) channel, 
%which dominates the sensitivity in the case of the $\Hc$ search, is approximately 20\%, 
%with the largest contributions originating from $\ttbar$+HF normalisation, $b$-tagging efficiency, 
%$c$-tagging efficiency, light-jet tagging efficiency and $\ttbar$ cross section.
%However, as shown in section~\ref{sec:result}, the fit to data in the nine analysis channels allows the overall background 
%uncertainty to be reduced significantly, to approximately 4.4\%. 
%The reduced uncertainty results from the significant constraints provided by the data on some
%systematic uncertainties, as well as the anti-correlations among sources of systematic uncertainty resulting
%from the fit to the data.
%The total systematic uncertainty on the $\Hc$ signal normalisation in the (4 j, 4 b) channel is approximately 17\%, 
%with similar contributions from uncertainties related to $b$-tagging and overall signal modelling. After the fit,
%this uncertainty is reduced to 7.8\%.
%Table~\ref{tab:SystSummary_WbHc} presents a summary of the sys\-te\-ma\-tic uncertainties for the $\Hc$ 
%search and their impact on the normalisation of the signal and the main backgrounds in the (4 j, 4 b) channel.
%
%The following sections describe each of the systematic uncertainties considered in the analyses. 
%
%\begin{table*}[htbp]
%\centering
%\begin{tabular}{l | c c c c  | c c c c}
%\toprule\toprule
% & \multicolumn{4}{c|}{Pre-fit} & \multicolumn{4}{c}{Post-fit} \\ 
% &  $WbHc$ & $t\bar{t}$+LJ & $t\bar{t}+c\bar{c}$ & $t\bar{t}+b\bar{b}$ &  $WbHc$ & $t\bar{t}$+LJ & $t\bar{t}+c\bar{c}$ & $t\bar{t}+b\bar{b}$ \\
%\midrule
%Luminosity  & $\pm 2.8 $  & $\pm 2.8 $  & $\pm 2.8 $  & $\pm 2.8 $  & $\pm 2.6$ & $\pm 2.6 $  & $\pm 2.6 $  & $\pm 2.6 $ \\ 
%Lepton efficiencies  & $\pm 1.5 $  & $\pm 1.5 $  & $\pm 1.5 $  & $\pm 1.5 $  & $\pm 1.5$ &  $\pm 1.5 $  & $\pm 1.5 $  & $\pm 1.5 $ \\ 
%Jet energy scale  & $\pm 3.3 $  & $\pm 2.9 $  & $\pm 2.3 $  & $\pm 5.8 $  & $\pm 1.4$ &  $\pm 1.2 $  & $\pm 1.8 $  & $\pm 4.1 $ \\ 
%Jet efficiencies  & $\pm 1.2 $  & --  & $\pm 1.9 $  & $\pm 1.7 $  & $\pm 0.9$ &  --  & $\pm 1.4 $  & $\pm 1.2 $ \\
%Jet energy resolution  & --  & $\pm 1.2 $  & $\pm 2.8 $  & $\pm 2.9 $  & -- &  -- & $\pm 1.0 $  & $\pm 1.1 $ \\ 
%$b$-tagging eff.  & $\pm 7.9 $  & $\pm 5.5 $  & $\pm 5.2 $  & $\pm 10 $  & $\pm 5.7$ & $\pm 3.9 $  & $\pm 3.7 $  & $\pm 6.6 $ \\ 
%$c$-tagging eff.  & $\pm 7.0 $  & $\pm 6.6 $  & $\pm 13 $  & $\pm 3.5 $  & $\pm 6.3$ &  $\pm 6.0 $  & $\pm 11 $  & $\pm 3.2 $ \\ 
%Light-jet tagging eff.  & $\pm 0.8 $  & $\pm 18 $  & $\pm 3.2 $  & $\pm 1.5 $  & $\pm 0.6$ &  $\pm 13 $  & $\pm 2.3 $  & $\pm 1.1 $ \\
%$t\bar{t}$: reweighting  & $\pm 5.9 $  & $\pm 2.7 $  & $\pm 4.2 $  & --  & $\pm 3.8$ &  $\pm 1.9 $  & $\pm 2.3 $  & -- \\ 
%$t\bar{t}$: parton shower  & $\pm 5.4 $  & $\pm 4.8 $  & $\pm 10 $  & $\pm 4.9 $  & $\pm 1.7$ &  $\pm 1.5 $  & $\pm 6.5 $  & $\pm 3.1 $ \\ 
%$t\bar{t}$+HF: normalisation  & --  & --  & $\pm 50 $  & $\pm 50 $  & -- &  --  & $\pm 32 $  & $\pm 16 $ \\ 
%$t\bar{t}$+HF: modelling  & --  & --  & --  & $\pm 7.7 $  & -- &  --  & --  & $\pm 7.4 $ \\ 
%Signal modelling  & $\pm 6.9 $  & --  & --  & --  & $\pm 6.9$ &  --  & --  & -- \\ 
%Theor. cross sections  & $\pm 6.2 $  & $\pm 6.2 $  & $\pm 6.2 $  & $\pm 6.2 $  & $\pm 3.9$ &  $\pm 3.9 $  & $\pm 3.9 $  & $\pm 3.9 $ \\ 
%\midrule                                                                                                                                                                                               
%Total   & $\pm 17 $  & $\pm 22 $  & $\pm 54 $  & $\pm 53 $  & $\pm 7.8$ &  $\pm 14 $  & $\pm 28 $  & $\pm 15 $ \\ 
%\bottomrule\bottomrule
%\end{tabular}
%\caption{$\Hcbb$ search: summary of the systematic uncertainties considered in the (4 j, 4 b) 
%channel and their impact (in \%) on the normalisation of the signal and the main backgrounds, before and after the fit to data.
%The $\Hc$ signal and the $t\bar{t}$+light-jets background are denoted by ``$WbHc$''  and ``$t\bar{t}$+LJ'' respectively.
%Only sources of systematic uncertainty resulting in a normalisation change of at least 0.5\% are displayed.
%The total post-fit uncertainty can differ from the sum in quadrature of individual sources due to the 
%anti-correlations between them resulting from the fit to the data.}
%\label{tab:SystSummary_WbHc}
%\end{table*}
%%%%%%%%%%%

The following sections describe the systematic uncertainties considered in these searches.

\subsection{Luminosity}
\label{sec:syst_lumi}

The uncertainty in the integrated luminosity is 2.1\%, affecting the overall normalisation of
all processes estimated from the simulation. It is derived, following a methodology similar to that detailed in Ref.~\cite{Aaboud:2016hhf}, 
from a preliminary calibration of the luminosity scale using $x$--$y$ beam-separation scans performed in August 2015 and May 2016.

\subsection{Reconstructed objects}
\label{sec:syst_objects}

%Uncertainties associated with electrons and muons arise from the trigger, reconstruction, identification, and isolation
%efficiencies, as well as the lepton momentum scale and resolution. These are measured in data using 
%$Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events~\cite{ATLAS-CONF-2016-024,Aad:2016jkr}. 
%The combined effect of all these uncertainties results in an overall normalisation 
%uncertainty in signal and background of approximately 1\%.

Uncertainties associated with electrons, muons, and $\tauhad$ candidates arise from the trigger, reconstruction,  
identification and isolation (in the case of electrons and muons) efficiencies, as well as the momentum scale and resolution. 
These are measured in data using $Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events ($\ell =e, \mu$)~\cite{ATLAS-CONF-2016-024,Aad:2016jkr} 
in the case of electrons and muons, and using $Z\to \tau^+\tau^-$ events in the case of $\tauhad$ candidates~\cite{ATLAS-CONF-2017-029}.

Uncertainties associated with jets arise from the jet energy scale
and resolution, and the efficiency to pass the JVT requirements. 
The largest contribution results from the jet energy scale,
whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pileup treatment is split into 21 uncorrelated components 
that are treated independently~\cite{Aaboud:2017jcu}.

Uncertainties associated with energy scales and resolutions of leptons and jets 
are propagated to $\met$. Additional uncertainties originating from the modelling 
of the underlying event, in particular its impact on the $\pt$ scale and resolution 
of unclustered energy, are negligible.

Efficiencies to tag jets from $b$- and $c$-quarks in the simulation are corrected to match the efficiencies in data by $\pt$-dependent factors,
whereas the light-jet efficiency is scaled by $\pt$- and $\eta$-dependent factors.
The $b$-jet efficiency is measured in a data sample enriched in $\ttbar$ events~\cite{Aaboud:2018xwy}, while the $c$-jet efficiency is measured
using $\ttbar$ events~\cite{ATLAS-CONF-2018-001} or $W$+$c$-jet events~\cite{Aad:2015ydr}. The light-jet efficiency 
is measured in a multijet data sample enriched in light-flavour jets~\cite{ATLAS-CONF-2018-006}.
Since the $\ttbar$ sample used to measure the $c$-jet tagging efficiency overlaps with the analysis sample, the $\Hbb$ search uses
instead the $W$+$c$-jet based scale factors.  
In the case of the $\Hbb$ ($\Htautau$) search, the uncertainties on these scale factors include a total of six independent sources affecting $b$-jets, one (three) source(s) affecting $c$-jets, and 17 sources affecting light jets. 
These systematic uncertainties are taken as uncorrelated between $b$-jets, $c$-jets, and light-jets. 
An additional uncertainty is included due to the extrapolation of these corrections to jets 
with $\pt$ beyond the kinematic reach of the data calibration samples used ($\pt>300~\gev$ for $b$- and $c$-jets, 
and $\pt>750~\gev$ for light-jets); it is taken to be correlated among the three jet flavours. 
%This uncertainty is evaluated in the simulation by comparing the tagging efficiencies while varying e.g. the fraction 
%of tracks with shared hits in the silicon detectors or the fraction of fake tracks resulting from random combinations of hits, 
%both of which typically increase at high $\pt$ due to growing track multiplicity and density of hits within the jet. 
Finally, an uncertainty related to the application of $c$-jet scale factors to $\tau$-jets is considered,
but has a negligible impact in these analyses.

\subsection{Background modelling}
\label{sec:syst_bkgmodeling}

A number of sources of systematic uncertainty affecting the modelling of $t\bar{t}$+jets are considered. 
An uncertainty of  6\% is assigned to the inclusive $\ttbar$ production
cross section~\cite{Czakon:2011xx}, including contributions from varying the factorisation and renormalisation 
scales, and from uncertainties in the PDF, $\alpha_{\textrm{S}}$, and the top quark mass, all added in quadrature. 
The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
{\powheg}+{\pythiaeight} with a prediction from either {\amcatnlo}+{\pythiaeight} (in the case of the $\Htautau$ search) or
\textsc{Sherpa} (in the case of the $\Hbb$ search). 
The uncertainty due to the choice of parton shower and hadronisation (PS \& Had) model is derived 
by comparing the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 
Additionally, the uncertainty on the modelling of additional radiation is assessed with two alternative {\powheg}+{\pythiaeight} samples:
the sample with increased radiation (referred to as ``radHi'') has the renormalisation and factorisation scales decreased by a factor of two, 
the $h_{\textrm{damp}}$ parameter doubled, and uses the Var3c upward variation of the A14 parameter set; 
the sample with decreased radiation (referred to as ``radLow'') has the scales increased by a factor of two 
and uses the Var3c downward variation of the A14 set~\cite{ATL-PHYS-PUB-2016-004}.

In the case of the $\Hbb$ search, where the $\ttbar$+HF background plays a more prominent role, a more 
detailed treatment of its associated systematic uncertainties is made. In particular, since several analysis 
regions have a sufficiently large number of events of $\ttbin$ background, its normalisation is completely 
determined by the data during the fit procedure.
%, with no prior uncertainty assumed. 
In the case of the $\ttcin$ normalisation, a normalisation uncertainty of 50\% is assumed, as the fit to the data is unable 
to precisely determine it and the analysis has very limited sensitivity to this uncertainty.
Since the diagrams that contribute to $\ttbar$+light-jets, $\ttcin$, $\ttbin$
production are different, all above uncertainties on $\ttbar$+jets
background modelling (NLO generator, PS \& Had, and radHi/radLow), except the uncertainty on the inclusive cross-section, are
considered to be uncorrelated among these processes.
Additional uncertainties on the $\ttbin$ background are considered associated with the NLO prediction from {\ShOL}, 
which is used for reweighting the nominal {\powheg}+{\pythiaeight} prediction. 
These include three different scale variations,  a different shower-recoil model scheme, and 
two alternative PDF sets (MSTW and NNPDF). Additional uncertainties are assessed for
the contributions to the $\ttbin$ background originating from multiple parton interactions.
Finally, an extra uncertainty on the $\ttbin$ background is assigned by comparing 
the predictions from {\powheg}+{\pythiaeight} and {\ShOL} 4F (5F vs 4F).
In the derivation of the above uncertainties, the overall normalisations of the \ttcin\ and \ttbin\ backgrounds 
at the particle level are fixed to the nominal prediction. In order to maintain the inclusive $\ttbar$ cross section, 
the normalisation of the $\ttbar$+light-jets background at the particle level is adjusted accordingly.
Further details are available in Ref.~\cite{Aaboud:2017rss}.

\textbf{Update discussion on small bkgs systs for tautau (recently updated).}

Uncertainties affecting the normalisation of the $V$+jets background are estimated for the sum
of $W$+jets and $Z$+jets, and separately for $V$+light-jets, $V$+$\geq$1$c$+jets, and $V$+$\geq$1$b$+jets subprocesses.
The total normalisation uncertainty of $V$+jets processes is estimated by comparing the data and total background prediction in 
the different analysis regions considered, but requiring exactly 0 $b$-tagged jets. Agreement between data and predicted background 
in these modified regions, which are dominated by $V$+light-jets, is found to be within approximately 30\%. This bound is taken to 
be the normalisation uncertainty, correlated across all $V$+jets subprocesses. 
Since {\sherpa}~2.2 has been found to underestimate $V$+heavy-flavour by about a factor
of 1.3~\cite{Aaboud:2017xsd}, additional 30\% normalisation uncertainties are assumed for $V$+$\geq$1$c$+jets and $V$+$\geq$1$b$+jets
subprocesses, considered uncorrelated between them.

Uncertainties affecting the modelling of the single-top-quark background include a 
$+5\%$/$-4\%$ uncertainty in the total cross section estimated as a weighted average 
of the theoretical uncertainties in $t$-, $Wt$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
Additional uncertainties associated with the modelling of additional radiation are assessed by comparing the nominal
samples with alternative samples where generator parameters are varied.
For the $t$- and $Wt$-channel processes, an uncertainty due to the choice of parton shower and hadronisation model is derived 
by comparing events produced by {\powheg} interfaced to {\pythia} 6 or {\herwigpp}.
These uncertainties are treated as fully correlated among single-top production processes, but uncorrelated with the
corresponding uncertainty in the $\ttbar$+jets background.
An additional systematic uncertainty on $Wt$-channel production concerning the separation 
between $t\bar{t}$ and $Wt$ at NLO~\cite{Frixione:2008yi} is assessed by comparing
the nominal sample, which uses the so-called ``diagram removal'' scheme, with an alternative sample
using the ``diagram subtraction'' scheme.

Uncertainties on the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah},
as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}
(we assume already two jets come from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the desired jet multiplicity,  
i.e. 34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively.
Recent comparisons between data and {\sherpa}~2.1.1 for $WZ(\to \ell\nu\ell\ell) + \geq$4 jets show
agreement within the experimental uncertainty of approximately 40\%~\cite{Aaboud:2016yus}, which further justifies the above uncertainty.

Uncertainties in the $\ttbar V$ and $\ttbar H$ cross sections are 15\% and $+10\%$/$-13\%$, respectively,
from the uncertainties in their respective NLO theoretical cross sections~\cite{Campbell:2012dh,Garzelli:2012bn,Dittmaier:2011ti}.

Uncertainties on the data-driven multijet background in the $\Hbb$ search estimate receive
contributions from the limited sample size in data, particularly at high jet and $b$-tag multiplicities, as 
well as from the uncertainty on the rate of fake leptons, estimated in 
different control regions (e.g. selected with a requirement on either the maximum $\met$ or $\mtw$). 
A combined normalisation uncertainty of 50\% due 
to all these effects is assigned, which is taken as correlated across jet
and $b$-tag multiplicity bins, but uncorrelated between electron and muon channels. 
No explicit shape uncertainty is assigned since the large statistical uncertainties associated with
the multijet background prediction, which are uncorrelated 
between bins in the final discriminant distribution, effectively cover all possible shape uncertainties.

Uncertainties on the data-driven fake $\tauhad$ background in the $\Htautau$ search are obtained by using additional signal-depleted samples. The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\tauhad$ identification criteria, and thus referred to as ``loose SR"  and ``loose CR". 
In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty on the prediction in the nominal SR. In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\tauhad$ candidate from the simulation that are added to the fake template in the $\hadhad$ channel as part of the fake $\tauhad$ background estimation procedure (see Section~\ref{sec:faketaus}). This uncertainty, associated with the modelling of the fake $\tauhad$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\tauhad$ candidate. Finally, the normalisation of the fake $\tauhad$ background in each SR is completely determined by the data during the fit procedure, and thus so is its uncertainty. In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template. The MC studies shows that non-H-to-tautau signal with fake taus can contribute to the $\lephad$ channel. So a 30\% uncertainty is  applied to these signal-faking-tau events.

\subsection{Signal modelling}
\label{sec:syst_sigmodeling}

Several normalisation and shape uncertainties are taken into account for the $\Hq$ signal.
The uncertainty on the $\ttbar$ cross section (see above) also applies to the $\Hq$ signal
and is taken to be the same as, and fully correlated with, the uncertainty assigned to the $\ttbar \to WbWb$ background. 
Uncertainties on the Higgs boson branching ratios are taken into account
following the recommendation in Ref.~\cite{deFlorian:2016spz}.
%: $\pm 1.1\%$ ($\Delta\alpha_\textrm{S}$),  $\pm 1.4\%$ ($\Delta m_b$) and $\pm 0.8\%$ (theory).
Additional uncertainties associated with the modelling of additional radiation, with the choice of NLO generator, and
with the choice of parton shower and hadronisation model, are estimated from the comparison of the nominal
and alternative $\ttbar \to WbWb$ background samples (see discussion above) and applied to $\Hq$ signal. 
These modelling uncertainties are taken to be uncorrelated with those affecting the $\ttbar \to WbWb$ background.

### 2018-07-17 sections/introduction.tex
Implemented additional CDS comments by Michele Webber

@@
 The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well multiple jets. 
-Both searches employ different multivariate techniques to discriminate between the signal and the background on the basis of their kinematic differences. 
+Both searches employ different multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
 These two searches are combined with previous ATLAS searches in the diphoton and multilepton final states using the same dataset~\cite{Aaboud:2017mfd,Aaboud:2018pob}, 

### 2018-07-17 sections/statistical_analysis.tex
Implemented additional CDS comments by Michele Webber

@@
 and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties in the signal and background expectations. 
-Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. With the exception of a few parameters 
+Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
+All nuisance parameters are implemented in the likelihood function as Gaussian or log-normal constraints, with the exception of a few parameters 
 that control the normalisation of the some of the background components (e.g. the \ttbin\ background in the case of the $\Hbb$ search) 
-and are treated as free parameters in the fit,  all other nuisance parameters are implemented in the likelihood function 
-as Gaussian or log-normal constraints.
+and are treated as free parameters in the fit.
 
@@
 The test statistic $q_\mu$ is defined as the profile likelihood ratio: 
-$q_\mu = -2\ln({\cal L}(\mu,\hat{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
+$q_\mu = -2\ln({\cal L}(\mu,{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
 where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
-maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and $\hat{\hat{\theta}}_\mu$ are the values of the
+maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and ${\hat{\theta}}_\mu$ are the values of the
 nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
@@
 A related statistic is used to determine the probability that the observed data are compatible with the background-only hypothesis (i.e.~the discovery test)  
-by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,\hat{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
+by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
 The $p$-value (referred to as $p_0$) representing the probability of the data being compatible with the 
 background-only hypothesis is estimated by integrating
-the distribution of $q_0$ from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js,ErratumCowan:2010js}, above the observed value of $q_0$.
+the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js,ErratumCowan:2010js}, above the observed value of $q_0$ in the data.
 The observed $p_0$-value is checked for each explored signal scenario.

### 2018-07-17 sections/strategy_Hbb.tex
Implemented additional CDS comments by Michele Webber

@@
 Given the choice of the $W\to\ell\nu$ and $H\to b\bar{b}$ decay modes, the $\ttbar \to WbHq$ signal 
-is expected to have four jets and three $b$-quarks in the final state, which can be effectively exploited 
-to suppress the background. 
+is expected to have four jets in the final state, three of them originating from $b$-quarks, which 
+can be effectively exploited to suppress the background. 
 Additional jets can also be present because of initial- or final-state radiation.
@@
 
-After event categorisation, the signal-to-background ratio is very low even in the most sensitive analysis regions, and a suitable
+After event categorisation, the signal-to-background ratio is insufficient even in the best cases to achieve sensitivity, and a suitable
 discriminating variable between signal and background needs to be constructed in order to improve the sensitivity of the search.
@@
 the analysis: $\ttbar$+light-jets and $\ttbin$. Thus, $P^\textrm{bkg}$ is computed as the average of
-the pdfs for both hypotheses, weighted by their relative fractions in simulated $\ttbar$+jets events, which depend
+the pdfs for both hypotheses, weighted by their relative fractions found in simulated $\ttbar$+jets events, which depend
 on the analysis region considered. Furthermore, in a significant fraction of $\Hq$ simulated events (e.g. about 40--50\% in 3b regions), 
@@
 
-An example of the discrimination between signal and background that is obtained is shown in Figure~\ref{fig:LHD},
-where the shape of the LH discriminant distribution is compared between the $\Hc$ and $\Hu$ signals and the 
+%An example of the discrimination between signal and background that is obtained is shown in Figure~\ref{fig:LHD},
+%where the shape of the LH discriminant distribution is compared between the $\Hc$ and $\Hu$ signals and the 
+%$t\bar{t}\to WbWb$ background in each of the analysis regions considered.
+
+Since this analysis has higher expected sensitivity to a $\Hc$ signal than to a $\Hu$ signal and, in order to allow probing 
+of the $\BR(t\to Hu)$ versus $\BR(t\to Hc)$ plane, the discriminant optimised for $\Hc$ is used for both 
+decay modes. It was verified that using the $\Hc$ discriminant for the $\Hu$ search does not result in a significant sensitivity loss.
+Figure~\ref{fig:LHD} compares the shape of the LH distribution between the $\Hc$ and $\Hu$ signals and the 
 $t\bar{t}\to WbWb$ background in each of the analysis regions considered.

### 2018-07-17 sections/strategy_Htautau.tex
Implemented additional CDS comments by Michele Webber

@@
 
-In the $\Htautau$ search, the final state signature of interest is characterised by the presence of two $\tau$-leptons from the
-decay of the Higgs boson and a light-quark jet, both originating from the decay of one of the top quarks. If one of the $\tau$-leptons
-decays leptonically, an isolated electron or muon and significant $\met$ would also be expected.
-The other top quark decays into a $W$ boson and a $b$-quark, with the $W$ boson in turn decaying hadronically, giving 
-three additional jets, one of which should be tagged as a $b$-jet. Therefore, at least four jets are typically expected in signal events.
+In the $\Htautau$ search, the $\ttbar \to WbHq$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
+the Higgs boson and at least four jets, only one of which originates from a $b$-quark.
+%In the $\Htautau$ search, the final state signature of interest is characterised by the presence of two $\tau$-leptons from the
+%decay of the Higgs boson as well as a light-quark jet, the latter two originating from the decay of one of the top quarks. 
+If one of the $\tau$-leptons decays leptonically, an isolated electron or muon and significant $\met$ is also expected.
+%The other top quark decays into a $W$ boson and a $b$-quark, with the $W$ boson in turn decaying hadronically, resulting in 
+%three additional jets. Therefore, at least four jets are typically expected in signal events.
 However, in a significant fraction of the events the trailing jet from the $W$-boson decay fails the minimum $\pt$ requirement of $30~\gev$,
 resulting in signal events with only three jets reconstructed.
-In order to optimise the sensitivity of the search, the selected events are categorised into four search 
-regions depending on the number of $\taulep$ and $\tauhad$ candidates, and on the number of jets:
+In order to optimise the sensitivity of the search, the selected events are categorised into four SRs depending 
+on the number of $\taulep$ and $\tauhad$ candidates, and on the number of jets:
 ($\lephad$, 3j), ($\lephad$, $\geq$4j), ($\hadhad$, 3j), and ($\hadhad$, $\geq$4j).
@@
 of $\met$ in the event (larger in $\lephad$ events compared to $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
-is missing or not (3j vs $\geq$4j events). This analysis adopts the event reconstruction strategy developed in Ref.~\cite{Chen:2015nta},
-which is briefly summarised in the following. Events with exactly three jets that are compatible with having a fully reconstructed hadronically decaying 
-top quark ($t \to Wb \to qqb$) necessarily miss the light-quark jet from the $t \to Hq$ decay and are thus rejected. 
+is missing or not (3j vs $\geq$4j events). 
+%This analysis adopts the event reconstruction strategy developed in Ref.~\cite{Chen:2015nta}, which is briefly summarised in the following. 
+The event reconstruction strategy used~\cite{Chen:2015nta} is summarised in the following.
+Events with exactly three jets that are compatible with having a fully reconstructed hadronically decaying 
+top quark ($t \to Wb \to qqb$) are rejected, as the $t \to Hq$ decay cannot be reconstructed due to the missing light-quark jet.
 For both 3j and $\geq$4j events, the selected jets are assigned to the different top quark decay products via a criterion based on 
@@
 $m_{\text{T,lep}}$                              	& $\times$  & $\times$  &             & \\
-$p_{\text{T,1}}$                             	&             &             & $\times$  & $\times$ \\
+$p_{\text{T,1}}$                             	& $\times$  & $\times$ & $\times$  & $\times$ \\
 $p_{\text{T,2}}$                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
@@
 Boosted decision trees (BDT)~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} are used in each SR to improve the separation between signal and background.
-The separate training naturally exploits differences in event kinematics across SRs.
+The separate training exploits differences in event kinematics across SRs.
+In the training, only the $\Hq$ signal is used against the total SM background, including both real and fake $\tauhad$ contributions.
 A large set of potential variables was investigated in each SR separately, and only those variables that led to an improved discrimination
-performance of the BDT were kept. In the training, only the $\Hq$ signal is used against the total SM background, including both real
-and fake $\tauhad$ contributions. The BDT input variables used per SR are listed in Table~\ref{tab:mva_var} and defined in the following:
+performance of the BDT were kept.  The BDT input variables in each SR are listed in Table~\ref{tab:mva_var} and defined in the following:
 

### 2018-07-17 sections/systematic_uncertainties.tex
Implemented additional CDS comments by Michele Webber

@@
 Each source of systematic uncertainty is considered to be uncorrelated with the other sources.  
-Correlations of a given systematic uncertainty are maintained across processes and channels.
+Correlations of a given systematic uncertainty are maintained across processes and channels 
+as appropriate.
+The following sections describe the systematic uncertainties considered.
 
@@
 
-The following sections describe the systematic uncertainties considered in these searches.
-
 \subsection{Luminosity}
@@
 Additionally, the uncertainty on the modelling of additional radiation is assessed with two alternative {\powheg}+{\pythiaeight} samples:
-the sample with increased radiation (referred to as ``radHi'') has the renormalisation and factorisation scales decreased by a factor of two, 
-the $h_{\textrm{damp}}$ parameter doubled, and uses the Var3c upward variation of the A14 parameter set; 
-the sample with decreased radiation (referred to as ``radLow'') has the scales increased by a factor of two 
-and uses the Var3c downward variation of the A14 set~\cite{ATL-PHYS-PUB-2016-004}.
+a sample with increased radiation (referred to as ``radHi'') is obtained by decreasing the renormalisation and factorisation scales  
+by a factor of two, doubling the $h_{\textrm{damp}}$ parameter, and using the Var3c upward variation of the A14 parameter set;
+a sample with decreased radiation (referred to as ``radLow'') is obtained by increasing the scales by a factor of two 
+and using the Var3c downward variation of the A14 set~\cite{ATL-PHYS-PUB-2016-004}.
 
@@
 detailed treatment of its associated systematic uncertainties is made. In particular, since several analysis 
-regions have a sufficiently large number of events of $\ttbin$ background, its normalisation is completely 
+regions have a sufficiently large number of events of $\ttbin$ background, its normalisation is 
 determined by the data during the fit procedure.
@@
 In the case of the $\ttcin$ normalisation, a normalisation uncertainty of 50\% is assumed, as the fit to the data is unable 
-to precisely determine it and the analysis has very limited sensitivity to this uncertainty.
+to precisely determine it, and the analysis has very limited sensitivity to this uncertainty.
 Since the diagrams that contribute to $\ttbar$+light-jets, $\ttcin$, $\ttbin$
@@
 An additional systematic uncertainty on $Wt$-channel production concerning the separation 
-between $t\bar{t}$ and $Wt$ at NLO~\cite{Frixione:2008yi} is assessed by comparing
-the nominal sample, which uses the so-called ``diagram removal'' scheme, with an alternative sample
-using the ``diagram subtraction'' scheme.
+between $t\bar{t}$ and $Wt$ at NLO is assessed by comparing
+the nominal sample, which uses the so-called ``diagram removal'' scheme~\cite{Frixione:2008yi}, with an alternative sample
+using the ``diagram subtraction'' scheme~\cite{Frixione:2008yi}.
 
@@
 (we assume already two jets come from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
-Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the desired jet multiplicity,  
+Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the selected jet multiplicity,  
 i.e. 34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively.
@@
 
-Uncertainties on the data-driven multijet background in the $\Hbb$ search estimate receive
+Uncertainties on the data-driven multijet background in the $\Hbb$ search estimate include
 contributions from the limited sample size in data, particularly at high jet and $b$-tag multiplicities, as 
@@
 This uncertainty, associated with the modelling of the fake $\tauhad$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\tauhad$ candidate.
-Finally, the normalisation of the fake $\tauhad$ background in each SR is completely determined by the data during the fit procedure, and thus so is its uncertainty.
+Finally, the normalisation of the fake $\tauhad$ background in each SR is determined by the data during the fit procedure, and thus so is its uncertainty.
 In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template.
@@
 Several normalisation and shape uncertainties are taken into account for the $\Hq$ signal.
-The uncertainty on the $\ttbar$ cross section (see above) also applies to the $\Hq$ signal
-and is taken to be the same as, and fully correlated with, the uncertainty assigned to the $\ttbar \to WbWb$ background. 
+The uncertainty on the $\ttbar$ cross section also applies to the $\Hq$ signal and is taken to be the same as, 
+and fully correlated with, the uncertainty assigned to the $\ttbar \to WbWb$ background (see Sect.~\ref{sec:syst_bkgmodeling}).
 Uncertainties on the Higgs boson branching ratios are taken into account
@@
 with the choice of parton shower and hadronisation model, are estimated from the comparison of the nominal
-and alternative $\ttbar \to WbWb$ background samples (see discussion above) and applied to $\Hq$ signal. 
+and alternative $\ttbar \to WbWb$ background samples (see discussion in Sect.~\ref{sec:syst_bkgmodeling}) and applied to $\Hq$ signal. 
 These modelling uncertainties are taken to be uncorrelated with those affecting the $\ttbar \to WbWb$ background.

### 2018-07-19 figures/Hbb/fit/cH_plots/Summary.C
updated summary plot

@@ -1,0 +1,1020 @@
+void Summary()
+{
+//=========Macro generated from canvas: base_ebv2_signal_cH_uH_default_summary/base_ebv2_signal_cH_uH_default_summary
+//=========  (Thu Jul 19 21:00:39 2018) by ROOT version6.04/14
+   TCanvas *base_ebv2_signal_cH_uH_default_summary = new TCanvas("base_ebv2_signal_cH_uH_default_summary", "base_ebv2_signal_cH_uH_default_summary",0,0,900,850);
+   gStyle->SetOptStat(0);
+   gStyle->SetOptTitle(0);
+   base_ebv2_signal_cH_uH_default_summary->SetHighLightColor(2);
+   base_ebv2_signal_cH_uH_default_summary->Range(0,0,1,1);
+   base_ebv2_signal_cH_uH_default_summary->SetFillColor(0);
+   base_ebv2_signal_cH_uH_default_summary->SetBorderMode(0);
+   base_ebv2_signal_cH_uH_default_summary->SetBorderSize(2);
+   base_ebv2_signal_cH_uH_default_summary->SetTickx(1);
+   base_ebv2_signal_cH_uH_default_summary->SetTicky(1);
+   base_ebv2_signal_cH_uH_default_summary->SetLeftMargin(0.16);
+   base_ebv2_signal_cH_uH_default_summary->SetRightMargin(0.05);
+   base_ebv2_signal_cH_uH_default_summary->SetTopMargin(0.05);
+   base_ebv2_signal_cH_uH_default_summary->SetBottomMargin(0.16);
+   base_ebv2_signal_cH_uH_default_summary->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1
+   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
+   pad1->Draw();
+   pad1->cd();
+   pad1->Range(-1.058824,-0.0873016,9.529412,1.5);
+   pad1->SetFillColor(0);
+   pad1->SetFillStyle(4000);
+   pad1->SetBorderMode(0);
+   pad1->SetBorderSize(0);
+   pad1->SetTickx(1);
+   pad1->SetTicky(1);
+   pad1->SetRightMargin(0.05);
[…]

### 2018-07-19 figures/Hbb/fit/cH_plots/Summary.C
fixing summary

@@ -1,7 +1,7 @@
 void Summary()
 {
 //=========Macro generated from canvas: base_ebv2_signal_cH_uH_default_summary/base_ebv2_signal_cH_uH_default_summary
-//=========  (Thu Jul 19 21:00:39 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 21:37:42 2018) by ROOT version6.04/14
    TCanvas *base_ebv2_signal_cH_uH_default_summary = new TCanvas("base_ebv2_signal_cH_uH_default_summary", "base_ebv2_signal_cH_uH_default_summary",0,0,900,850);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -45,13 +45,13 @@ void Summary()
    h_dummy2__109->SetMarkerStyle(20);
    h_dummy2__109->SetMarkerSize(1.2);
    h_dummy2__109->GetXaxis()->SetBinLabel(1,"4j, 2b");
-   h_dummy2__109->GetXaxis()->SetBinLabel(2,"4j, 3b");
-   h_dummy2__109->GetXaxis()->SetBinLabel(3,"4j, #geq4b");
-   h_dummy2__109->GetXaxis()->SetBinLabel(4,"5j, 2b");
+   h_dummy2__109->GetXaxis()->SetBinLabel(2,"5j, 2b");
+   h_dummy2__109->GetXaxis()->SetBinLabel(3,"#geq6j, 2b");
+   h_dummy2__109->GetXaxis()->SetBinLabel(4,"4j, 3b");
    h_dummy2__109->GetXaxis()->SetBinLabel(5,"5j, 3b");
-   h_dummy2__109->GetXaxis()->SetBinLabel(6,"5j, #geq4b");
-   h_dummy2__109->GetXaxis()->SetBinLabel(7,"#geq6j, 2b");
-   h_dummy2__109->GetXaxis()->SetBinLabel(8,"#geq6j, 3b");
+   h_dummy2__109->GetXaxis()->SetBinLabel(6,"#geq6j, 3b");
+   h_dummy2__109->GetXaxis()->SetBinLabel(7,"4j, #geq4b");
+   h_dummy2__109->GetXaxis()->SetBinLabel(8,"5j, #geq4b");
    h_dummy2__109->GetXaxis()->SetBinLabel(9,"#geq6j, #geq4b");
    h_dummy2__109->GetXaxis()->SetBit(TAxis::kLabelsVert);
    h_dummy2__109->GetXaxis()->SetLabelFont(43);
[…]

### 2018-07-19 sections/data_presel.tex
Implemented some CDS comments from Michele Weber

@@
 The selected light lepton (electron or muon) is required to match, with $\Delta R < 0.15$, the lepton reconstructed by 
-the trigger and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1--2~\gev. In addition, its electric charge is required to be of
-opposite sign to that of the leading $\tauhad$ candidate.
+the trigger and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev or 2~\gev (depending on the lepton trigger and 
+data taking period). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
 Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 

### 2018-07-19 sections/signal_background_modeling.tex
Implemented some CDS comments from Michele Weber

@@
 The simulation study shows that b-jet faking rate is quite low and the fake $\tauhad$ candidates primarily result from the misidentification of light-quark jets.
+\textbf{Add sentence requested by Xin.}
 This background is estimated directly from data by defining control regions (CR) enriched in fake $\tauhad$ candidates via loosened $\tauhad$ requirements.

### 2018-07-19 sections/statistical_analysis.tex
Implemented some CDS comments from Michele Weber

@@
 the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js,ErratumCowan:2010js}, above the observed value of $q_0$ in the data.
-The observed $p_0$-value is checked for each explored signal scenario.
-In the absence of any significant excess above the background expectation, upper limits on $\mu$, and thus on 
+%The observed $p_0$-value is checked for each explored signal scenario.
+In the case of the data being compatible with the background expectation, upper limits on $\mu$, and thus on 
 $\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.

### 2018-07-19 sections/strategy_Hbb.tex
Implemented some CDS comments from Michele Weber

@@
 Regions with exactly two $b$-tagged jets are dominated by $\ttbar$+light jets, while regions with 
-$\geq$4 $b$-tagged jets are dominated by $\ttbb$. Intermediate compositions are found in regions with exactly three 
+at least four $b$-tagged jets are dominated by $\ttbb$. Intermediate compositions are found in regions with exactly three 
 $b$-tagged jets.  Most of the $\ttbar$+light-jets background in the these regions have a charm jet from the hadronic $W$ boson 
@@
 
-In the regions with four or five jets and exactly three $b$-tags, which dominate the sensitivity of this search, 
+In the regions with four or five jets and exactly three $b$-tagged jets, which dominate the sensitivity of this search, 
 the selected signal events have a $H \to b\bar{b}$ decay in more than 97\% of the events.
-Because of somewhat larger fraction of $\Hc$ signal in the regions with exactly three $b$-tags,
+Because of somewhat larger fraction of $\Hc$ signal in the regions with exactly three $b$-tagged jets,
 this analysis is expected to have slightly better sensitivity for $\Hc$ than for $\Hu$ signal.
@@
 The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
-which is determined via a likelihood fit to data. \textbf{TO DO: Improve style.}} 
+which is determined via a likelihood fit to data.} 
 \label{fig:Hbb_Summary}

### 2018-07-19 sections/strategy_Htautau.tex
Implemented some CDS comments from Michele Weber

@@
 of $\met$ in the event (larger in $\lephad$ events compared to $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
-is missing or not (3j vs $\geq$4j events). 
+is missing or not (events with exactly three jets or at least four jets).
 %This analysis adopts the event reconstruction strategy developed in Ref.~\cite{Chen:2015nta}, which is briefly summarised in the following. 
@@
 top quark ($t \to Wb \to qqb$) are rejected, as the $t \to Hq$ decay cannot be reconstructed due to the missing light-quark jet.
-For both 3j and $\geq$4j events, the selected jets are assigned to the different top quark decay products via a criterion based on 
+For the remaining events, the selected jets are assigned to the different top quark decay products via a criterion based on 
 minimising a sum of angular distances between objects. Finally, the four-momenta of the invisible decay products for each $\tau$-lepton decay 
@@
 \item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$-boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark.
-This variable is only defined for $\geq$4j events.
+This variable is only defined for events with at least four jets.
 \end{itemize}
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
-\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most
+\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of some of the most
 important BDT input variables in the $\lephad$ channel. The distributions are shown for
-(a) $m_{\tau\tau}^{\text{fit}}$ in the 3j region, (b) $m_{\tau\tau}^{\text{fit}}$ in the $\geq$4j region, (c) $p_{\text{T},2}$ in the 3j region,
-and (d) $p_{\text{T},2}$ in the $\geq$4j region.
+$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
+$p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
 The expected $\Hc$ signal (dashed histogram) is shown normalised to $\BR(t\to Hc)=1\%$.
@@
 important BDT input variables in the $\hadhad$ channel. The distributions are shown for
-(a) $m_{\tau\tau}^{\text{fit}}$ in the 3j region, (b) $m_{\tau\tau}^{\text{fit}}$ in the $\geq$4j region, (c) $x_{1}^{\text{fit}}$ in the 3j region,
-and (d) $x_{2}^{\text{fit}}$ in the $\geq$4j region.
+$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
+(c) $x_{1}^{\text{fit}}$ in the ($\hadhad$, 3j)  region, and (d) $x_{2}^{\text{fit}}$ in the ($\hadhad$, $\geq$4j) region.
 The expected $\Hc$ signal (dashed histogram) is shown normalised to $\BR(t\to Hc)=1\%$.

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep4jex2bex.C
adding new fit plots Hbb

@@ -1,7 +1,7 @@
 void c1lep4jex2bex()
 {
 //=========Macro generated from canvas: c_c1lep4jex2bex/c_c1lep4jex2bex
-//=========  (Thu Jul 19 11:17:23 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:20:13 2018) by ROOT version6.04/14
    TCanvas *c_c1lep4jex2bex = new TCanvas("c_c1lep4jex2bex", "c_c1lep4jex2bex",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -594,7 +594,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
+   TLegend *leg = new TLegend(0.5308,0.63,0.92,0.93,NULL,"brNDC");
    leg->SetBorderSize(0);
    leg->SetTextFont(43);
    leg->SetTextSize(18.9);

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep4jex2bex_postFit.C

@@ -1,7 +1,7 @@
 void c1lep4jex2bex_postFit()
 {
 //=========Macro generated from canvas: c_c1lep4jex2bex_postFit/c_c1lep4jex2bex_postFit
-//=========  (Thu Jul 19 11:48:32 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:32:21 2018) by ROOT version6.04/14
    TCanvas *c_c1lep4jex2bex_postFit = new TCanvas("c_c1lep4jex2bex_postFit", "c_c1lep4jex2bex_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -53,7 +53,7 @@ void c1lep4jex2bex_postFit()
    h_dummy2__1->GetXaxis()->SetTitleSize(21);
    h_dummy2__1->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__1->GetXaxis()->SetTitleFont(43);
-   h_dummy2__1->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__1->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2__1->GetYaxis()->SetNdivisions(-504);
    h_dummy2__1->GetYaxis()->SetLabelFont(43);
    h_dummy2__1->GetYaxis()->SetLabelOffset(0.02);
@@ -185,7 +185,7 @@ void c1lep4jex2bex_postFit()
    h_dummy2_copy__2->GetXaxis()->SetTitleSize(21);
    h_dummy2_copy__2->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__2->GetXaxis()->SetTitleFont(43);
-   h_dummy2_copy__2->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__2->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2_copy__2->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__2->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__2->GetYaxis()->SetLabelOffset(0.02);
@@ -594,7 +594,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
[…]

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep4jex3bex.C

@@ -1,7 +1,7 @@
 void c1lep4jex3bex()
 {
 //=========Macro generated from canvas: c_c1lep4jex3bex/c_c1lep4jex3bex
-//=========  (Thu Jul 19 11:17:23 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:20:13 2018) by ROOT version6.04/14
    TCanvas *c_c1lep4jex3bex = new TCanvas("c_c1lep4jex3bex", "c_c1lep4jex3bex",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -890,7 +890,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
+   TLegend *leg = new TLegend(0.5308,0.63,0.92,0.93,NULL,"brNDC");
    leg->SetBorderSize(0);
    leg->SetTextFont(43);
    leg->SetTextSize(18.9);

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep4jex3bex_postFit.C

@@ -1,7 +1,7 @@
 void c1lep4jex3bex_postFit()
 {
 //=========Macro generated from canvas: c_c1lep4jex3bex_postFit/c_c1lep4jex3bex_postFit
-//=========  (Thu Jul 19 11:48:33 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:32:22 2018) by ROOT version6.04/14
    TCanvas *c_c1lep4jex3bex_postFit = new TCanvas("c_c1lep4jex3bex_postFit", "c_c1lep4jex3bex_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -53,7 +53,7 @@ void c1lep4jex3bex_postFit()
    h_dummy2__10->GetXaxis()->SetTitleSize(21);
    h_dummy2__10->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__10->GetXaxis()->SetTitleFont(43);
-   h_dummy2__10->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__10->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2__10->GetYaxis()->SetNdivisions(-504);
    h_dummy2__10->GetYaxis()->SetLabelFont(43);
    h_dummy2__10->GetYaxis()->SetLabelOffset(0.02);
@@ -293,7 +293,7 @@ void c1lep4jex3bex_postFit()
    h_dummy2_copy__11->GetXaxis()->SetTitleSize(21);
    h_dummy2_copy__11->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__11->GetXaxis()->SetTitleFont(43);
-   h_dummy2_copy__11->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__11->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2_copy__11->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__11->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__11->GetYaxis()->SetLabelOffset(0.02);
@@ -890,7 +890,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
[…]

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep4jex4bin.C

@@ -1,7 +1,7 @@
 void c1lep4jex4bin()
 {
 //=========Macro generated from canvas: c_c1lep4jex4bin/c_c1lep4jex4bin
-//=========  (Thu Jul 19 11:17:23 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:20:13 2018) by ROOT version6.04/14
    TCanvas *c_c1lep4jex4bin = new TCanvas("c_c1lep4jex4bin", "c_c1lep4jex4bin",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -618,7 +618,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
+   TLegend *leg = new TLegend(0.5308,0.63,0.92,0.93,NULL,"brNDC");
    leg->SetBorderSize(0);
    leg->SetTextFont(43);
    leg->SetTextSize(18.9);

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep4jex4bin_postFit.C

@@ -1,7 +1,7 @@
 void c1lep4jex4bin_postFit()
 {
 //=========Macro generated from canvas: c_c1lep4jex4bin_postFit/c_c1lep4jex4bin_postFit
-//=========  (Thu Jul 19 11:48:34 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:32:23 2018) by ROOT version6.04/14
    TCanvas *c_c1lep4jex4bin_postFit = new TCanvas("c_c1lep4jex4bin_postFit", "c_c1lep4jex4bin_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -53,7 +53,7 @@ void c1lep4jex4bin_postFit()
    h_dummy2__19->GetXaxis()->SetTitleSize(21);
    h_dummy2__19->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__19->GetXaxis()->SetTitleFont(43);
-   h_dummy2__19->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__19->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2__19->GetYaxis()->SetNdivisions(-504);
    h_dummy2__19->GetYaxis()->SetLabelFont(43);
    h_dummy2__19->GetYaxis()->SetLabelOffset(0.02);
@@ -197,7 +197,7 @@ void c1lep4jex4bin_postFit()
    h_dummy2_copy__20->GetXaxis()->SetTitleSize(21);
    h_dummy2_copy__20->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__20->GetXaxis()->SetTitleFont(43);
-   h_dummy2_copy__20->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__20->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2_copy__20->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__20->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__20->GetYaxis()->SetLabelOffset(0.02);
@@ -618,7 +618,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
[…]

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep5jex2bex.C

@@ -1,7 +1,7 @@
 void c1lep5jex2bex()
 {
 //=========Macro generated from canvas: c_c1lep5jex2bex/c_c1lep5jex2bex
-//=========  (Thu Jul 19 11:17:24 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:20:14 2018) by ROOT version6.04/14
    TCanvas *c_c1lep5jex2bex = new TCanvas("c_c1lep5jex2bex", "c_c1lep5jex2bex",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -594,7 +594,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
+   TLegend *leg = new TLegend(0.5308,0.63,0.92,0.93,NULL,"brNDC");
    leg->SetBorderSize(0);
    leg->SetTextFont(43);
    leg->SetTextSize(18.9);

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep5jex2bex_postFit.C

@@ -1,7 +1,7 @@
 void c1lep5jex2bex_postFit()
 {
 //=========Macro generated from canvas: c_c1lep5jex2bex_postFit/c_c1lep5jex2bex_postFit
-//=========  (Thu Jul 19 11:48:35 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:32:23 2018) by ROOT version6.04/14
    TCanvas *c_c1lep5jex2bex_postFit = new TCanvas("c_c1lep5jex2bex_postFit", "c_c1lep5jex2bex_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -53,7 +53,7 @@ void c1lep5jex2bex_postFit()
    h_dummy2__28->GetXaxis()->SetTitleSize(21);
    h_dummy2__28->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__28->GetXaxis()->SetTitleFont(43);
-   h_dummy2__28->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__28->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2__28->GetYaxis()->SetNdivisions(-504);
    h_dummy2__28->GetYaxis()->SetLabelFont(43);
    h_dummy2__28->GetYaxis()->SetLabelOffset(0.02);
@@ -185,7 +185,7 @@ void c1lep5jex2bex_postFit()
    h_dummy2_copy__29->GetXaxis()->SetTitleSize(21);
    h_dummy2_copy__29->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__29->GetXaxis()->SetTitleFont(43);
-   h_dummy2_copy__29->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__29->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2_copy__29->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__29->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__29->GetYaxis()->SetLabelOffset(0.02);
@@ -594,7 +594,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
[…]

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep5jex3bex.C

@@ -1,7 +1,7 @@
 void c1lep5jex3bex()
 {
 //=========Macro generated from canvas: c_c1lep5jex3bex/c_c1lep5jex3bex
-//=========  (Thu Jul 19 11:17:24 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:20:14 2018) by ROOT version6.04/14
    TCanvas *c_c1lep5jex3bex = new TCanvas("c_c1lep5jex3bex", "c_c1lep5jex3bex",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -890,7 +890,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
+   TLegend *leg = new TLegend(0.5308,0.63,0.92,0.93,NULL,"brNDC");
    leg->SetBorderSize(0);
    leg->SetTextFont(43);
    leg->SetTextSize(18.9);

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep5jex3bex_postFit.C

@@ -1,7 +1,7 @@
 void c1lep5jex3bex_postFit()
 {
 //=========Macro generated from canvas: c_c1lep5jex3bex_postFit/c_c1lep5jex3bex_postFit
-//=========  (Thu Jul 19 11:48:36 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:32:24 2018) by ROOT version6.04/14
    TCanvas *c_c1lep5jex3bex_postFit = new TCanvas("c_c1lep5jex3bex_postFit", "c_c1lep5jex3bex_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -53,7 +53,7 @@ void c1lep5jex3bex_postFit()
    h_dummy2__37->GetXaxis()->SetTitleSize(21);
    h_dummy2__37->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__37->GetXaxis()->SetTitleFont(43);
-   h_dummy2__37->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__37->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2__37->GetYaxis()->SetNdivisions(-504);
    h_dummy2__37->GetYaxis()->SetLabelFont(43);
    h_dummy2__37->GetYaxis()->SetLabelOffset(0.02);
@@ -293,7 +293,7 @@ void c1lep5jex3bex_postFit()
    h_dummy2_copy__38->GetXaxis()->SetTitleSize(21);
    h_dummy2_copy__38->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__38->GetXaxis()->SetTitleFont(43);
-   h_dummy2_copy__38->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__38->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2_copy__38->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__38->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__38->GetYaxis()->SetLabelOffset(0.02);
@@ -890,7 +890,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
[…]

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep5jex4bin.C

@@ -1,7 +1,7 @@
 void c1lep5jex4bin()
 {
 //=========Macro generated from canvas: c_c1lep5jex4bin/c_c1lep5jex4bin
-//=========  (Thu Jul 19 11:17:24 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:20:14 2018) by ROOT version6.04/14
    TCanvas *c_c1lep5jex4bin = new TCanvas("c_c1lep5jex4bin", "c_c1lep5jex4bin",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -618,7 +618,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
+   TLegend *leg = new TLegend(0.5308,0.63,0.92,0.93,NULL,"brNDC");
    leg->SetBorderSize(0);
    leg->SetTextFont(43);
    leg->SetTextSize(18.9);

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep5jex4bin_postFit.C

@@ -1,7 +1,7 @@
 void c1lep5jex4bin_postFit()
 {
 //=========Macro generated from canvas: c_c1lep5jex4bin_postFit/c_c1lep5jex4bin_postFit
-//=========  (Thu Jul 19 11:48:37 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:32:25 2018) by ROOT version6.04/14
    TCanvas *c_c1lep5jex4bin_postFit = new TCanvas("c_c1lep5jex4bin_postFit", "c_c1lep5jex4bin_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -53,7 +53,7 @@ void c1lep5jex4bin_postFit()
    h_dummy2__46->GetXaxis()->SetTitleSize(21);
    h_dummy2__46->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__46->GetXaxis()->SetTitleFont(43);
-   h_dummy2__46->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__46->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2__46->GetYaxis()->SetNdivisions(-504);
    h_dummy2__46->GetYaxis()->SetLabelFont(43);
    h_dummy2__46->GetYaxis()->SetLabelOffset(0.02);
@@ -197,7 +197,7 @@ void c1lep5jex4bin_postFit()
    h_dummy2_copy__47->GetXaxis()->SetTitleSize(21);
    h_dummy2_copy__47->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__47->GetXaxis()->SetTitleFont(43);
-   h_dummy2_copy__47->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__47->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2_copy__47->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__47->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__47->GetYaxis()->SetLabelOffset(0.02);
@@ -618,7 +618,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
[…]

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep6jin2bex.C

@@ -1,7 +1,7 @@
 void c1lep6jin2bex()
 {
 //=========Macro generated from canvas: c_c1lep6jin2bex/c_c1lep6jin2bex
-//=========  (Thu Jul 19 11:17:24 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:20:15 2018) by ROOT version6.04/14
    TCanvas *c_c1lep6jin2bex = new TCanvas("c_c1lep6jin2bex", "c_c1lep6jin2bex",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -594,7 +594,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
+   TLegend *leg = new TLegend(0.5308,0.63,0.92,0.93,NULL,"brNDC");
    leg->SetBorderSize(0);
    leg->SetTextFont(43);
    leg->SetTextSize(18.9);

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep6jin2bex_postFit.C

@@ -1,7 +1,7 @@
 void c1lep6jin2bex_postFit()
 {
 //=========Macro generated from canvas: c_c1lep6jin2bex_postFit/c_c1lep6jin2bex_postFit
-//=========  (Thu Jul 19 11:48:38 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:32:26 2018) by ROOT version6.04/14
    TCanvas *c_c1lep6jin2bex_postFit = new TCanvas("c_c1lep6jin2bex_postFit", "c_c1lep6jin2bex_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -53,7 +53,7 @@ void c1lep6jin2bex_postFit()
    h_dummy2__55->GetXaxis()->SetTitleSize(21);
    h_dummy2__55->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__55->GetXaxis()->SetTitleFont(43);
-   h_dummy2__55->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__55->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2__55->GetYaxis()->SetNdivisions(-504);
    h_dummy2__55->GetYaxis()->SetLabelFont(43);
    h_dummy2__55->GetYaxis()->SetLabelOffset(0.02);
@@ -185,7 +185,7 @@ void c1lep6jin2bex_postFit()
    h_dummy2_copy__56->GetXaxis()->SetTitleSize(21);
    h_dummy2_copy__56->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__56->GetXaxis()->SetTitleFont(43);
-   h_dummy2_copy__56->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__56->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2_copy__56->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__56->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__56->GetYaxis()->SetLabelOffset(0.02);
@@ -594,7 +594,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
[…]

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep6jin3bex.C

@@ -1,7 +1,7 @@
 void c1lep6jin3bex()
 {
 //=========Macro generated from canvas: c_c1lep6jin3bex/c_c1lep6jin3bex
-//=========  (Thu Jul 19 11:17:25 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:20:15 2018) by ROOT version6.04/14
    TCanvas *c_c1lep6jin3bex = new TCanvas("c_c1lep6jin3bex", "c_c1lep6jin3bex",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -890,7 +890,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
+   TLegend *leg = new TLegend(0.5308,0.63,0.92,0.93,NULL,"brNDC");
    leg->SetBorderSize(0);
    leg->SetTextFont(43);
    leg->SetTextSize(18.9);

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep6jin3bex_postFit.C

@@ -1,7 +1,7 @@
 void c1lep6jin3bex_postFit()
 {
 //=========Macro generated from canvas: c_c1lep6jin3bex_postFit/c_c1lep6jin3bex_postFit
-//=========  (Thu Jul 19 11:48:39 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:32:27 2018) by ROOT version6.04/14
    TCanvas *c_c1lep6jin3bex_postFit = new TCanvas("c_c1lep6jin3bex_postFit", "c_c1lep6jin3bex_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -53,7 +53,7 @@ void c1lep6jin3bex_postFit()
    h_dummy2__64->GetXaxis()->SetTitleSize(21);
    h_dummy2__64->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__64->GetXaxis()->SetTitleFont(43);
-   h_dummy2__64->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__64->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2__64->GetYaxis()->SetNdivisions(-504);
    h_dummy2__64->GetYaxis()->SetLabelFont(43);
    h_dummy2__64->GetYaxis()->SetLabelOffset(0.02);
@@ -293,7 +293,7 @@ void c1lep6jin3bex_postFit()
    h_dummy2_copy__65->GetXaxis()->SetTitleSize(21);
    h_dummy2_copy__65->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__65->GetXaxis()->SetTitleFont(43);
-   h_dummy2_copy__65->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__65->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2_copy__65->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__65->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__65->GetYaxis()->SetLabelOffset(0.02);
@@ -890,7 +890,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
[…]

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep6jin4bin.C

@@ -1,7 +1,7 @@
 void c1lep6jin4bin()
 {
 //=========Macro generated from canvas: c_c1lep6jin4bin/c_c1lep6jin4bin
-//=========  (Thu Jul 19 11:17:25 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:20:15 2018) by ROOT version6.04/14
    TCanvas *c_c1lep6jin4bin = new TCanvas("c_c1lep6jin4bin", "c_c1lep6jin4bin",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -618,7 +618,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
+   TLegend *leg = new TLegend(0.5308,0.63,0.92,0.93,NULL,"brNDC");
    leg->SetBorderSize(0);
    leg->SetTextFont(43);
    leg->SetTextSize(18.9);

### 2018-07-19 figures/Hbb/fit/cH_plots/c1lep6jin4bin_postFit.C

@@ -1,7 +1,7 @@
 void c1lep6jin4bin_postFit()
 {
 //=========Macro generated from canvas: c_c1lep6jin4bin_postFit/c_c1lep6jin4bin_postFit
-//=========  (Thu Jul 19 11:48:40 2018) by ROOT version6.04/14
+//=========  (Thu Jul 19 23:32:28 2018) by ROOT version6.04/14
    TCanvas *c_c1lep6jin4bin_postFit = new TCanvas("c_c1lep6jin4bin_postFit", "c_c1lep6jin4bin_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -53,7 +53,7 @@ void c1lep6jin4bin_postFit()
    h_dummy2__73->GetXaxis()->SetTitleSize(21);
    h_dummy2__73->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__73->GetXaxis()->SetTitleFont(43);
-   h_dummy2__73->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__73->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2__73->GetYaxis()->SetNdivisions(-504);
    h_dummy2__73->GetYaxis()->SetLabelFont(43);
    h_dummy2__73->GetYaxis()->SetLabelOffset(0.02);
@@ -197,7 +197,7 @@ void c1lep6jin4bin_postFit()
    h_dummy2_copy__74->GetXaxis()->SetTitleSize(21);
    h_dummy2_copy__74->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__74->GetXaxis()->SetTitleFont(43);
-   h_dummy2_copy__74->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__74->GetYaxis()->SetTitle("Data / Pred");
    h_dummy2_copy__74->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__74->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__74->GetYaxis()->SetLabelOffset(0.02);
@@ -618,7 +618,7 @@ tex->SetNDC();
    tex->SetLineWidth(2);
    tex->Draw();
    
-   TLegend *leg = new TLegend(0.5508,0.63,0.94,0.93,NULL,"brNDC");
[…]

### 2018-07-20 sections/signal_background_modeling.tex
Additional fixes

--- 2018-06-30 sections/signal_background_modeling.tex
@@
 multijet production, depending on the analysis channel, with $W$+jets production contributing to a lesser extent. 
-The simulation study shows that b-jet faking rate is quite low and the fake $\tauhad$ candidates primarily result from the misidentification of light-quark jets.
+Studies based on the simulation show that , for all above processes, fake $\tauhad$ candidates primarily result from the 
+misidentification of light-quark jets, with the contribution from $b$-quarks and gluon jets playing a subdominant role.
+It is also found that the fake rate decreases as the $\tauhad$ candidate $\pt$ increases for all jet flavours.
+
 This background is estimated directly from data by defining control regions (CR) enriched in fake $\tauhad$ candidates via loosened $\tauhad$ requirements.

### 2018-07-20 sections/systematic_uncertainties.tex
Additional fixes

@@
 
-\textbf{Update discussion on small bkgs systs for tautau (recently updated).}
-
 Uncertainties affecting the normalisation of the $V$+jets background are estimated for the sum
@@
 comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}
-(we assume already two jets come from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
+(it is assumed that two jets come from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
 Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the selected jet multiplicity,  
@@
 The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\tauhad$ identification criteria, and thus referred to as ``loose SR"  and ``loose CR".
-In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty on the prediction in the nominal SR.
+%The shape difference between the fake $\tauhad$ background prediction in each loose SR and its associated loose CR
+%is applied as an uncertainty on the prediction in the nominal SR.
+%In each loose SR, the shape difference between the data and the fake $\tauhad$ background estimate based on its associated loose CR,
+%in both cases having subtracted the small contribution from real $\tauhad$ candidates based on the simulation, 
+%is applied as an uncertainty on the prediction in the nominal SR. 
+%In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty on the prediction in the nominal SR. 
+In each loose SR, after subtracting the small contribution from real $\tauhad$ candidates based on the simulation, 
+the shape difference between the remaining data and the fake $\tauhad$ background estimate based on its associated loose CR 
+is applied as an uncertainty on the prediction in the nominal SR.
 In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\tauhad$ candidate from the simulation that are added to the fake template in the $\hadhad$ channel as part of the fake $\tauhad$ background estimation procedure (see Section~\ref{sec:faketaus}).

### 2018-07-20 figures/Hbb/fit/cH_plots/Summary.C
fixing geq4b vs 4b in bb plots

@@ -1,7 +1,7 @@
 void Summary()
 {
 //=========Macro generated from canvas: base_ebv2_signal_cH_uH_default_summary/base_ebv2_signal_cH_uH_default_summary
-//=========  (Thu Jul 19 21:37:42 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 10:20:53 2018) by ROOT version6.04/14
    TCanvas *base_ebv2_signal_cH_uH_default_summary = new TCanvas("base_ebv2_signal_cH_uH_default_summary", "base_ebv2_signal_cH_uH_default_summary",0,0,900,850);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -50,7 +50,7 @@ void Summary()
    h_dummy2__109->GetXaxis()->SetBinLabel(4,"4j, 3b");
    h_dummy2__109->GetXaxis()->SetBinLabel(5,"5j, 3b");
    h_dummy2__109->GetXaxis()->SetBinLabel(6,"#geq6j, 3b");
-   h_dummy2__109->GetXaxis()->SetBinLabel(7,"4j, #geq4b");
+   h_dummy2__109->GetXaxis()->SetBinLabel(7,"4j, 4b");
    h_dummy2__109->GetXaxis()->SetBinLabel(8,"5j, #geq4b");
    h_dummy2__109->GetXaxis()->SetBinLabel(9,"#geq6j, #geq4b");
    h_dummy2__109->GetXaxis()->SetBit(TAxis::kLabelsVert);
@@ -288,7 +288,7 @@ void Summary()
    h_dummy2_copy__110->GetXaxis()->SetBinLabel(4,"4j, 3b");
    h_dummy2_copy__110->GetXaxis()->SetBinLabel(5,"5j, 3b");
    h_dummy2_copy__110->GetXaxis()->SetBinLabel(6,"#geq6j, 3b");
-   h_dummy2_copy__110->GetXaxis()->SetBinLabel(7,"4j, #geq4b");
+   h_dummy2_copy__110->GetXaxis()->SetBinLabel(7,"4j, 4b");
    h_dummy2_copy__110->GetXaxis()->SetBinLabel(8,"5j, #geq4b");
    h_dummy2_copy__110->GetXaxis()->SetBinLabel(9,"#geq6j, #geq4b");
[…]

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep4jex2bex.C

@@ -1,7 +1,7 @@
 void c1lep4jex2bex()
 {
 //=========Macro generated from canvas: c_c1lep4jex2bex/c_c1lep4jex2bex
-//=========  (Thu Jul 19 23:20:13 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:19:20 2018) by ROOT version6.04/14
    TCanvas *c_c1lep4jex2bex = new TCanvas("c_c1lep4jex2bex", "c_c1lep4jex2bex",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep4jex2bex()
    h_dummy2__1->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__1->GetXaxis()->SetTitleFont(43);
    h_dummy2__1->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__1->GetYaxis()->CenterTitle(true);
    h_dummy2__1->GetYaxis()->SetNdivisions(-504);
    h_dummy2__1->GetYaxis()->SetLabelFont(43);
    h_dummy2__1->GetYaxis()->SetLabelOffset(0.02);
@@ -186,6 +187,7 @@ void c1lep4jex2bex()
    h_dummy2_copy__2->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__2->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__2->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__2->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__2->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__2->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__2->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep4jex2bex_postFit.C

@@ -1,7 +1,7 @@
 void c1lep4jex2bex_postFit()
 {
 //=========Macro generated from canvas: c_c1lep4jex2bex_postFit/c_c1lep4jex2bex_postFit
-//=========  (Thu Jul 19 23:32:21 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:23:07 2018) by ROOT version6.04/14
    TCanvas *c_c1lep4jex2bex_postFit = new TCanvas("c_c1lep4jex2bex_postFit", "c_c1lep4jex2bex_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep4jex2bex_postFit()
    h_dummy2__1->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__1->GetXaxis()->SetTitleFont(43);
    h_dummy2__1->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2__1->GetYaxis()->CenterTitle(true);
    h_dummy2__1->GetYaxis()->SetNdivisions(-504);
    h_dummy2__1->GetYaxis()->SetLabelFont(43);
    h_dummy2__1->GetYaxis()->SetLabelOffset(0.02);
@@ -186,6 +187,7 @@ void c1lep4jex2bex_postFit()
    h_dummy2_copy__2->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__2->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__2->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2_copy__2->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__2->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__2->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__2->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep4jex3bex.C

@@ -1,7 +1,7 @@
 void c1lep4jex3bex()
 {
 //=========Macro generated from canvas: c_c1lep4jex3bex/c_c1lep4jex3bex
-//=========  (Thu Jul 19 23:20:13 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:19:20 2018) by ROOT version6.04/14
    TCanvas *c_c1lep4jex3bex = new TCanvas("c_c1lep4jex3bex", "c_c1lep4jex3bex",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep4jex3bex()
    h_dummy2__10->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__10->GetXaxis()->SetTitleFont(43);
    h_dummy2__10->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__10->GetYaxis()->CenterTitle(true);
    h_dummy2__10->GetYaxis()->SetNdivisions(-504);
    h_dummy2__10->GetYaxis()->SetLabelFont(43);
    h_dummy2__10->GetYaxis()->SetLabelOffset(0.02);
@@ -294,6 +295,7 @@ void c1lep4jex3bex()
    h_dummy2_copy__11->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__11->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__11->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__11->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__11->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__11->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__11->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep4jex3bex_postFit.C

@@ -1,7 +1,7 @@
 void c1lep4jex3bex_postFit()
 {
 //=========Macro generated from canvas: c_c1lep4jex3bex_postFit/c_c1lep4jex3bex_postFit
-//=========  (Thu Jul 19 23:32:22 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:23:08 2018) by ROOT version6.04/14
    TCanvas *c_c1lep4jex3bex_postFit = new TCanvas("c_c1lep4jex3bex_postFit", "c_c1lep4jex3bex_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep4jex3bex_postFit()
    h_dummy2__10->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__10->GetXaxis()->SetTitleFont(43);
    h_dummy2__10->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2__10->GetYaxis()->CenterTitle(true);
    h_dummy2__10->GetYaxis()->SetNdivisions(-504);
    h_dummy2__10->GetYaxis()->SetLabelFont(43);
    h_dummy2__10->GetYaxis()->SetLabelOffset(0.02);
@@ -294,6 +295,7 @@ void c1lep4jex3bex_postFit()
    h_dummy2_copy__11->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__11->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__11->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2_copy__11->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__11->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__11->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__11->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep4jex4bin.C

@@ -1,7 +1,7 @@
 void c1lep4jex4bin()
 {
 //=========Macro generated from canvas: c_c1lep4jex4bin/c_c1lep4jex4bin
-//=========  (Thu Jul 19 23:20:13 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:19:20 2018) by ROOT version6.04/14
    TCanvas *c_c1lep4jex4bin = new TCanvas("c_c1lep4jex4bin", "c_c1lep4jex4bin",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep4jex4bin()
    h_dummy2__19->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__19->GetXaxis()->SetTitleFont(43);
    h_dummy2__19->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__19->GetYaxis()->CenterTitle(true);
    h_dummy2__19->GetYaxis()->SetNdivisions(-504);
    h_dummy2__19->GetYaxis()->SetLabelFont(43);
    h_dummy2__19->GetYaxis()->SetLabelOffset(0.02);
@@ -198,6 +199,7 @@ void c1lep4jex4bin()
    h_dummy2_copy__20->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__20->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__20->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__20->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__20->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__20->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__20->GetYaxis()->SetLabelOffset(0.02);
@@ -605,7 +607,7 @@ tex->SetNDC();
    tex->SetTextSize(21);
    tex->SetLineWidth(2);
    tex->Draw();
-      tex = new TLatex(0.18,0.73,"4j, #geq4b");
+      tex = new TLatex(0.18,0.73,"4j, 4b");
 tex->SetNDC();
    tex->SetTextFont(43);
    tex->SetTextSize(21);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep4jex4bin_postFit.C

@@ -1,7 +1,7 @@
 void c1lep4jex4bin_postFit()
 {
 //=========Macro generated from canvas: c_c1lep4jex4bin_postFit/c_c1lep4jex4bin_postFit
-//=========  (Thu Jul 19 23:32:23 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:23:09 2018) by ROOT version6.04/14
    TCanvas *c_c1lep4jex4bin_postFit = new TCanvas("c_c1lep4jex4bin_postFit", "c_c1lep4jex4bin_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep4jex4bin_postFit()
    h_dummy2__19->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__19->GetXaxis()->SetTitleFont(43);
    h_dummy2__19->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2__19->GetYaxis()->CenterTitle(true);
    h_dummy2__19->GetYaxis()->SetNdivisions(-504);
    h_dummy2__19->GetYaxis()->SetLabelFont(43);
    h_dummy2__19->GetYaxis()->SetLabelOffset(0.02);
@@ -198,6 +199,7 @@ void c1lep4jex4bin_postFit()
    h_dummy2_copy__20->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__20->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__20->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2_copy__20->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__20->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__20->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__20->GetYaxis()->SetLabelOffset(0.02);
@@ -605,7 +607,7 @@ tex->SetNDC();
    tex->SetTextSize(21);
    tex->SetLineWidth(2);
    tex->Draw();
-      tex = new TLatex(0.18,0.73,"4j, #geq4b");
+      tex = new TLatex(0.18,0.73,"4j, 4b");
 tex->SetNDC();
    tex->SetTextFont(43);
    tex->SetTextSize(21);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep5jex2bex.C

@@ -1,7 +1,7 @@
 void c1lep5jex2bex()
 {
 //=========Macro generated from canvas: c_c1lep5jex2bex/c_c1lep5jex2bex
-//=========  (Thu Jul 19 23:20:14 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:19:21 2018) by ROOT version6.04/14
    TCanvas *c_c1lep5jex2bex = new TCanvas("c_c1lep5jex2bex", "c_c1lep5jex2bex",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep5jex2bex()
    h_dummy2__28->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__28->GetXaxis()->SetTitleFont(43);
    h_dummy2__28->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__28->GetYaxis()->CenterTitle(true);
    h_dummy2__28->GetYaxis()->SetNdivisions(-504);
    h_dummy2__28->GetYaxis()->SetLabelFont(43);
    h_dummy2__28->GetYaxis()->SetLabelOffset(0.02);
@@ -186,6 +187,7 @@ void c1lep5jex2bex()
    h_dummy2_copy__29->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__29->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__29->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__29->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__29->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__29->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__29->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep5jex2bex_postFit.C

@@ -1,7 +1,7 @@
 void c1lep5jex2bex_postFit()
 {
 //=========Macro generated from canvas: c_c1lep5jex2bex_postFit/c_c1lep5jex2bex_postFit
-//=========  (Thu Jul 19 23:32:23 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:23:09 2018) by ROOT version6.04/14
    TCanvas *c_c1lep5jex2bex_postFit = new TCanvas("c_c1lep5jex2bex_postFit", "c_c1lep5jex2bex_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep5jex2bex_postFit()
    h_dummy2__28->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__28->GetXaxis()->SetTitleFont(43);
    h_dummy2__28->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2__28->GetYaxis()->CenterTitle(true);
    h_dummy2__28->GetYaxis()->SetNdivisions(-504);
    h_dummy2__28->GetYaxis()->SetLabelFont(43);
    h_dummy2__28->GetYaxis()->SetLabelOffset(0.02);
@@ -186,6 +187,7 @@ void c1lep5jex2bex_postFit()
    h_dummy2_copy__29->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__29->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__29->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2_copy__29->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__29->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__29->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__29->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep5jex3bex.C

@@ -1,7 +1,7 @@
 void c1lep5jex3bex()
 {
 //=========Macro generated from canvas: c_c1lep5jex3bex/c_c1lep5jex3bex
-//=========  (Thu Jul 19 23:20:14 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:19:21 2018) by ROOT version6.04/14
    TCanvas *c_c1lep5jex3bex = new TCanvas("c_c1lep5jex3bex", "c_c1lep5jex3bex",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep5jex3bex()
    h_dummy2__37->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__37->GetXaxis()->SetTitleFont(43);
    h_dummy2__37->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__37->GetYaxis()->CenterTitle(true);
    h_dummy2__37->GetYaxis()->SetNdivisions(-504);
    h_dummy2__37->GetYaxis()->SetLabelFont(43);
    h_dummy2__37->GetYaxis()->SetLabelOffset(0.02);
@@ -294,6 +295,7 @@ void c1lep5jex3bex()
    h_dummy2_copy__38->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__38->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__38->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__38->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__38->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__38->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__38->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep5jex3bex_postFit.C

@@ -1,7 +1,7 @@
 void c1lep5jex3bex_postFit()
 {
 //=========Macro generated from canvas: c_c1lep5jex3bex_postFit/c_c1lep5jex3bex_postFit
-//=========  (Thu Jul 19 23:32:24 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:23:10 2018) by ROOT version6.04/14
    TCanvas *c_c1lep5jex3bex_postFit = new TCanvas("c_c1lep5jex3bex_postFit", "c_c1lep5jex3bex_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep5jex3bex_postFit()
    h_dummy2__37->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__37->GetXaxis()->SetTitleFont(43);
    h_dummy2__37->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2__37->GetYaxis()->CenterTitle(true);
    h_dummy2__37->GetYaxis()->SetNdivisions(-504);
    h_dummy2__37->GetYaxis()->SetLabelFont(43);
    h_dummy2__37->GetYaxis()->SetLabelOffset(0.02);
@@ -294,6 +295,7 @@ void c1lep5jex3bex_postFit()
    h_dummy2_copy__38->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__38->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__38->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2_copy__38->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__38->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__38->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__38->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep5jex4bin.C

@@ -1,7 +1,7 @@
 void c1lep5jex4bin()
 {
 //=========Macro generated from canvas: c_c1lep5jex4bin/c_c1lep5jex4bin
-//=========  (Thu Jul 19 23:20:14 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:19:21 2018) by ROOT version6.04/14
    TCanvas *c_c1lep5jex4bin = new TCanvas("c_c1lep5jex4bin", "c_c1lep5jex4bin",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep5jex4bin()
    h_dummy2__46->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__46->GetXaxis()->SetTitleFont(43);
    h_dummy2__46->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__46->GetYaxis()->CenterTitle(true);
    h_dummy2__46->GetYaxis()->SetNdivisions(-504);
    h_dummy2__46->GetYaxis()->SetLabelFont(43);
    h_dummy2__46->GetYaxis()->SetLabelOffset(0.02);
@@ -198,6 +199,7 @@ void c1lep5jex4bin()
    h_dummy2_copy__47->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__47->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__47->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__47->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__47->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__47->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__47->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep5jex4bin_postFit.C

@@ -1,7 +1,7 @@
 void c1lep5jex4bin_postFit()
 {
 //=========Macro generated from canvas: c_c1lep5jex4bin_postFit/c_c1lep5jex4bin_postFit
-//=========  (Thu Jul 19 23:32:25 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:23:10 2018) by ROOT version6.04/14
    TCanvas *c_c1lep5jex4bin_postFit = new TCanvas("c_c1lep5jex4bin_postFit", "c_c1lep5jex4bin_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep5jex4bin_postFit()
    h_dummy2__46->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__46->GetXaxis()->SetTitleFont(43);
    h_dummy2__46->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2__46->GetYaxis()->CenterTitle(true);
    h_dummy2__46->GetYaxis()->SetNdivisions(-504);
    h_dummy2__46->GetYaxis()->SetLabelFont(43);
    h_dummy2__46->GetYaxis()->SetLabelOffset(0.02);
@@ -198,6 +199,7 @@ void c1lep5jex4bin_postFit()
    h_dummy2_copy__47->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__47->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__47->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2_copy__47->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__47->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__47->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__47->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep6jin2bex.C

@@ -1,7 +1,7 @@
 void c1lep6jin2bex()
 {
 //=========Macro generated from canvas: c_c1lep6jin2bex/c_c1lep6jin2bex
-//=========  (Thu Jul 19 23:20:15 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:19:21 2018) by ROOT version6.04/14
    TCanvas *c_c1lep6jin2bex = new TCanvas("c_c1lep6jin2bex", "c_c1lep6jin2bex",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep6jin2bex()
    h_dummy2__55->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__55->GetXaxis()->SetTitleFont(43);
    h_dummy2__55->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__55->GetYaxis()->CenterTitle(true);
    h_dummy2__55->GetYaxis()->SetNdivisions(-504);
    h_dummy2__55->GetYaxis()->SetLabelFont(43);
    h_dummy2__55->GetYaxis()->SetLabelOffset(0.02);
@@ -186,6 +187,7 @@ void c1lep6jin2bex()
    h_dummy2_copy__56->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__56->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__56->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__56->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__56->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__56->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__56->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep6jin2bex_postFit.C

@@ -1,7 +1,7 @@
 void c1lep6jin2bex_postFit()
 {
 //=========Macro generated from canvas: c_c1lep6jin2bex_postFit/c_c1lep6jin2bex_postFit
-//=========  (Thu Jul 19 23:32:26 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:23:11 2018) by ROOT version6.04/14
    TCanvas *c_c1lep6jin2bex_postFit = new TCanvas("c_c1lep6jin2bex_postFit", "c_c1lep6jin2bex_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep6jin2bex_postFit()
    h_dummy2__55->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__55->GetXaxis()->SetTitleFont(43);
    h_dummy2__55->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2__55->GetYaxis()->CenterTitle(true);
    h_dummy2__55->GetYaxis()->SetNdivisions(-504);
    h_dummy2__55->GetYaxis()->SetLabelFont(43);
    h_dummy2__55->GetYaxis()->SetLabelOffset(0.02);
@@ -186,6 +187,7 @@ void c1lep6jin2bex_postFit()
    h_dummy2_copy__56->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__56->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__56->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2_copy__56->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__56->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__56->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__56->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep6jin3bex.C

@@ -1,7 +1,7 @@
 void c1lep6jin3bex()
 {
 //=========Macro generated from canvas: c_c1lep6jin3bex/c_c1lep6jin3bex
-//=========  (Thu Jul 19 23:20:15 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:19:21 2018) by ROOT version6.04/14
    TCanvas *c_c1lep6jin3bex = new TCanvas("c_c1lep6jin3bex", "c_c1lep6jin3bex",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep6jin3bex()
    h_dummy2__64->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__64->GetXaxis()->SetTitleFont(43);
    h_dummy2__64->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__64->GetYaxis()->CenterTitle(true);
    h_dummy2__64->GetYaxis()->SetNdivisions(-504);
    h_dummy2__64->GetYaxis()->SetLabelFont(43);
    h_dummy2__64->GetYaxis()->SetLabelOffset(0.02);
@@ -294,6 +295,7 @@ void c1lep6jin3bex()
    h_dummy2_copy__65->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__65->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__65->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__65->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__65->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__65->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__65->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep6jin3bex_postFit.C

@@ -1,7 +1,7 @@
 void c1lep6jin3bex_postFit()
 {
 //=========Macro generated from canvas: c_c1lep6jin3bex_postFit/c_c1lep6jin3bex_postFit
-//=========  (Thu Jul 19 23:32:27 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:23:12 2018) by ROOT version6.04/14
    TCanvas *c_c1lep6jin3bex_postFit = new TCanvas("c_c1lep6jin3bex_postFit", "c_c1lep6jin3bex_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep6jin3bex_postFit()
    h_dummy2__64->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__64->GetXaxis()->SetTitleFont(43);
    h_dummy2__64->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2__64->GetYaxis()->CenterTitle(true);
    h_dummy2__64->GetYaxis()->SetNdivisions(-504);
    h_dummy2__64->GetYaxis()->SetLabelFont(43);
    h_dummy2__64->GetYaxis()->SetLabelOffset(0.02);
@@ -294,6 +295,7 @@ void c1lep6jin3bex_postFit()
    h_dummy2_copy__65->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__65->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__65->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2_copy__65->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__65->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__65->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__65->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep6jin4bin.C

@@ -1,7 +1,7 @@
 void c1lep6jin4bin()
 {
 //=========Macro generated from canvas: c_c1lep6jin4bin/c_c1lep6jin4bin
-//=========  (Thu Jul 19 23:20:15 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:19:21 2018) by ROOT version6.04/14
    TCanvas *c_c1lep6jin4bin = new TCanvas("c_c1lep6jin4bin", "c_c1lep6jin4bin",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep6jin4bin()
    h_dummy2__73->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__73->GetXaxis()->SetTitleFont(43);
    h_dummy2__73->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2__73->GetYaxis()->CenterTitle(true);
    h_dummy2__73->GetYaxis()->SetNdivisions(-504);
    h_dummy2__73->GetYaxis()->SetLabelFont(43);
    h_dummy2__73->GetYaxis()->SetLabelOffset(0.02);
@@ -198,6 +199,7 @@ void c1lep6jin4bin()
    h_dummy2_copy__74->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__74->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__74->GetYaxis()->SetTitle("Data / Bkg");
+   h_dummy2_copy__74->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__74->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__74->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__74->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-20 figures/Hbb/fit/cH_plots/c1lep6jin4bin_postFit.C

@@ -1,7 +1,7 @@
 void c1lep6jin4bin_postFit()
 {
 //=========Macro generated from canvas: c_c1lep6jin4bin_postFit/c_c1lep6jin4bin_postFit
-//=========  (Thu Jul 19 23:32:28 2018) by ROOT version6.04/14
+//=========  (Fri Jul 20 11:23:12 2018) by ROOT version6.04/14
    TCanvas *c_c1lep6jin4bin_postFit = new TCanvas("c_c1lep6jin4bin_postFit", "c_c1lep6jin4bin_postFit",0,0,600,700);
    gStyle->SetOptStat(0);
    gStyle->SetOptTitle(0);
@@ -54,6 +54,7 @@ void c1lep6jin4bin_postFit()
    h_dummy2__73->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2__73->GetXaxis()->SetTitleFont(43);
    h_dummy2__73->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2__73->GetYaxis()->CenterTitle(true);
    h_dummy2__73->GetYaxis()->SetNdivisions(-504);
    h_dummy2__73->GetYaxis()->SetLabelFont(43);
    h_dummy2__73->GetYaxis()->SetLabelOffset(0.02);
@@ -198,6 +199,7 @@ void c1lep6jin4bin_postFit()
    h_dummy2_copy__74->GetXaxis()->SetTitleOffset(5.05);
    h_dummy2_copy__74->GetXaxis()->SetTitleFont(43);
    h_dummy2_copy__74->GetYaxis()->SetTitle("Data / Pred");
+   h_dummy2_copy__74->GetYaxis()->CenterTitle(true);
    h_dummy2_copy__74->GetYaxis()->SetNdivisions(-504);
    h_dummy2_copy__74->GetYaxis()->SetLabelFont(43);
    h_dummy2_copy__74->GetYaxis()->SetLabelOffset(0.02);

### 2018-07-22 sections/signal_background_modeling.tex
v0.3 of paper draft

@@
 the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix element calculation 
-is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to \textsc{Pythia} 8.212~\cite{Sjostrand:2007gs} for parton showering and fragmentation.
-The A14~\cite{ATLASUETune4} set of tuned parameters in \textsc{Pythia} controlling the description of multiparton interactions and  
+is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} for parton showering and fragmentation.
+The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
 initial and final state radiation, referred to as the ``tune'', is used.
@@
 matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, is set to 1.5 times the top quark mass. 
-Parton shower and hadronisation are modelled by {\textsc Pythia}~8.2 with the A14 tune.
+Parton shower and hadronisation are modelled by {\pythia}~8.2 with the A14 tune.
 Alternative $\ttbar$ simulation samples used to derive systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
@@
 
-Samples of $\ttbar V$ and $\ttbar H$ events are generated with {\amcatnlo}~2.3.2, using 
+Samples of $\ttbar V$ and $\ttbar H$ events are generated with {\amcatnlo}~2.~.2, using 
 NLO matrix elements and the NNPDF3.0 NLO~\cite{Ball:2014uwa} PDF set. 
@@
 %The production of four-top-quark events in the SM was simulated by samples generated at LO using {\amcatnlo}~2.2.2
-%and the NNPDF2.3 LO PDF set, interfaced to {\pythia} 8.186 in combination with the A14 tune. 
+%and the NNPDF2.3 LO PDF set, interfaced to {\pythia}~8.186 in combination with the A14 tune. 
 %The sample was normalised to a cross section of 9.2 fb, computed at NLO~\cite{Alwall:2014hca}.
@@
 utilise \textsc{EvtGen}~v1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
-To model the effects of pileup, events from minimum-bias interactions are generated using the \textsc{Pythia}~8.186~\cite{Sjostrand:2007gs} 
+To model the effects of pileup, events from minimum-bias interactions are generated using the {\pythia}~8.186~\cite{Sjostrand:2007gs} 
 event generator and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 

### 2018-07-22 sections/systematic_uncertainties.tex
v0.3 of paper draft

@@
 For the $t$- and $Wt$-channel processes, an uncertainty due to the choice of parton shower and hadronisation model is derived 
-by comparing events produced by {\powheg} interfaced to {\pythia} 6 or {\herwigpp}.
+by comparing events produced by {\powheg} interfaced to {\pythia}~6 or {\herwigpp}.
 These uncertainties are treated as fully correlated among single-top production processes, but uncorrelated with the

### 2018-07-28 ANA-TOPQ-2017-07-PAPER-metadata.tex
Updated metadata.tex in v0.3
some updates
included combo results

@@
 % Comment or remove in final version.
-\AtlasVersion{0.3}
+\AtlasVersion{0.4}
 % Abstract - % directly after { is important for correct indentation
@@
 The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
-yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of 0.XX\% (0.XX\%) and 0.XX\% (0.XX\%) respectively.
-The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.XX (0.XX) and 0.XX (0.XX) respectively. 
+yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
+and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$) respectively.
+The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.064 (0.055) respectively. 
 %Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
@@
 % ATLAS heading - heading at top of title page. Set for TDR etc.
-\AtlasHeading{ATLAS ABC TDR}
+%\AtlasHeading{ATLAS ABC TDR}
+
+% Submission journal and final reference
+\AtlasJournal{JHEP}
+% \AtlasJournal{Phys.\ Lett.\ B.}
+% \AtlasJournalRef{\PLB 789 (2017) 123}
+% \AtlasDOI{}
 

### 2018-07-28 sections/conclusion.tex
Implemented additional CDS comments by Michele Webber
included combo results

@@
 The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well multiple jets. 
-Both searches employ different multivariate techniques to discriminate between the signal and the background on the basis of their kinematic differences. 
+Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
 No significant excess of events above the background expectation is found, and observed (expected) 95\% CL upper limits are derived.
 The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
-yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of 0.XX\% (0.XX\%) and 0.XX\% (0.XX\%) respectively.
-The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.XX (0.XX) and 0.XX (0.XX) respectively. 
+yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
+and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$) respectively.
+The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.064 (0.055) respectively. 
 %Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.

### 2018-08-03 ANA-TOPQ-2017-07-PAPER-metadata.tex
some fixes to text

@@
 A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the 
-Standard Model Higgs boson, is presented. 
+Standard Model Higgs boson, $t\to Hq$, is presented. 
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
@@
 multivariate techniques to separate the signal from the background, which is dominated by $t\bar{t}$ production.
-No significant excess of events above the background expectation is found, and observed (expected) 95\% CL upper limits are derived.
+No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
 The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 

### 2018-08-03 sections/data_presel.tex
some fixes to text

--- 2018-06-30 sections/data_presel.tex
@@
 along with triggers with a 60~\gev\ threshold and no isolation requirement, and with a 120 (140)~\gev\ threshold with looser identification criteria.
-For ditau triggers, the threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
+For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
 In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.
@@
 
-Events selected by the $\Htautau$ search are classified into $\lephad$ and $\hadhad$ channels depending on the 
+In the $\Htautau$ search, events are classified into $\lephad$ and $\hadhad$ channels depending on the 
 multiplicity of selected leptons. Events in the $\lephad$ channel are recorded with a single-electron or single-muon trigger 
@@
 The selected light lepton (electron or muon) is required to match, with $\Delta R < 0.15$, the lepton reconstructed by 
-the trigger and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1--2~\gev. In addition, its electric charge is required to be of
-opposite sign to that of the leading $\tauhad$ candidate.
+the trigger and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
+data taking period). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
 Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
@@
 Tau leptons & -- & $\geq$1 $\tauhad$ & $\geq$2 $\tauhad$ \\
-Electric charge & -- & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
+Electric charge ($q$) & -- & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
 Jets  &  $\geq$4 jets & $\geq$3 jets & $\geq$3 jets \\

### 2018-08-03 sections/introduction.tex
Implemented some CDS comments from Michele Weber
some fixes to text

@@
 See Ref.~\cite{AguilarSaavedra:2004wm} for a review.
-\textbf{Update a bit above paragraph mentioning more recent models.}
+%\textbf{Update a bit above paragraph mentioning more recent models.}
 
@@
 Finally, searches have also been performed considering the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
-of $\BR(H\to b\bar{b})\simeq 58\%$. Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $13~\tev$, 
+of $\BR(H\to b\bar{b})\simeq 58\%$. Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, 
 as well as the larger integrated luminosity.
@@
 signatures with two same-charge light leptons (electrons or muons) or three light leptons resulting from 
-$H \to WW^*$, $H\to \tau\tau$ in which both leptons decay leptonically, or $H \to ZZ^*$~\cite{Aaboud:2018pob}.
+$H \to WW^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically, or $H \to ZZ^*$~\cite{Aaboud:2018pob}.
 These upper limits are derived under the assumption of $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ under the
@@
 which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
-The $\Hbb$ search selects events with one isolated light lepton from the $W \to \ell\nu$ decay, and multiple jets, with several 
-of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
+The $\Hbb$ search selects events with one isolated light lepton from the $W \to \ell\nu$ decay, and multiple jets, several 
+of which are identified with high purity as originating from the hadronisation of $b$-quarks. 
 The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well multiple jets. 

### 2018-08-03 sections/objects.tex
some fixes to text

@@
 Electron (muon) candidates are matched to the primary vertex by requiring that the significance of their transverse impact parameter, $d_0$, 
-satisfies $|d_0/\sigma(d_0)|<5(3)$, where $\sigma(d_0)$ is the measured uncertainty in $d_0$,
+satisfies $|d_0/\sigma(d_0)|<5\,(3)$, where $\sigma(d_0)$ is the measured uncertainty in $d_0$,
 and by requiring that their longitudinal impact parameter, $z_0$, satisfies $|z_0 \sin\theta|<0.5$~mm.
@@
 
-Hadronically decaying $\tau$-lepton candidates ($\tauhad$) are reconstructed from clusters in the calorimeters and
+Hadronically decaying $\tau$-lepton ($\tauhad$) candidates are reconstructed from clusters in the calorimeters and
 associated inner detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
-with a total charge of 1. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
+with a total charge of $\pm 1$. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
 A boosted decision tree (BDT) discriminant using calorimeter- and tracking-based variables is used to identify $\tauhad$ candidates and reject
@@
 
-Overlaps between candidate objects are removed sequentially, following this order: muons, electron, taus (only for the $\Htautau$ search) and jets. 
+Overlaps between candidate objects are removed sequentially, following this order: muons, electrons, $\tauhad$ (only for the $\Htautau$ search), and jets. 
 In the $\Hbb$ search, firstly, electron candidates that lie within $\Delta R = 0.01$ of a muon 

### 2018-08-03 sections/signal_background_modeling.tex
some fixes to text

@@
 production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
-with prompt leptons, i.e. those originating from the decay of a $W$ boson, a $Z$ boson, or a tau lepton,
+with prompt leptons, i.e. those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
 are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
@@
 the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix element calculation 
-is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} for parton showering and fragmentation.
+is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} for the modelling of parton showering, hadronisation, and the underlying event.
 The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
@@
 terms~\cite{Cacciari:2011hy,Baernreuther:2012ws,Czakon:2012zr,Czakon:2012pz,Czakon:2013goa}, 
-and using the MSTW 2008 NNLO~\cite{Martin:2009iq,Martin:2009bu} set of PDFs. 
+and using the MSTW 2008 NNLO~\cite{Martin:2009iq,Martin:2009bu} PDF set. 
 The theoretical uncertainties result from variations of the factorisation and renormalisation scales, as well as from uncertainties in the
@@
 The parton shower, hadronisation and the underlying event are modelled using {\pythia}~6.428 with the CTEQ6L1 PDF set 
-in combination with the P2012 tune.
+in combination with the Perugia 2012 tune~\cite{Skands:2010ak}.
 The single-top-quark samples are normalised to the approximate NNLO theoretical cross 
@@
 Separate samples are generated for different $W/Z$+jets categories using filters for a $b$-jet 
-($W/Z+\geq$1$b$+jets), a $c$-jet and no $b$-jet ($W/Z+\geq$1$c$+jets), and with a veto on $b$- and $c$-jets 
+($W/Z$+$\geq$1$b$+jets), a $c$-jet and no $b$-jet ($W/Z$+$\geq$1$c$+jets), and with a veto on $b$- and $c$-jets 
 ($W/Z$+light-jets), which are combined into the inclusive $W/Z$+jets samples.
@@
 
-Samples of $\ttbar V$ and $\ttbar H$ events are generated with {\amcatnlo}~2.~.2, using 
+Samples of $\ttbar V$ and $\ttbar H$ events are generated with {\amcatnlo}~2.2.1, using 
 NLO matrix elements and the NNPDF3.0 NLO~\cite{Ball:2014uwa} PDF set. 
@@
 All simulated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
-utilise \textsc{EvtGen}~v1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
+utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
 To model the effects of pileup, events from minimum-bias interactions are generated using the {\pythia}~8.186~\cite{Sjostrand:2007gs} 
@@
 prompt leptons and leptons that are either non-prompt or result from the misidentification of photons or jets. 
-Further details can be found in Ref.~\cite{ttbareson13TeV}.
+Further details can be found in Ref.~\cite{Aaboud:2018mjh}.
 
@@
 multijet production, depending on the analysis channel, with $W$+jets production contributing to a lesser extent. 
-Studies based on the simulation show that , for all above processes, fake $\tauhad$ candidates primarily result from the 
+Studies based on the simulation show that, for all above processes, fake $\tauhad$ candidates primarily result from the 
 misidentification of light-quark jets, with the contribution from $b$-quarks and gluon jets playing a subdominant role.
@@
 
-The fake $\tauhad$ background events in a given SR are modeled by the fake template derived from its corresponding CR, which is a data-driven method.
+The fake $\tauhad$ background prediction in a given SR is modelled by the fake template derived from its corresponding CR, which is a data-driven method.
 The fake template is defined as the data subtracted by the contributions from the simulated backgrounds with real $\tauhad$ candidates.
 In the $\lephad$ channel, simulation studies indicate that the fake $\tauhad$ background composition is consistent between the SR and the CR, and dominated by $\ttbar$.
-In this case, the fake template is simply normalised to the fake $\tauhad$ background yield in the SR and taken as the fake $\tauhad$ background.
+In this case, the fake template is simply normalised to the fake $\tauhad$ background yield in the SR and taken as the fake $\tauhad$ background prediction.
 In the $\hadhad$ channel, the fake $\tauhad$ background is expected to be dominated by multijet production.
@@
 Therefore, an appropriate amount of simulated $\ttbar$ events with fake $\tauhad$ candidates in the CR are added to the fake template to match the fake $\tauhad$ background composition in the SR.
-This modified fake template is then normalised to the expected fake $\tauhad$ background yield in the SR, same as in the case of the $\lephad$ channel.
+This modified fake template is then normalised to the expected fake $\tauhad$ background yield in the SR, as sone in the case of the $\lephad$ channel.
 

### 2018-08-03 sections/statistical_analysis.tex
some fixes to text

@@
 background-only hypothesis is estimated by integrating
-the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js,ErratumCowan:2010js}, above the observed value of $q_0$ in the data.
+the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, above the observed value of $q_0$ in the data.
 %The observed $p_0$-value is checked for each explored signal scenario.
@@
 For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
-where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js,ErratumCowan:2010js}, are excluded at $\geq 95\%$ CL.
+where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

### 2018-08-03 sections/strategy_Hbb.tex
some fixes to text

@@
 Regions with exactly two $b$-tagged jets are dominated by $\ttbar$+light jets, while regions with 
-at least four $b$-tagged jets are dominated by $\ttbb$. Intermediate compositions are found in regions with exactly three 
+at least four $b$-tagged jets are dominated by \ttbin. Intermediate compositions are found in regions with exactly three 
 $b$-tagged jets.  Most of the $\ttbar$+light-jets background in the these regions have a charm jet from the hadronic $W$ boson 
@@
 through a likelihood fit to data (see Section~\ref{sec:stat_analysis}).
-A table summarising the observed and expected yields before the fit to data in each of the analysis regions 
-can be found in Appendix~\ref{sec:prepostfit_yields_Hbb_appendix}.
 
@@
 between them. The most prominent features are the different resonances present in the decay (i.e. the Higgs boson in the case 
-of $\Hq$ signal and a hadronically decaying $W$ boson in the case of the $\ttbar \to WbWb$ background), and the different flavour content of the 
+of $\Hq$ signal and a hadronically decaying $W$ boson in the case of the $\ttbar \to WbWb$ background), and the different flavour of the 
 jets forming those resonances. However, the large number of jets in the final state causes ambiguities in the calculation 
@@
 Two background hypotheses are considered, corresponding to the dominant backgrounds in
-the analysis: $\ttbar$+light-jets and $\ttbin$. Thus, $P^\textrm{bkg}$ is computed as the average of
+the analysis: $\ttbar$+light-jets and \ttbin. Thus, $P^\textrm{bkg}$ is computed as the average of
 the pdfs for both hypotheses, weighted by their relative fractions found in simulated $\ttbar$+jets events, which depend
-on the analysis region considered. Furthermore, in a significant fraction of $\Hq$ simulated events (e.g. about 40--50\% in 3b regions), 
+on the analysis region considered. Furthermore, in a significant fraction of $\Hq$ simulated events (e.g. about 40--50\% in regions with exactly three $b$-tagged jets), 
 the light-quark jet from the hadronic top-quark decay is not among the selected jets.
-Similarly, in about 30--40\% (50--90\%) of simulated $\ttbar$+light-jets ($\ttbin$) background events in 3b regions, 
+Similarly, in about 30--40\% (50--90\%) of simulated $\ttbar$+light-jets ($\ttbin$) background events in regions with exactly three $b$-tagged jets, 
 the light-quark jet originating from the $W$ boson decay is also not selected. Thus, the calculation of $P^\textrm{sig}$ and
@@
 Since this analysis has higher expected sensitivity to a $\Hc$ signal than to a $\Hu$ signal and, in order to allow probing 
-of the $\BR(t\to Hu)$ versus $\BR(t\to Hc)$ plane, the discriminant optimised for $\Hc$ is used for both 
+of the $\BR(t\to Hu)$ versus $\BR(t\to Hc)$ plane, the LH discriminant optimised for $\Hc$ is used for both 
 decay modes. It was verified that using the $\Hc$ discriminant for the $\Hu$ search does not result in a significant sensitivity loss.
-Figure~\ref{fig:LHD} compares the shape of the LH distribution between the $\Hc$ and $\Hu$ signals and the 
+Figure~\ref{fig:LHD} compares the shape of the LH discriminant distribution between the $\Hc$ and $\Hu$ signals and the 
 $t\bar{t}\to WbWb$ background in each of the analysis regions considered.

### 2018-08-03 sections/strategy_Htautau.tex
v0.3 of paper draft
some updates
some fixes to text

@@
 decay products in the $\tau$-lepton decay, and including Gaussian constraints on the $\tau$-lepton mass, the Higgs boson mass and the
-measured $\met$. After the minimisation, an improved resolution is obtained on the determination of the Higgs boson four-momentum, and hence
+measured $\met$. After the $\chi^2$ minimisation, an improved resolution is obtained on the determination of the Higgs boson four-momentum, and hence
 its invariant mass, as well as on the four-momentum of the parent top quark. Following the event kinematic reconstruction, several kinematic variables
@@
 \item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically-decaying $W$ boson.
-\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance with the $\tauhad$ candidate.
+\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance with the $\lep$ candidate.
 \item $m_{\tau j}$: the invariant mass of the  $\tauhad$ candidate and the jet that has the smallest angular distance with the $\tauhad$ candidate.
@@
 (whether $\taulep$ or $\tauhad$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
-\item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$-boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark.
+\item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$ boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark.
 This variable is only defined for events with at least four jets.
@@
 Among these variables, the most discriminating ones include $m_{\tau\tau}^{\text{fit}}$, $p_{\text{T},2}$, $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$.
-A comparison between data and background prediction
-for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:BDT_inputs_lephad} and~\ref{fig:BDT_inputs_hadhad}.
+A comparison between data and background prediction for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:BDT_inputs_lephad} and~\ref{fig:BDT_inputs_hadhad}.
 A good description of the data by the background model is observed in all cases.
@@
 \caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of some of the most
-important BDT input variables in the $\lephad$ channel. The distributions are shown for
+important BDT input variables in the $\lephad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
 $m_{\tau\tau}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
 $p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
-The expected $\Hc$ signal (dashed histogram) is shown normalised to $\BR(t\to Hc)=1\%$.
+The small contributions from $\ttbar V$, $\ttbar H$, single top, $Z\to \ell^+\ell^-$ ($\ell = e, \mu$), and diboson backgrounds are combined 
+into a single background source referred to as ``Other''. 
+The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
+added on top of the background prediction.
+The last bin in all figures contains the overflow.
 The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
-The hashed area represents the total uncertainty of the background. \textbf{Improve style.}}
+The hashed area represents the total uncertainty of the background.}
 \label{fig:BDT_inputs_lephad}
@@
 \caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
-important BDT input variables in the $\hadhad$ channel. The distributions are shown for
+important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
 $m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
 (c) $x_{1}^{\text{fit}}$ in the ($\hadhad$, 3j)  region, and (d) $x_{2}^{\text{fit}}$ in the ($\hadhad$, $\geq$4j) region.
-The expected $\Hc$ signal (dashed histogram) is shown normalised to $\BR(t\to Hc)=1\%$.
+The small contributions from $\ttbar V$, $\ttbar H$, single top, $Z\to \ell^+\ell^-$ ($\ell = e, \mu$), and diboson backgrounds are combined 
+into a single background source referred to as ``Other''. 
+The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
+added on top of the background prediction.
+The last bin in all figures contains the overflow.
 The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
-The hashed area represents the total uncertainty of the background. \textbf{Improve style.}} 
+The blue triangles indicate points that are outside the vertical range of the figure. 
+The hashed area represents the total uncertainty of the background. } 
 \label{fig:BDT_inputs_hadhad}

### 2018-08-04 sections/systematic_uncertainties.tex
some text fixes

@@
 The $b$-jet efficiency is measured in a data sample enriched in $\ttbar$ events~\cite{Aaboud:2018xwy}, while the $c$-jet efficiency is measured
-using $\ttbar$ events~\cite{ATLAS-CONF-2018-001} or $W$+$c$-jet events~\cite{Aad:2015ydr}. The light-jet efficiency 
-is measured in a multijet data sample enriched in light-flavour jets~\cite{ATLAS-CONF-2018-006}.
+using $\ttbar$ events~\cite{ATLAS-CONF-2018-001} or $W$+$c$-jet events~\cite{Aad:2015ydr}. 
+The light-jet efficiency is measured in a multijet data sample enriched in light-flavour jets~\cite{ATLAS-CONF-2018-006}.
 Since the $\ttbar$ sample used to measure the $c$-jet tagging efficiency overlaps with the analysis sample, the $\Hbb$ search uses
@@
 detailed treatment of its associated systematic uncertainties is made. In particular, since several analysis 
-regions have a sufficiently large number of events of $\ttbin$ background, its normalisation is 
+regions have a sufficiently large number of events of \ttbin\ background, its normalisation is 
 determined by the data during the fit procedure.
 %, with no prior uncertainty assumed. 
-In the case of the $\ttcin$ normalisation, a normalisation uncertainty of 50\% is assumed, as the fit to the data is unable 
+In the case of the \ttcin\ normalisation, a normalisation uncertainty of 50\% is assumed, as the fit to the data is unable 
 to precisely determine it, and the analysis has very limited sensitivity to this uncertainty.
-Since the diagrams that contribute to $\ttbar$+light-jets, $\ttcin$, $\ttbin$
+Since the diagrams that contribute to $\ttbar$+light-jets, \ttcin, \ttbin\
 production are different, all above uncertainties on $\ttbar$+jets
@@
 considered to be uncorrelated among these processes.
-Additional uncertainties on the $\ttbin$ background are considered associated with the NLO prediction from {\ShOL}, 
+Additional uncertainties on the \ttbin\ background are considered associated with the NLO prediction from {\ShOL}, 
 which is used for reweighting the nominal {\powheg}+{\pythiaeight} prediction. 
@@
 two alternative PDF sets (MSTW and NNPDF). Additional uncertainties are assessed for
-the contributions to the $\ttbin$ background originating from multiple parton interactions.
-Finally, an extra uncertainty on the $\ttbin$ background is assigned by comparing 
+the contributions to the \ttbin\ background originating from multiple parton interactions.
+Finally, an extra uncertainty on the \ttbin\ background is assigned by comparing 
 the predictions from {\powheg}+{\pythiaeight} and {\ShOL} 4F (5F vs 4F).
@@
 The total normalisation uncertainty of $V$+jets processes is estimated by comparing the data and total background prediction in 
-the different analysis regions considered, but requiring exactly 0 $b$-tagged jets. Agreement between data and predicted background 
+the different analysis regions considered, but requiring exactly zero $b$-tagged jets. Agreement between data and predicted background 
 in these modified regions, which are dominated by $V$+light-jets, is found to be within approximately 30\%. This bound is taken to 
@@
 This uncertainty, associated with the modelling of the fake $\tauhad$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\tauhad$ candidate.
+In addition, a systematic uncertainty is assigned to account for the different fractional composition of particles (various types of leptons and partons) originating the fake $\tauhad$ candidates 
+between each SR and its corresponding CR in the $\ttbar$ simulation. 
 Finally, the normalisation of the fake $\tauhad$ background in each SR is determined by the data during the fit procedure, and thus so is its uncertainty. 
-In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template.
+%In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template.
 The MC studies shows that non-H-to-tautau signal with fake taus can contribute to the $\lephad$ channel.
@@
 These modelling uncertainties are taken to be uncorrelated with those affecting the $\ttbar \to WbWb$ background.
+Finally, a 30\% uncertainty is assigned to the signal events with fake $\tauhad$ candidates selected by the $\Htautau$ search.

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex2bex.C
cleaning

@@ -1,685 +1,0 @@
-void c1lep4jex2bex()
-{
-//=========Macro generated from canvas: c_c1lep4jex2bex/c_c1lep4jex2bex
-//=========  (Thu Jul 19 17:38:01 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex2bex = new TCanvas("c_c1lep4jex2bex", "c_c1lep4jex2bex",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex2bex->SetHighLightColor(2);
-   c_c1lep4jex2bex->Range(0,0,1,1);
-   c_c1lep4jex2bex->SetFillColor(0);
-   c_c1lep4jex2bex->SetBorderMode(0);
-   c_c1lep4jex2bex->SetBorderSize(2);
-   c_c1lep4jex2bex->SetTickx(1);
-   c_c1lep4jex2bex->SetTicky(1);
-   c_c1lep4jex2bex->SetLeftMargin(0.16);
-   c_c1lep4jex2bex->SetRightMargin(0.05);
-   c_c1lep4jex2bex->SetTopMargin(0.05);
-   c_c1lep4jex2bex->SetBottomMargin(0.16);
-   c_c1lep4jex2bex->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0.5308642,-0.0873016,1.024691,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis1[2] = {0.6, 1}; 
-   
-   TH1D *h_dummy2__1 = new TH1D("h_dummy2__1","Data/MC",1, xAxis1);
-   h_dummy2__1->SetMinimum(0.5);
-   h_dummy2__1->SetMaximum(1.5);
-   h_dummy2__1->SetEntries(5042418);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex3bex.C

@@ -1,981 +1,0 @@
-void c1lep4jex3bex()
-{
-//=========Macro generated from canvas: c_c1lep4jex3bex/c_c1lep4jex3bex
-//=========  (Thu Jul 19 17:38:02 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex3bex = new TCanvas("c_c1lep4jex3bex", "c_c1lep4jex3bex",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex3bex->SetHighLightColor(2);
-   c_c1lep4jex3bex->Range(0,0,1,1);
-   c_c1lep4jex3bex->SetFillColor(0);
-   c_c1lep4jex3bex->SetBorderMode(0);
-   c_c1lep4jex3bex->SetBorderSize(2);
-   c_c1lep4jex3bex->SetTickx(1);
-   c_c1lep4jex3bex->SetTicky(1);
-   c_c1lep4jex3bex->SetLeftMargin(0.16);
-   c_c1lep4jex3bex->SetRightMargin(0.05);
-   c_c1lep4jex3bex->SetTopMargin(0.05);
-   c_c1lep4jex3bex->SetBottomMargin(0.16);
-   c_c1lep4jex3bex->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-0.1728395,-0.0873016,1.061728,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis11[11] = {0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1}; 
-   
-   TH1D *h_dummy2__10 = new TH1D("h_dummy2__10","Data/MC",10, xAxis11);
-   h_dummy2__10->SetMinimum(0.5);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex3bex_bjets_n.C

@@ -1,744 +1,0 @@
-void c1lep4jex3bex_bjets_n()
-{
-//=========Macro generated from canvas: c_c1lep4jex3bex_bjets_n/c_c1lep4jex3bex_bjets_n
-//=========  (Thu Jul 19 16:48:44 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex3bex_bjets_n = new TCanvas("c_c1lep4jex3bex_bjets_n", "c_c1lep4jex3bex_bjets_n",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex3bex_bjets_n->SetHighLightColor(2);
-   c_c1lep4jex3bex_bjets_n->Range(0,0,1,1);
-   c_c1lep4jex3bex_bjets_n->SetFillColor(0);
-   c_c1lep4jex3bex_bjets_n->SetBorderMode(0);
-   c_c1lep4jex3bex_bjets_n->SetBorderSize(2);
-   c_c1lep4jex3bex_bjets_n->SetTickx(1);
-   c_c1lep4jex3bex_bjets_n->SetTicky(1);
-   c_c1lep4jex3bex_bjets_n->SetLeftMargin(0.16);
-   c_c1lep4jex3bex_bjets_n->SetRightMargin(0.05);
-   c_c1lep4jex3bex_bjets_n->SetTopMargin(0.05);
-   c_c1lep4jex3bex_bjets_n->SetBottomMargin(0.16);
-   c_c1lep4jex3bex_bjets_n->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0.9814815,-0.0873016,4.685185,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex3bex_hthad.C

@@ -1,894 +1,0 @@
-void c1lep4jex3bex_hthad()
-{
-//=========Macro generated from canvas: c_c1lep4jex3bex_hthad/c_c1lep4jex3bex_hthad
-//=========  (Thu Jul 19 17:38:04 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex3bex_hthad = new TCanvas("c_c1lep4jex3bex_hthad", "c_c1lep4jex3bex_hthad",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex3bex_hthad->SetHighLightColor(2);
-   c_c1lep4jex3bex_hthad->Range(0,0,1,1);
-   c_c1lep4jex3bex_hthad->SetFillColor(0);
-   c_c1lep4jex3bex_hthad->SetBorderMode(0);
-   c_c1lep4jex3bex_hthad->SetBorderSize(2);
-   c_c1lep4jex3bex_hthad->SetTickx(1);
-   c_c1lep4jex3bex_hthad->SetTicky(1);
-   c_c1lep4jex3bex_hthad->SetLeftMargin(0.16);
-   c_c1lep4jex3bex_hthad->SetRightMargin(0.05);
-   c_c1lep4jex3bex_hthad->SetTopMargin(0.05);
-   c_c1lep4jex3bex_hthad->SetBottomMargin(0.16);
-   c_c1lep4jex3bex_hthad->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-20.98765,-0.0873016,843.2099,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis141[8] = {100, 200, 300, 400, 500, 600, 700, 800}; 
-   
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex3bex_jets_n.C

@@ -1,776 +1,0 @@
-void c1lep4jex3bex_jets_n()
-{
-//=========Macro generated from canvas: c_c1lep4jex3bex_jets_n/c_c1lep4jex3bex_jets_n
-//=========  (Thu Jul 19 16:48:43 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex3bex_jets_n = new TCanvas("c_c1lep4jex3bex_jets_n", "c_c1lep4jex3bex_jets_n",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex3bex_jets_n->SetHighLightColor(2);
-   c_c1lep4jex3bex_jets_n->Range(0,0,1,1);
-   c_c1lep4jex3bex_jets_n->SetFillColor(0);
-   c_c1lep4jex3bex_jets_n->SetBorderMode(0);
-   c_c1lep4jex3bex_jets_n->SetBorderSize(2);
-   c_c1lep4jex3bex_jets_n->SetTickx(1);
-   c_c1lep4jex3bex_jets_n->SetTicky(1);
-   c_c1lep4jex3bex_jets_n->SetLeftMargin(0.16);
-   c_c1lep4jex3bex_jets_n->SetRightMargin(0.05);
-   c_c1lep4jex3bex_jets_n->SetTopMargin(0.05);
-   c_c1lep4jex3bex_jets_n->SetBottomMargin(0.16);
-   c_c1lep4jex3bex_jets_n->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(2.808642,-0.0873016,7.746914,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis381[5] = {3.5, 4.5, 5.5, 6.5, 7.5}; 
-   
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex3bex_jets_pt.C

@@ -1,860 +1,0 @@
-void c1lep4jex3bex_jets_pt()
-{
-//=========Macro generated from canvas: c_c1lep4jex3bex_jets_pt/c_c1lep4jex3bex_jets_pt
-//=========  (Thu Jul 19 17:38:06 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex3bex_jets_pt = new TCanvas("c_c1lep4jex3bex_jets_pt", "c_c1lep4jex3bex_jets_pt",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex3bex_jets_pt->SetHighLightColor(2);
-   c_c1lep4jex3bex_jets_pt->Range(0,0,1,1);
-   c_c1lep4jex3bex_jets_pt->SetFillColor(0);
-   c_c1lep4jex3bex_jets_pt->SetBorderMode(0);
-   c_c1lep4jex3bex_jets_pt->SetBorderSize(2);
-   c_c1lep4jex3bex_jets_pt->SetTickx(1);
-   c_c1lep4jex3bex_jets_pt->SetTicky(1);
-   c_c1lep4jex3bex_jets_pt->SetLeftMargin(0.16);
-   c_c1lep4jex3bex_jets_pt->SetRightMargin(0.05);
-   c_c1lep4jex3bex_jets_pt->SetTopMargin(0.05);
-   c_c1lep4jex3bex_jets_pt->SetBottomMargin(0.16);
-   c_c1lep4jex3bex_jets_pt->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-26.85185,-0.0873016,343.5185,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex3bex_lep0_eta.C

@@ -1,996 +1,0 @@
-void c1lep4jex3bex_lep0_eta()
-{
-//=========Macro generated from canvas: c_c1lep4jex3bex_lep0_eta/c_c1lep4jex3bex_lep0_eta
-//=========  (Thu Jul 19 17:38:06 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex3bex_lep0_eta = new TCanvas("c_c1lep4jex3bex_lep0_eta", "c_c1lep4jex3bex_lep0_eta",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex3bex_lep0_eta->SetHighLightColor(2);
-   c_c1lep4jex3bex_lep0_eta->Range(0,0,1,1);
-   c_c1lep4jex3bex_lep0_eta->SetFillColor(0);
-   c_c1lep4jex3bex_lep0_eta->SetBorderMode(0);
-   c_c1lep4jex3bex_lep0_eta->SetBorderSize(2);
-   c_c1lep4jex3bex_lep0_eta->SetTickx(1);
-   c_c1lep4jex3bex_lep0_eta->SetTicky(1);
-   c_c1lep4jex3bex_lep0_eta->SetLeftMargin(0.16);
-   c_c1lep4jex3bex_lep0_eta->SetRightMargin(0.05);
-   c_c1lep4jex3bex_lep0_eta->SetTopMargin(0.05);
-   c_c1lep4jex3bex_lep0_eta->SetBottomMargin(0.16);
-   c_c1lep4jex3bex_lep0_eta->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-3.364198,-0.0873016,2.808642,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex3bex_lep0_pt.C

@@ -1,792 +1,0 @@
-void c1lep4jex3bex_lep0_pt()
-{
-//=========Macro generated from canvas: c_c1lep4jex3bex_lep0_pt/c_c1lep4jex3bex_lep0_pt
-//=========  (Thu Jul 19 17:38:07 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex3bex_lep0_pt = new TCanvas("c_c1lep4jex3bex_lep0_pt", "c_c1lep4jex3bex_lep0_pt",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex3bex_lep0_pt->SetHighLightColor(2);
-   c_c1lep4jex3bex_lep0_pt->Range(0,0,1,1);
-   c_c1lep4jex3bex_lep0_pt->SetFillColor(0);
-   c_c1lep4jex3bex_lep0_pt->SetBorderMode(0);
-   c_c1lep4jex3bex_lep0_pt->SetBorderSize(2);
-   c_c1lep4jex3bex_lep0_pt->SetTickx(1);
-   c_c1lep4jex3bex_lep0_pt->SetTicky(1);
-   c_c1lep4jex3bex_lep0_pt->SetLeftMargin(0.16);
-   c_c1lep4jex3bex_lep0_pt->SetRightMargin(0.05);
-   c_c1lep4jex3bex_lep0_pt->SetTopMargin(0.05);
-   c_c1lep4jex3bex_lep0_pt->SetBottomMargin(0.16);
-   c_c1lep4jex3bex_lep0_pt->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-9.567901,-0.0873016,237.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex3bex_mbb_leading_bjets.C

@@ -1,972 +1,0 @@
-void c1lep4jex3bex_mbb_leading_bjets()
-{
-//=========Macro generated from canvas: c_c1lep4jex3bex_mbb_leading_bjets/c_c1lep4jex3bex_mbb_leading_bjets
-//=========  (Thu Jul 19 17:38:08 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex3bex_mbb_leading_bjets = new TCanvas("c_c1lep4jex3bex_mbb_leading_bjets", "c_c1lep4jex3bex_mbb_leading_bjets",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex3bex_mbb_leading_bjets->SetHighLightColor(2);
-   c_c1lep4jex3bex_mbb_leading_bjets->Range(0,0,1,1);
-   c_c1lep4jex3bex_mbb_leading_bjets->SetFillColor(0);
-   c_c1lep4jex3bex_mbb_leading_bjets->SetBorderMode(0);
-   c_c1lep4jex3bex_mbb_leading_bjets->SetBorderSize(2);
-   c_c1lep4jex3bex_mbb_leading_bjets->SetTickx(1);
-   c_c1lep4jex3bex_mbb_leading_bjets->SetTicky(1);
-   c_c1lep4jex3bex_mbb_leading_bjets->SetLeftMargin(0.16);
-   c_c1lep4jex3bex_mbb_leading_bjets->SetRightMargin(0.05);
-   c_c1lep4jex3bex_mbb_leading_bjets->SetTopMargin(0.05);
-   c_c1lep4jex3bex_mbb_leading_bjets->SetBottomMargin(0.16);
-   c_c1lep4jex3bex_mbb_leading_bjets->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-27.77778,-0.0873016,527.7778,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex3bex_mbb_mindR.C

@@ -1,938 +1,0 @@
-void c1lep4jex3bex_mbb_mindR()
-{
-//=========Macro generated from canvas: c_c1lep4jex3bex_mbb_mindR/c_c1lep4jex3bex_mbb_mindR
-//=========  (Thu Jul 19 17:38:09 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex3bex_mbb_mindR = new TCanvas("c_c1lep4jex3bex_mbb_mindR", "c_c1lep4jex3bex_mbb_mindR",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex3bex_mbb_mindR->SetHighLightColor(2);
-   c_c1lep4jex3bex_mbb_mindR->Range(0,0,1,1);
-   c_c1lep4jex3bex_mbb_mindR->SetFillColor(0);
-   c_c1lep4jex3bex_mbb_mindR->SetBorderMode(0);
-   c_c1lep4jex3bex_mbb_mindR->SetBorderSize(2);
-   c_c1lep4jex3bex_mbb_mindR->SetTickx(1);
-   c_c1lep4jex3bex_mbb_mindR->SetTicky(1);
-   c_c1lep4jex3bex_mbb_mindR->SetLeftMargin(0.16);
-   c_c1lep4jex3bex_mbb_mindR->SetRightMargin(0.05);
-   c_c1lep4jex3bex_mbb_mindR->SetTopMargin(0.05);
-   c_c1lep4jex3bex_mbb_mindR->SetBottomMargin(0.16);
-   c_c1lep4jex3bex_mbb_mindR->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(15.4321,-0.0873016,262.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex3bex_meff.C

@@ -1,894 +1,0 @@
-void c1lep4jex3bex_meff()
-{
-//=========Macro generated from canvas: c_c1lep4jex3bex_meff/c_c1lep4jex3bex_meff
-//=========  (Thu Jul 19 17:38:03 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex3bex_meff = new TCanvas("c_c1lep4jex3bex_meff", "c_c1lep4jex3bex_meff",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex3bex_meff->SetHighLightColor(2);
-   c_c1lep4jex3bex_meff->Range(0,0,1,1);
-   c_c1lep4jex3bex_meff->SetFillColor(0);
-   c_c1lep4jex3bex_meff->SetBorderMode(0);
-   c_c1lep4jex3bex_meff->SetBorderSize(2);
-   c_c1lep4jex3bex_meff->SetTickx(1);
-   c_c1lep4jex3bex_meff->SetTicky(1);
-   c_c1lep4jex3bex_meff->SetLeftMargin(0.16);
-   c_c1lep4jex3bex_meff->SetRightMargin(0.05);
-   c_c1lep4jex3bex_meff->SetTopMargin(0.05);
-   c_c1lep4jex3bex_meff->SetBottomMargin(0.16);
-   c_c1lep4jex3bex_meff->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(4.012346,-0.0873016,868.2099,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis101[8] = {125, 225, 325, 425, 525, 625, 725, 825}; 
-   
-   TH1D *h_dummy2__91 = new TH1D("h_dummy2__91","Data/MC",7, xAxis101);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex3bex_met.C

@@ -1,792 +1,0 @@
-void c1lep4jex3bex_met()
-{
-//=========Macro generated from canvas: c_c1lep4jex3bex_met/c_c1lep4jex3bex_met
-//=========  (Thu Jul 19 17:38:05 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex3bex_met = new TCanvas("c_c1lep4jex3bex_met", "c_c1lep4jex3bex_met",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex3bex_met->SetHighLightColor(2);
-   c_c1lep4jex3bex_met->Range(0,0,1,1);
-   c_c1lep4jex3bex_met->SetFillColor(0);
-   c_c1lep4jex3bex_met->SetBorderMode(0);
-   c_c1lep4jex3bex_met->SetBorderSize(2);
-   c_c1lep4jex3bex_met->SetTickx(1);
-   c_c1lep4jex3bex_met->SetTicky(1);
-   c_c1lep4jex3bex_met->SetLeftMargin(0.16);
-   c_c1lep4jex3bex_met->SetRightMargin(0.05);
-   c_c1lep4jex3bex_met->SetTopMargin(0.05);
-   c_c1lep4jex3bex_met->SetBottomMargin(0.16);
-   c_c1lep4jex3bex_met->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-34.5679,-0.0873016,212.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis181[5] = {0, 50, 100, 150, 200}; 
-   
-   TH1D *h_dummy2__163 = new TH1D("h_dummy2__163","Data/MC",4, xAxis181);
-   h_dummy2__163->SetMinimum(0.5);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex3bex_mtw.C

@@ -1,792 +1,0 @@
-void c1lep4jex3bex_mtw()
-{
-//=========Macro generated from canvas: c_c1lep4jex3bex_mtw/c_c1lep4jex3bex_mtw
-//=========  (Thu Jul 19 17:38:05 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex3bex_mtw = new TCanvas("c_c1lep4jex3bex_mtw", "c_c1lep4jex3bex_mtw",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex3bex_mtw->SetHighLightColor(2);
-   c_c1lep4jex3bex_mtw->Range(0,0,1,1);
-   c_c1lep4jex3bex_mtw->SetFillColor(0);
-   c_c1lep4jex3bex_mtw->SetBorderMode(0);
-   c_c1lep4jex3bex_mtw->SetBorderSize(2);
-   c_c1lep4jex3bex_mtw->SetTickx(1);
-   c_c1lep4jex3bex_mtw->SetTicky(1);
-   c_c1lep4jex3bex_mtw->SetLeftMargin(0.16);
-   c_c1lep4jex3bex_mtw->SetRightMargin(0.05);
-   c_c1lep4jex3bex_mtw->SetTopMargin(0.05);
-   c_c1lep4jex3bex_mtw->SetBottomMargin(0.16);
-   c_c1lep4jex3bex_mtw->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-34.5679,-0.0873016,212.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis221[5] = {0, 50, 100, 150, 200}; 
-   
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jex4bin.C

@@ -1,709 +1,0 @@
-void c1lep4jex4bin()
-{
-//=========Macro generated from canvas: c_c1lep4jex4bin/c_c1lep4jex4bin
-//=========  (Thu Jul 19 17:38:02 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex4bin = new TCanvas("c_c1lep4jex4bin", "c_c1lep4jex4bin",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex4bin->SetHighLightColor(2);
-   c_c1lep4jex4bin->Range(0,0,1,1);
-   c_c1lep4jex4bin->SetFillColor(0);
-   c_c1lep4jex4bin->SetBorderMode(0);
-   c_c1lep4jex4bin->SetBorderSize(2);
-   c_c1lep4jex4bin->SetTickx(1);
-   c_c1lep4jex4bin->SetTicky(1);
-   c_c1lep4jex4bin->SetLeftMargin(0.16);
-   c_c1lep4jex4bin->SetRightMargin(0.05);
-   c_c1lep4jex4bin->SetTopMargin(0.05);
-   c_c1lep4jex4bin->SetBottomMargin(0.16);
-   c_c1lep4jex4bin->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-0.1728395,-0.0873016,1.061728,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis21[3] = {0, 0.5, 1}; 
-   
-   TH1D *h_dummy2__19 = new TH1D("h_dummy2__19","Data/MC",2, xAxis21);
-   h_dummy2__19->SetMinimum(0.5);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jin2bin_bjets_n.C

@@ -1,756 +1,0 @@
-void c1lep4jin2bin_bjets_n()
-{
-//=========Macro generated from canvas: c_c1lep4jin2bin_bjets_n/c_c1lep4jin2bin_bjets_n
-//=========  (Thu Jul 19 17:38:08 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jin2bin_bjets_n = new TCanvas("c_c1lep4jin2bin_bjets_n", "c_c1lep4jin2bin_bjets_n",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jin2bin_bjets_n->SetHighLightColor(2);
-   c_c1lep4jin2bin_bjets_n->Range(0,0,1,1);
-   c_c1lep4jin2bin_bjets_n->SetFillColor(0);
-   c_c1lep4jin2bin_bjets_n->SetBorderMode(0);
-   c_c1lep4jin2bin_bjets_n->SetBorderSize(2);
-   c_c1lep4jin2bin_bjets_n->SetTickx(1);
-   c_c1lep4jin2bin_bjets_n->SetTicky(1);
-   c_c1lep4jin2bin_bjets_n->SetLeftMargin(0.16);
-   c_c1lep4jin2bin_bjets_n->SetRightMargin(0.05);
-   c_c1lep4jin2bin_bjets_n->SetTopMargin(0.05);
-   c_c1lep4jin2bin_bjets_n->SetBottomMargin(0.16);
-   c_c1lep4jin2bin_bjets_n->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0.9814815,-0.0873016,4.685185,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jin2bin_hthad.C

@@ -1,894 +1,0 @@
-void c1lep4jin2bin_hthad()
-{
-//=========Macro generated from canvas: c_c1lep4jin2bin_hthad/c_c1lep4jin2bin_hthad
-//=========  (Thu Jul 19 17:38:04 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jin2bin_hthad = new TCanvas("c_c1lep4jin2bin_hthad", "c_c1lep4jin2bin_hthad",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jin2bin_hthad->SetHighLightColor(2);
-   c_c1lep4jin2bin_hthad->Range(0,0,1,1);
-   c_c1lep4jin2bin_hthad->SetFillColor(0);
-   c_c1lep4jin2bin_hthad->SetBorderMode(0);
-   c_c1lep4jin2bin_hthad->SetBorderSize(2);
-   c_c1lep4jin2bin_hthad->SetTickx(1);
-   c_c1lep4jin2bin_hthad->SetTicky(1);
-   c_c1lep4jin2bin_hthad->SetLeftMargin(0.16);
-   c_c1lep4jin2bin_hthad->SetRightMargin(0.05);
-   c_c1lep4jin2bin_hthad->SetTopMargin(0.05);
-   c_c1lep4jin2bin_hthad->SetBottomMargin(0.16);
-   c_c1lep4jin2bin_hthad->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-20.98765,-0.0873016,843.2099,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis131[8] = {100, 200, 300, 400, 500, 600, 700, 800}; 
-   
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jin2bin_jets_n.C

@@ -1,792 +1,0 @@
-void c1lep4jin2bin_jets_n()
-{
-//=========Macro generated from canvas: c_c1lep4jin2bin_jets_n/c_c1lep4jin2bin_jets_n
-//=========  (Thu Jul 19 17:38:08 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jin2bin_jets_n = new TCanvas("c_c1lep4jin2bin_jets_n", "c_c1lep4jin2bin_jets_n",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jin2bin_jets_n->SetHighLightColor(2);
-   c_c1lep4jin2bin_jets_n->Range(0,0,1,1);
-   c_c1lep4jin2bin_jets_n->SetFillColor(0);
-   c_c1lep4jin2bin_jets_n->SetBorderMode(0);
-   c_c1lep4jin2bin_jets_n->SetBorderSize(2);
-   c_c1lep4jin2bin_jets_n->SetTickx(1);
-   c_c1lep4jin2bin_jets_n->SetTicky(1);
-   c_c1lep4jin2bin_jets_n->SetLeftMargin(0.16);
-   c_c1lep4jin2bin_jets_n->SetRightMargin(0.05);
-   c_c1lep4jin2bin_jets_n->SetTopMargin(0.05);
-   c_c1lep4jin2bin_jets_n->SetBottomMargin(0.16);
-   c_c1lep4jin2bin_jets_n->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(2.808642,-0.0873016,7.746914,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis371[5] = {3.5, 4.5, 5.5, 6.5, 7.5}; 
-   
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jin2bin_jets_pt.C

@@ -1,860 +1,0 @@
-void c1lep4jin2bin_jets_pt()
-{
-//=========Macro generated from canvas: c_c1lep4jin2bin_jets_pt/c_c1lep4jin2bin_jets_pt
-//=========  (Thu Jul 19 17:38:06 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jin2bin_jets_pt = new TCanvas("c_c1lep4jin2bin_jets_pt", "c_c1lep4jin2bin_jets_pt",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jin2bin_jets_pt->SetHighLightColor(2);
-   c_c1lep4jin2bin_jets_pt->Range(0,0,1,1);
-   c_c1lep4jin2bin_jets_pt->SetFillColor(0);
-   c_c1lep4jin2bin_jets_pt->SetBorderMode(0);
-   c_c1lep4jin2bin_jets_pt->SetBorderSize(2);
-   c_c1lep4jin2bin_jets_pt->SetTickx(1);
-   c_c1lep4jin2bin_jets_pt->SetTicky(1);
-   c_c1lep4jin2bin_jets_pt->SetLeftMargin(0.16);
-   c_c1lep4jin2bin_jets_pt->SetRightMargin(0.05);
-   c_c1lep4jin2bin_jets_pt->SetTopMargin(0.05);
-   c_c1lep4jin2bin_jets_pt->SetBottomMargin(0.16);
-   c_c1lep4jin2bin_jets_pt->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-26.85185,-0.0873016,343.5185,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jin2bin_lep0_eta.C

@@ -1,996 +1,0 @@
-void c1lep4jin2bin_lep0_eta()
-{
-//=========Macro generated from canvas: c_c1lep4jin2bin_lep0_eta/c_c1lep4jin2bin_lep0_eta
-//=========  (Thu Jul 19 17:38:06 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jin2bin_lep0_eta = new TCanvas("c_c1lep4jin2bin_lep0_eta", "c_c1lep4jin2bin_lep0_eta",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jin2bin_lep0_eta->SetHighLightColor(2);
-   c_c1lep4jin2bin_lep0_eta->Range(0,0,1,1);
-   c_c1lep4jin2bin_lep0_eta->SetFillColor(0);
-   c_c1lep4jin2bin_lep0_eta->SetBorderMode(0);
-   c_c1lep4jin2bin_lep0_eta->SetBorderSize(2);
-   c_c1lep4jin2bin_lep0_eta->SetTickx(1);
-   c_c1lep4jin2bin_lep0_eta->SetTicky(1);
-   c_c1lep4jin2bin_lep0_eta->SetLeftMargin(0.16);
-   c_c1lep4jin2bin_lep0_eta->SetRightMargin(0.05);
-   c_c1lep4jin2bin_lep0_eta->SetTopMargin(0.05);
-   c_c1lep4jin2bin_lep0_eta->SetBottomMargin(0.16);
-   c_c1lep4jin2bin_lep0_eta->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-3.364198,-0.0873016,2.808642,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jin2bin_lep0_pt.C

@@ -1,792 +1,0 @@
-void c1lep4jin2bin_lep0_pt()
-{
-//=========Macro generated from canvas: c_c1lep4jin2bin_lep0_pt/c_c1lep4jin2bin_lep0_pt
-//=========  (Thu Jul 19 17:38:07 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jin2bin_lep0_pt = new TCanvas("c_c1lep4jin2bin_lep0_pt", "c_c1lep4jin2bin_lep0_pt",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jin2bin_lep0_pt->SetHighLightColor(2);
-   c_c1lep4jin2bin_lep0_pt->Range(0,0,1,1);
-   c_c1lep4jin2bin_lep0_pt->SetFillColor(0);
-   c_c1lep4jin2bin_lep0_pt->SetBorderMode(0);
-   c_c1lep4jin2bin_lep0_pt->SetBorderSize(2);
-   c_c1lep4jin2bin_lep0_pt->SetTickx(1);
-   c_c1lep4jin2bin_lep0_pt->SetTicky(1);
-   c_c1lep4jin2bin_lep0_pt->SetLeftMargin(0.16);
-   c_c1lep4jin2bin_lep0_pt->SetRightMargin(0.05);
-   c_c1lep4jin2bin_lep0_pt->SetTopMargin(0.05);
-   c_c1lep4jin2bin_lep0_pt->SetBottomMargin(0.16);
-   c_c1lep4jin2bin_lep0_pt->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-9.567901,-0.0873016,237.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jin2bin_mbb_leading_bjets.C

@@ -1,972 +1,0 @@
-void c1lep4jin2bin_mbb_leading_bjets()
-{
-//=========Macro generated from canvas: c_c1lep4jin2bin_mbb_leading_bjets/c_c1lep4jin2bin_mbb_leading_bjets
-//=========  (Thu Jul 19 17:38:08 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jin2bin_mbb_leading_bjets = new TCanvas("c_c1lep4jin2bin_mbb_leading_bjets", "c_c1lep4jin2bin_mbb_leading_bjets",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jin2bin_mbb_leading_bjets->SetHighLightColor(2);
-   c_c1lep4jin2bin_mbb_leading_bjets->Range(0,0,1,1);
-   c_c1lep4jin2bin_mbb_leading_bjets->SetFillColor(0);
-   c_c1lep4jin2bin_mbb_leading_bjets->SetBorderMode(0);
-   c_c1lep4jin2bin_mbb_leading_bjets->SetBorderSize(2);
-   c_c1lep4jin2bin_mbb_leading_bjets->SetTickx(1);
-   c_c1lep4jin2bin_mbb_leading_bjets->SetTicky(1);
-   c_c1lep4jin2bin_mbb_leading_bjets->SetLeftMargin(0.16);
-   c_c1lep4jin2bin_mbb_leading_bjets->SetRightMargin(0.05);
-   c_c1lep4jin2bin_mbb_leading_bjets->SetTopMargin(0.05);
-   c_c1lep4jin2bin_mbb_leading_bjets->SetBottomMargin(0.16);
-   c_c1lep4jin2bin_mbb_leading_bjets->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-27.77778,-0.0873016,527.7778,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jin2bin_mbb_mindR.C

@@ -1,938 +1,0 @@
-void c1lep4jin2bin_mbb_mindR()
-{
-//=========Macro generated from canvas: c_c1lep4jin2bin_mbb_mindR/c_c1lep4jin2bin_mbb_mindR
-//=========  (Thu Jul 19 17:38:09 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jin2bin_mbb_mindR = new TCanvas("c_c1lep4jin2bin_mbb_mindR", "c_c1lep4jin2bin_mbb_mindR",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jin2bin_mbb_mindR->SetHighLightColor(2);
-   c_c1lep4jin2bin_mbb_mindR->Range(0,0,1,1);
-   c_c1lep4jin2bin_mbb_mindR->SetFillColor(0);
-   c_c1lep4jin2bin_mbb_mindR->SetBorderMode(0);
-   c_c1lep4jin2bin_mbb_mindR->SetBorderSize(2);
-   c_c1lep4jin2bin_mbb_mindR->SetTickx(1);
-   c_c1lep4jin2bin_mbb_mindR->SetTicky(1);
-   c_c1lep4jin2bin_mbb_mindR->SetLeftMargin(0.16);
-   c_c1lep4jin2bin_mbb_mindR->SetRightMargin(0.05);
-   c_c1lep4jin2bin_mbb_mindR->SetTopMargin(0.05);
-   c_c1lep4jin2bin_mbb_mindR->SetBottomMargin(0.16);
-   c_c1lep4jin2bin_mbb_mindR->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(15.4321,-0.0873016,262.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jin2bin_meff.C

@@ -1,894 +1,0 @@
-void c1lep4jin2bin_meff()
-{
-//=========Macro generated from canvas: c_c1lep4jin2bin_meff/c_c1lep4jin2bin_meff
-//=========  (Thu Jul 19 17:38:03 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jin2bin_meff = new TCanvas("c_c1lep4jin2bin_meff", "c_c1lep4jin2bin_meff",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jin2bin_meff->SetHighLightColor(2);
-   c_c1lep4jin2bin_meff->Range(0,0,1,1);
-   c_c1lep4jin2bin_meff->SetFillColor(0);
-   c_c1lep4jin2bin_meff->SetBorderMode(0);
-   c_c1lep4jin2bin_meff->SetBorderSize(2);
-   c_c1lep4jin2bin_meff->SetTickx(1);
-   c_c1lep4jin2bin_meff->SetTicky(1);
-   c_c1lep4jin2bin_meff->SetLeftMargin(0.16);
-   c_c1lep4jin2bin_meff->SetRightMargin(0.05);
-   c_c1lep4jin2bin_meff->SetTopMargin(0.05);
-   c_c1lep4jin2bin_meff->SetBottomMargin(0.16);
-   c_c1lep4jin2bin_meff->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(4.012346,-0.0873016,868.2099,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis91[8] = {125, 225, 325, 425, 525, 625, 725, 825}; 
-   
-   TH1D *h_dummy2__82 = new TH1D("h_dummy2__82","Data/MC",7, xAxis91);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep4jin2bin_met.C

@@ -1,792 +1,0 @@
-void c1lep4jin2bin_met()
-{
-//=========Macro generated from canvas: c_c1lep4jin2bin_met/c_c1lep4jin2bin_met
-//=========  (Thu Jul 19 17:38:04 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jin2bin_met = new TCanvas("c_c1lep4jin2bin_met", "c_c1lep4jin2bin_met",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jin2bin_met->SetHighLightColor(2);
-   c_c1lep4jin2bin_met->Range(0,0,1,1);
-   c_c1lep4jin2bin_met->SetFillColor(0);
-   c_c1lep4jin2bin_met->SetBorderMode(0);
-   c_c1lep4jin2bin_met->SetBorderSize(2);
-   c_c1lep4jin2bin_met->SetTickx(1);
-   c_c1lep4jin2bin_met->SetTicky(1);
-   c_c1lep4jin2bin_met->SetLeftMargin(0.16);
-   c_c1lep4jin2bin_met->SetRightMargin(0.05);
-   c_c1lep4jin2bin_met->SetTopMargin(0.05);
-   c_c1lep4jin2bin_met->SetBottomMargin(0.16);
-   c_c1lep4jin2bin_met->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-34.5679,-0.0873016,212.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis171[5] = {0, 50, 100, 150, 200}; 
-   
-   TH1D *h_dummy2__154 = new TH1D("h_dummy2__154","Data/MC",4, xAxis171);
-   h_dummy2__154->SetMinimum(0.5);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep5jex2bex.C

@@ -1,685 +1,0 @@
-void c1lep5jex2bex()
-{
-//=========Macro generated from canvas: c_c1lep5jex2bex/c_c1lep5jex2bex
-//=========  (Thu Jul 19 17:38:02 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep5jex2bex = new TCanvas("c_c1lep5jex2bex", "c_c1lep5jex2bex",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep5jex2bex->SetHighLightColor(2);
-   c_c1lep5jex2bex->Range(0,0,1,1);
-   c_c1lep5jex2bex->SetFillColor(0);
-   c_c1lep5jex2bex->SetBorderMode(0);
-   c_c1lep5jex2bex->SetBorderSize(2);
-   c_c1lep5jex2bex->SetTickx(1);
-   c_c1lep5jex2bex->SetTicky(1);
-   c_c1lep5jex2bex->SetLeftMargin(0.16);
-   c_c1lep5jex2bex->SetRightMargin(0.05);
-   c_c1lep5jex2bex->SetTopMargin(0.05);
-   c_c1lep5jex2bex->SetBottomMargin(0.16);
-   c_c1lep5jex2bex->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0.5308642,-0.0873016,1.024691,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis31[2] = {0.6, 1}; 
-   
-   TH1D *h_dummy2__28 = new TH1D("h_dummy2__28","Data/MC",1, xAxis31);
-   h_dummy2__28->SetMinimum(0.5);
-   h_dummy2__28->SetMaximum(1.5);
-   h_dummy2__28->SetEntries(2849793);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep5jex3bex.C

@@ -1,981 +1,0 @@
-void c1lep5jex3bex()
-{
-//=========Macro generated from canvas: c_c1lep5jex3bex/c_c1lep5jex3bex
-//=========  (Thu Jul 19 17:38:02 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep5jex3bex = new TCanvas("c_c1lep5jex3bex", "c_c1lep5jex3bex",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep5jex3bex->SetHighLightColor(2);
-   c_c1lep5jex3bex->Range(0,0,1,1);
-   c_c1lep5jex3bex->SetFillColor(0);
-   c_c1lep5jex3bex->SetBorderMode(0);
-   c_c1lep5jex3bex->SetBorderSize(2);
-   c_c1lep5jex3bex->SetTickx(1);
-   c_c1lep5jex3bex->SetTicky(1);
-   c_c1lep5jex3bex->SetLeftMargin(0.16);
-   c_c1lep5jex3bex->SetRightMargin(0.05);
-   c_c1lep5jex3bex->SetTopMargin(0.05);
-   c_c1lep5jex3bex->SetBottomMargin(0.16);
-   c_c1lep5jex3bex->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-0.1728395,-0.0873016,1.061728,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis41[11] = {0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1}; 
-   
-   TH1D *h_dummy2__37 = new TH1D("h_dummy2__37","Data/MC",10, xAxis41);
-   h_dummy2__37->SetMinimum(0.5);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep5jex3bex_bjets_n.C

@@ -1,744 +1,0 @@
-void c1lep5jex3bex_bjets_n()
-{
-//=========Macro generated from canvas: c_c1lep5jex3bex_bjets_n/c_c1lep5jex3bex_bjets_n
-//=========  (Thu Jul 19 16:48:44 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep5jex3bex_bjets_n = new TCanvas("c_c1lep5jex3bex_bjets_n", "c_c1lep5jex3bex_bjets_n",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep5jex3bex_bjets_n->SetHighLightColor(2);
-   c_c1lep5jex3bex_bjets_n->Range(0,0,1,1);
-   c_c1lep5jex3bex_bjets_n->SetFillColor(0);
-   c_c1lep5jex3bex_bjets_n->SetBorderMode(0);
-   c_c1lep5jex3bex_bjets_n->SetBorderSize(2);
-   c_c1lep5jex3bex_bjets_n->SetTickx(1);
-   c_c1lep5jex3bex_bjets_n->SetTicky(1);
-   c_c1lep5jex3bex_bjets_n->SetLeftMargin(0.16);
-   c_c1lep5jex3bex_bjets_n->SetRightMargin(0.05);
-   c_c1lep5jex3bex_bjets_n->SetTopMargin(0.05);
-   c_c1lep5jex3bex_bjets_n->SetBottomMargin(0.16);
-   c_c1lep5jex3bex_bjets_n->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0.9814815,-0.0873016,4.685185,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep5jex3bex_jets_n.C

@@ -1,776 +1,0 @@
-void c1lep5jex3bex_jets_n()
-{
-//=========Macro generated from canvas: c_c1lep5jex3bex_jets_n/c_c1lep5jex3bex_jets_n
-//=========  (Thu Jul 19 16:48:43 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep5jex3bex_jets_n = new TCanvas("c_c1lep5jex3bex_jets_n", "c_c1lep5jex3bex_jets_n",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep5jex3bex_jets_n->SetHighLightColor(2);
-   c_c1lep5jex3bex_jets_n->Range(0,0,1,1);
-   c_c1lep5jex3bex_jets_n->SetFillColor(0);
-   c_c1lep5jex3bex_jets_n->SetBorderMode(0);
-   c_c1lep5jex3bex_jets_n->SetBorderSize(2);
-   c_c1lep5jex3bex_jets_n->SetTickx(1);
-   c_c1lep5jex3bex_jets_n->SetTicky(1);
-   c_c1lep5jex3bex_jets_n->SetLeftMargin(0.16);
-   c_c1lep5jex3bex_jets_n->SetRightMargin(0.05);
-   c_c1lep5jex3bex_jets_n->SetTopMargin(0.05);
-   c_c1lep5jex3bex_jets_n->SetBottomMargin(0.16);
-   c_c1lep5jex3bex_jets_n->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(2.808642,-0.0873016,7.746914,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis391[5] = {3.5, 4.5, 5.5, 6.5, 7.5}; 
-   
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep5jex3bex_jets_pt.C

@@ -1,860 +1,0 @@
-void c1lep5jex3bex_jets_pt()
-{
-//=========Macro generated from canvas: c_c1lep5jex3bex_jets_pt/c_c1lep5jex3bex_jets_pt
-//=========  (Thu Jul 19 17:38:06 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep5jex3bex_jets_pt = new TCanvas("c_c1lep5jex3bex_jets_pt", "c_c1lep5jex3bex_jets_pt",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep5jex3bex_jets_pt->SetHighLightColor(2);
-   c_c1lep5jex3bex_jets_pt->Range(0,0,1,1);
-   c_c1lep5jex3bex_jets_pt->SetFillColor(0);
-   c_c1lep5jex3bex_jets_pt->SetBorderMode(0);
-   c_c1lep5jex3bex_jets_pt->SetBorderSize(2);
-   c_c1lep5jex3bex_jets_pt->SetTickx(1);
-   c_c1lep5jex3bex_jets_pt->SetTicky(1);
-   c_c1lep5jex3bex_jets_pt->SetLeftMargin(0.16);
-   c_c1lep5jex3bex_jets_pt->SetRightMargin(0.05);
-   c_c1lep5jex3bex_jets_pt->SetTopMargin(0.05);
-   c_c1lep5jex3bex_jets_pt->SetBottomMargin(0.16);
-   c_c1lep5jex3bex_jets_pt->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-26.85185,-0.0873016,343.5185,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep5jex3bex_lep0_eta.C

@@ -1,996 +1,0 @@
-void c1lep5jex3bex_lep0_eta()
-{
-//=========Macro generated from canvas: c_c1lep5jex3bex_lep0_eta/c_c1lep5jex3bex_lep0_eta
-//=========  (Thu Jul 19 17:38:07 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep5jex3bex_lep0_eta = new TCanvas("c_c1lep5jex3bex_lep0_eta", "c_c1lep5jex3bex_lep0_eta",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep5jex3bex_lep0_eta->SetHighLightColor(2);
-   c_c1lep5jex3bex_lep0_eta->Range(0,0,1,1);
-   c_c1lep5jex3bex_lep0_eta->SetFillColor(0);
-   c_c1lep5jex3bex_lep0_eta->SetBorderMode(0);
-   c_c1lep5jex3bex_lep0_eta->SetBorderSize(2);
-   c_c1lep5jex3bex_lep0_eta->SetTickx(1);
-   c_c1lep5jex3bex_lep0_eta->SetTicky(1);
-   c_c1lep5jex3bex_lep0_eta->SetLeftMargin(0.16);
-   c_c1lep5jex3bex_lep0_eta->SetRightMargin(0.05);
-   c_c1lep5jex3bex_lep0_eta->SetTopMargin(0.05);
-   c_c1lep5jex3bex_lep0_eta->SetBottomMargin(0.16);
-   c_c1lep5jex3bex_lep0_eta->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-3.364198,-0.0873016,2.808642,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep5jex3bex_lep0_pt.C

@@ -1,792 +1,0 @@
-void c1lep5jex3bex_lep0_pt()
-{
-//=========Macro generated from canvas: c_c1lep5jex3bex_lep0_pt/c_c1lep5jex3bex_lep0_pt
-//=========  (Thu Jul 19 17:38:07 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep5jex3bex_lep0_pt = new TCanvas("c_c1lep5jex3bex_lep0_pt", "c_c1lep5jex3bex_lep0_pt",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep5jex3bex_lep0_pt->SetHighLightColor(2);
-   c_c1lep5jex3bex_lep0_pt->Range(0,0,1,1);
-   c_c1lep5jex3bex_lep0_pt->SetFillColor(0);
-   c_c1lep5jex3bex_lep0_pt->SetBorderMode(0);
-   c_c1lep5jex3bex_lep0_pt->SetBorderSize(2);
-   c_c1lep5jex3bex_lep0_pt->SetTickx(1);
-   c_c1lep5jex3bex_lep0_pt->SetTicky(1);
-   c_c1lep5jex3bex_lep0_pt->SetLeftMargin(0.16);
-   c_c1lep5jex3bex_lep0_pt->SetRightMargin(0.05);
-   c_c1lep5jex3bex_lep0_pt->SetTopMargin(0.05);
-   c_c1lep5jex3bex_lep0_pt->SetBottomMargin(0.16);
-   c_c1lep5jex3bex_lep0_pt->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-9.567901,-0.0873016,237.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep5jex3bex_mbb_mindR.C

@@ -1,938 +1,0 @@
-void c1lep5jex3bex_mbb_mindR()
-{
-//=========Macro generated from canvas: c_c1lep5jex3bex_mbb_mindR/c_c1lep5jex3bex_mbb_mindR
-//=========  (Thu Jul 19 17:38:09 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep5jex3bex_mbb_mindR = new TCanvas("c_c1lep5jex3bex_mbb_mindR", "c_c1lep5jex3bex_mbb_mindR",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep5jex3bex_mbb_mindR->SetHighLightColor(2);
-   c_c1lep5jex3bex_mbb_mindR->Range(0,0,1,1);
-   c_c1lep5jex3bex_mbb_mindR->SetFillColor(0);
-   c_c1lep5jex3bex_mbb_mindR->SetBorderMode(0);
-   c_c1lep5jex3bex_mbb_mindR->SetBorderSize(2);
-   c_c1lep5jex3bex_mbb_mindR->SetTickx(1);
-   c_c1lep5jex3bex_mbb_mindR->SetTicky(1);
-   c_c1lep5jex3bex_mbb_mindR->SetLeftMargin(0.16);
-   c_c1lep5jex3bex_mbb_mindR->SetRightMargin(0.05);
-   c_c1lep5jex3bex_mbb_mindR->SetTopMargin(0.05);
-   c_c1lep5jex3bex_mbb_mindR->SetBottomMargin(0.16);
-   c_c1lep5jex3bex_mbb_mindR->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(15.4321,-0.0873016,262.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep5jex3bex_meff.C

@@ -1,894 +1,0 @@
-void c1lep5jex3bex_meff()
-{
-//=========Macro generated from canvas: c_c1lep5jex3bex_meff/c_c1lep5jex3bex_meff
-//=========  (Thu Jul 19 17:38:03 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep5jex3bex_meff = new TCanvas("c_c1lep5jex3bex_meff", "c_c1lep5jex3bex_meff",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep5jex3bex_meff->SetHighLightColor(2);
-   c_c1lep5jex3bex_meff->Range(0,0,1,1);
-   c_c1lep5jex3bex_meff->SetFillColor(0);
-   c_c1lep5jex3bex_meff->SetBorderMode(0);
-   c_c1lep5jex3bex_meff->SetBorderSize(2);
-   c_c1lep5jex3bex_meff->SetTickx(1);
-   c_c1lep5jex3bex_meff->SetTicky(1);
-   c_c1lep5jex3bex_meff->SetLeftMargin(0.16);
-   c_c1lep5jex3bex_meff->SetRightMargin(0.05);
-   c_c1lep5jex3bex_meff->SetTopMargin(0.05);
-   c_c1lep5jex3bex_meff->SetBottomMargin(0.16);
-   c_c1lep5jex3bex_meff->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(4.012346,-0.0873016,868.2099,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis111[8] = {125, 225, 325, 425, 525, 625, 725, 825}; 
-   
-   TH1D *h_dummy2__100 = new TH1D("h_dummy2__100","Data/MC",7, xAxis111);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep5jex3bex_met.C

@@ -1,792 +1,0 @@
-void c1lep5jex3bex_met()
-{
-//=========Macro generated from canvas: c_c1lep5jex3bex_met/c_c1lep5jex3bex_met
-//=========  (Thu Jul 19 17:38:05 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep5jex3bex_met = new TCanvas("c_c1lep5jex3bex_met", "c_c1lep5jex3bex_met",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep5jex3bex_met->SetHighLightColor(2);
-   c_c1lep5jex3bex_met->Range(0,0,1,1);
-   c_c1lep5jex3bex_met->SetFillColor(0);
-   c_c1lep5jex3bex_met->SetBorderMode(0);
-   c_c1lep5jex3bex_met->SetBorderSize(2);
-   c_c1lep5jex3bex_met->SetTickx(1);
-   c_c1lep5jex3bex_met->SetTicky(1);
-   c_c1lep5jex3bex_met->SetLeftMargin(0.16);
-   c_c1lep5jex3bex_met->SetRightMargin(0.05);
-   c_c1lep5jex3bex_met->SetTopMargin(0.05);
-   c_c1lep5jex3bex_met->SetBottomMargin(0.16);
-   c_c1lep5jex3bex_met->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-34.5679,-0.0873016,212.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis191[5] = {0, 50, 100, 150, 200}; 
-   
-   TH1D *h_dummy2__172 = new TH1D("h_dummy2__172","Data/MC",4, xAxis191);
-   h_dummy2__172->SetMinimum(0.5);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep5jex3bex_mtw.C

@@ -1,792 +1,0 @@
-void c1lep5jex3bex_mtw()
-{
-//=========Macro generated from canvas: c_c1lep5jex3bex_mtw/c_c1lep5jex3bex_mtw
-//=========  (Thu Jul 19 17:38:05 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep5jex3bex_mtw = new TCanvas("c_c1lep5jex3bex_mtw", "c_c1lep5jex3bex_mtw",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep5jex3bex_mtw->SetHighLightColor(2);
-   c_c1lep5jex3bex_mtw->Range(0,0,1,1);
-   c_c1lep5jex3bex_mtw->SetFillColor(0);
-   c_c1lep5jex3bex_mtw->SetBorderMode(0);
-   c_c1lep5jex3bex_mtw->SetBorderSize(2);
-   c_c1lep5jex3bex_mtw->SetTickx(1);
-   c_c1lep5jex3bex_mtw->SetTicky(1);
-   c_c1lep5jex3bex_mtw->SetLeftMargin(0.16);
-   c_c1lep5jex3bex_mtw->SetRightMargin(0.05);
-   c_c1lep5jex3bex_mtw->SetTopMargin(0.05);
-   c_c1lep5jex3bex_mtw->SetBottomMargin(0.16);
-   c_c1lep5jex3bex_mtw->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-34.5679,-0.0873016,212.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis231[5] = {0, 50, 100, 150, 200}; 
-   
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep5jex4bin.C

@@ -1,709 +1,0 @@
-void c1lep5jex4bin()
-{
-//=========Macro generated from canvas: c_c1lep5jex4bin/c_c1lep5jex4bin
-//=========  (Thu Jul 19 17:38:02 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep5jex4bin = new TCanvas("c_c1lep5jex4bin", "c_c1lep5jex4bin",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep5jex4bin->SetHighLightColor(2);
-   c_c1lep5jex4bin->Range(0,0,1,1);
-   c_c1lep5jex4bin->SetFillColor(0);
-   c_c1lep5jex4bin->SetBorderMode(0);
-   c_c1lep5jex4bin->SetBorderSize(2);
-   c_c1lep5jex4bin->SetTickx(1);
-   c_c1lep5jex4bin->SetTicky(1);
-   c_c1lep5jex4bin->SetLeftMargin(0.16);
-   c_c1lep5jex4bin->SetRightMargin(0.05);
-   c_c1lep5jex4bin->SetTopMargin(0.05);
-   c_c1lep5jex4bin->SetBottomMargin(0.16);
-   c_c1lep5jex4bin->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-0.1728395,-0.0873016,1.061728,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis51[3] = {0, 0.5, 1}; 
-   
-   TH1D *h_dummy2__46 = new TH1D("h_dummy2__46","Data/MC",2, xAxis51);
-   h_dummy2__46->SetMinimum(0.5);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep6jin2bex.C

@@ -1,685 +1,0 @@
-void c1lep6jin2bex()
-{
-//=========Macro generated from canvas: c_c1lep6jin2bex/c_c1lep6jin2bex
-//=========  (Thu Jul 19 17:38:02 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin2bex = new TCanvas("c_c1lep6jin2bex", "c_c1lep6jin2bex",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin2bex->SetHighLightColor(2);
-   c_c1lep6jin2bex->Range(0,0,1,1);
-   c_c1lep6jin2bex->SetFillColor(0);
-   c_c1lep6jin2bex->SetBorderMode(0);
-   c_c1lep6jin2bex->SetBorderSize(2);
-   c_c1lep6jin2bex->SetTickx(1);
-   c_c1lep6jin2bex->SetTicky(1);
-   c_c1lep6jin2bex->SetLeftMargin(0.16);
-   c_c1lep6jin2bex->SetRightMargin(0.05);
-   c_c1lep6jin2bex->SetTopMargin(0.05);
-   c_c1lep6jin2bex->SetBottomMargin(0.16);
-   c_c1lep6jin2bex->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0.5308642,-0.0873016,1.024691,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis61[2] = {0.6, 1}; 
-   
-   TH1D *h_dummy2__55 = new TH1D("h_dummy2__55","Data/MC",1, xAxis61);
-   h_dummy2__55->SetMinimum(0.5);
-   h_dummy2__55->SetMaximum(1.5);
-   h_dummy2__55->SetEntries(2561961);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep6jin3bex.C

@@ -1,981 +1,0 @@
-void c1lep6jin3bex()
-{
-//=========Macro generated from canvas: c_c1lep6jin3bex/c_c1lep6jin3bex
-//=========  (Thu Jul 19 17:38:03 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin3bex = new TCanvas("c_c1lep6jin3bex", "c_c1lep6jin3bex",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin3bex->SetHighLightColor(2);
-   c_c1lep6jin3bex->Range(0,0,1,1);
-   c_c1lep6jin3bex->SetFillColor(0);
-   c_c1lep6jin3bex->SetBorderMode(0);
-   c_c1lep6jin3bex->SetBorderSize(2);
-   c_c1lep6jin3bex->SetTickx(1);
-   c_c1lep6jin3bex->SetTicky(1);
-   c_c1lep6jin3bex->SetLeftMargin(0.16);
-   c_c1lep6jin3bex->SetRightMargin(0.05);
-   c_c1lep6jin3bex->SetTopMargin(0.05);
-   c_c1lep6jin3bex->SetBottomMargin(0.16);
-   c_c1lep6jin3bex->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-0.1728395,-0.0873016,1.061728,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis71[11] = {0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1}; 
-   
-   TH1D *h_dummy2__64 = new TH1D("h_dummy2__64","Data/MC",10, xAxis71);
-   h_dummy2__64->SetMinimum(0.5);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep6jin3bex_bjets_n.C

@@ -1,744 +1,0 @@
-void c1lep6jin3bex_bjets_n()
-{
-//=========Macro generated from canvas: c_c1lep6jin3bex_bjets_n/c_c1lep6jin3bex_bjets_n
-//=========  (Thu Jul 19 16:48:44 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin3bex_bjets_n = new TCanvas("c_c1lep6jin3bex_bjets_n", "c_c1lep6jin3bex_bjets_n",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin3bex_bjets_n->SetHighLightColor(2);
-   c_c1lep6jin3bex_bjets_n->Range(0,0,1,1);
-   c_c1lep6jin3bex_bjets_n->SetFillColor(0);
-   c_c1lep6jin3bex_bjets_n->SetBorderMode(0);
-   c_c1lep6jin3bex_bjets_n->SetBorderSize(2);
-   c_c1lep6jin3bex_bjets_n->SetTickx(1);
-   c_c1lep6jin3bex_bjets_n->SetTicky(1);
-   c_c1lep6jin3bex_bjets_n->SetLeftMargin(0.16);
-   c_c1lep6jin3bex_bjets_n->SetRightMargin(0.05);
-   c_c1lep6jin3bex_bjets_n->SetTopMargin(0.05);
-   c_c1lep6jin3bex_bjets_n->SetBottomMargin(0.16);
-   c_c1lep6jin3bex_bjets_n->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0.9814815,-0.0873016,4.685185,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep6jin3bex_hthad.C

@@ -1,903 +1,0 @@
-void c1lep6jin3bex_hthad()
-{
-//=========Macro generated from canvas: c_c1lep6jin3bex_hthad/c_c1lep6jin3bex_hthad
-//=========  (Thu Jul 19 17:38:04 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin3bex_hthad = new TCanvas("c_c1lep6jin3bex_hthad", "c_c1lep6jin3bex_hthad",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin3bex_hthad->SetHighLightColor(2);
-   c_c1lep6jin3bex_hthad->Range(0,0,1,1);
-   c_c1lep6jin3bex_hthad->SetFillColor(0);
-   c_c1lep6jin3bex_hthad->SetBorderMode(0);
-   c_c1lep6jin3bex_hthad->SetBorderSize(2);
-   c_c1lep6jin3bex_hthad->SetTickx(1);
-   c_c1lep6jin3bex_hthad->SetTicky(1);
-   c_c1lep6jin3bex_hthad->SetLeftMargin(0.16);
-   c_c1lep6jin3bex_hthad->SetRightMargin(0.05);
-   c_c1lep6jin3bex_hthad->SetTopMargin(0.05);
-   c_c1lep6jin3bex_hthad->SetBottomMargin(0.16);
-   c_c1lep6jin3bex_hthad->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-20.98765,-0.0873016,843.2099,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis161[8] = {100, 200, 300, 400, 500, 600, 700, 800}; 
-   
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep6jin3bex_jets_n.C

@@ -1,788 +1,0 @@
-void c1lep6jin3bex_jets_n()
-{
-//=========Macro generated from canvas: c_c1lep6jin3bex_jets_n/c_c1lep6jin3bex_jets_n
-//=========  (Thu Jul 19 16:48:44 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin3bex_jets_n = new TCanvas("c_c1lep6jin3bex_jets_n", "c_c1lep6jin3bex_jets_n",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin3bex_jets_n->SetHighLightColor(2);
-   c_c1lep6jin3bex_jets_n->Range(0,0,1,1);
-   c_c1lep6jin3bex_jets_n->SetFillColor(0);
-   c_c1lep6jin3bex_jets_n->SetBorderMode(0);
-   c_c1lep6jin3bex_jets_n->SetBorderSize(2);
-   c_c1lep6jin3bex_jets_n->SetTickx(1);
-   c_c1lep6jin3bex_jets_n->SetTicky(1);
-   c_c1lep6jin3bex_jets_n->SetLeftMargin(0.16);
-   c_c1lep6jin3bex_jets_n->SetRightMargin(0.05);
-   c_c1lep6jin3bex_jets_n->SetTopMargin(0.05);
-   c_c1lep6jin3bex_jets_n->SetBottomMargin(0.16);
-   c_c1lep6jin3bex_jets_n->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(2.808642,-0.0873016,7.746914,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis401[5] = {3.5, 4.5, 5.5, 6.5, 7.5}; 
-   
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep6jin3bex_jets_pt.C

@@ -1,860 +1,0 @@
-void c1lep6jin3bex_jets_pt()
-{
-//=========Macro generated from canvas: c_c1lep6jin3bex_jets_pt/c_c1lep6jin3bex_jets_pt
-//=========  (Thu Jul 19 17:38:06 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin3bex_jets_pt = new TCanvas("c_c1lep6jin3bex_jets_pt", "c_c1lep6jin3bex_jets_pt",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin3bex_jets_pt->SetHighLightColor(2);
-   c_c1lep6jin3bex_jets_pt->Range(0,0,1,1);
-   c_c1lep6jin3bex_jets_pt->SetFillColor(0);
-   c_c1lep6jin3bex_jets_pt->SetBorderMode(0);
-   c_c1lep6jin3bex_jets_pt->SetBorderSize(2);
-   c_c1lep6jin3bex_jets_pt->SetTickx(1);
-   c_c1lep6jin3bex_jets_pt->SetTicky(1);
-   c_c1lep6jin3bex_jets_pt->SetLeftMargin(0.16);
-   c_c1lep6jin3bex_jets_pt->SetRightMargin(0.05);
-   c_c1lep6jin3bex_jets_pt->SetTopMargin(0.05);
-   c_c1lep6jin3bex_jets_pt->SetBottomMargin(0.16);
-   c_c1lep6jin3bex_jets_pt->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-26.85185,-0.0873016,343.5185,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep6jin3bex_lep0_eta.C

@@ -1,996 +1,0 @@
-void c1lep6jin3bex_lep0_eta()
-{
-//=========Macro generated from canvas: c_c1lep6jin3bex_lep0_eta/c_c1lep6jin3bex_lep0_eta
-//=========  (Thu Jul 19 17:38:07 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin3bex_lep0_eta = new TCanvas("c_c1lep6jin3bex_lep0_eta", "c_c1lep6jin3bex_lep0_eta",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin3bex_lep0_eta->SetHighLightColor(2);
-   c_c1lep6jin3bex_lep0_eta->Range(0,0,1,1);
-   c_c1lep6jin3bex_lep0_eta->SetFillColor(0);
-   c_c1lep6jin3bex_lep0_eta->SetBorderMode(0);
-   c_c1lep6jin3bex_lep0_eta->SetBorderSize(2);
-   c_c1lep6jin3bex_lep0_eta->SetTickx(1);
-   c_c1lep6jin3bex_lep0_eta->SetTicky(1);
-   c_c1lep6jin3bex_lep0_eta->SetLeftMargin(0.16);
-   c_c1lep6jin3bex_lep0_eta->SetRightMargin(0.05);
-   c_c1lep6jin3bex_lep0_eta->SetTopMargin(0.05);
-   c_c1lep6jin3bex_lep0_eta->SetBottomMargin(0.16);
-   c_c1lep6jin3bex_lep0_eta->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-3.364198,-0.0873016,2.808642,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep6jin3bex_lep0_pt.C

@@ -1,792 +1,0 @@
-void c1lep6jin3bex_lep0_pt()
-{
-//=========Macro generated from canvas: c_c1lep6jin3bex_lep0_pt/c_c1lep6jin3bex_lep0_pt
-//=========  (Thu Jul 19 17:38:07 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin3bex_lep0_pt = new TCanvas("c_c1lep6jin3bex_lep0_pt", "c_c1lep6jin3bex_lep0_pt",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin3bex_lep0_pt->SetHighLightColor(2);
-   c_c1lep6jin3bex_lep0_pt->Range(0,0,1,1);
-   c_c1lep6jin3bex_lep0_pt->SetFillColor(0);
-   c_c1lep6jin3bex_lep0_pt->SetBorderMode(0);
-   c_c1lep6jin3bex_lep0_pt->SetBorderSize(2);
-   c_c1lep6jin3bex_lep0_pt->SetTickx(1);
-   c_c1lep6jin3bex_lep0_pt->SetTicky(1);
-   c_c1lep6jin3bex_lep0_pt->SetLeftMargin(0.16);
-   c_c1lep6jin3bex_lep0_pt->SetRightMargin(0.05);
-   c_c1lep6jin3bex_lep0_pt->SetTopMargin(0.05);
-   c_c1lep6jin3bex_lep0_pt->SetBottomMargin(0.16);
-   c_c1lep6jin3bex_lep0_pt->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-9.567901,-0.0873016,237.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep6jin3bex_mbb_leading_bjets.C

@@ -1,972 +1,0 @@
-void c1lep6jin3bex_mbb_leading_bjets()
-{
-//=========Macro generated from canvas: c_c1lep6jin3bex_mbb_leading_bjets/c_c1lep6jin3bex_mbb_leading_bjets
-//=========  (Thu Jul 19 17:38:09 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin3bex_mbb_leading_bjets = new TCanvas("c_c1lep6jin3bex_mbb_leading_bjets", "c_c1lep6jin3bex_mbb_leading_bjets",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin3bex_mbb_leading_bjets->SetHighLightColor(2);
-   c_c1lep6jin3bex_mbb_leading_bjets->Range(0,0,1,1);
-   c_c1lep6jin3bex_mbb_leading_bjets->SetFillColor(0);
-   c_c1lep6jin3bex_mbb_leading_bjets->SetBorderMode(0);
-   c_c1lep6jin3bex_mbb_leading_bjets->SetBorderSize(2);
-   c_c1lep6jin3bex_mbb_leading_bjets->SetTickx(1);
-   c_c1lep6jin3bex_mbb_leading_bjets->SetTicky(1);
-   c_c1lep6jin3bex_mbb_leading_bjets->SetLeftMargin(0.16);
-   c_c1lep6jin3bex_mbb_leading_bjets->SetRightMargin(0.05);
-   c_c1lep6jin3bex_mbb_leading_bjets->SetTopMargin(0.05);
-   c_c1lep6jin3bex_mbb_leading_bjets->SetBottomMargin(0.16);
-   c_c1lep6jin3bex_mbb_leading_bjets->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-27.77778,-0.0873016,527.7778,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep6jin3bex_mbb_mindR.C

@@ -1,938 +1,0 @@
-void c1lep6jin3bex_mbb_mindR()
-{
-//=========Macro generated from canvas: c_c1lep6jin3bex_mbb_mindR/c_c1lep6jin3bex_mbb_mindR
-//=========  (Thu Jul 19 17:38:09 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin3bex_mbb_mindR = new TCanvas("c_c1lep6jin3bex_mbb_mindR", "c_c1lep6jin3bex_mbb_mindR",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin3bex_mbb_mindR->SetHighLightColor(2);
-   c_c1lep6jin3bex_mbb_mindR->Range(0,0,1,1);
-   c_c1lep6jin3bex_mbb_mindR->SetFillColor(0);
-   c_c1lep6jin3bex_mbb_mindR->SetBorderMode(0);
-   c_c1lep6jin3bex_mbb_mindR->SetBorderSize(2);
-   c_c1lep6jin3bex_mbb_mindR->SetTickx(1);
-   c_c1lep6jin3bex_mbb_mindR->SetTicky(1);
-   c_c1lep6jin3bex_mbb_mindR->SetLeftMargin(0.16);
-   c_c1lep6jin3bex_mbb_mindR->SetRightMargin(0.05);
-   c_c1lep6jin3bex_mbb_mindR->SetTopMargin(0.05);
-   c_c1lep6jin3bex_mbb_mindR->SetBottomMargin(0.16);
-   c_c1lep6jin3bex_mbb_mindR->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(15.4321,-0.0873016,262.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep6jin3bex_meff.C

@@ -1,892 +1,0 @@
-void c1lep6jin3bex_meff()
-{
-//=========Macro generated from canvas: c_c1lep6jin3bex_meff/c_c1lep6jin3bex_meff
-//=========  (Thu Jul 19 17:38:04 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin3bex_meff = new TCanvas("c_c1lep6jin3bex_meff", "c_c1lep6jin3bex_meff",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin3bex_meff->SetHighLightColor(2);
-   c_c1lep6jin3bex_meff->Range(0,0,1,1);
-   c_c1lep6jin3bex_meff->SetFillColor(0);
-   c_c1lep6jin3bex_meff->SetBorderMode(0);
-   c_c1lep6jin3bex_meff->SetBorderSize(2);
-   c_c1lep6jin3bex_meff->SetTickx(1);
-   c_c1lep6jin3bex_meff->SetTicky(1);
-   c_c1lep6jin3bex_meff->SetLeftMargin(0.16);
-   c_c1lep6jin3bex_meff->SetRightMargin(0.05);
-   c_c1lep6jin3bex_meff->SetTopMargin(0.05);
-   c_c1lep6jin3bex_meff->SetBottomMargin(0.16);
-   c_c1lep6jin3bex_meff->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(4.012346,-0.0873016,868.2099,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis121[8] = {125, 225, 325, 425, 525, 625, 725, 825}; 
-   
-   TH1D *h_dummy2__109 = new TH1D("h_dummy2__109","Data/MC",7, xAxis121);
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep6jin3bex_mtw.C

@@ -1,792 +1,0 @@
-void c1lep6jin3bex_mtw()
-{
-//=========Macro generated from canvas: c_c1lep6jin3bex_mtw/c_c1lep6jin3bex_mtw
-//=========  (Thu Jul 19 17:38:05 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin3bex_mtw = new TCanvas("c_c1lep6jin3bex_mtw", "c_c1lep6jin3bex_mtw",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin3bex_mtw->SetHighLightColor(2);
-   c_c1lep6jin3bex_mtw->Range(0,0,1,1);
-   c_c1lep6jin3bex_mtw->SetFillColor(0);
-   c_c1lep6jin3bex_mtw->SetBorderMode(0);
-   c_c1lep6jin3bex_mtw->SetBorderSize(2);
-   c_c1lep6jin3bex_mtw->SetTickx(1);
-   c_c1lep6jin3bex_mtw->SetTicky(1);
-   c_c1lep6jin3bex_mtw->SetLeftMargin(0.16);
-   c_c1lep6jin3bex_mtw->SetRightMargin(0.05);
-   c_c1lep6jin3bex_mtw->SetTopMargin(0.05);
-   c_c1lep6jin3bex_mtw->SetBottomMargin(0.16);
-   c_c1lep6jin3bex_mtw->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-34.5679,-0.0873016,212.3457,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis241[5] = {0, 50, 100, 150, 200}; 
-   
[…]

### 2018-08-13 figures/Hbb/other_variables/c1lep6jin4bin.C

@@ -1,709 +1,0 @@
-void c1lep6jin4bin()
-{
-//=========Macro generated from canvas: c_c1lep6jin4bin/c_c1lep6jin4bin
-//=========  (Thu Jul 19 17:38:03 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin4bin = new TCanvas("c_c1lep6jin4bin", "c_c1lep6jin4bin",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin4bin->SetHighLightColor(2);
-   c_c1lep6jin4bin->Range(0,0,1,1);
-   c_c1lep6jin4bin->SetFillColor(0);
-   c_c1lep6jin4bin->SetBorderMode(0);
-   c_c1lep6jin4bin->SetBorderSize(2);
-   c_c1lep6jin4bin->SetTickx(1);
-   c_c1lep6jin4bin->SetTicky(1);
-   c_c1lep6jin4bin->SetLeftMargin(0.16);
-   c_c1lep6jin4bin->SetRightMargin(0.05);
-   c_c1lep6jin4bin->SetTopMargin(0.05);
-   c_c1lep6jin4bin->SetBottomMargin(0.16);
-   c_c1lep6jin4bin->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-0.1728395,-0.0873016,1.061728,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis81[3] = {0, 0.5, 1}; 
-   
-   TH1D *h_dummy2__73 = new TH1D("h_dummy2__73","Data/MC",2, xAxis81);
-   h_dummy2__73->SetMinimum(0.5);
-   h_dummy2__73->SetMaximum(1.5);
-   h_dummy2__73->SetEntries(872895);
[…]

### 2018-08-14 sections/conclusion.tex
some fixes to text
Implemented most CDS comments on v0.4

@@
 of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
-The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well multiple jets. 
+The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
 Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
-No significant excess of events above the background expectation is found, and observed (expected) 95\% CL upper limits are derived.
+No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
 The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 

### 2018-08-14 sections/strategy_Hbb.tex
Implemented most CDS comments on v0.4

@@
 However, the use of the 60\% $b$-tagging operating point, characterised by a low mistag rate for
-charm and light jets, make both $\Hc$ and $\Hu$ signals have a similar $b$-tag multiplicity spectrum,
+charm and light jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity spectrum,
 with a very small fraction of events having four or more $b$-tagged jets.
@@
 at least four $b$-tagged jets are dominated by \ttbin. Intermediate compositions are found in regions with exactly three 
-$b$-tagged jets.  Most of the $\ttbar$+light-jets background in the these regions have a charm jet from the hadronic $W$ boson 
+$b$-tagged jets.  Most of the $\ttbar$+light-jets background in the these regions has a charm jet from the hadronic $W$ boson 
 decay  being $b$-tagged, in addition to the two $b$-jets from the top quark decays.
@@
 between them. The most prominent features are the different resonances present in the decay (i.e. the Higgs boson in the case 
-of $\Hq$ signal and a hadronically decaying $W$ boson in the case of the $\ttbar \to WbWb$ background), and the different flavour of the 
+of the $\Hq$ signal and a hadronically decaying $W$ boson in the case of the $\ttbar \to WbWb$ background), and the different flavour of the 
 jets forming those resonances. However, the large number of jets in the final state causes ambiguities in the calculation 
-of these kinematic variable to discriminate signal events from background events.
+of these kinematic variables to discriminate signal events from background events.
 
@@
 
-Since this analysis has higher expected sensitivity to a $\Hc$ signal than to a $\Hu$ signal and, in order to allow probing 
+Since this analysis has higher expected sensitivity to a $\Hc$ signal than to a $\Hu$ signal, and, in order to allow probing 
 of the $\BR(t\to Hu)$ versus $\BR(t\to Hc)$ plane, the LH discriminant optimised for $\Hc$ is used for both 
@@
 (a) (4j, 2b), (b) (4j, 3b), (c) (4j, 4b), (d) (5j, 2b), (e) (5j, 3b), (f) (5j, $\geq$4b), (g) ($\geq$6j, 2b), 
-(h) ($\geq$6j, 3b), and (i) ($\geq$6j, $\geq$4b). Due to the small signal acceptance in 4b regions,
-which translates into low statistics for the simulated samples, only two bins are used for this distribution.} 
+(h) ($\geq$6j, 3b), and (i) ($\geq$6j, $\geq$4b). 
+%Due to the small signal acceptance in 4b regions,
+%which translates into low statistics for the simulated samples, only two bins are used for this distribution.
+In the regions with $\geq$4 $b$-tagged jets, the signal acceptance is small, which translates
+into low statistics for the simulated samples. Therefore, only two bins are used for these distributions.} 
 \label{fig:LHD}

### 2018-08-14 sections/strategy_Htautau.tex
Implemented most CDS comments on v0.4

@@
 Boosted decision trees (BDT)~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} are used in each SR to improve the separation between signal and background. 
-The separate training exploits differences in event kinematics across SRs.
+%The separate training exploits differences in event kinematics across SRs.  
 In the training, only the $\Hq$ signal is used against the total SM background, including both real and fake $\tauhad$ contributions.
@@
 \item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically-decaying $W$ boson.
-\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance with the $\lep$ candidate.
-\item $m_{\tau j}$: the invariant mass of the  $\tauhad$ candidate and the jet that has the smallest angular distance with the $\tauhad$ candidate.
+\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance to the $\lep$ candidate.
+\item $m_{\tau j}$: the invariant mass of the  $\tauhad$ candidate and the jet that has the smallest angular distance to the $\tauhad$ candidate.
 \item $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$: the momentum fractions carried by the visible decay products from the two $\tau$-lepton candidates 
@@
 
-Among these variables, the most discriminating ones include $m_{\tau\tau}^{\text{fit}}$, $p_{\text{T},2}$, $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$.
+Among these variables, the most discriminating ones are $m_{\tau\tau}^{\text{fit}}$, $p_{\text{T},2}$, $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$.
 A comparison between data and background prediction for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:BDT_inputs_lephad} and~\ref{fig:BDT_inputs_hadhad}.
@@
 $p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
-The small contributions from $\ttbar V$, $\ttbar H$, single top, $Z\to \ell^+\ell^-$ ($\ell = e, \mu$), and diboson backgrounds are combined 
-into a single background source referred to as ``Other''. 
+The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
+$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
 The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
@@
 (c) $x_{1}^{\text{fit}}$ in the ($\hadhad$, 3j)  region, and (d) $x_{2}^{\text{fit}}$ in the ($\hadhad$, $\geq$4j) region.
-The small contributions from $\ttbar V$, $\ttbar H$, single top, $Z\to \ell^+\ell^-$ ($\ell = e, \mu$), and diboson backgrounds are combined 
-into a single background source referred to as ``Other''. 
+The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
+$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
 The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,

### 2018-08-14 sections/systematic_uncertainties.tex
v0.4 of paper draft
Implemented most CDS comments on v0.4

@@
 and background and/or the shape of their corresponding final discriminant distributions.  
-Each source of systematic uncertainty is considered to be uncorrelated with the other sources.  
+Each source is considered to be uncorrelated with the other sources.  
 Correlations of a given systematic uncertainty are maintained across processes and channels 
@@
 and resolution, and the efficiency to pass the JVT requirements. 
-The largest contribution results from the jet energy scale,
-whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pileup treatment is split into 21 uncorrelated components 
-that are treated independently~\cite{Aaboud:2017jcu}.
+The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pileup treatment, 
+is split into 21 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}.
 
@@
 regions have a sufficiently large number of events of \ttbin\ background, its normalisation is 
-determined by the data during the fit procedure.
+determined in the fit to data.
 %, with no prior uncertainty assumed. 
-In the case of the \ttcin\ normalisation, a normalisation uncertainty of 50\% is assumed, as the fit to the data is unable 
+In the case of the \ttcin\ normalisation, an uncertainty of 50\% is assumed, as the fit to the data is unable 
 to precisely determine it, and the analysis has very limited sensitivity to this uncertainty.
@@
 $+5\%$/$-4\%$ uncertainty in the total cross section estimated as a weighted average 
-of the theoretical uncertainties in $t$-, $Wt$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
+of the theoretical uncertainties in $t$-, $tW$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
 Additional uncertainties associated with the modelling of additional radiation are assessed by comparing the nominal
 samples with alternative samples where generator parameters are varied.
-For the $t$- and $Wt$-channel processes, an uncertainty due to the choice of parton shower and hadronisation model is derived 
+For the $t$- and $tW$-channel processes, an uncertainty due to the choice of parton shower and hadronisation model is derived 
 by comparing events produced by {\powheg} interfaced to {\pythia}~6 or {\herwigpp}.
@@
 corresponding uncertainty in the $\ttbar$+jets background.
-An additional systematic uncertainty on $Wt$-channel production concerning the separation 
-between $t\bar{t}$ and $Wt$ at NLO is assessed by comparing
+An additional systematic uncertainty on $tW$-channel production concerning the separation 
+between $t\bar{t}$ and $tW$ at NLO is assessed by comparing
 the nominal sample, which uses the so-called ``diagram removal'' scheme~\cite{Frixione:2008yi}, with an alternative sample
@@
 
-Uncertainties on the data-driven fake $\tauhad$ background in the $\Htautau$ search are obtained by using additional signal-depleted samples.
+Uncertainties on the data-driven fake $\tauhad$ background in the $\Htautau$ search are obtained by using additional signal-depleted regions.
 The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\tauhad$ identification criteria, and thus referred to as ``loose SR"  and ``loose CR".
@@
 is applied as an uncertainty on the prediction in the nominal SR.
-In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\tauhad$ candidate from the simulation that are added to the fake template in the $\hadhad$ channel as part of the fake $\tauhad$ background estimation procedure (see Section~\ref{sec:faketaus}).
+In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\tauhad$ candidate from the simulation that are added to the fake $\tauhad$ template in the $\hadhad$ channel as part of the fake $\tauhad$ background estimation procedure (see Section~\ref{sec:faketaus}).
 This uncertainty, associated with the modelling of the fake $\tauhad$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\tauhad$ candidate.
+The same uncertainty is assigned to the selected signal events with fake $\tauhad$ candidates.
 In addition, a systematic uncertainty is assigned to account for the different fractional composition of particles (various types of leptons and partons) originating the fake $\tauhad$ candidates 
 between each SR and its corresponding CR in the $\ttbar$ simulation. 
-Finally, the normalisation of the fake $\tauhad$ background in each SR is determined by the data during the fit procedure, and thus so is its uncertainty. 
+Finally, the normalisation of the fake $\tauhad$ background in each SR is determined in the fit to data. 
 %In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template.
@@
 These modelling uncertainties are taken to be uncorrelated with those affecting the $\ttbar \to WbWb$ background.
-Finally, a 30\% uncertainty is assigned to the signal events with fake $\tauhad$ candidates selected by the $\Htautau$ search.

### 2018-08-14 ANA-TOPQ-2017-07-PAPER-metadata.tex

@@
 % Comment or remove in final version.
-\AtlasVersion{0.4}
+\AtlasVersion{0.5}
 % Abstract - % directly after { is important for correct indentation
@@
 CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
-Two analyses are performed searching for top quark pair events in which one top quark decays to $Wb$ and the other top quark decays to $Hq$,
-and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
+Two analyses are performed that search for top quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
+and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
 They exploit either the high multiplicity of $b$-quark jets, or the presence of hadronically decaying tau leptons, and employ different
@@
 yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
-and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$) respectively.
+and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), respectively.
 The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.064 (0.055) respectively. 

### 2018-08-14 sections/data_presel.tex

@@
 Events selected by the $\Hbb$ search are recorded with a single-electron or single-muon trigger and 
-are required to have exactly one electron or muon that matches the lepton reconstructed by the trigger.  
+are required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger.  
 Furthermore, at least four jets are required, of which at least two must be $b$-tagged.
@@
 no selected light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
-In addition, in both channels at least three jets and exactly one $b$-tagged jet are required.
+In addition, in both channels, at least three jets and exactly one $b$-tagged jet are required.
 
@@
 %, which are in general different between both searches. 
-These requirements are referred to as the ``preselection'' and are summarised in Table~\ref{tab:preselection}.
+These requirements, which ensure a negligible overlap between the $\Hbb$ and $\Htautau$ searches,
+are referred to as the ``preselection'' and are summarised in Table~\ref{tab:preselection}.
 

### 2018-08-14 sections/introduction.tex

@@
 ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
-On the other hand, large enhancements in these branching ratios are possible in some beyond-SM scenarios.
+In contrast, large enhancements in these branching ratios are possible in some beyond-SM scenarios.
 Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
@@
 the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling. 
-See Ref.~\cite{AguilarSaavedra:2004wm} for a review.
+See Ref.~\cite{Agashe:2013hma} for a review.
 %\textbf{Update a bit above paragraph mentioning more recent models.}
@@
 has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
-and excellent diphoton mass re\-so\-lu\-tion. In contrast, multilepton searches are able to exploit a significantly larger branching ratio for the Higgs 
+and excellent diphoton mass re\-so\-lu\-tion. 
+Searches targeting signatures with two same-charge light leptons (electrons or muons) or three light leptons, generically referred to as ``multileptons",
+are able to exploit a significantly larger branching ratio for the Higgs 
 boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, and are also characterised by relatively small backgrounds.
@@
 $\BR(t\to Hc)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, and of $\BR(t\to Hc)<0.16\%$ based on
-signatures with two same-charge light leptons (electrons or muons) or three light leptons resulting from 
+%signatures with two same-charge light leptons (electrons or muons) or three light leptons 
+multilepton signatures resulting from 
 $H \to WW^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically, or $H \to ZZ^*$~\cite{Aaboud:2018pob}.
 These upper limits are derived under the assumption of $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ under the
-assumption of $\BR(t\to Hc)=0$. On the other hand, the CMS Collaboration has performed a search using  
+assumption of $\BR(t\to Hc)=0$. In addition, the CMS Collaboration has performed a search using  
 $H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} using 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
@@
 The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
-Therefore, they help complete the programme of searches for $t \to Hq$ decays at the ATLAS experiment based on proton-proton collision 
+Therefore, they help to complete the programme of searches for $t \to Hq$ decays at the ATLAS experiment based on $pp$ collision 
 data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
@@
 of which are identified with high purity as originating from the hadronisation of $b$-quarks. 
-The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well multiple jets. 
+The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
 Both searches employ different multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 

### 2018-08-14 sections/objects.tex

@@
 makes $\pt$-dependent requirements on $I_R/\pt^\ell$. Additionally, the $\Htautau$ search requires leptons to
-satisfy a calorimeter-based isolation criterion; a requirement is made on the sum of the transverse energy of
-topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contribution
-from the energy deposit of the lepton itself and correcting for pile-up effects, to be less than a $\pt$-dependent 
+satisfy a calorimeter-based isolation criterion: the sum of the transverse energy of
+topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contributions
+from pile-up and the energy deposit of the lepton itself, is required to be less than a $\pt$-dependent 
 percentage of the lepton energy. 
+%Additionally, the $\Htautau$ search requires leptons to
+%satisfy a calorimeter-based isolation criterion; a requirement is made on the sum of the transverse energy of
+%topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contribution
+%from the energy deposit of the lepton itself and correcting for pile-up effects, to be less than a $\pt$-dependent 
+%percentage of the lepton energy. 
 %The combined efficiency of track-based and calorimeter-based isolation requirements made by the $\Htautau$ 
@@
 values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
-working point for the nominal selection, while the loose working point is used for the purpose of background estimation.
+working point for the nominal selection, while the loose working point is used for background estimation.
 The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\tauhad$ 
 decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-quark/gluon jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
-Electrons that are reconstructed as one-prong $\tauhad$ candidates are removed via a BDT trained to reject electrons.
+Electrons that are reconstructed as one-prong $\tauhad$ candidates are removed via a BDT.
 Any $\tauhad$ candidate that is also $b$-tagged is rejected.

### 2018-08-14 sections/signal_background_modeling.tex

@@
 
-Signal and most background processes are modelled using Monte Carlo (MC) simulations.
+Signal and most background processes are modelled using Monte Carlo (MC) simulation.
 After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
@@
 The background prediction is further improved during the statistical analysis by performing a likelihood 
-fit to data using several signal-depleted search regions, as discussed in Sections~\ref{sec:strategy_Hbb} and~\ref{sec:strategy_Htautau}.
+fit to data using several signal-depleted analysis regions, as discussed in Sections~\ref{sec:strategy_Hbb} and~\ref{sec:strategy_Htautau}.
 
@@
 the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix element calculation 
-is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} for the modelling of parton showering, hadronisation, and the underlying event.
+is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering, hadronisation, and the underlying event.
 The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
@@
 
-The nominal sample used to model the $\ttbar$ background is generated with the NLO generator {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd} using the NNPDF3.0 PDF set.
+The nominal sample used to model the $\ttbar$ background is generated with the NLO generator {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd} using the NNPDF3.0 NLO PDF set.
 The {\powheg} model parameter $h_{\textrm{damp}}$, which controls
 matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, is set to 1.5 times the top quark mass. 
-Parton shower and hadronisation are modelled by {\pythia}~8.2 with the A14 tune.
+Parton shower, hadronisation, and underlying event are modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
 Alternative $\ttbar$ simulation samples used to derive systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
@@
 
-The $\Hbb$ search requires a more sophisticated treatment of the $\ttbar$ background. Therefore, the simulated $\ttbar$ events are categorised depending 
+%The $\Hbb$ search requires a more sophisticated treatment of the $\ttbar$ background. 
+The $\ttbar$ background selected by the $\Hbb$ search is enriched in $\ttbar$+heavy-flavour production, and thus requires a more sophisticated 
+treatment than provided by the nominal $\ttbar$ sample. 
+%The large and complex $\ttbar$ background selected by the $\Hbb$ search requires a more sophisticated treatment than provided by the nominal $\ttbar$ sample. 
+Therefore, the simulated $\ttbar$ events are categorised depending 
 on the flavour content of additional particle jets not originating from the decay of the $\ttbar$ system (see Ref.~\cite{Aaboud:2017rss} for details).
@@
 A finer categorisation of \ttbin\ events is considered for the purpose of applying further corrections and
-assigning systematic uncertainties associated with the modelling of heavy-flavour production in different topologies~\cite{Aaboud:2017rss}.
+assigning systematic uncertainties associated with the modelling of heavy-flavour production in different event topologies~\cite{Aaboud:2017rss}.
 In particular, the \ttbin\ events are reweighted to an NLO prediction in the four-flavour (4F) scheme 
@@
 in the following) using the CT10 PDF set.  This reweighting is performed in such a way that the inter-normalisations of the \ttbin\ categories are at NLO accuracy, 
-while preserving the nominal \ttbin\ cross section in {\powheg}+{\pythia}. This reweighting is applied as well to the alternative $\ttbar$ samples.
+while preserving the nominal \ttbin\ cross section of the nominal $\ttbar$ sample. This reweighting is applied to the alternative $\ttbar$ samples as well.
 
@@
 and the fixed 4F \textsc{CT10}f\textsc{4}~\cite{Lai:2010vv} PDF set.
-Samples corresponding to the $Wt$- and $s$-channel production mechanisms are generated 
-with {\powheg}~v1 using the CT10 PDF set. Overlaps between the $\ttbar$ and $Wt$ final states are avoided by using 
+Samples corresponding to the $tW$- and $s$-channel production mechanisms are generated 
+with {\powheg}~v1 using the CT10 PDF set. Overlaps between the $\ttbar$ and $tW$ final states are avoided by using 
 the ``diagram removal'' scheme~\cite{Frixione:2005vw}.
-The parton shower, hadronisation and the underlying event are modelled using {\pythia}~6.428 with the CTEQ6L1 PDF set 
+The parton shower, hadronisation and the underlying event are modelled using {\pythia}~6.428 with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set 
 in combination with the Perugia 2012 tune~\cite{Skands:2010ak}.
@@
 Samples of $WW/WZ/ZZ$+jets events are generated with {\sherpa}~2.1.1 using the CT10 PDF set
-and include processes containing up to four electroweak vertices. The matrix element includes zero additional partons 
+and include processes containing up to four electroweak vertices. 
+In the case of $WW/WZ$+jets ($ZZ$+jets) the matrix element is calculated for zero (up to one) additional partons 
 at NLO and up to three partons at LO using the same procedure as for the $W/Z$+jets samples. 
@@
 
-Samples of $\ttbar V$ and $\ttbar H$ events are generated with {\amcatnlo}~2.2.1, using 
-NLO matrix elements and the NNPDF3.0 NLO~\cite{Ball:2014uwa} PDF set. 
-Showering is performed using {\pythia}~8.210 and the A14 tune.
+Samples of $\ttbar V$ and $\ttbar H$ events are generated with {\amcatnlo}~2.2.1, using NLO matrix elements and the NNPDF3.0 NLO PDF set,
+and interfaced to {\pythia}~8.210 with the NNPDF2.3 LO PDF set and the A14 tune.
 The $\ttbar V$ samples are normalised to the NLO cross section computed with {\amcatnlo}.
-The $\ttbar H$ sample is normalised using the NLO cross section~\cite{Raitio:1978pt,Beenakker:2002nc,Dawson:2003zu,Yu:2014cka,Frixione:2015zaa}  
-and the Higgs boson decay branching ratios calculated using \textsc{Hdecay}.
+The $\ttbar H$ sample is normalised using the NLO cross section~\cite{Raitio:1978pt,Beenakker:2002nc,Dawson:2003zu,Yu:2014cka,Frixione:2015zaa}.
 
@@
 
-The fake $\tauhad$ background prediction in a given SR is modelled by the fake template derived from its corresponding CR, which is a data-driven method.
-The fake template is defined as the data subtracted by the contributions from the simulated backgrounds with real $\tauhad$ candidates.
+The fake $\tauhad$ background prediction in a given SR is modelled by the distribution (referred to as ``fake $\tauhad$ template") derived from data in the corresponding CR.
+The fake $\tauhad$ template is defined as the data distribution from which the contributions from the simulated backgrounds with real $\tauhad$ candidates are subtracted.
 In the $\lephad$ channel, simulation studies indicate that the fake $\tauhad$ background composition is consistent between the SR and the CR, and dominated by $\ttbar$.
-In this case, the fake template is simply normalised to the fake $\tauhad$ background yield in the SR and taken as the fake $\tauhad$ background prediction.
 In the $\hadhad$ channel, the fake $\tauhad$ background is expected to be dominated by multijet production.
-However, simulation studies indicate that the fraction of $\ttbar$ yield is higher in the SR than in the CR.
-Therefore, an appropriate amount of simulated $\ttbar$ events with fake $\tauhad$ candidates in the CR are added to the fake template to match the fake $\tauhad$ background composition in the SR.
-This modified fake template is then normalised to the expected fake $\tauhad$ background yield in the SR, as sone in the case of the $\lephad$ channel.
+However, simulation studies indicate that the contribution of $\ttbar$ events to the fake $\tauhad$ background is higher in the SR than in the CR.
+Therefore, an appropriate amount of simulated $\ttbar$ events with fake $\tauhad$ candidates in the CR is added to the fake $\tauhad$ template to match the fake $\tauhad$ background composition in the SR.
+In both the $\lephad$ and $\hadhad$ channels, the fake $\tauhad$ template in each SR is initially normalised to the estimated fake $\tauhad$ background yield, 
+defined as the data yield minus the contributions from the simulated backgrounds with real $\tauhad$ candidates (i.e. assuming no signal contribution).
+During the statistical analysis, the normalisation of the fake $\tauhad$ background in each SR will be allowed to vary unconstrained in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.
 

### 2018-08-17 ANA-TOPQ-2017-07-PAPER-auxmat.tex
updated bb postfit tables and added bb aux material plots

\part*{Auxiliary material}
\addcontentsline{toc}{part}{Auxiliary material}
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[htbp]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_lep0_pt.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_met.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_hthad.eps}} 
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_mbb_mindR.eps}} \\ 
\caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
distributions in the (4j, 2b) region (prior to the application of the cut on the LH discriminant above 0.6) before performing the fit to data (``Pre-Fit''). 
The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
the jets ($\hthad$), and (d) the invariant mass distribution of the two $b$-tagged jets with lowest 
$\Delta R$ separation ($\mbb$).
The small contributions from $\ttbar V$, $\ttbar H$, single top, $W/Z$+jets, diboson, and multijet backgrounds are combined 
into a single background source referred to as ``Non-$\ttbar$''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The last bin in all figures contains the overflow.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
The blue triangles indicate points that are outside the vertical range of the figure. 
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
which is determined via a likelihood fit to data.}}
\label{fig:Hbb_extravars_4j2b}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[htbp]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_lep0_pt.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_met.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_hthad.eps}} 
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_mbb_mindR.eps}} \\ 
\caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
distributions in the (4j, 3b) region before performing the fit to data (``Pre-Fit''). 
The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
the jets ($\hthad$), and (d) the invariant mass distribution of the two $b$-tagged jets with lowest 
$\Delta R$ separation ($\mbb$).
The small contributions from $\ttbar V$, $\ttbar H$, single top, $W/Z$+jets, diboson, and multijet backgrounds are combined 
into a single background source referred to as ``Non-$\ttbar$''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The last bin in all figures contains the overflow.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
The blue triangles indicate points that are outside the vertical range of the figure. 
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
which is determined via a likelihood fit to data.}}
\label{fig:Hbb_extravars_4j3b}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[htbp]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_lep0_pt.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_met.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_hthad.eps}} 
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_mbb_mindR.eps}} \\ 
\caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
distributions in the (5j, 3b) region before performing the fit to data (``Pre-Fit''). 
The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
the jets ($\hthad$), and (d) the invariant mass distribution of the two $b$-tagged jets with lowest 
$\Delta R$ separation ($\mbb$).
The small contributions from $\ttbar V$, $\ttbar H$, single top, $W/Z$+jets, diboson, and multijet backgrounds are combined 
into a single background source referred to as ``Non-$\ttbar$''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The last bin in all figures contains the overflow.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
The blue triangles indicate points that are outside the vertical range of the figure. 
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
which is determined via a likelihood fit to data.}}
\label{fig:Hbb_extravars_5j3b}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-08-17 sections/statistical_analysis.tex
updated bb postfit tables and added bb aux material plots

@@
 All nuisance parameters are implemented in the likelihood function as Gaussian or log-normal constraints, with the exception of a few parameters 
-that control the normalisation of the some of the background components (e.g. the \ttbin\ background in the case of the $\Hbb$ search) 
-and are treated as free parameters in the fit.
+that control the normalisation of the some of the background components (e.g. the \ttbin\ background in the case of the $\Hbb$ search), which 
+are treated as free parameters in the fit.
 
@@
 The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
-A related statistic is used to determine the probability that the observed data are compatible with the background-only hypothesis (i.e.~the discovery test)  
+A related statistic is used to determine the compatibility of the observed data with the background-only hypothesis (i.e.~the discovery test)  
 by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
-The $p$-value (referred to as $p_0$) representing the probability of the data being compatible with the 
-background-only hypothesis is estimated by integrating
-the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, above the observed value of $q_0$ in the data.
+The $p$-value (referred to as $p_0$) representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
+the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
+above the observed value of $q_0$ in the data. 
 %The observed $p_0$-value is checked for each explored signal scenario.

### 2018-08-17 sections/strategy_Htautau.tex
updated bb postfit tables and added bb aux material plots

@@
 added on top of the background prediction.
-The last bin in all figures contains the overflow.
+The first and the last bins in all figures contain the underflow and overflow respectively.
 The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
-The hashed area represents the total uncertainty of the background.}
+The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
+which is determined via a likelihood fit to data.}
 \label{fig:BDT_inputs_lephad}
@@
 added on top of the background prediction.
-The last bin in all figures contains the overflow.
+The first and the last bins in all figures contain the underflow and overflow respectively.
 The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
-The blue triangles indicate points that are outside the vertical range of the figure. 
-The hashed area represents the total uncertainty of the background. } 
+The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
+which is determined via a likelihood fit to data.} 
 \label{fig:BDT_inputs_hadhad}

### 2018-08-17 ANA-TOPQ-2017-07-PAPER-metadata.tex
update to metadata

@@
 % Comment deadline
-% \AtlasCoverCommentsDeadline{DD Month 2016}
+\AtlasCoverCommentsDeadline{2 September 2018}
 
@@
 Yulia Rodina, Yanjun Tu,  Lo\"ic Val\'ery, \\ Tal Van Daalen, Jia-Shian Wang, Daiki Yamaguchi; \\
-$H \to \tau^+\tau^-$: Xin Chen, Antonio De Maria, Boyang Li, Ligang Xia; \\
+$H \to \tau^+\tau^-$: Xin Chen, Antonio De Maria, Boyang Li, Ligang Xia, Gang Zhang; \\
 Combination: Peter Onyisi, Harish Potti}

### 2018-08-17 ANA-TOPQ-2017-07-PAPER-auxmat.tex
v0.5

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\begin{center}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_lephad_3j_FR.eps}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_lephad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_lephad_3j_FR.eps}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_lephad_4j_FR.eps}} \\
+\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of some of the most
+important BDT input variables in the $\lephad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
+$x_{1}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
+$x_{2}^{\text{fit}}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
+The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
+$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
+The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
+added on top of the background prediction.
+The first and the last bins in all figures contain the underflow and overflow respectively.
+The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
+The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
+which is determined via a likelihood fit to data.}
+\label{fig:BDT_inputs_lephad_2}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\begin{center}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_hadhad_3j_FR.eps}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_hadhad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_hadhad_3j_FR.eps}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_hadhad_4j_FR.eps}} \\
+\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
+important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
+$x_{2}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
+$p_{\text{T},2}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
+The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
+$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
+The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
+added on top of the background prediction.
+The first and the last bins in all figures contain the underflow and overflow respectively.
+The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
+The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
+which is determined via a likelihood fit to data.} 
+\label{fig:BDT_inputs_hadhad_2}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-08-17 sections/strategy_Htautau.tex
v0.5

@@
 %The separate training exploits differences in event kinematics across SRs.  
-In the training, only the $\Hq$ signal is used against the total SM background, including both real and fake $\tauhad$ contributions.
+In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
+whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
 A large set of potential variables was investigated in each SR separately, and only those variables that led to an improved discrimination
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_hadhad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_4j_FR.eps}} \\
 \caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
@@
 $m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
-(c) $x_{1}^{\text{fit}}$ in the ($\hadhad$, 3j)  region, and (d) $x_{2}^{\text{fit}}$ in the ($\hadhad$, $\geq$4j) region.
+$x_{1}^{\text{fit}}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
 The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into

### 2018-08-28 sections/detector.tex
first set of simple comments

@@
 Within the region $|\eta|< 3.2$, electromagnetic (EM) calorimetry is provided by barrel and 
-endcap high-granularity lead/liquid-argon (LAr) electromagnetic calorimeters,
+endcap high-granularity lead/liquid-argon (LAr) sampling calorimeters,
 with an additional thin LAr presampler covering $|\eta| < 1.8$,
@@
 of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking 
-chambers located in a toroidal field of approximately 0.5~T and 1~T in the central and endcap regions of ATLAS, respectively. 
-The muon spectrometer is also instrumented with separate trigger chambers covering $|\eta|<2.4$.
+chambers located in a toroidal field of approximately 0.5~T and 1~T in the central and endcap regions, respectively. 
+The muon spectrometer is instrumented with separate trigger chambers covering $|\eta|<2.4$.
 A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based Level-1 trigger followed by 
-a software-based High-Level Trigger (HLT), is used to reduce the event rate to a maximum of around 1 kHz for offline storage.
+a software-based High-Level Trigger, is used to reduce the event rate to a maximum of around 1 kHz for offline storage.

### 2018-08-28 sections/introduction.tex
first set of simple comments

@@
 measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, such interactions would manifest themselves as FCNC top quark decays, $t\to H q$.  
-In the Standard Model (SM), such decays are extremely suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
+In the Standard Model (SM), such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
 interactions are forbidden at the tree level and even suppressed at higher-orders in the perturbative expansion due to the 
@@
 These upper limits are derived under the assumption of $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ under the
-assumption of $\BR(t\to Hc)=0$. In addition, the CMS Collaboration has performed a search using  
+assumption of $\BR(t\to Hc)=0$. The CMS Collaboration has performed a search using  
 $H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} using 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 

### 2018-08-28 sections/objects.tex
first set of simple comments

@@
 A track-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$, where
-the sum includes all tracks (excluding the lepton candidate itself) within the cone defined by $\Delta R<R_{\textrm{cut}}$ about the %axis
+the scalar sum includes all tracks (excluding the lepton candidate itself) within the cone defined by $\Delta R<R_{\textrm{cut}}$ about the %axis
 direction of the lepton.  The value of $R_{\textrm{cut}}$ is the smaller of $r_{\textrm{min}}$ and $10~\gev/\pt^\ell$, where

### 2018-08-29 sections/objects.tex
adding new textual changes

@@
 The event reconstruction is affected by multiple $pp$ collisions in a single bunch crossing and by collisions
-in neighboring bunch crossings, referred to as ``pileup''. 
+in neighbouring bunch crossings, referred to as ``pile-up''. 
 Interaction vertices from the $pp$ collisions are reconstructed from at least two tracks 
@@
 makes $\pt$-dependent requirements on $I_R/\pt^\ell$. Additionally, the $\Htautau$ search requires leptons to
-satisfy a calorimeter-based isolation criterion: the sum of the transverse energy of
-topological clusters within the cone defined by $\Delta R<0.2$ around the lepton, after subtracting the contributions
+satisfy a calorimeter-based isolation criterion: the sum of the transverse energy within a cone of
+$\Delta R<0.2$ around the lepton, after subtracting the contributions
 from pile-up and the energy deposit of the lepton itself, is required to be less than a $\pt$-dependent 

### 2018-08-29 sections/signal_background_modeling.tex
adding new textual changes

@@
 utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
-To model the effects of pileup, events from minimum-bias interactions are generated using the {\pythia}~8.186~\cite{Sjostrand:2007gs} 
+To model the effects of pile-up, events from minimum-bias interactions are generated using the {\pythia}~8.186~\cite{Sjostrand:2007gs} 
 event generator and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
@@
 The CR selection requirements are analogous to those used to define the different SRs, except that the leading (trailing) $\tauhad$ candidate
-in the $\lephad$ ($\hadhad$) channel is required to be of loose-not-medium quality, and the requirement on its charge is dropped.
+in the $\lephad$ ($\hadhad$) channel is required to be of loose-not-medium quality, and the requirement on its charge is removed.
 

### 2018-08-29 sections/statistical_analysis.tex
adding new textual changes

@@
 All nuisance parameters are implemented in the likelihood function as Gaussian or log-normal constraints, with the exception of a few parameters 
-that control the normalisation of the some of the background components (e.g. the \ttbin\ background in the case of the $\Hbb$ search), which 
+that control the normalisation of some background components (e.g. the \ttbin\ background in the case of the $\Hbb$ search), which 
 are treated as free parameters in the fit.

### 2018-08-29 sections/strategy_Hbb.tex
adding new textual changes

@@
 at least four $b$-tagged jets are dominated by \ttbin. Intermediate compositions are found in regions with exactly three 
-$b$-tagged jets.  Most of the $\ttbar$+light-jets background in the these regions has a charm jet from the hadronic $W$ boson 
+$b$-tagged jets.  Most of the $\ttbar$+light-jets background in these regions has a charm jet from the hadronic $W$ boson 
 decay  being $b$-tagged, in addition to the two $b$-jets from the top quark decays.

### 2018-08-29 sections/systematic_uncertainties.tex
adding new textual changes

@@
 all processes estimated from the simulation. It is derived, following a methodology similar to that detailed in Ref.~\cite{Aaboud:2016hhf}, 
-from a preliminary calibration of the luminosity scale using $x$--$y$ beam-separation scans performed in August 2015 and May 2016.
+from a calibration of the luminosity scale using $x$--$y$ beam-separation scans performed in August 2015 and May 2016.
 
@@
 and resolution, and the efficiency to pass the JVT requirements. 
-The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pileup treatment, 
+The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pile-up treatment, 
 is split into 21 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}.
@@
 comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}
-(it is assumed that two jets come from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
+(it is assumed that two jets originate from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
 Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the selected jet multiplicity,  

### 2018-08-29 sections/objects.tex
fixing references according to Ceradini comments

@@
 This soft term is calculated from inner-detector tracks matched to the selected primary vertex to make it more resilient to
-contamination from pile-up interactions~\cite{Aad:2016nrq,ATL-PHYS-PUB-2015-027}.
+contamination from pile-up interactions~\cite{run_2_met,ATL-PHYS-PUB-2015-027}.

### 2018-08-29 sections/data_presel.tex
fixing textual TLC comments

@@
 For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
-along with triggers with a 60~\gev\ threshold and no isolation requirement, and with a 120 (140)~\gev\ threshold with looser identification criteria.
+along with triggers with a 60~\gev\ threshold and no isolation requirement, and with a 120 (140)~\gev\ threshold 
+with looser identification criteria and no isolation requirement.
 For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.

### 2018-08-29 sections/objects.tex
fixing textual TLC comments

@@
 
-Hadronically decaying $\tau$-lepton ($\tauhad$) candidates are reconstructed from clusters in the calorimeters and
+Hadronically decaying $\tau$-lepton ($\tauhad$) candidates are reconstructed from energy clusters in the calorimeters and
 associated inner detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,

### 2018-08-29 sections/signal_background_modeling.tex
fixing textual TLC comments

@@
 
-All simulated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
+All generated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
 utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 

### 2018-08-29 sections/conclusion.tex
non simple textual comments part 1

@@
 yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
-and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$) respectively.
+and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming that $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$ respectively.
 The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.064 (0.055) respectively. 

### 2018-08-29 sections/introduction.tex
non simple textual comments part 1

@@
 An interesting possibility is the presence of flavour-changing neutral current (FCNC) interactions 
-between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$). Since the Higgs boson is lighter than the top quark, with a 
-measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, such interactions would manifest themselves as FCNC top quark decays, $t\to H q$.  
+between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$). Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl}, 
+%with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
+such interactions would manifest themselves as FCNC top quark decays, $t\to H q$.  
 In the Standard Model (SM), such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
@@
 
-The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
+%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
+The searches presented in this paper are focused on fermionic decay modes.
 Therefore, they help to complete the programme of searches for $t \to Hq$ decays at the ATLAS experiment based on $pp$ collision 
@@
 of which are identified with high purity as originating from the hadronisation of $b$-quarks. 
-The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
+%The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
+The $\Htautau$ search selects events with two $\tau$-lepton candidates of which at least one is decaying hadronically, as well as multiple jets.
+
+%two of which originating from hadronic $W$ decays. 
 Both searches employ different multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 

### 2018-09-01 ANA-TOPQ-2017-07-PAPER-metadata.tex
v1.0
v1.0 with correct deadline for comments
toronto textual comments part 1

@@
 % Comment or remove in final version.
-\AtlasVersion{0.5}
+\AtlasVersion{1.0}
 % Abstract - % directly after { is important for correct indentation
@@
 CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
-Two analyses are performed that search for top quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
+Two analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
 and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
@@
 The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.064 (0.055) respectively. 
-%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
 These are the most restrictive direct bounds on $tqH$ interactions measured so far.
@@
 % Comment deadline
-\AtlasCoverCommentsDeadline{2 September 2018}
+\AtlasCoverCommentsDeadline{3 September 2018}
 

### 2018-09-01 sections/introduction.tex
toronto textual comments part 1

@@
 %with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
-such interactions would manifest themselves as FCNC top quark decays, $t\to H q$.  
+such interactions would manifest themselves as FCNC top-quark decays, $t\to H q$.  
 In the Standard Model (SM), such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
-interactions are forbidden at the tree level and even suppressed at higher-orders in the perturbative expansion due to the 
+interactions are forbidden at the tree level and even suppressed at higher orders in the perturbative expansion due to the 
 Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.  As a result, the SM predictions for the $t \to Hq$ branching 
@@
 %The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
-The searches presented in this paper are focused on fermionic decay modes.
+The searches presented in this paper are focussed on fermionic decay modes.
 Therefore, they help to complete the programme of searches for $t \to Hq$ decays at the ATLAS experiment based on $pp$ collision 

### 2018-09-01 sections/strategy_Hbb.tex
non simple textual comments part 1
toronto textual comments part 1

@@
 before the fit to data (``Pre-Fit"). Backgrounds are normalised to their nominal cross sections discussed in Section~\ref{sec:simulations}.
-The small contributions from $W/Z$+jets,  single top, diboson and multijet backgrounds are combined into a single background source 
+The small contributions from $W/Z$+jets,  single-top-quark, diboson and multijet backgrounds are combined into a single background source 
 referred to as ``Non-$\ttbar$''. 
@@
 discriminating variable between signal and background needs to be constructed in order to improve the sensitivity of the search.
-Since both signal and background result from the $\ttbar$ decay, there are few experimental handles available to discriminate
-between them. The most prominent features are the different resonances present in the decay (i.e. the Higgs boson in the case 
+Since both signal and background result from the $\ttbar$ decay, 
+their discrimination is a challenge and it is based on a few experimental attributes.  
+%there are few experimental handles available to discriminate between them. 
+The most prominent features are the different resonances present in the decay (i.e. the Higgs boson in the case 
 of the $\Hq$ signal and a hadronically decaying $W$ boson in the case of the $\ttbar \to WbWb$ background), and the different flavour of the 

### 2018-09-01 sections/strategy_Htautau.tex
toronto textual comments part 1

@@
 $p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
-The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
 a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
@@
 $x_{1}^{\text{fit}}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
-The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
 a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 

### 2018-09-01 sections/systematic_uncertainties.tex
toronto textual comments part 1

@@
 by comparing events produced by {\powheg} interfaced to {\pythia}~6 or {\herwigpp}.
-These uncertainties are treated as fully correlated among single-top production processes, but uncorrelated with the
+These uncertainties are treated as fully correlated among single-top-quark production processes, but uncorrelated with the
 corresponding uncertainty in the $\ttbar$+jets background.

### 2018-09-02 sections/data_presel.tex
toronto textual part 2

@@
 Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
-with higher-threshold triggers without isolation requirements to give maximum efficiency. 
+with higher-threshold triggers without isolation requirements to ensure maximum efficiency. 
 For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
@@
 the trigger and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
-data taking period). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
+data taking conditions). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
 Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
@@
 \caption{\small{Summary of preselection requirements for the $\Hbb$ and $\Htautau$ searches. 
-The leading and sub-leading $\tauhad$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
+The leading and trailing $\tauhad$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
 \label{tab:preselection}

### 2018-09-02 sections/signal_background_modeling.tex
toronto textual part 2

@@
 in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
-with the MSTW 2008 68\% CL NNLO, CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3 5f FFN~\cite{Ball:2012cx} PDF sets.
+with the MSTW 2008 68\% CL NNLO, CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3 5F FFN~\cite{Ball:2012cx} PDF sets.
 
@@
 the ``diagram removal'' scheme~\cite{Frixione:2005vw}.
-The parton shower, hadronisation and the underlying event are modelled using {\pythia}~6.428 with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set 
+The parton shower, hadronisation and the underlying event are modelled using {\pythia}~6.428~\cite{Sjostrand:2006za} 
+with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set 
 in combination with the Perugia 2012 tune~\cite{Skands:2010ak}.
@@
 the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
-is adopted for some of the samples used to estimate systematic uncertainties.
+is adopted for some of the samples.
+% used to estimate systematic uncertainties.
 Simulated events are processed through the same reconstruction software as the data, and corrections are applied so that the object identification 

### 2018-09-02 sections/strategy_Hbb.tex
toronto textual part 2

@@
 However, the use of the 60\% $b$-tagging operating point, characterised by a low mistag rate for
-charm and light jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity spectrum,
+charm and light jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity distribution,
 with a very small fraction of events having four or more $b$-tagged jets.

### 2018-09-02 sections/strategy_Htautau.tex
toronto textual part 2

@@
 %The separate training exploits differences in event kinematics across SRs.  
+%draft 1 version
+%In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
+%whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
 In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
-whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
+elsewhere the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account.
+
 A large set of potential variables was investigated in each SR separately, and only those variables that led to an improved discrimination

### 2018-09-02 sections/data_presel.tex
more textual comments

@@
 For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
-along with triggers with a 60~\gev\ threshold and no isolation requirement, and with a 120 (140)~\gev\ threshold 
-with looser identification criteria and no isolation requirement.
+along with triggers with a 60~\gev\ threshold and no isolation requirements, and with a 120 (140)~\gev\ threshold 
+with looser identification criteria and no isolation requirements.
 For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.

### 2018-09-02 sections/strategy_Hbb.tex
more textual comments

--- 2018-09-01 sections/strategy_Hbb.tex
@@
 Additional jets can also be present because of initial- or final-state radiation.
-However, the use of the 60\% $b$-tagging operating point, characterised by a low mistag rate for
-charm and light jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity spectrum,
+However, the use of the 60\% $b$-tagging efficiency operating point, characterised by a low mistag rate for
+charm and light jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity distribution,
 with a very small fraction of events having four or more $b$-tagged jets.

### 2018-09-02 sections/objects.tex
toronto textual comments part 1
more textual comments and bib formatting

@@
 separation between electrons and jets.
+
 Muon candidates~\cite{Aad:2016jkr} are reconstructed by matching track segments in %the various
@@
 The efficiency for the leptons with a certain $\pt$ is $(0.1143*\pt[\GeV]+92.14)\%*(0.1143*\pt[\GeV]+92.14)\%$.
-
-Candidate jets are reconstructed with the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq,Cacciari:2011ma} with a
-radius parameter $R=0.4$, using topological clusters~\cite{Aad:2016upy} 
-built from energy deposits in the calorimeters calibrated to the electromagnetic scale. 
+%draft 1 version
+%Candidate jets are reconstructed with the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq,Cacciari:2011ma} with a
+%radius parameter $R=0.4$, using topological clusters~\cite{Aad:2016upy} 
+%built from energy deposits in the calorimeters calibrated to the electromagnetic scale. 
+Candidate jets are reconstructed with the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq} with a
+radius parameter $R=0.4$, as implemented in the \fastjet\ package~\cite{Cacciari:2011ma}.  
+Jet reconstruction in the calorimeter starts from topological clustering~\cite{Aad:2016upy} of individual calorimeter cells calibrated to the electromagnetic scale. 
 The reconstructed jets are then calibrated to the particle level by the application of a jet energy scale 

### 2018-09-02 sections/conclusion.tex
more small changes

@@
 Two analyses are performed searching for $\ttbar \to WbHq$ production, and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, respectively.  
-The $\Hbb$ search selects events with one isolated light lepton from the $W \to \ell\nu$ decay, and multiple jets, with several 
+The $\Hbb$ search selects events with one isolated charged light lepton from the $W \to \ell\nu$ decay, and multiple jets, with several 
 of them being identified with high purity as originating from the hadronisation of $b$-quarks. 

### 2018-09-02 sections/data_presel.tex
more small changes

@@
 Events selected by the $\Hbb$ search are recorded with a single-electron or single-muon trigger and 
-are required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger.  
+are required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton triggering the event.  
 Furthermore, at least four jets are required, of which at least two must be $b$-tagged.
@@
 and are required to have exactly one selected electron or muon and at least one $\tauhad$ candidate. 
-The selected light lepton (electron or muon) is required to match, with $\Delta R < 0.15$, the lepton reconstructed by 
-the trigger and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
+The selected charged light lepton is required to match, with $\Delta R < 0.15$, the lepton triggering the event and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and
 data taking conditions). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
 Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
-no selected light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
+no selected charged light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
 In addition, in both channels, at least three jets and exactly one $b$-tagged jet are required.
@@
 Trigger & single-lepton trigger & single-lepton trigger & ditau trigger  \\
-Light leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
+Charged light leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
 Tau leptons & -- & $\geq$1 $\tauhad$ & $\geq$2 $\tauhad$ \\

### 2018-09-02 sections/introduction.tex
more small changes

@@
 and excellent diphoton mass re\-so\-lu\-tion. 
-Searches targeting signatures with two same-charge light leptons (electrons or muons) or three light leptons, generically referred to as ``multileptons",
+Searches targeting signatures with two same-charge light leptons (electrons or muons) or three charged light leptons, generically referred to as ``multileptons",
 are able to exploit a significantly larger branching ratio for the Higgs 
@@
 which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
-The $\Hbb$ search selects events with one isolated light lepton from the $W \to \ell\nu$ decay, and multiple jets, several 
+The $\Hbb$ search selects events with one isolated charged light lepton from the $W \to \ell\nu$ decay, and multiple jets, several 
 of which are identified with high purity as originating from the hadronisation of $b$-quarks. 

### 2018-09-02 sections/signal_background_modeling.tex
more editing

@@
 initial and final state radiation, referred to as the ``tune'', is used.
-The signal sample is normalised to the same cross section as used for the $t\bar{t}\to WbWb$ sample (see discussion below) and
+The signal sample is normalised to the same total cross section as used for the $t\bar{t}\to WbWb$ sample (see discussion below) and
 assuming a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
@@
 in the following) using the CT10 PDF set.  This reweighting is performed in such a way that the inter-normalisations of the \ttbin\ categories are at NLO accuracy, 
-while preserving the nominal \ttbin\ cross section of the nominal $\ttbar$ sample. This reweighting is applied to the alternative $\ttbar$ samples as well.
+while preserving the nominal \ttbin\ cross section of the nominal $\ttbar$ sample. 
+%This reweighting is applied to the alternative $\ttbar$ samples as well.
+This reweighting is also applied to the alternative $\ttbar$ samples that are used to study systematic uncertainties (see section~\ref{sec:syst_bkgmodeling}).
 

### 2018-09-03 sections/conclusion.tex
Fixed typo on tuH coupling in abstract and conclusions

@@
 and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming that $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$ respectively.
-The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.064 (0.055) respectively. 
+The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055) respectively. 
 %Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.

### 2018-09-04 sections/signal_background_modeling.tex
trigger-matching, fake estimate for tautau

@@
 
-This background is estimated directly from data by defining control regions (CR) enriched in fake $\tauhad$ candidates via loosened $\tauhad$ requirements.
+This background is estimated directly from data by defining control regions (CR) enriched in fake $\tauhad$ candidates via loosened $\tauhad$ requirements or flipped charge.
 These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
 The CR selection requirements are analogous to those used to define the different SRs, except that the leading (trailing) $\tauhad$ candidate
-in the $\lephad$ ($\hadhad$) channel is required to be of loose-not-medium quality, and the requirement on its charge is removed.
+in the $\lephad$ ($\hadhad$) channel is required to fail the medium tau identification but pass the loose one, or the two tau candidates have the same charge.
 

### 2018-09-04 ANA-TOPQ-2017-07-PAPER-metadata.tex

@@
 and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), respectively.
-The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.064 (0.055) respectively. 
+The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055) respectively. 
 These are the most restrictive direct bounds on $tqH$ interactions measured so far.

### 2018-09-06 sections/signal_background_modeling.tex
little fixes

--- 2018-09-02 sections/signal_background_modeling.tex
@@
 %This reweighting is applied to the alternative $\ttbar$ samples as well.
-This reweighting is also applied to the alternative $\ttbar$ samples that are used to study systematic uncertainties (see section~\ref{sec:syst_bkgmodeling}).
+This reweighting is also applied to the alternative $\ttbar$ samples that are used to study systematic uncertainties (see Section~\ref{sec:syst_bkgmodeling}).
 

### 2018-09-06 sections/objects.tex
more small changes

@@
 %-------------------------------------------------------------------------------
-\section{Object reconstruction}
+\section{Event reconstruction}
 \label{sec:objects}
@@
 while the $\Htautau$ search uses jets with $\pt > 30~\gev$ and $|\eta| < 4.5$.
+Jet four-momenta are corrected for pile-up effects using the jet-area method~\cite{Cacciari:2008gn}.
+
 Quality criteria are imposed to reject events that contain any jets arising from non-collision sources
@@
 
-Overlaps between candidate objects are removed sequentially, following this order: muons, electrons, $\tauhad$ (only for the $\Htautau$ search), and jets. 
-In the $\Hbb$ search, firstly, electron candidates that lie within $\Delta R = 0.01$ of a muon 
-candidate are removed to suppress contributions from muon bremsstrahlung.  Overlaps between electron and jet candidates are resolved 
+In the $\Hbb$ search, overlaps between candidate objects are removed sequentially, following this order: muons, electrons and jets.
+Firstly, electron candidates that lie within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung.
+Overlaps between electron and jet candidates are resolved
 next, and finally, overlaps between remaining jet candidates and muon candidates are removed.
 Clusters from identified electrons are not excluded during jet reconstruction.
-In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron is discarded. If 
-the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
+In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron is discarded.
+If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
 The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
@@
 if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
-In the $\Htautau$ search, a fixed cone size of $\Delta R = 0.2$ is used to determine the overlap between candidate objects, and only the
-highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the analysis channel, see Section~\ref{sec:data_presel}) are considered 
-to resolve their overlap with jets. 
+In the $\Htautau$ search, the objects are removed with the following sequence: if two electrons have overlapped second-layer cluser, or shared tracks, the electron with lower $\pt$ is removed; $\tauhad$ within a $\Delta R=0.2$ cone of an electron or muon are removed; if a muon sharing an ID track with an electron and the muon is calo-tagged, the muon is removed, otherwise the electron is removed; jets within a $\Delta R=0.2$ cone of an electron are removed; electrons within a $\Delta R=0.4$ cone of a jet are removed; when a muon ID track is ghost associated to a jet or within a $\Delta R=0.2$ cone of a jet, the jet is removed if it has less than 3 tracks with $\pt>500$ MeV or has a relative small $\pt$ ($\pt^{\mu}>0.5\pt^{\text{jet}} \text{ and } \pt^{\mu}>0.7[\text{the scalar sum of the } \pt \text{'s of the jet tracks with } \pt>500$ MeV]); muons within a $\Delta R=0.4$ cone of a jet are removed; jets within a $\Delta R=0.2$ cone of the leading $\tauhad$ ($\lephad$), or with the two leading $\tauhad$'s ($\hadhad$), are removed.
+
 %firstly, the electron within a ${\Delta}R = 0.2$ cone of muons are excluded, then the $\tau_{had}$'s or jets within a ${\Delta}R = 0.2$ cone of an electron or muon are excluded.

### 2018-09-06 sections/objects.tex
simple textual changes

@@
 $\pt >20~\gev$ and $|\eta|<2.5$ in simulated $\ttbar$ events. In contrast, the $\Hbb$ search employs a tighter $b$-tagging requirement, 
-corresponding to an average efficiency of 60\% to tag a $b$-quark jet, and light-jet and charm-jet rejection factors of 1539 and 34, respectively.
+corresponding to an average efficiency of 60\% to tag a $b$-quark jet, and light-jet and charm-jet rejection factors of 1538 and 34, respectively.
 

### 2018-09-06 sections/statistical_analysis.tex
simple textual changes

@@
 The $p$-value (referred to as $p_0$) representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
-the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
+%the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
+the distribution of $q_0$ based on the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
 above the observed value of $q_0$ in the data. 

### 2018-09-07 sections/data_presel.tex
simple textual changes
little changes I forgot to plug in

@@
 with looser identification criteria and no isolation requirements.
-For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
+%For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
+For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev.
 In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.
@@
 no selected charged light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
-In addition, in both channels, at least three jets and exactly one $b$-tagged jet are required.
+In addition, in both ditau channels, trigger matching for $\tauhad$ candidates, at least three jets and exactly one $b$-tagged jet are required.
 

### 2018-09-07 sections/objects.tex
little changes I forgot to plug in

@@
 The missing transverse momentum $\mpt$ (with magnitude $\met$) is defined as the negative vector sum of the 
-$\pt$ of all selected and calibrated objects in the event, including a term to account for energy from soft particles 
+$\pt$ of all selected and calibrated objects in the event, including a term to account for momentum from soft particles 
 in the event which are not associated with any of the selected objects. 

### 2018-09-08 sections/conclusion.tex
Implemented remaining replies to CDS comments from Jason Nielsen

@@
 No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
+In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
+are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$ respectively.
+In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
+are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$ respectively.
 The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 

### 2018-09-08 sections/data_presel.tex
Implemented remaining replies to CDS comments from Jason Nielsen

@@
 no selected charged light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
-In addition, in both ditau channels, trigger matching for $\tauhad$ candidates, at least three jets and exactly one $b$-tagged jet are required.
+In addition, in both $\Htautau$ search channels, trigger matching for $\tauhad$ candidates, at least three jets and exactly one $b$-tagged jet are required.
 

### 2018-09-08 sections/introduction.tex
little changes I forgot to plug in
Implemented remaining replies to CDS comments from Jason Nielsen

@@
 %with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
-such interactions would manifest themselves as FCNC top-quark decays, $t\to H q$.  
+such interactions would manifest themselves as FCNC top-quark decays~\cite{Agashe:2013hma}, $t\to H q$.  
 In the Standard Model (SM), such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
@@
 the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling. 
-See Ref.~\cite{Agashe:2013hma} for a review.
+%See Ref.~\cite{Agashe:2013hma} for a review.
 %\textbf{Update a bit above paragraph mentioning more recent models.}
@@
 The $\Htautau$ search selects events with two $\tau$-lepton candidates of which at least one is decaying hadronically, as well as multiple jets. 
+The latter requirement is aimed at selecting events with a hadronically-decaying $W$ boson, since this allows an improved reconstruction of the
+event kinematics.
 

### 2018-09-08 sections/signal_background_modeling.tex
Implemented remaining replies to CDS comments from Jason Nielsen

@@
 The signal sample is normalised to the same total cross section as used for the $t\bar{t}\to WbWb$ sample (see discussion below) and
-assuming a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
+assuming an arbitrary branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
 The case of both top quarks decaying into $Hq$ is neglected in the analysis given existing upper limits on $\BR(t \to Hq)$ (see Section~\ref{sec:intro}).
@@
 in the following) using the CT10 PDF set.  This reweighting is performed in such a way that the inter-normalisations of the \ttbin\ categories are at NLO accuracy, 
-while preserving the nominal \ttbin\ cross section of the nominal $\ttbar$ sample. 
+while preserving the \ttbin\ cross section of the nominal $\ttbar$ sample. 
 %This reweighting is applied to the alternative $\ttbar$ samples as well.

### 2018-09-08 sections/signal_background_modeling.tex
Implemented remaining replies to CDS comments from Susumu Oda

@@
 The fake $\tauhad$ background prediction in a given SR is modelled by the distribution (referred to as ``fake $\tauhad$ template") derived from data in the corresponding CR.
-The fake $\tauhad$ template is defined as the data distribution from which the contributions from the simulated backgrounds with real $\tauhad$ candidates are subtracted.
+The fake $\tauhad$ template is defined as the data distribution from which the contributions from the simulated backgrounds with real $\tauhad$ candidates, originating primarily from
+$W(\to \tau\nu)$+jets and $Z(\to \tau\tau)$+jets, are subtracted.
 In the $\lephad$ channel, simulation studies indicate that the fake $\tauhad$ background composition is consistent between the SR and the CR, and dominated by $\ttbar$.

### 2018-09-08 sections/introduction.tex
Partial implementation of remaining replies to CDS comments from George Redlinger

@@
 in upper limits of $\BR(t\to Hc)<0.47\%$ and $\BR(t\to Hu)<0.47\%$, in each case neglecting the other decay mode.
+Compared to previous searches, the search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
+$pp \to tH$ production~\cite{Greljo:2014dka}.
 
@@
 data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
-Two analyses are performed searching for $\ttbar \to WbHq$ production, and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, 
-which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
+Two analyses are performed searching for $\ttbar \to WbHq$ production (i.e. $pp \to tH$ production is ignored), and targeting the 
+$H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
 The $\Hbb$ search selects events with one isolated charged light lepton from the $W \to \ell\nu$ decay, and multiple jets, several 

### 2018-09-08 sections/statistical_analysis.tex
Partial implementation of remaining replies to CDS comments from George Redlinger

@@
 the search sensitivity by taking advantage of the highly populated background-dominated bins included in the likelihood fit.
-To verify the improved background prediction, fits under the background-only hypothesis are performed, 
-and differences between the data and the post-fit background prediction are checked 
-using kinematic variables other than the ones used in the fit. 
+%To verify the improved background prediction, fits under the background-only hypothesis are performed, 
+%and differences between the data and the post-fit background prediction are checked 
+%using kinematic variables other than the ones used in the fit. 
 Statistical uncertainties in each bin of the predicted final discriminant distributions due to the limited size of the simulated samples 
@@
 hypothesis, i.e. maximising the likelihood function $L(\mu,\theta)$ over $\mu$ and $\theta$.
+
+The fitting procedure is initially validated through extensive studies using mocked data, defined as the sum of all predicted backgrounds 
+plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
+a signal contamination above 5\% are excluded (referred to as ``blinding cuts").
+In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
+when varying assumptions regarding some of the leading sources of uncertainty. At this point, the blinding cuts in data 
+are removed and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
+nuisance parameters before and after removal of the blinding cuts, which are found to be consistent. In addition, it is verified that the 
+fit is able to correctly determine the strength of a simulated signal injected in the real data.
 

### 2018-09-08 sections/strategy_Hbb.tex
Implemented remaining replies to CDS comments from Christian Johnson
Partial implementation of remaining replies to CDS comments from George Redlinger

@@
 \includegraphics[width=0.55\textwidth]{figures/Hbb/fit/cH_plots/Summary.eps}
-\caption{$\Hbb$ search: Comparison between the data and background prediction for the yields in each of the analysis regions considered 
-before the fit to data (``Pre-Fit"). Backgrounds are normalised to their nominal cross sections discussed in Section~\ref{sec:simulations}.
+\caption{$\Hbb$ search: Comparison between the data and background prediction for the event yields in each of the analysis regions considered 
+before the fit to data (``Pre-Fit"). All events satisfy the preselection requirements, whereas those with exactly two $b$-tagged jets are
+in addition required to have a value of the the likelihood discriminant above 0.6 (see Section~\ref{sec:likelihood_discriminant}).
+Backgrounds are normalised to their nominal cross sections discussed in Section~\ref{sec:simulations}.
 The small contributions from $W/Z$+jets,  single-top-quark, diboson and multijet backgrounds are combined into a single background source 
@@
 \begin{equation}
-L(\mathbf{x}) = \frac{P^\textrm{sig}(\mathbf{x}) }{P^\textrm{sig}(\mathbf{x}) +P^\textrm{bkg}(\mathbf{x}) },
+LH(\mathbf{x}) = \frac{P^\textrm{sig}(\mathbf{x}) }{P^\textrm{sig}(\mathbf{x}) +P^\textrm{bkg}(\mathbf{x}) },
 \label{eq:D}
@@
 \subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep6jin4bin_FcncDiscriminant.eps}} \\
-\caption{$\Hbb$ search: Comparison of the shape of the LH discriminant distribution between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
+\caption{$\Hbb$ search: Comparison of the shape of the LH discriminant distribution after preselection 
+between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
 and the $t\bar{t}\to WbWb$ background (black solid) in several regions considered in the analysis:

### 2018-09-08 sections/strategy_Htautau.tex
more textual comments
Partial implementation of remaining replies to CDS comments from George Redlinger

@@
 %This analysis adopts the event reconstruction strategy developed in Ref.~\cite{Chen:2015nta}, which is briefly summarised in the following. 
-The event reconstruction strategy used~\cite{Chen:2015nta} is summarised in the following.
+%The event reconstruction strategy used~\cite{Chen:2015nta} is summarised in the following.
+The event reconstruction is based on the strategy previously used in~\cite{Chen:2015nta}.
+
 Events with exactly three jets that are compatible with having a fully reconstructed hadronically decaying 
@@
 orthogonal, and that the smaller angle between the tau decay products defines the positive quadrant of the transformed plane. 
-The $\met$ $\phi$ centrality is defined as the sum of the parallel ($\parallel$) and perpendicular ($\perp$) components of the $\mpt$ unit vector in this transformed plane.
-\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
-\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the transverse direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
+The $\met$ $\phi$ centrality is defined as the sum of the $x$- and $y$-components of the $\mpt$ unit vector in this transformed plane.
+%\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
+%\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the transverse direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
+\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector, minus 
+the magnitude of the fitted $\mpt$ vector.
+\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector.
 \item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically-decaying $W$ boson.
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
-\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of some of the most
+\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of some of the most
 important BDT input variables in the $\lephad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_4j_FR.eps}} \\
-\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
+\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of two of the most 
 important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh4j/canv_.eps}} \\
-\caption{$\Htautau$ search: Comparison of the shape of the BDT discriminant distribution between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
+\caption{$\Htautau$ search: Comparison of the shape of the BDT discriminant distribution after preselection between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
 and the total background (black solid) in the different search regions considered:

### 2018-09-09 sections/strategy_Hbb.tex
Implemented remaining replies to CDS comments from George Redlinger

@@
 
+Figure~\ref{fig:Hbb_extravars_4j3b} shows a comparison between data and prediction in the most sensitive analysis region, (4j, 3b), 
+for several kinematic variables associated with the reconstructed lepton, jets, and missing transverse momentum. 
+The distributions shown correspond to the lepton $\pt$, $\met$, the scalar sum of the transverse momenta of 
+the jets, and the invariant mass distribution of the two $b$-tagged jets with lowest $\Delta R$ separation.
+In general, a good description of the data by the background prediction is observed.
+
+Figure~\ref{fig:LHD} compares the shape of the LH discriminant distribution between the $\Hc$ and $\Hu$ signals and the 
+$t\bar{t}\to WbWb$ background in each of the analysis regions considered.
 Since this analysis has higher expected sensitivity to a $\Hc$ signal than to a $\Hu$ signal, and, in order to allow probing 
@@
 decay modes. It was verified that using the $\Hc$ discriminant for the $\Hu$ search does not result in a significant sensitivity loss.
-Figure~\ref{fig:LHD} compares the shape of the LH discriminant distribution between the $\Hc$ and $\Hu$ signals and the 
-$t\bar{t}\to WbWb$ background in each of the analysis regions considered.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[htbp]
+\begin{center}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_lep0_pt.eps}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_met.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_hthad.eps}} 
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_mbb_mindR.eps}} \\ 
+\caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
+distributions in the (4j, 3b) region before performing the fit to data (``Pre-Fit''). 
+The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
+the jets ($\hthad$), and (d) the invariant mass distribution of the two $b$-tagged jets with lowest 
+$\Delta R$ separation ($\mbb$).
+The small contributions from $\ttbar V$, $\ttbar H$, single top, $W/Z$+jets, diboson, and multijet backgrounds are combined 
+into a single background source referred to as ``Non-$\ttbar$''. 
+The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
+added on top of the background prediction.
+The last bin in all figures contains the overflow.
+The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
+The blue triangles indicate points that are outside the vertical range of the figure. 
+The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
+which is determined via a likelihood fit to data.}}
+\label{fig:Hbb_extravars_4j3b}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2018-09-09 ANA-TOPQ-2017-07-PAPER-metadata.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

@@
 CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
-Two analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
+Two complementary analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
 and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
-They exploit either the high multiplicity of $b$-quark jets, or the presence of hadronically decaying tau leptons, and employ different
-multivariate techniques to separate the signal from the background, which is dominated by $t\bar{t}$ production.
+The high multiplicity of $b$-quark jets, or the presence of hadronically decaying tau leptons, are exploited in the two analyses respectively. 
+Multivariate techniques are used to separate the signal from the background, which is dominated by top-quark pair production.
 No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.

### 2018-09-09 sections/conclusion.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

@@
 CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
-Two analyses are performed searching for $\ttbar \to WbHq$ production, and targeting the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, respectively.  
-The $\Hbb$ search selects events with one isolated charged light lepton from the $W \to \ell\nu$ decay, and multiple jets, with several 
+Two complementary analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
+and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
+The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, with several 
 of them being identified with high purity as originating from the hadronisation of $b$-quarks. 

### 2018-09-09 sections/data_presel.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

@@
 
+%Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
+%with higher-threshold triggers without isolation requirements to ensure maximum efficiency. 
+%For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
+%For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
+%along with triggers with a 60~\gev\ threshold and no isolation requirements, and with a 120 (140)~\gev\ threshold 
+%with looser identification criteria and no isolation requirements.
 Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
-with higher-threshold triggers without isolation requirements to ensure maximum efficiency. 
-For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
-For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
-along with triggers with a 60~\gev\ threshold and no isolation requirements, and with a 120 (140)~\gev\ threshold 
-with looser identification criteria and no isolation requirements.
+with higher-threshold triggers but with a looser identification criterion and without any isolation requirement.
+The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016), while for electrons the threshold is 24 (26)~\gev.
 %For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
@@
 Events selected by the $\Hbb$ search are recorded with a single-electron or single-muon trigger and 
-are required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton triggering the event.  
+are required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger.  
 Furthermore, at least four jets are required, of which at least two must be $b$-tagged.
@@
 and are required to have exactly one selected electron or muon and at least one $\tauhad$ candidate. 
-The selected charged light lepton is required to match, with $\Delta R < 0.15$, the lepton triggering the event and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and
+The selected electron or muon is required to match, with $\Delta R < 0.15$, the lepton reconstructed by the trigger 
+and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
 data taking conditions). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
 Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
-no selected charged light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
+no selected electrons or muons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
 In addition, in both $\Htautau$ search channels, trigger matching for $\tauhad$ candidates, at least three jets and exactly one $b$-tagged jet are required.
@@
 Trigger & single-lepton trigger & single-lepton trigger & ditau trigger  \\
-Charged light leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
-Tau leptons & -- & $\geq$1 $\tauhad$ & $\geq$2 $\tauhad$ \\
+Leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
+               & -- & $\geq$1 $\tauhad$ & $\geq$2 $\tauhad$ \\
 Electric charge ($q$) & -- & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\

### 2018-09-09 sections/detector.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

@@
 Hadronic calorimetry is provided by %the
-a
-steel/scintillator-tile calorimeter,
+a steel/scintillator-tile calorimeter,
 segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
@@
 optimised for electromagnetic and hadronic measurements, respectively.
-The muon spectrometer measures the %deflection
-trajectories
-of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking 
-chambers located in a toroidal field of approximately 0.5~T and 1~T in the central and endcap regions, respectively. 
-The muon spectrometer is instrumented with separate trigger chambers covering $|\eta|<2.4$.
+The calorimeters are surrounded by a muon spectrometer within a magnetic field provided by air-core toroid magnets 
+with a bending integral of about 2.5 Tm in the barrel and up to 6 Tm in the end-caps. 
+The muon spectrometer measures the trajectories of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking chambers,
+and is instrumented with separate trigger chambers covering $|\eta|<2.4$.
 A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based Level-1 trigger followed by 

### 2018-09-09 sections/introduction.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

@@
 Searches for $t \to Hq$ decays have been performed by the ATLAS and CMS collaborations, taking advantage of the large samples
-of $\ttbar$ events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{Aaboud:2017mfd,Aaboud:2018pob,Sirunyan:2017uae} using early Run~2 data.
+of top-quark pair ($\ttbar$) events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{Aaboud:2017mfd,Aaboud:2018pob,Sirunyan:2017uae} using early Run~2 data.
 In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{ 
@@
 and excellent diphoton mass re\-so\-lu\-tion. 
-Searches targeting signatures with two same-charge light leptons (electrons or muons) or three charged light leptons, generically referred to as ``multileptons",
+Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as ``multileptons",
 are able to exploit a significantly larger branching ratio for the Higgs 
@@
 $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
-The $\Hbb$ search selects events with one isolated charged light lepton from the $W \to \ell\nu$ decay, and multiple jets, several 
+The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, several 
 of which are identified with high purity as originating from the hadronisation of $b$-quarks. 

### 2018-09-09 sections/signal_background_modeling.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

@@
 initial and final state radiation, referred to as the ``tune'', is used.
-The signal sample is normalised to the same total cross section as used for the $t\bar{t}\to WbWb$ sample (see discussion below) and
+The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
 assuming an arbitrary branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
@@
 and using the MSTW 2008 NNLO~\cite{Martin:2009iq,Martin:2009bu} PDF set. 
-The theoretical uncertainties result from variations of the factorisation and renormalisation scales, as well as from uncertainties in the
-top quark mass, and in the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution to the overall theoretical uncertainty 
-in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
-with the MSTW 2008 68\% CL NNLO, CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3 5F FFN~\cite{Ball:2012cx} PDF sets.
+%The theoretical uncertainties result from variations of the factorisation and renormalisation scales, as well as from uncertainties in the
+%top quark mass, and in the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution to the overall theoretical uncertainty 
+%in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
+%with the MSTW 2008 68\% CL NNLO, CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3 5F FFN~\cite{Ball:2012cx} PDF sets.
 
@@
 The $\ttbar V$ samples are normalised to the NLO cross section computed with {\amcatnlo}.
-The $\ttbar H$ sample is normalised using the NLO cross section~\cite{Raitio:1978pt,Beenakker:2002nc,Dawson:2003zu,Yu:2014cka,Frixione:2015zaa}.
+The $\ttbar H$ sample is normalised using the NLO cross section~\cite{deFlorian:2016spz}.
+%Raitio:1978pt,Beenakker:2002nc,Dawson:2003zu,Yu:2014cka,Frixione:2015zaa}.
 
@@
 the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
-is adopted for some of the samples.
-% used to estimate systematic uncertainties.
+is adopted for some of the samples used to estimate modelling systematic uncertainties.
 Simulated events are processed through the same reconstruction software as the data, and corrections are applied so that the object identification 

### 2018-09-09 sections/statistical_analysis.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

@@
 Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
-All nuisance parameters are implemented in the likelihood function as Gaussian or log-normal constraints, with the exception of a few parameters 
+All nuisance parameters are subject to additional Gaussian or log-normal constraints in the likelihood, with the exception of a few parameters 
 that control the normalisation of some background components (e.g. the \ttbin\ background in the case of the $\Hbb$ search), which 

### 2018-09-09 sections/strategy_Htautau.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

@@
 %three additional jets. Therefore, at least four jets are typically expected in signal events.
-However, in a significant fraction of the events the trailing jet from the $W$-boson decay fails the minimum $\pt$ requirement of $30~\gev$,
+However, in a significant fraction of the events the lowest-$\pt$ jet from the $W$-boson decay fails the minimum $\pt$ requirement of $30~\gev$,
 resulting in signal events with only three jets reconstructed.
@@
 %The event reconstruction strategy used~\cite{Chen:2015nta} is summarised in the following.
-The event reconstruction is based on the strategy previously used in~\cite{Chen:2015nta}.
+The event reconstruction is based on the strategy previously used in Ref.~\cite{Chen:2015nta}.
 
@@
 top quark ($t \to Wb \to qqb$) are rejected, as the $t \to Hq$ decay cannot be reconstructed due to the missing light-quark jet.
+As in Ref.~\cite{Chen:2015nta}, this compatibility is assessed via a likelihood function that depens on the reconstructed mass of the three-jet 
+system and the two non-$b$-tagged jets.
 For the remaining events, the selected jets are assigned to the different top quark decay products via a criterion based on 
@@
 added on top of the background prediction.
-The first and the last bins in all figures contain the underflow and overflow respectively.
+The first and the last bins in the figures in (a) and (b) contain the underflow and overflow respectively.
 The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.

### 2018-09-09 sections/systematic_uncertainties.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

@@
 cross section~\cite{Czakon:2011xx}, including contributions from varying the factorisation and renormalisation 
-scales, and from uncertainties in the PDF, $\alpha_{\textrm{S}}$, and the top quark mass, all added in quadrature. 
+scales, as well as from the top quark mass, the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution 
+to the overall theoretical uncertainty in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
+with the MSTW 2008 68\% CL NNLO, CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3 5F FFN~\cite{Ball:2012cx} PDF sets.
 The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
@@
 Uncertainties in the $\ttbar V$ and $\ttbar H$ cross sections are 15\% and $+10\%$/$-13\%$, respectively,
-from the uncertainties in their respective NLO theoretical cross sections~\cite{Campbell:2012dh,Garzelli:2012bn,Dittmaier:2011ti}.
+from the uncertainties in their respective NLO theoretical cross sections~\cite{Campbell:2012dh,Garzelli:2012bn,deFlorian:2016spz}.
 

### 2018-09-09 ANA-TOPQ-2017-07-PAPER-auxmat.tex
Implemented remaining replies to CDS comments from Sana Ketabchi
Updated auxmat

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[htbp]
-\begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_lep0_pt.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_met.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_hthad.eps}} 
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_mbb_mindR.eps}} \\ 
-\caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
-distributions in the (4j, 3b) region before performing the fit to data (``Pre-Fit''). 
-The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
-the jets ($\hthad$), and (d) the invariant mass distribution of the two $b$-tagged jets with lowest 
-$\Delta R$ separation ($\mbb$).
-The small contributions from $\ttbar V$, $\ttbar H$, single top, $W/Z$+jets, diboson, and multijet backgrounds are combined 
-into a single background source referred to as ``Non-$\ttbar$''. 
-The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
-added on top of the background prediction.
-The last bin in all figures contains the overflow.
-The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
-The blue triangles indicate points that are outside the vertical range of the figure. 
-The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
-which is determined via a likelihood fit to data.}}
-\label{fig:Hbb_extravars_4j3b}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure*}[htbp]
+%\begin{center}
+%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_lep0_pt.eps}}
+%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_met.eps}} \\
+%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_hthad.eps}} 
+%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_mbb_mindR.eps}} \\ 
+%\caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
+%distributions in the (4j, 3b) region before performing the fit to data (``Pre-Fit''). 
+%The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
+%the jets ($\hthad$), and (d) the invariant mass distribution of the two $b$-tagged jets with lowest 
+%$\Delta R$ separation ($\mbb$).
+%The small contributions from $\ttbar V$, $\ttbar H$, single top, $W/Z$+jets, diboson, and multijet backgrounds are combined 
+%into a single background source referred to as ``Non-$\ttbar$''. 
+%The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
+%added on top of the background prediction.
+%The last bin in all figures contains the overflow.
+%The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
+%The blue triangles indicate points that are outside the vertical range of the figure. 
+%The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
+%which is determined via a likelihood fit to data.}}
+%\label{fig:Hbb_extravars_4j3b}
+%\end{center}
+%\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 added on top of the background prediction.
-The first and the last bins in all figures contain the underflow and overflow respectively.
+%The first and the last bins in all figures contain the underflow and overflow respectively.
 The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
@@
 added on top of the background prediction.
-The first and the last bins in all figures contain the underflow and overflow respectively.
+The first and the last bins in the figures in (c) and (d) contain the underflow and overflow respectively.
 The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.

### 2018-09-13 sections/systematic_uncertainties.tex
correction to syst description for tau fakes

@@
 In each loose SR, after subtracting the small contribution from real $\tauhad$ candidates based on the simulation, 
-the shape difference between the remaining data and the fake $\tauhad$ background estimate based on its associated loose CR 
+the relative difference in the shape of the distribution between the remaining data and the fake $\tauhad$ background estimate based on its associated loose CR 
 is applied as an uncertainty on the prediction in the nominal SR.

### 2018-09-15 sections/signal_background_modeling.tex
Some updates from CDS comments on MC/samples

@@
 including resummation of next-to-next-to-leading logarithmic (NNLL) soft gluon 
-terms~\cite{Cacciari:2011hy,Baernreuther:2012ws,Czakon:2012zr,Czakon:2012pz,Czakon:2013goa}, 
-and using the MSTW 2008 NNLO~\cite{Martin:2009iq,Martin:2009bu} PDF set. 
+terms~\cite{Cacciari:2011hy,Baernreuther:2012ws,Czakon:2012zr,Czakon:2012pz,Czakon:2013goa}.
+%and using the MSTW 2008 NNLO~\cite{Martin:2009iq,Martin:2009bu} PDF set. 
 %The theoretical uncertainties result from variations of the factorisation and renormalisation scales, as well as from uncertainties in the
@@
 The $\ttbar$ background selected by the $\Hbb$ search is enriched in $\ttbar$+heavy-flavour production, and thus requires a more sophisticated 
-treatment than provided by the nominal $\ttbar$ sample. 
+treatment than provided by the nominal $\ttbar$ sample, which is briefly outlined below. A detailed discussion can be found in Ref.~\cite{Aaboud:2017rss}.
 %The large and complex $\ttbar$ background selected by the $\Hbb$ search requires a more sophisticated treatment than provided by the nominal $\ttbar$ sample. 
-Therefore, the simulated $\ttbar$ events are categorised depending 
-on the flavour content of additional particle jets not originating from the decay of the $\ttbar$ system (see Ref.~\cite{Aaboud:2017rss} for details).
+The simulated $\ttbar$ events are categorised depending 
+on the flavour content of additional particle jets not originating from the decay of the $\ttbar$ system.
 Events labelled as either \ttbin\ or \ttcin\ are generically referred to in the following as $\ttbar$+HF events, where HF stands for ``heavy flavour''.
@@
 of \ttbin\ production including parton showering~\cite{Cascioli:2013era}, based on {\ShOLlong}~\cite{Gleisberg:2008ta, Cascioli:2011va} (referred to as {\ShOL} 
-in the following) using the CT10 PDF set.  This reweighting is performed in such a way that the inter-normalisations of the \ttbin\ categories are at NLO accuracy, 
+in the following) using the CT10 4F PDF set.  This reweighting is performed in such a way that the inter-normalisations of the \ttbin\ categories are at NLO accuracy, 
 while preserving the \ttbin\ cross section of the nominal $\ttbar$ sample. 
@@
 
-Samples of $W/Z$+jets events are generated with the {\sherpa}~2.2.0~\cite{Gleisberg:2008ta} generator. 
+Samples of $W/Z$+jets events are generated with the {\sherpa}~2.2.1~\cite{Gleisberg:2008ta} generator. 
 The matrix element is calculated for up to two partons at NLO and up to four partons at LO using 
@@
 and interfaced to {\pythia}~8.210 with the NNPDF2.3 LO PDF set and the A14 tune. 
-The $\ttbar V$ samples are normalised to the NLO cross section computed with {\amcatnlo}.
-The $\ttbar H$ sample is normalised using the NLO cross section~\cite{deFlorian:2016spz}.
+Instead, the $\ttbar V$ samples used by the $\Hbb$ search are based on LO matrix elements computed for up to two additional partons 
+using the NNPDF3.0 NLO PDF set, and merged using the CKKW-L approach~\cite{Lonnblad:2001iq}.
+The $\ttbar V$ samples are normalised to the NLO cross section computed with {\amcatnlo}, while the $\ttbar H$ sample is normalised using 
+the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.
 %Raitio:1978pt,Beenakker:2002nc,Dawson:2003zu,Yu:2014cka,Frixione:2015zaa}.
@@
 utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
-To model the effects of pile-up, events from minimum-bias interactions are generated using the {\pythia}~8.186~\cite{Sjostrand:2007gs} 
-event generator and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
+To model the effects of pile-up, events from minimum-bias interactions are generated using {\pythia}~8.186~\cite{Sjostrand:2007gs}  
+in combination with the A2 tune~\cite{ATL-PHYS-PUB-2011-014}, 
+and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
 The generated events are processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 

### 2018-09-15 sections/systematic_uncertainties.tex
Some updates from CDS comments on MC/samples

@@
 The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
-{\powheg}+{\pythiaeight} with a prediction from either {\amcatnlo}+{\pythiaeight} (in the case of the $\Htautau$ search) or
-\textsc{Sherpa} (in the case of the $\Hbb$ search). 
+{\powheg}+{\pythiaeight} with a prediction from \textsc{Sherpa}~2.2.1. For the latter, the matrix element calculation is performed 
+for up to two partons at NLO and up to four partons at LO using \textsc{Comix} and \textsc{OpenLoops}, and
+merged with the {\sherpa} parton shower using the ME+PS@NLO prescription.
+%either {\amcatnlo}+{\pythiaeight} (in the case of the $\Htautau$ search) or
+%\textsc{Sherpa} (in the case of the $\Hbb$ search). 
 The uncertainty due to the choice of parton shower and hadronisation (PS \& Had) model is derived 
 by comparing the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 
+The latter uses MMHT2014 LO~\cite{Harland-Lang:2014zoa} PDF set in combination with the H7UE tune~\cite{Bellm:2015jjp}.
 Additionally, the uncertainty on the modelling of additional radiation is assessed with two alternative {\powheg}+{\pythiaeight} samples:
@@
 These include three different scale variations,  a different shower-recoil model scheme, and 
-two alternative PDF sets (MSTW and NNPDF). Additional uncertainties are assessed for
+two alternative PDF sets (MSTW 2008 NLO and NNPDF2.3 NLO). Additional uncertainties are assessed for
 the contributions to the \ttbin\ background originating from multiple parton interactions.

### 2018-09-15 sections/objects.tex
Implemented remaining replies to CDS comments from Jason Nielsen
Reverting to old description of OL. Need to fix for tautau

@@
 decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-quark/gluon jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
-Electrons that are reconstructed as one-prong $\tauhad$ candidates are removed via a BDT.
+Electrons that are reconstructed as one-prong $\tauhad$ candidates are removed via a BDT trained to reject electrons.
 Any $\tauhad$ candidate that is also $b$-tagged is rejected.
 
-In the $\Hbb$ search, overlaps between candidate objects are removed sequentially, following this order: muons, electrons and jets.
-Firstly, electron candidates that lie within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung.
-Overlaps between electron and jet candidates are resolved
-next, and finally, overlaps between remaining jet candidates and muon candidates are removed.
-Clusters from identified electrons are not excluded during jet reconstruction.
-In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron is discarded.
-If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
+Overlaps between candidate objects are removed sequentially, following this order: muons, electrons,
+$\tauhad$ (only for the $\Htautau$ search), and jets. In the $\Hbb$ search, firstly, electron candidates that lie 
+within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
+Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
+and muon candidates are removed. Clusters from identified electrons are not excluded during jet reconstruction. 
+In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
+is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
 The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
@@
 if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
-In the $\Htautau$ search, the objects are removed with the following sequence: if two electrons have overlapped second-layer cluser, or shared tracks, the electron with lower $\pt$ is removed; $\tauhad$ within a $\Delta R=0.2$ cone of an electron or muon are removed; if a muon sharing an ID track with an electron and the muon is calo-tagged, the muon is removed, otherwise the electron is removed; jets within a $\Delta R=0.2$ cone of an electron are removed; electrons within a $\Delta R=0.4$ cone of a jet are removed; when a muon ID track is ghost associated to a jet or within a $\Delta R=0.2$ cone of a jet, the jet is removed if it has less than 3 tracks with $\pt>500$ MeV or has a relative small $\pt$ ($\pt^{\mu}>0.5\pt^{\text{jet}} \text{ and } \pt^{\mu}>0.7[\text{the scalar sum of the } \pt \text{'s of the jet tracks with } \pt>500$ MeV]); muons within a $\Delta R=0.4$ cone of a jet are removed; jets within a $\Delta R=0.2$ cone of the leading $\tauhad$ ($\lephad$), or with the two leading $\tauhad$'s ($\hadhad$), are removed.
+In the $\Htautau$ search, a fixed cone size of $\Delta R=0.2$ is used to determine the overlap between
+candidate objects, and only the highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the
+analysis channel, see Section~\ref{sec:data_presel}) are considered to resolve their overlap with jets.
+
+% TEXT FROM BOYANG. NEED TO RECHECK WHAT WE HAVE ABOVE IS ACCURATE
+%In the $\Hbb$ search, overlaps between candidate objects are removed sequentially, following this order: muons, electrons and jets.
+Firstly, electron candidates that lie within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung.
+Overlaps between electron and jet candidates are resolved
+%next, and finally, overlaps between remaining jet candidates and muon candidates are removed.
+Clusters from identified electrons are not excluded during jet reconstruction.
+In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron is discarded.
+If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
+%The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
+%that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
+%Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
+%and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
+%few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
+%if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
+%In the $\Htautau$ search, the objects are removed with the following sequence: if two electrons have overlapping second-layer cluser, or shared tracks, the electron with lower $\pt$ is removed; $\tauhad$ within a $\Delta R=0.2$ cone of an electron or muon are removed; if a muon sharing an ID track with an electron and the muon is calo-tagged, the muon is removed, otherwise the electron is removed; jets within a $\Delta R=0.2$ cone of an electron are removed; electrons within a $\Delta R=0.4$ cone of a jet are removed; when a muon ID track is ghost associated to a jet or within a $\Delta R=0.2$ cone of a jet, the jet is removed if it has less than 3 tracks with $\pt>500$ MeV or has a relative small $\pt$ ($\pt^{\mu}>0.5\pt^{\text{jet}} \text{ and } \pt^{\mu}>0.7[\text{the scalar sum of the } \pt \text{'s of the jet tracks with } \pt>500$ MeV]); muons within a $\Delta R=0.4$ cone of a jet are removed; jets within a $\Delta R=0.2$ cone of the leading $\tauhad$ ($\lephad$), or with the two leading $\tauhad$'s ($\hadhad$), are removed.
 

### 2018-09-15 sections/objects.tex
added CONF note number, removed acknowledgements, updated tautau OL discussion

@@
 
-Overlaps between candidate objects are removed sequentially, following this order: muons, electrons,
-$\tauhad$ (only for the $\Htautau$ search), and jets. In the $\Hbb$ search, firstly, electron candidates that lie 
+%Overlaps between candidate objects are removed sequentially, following this order: muons, electrons,
+%$\tauhad$ (only for the $\Htautau$ search), and jets. In the $\Hbb$ search, firstly, electron candidates that lie 
+%within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
+%Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
+%and muon candidates are removed. Clusters from identified electrons are not excluded during jet reconstruction. 
+%In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
+%is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
+%The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
+%that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
+%Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
+%and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
+%few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
+%if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
+%In the $\Htautau$ search, a fixed cone size of $\Delta R=0.2$ is used to determine the overlap between
+%candidate objects, and only the highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the
+%analysis channel, see Section~\ref{sec:data_presel}) are considered to resolve their overlap with jets.
+
+Overlaps between candidate objects are removed sequentially. In the $\Hbb$ search, firstly, electron candidates that lie 
 within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
@@
 if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
-In the $\Htautau$ search, a fixed cone size of $\Delta R=0.2$ is used to determine the overlap between
-candidate objects, and only the highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the
-analysis channel, see Section~\ref{sec:data_presel}) are considered to resolve their overlap with jets.
+The overlap removal procedure in $\Htautau$ search is similar to that of the $\Hbb$ search, except that the
+first step is the removal of $\tauhad$ candidates within $\Delta R=0.2$ of electrons or muons, and the last step is the
+removal of jets whose axis lies within $\Delta R=0.2$ of the highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the
+analysis channel, see Section~\ref{sec:data_presel}). In addition, the muon--jet overlap removal is slightly different:
+if a muon lies within $\Delta R = 0.2$ of the axis of a jet, the jet is removed if either it has fewer than three tracks originating from the 
+primary vertex or it has a small $\pt$ compared to that of the muon (the $\pt$ of the jet is less than 50\% of the $\pt$ of the muon,
+or the scalar sum of the $\pt$ of the tracks associated to the jet is less than 70\% of the $\pt$ of the muon).
 
 % TEXT FROM BOYANG. NEED TO RECHECK WHAT WE HAVE ABOVE IS ACCURATE
-%In the $\Hbb$ search, overlaps between candidate objects are removed sequentially, following this order: muons, electrons and jets.
-Firstly, electron candidates that lie within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung.
-Overlaps between electron and jet candidates are resolved
-%next, and finally, overlaps between remaining jet candidates and muon candidates are removed.
-Clusters from identified electrons are not excluded during jet reconstruction.
-In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron is discarded.
-If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
-%The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
-%that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
-%Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
-%and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
-%few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
-%if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
 %In the $\Htautau$ search, the objects are removed with the following sequence: if two electrons have overlapping second-layer cluser, or shared tracks, the electron with lower $\pt$ is removed; $\tauhad$ within a $\Delta R=0.2$ cone of an electron or muon are removed; if a muon sharing an ID track with an electron and the muon is calo-tagged, the muon is removed, otherwise the electron is removed; jets within a $\Delta R=0.2$ cone of an electron are removed; electrons within a $\Delta R=0.4$ cone of a jet are removed; when a muon ID track is ghost associated to a jet or within a $\Delta R=0.2$ cone of a jet, the jet is removed if it has less than 3 tracks with $\pt>500$ MeV or has a relative small $\pt$ ($\pt^{\mu}>0.5\pt^{\text{jet}} \text{ and } \pt^{\mu}>0.7[\text{the scalar sum of the } \pt \text{'s of the jet tracks with } \pt>500$ MeV]); muons within a $\Delta R=0.4$ cone of a jet are removed; jets within a $\Delta R=0.2$ cone of the leading $\tauhad$ ($\lephad$), or with the two leading $\tauhad$'s ($\hadhad$), are removed.

### 2018-09-16 ANA-TOPQ-2017-07-PAPER-metadata.tex
Implemented remaining replies to CDS comments from Filippo Ceradini
updated metadata file
removed version number from metadata file
added CONF note number, removed acknowledgements, updated tautau OL discussion
implemented sign-off comments from George

@@
 % Comment or remove in final version.
-\AtlasVersion{1.0}
+\AtlasVersion{1.2}
 % Abstract - % directly after { is important for correct indentation
@@
 No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
-The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
-yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
+The combination of these searches with ATLAS searches in diphoton and multilepton final states 
+%significantly improves the sensitivity, 
+yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
 and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), respectively.
@@
 % ATLAS reference code, to help ATLAS members to locate the paper
-\AtlasRefCode{TOPQ-2017-07}
+%\AtlasRefCode{TOPQ-2017-07}
+\AtlasRefCode{ATLAS-CONF-2018-049}
 

### 2018-09-16 sections/conclusion.tex
implemented sign-off comments from George

@@
 are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$ respectively.
-The combination of these searches with ATLAS searches in diphoton and multilepton final states significantly improves the sensitivity, 
-yielding observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
+The combination of these searches with ATLAS searches in diphoton and multilepton final states 
+%significantly improves the sensitivity, 
+yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
 and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming that $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$ respectively.

### 2018-09-16 sections/objects.tex
small fix from George

@@
 if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
-The overlap removal procedure in $\Htautau$ search is similar to that of the $\Hbb$ search, except that the
+The overlap removal procedure in the $\Htautau$ search is similar to that of the $\Hbb$ search, except that the
 first step is the removal of $\tauhad$ candidates within $\Delta R=0.2$ of electrons or muons, and the last step is the

### 2018-09-17 sections/introduction.tex
implementing Jason comments for the conf signoff

@@
 and excellent diphoton mass re\-so\-lu\-tion. 
-Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as ``multileptons",
+Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as ``multileptons'',
 are able to exploit a significantly larger branching ratio for the Higgs 
@@
 Two analyses are performed searching for $\ttbar \to WbHq$ production (i.e. $pp \to tH$ production is ignored), and targeting the 
-$H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
+$H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which will be referred to as ``$\Hbb$ search'' and ``$\Htautau$ search'', respectively.
 The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, several 

### 2018-09-17 sections/signal_background_modeling.tex
jason comments and fix to prelim plot

@@
 Backgrounds with non-prompt electrons or muons, with photons or jets misidentified as electrons, or with jets misidentified as $\tauhad$ candidates, 
-generically referred to as ``fake leptons", are estimated using data-driven methods. 
+generically referred to as ``fake leptons'', are estimated using data-driven methods. 
 The background prediction is further improved during the statistical analysis by performing a likelihood 
@@
 
-The fake $\tauhad$ background prediction in a given SR is modelled by the distribution (referred to as ``fake $\tauhad$ template") derived from data in the corresponding CR.
+The fake $\tauhad$ background prediction in a given SR is modelled by the distribution (referred to as ``fake $\tauhad$ template'') derived from data in the corresponding CR.
 The fake $\tauhad$ template is defined as the data distribution from which the contributions from the simulated backgrounds with real $\tauhad$ candidates, originating primarily from
@@
 defined as the data yield minus the contributions from the simulated backgrounds with real $\tauhad$ candidates (i.e. assuming no signal contribution).
-During the statistical analysis, the normalisation of the fake $\tauhad$ background in each SR will be allowed to vary unconstrained in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.
+During the statistical analysis, the normalisation of the fake $\tauhad$ background in each SR is allowed to vary unconstrained in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.
 

### 2018-09-17 sections/statistical_analysis.tex
jason comments and fix to prelim plot

@@
 
-The fitting procedure is initially validated through extensive studies using mocked data, defined as the sum of all predicted backgrounds 
+The fitting procedure is initially validated through extensive studies using mock data, defined as the sum of all predicted backgrounds 
 plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
-a signal contamination above 5\% are excluded (referred to as ``blinding cuts").
+a signal contamination above 5\% are excluded (referred to as ``blinding cuts'').
 In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 

### 2018-09-17 sections/strategy_Htautau.tex
implemented sign-off comments from George
jason comments and fix to prelim plot

@@
 the magnitude of the fitted $\mpt$ vector.
-\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector.
+\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector perpendicular to the fitted $\mpt$ vector.
 \item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically-decaying $W$ boson.
@@
 The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
-a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
+a single background source referred to as ``Top (real $\tauhad$)'', whereas the small contributions from 
 $Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 

### 2018-09-17 sections/systematic_uncertainties.tex
jason comments and fix to prelim plot

@@
 Uncertainties on the data-driven fake $\tauhad$ background in the $\Htautau$ search are obtained by using additional signal-depleted regions.
-The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\tauhad$ identification criteria, and thus referred to as ``loose SR"  and ``loose CR".
+The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\tauhad$ identification criteria, and thus referred to as ``loose SR''  and ``loose CR''.
 %The shape difference between the fake $\tauhad$ background prediction in each loose SR and its associated loose CR

### 2018-09-17 sections/detector.tex

@@
 The calorimeters are surrounded by a muon spectrometer within a magnetic field provided by air-core toroid magnets 
-with a bending integral of about 2.5 Tm in the barrel and up to 6 Tm in the end-caps. 
+with a bending integral of about 2.5 $\text{T}\cdot\text{m}$ in the barrel and up to 6 $\text{T}\cdot\text{m}$ in the end-caps. 
 The muon spectrometer measures the trajectories of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking chambers,

### 2018-09-17 sections/strategy_Hbb.tex
Implemented remaining replies to CDS comments from Sana Ketabchi

@@
 the selected signal events have a $H \to b\bar{b}$ decay in more than 97\% of the events.
-Because of somewhat larger fraction of $\Hc$ signal in the regions with exactly three $b$-tagged jets,
-this analysis is expected to have slightly better sensitivity for $\Hc$ than for $\Hu$ signal.
 The rest of the regions have significantly lower signal-to-background ratios, but they are used for the purpose of improving 
@@
 through a likelihood fit to data (see Section~\ref{sec:stat_analysis}).  
+Because of somewhat larger fraction of $\Hc$ signal in the regions with exactly three $b$-tagged jets,
+this analysis is expected to have slightly better sensitivity for $\Hc$ than for $\Hu$ signal.
 
@@
 \caption{$\Hbb$ search: Comparison between the data and background prediction for the event yields in each of the analysis regions considered 
-before the fit to data (``Pre-Fit"). All events satisfy the preselection requirements, whereas those with exactly two $b$-tagged jets are
+before the fit to data (``Pre-Fit''). All events satisfy the preselection requirements, whereas those with exactly two $b$-tagged jets are
 in addition required to have a value of the the likelihood discriminant above 0.6 (see Section~\ref{sec:likelihood_discriminant}).
@@
 The most prominent features are the different resonances present in the decay (i.e. the Higgs boson in the case 
-of the $\Hq$ signal and a hadronically decaying $W$ boson in the case of the $\ttbar \to WbWb$ background), and the different flavour of the 
+of the $\Hq$ signal and a hadronically decaying $W$ boson in the case of the $\ttbar \to WbWb$ background), and the different flavours of the 
 jets forming those resonances. However, the large number of jets in the final state causes ambiguities in the calculation 

### 2018-09-17 ANA-TOPQ-2017-07-PAPER-auxmat.tex
final version for conf

@@
 $x_{2}^{\text{fit}}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
-The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
-a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
 $Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
@@
 The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
-The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
+The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
 which is determined via a likelihood fit to data.}
@@
 $p_{\text{T},2}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
-The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
-a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
 $Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
@@
 The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
-The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
+The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
 which is determined via a likelihood fit to data.} 

### 2018-09-17 sections/data_presel.tex
Implemented remaining replies to CDS comments from Filippo Ceradini
implementing Jason comments for the conf signoff
final version for conf

@@
 %For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
-For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev.
+For ditau triggers, the $\pt$ threshold of the leading (trailing) $\had$ candidate is 35 (25)~\gev.
 In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.
@@
 multiplicity of selected leptons. Events in the $\lephad$ channel are recorded with a single-electron or single-muon trigger 
-and are required to have exactly one selected electron or muon and at least one $\tauhad$ candidate. 
+and are required to have exactly one selected electron or muon and at least one $\had$ candidate. 
 The selected electron or muon is required to match, with $\Delta R < 0.15$, the lepton reconstructed by the trigger 
 and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
-data taking conditions). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
-Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
-no selected electrons or muons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
-In addition, in both $\Htautau$ search channels, trigger matching for $\tauhad$ candidates, at least three jets and exactly one $b$-tagged jet are required.
+data taking conditions). In addition, its electric charge is required to be of opposite sign to that of the leading $\had$ candidate.
+Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\had$ candidates and 
+no selected electrons or muons. The two leading $\had$ candidates are required to have charges of opposite sign. 
+In addition, in both $\Htautau$ search channels, trigger matching for $\had$ candidates, at least three jets and exactly one $b$-tagged jet are required.
 
@@
 Leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
-               & -- & $\geq$1 $\tauhad$ & $\geq$2 $\tauhad$ \\
+               & -- & $\geq$1 $\had$ & $\geq$2 $\had$ \\
 Electric charge ($q$) & -- & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
@@
 \caption{\small{Summary of preselection requirements for the $\Hbb$ and $\Htautau$ searches. 
-The leading and trailing $\tauhad$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
+The leading and trailing $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
 \label{tab:preselection}

### 2018-09-17 sections/objects.tex
final version for conf

--- 2018-09-15 sections/objects.tex
@@
 
-Hadronically decaying $\tau$-lepton ($\tauhad$) candidates are reconstructed from energy clusters in the calorimeters and
+Hadronically decaying $\tau$-lepton ($\had$) candidates are reconstructed from energy clusters in the calorimeters and
 associated inner detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
 with a total charge of $\pm 1$. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
-A boosted decision tree (BDT) discriminant using calorimeter- and tracking-based variables is used to identify $\tauhad$ candidates and reject
-jet backgrounds. Three working points labelled loose, medium and tight are defined, and correspond to different $\tauhad$ identification efficiency 
+A boosted decision tree (BDT) discriminant using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject
+jet backgrounds. Three working points labelled loose, medium and tight are defined, and correspond to different $\had$ identification efficiency 
 values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
 working point for the nominal selection, while the loose working point is used for background estimation.
-The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\tauhad$ 
+The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\had$ 
 decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-quark/gluon jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
-Electrons that are reconstructed as one-prong $\tauhad$ candidates are removed via a BDT trained to reject electrons.
-Any $\tauhad$ candidate that is also $b$-tagged is rejected.
+Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
+Any $\had$ candidate that is also $b$-tagged is rejected.
 
@@
 if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
-The overlap removal procedure in $\Htautau$ search is similar to that of the $\Hbb$ search, except that the
-first step is the removal of $\tauhad$ candidates within $\Delta R=0.2$ of electrons or muons, and the last step is the
-removal of jets whose axis lies within $\Delta R=0.2$ of the highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the
+The overlap removal procedure in the $\Htautau$ search is similar to that of the $\Hbb$ search, except that the
+first step is the removal of $\had$ candidates within $\Delta R=0.2$ of electrons or muons, and the last step is the
+removal of jets whose axis lies within $\Delta R=0.2$ of the highest-$\pt$ (leading) or the two leading $\had$ candidates (depending on the
 analysis channel, see Section~\ref{sec:data_presel}). In addition, the muon--jet overlap removal is slightly different:

### 2018-09-17 sections/signal_background_modeling.tex
final version for conf

@@
 and the Higgs boson is allowed to decay into all SM particles with branching ratios calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
-Backgrounds with non-prompt electrons or muons, with photons or jets misidentified as electrons, or with jets misidentified as $\tauhad$ candidates, 
+Backgrounds with non-prompt electrons or muons, with photons or jets misidentified as electrons, or with jets misidentified as $\had$ candidates, 
 generically referred to as ``fake leptons'', are estimated using data-driven methods. 
@@
 \label{sec:faketaus}
-In the $\Htautau$ search, the background with one or more fake $\tauhad$ candidates is mainly arising from $\ttbar$ or
+In the $\Htautau$ search, the background with one or more fake $\had$ candidates is mainly arising from $\ttbar$ or
 multijet production, depending on the analysis channel, with $W$+jets production contributing to a lesser extent. 
-Studies based on the simulation show that, for all above processes, fake $\tauhad$ candidates primarily result from the 
+Studies based on the simulation show that, for all above processes, fake $\had$ candidates primarily result from the 
 misidentification of light-quark jets, with the contribution from $b$-quarks and gluon jets playing a subdominant role.
-It is also found that the fake rate decreases as the $\tauhad$ candidate $\pt$ increases for all jet flavours.
+It is also found that the fake rate decreases as the $\had$ candidate $\pt$ increases for all jet flavours.
 
-This background is estimated directly from data by defining control regions (CR) enriched in fake $\tauhad$ candidates via loosened $\tauhad$ requirements or flipped charge.
+This background is estimated directly from data by defining control regions (CR) enriched in fake $\had$ candidates via loosened $\had$ requirements or flipped charge.
 These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
-The CR selection requirements are analogous to those used to define the different SRs, except that the leading (trailing) $\tauhad$ candidate
+The CR selection requirements are analogous to those used to define the different SRs, except that the leading (trailing) $\had$ candidate
 in the $\lephad$ ($\hadhad$) channel is required to fail the medium tau identification but pass the loose one, or the two tau candidates have the same charge.
 
-The fake $\tauhad$ background prediction in a given SR is modelled by the distribution (referred to as ``fake $\tauhad$ template'') derived from data in the corresponding CR.
-The fake $\tauhad$ template is defined as the data distribution from which the contributions from the simulated backgrounds with real $\tauhad$ candidates, originating primarily from
+The fake $\had$ background prediction in a given SR is modelled by the distribution (referred to as ``fake $\had$ template'') derived from data in the corresponding CR.
+The fake $\had$ template is defined as the data distribution from which the contributions from the simulated backgrounds with real $\had$ candidates, originating primarily from
 $W(\to \tau\nu)$+jets and $Z(\to \tau\tau)$+jets, are subtracted.
-In the $\lephad$ channel, simulation studies indicate that the fake $\tauhad$ background composition is consistent between the SR and the CR, and dominated by $\ttbar$.
-In the $\hadhad$ channel, the fake $\tauhad$ background is expected to be dominated by multijet production.
-However, simulation studies indicate that the contribution of $\ttbar$ events to the fake $\tauhad$ background is higher in the SR than in the CR.
-Therefore, an appropriate amount of simulated $\ttbar$ events with fake $\tauhad$ candidates in the CR is added to the fake $\tauhad$ template to match the fake $\tauhad$ background composition in the SR.
-In both the $\lephad$ and $\hadhad$ channels, the fake $\tauhad$ template in each SR is initially normalised to the estimated fake $\tauhad$ background yield, 
-defined as the data yield minus the contributions from the simulated backgrounds with real $\tauhad$ candidates (i.e. assuming no signal contribution).
-During the statistical analysis, the normalisation of the fake $\tauhad$ background in each SR is allowed to vary unconstrained in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.
+In the $\lephad$ channel, simulation studies indicate that the fake $\had$ background composition is consistent between the SR and the CR, and dominated by $\ttbar$.
+In the $\hadhad$ channel, the fake $\had$ background is expected to be dominated by multijet production.
+However, simulation studies indicate that the contribution of $\ttbar$ events to the fake $\had$ background is higher in the SR than in the CR.
+Therefore, an appropriate amount of simulated $\ttbar$ events with fake $\had$ candidates in the CR is added to the fake $\had$ template to match the fake $\had$ background composition in the SR.
+In both the $\lephad$ and $\hadhad$ channels, the fake $\had$ template in each SR is initially normalised to the estimated fake $\had$ background yield, 
+defined as the data yield minus the contributions from the simulated backgrounds with real $\had$ candidates (i.e. assuming no signal contribution).
+During the statistical analysis, the normalisation of the fake $\had$ background in each SR is allowed to vary unconstrained in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.
 

### 2018-09-17 sections/strategy_Htautau.tex
final version for conf

@@
 In order to optimise the sensitivity of the search, the selected events are categorised into four SRs depending 
-on the number of $\taulep$ and $\tauhad$ candidates, and on the number of jets:
+on the number of $\taulep$ and $\had$ candidates, and on the number of jets:
 ($\lephad$, 3j), ($\lephad$, $\geq$4j), ($\hadhad$, 3j), and ($\hadhad$, $\geq$4j).
@@
 %whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
-In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
+In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\had$ contributions), 
 elsewhere the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account.
@@
 \item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\met$ in the $\lephad$ channel.
-\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\tauhad$ candidate (denoted as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\tauhad$ candidates (denoted as particles 1 and 2 respectively) in the $\hadhad$ channel.
+\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\had$ candidate (denoted as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\had$ candidates (denoted as particles 1 and 2 respectively) in the $\hadhad$ channel.
 \item $\met$ $\phi$ centrality: a variable that quantifies the relative angular position of the $\mpt$ with respect to the 
@@
 \item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance to the $\lep$ candidate.
-\item $m_{\tau j}$: the invariant mass of the  $\tauhad$ candidate and the jet that has the smallest angular distance to the $\tauhad$ candidate.
+\item $m_{\tau j}$: the invariant mass of the  $\had$ candidate and the jet that has the smallest angular distance to the $\had$ candidate.
 \item $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$: the momentum fractions carried by the visible decay products from the two $\tau$-lepton candidates 
-(whether $\taulep$ or $\tauhad$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
+(whether $\taulep$ or $\had$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
 \item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$ boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark.
@@
 $p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
-The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
-a single background source referred to as ``Top (real $\tauhad$)'', whereas the small contributions from 
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
+a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
 $Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
@@
 $x_{1}^{\text{fit}}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
-The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
-a single background source referred to as ``Top (real $\tauhad$)'', whereas the small contributions from 
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
+a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
 $Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 

### 2018-09-17 sections/systematic_uncertainties.tex
final version for conf

--- 2018-09-15 sections/systematic_uncertainties.tex
@@
 
-Uncertainties associated with electrons, muons, and $\tauhad$ candidates arise from the trigger, reconstruction,  
+Uncertainties associated with electrons, muons, and $\had$ candidates arise from the trigger, reconstruction,  
 identification and isolation (in the case of electrons and muons) efficiencies, as well as the momentum scale and resolution. 
 These are measured in data using $Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events ($\ell =e, \mu$)~\cite{ATLAS-CONF-2016-024,Aad:2016jkr} 
-in the case of electrons and muons, and using $Z\to \tau^+\tau^-$ events in the case of $\tauhad$ candidates~\cite{ATLAS-CONF-2017-029}.
+in the case of electrons and muons, and using $Z\to \tau^+\tau^-$ events in the case of $\had$ candidates~\cite{ATLAS-CONF-2017-029}.
 
@@
 
-Uncertainties on the data-driven fake $\tauhad$ background in the $\Htautau$ search are obtained by using additional signal-depleted regions.
-The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\tauhad$ identification criteria, and thus referred to as ``loose SR"  and ``loose CR".
+Uncertainties on the data-driven fake $\had$ background in the $\Htautau$ search are obtained by using additional signal-depleted regions.
+The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\had$ identification criteria, and thus referred to as ``loose SR''  and ``loose CR''.
 %The shape difference between the fake $\tauhad$ background prediction in each loose SR and its associated loose CR
@@
 %In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty on the prediction in the nominal SR. 
-In each loose SR, after subtracting the small contribution from real $\tauhad$ candidates based on the simulation, 
-the relative difference in the shape of the distribution between the remaining data and the fake $\tauhad$ background estimate based on its associated loose CR 
+In each loose SR, after subtracting the small contribution from real $\had$ candidates based on the simulation, 
+the relative difference in the shape of the distribution between the remaining data and the fake $\had$ background estimate based on its associated loose CR 
 is applied as an uncertainty on the prediction in the nominal SR.
-In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\tauhad$ candidate from the simulation that are added to the fake $\tauhad$ template in the $\hadhad$ channel as part of the fake $\tauhad$ background estimation procedure (see Section~\ref{sec:faketaus}).
-This uncertainty, associated with the modelling of the fake $\tauhad$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\tauhad$ candidate.
-The same uncertainty is assigned to the selected signal events with fake $\tauhad$ candidates.
-In addition, a systematic uncertainty is assigned to account for the different fractional composition of particles (various types of leptons and partons) originating the fake $\tauhad$ candidates 
+In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\had$ candidate from the simulation that are added to the fake $\had$ template in the $\hadhad$ channel as part of the fake $\had$ background estimation procedure (see Section~\ref{sec:faketaus}).
+This uncertainty, associated with the modelling of the fake $\had$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\had$ candidate.
+The same uncertainty is assigned to the selected signal events with fake $\had$ candidates.
+In addition, a systematic uncertainty is assigned to account for the different fractional composition of particles (various types of leptons and partons) originating the fake $\had$ candidates 
 between each SR and its corresponding CR in the $\ttbar$ simulation. 
-Finally, the normalisation of the fake $\tauhad$ background in each SR is determined in the fit to data. 
+Finally, the normalisation of the fake $\had$ background in each SR is determined in the fit to data. 
 %In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template.

### 2018-10-03 ANA-TOPQ-2017-07-PAPER-auxmat.tex
sync local version with master
porting language editor comments

@@
 \caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
-distributions in the (4j, 2b) region (prior to the application of the cut on the LH discriminant above 0.6) before performing the fit to data (``Pre-Fit''). 
+distributions in the (4j, 2b) region (prior to the application of the cut on the LH discriminant above 0.6) before  the fit to data (``Pre-Fit''). 
 The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
-the jets ($\hthad$), and (d) the invariant mass distribution of the two $b$-tagged jets with lowest 
+the jets ($\hthad$), and (d) the invariant mass of the two $b$-tagged jets with lowest 
 $\Delta R$ separation ($\mbb$).
@@
 The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
-added on top of the background prediction.
+added to the background prediction.
 The last bin in all figures contains the overflow.
@@
 The blue triangles indicate points that are outside the vertical range of the figure. 
-The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
+The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
 which is determined via a likelihood fit to data.}}
@@
 \caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
-distributions in the (5j, 3b) region before performing the fit to data (``Pre-Fit''). 
+distributions in the (5j, 3b) region before the fit to data (``Pre-Fit''). 
 The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
-the jets ($\hthad$), and (d) the invariant mass distribution of the two $b$-tagged jets with lowest 
+the jets ($\hthad$), and (d) the invariant mass of the two $b$-tagged jets with lowest 
 $\Delta R$ separation ($\mbb$).
@@
 \caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of some of the most
-important BDT input variables in the $\lephad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
+discriminating BDT input variables in the $\lephad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
 $x_{1}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
@@
 The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
-added on top of the background prediction.
+added to the background prediction.
 %The first and the last bins in all figures contain the underflow and overflow respectively.
 The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
-The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
+The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
 which is determined via a likelihood fit to data.}
@@
 \caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
-important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
+discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
 $x_{2}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
@@
 The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
-added on top of the background prediction.
+added to the background prediction.
 The first and the last bins in the figures in (c) and (d) contain the underflow and overflow respectively.
 The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
-The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
+The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
 which is determined via a likelihood fit to data.} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure*}[t]
+%\begin{center}
+%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}}
+%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}} \\
+%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}}
+%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}} \\
+%\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
+%important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
+%$x_{2}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
+%$p_{\text{T},2}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
+%The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+%a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
+%$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
+%The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
+%added on top of the background prediction.
+%The first and the last bins in the figures in (c) and (d) contain the underflow and overflow respectively.
+%The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
+%The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
+%which is determined via a likelihood fit to data.} 
+%\label{fig:BDT_inputs_hadhad_3}
+%\end{center}
+%\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure*}[t]
+%\begin{center}
+%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}}
+%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}} \\
+%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}}
+%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}} \\
+%\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
+%important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
+%$x_{2}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
+%$p_{\text{T},2}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
+%The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+%a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
+%$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
+%The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
+%added on top of the background prediction.
+%The first and the last bins in the figures in (c) and (d) contain the underflow and overflow respectively.
+%The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
+%The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
+%which is determined via a likelihood fit to data.} 
+%\label{fig:BDT_inputs_hadhad_3}
+%\end{center}
+%\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-10-03 sections/detector.tex
porting language editor comments

--- 2018-09-09 sections/detector.tex
@@
 together providing a precise reconstruction of tracks of charged particles in the pseudorapidity range $|\eta|<2.5$.
-The inner detector also includes a transition radiation tracker that provides tracking and electron identification information for $|\eta|<2.0$.
+The inner detector also includes a transition radiation tracker that provides tracking and electron identification for $|\eta|<2.0$.
 %The electromagnetic (EM) sampling calorimeter uses lead as the absorber material 
@@
 and is instrumented with separate trigger chambers covering $|\eta|<2.4$.
-A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based Level-1 trigger followed by 
-a software-based High-Level Trigger, is used to reduce the event rate to a maximum of around 1 kHz for offline storage.
+A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based level-1 trigger followed by 
+a software-based high-level trigger, is used to reduce the event rate to a maximum of around 1 kHz for offline storage.

### 2018-10-03 sections/objects.tex
porting language editor comments

@@
 The event reconstruction is affected by multiple $pp$ collisions in a single bunch crossing and by collisions
-in neighbouring bunch crossings, referred to as ``pile-up''. 
+in neighbouring bunch crossings, referred to as pile-up. 
 Interaction vertices from the $pp$ collisions are reconstructed from at least two tracks 
@@
 from pile-up and the energy deposit of the lepton itself, is required to be less than a $\pt$-dependent 
-percentage of the lepton energy. 
+fraction of the lepton energy. 
 %Additionally, the $\Htautau$ search requires leptons to
@@
 The reconstructed jets are then calibrated to the particle level by the application of a jet energy scale 
-derived from simulation and {\textit{in situ}} corrections based on $\sqrt{s}=13~\tev$ data~\cite{Aaboud:2017jcu}.
-The calibrated jets used by the $\Hbb$ search are required to have $\pt > 25~\gev$ and $|\eta| < 2.5$,
+derived from simulation and in situ corrections based on $\sqrt{s}=13~\tev$ data~\cite{Aaboud:2017jcu}.
+The calibrated jets used in the $\Hbb$ search are required to have $\pt > 25~\gev$ and $|\eta| < 2.5$,
 while the $\Htautau$ search uses jets with $\pt > 30~\gev$ and $|\eta| < 4.5$.
@@
 or detector noise~\cite{ATLAS-CONF-2015-029}.  To reduce the contamination due to jets originating from pile-up interactions,
-additional requirements are made on the Jet Vertex Tagger (JVT)~\cite{Aad:2015ina} output for jets with $\pt<60~\gev$ and $|\eta| < 2.4$,
+additional requirements are made on the jet vertex tagger (JVT)~\cite{Aad:2015ina} output for jets with $\pt<60~\gev$ and $|\eta| < 2.4$,
 or on the forward JVT~\cite{Aaboud:2017pou} output for jets with $\pt<50~\gev$ and $|\eta| > 2.5$.
@@
 an average 70\% efficiency to tag a $b$-quark jet, with a light-jet\footnote{Light-jet refers to a jet originating from the hadronisation of a light quark 
-($u$, $d$, $s$) or a gluon.} rejection factor of $\sim$381 and a charm-jet rejection factor of $\sim$12, as determined for jets with
+($u$, $d$, $s$) or a gluon.} rejection factor of about 380 and a charm-jet rejection factor of about 12, as determined for jets with
 $\pt >20~\gev$ and $|\eta|<2.5$ in simulated $\ttbar$ events. In contrast, the $\Hbb$ search employs a tighter $b$-tagging requirement, 
-corresponding to an average efficiency of 60\% to tag a $b$-quark jet, and light-jet and charm-jet rejection factors of 1538 and 34, respectively.
+corresponding to an average efficiency of 60\% to tag a $b$-quark jet, and light-jet and charm-jet rejection factors of about 1500 and 34, respectively.
 
@@
 The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\had$ 
-decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-quark/gluon jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
+decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
 Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
@@
 
-Overlaps between candidate objects are removed sequentially. In the $\Hbb$ search, firstly, electron candidates that lie 
+Overlaps between reconstructed objects are removed sequentially. In the $\Hbb$ search, firstly, electron candidates that lie 
 within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
@@
 The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
-that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
+that are likely to have arisen in the decay of hadrons and to retain the overlapping jet instead. 
 Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
@@
 removal of jets whose axis lies within $\Delta R=0.2$ of the highest-$\pt$ (leading) or the two leading $\had$ candidates (depending on the
-analysis channel, see Section~\ref{sec:data_presel}). In addition, the muon--jet overlap removal is slightly different:
+analysis channel). In addition, the muon--jet overlap removal is slightly different:
 if a muon lies within $\Delta R = 0.2$ of the axis of a jet, the jet is removed if either it has fewer than three tracks originating from the 

### 2018-10-03 sections/strategy_Hbb.tex
porting language editor comments

@@
 
-This section presents an overview of the analysis strategy adopted by the $\Hbb$ search, which
+This section presents an overview of the analysis strategy adopted in the $\Hbb$ search, which
 follows closely that of the previous search performed on the Run 1 dataset~\cite{Aad:2015pja}.
@@
 multiplicities, as illustrated in Figure~\ref{fig:Hbb_Summary}.
-Regions with exactly two $b$-tagged jets are dominated by $\ttbar$+light jets, while regions with 
+Regions with exactly two $b$-tagged jets are dominated by $\ttbar$+light-jets, while regions with 
 at least four $b$-tagged jets are dominated by \ttbin. Intermediate compositions are found in regions with exactly three 
-$b$-tagged jets.  Most of the $\ttbar$+light-jets background in these regions has a charm jet from the hadronic $W$ boson 
+$b$-tagged jets.  Most of the $\ttbar$+light-jets background in these regions have a charm jet from the hadronic $W$ boson 
 decay  being $b$-tagged, in addition to the two $b$-jets from the top quark decays.
@@
 the selected signal events have a $H \to b\bar{b}$ decay in more than 97\% of the events.
-The rest of the regions have significantly lower signal-to-background ratios, but they are used for the purpose of improving 
-the $\ttbar$+jets background prediction and constraining the related systematic uncertainties (see Section~\ref{sec:systematics})
-through a likelihood fit to data (see Section~\ref{sec:stat_analysis}).  
+The other regions have significantly lower signal-to-background ratios, but they are used for the purpose of improving 
+the $\ttbar$+jets background prediction and constraining the related systematic uncertainties
+through a likelihood fit to data.  
 Because of somewhat larger fraction of $\Hc$ signal in the regions with exactly three $b$-tagged jets,
@@
 before the fit to data (``Pre-Fit''). All events satisfy the preselection requirements, whereas those with exactly two $b$-tagged jets are
-in addition required to have a value of the the likelihood discriminant above 0.6 (see Section~\ref{sec:likelihood_discriminant}).
-Backgrounds are normalised to their nominal cross sections discussed in Section~\ref{sec:simulations}.
+in addition required to have a value of the likelihood discriminant above 0.6 (see Section~\ref{sec:likelihood_discriminant}).
+Backgrounds are normalised to their nominal cross sections.
 The small contributions from $W/Z$+jets,  single-top-quark, diboson and multijet backgrounds are combined into a single background source 
@@
 Since both signal and background result from the $\ttbar$ decay, 
-their discrimination is a challenge and it is based on a few experimental attributes.  
+their discrimination is a challenge and it is based on a few measured quantities.  
 %there are few experimental handles available to discriminate between them. 
-The most prominent features are the different resonances present in the decay (i.e. the Higgs boson in the case 
+The most prominent features are the different resonances present in the decay (the Higgs boson in the case 
 of the $\Hq$ signal and a hadronically decaying $W$ boson in the case of the $\ttbar \to WbWb$ background), and the different flavours of the 
@@
 The LH variable for a given event is defined as:
-\begin{equation}
+\begin{equation*}
 LH(\mathbf{x}) = \frac{P^\textrm{sig}(\mathbf{x}) }{P^\textrm{sig}(\mathbf{x}) +P^\textrm{bkg}(\mathbf{x}) },
 \label{eq:D}
-\end{equation}
+\end{equation*}
 where $P^\textrm{sig}(\mathbf{x}) $ and $P^\textrm{bkg}(\mathbf{x}) $ represent the probability density functions (pdf) of a given event under
@@
 that correspond to the expected resonances in the event (the leptonically decaying $W$ boson, the Higgs boson or the hadronically 
-decaying $W$ boson, and the corresponding top quark parent particles). These invariant masses are computed from the reconstructed 
+decaying $W$ boson, and the corresponding parent top quarks). These invariant masses are computed from the reconstructed 
 lepton, jets, and missing transverse momentum.
 As in Ref.~\cite{Aad:2015pja}, $P^\textrm{sig}$ and $P^\textrm{bkg}$ are approximated as a product of one-dimensional pdfs for
-each of the invariant masses considered, and averaged among all possible jet-parton matching combinations. 
+each of the invariant masses considered, and averaged among all possible parton--jet matching combinations. 
 Combinations are weighted using information on the per-jet multivariate $b$-tagging discriminant value to suppress the impact from 
-parton-jet assignments that are inconsistent with the correct parton candidates flavour.
+parton--jet assignments that are inconsistent with the correct parton candidates flavour.
 
@@
 the pdfs for both hypotheses, weighted by their relative fractions found in simulated $\ttbar$+jets events, which depend
-on the analysis region considered. Furthermore, in a significant fraction of $\Hq$ simulated events (e.g. about 40--50\% in regions with exactly three $b$-tagged jets), 
+on the analysis region considered. Furthermore, in a significant fraction of $\Hq$ simulated events (about 40--50\% in regions with exactly three $b$-tagged jets), 
 the light-quark jet from the hadronic top-quark decay is not among the selected jets.
@@
 
-Figure~\ref{fig:LHD} compares the shape of the LH discriminant distribution between the $\Hc$ and $\Hu$ signals and the 
+Figure~\ref{fig:LHD} compares the distribution of the LH discriminant between the $\Hc$ and $\Hu$ signals and the 
 $t\bar{t}\to WbWb$ background in each of the analysis regions considered.
-Since this analysis has higher expected sensitivity to a $\Hc$ signal than to a $\Hu$ signal, and, in order to allow probing 
+Since this analysis has higher expected sensitivity to a $\Hc$ signal than to a $\Hu$ signal, in order to allow probing 
 of the $\BR(t\to Hu)$ versus $\BR(t\to Hc)$ plane, the LH discriminant optimised for $\Hc$ is used for both 
@@
 \caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
-distributions in the (4j, 3b) region before performing the fit to data (``Pre-Fit''). 
+distributions in the (4j, 3b) region before the fit to data (``Pre-Fit''). 
 The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
-the jets ($\hthad$), and (d) the invariant mass distribution of the two $b$-tagged jets with lowest 
+the jets ($\hthad$), and (d) the invariant mass of the two $b$-tagged jets with lowest 
 $\Delta R$ separation ($\mbb$).
@@
 \subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep6jin4bin_FcncDiscriminant.eps}} \\
-\caption{$\Hbb$ search: Comparison of the shape of the LH discriminant distribution after preselection 
+\caption{$\Hbb$ search: Comparison of the distribution of the LH discriminant after preselection 
 between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
-and the $t\bar{t}\to WbWb$ background (black solid) in several regions considered in the analysis:
+and the $t\bar{t}\to WbWb$ background (black solid) in different regions considered in the analysis:
 (a) (4j, 2b), (b) (4j, 3b), (c) (4j, 4b), (d) (5j, 2b), (e) (5j, 3b), (f) (5j, $\geq$4b), (g) ($\geq$6j, 2b), 

### 2018-10-03 sections/strategy_Htautau.tex
porting language editor comments

@@
 
-The analysis strategy adopted by the $\Htautau$ search follows closely that developed in Ref.~\cite{Chen:2015nta} and is summarised in this section.
+The analysis strategy adopted in the $\Htautau$ search follows closely that developed in Ref.~\cite{Chen:2015nta} and is summarised in this section.
 
@@
 %The event reconstruction strategy used~\cite{Chen:2015nta} is summarised in the following.
-The event reconstruction is based on the strategy previously used in Ref.~\cite{Chen:2015nta}.
+The event reconstruction is based on the strategy used in Ref.~\cite{Chen:2015nta}.
 
@@
 top quark ($t \to Wb \to qqb$) are rejected, as the $t \to Hq$ decay cannot be reconstructed due to the missing light-quark jet.
-As in Ref.~\cite{Chen:2015nta}, this compatibility is assessed via a likelihood function that depens on the reconstructed mass of the three-jet 
+This compatibility is assessed via a likelihood function that depens on the reconstructed mass of the three-jet 
 system and the two non-$b$-tagged jets.
-For the remaining events, the selected jets are assigned to the different top quark decay products via a criterion based on 
+For the remaining events, the selected jets are assigned to the different top-quark decay products via a criterion based on 
 minimising a sum of angular distances between objects. Finally, the four-momenta of the invisible decay products for each $\tau$-lepton decay 
@@
 $x_2^{\text{fit}}$				& $\times$  & $\times$  & $\times$  & $\times$ \\
-$m_{b j_1 j_2 }$             	   		&             & $\times$  &             & $\times$ \\ \hline
+$m_{b j_1 j_2 }$             	   		&             & $\times$  &             & $\times$ \\ 
+%\hline
 \bottomrule\bottomrule
@@
 
-Boosted decision trees (BDT)~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} are used in each SR to improve the separation between signal and background. 
+Boosted decision trees~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} are used in each SR to improve the separation between signal and background. 
 %The separate training exploits differences in event kinematics across SRs.  
@@
 \item $\met$ $\phi$ centrality: a variable that quantifies the relative angular position of the $\mpt$ with respect to the 
-visible tau decay products in the transverse plane. The transverse plane is transformed such that the direction of the tau decay products are 
-orthogonal, and that the smaller angle between the tau decay products defines the positive quadrant of the transformed plane. 
-The $\met$ $\phi$ centrality is defined as the sum of the $x$- and $y$-components of the $\mpt$ unit vector in this transformed plane.
+visible $\tau$-lepton decay products in the transverse plane. The transverse plane is transformed such that the direction of the $\tau$-lepton decay products are 
+orthogonal, and that the smaller angle between the $\tau$-lepton decay products defines the positive quadrant of the transformed plane. 
+The $\met$ $\phi$ centrality is defined as the sum of the $x$ and $y$ components of the $\mpt$ unit vector in this transformed plane.
 %\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
@@
 \item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector perpendicular to the fitted $\mpt$ vector.
-\item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically-decaying $W$ boson.
+\item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically decaying $W$ boson.
 \item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance to the $\lep$ candidate.
@@
 
-Among these variables, the most discriminating ones are $m_{\tau\tau}^{\text{fit}}$, $p_{\text{T},2}$, $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$.
+Among these variables, the most discriminating are $m_{\tau\tau}^{\text{fit}}$, $p_{\text{T},2}$, $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$.
 A comparison between data and background prediction for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:BDT_inputs_lephad} and~\ref{fig:BDT_inputs_hadhad}.
@@
 \caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of some of the most
-important BDT input variables in the $\lephad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
+discriminating BDT input variables in the $\lephad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
 $m_{\tau\tau}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
@@
 The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
-added on top of the background prediction.
+added to the background prediction.
 The first and the last bins in all figures contain the underflow and overflow respectively.
 The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
-The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
+The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
 which is determined via a likelihood fit to data.}
@@
 \caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of two of the most 
-important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
+discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
 $m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
@@
 The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
-added on top of the background prediction.
+added to the background prediction.
 The first and the last bins in the figures in (a) and (b) contain the underflow and overflow respectively.
 The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
-The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
+The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
 which is determined via a likelihood fit to data.} 
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh4j/canv_.eps}} \\
-\caption{$\Htautau$ search: Comparison of the shape of the BDT discriminant distribution after preselection between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
+\caption{$\Htautau$ search: Comparison of the distribution of the BDT discriminant after preselection between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
 and the total background (black solid) in the different search regions considered:

### 2018-10-03 sections/systematic_uncertainties.tex
porting language editor comments

@@
 Several sources of systematic uncertainty are considered that can affect the normalisation of signal 
-and background and/or the shape of their corresponding final discriminant distributions.  
+and background and/or the shape of their corresponding discriminant distributions.  
 Each source is considered to be uncorrelated with the other sources.  
@@
 identification and isolation (in the case of electrons and muons) efficiencies, as well as the momentum scale and resolution. 
-These are measured in data using $Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events ($\ell =e, \mu$)~\cite{ATLAS-CONF-2016-024,Aad:2016jkr} 
+These are measured using $Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events ($\ell =e, \mu$)~\cite{ATLAS-CONF-2016-024,Aad:2016jkr} 
 in the case of electrons and muons, and using $Z\to \tau^+\tau^-$ events in the case of $\had$ candidates~\cite{ATLAS-CONF-2017-029}.
@@
 Since the $\ttbar$ sample used to measure the $c$-jet tagging efficiency overlaps with the analysis sample, the $\Hbb$ search uses
-instead the $W$+$c$-jet based scale factors.  
-In the case of the $\Hbb$ ($\Htautau$) search, the uncertainties on these scale factors include a total of six independent sources affecting $b$-jets, one (three) source(s) affecting $c$-jets, and 17 sources affecting light jets.
+instead the $W$+$c$-jet scale factors.  
+In the case of the $\Hbb$ ($\Htautau$) search, the uncertainties on these scale factors include a total of six independent sources affecting $b$-jets, one (three) source(s) affecting $c$-jets, and 17 sources affecting light-jets.
 These systematic uncertainties are taken as uncorrelated between $b$-jets, $c$-jets, and light-jets. 
@@
 cross section~\cite{Czakon:2011xx}, including contributions from varying the factorisation and renormalisation 
-scales, as well as from the top quark mass, the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution 
+scales, as well as from the top-quark mass, the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution 
 to the overall theoretical uncertainty in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
@@
 The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
-{\powheg}+{\pythiaeight} with a prediction from \textsc{Sherpa}~2.2.1. For the latter, the matrix element calculation is performed 
+{\powheg}+{\pythiaeight} with a prediction from \textsc{Sherpa}~2.2.1. For the latter, the matrix-element calculation is performed 
 for up to two partons at NLO and up to four partons at LO using \textsc{Comix} and \textsc{OpenLoops}, and
@@
 The latter uses MMHT2014 LO~\cite{Harland-Lang:2014zoa} PDF set in combination with the H7UE tune~\cite{Bellm:2015jjp}.
-Additionally, the uncertainty on the modelling of additional radiation is assessed with two alternative {\powheg}+{\pythiaeight} samples:
-a sample with increased radiation (referred to as ``radHi'') is obtained by decreasing the renormalisation and factorisation scales  
+The uncertainty of the modelling of additional radiation is assessed with two alternative {\powheg}+{\pythiaeight} samples:
+a sample with increased radiation (referred to as radHi) is obtained by decreasing the renormalisation and factorisation scales  
 by a factor of two, doubling the $h_{\textrm{damp}}$ parameter, and using the Var3c upward variation of the A14 parameter set;
-a sample with decreased radiation (referred to as ``radLow'') is obtained by increasing the scales by a factor of two 
+a sample with decreased radiation (referred to as radLow) is obtained by increasing the scales by a factor of two 
 and using the Var3c downward variation of the A14 set~\cite{ATL-PHYS-PUB-2016-004}.
 
-In the case of the $\Hbb$ search, where the $\ttbar$+HF background plays a more prominent role, a more 
+In the case of the $\Hbb$ search, where the $\ttbar$+HF background plays a prominent role, a more 
 detailed treatment of its associated systematic uncertainties is made. In particular, since several analysis 
@@
 production are different, all above uncertainties on $\ttbar$+jets
-background modelling (NLO generator, PS \& Had, and radHi/radLow), except the uncertainty on the inclusive cross-section, are
+background modelling (NLO generator, PS \& Had, and radHi/radLow), except the uncertainty of the inclusive cross section, are
 considered to be uncorrelated among these processes.
-Additional uncertainties on the \ttbin\ background are considered associated with the NLO prediction from {\ShOL}, 
+Additional uncertainties of the \ttbin\ background are considered associated with the NLO prediction from {\ShOL}, 
 which is used for reweighting the nominal {\powheg}+{\pythiaeight} prediction. 
@@
 the contributions to the \ttbin\ background originating from multiple parton interactions.
-Finally, an extra uncertainty on the \ttbin\ background is assigned by comparing 
+Finally, an extra uncertainty on the \ttbin\ background is assigned by 
+comparing
 the predictions from {\powheg}+{\pythiaeight} and {\ShOL} 4F (5F vs 4F).
@@
 the normalisation of the $\ttbar$+light-jets background at the particle level is adjusted accordingly.
-Further details are available in Ref.~\cite{Aaboud:2017rss}.
+% Further details are available in Ref.~\cite{Aaboud:2017rss}.
 
@@
 Uncertainties affecting the modelling of the single-top-quark background include a 
-$+5\%$/$-4\%$ uncertainty in the total cross section estimated as a weighted average 
+$+5\%$/$-4\%$ uncertainty of the total cross section estimated as a weighted average 
 of the theoretical uncertainties in $t$-, $tW$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
@@
 These uncertainties are treated as fully correlated among single-top-quark production processes, but uncorrelated with the
-corresponding uncertainty in the $\ttbar$+jets background.
+corresponding uncertainty of the $\ttbar$+jets background.
 An additional systematic uncertainty on $tW$-channel production concerning the separation 
 between $t\bar{t}$ and $tW$ at NLO is assessed by comparing
-the nominal sample, which uses the so-called ``diagram removal'' scheme~\cite{Frixione:2008yi}, with an alternative sample
-using the ``diagram subtraction'' scheme~\cite{Frixione:2008yi}.
+the nominal sample, which uses the diagram removal scheme~\cite{Frixione:2008yi}, with an alternative sample
+using the diagram subtraction scheme~\cite{Frixione:2008yi}.
 
-Uncertainties on the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah},
+Uncertainties of the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah},
 as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
@@
 Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the selected jet multiplicity,  
-i.e. 34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively.
+34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively.
 Recent comparisons between data and {\sherpa}~2.1.1 for $WZ(\to \ell\nu\ell\ell) + \geq$4 jets show
@@
 
-Uncertainties in the $\ttbar V$ and $\ttbar H$ cross sections are 15\% and $+10\%$/$-13\%$, respectively,
-from the uncertainties in their respective NLO theoretical cross sections~\cite{Campbell:2012dh,Garzelli:2012bn,deFlorian:2016spz}.
+Uncertainties of the $\ttbar V$ and $\ttbar H$ cross sections are 15\% and $+10\%$/$-13\%$, respectively,
+from the uncertainties of their respective NLO theoretical cross sections~\cite{Campbell:2012dh,Garzelli:2012bn,deFlorian:2016spz}.
 
-Uncertainties on the data-driven multijet background in the $\Hbb$ search estimate include
-contributions from the limited sample size in data, particularly at high jet and $b$-tag multiplicities, as 
+Uncertainties of the data-driven multijet background in the $\Hbb$ search include
+contributions from the limited size of the data sample, particularly at high jet and $b$-tag multiplicities, as 
 well as from the uncertainty on the rate of fake leptons, estimated in 
-different control regions (e.g. selected with a requirement on either the maximum $\met$ or $\mtw$). 
+different control regions (selected with a requirement on either the maximum $\met$ or $\mtw$). 
 A combined normalisation uncertainty of 50\% due 
@@
 is applied as an uncertainty on the prediction in the nominal SR.
-In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\had$ candidate from the simulation that are added to the fake $\had$ template in the $\hadhad$ channel as part of the fake $\had$ background estimation procedure (see Section~\ref{sec:faketaus}).
+In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\had$ candidate from the simulation that are added to the fake $\had$ template in the $\hadhad$ channel as part of the fake $\had$ background estimation procedure.
 This uncertainty, associated with the modelling of the fake $\had$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\had$ candidate.
@@
 Several normalisation and shape uncertainties are taken into account for the $\Hq$ signal.
-The uncertainty on the $\ttbar$ cross section also applies to the $\Hq$ signal and is taken to be the same as, 
-and fully correlated with, the uncertainty assigned to the $\ttbar \to WbWb$ background (see Sect.~\ref{sec:syst_bkgmodeling}).
-Uncertainties on the Higgs boson branching ratios are taken into account
+The uncertainty of the $\ttbar$ cross section also applies to the $\Hq$ signal and is taken to be the same as, 
+and fully correlated with, the uncertainty assigned to the $\ttbar \to WbWb$ background.
+Uncertainties of the Higgs boson branching ratios are taken into account
 following the recommendation in Ref.~\cite{deFlorian:2016spz}.
@@
 with the choice of parton shower and hadronisation model, are estimated from the comparison of the nominal
-and alternative $\ttbar \to WbWb$ background samples (see discussion in Sect.~\ref{sec:syst_bkgmodeling}) and applied to $\Hq$ signal. 
+and alternative $\ttbar \to WbWb$ background samples (discussed in Section~\ref{sec:syst_bkgmodeling}) and applied to $\Hq$ signal. 
 These modelling uncertainties are taken to be uncorrelated with those affecting the $\ttbar \to WbWb$ background.

### 2018-10-11 sections/strategy_Htautau.tex
language_editor

@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh4j/canv_.eps}} \\
-\caption{$\Htautau$ search: Comparison of the distribution of the BDT discriminant after preselection between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
+\caption{$\Htautau$ search: Comparison of the shape of the BDT discriminant distribution after preselection between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
 and the total background (black solid) in the different search regions considered:

### 2018-10-11 sections/systematic_uncertainties.tex
language_editor

@@
 well as from the uncertainty on the rate of fake leptons, estimated in 
-different control regions (selected with a requirement on either the maximum $\met$ or $\mtw$). 
+different control regions (e.g. selected with a requirement on either the maximum $\met$ or $\mtw$). 
 A combined normalisation uncertainty of 50\% due 

### 2018-10-11 ANA-TOPQ-2017-07-PAPER-auxmat.tex
extra language editor comments

@@
 %-------------------------------------------------------------------------------
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[htbp]
+\small
+\begin{center}
+\begin{tabular}{l*{3}{c}}
+\hline\hline
+ & 4j, 2b & 4j, 3b & 4j, 4b \\
+\hline
+$\Hc$ & $ 1990 \pm 190 $ &   $ 1260 \pm 190 $ &   $ 24.8 \pm 9.5 $ \\
+$\Hu$ & $ 1950 \pm 190 $ &   $ 1110 \pm 170 $ &   $ 19 \pm 16 $ \\ 
+\hline
+$\ttbar$+light-jets & $ 87000 \pm 11000 $ &   $ 4300 \pm 1200 $ &   $ 10.2 \pm 9.6 $ \\ 
+$\ttcin$ & $ 8300 \pm 4300 $ &   $ 1050 \pm 640 $ &   $ 3.2 \pm 3.3 $ \\ 
+$\ttbin$ & $ 3620 \pm 440 $ &   $ 2900 \pm 580 $ &   $ 95 \pm 33 $ \\ 
+$t\bar{t}V$ & $ 176 \pm 31 $ &   $ 34.8 \pm 6.9 $ &   $ 2.84 \pm 0.74 $ \\ 
+$t\bar{t}H$ & $ 61.7 \pm 9.2 $ &   $ 48.7 \pm 8.3 $ &   $ 5.1 \pm 1.0 $ \\
+$W$+jets & $ 5400 \pm 2400 $ &   $ 280 \pm 130 $ &   $ 3.3 \pm 1.8 $ \\ 
+$Z$+jets & $ 2120 \pm 960 $ &   $ 115 \pm 55 $ &   $ 2.4 \pm 1.4 $ \\ 
+Single top & $ 7100 \pm 1300 $ &   $ 400 \pm 120 $ &   $ 7.8 \pm 6.0 $ \\ 
+Diboson & $ 267 \pm 97 $ &   $ 17.2 \pm 6.5 $ &   $ 0.58 \pm 0.27 $ \\ 
+Multijet & $ 7800 \pm 3400 $ &   $ 930 \pm 360 $ &   $ 31 \pm 17 $ \\
+\hline
+Total background & $ 120000 \pm 15000 $ &   $ 10000 \pm 2000 $ &   $ 162 \pm 44 $ \\ 
+\hline
+Data & 120572  & 11275  & 176  \\
+\hline\hline    
+\end{tabular}
+%%\\
+\vspace{0.2cm}
+
+\begin{tabular}{l*{3}{c}}
+\hline\hline
+ & 5j, 2b & 5j, 3b & 5j, $\geq$4b \\
+\hline
+$\Hc$ & $ 1260 \pm 240 $ &   $ 1010 \pm 190 $ &   $ 26.2 \pm 8.8 $ \\ 
+$\Hu$ & $ 1160 \pm 240 $ &   $ 930 \pm 160 $ &   $ 23 \pm 12 $ \\ 
+\hline
+$\ttbar$+light-jets & $ 41300 \pm 9100 $ &   $ 3200 \pm 900 $ &   $ 13 \pm 11 $ \\ 
+$\ttcin$ & $ 5900 \pm 3100 $ &   $ 1320 \pm 760 $ &   $ 21 \pm 17 $ \\ 
+$\ttbin$ & $ 3040 \pm 250 $ &   $ 4300 \pm 760 $ &   $ 310 \pm 83 $ \\ 
+$t\bar{t}V$  &   $ 175 \pm 29 $ &   $ 67 \pm 12 $ &   $ 9.1 \pm 2.0 $ \\ 
+$t\bar{t}H$  &   $ 81.3 \pm 9.5 $ &   $ 103 \pm 15 $ &   $ 18.4 \pm 3.5 $ \\ 
+$W$+jets  &   $ 2400 \pm 1100 $ &   $ 186 \pm 89 $ &   $ 7.3 \pm 3.9 $ \\ 
+$Z$+jets  &   $ 780 \pm 350 $ &   $ 83 \pm 39 $ &   $ 6.1 \pm 3.8 $ \\ 
+Single top  &   $ 2990 \pm 780 $ &   $ 350 \pm 110 $ &   $ 16.6 \pm 7.6 $ \\ 
+Diboson  &   $ 125 \pm 56 $ &   $ 13.7 \pm 6.3 $ &   $ 0.89 \pm 0.47 $ \\ 
+Multijet  &   $ 3700 \pm 1500 $ &   $ 500 \pm 230 $ &   $ 3.8 \pm 4.9 $ \\ 
+\hline
+Total background &  $ 60000 \pm 11000 $ &   $ 10100 \pm 1900 $ &   $ 405 \pm 98 $ \\
+\hline
+Data & 58557  & 11707  & 466  \\ 
+\hline\hline    
+\end{tabular}
+%%\\
+\vspace{0.2cm}
+
+\begin{tabular}{l*{3}{c}}
+\hline\hline
+ & $\geq$ 6j, 2b & $\geq$6j, 3b & $\geq$6j, $\geq$4b \\
+\hline
+$\Hc$ & $ 760 \pm 250 $ &   $ 690 \pm 210 $ &   $ 60 \pm 60 $ \\ 
+$\Hu$ & $ 680 \pm 240 $ &   $ 570 \pm 180 $ &   $ 36 \pm 40 $ \\ 
+\hline
+$\ttbar$+light-jets  &   $ 22900 \pm 8100 $ &   $ 2400 \pm 910 $ &   $ 14 \pm 18 $ \\ 
+$\ttcin$  &   $ 5300 \pm 3000 $ &   $ 1800 \pm 1100 $ &   $ 29 \pm 23 $ \\ 
+$\ttbin$  &   $ 3270 \pm 510 $ &   $ 7300 \pm 1300 $ &   $ 1100 \pm 240 $ \\ 
+$t\bar{t}V$  &   $ 229 \pm 41 $ &   $ 154 \pm 30 $ &   $ 30.8 \pm 6.9 $ \\ 
+$t\bar{t}H$  &   $ 140 \pm 18 $ &   $ 262 \pm 39 $ &   $ 71 \pm 14 $ \\ 
+$W$+jets  &   $ 1360 \pm 630 $ &   $ 200 \pm 100 $ &   $ 15.4 \pm 8.2 $ \\ 
+$Z$+jets  &   $ 410 \pm 200 $ &   $ 63 \pm 32 $ &   $ 5.1 \pm 4.0 $ \\ 
+Single top  &   $ 1510 \pm 560 $ &   $ 360 \pm 160 $ &   $ 34 \pm 20 $ \\ 
+Diboson  &   $ 93 \pm 47 $ &   $ 18.5 \pm 9.6 $ &   $ 2.1 \pm 1.2 $ \\ 
+Multijet  &   $ 1920 \pm 820 $ &   $ 780 \pm 360 $ &   $ 43 \pm 29 $ \\ 
+\hline
+Total background &  $ 37100 \pm 9600 $ &   $ 13400 \pm 2600 $ &   $ 1360 \pm 290 $ \\ 
+\hline
+Data & 35886  & 14877  & 1335  \\ 
+\hline\hline    
+\end{tabular}
+%%\\
+%\vspace{0.2cm}
+
+%
+\end{center}
+%\vspace{-0.5cm}
+\caption{
+$\Hbb$ search: Predicted and observed yields in each of the analysis regions considered.
+The prediction is shown before the fit to data. Also shown are the signal expectations for 
+$\Hc$ and $\Hu$ assuming $\BR(t\to Hc)=1\%$ and $\BR(t\to Hu)=1\%$ respectively.
+The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
+excluding the normalisation uncertainty of the $\ttbin$ background, which is determined via a likelihood fit to data.
+}
+\label{tab:Hbb_Prefit_Yields_Unblind}
+\end{table} 
+%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[htbp]
+\small
+\begin{center}
+\begin{tabular}{l*{3}{c}}
+\hline\hline
+ & 4j, 2b & 4j, 3b & 4j, 4b \\
+\hline
+$\Hc$  &   $ -30 \pm 470 $ &   $ -20 \pm 300 $ &   $ -0.4 \pm 5.9 $ \\ 
+\hline
+$\ttbar$+light-jets  &    $ 82900 \pm 4200 $ &   $ 4900 \pm 500 $ &   $ 16 \pm 12 $ \\ 
+$\ttcin$  &   $ 11400 \pm 4800 $ &   $ 1360 \pm 550 $ &   $ 5.9 \pm 4.2 $ \\ 
+$\ttbin$  &   $ 4270 \pm 590 $ &   $ 3400 \pm 350 $ &   $ 110 \pm 17 $ \\ 
+$t\bar{t}V$  &    $ 174 \pm 28 $ &   $ 35.0 \pm 5.9 $ &   $ 2.69 \pm 0.55 $ \\ 
+$t\bar{t}H$  &   $ 62.6 \pm 7.8 $ &   $ 47.3 \pm 6.3 $ &   $ 4.68 \pm 0.69 $ \\ 
+$W$+jets  &   $ 4800 \pm 1800 $ &   $ 260 \pm 100 $ &   $ 2.9 \pm 1.3 $ \\ 
+$Z$+jets  &    $ 1870 \pm 730 $ &   $ 102 \pm 41 $ &   $ 1.9 \pm 1.0 $ \\ 
+Single-top  &  $ 6360 \pm 980 $ &   $ 393 \pm 96 $ &   $ 7.6 \pm 5.2 $ \\ 
+Diboson  &   $ 242 \pm 84 $ &   $ 16.3 \pm 5.7 $ &   $ 0.50 \pm 0.22 $ \\ 
+Multijet  &   $ 9000 \pm 3500 $ &   $ 820 \pm 240 $ &   $ 29 \pm 16 $ \\ 
+\hline
+Total & $ 121100 \pm 2200 $ &   $ 11290 \pm 280 $ &   $ 181 \pm 23 $ \\ 
+\hline
+Data & 120572  & 11275  & 176  \\ 
+\hline\hline      
+\end{tabular}
+%%\\
+\vspace{0.2cm}
+
+\begin{tabular}{l*{3}{c}}
+\hline\hline
+ & 5j, 2b & 5j, 3b & 5j, $\geq$4b \\
+\hline
+$\Hc$  &   $ -20 \pm 300 $ &   $ -10 \pm 240 $ &   $ -0.4 \pm 6.2 $ \\ 
+\hline
+$\ttbar$+light-jets  &   $ 38000 \pm 3100 $ &   $ 3480 \pm 460 $ &   $ 15.8 \pm 9.5 $ \\ 
+$\ttcin$  &   $ 8300 \pm 3400 $ &   $ 2000 \pm 760 $ &   $ 39 \pm 18 $ \\ 
+$\ttbin$  &   $ 3410 \pm 470 $ &   $ 4900 \pm 460 $ &   $ 356 \pm 29 $ \\ 
+$t\bar{t}V$  &   $ 168 \pm 26 $ &   $ 65 \pm 10 $ &   $ 8.2 \pm 1.4 $ \\ 
+$t\bar{t}H$  &   $ 81.1 \pm 8.9 $ &   $ 99 \pm 12 $ &   $ 16.6 \pm 2.3 $ \\ 
+$W$+jets  &   $ 2080 \pm 820 $ &   $ 169 \pm 68 $ &   $ 6.0 \pm 2.8 $ \\ 
+$Z$+jets  &   $ 700 \pm 270 $ &   $ 74 \pm 30 $ &   $ 5.6 \pm 3.2 $ \\ 
+Single-top  &   $ 2560 \pm 590 $ &   $ 322 \pm 90 $ &   $ 13.3 \pm 5.8 $ \\ 
+Diboson  &   $ 111 \pm 48 $ &   $ 12.5 \pm 5.4 $ &   $ 0.76 \pm 0.39 $ \\ 
+Multijet  &   $ 3380 \pm 950 $ &   $ 560 \pm 230 $ &   $ 3.6 \pm 4.8 $ \\ 
+\hline
+Total & $ 58800 \pm 1400 $ &   $ 11690 \pm 360 $ &   $ 465 \pm 29 $ \\ 
+\hline
+Data & 58557  & 11707  & 466  \\ 
+\hline\hline      
+\end{tabular}
+%%\\
+\vspace{0.2cm}
+
+\begin{tabular}{l*{3}{c}}
+\hline\hline
+ & $\geq$6j, 2b & $\geq$6j, 3b & $\geq$6j, $\geq$4b \\
+\hline
+$\Hc$  &   $ -10 \pm 180 $ &   $ -10 \pm 160 $ &   $ -1 \pm 14 $ \\ 
+\hline
+$\ttbar$+light-jets  &   $ 20100 \pm 2500 $ &   $ 2560 \pm 490 $ &   $ 21 \pm 23 $ \\ 
+$\ttcin$  &   $ 7800 \pm 3300 $ &   $ 3000 \pm 1100 $ &   $ 59 \pm 25 $ \\ 
+$\ttbin$  &   $ 3390 \pm 480 $ &   $ 7510 \pm 760 $ &   $ 1106 \pm 83 $ \\ 
+$t\bar{t}V$  &   $ 213 \pm 34 $ &   $ 145 \pm 24 $ &   $ 27.0 \pm 4.8 $ \\ 
+$t\bar{t}H$  &   $ 134 \pm 15 $ &   $ 240 \pm 30 $ &   $ 61.6 \pm 8.8 $ \\ 
+$W$+jets  &   $ 1200 \pm 470 $ &   $ 183 \pm 75 $ &   $ 12.5 \pm 5.7 $ \\ 
+$Z$+jets  &   $ 350 \pm 150 $ &   $ 56 \pm 24 $ &   $ 3.5 \pm 2.2 $ \\ 
+Single-top  &   $ 1220 \pm 400 $ &   $ 310 \pm 120 $ &   $ 27 \pm 14 $ \\ 
+Diboson  &   $ 82 \pm 40 $ &   $ 16.7 \pm 8.2 $ &   $ 1.70 \pm 0.90 $ \\ 
+Multijet  &   $ 1540 \pm 530 $ &   $ 860 \pm 340 $ &   $ 37 \pm 26 $ \\ 
+\hline
+Total &   $ 36000 \pm 1300 $ &   $ 14880 \pm 500 $ &   $ 1360 \pm 72 $ \\ 
+\hline
+Data & 35886  & 14877  & 1335  \\
+\hline\hline      
+\end{tabular}
+%%\\
+%\vspace{0.2cm}
+
+%
+\end{center}
+%\vspace{-0.5cm}
+\caption{
+$\Hbb$ search: Predicted and observed yields in each of the analysis regions considered.
+The background prediction is shown after the fit to data under the signal-plus-background hypothesis 
+(assuming $\Hc$ as signal).
+The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
+computed taking into account correlations among nuisance parameters and among processes.
+}
+\label{tab:Hbb_Postfit_Yields_Unblind_Hc}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[htbp]
+\small
+\begin{center}
+\begin{tabular}{l*{3}{c}}
+\hline\hline
+ & 4j, 2b & 4j, 3b & 4j, 4b \\
+\hline
+$\Hu$  &   $ 40 \pm 550 $ &   $ 20 \pm 320 $ &   $ 0.4 \pm 5.3 $ \\
+\hline
+$\ttbar$+light-jets  &   $ 82700 \pm 4400 $ &   $ 4860 \pm 530 $ &   $ 15 \pm 12 $ \\ 
+$\ttcin$  &   $ 11500 \pm 5100 $ &   $ 1400 \pm 580 $ &   $ 5.8 \pm 4.2 $ \\ 
+$\ttbin$  &   $ 4260 \pm 590 $ &   $ 3400 \pm 350 $ &   $ 110 \pm 17 $ \\ 
+$t\bar{t}V$  &   $ 173 \pm 28 $ &   $ 34.8 \pm 5.8 $ &   $ 2.68 \pm 0.54 $ \\ 
+$t\bar{t}H$  &   $ 62.4 \pm 7.7 $ &   $ 47.1 \pm 6.2 $ &   $ 4.66 \pm 0.68 $ \\ 
+$W$+jets  &   $ 4800 \pm 1900 $ &   $ 260 \pm 100 $ &   $ 2.9 \pm 1.4 $ \\ 
+$Z$+jets  &   $ 1880 \pm 740 $ &   $ 103 \pm 42 $ &   $ 1.9 \pm 1.0 $ \\ 
+Single-top  &   $ 6380 \pm 990 $ &   $ 392 \pm 96 $ &   $ 7.5 \pm 5.2 $ \\ 
+Diboson  &   $ 243 \pm 85 $ &   $ 16.3 \pm 5.7 $ &   $ 0.50 \pm 0.22 $ \\ 
+Multijet  &   $ 9000 \pm 3500 $ &   $ 810 \pm 240 $ &   $ 29 \pm 16 $ \\ 
+\hline
+Total &   $ 121000 \pm 2300 $ &   $ 11290 \pm 290 $ &   $ 181 \pm 23 $ \\ 
+\hline
+Data & 120572  & 11275  & 176  \\ 
+\hline\hline      
+\end{tabular}
+%%\\
+\vspace{0.2cm}
+
+\begin{tabular}{l*{3}{c}}
+\hline\hline
+ & 5j, 2b & 5j, 3b & 5j, $\geq$4b \\
+\hline
+$\Hu$  &   $ 20 \pm 330 $ &   $ 20 \pm 270 $ &   $ 0.4 \pm 6.6 $ \\ 
+\hline
+$\ttbar$+light-jets  &   $ 37800 \pm 3400 $ &   $ 3450 \pm 500 $ &   $ 15.8 \pm 9.7 $ \\ 
+$\ttcin$  &   $ 8400 \pm 3700 $ &   $ 2000 \pm 800 $ &   $ 39 \pm 19 $ \\ 
+$\ttbin$  &   $ 3400 \pm 470 $ &   $ 4920 \pm 460 $ &   $ 356 \pm 29 $ \\ 
+$t\bar{t}V$  &   $ 168 \pm 26 $ &   $ 65 \pm 10 $ &   $ 8.2 \pm 1.4 $ \\ 
+$t\bar{t}H$  &   $ 81.0 \pm 8.9 $ &   $ 99 \pm 12 $ &   $ 16.6 \pm 2.3 $ \\ 
+$W$+jets  &   $ 2100 \pm 840 $ &   $ 169 \pm 69 $ &   $ 6.0 \pm 2.8 $ \\ 
+$Z$+jets  &   $ 710 \pm 280 $ &   $ 74 \pm 30 $ &   $ 5.5 \pm 3.2 $ \\ 
+Single-top  &   $ 2570 \pm 600 $ &   $ 320 \pm 90 $ &   $ 13.4 \pm 5.8 $ \\ 
+Diboson  &   $ 112 \pm 48 $ &   $ 12.5 \pm 5.5 $ &   $ 0.77 \pm 0.39 $ \\ 
+Multijet  &   $ 3430 \pm 990 $ &   $ 560 \pm 230 $ &   $ 3.6 \pm 4.8 $ \\ 
+\hline
+Total &   $ 58800 \pm 1500 $ &   $ 11690 \pm 380 $ &   $ 465 \pm 29 $ \\ 
+\hline
+Data & 58557  & 11707  & 466  \\ 
+\hline\hline      
+\end{tabular}
+%%\\
+\vspace{0.2cm}
+
+\begin{tabular}{l*{3}{c}}
+\hline\hline
+ & $\geq$6j, 2b & $\geq$6j, 3b & $\geq$6j, $\geq$4b \\
+\hline
+$\Hu$ &   $ 10 \pm 190 $ &   $ 10 \pm 160 $ &   $ 1 \pm 10 $ \\ 
+\hline
+$\ttbar$+light-jets  &   $ 20000 \pm 2700 $ &   $ 2530 \pm 520 $ &   $ 20 \pm 24 $ \\ 
+$\ttcin$  &   $ 7900 \pm 3600 $ &   $ 3000 \pm 1200 $ &   $ 58 \pm 26 $ \\ 
+$\ttbin$  &   $ 3390 \pm 480 $ &   $ 7520 \pm 760 $ &   $ 1106 \pm 83 $ \\ 
+$t\bar{t}V$  &   $ 213 \pm 34 $ &   $ 147 \pm 24 $ &   $ 27.0 \pm 4.8 $ \\ 
+$t\bar{t}H$  &   $ 135 \pm 16 $ &   $ 241 \pm 30 $ &   $ 61.9 \pm 9.0 $ \\ 
+$W$+jets  &   $ 1210 \pm 480 $ &   $ 184 \pm 76 $ &   $ 12.6 \pm 5.8 $ \\ 
+$Z$+jets  &   $ 360 \pm 150 $ &   $ 57 \pm 24 $ &   $ 3.6 \pm 2.2 $ \\ 
+Single-top  &   $ 1240 \pm 400 $ &   $ 320 \pm 120 $ &   $ 27 \pm 14 $ \\ 
+Diboson  &   $ 83 \pm 40 $ &   $ 16.8 \pm 8.3 $ &   $ 1.71 \pm 0.91 $ \\ 
+Multijet  &   $ 1530 \pm 530 $ &   $ 860 \pm 340 $ &   $ 37 \pm 26 $ \\ 
+\hline
+Total &   $ 36000 \pm 1400 $ &   $ 14880 \pm 530 $ &   $ 1360 \pm 73 $ \\ 
+\hline
+Data & 35886  & 14877  & 1335  \\
+\hline\hline      
+\end{tabular}
+%%\\
+%\vspace{0.2cm}
+
+%
+\end{center}
+%\vspace{-0.5cm}
+\caption{
+$\Hbb$ search: Predicted and observed yields in each of the analysis regions considered.
+The background prediction is shown after the fit to data under the signal-plus-background hypothesis (assuming $\Hu$ as signal).
+The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
+computed taking into account correlations among nuisance parameters and among processes.
+}
+\label{tab:Hbb_Postfit_Yields_Unblind_Hu}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[htbp]
+\small
+\begin{center}
+\begin{tabular}{l*{4}{c}}
+\hline\hline
+ & $\lephad$ 3j & $\lephad$ $\geq$4j & $\hadhad$ 3j &  $\hadhad$ $\geq$4j \\
+\hline
+$\Hc$  &   $ 89 \pm 14 $ &   $ 226 \pm 43 $ &   $ 46 \pm 14 $ &   $ 122 \pm 32 $ \\ 
+$\Hu$  &   $ 100 \pm 17 $ &   $ 237 \pm 47 $ &   $ 32 \pm 10 $ &   $ 114 \pm 28 $ \\ 
+\hline
+Fake $\had$  &   $ 2828 \pm 78 $ &   $ 3200 \pm 100 $ &   $ 710 \pm 110 $ &   $ 500 \pm 62 $ \\
+Top (real $\had$)  &   $ 3840 \pm 720 $ &   $ 3160 \pm 890 $ &   $ 113 \pm 72 $ &   $ 117 \pm 35 $ \\  
+$Z \to \tau\tau$  &   $ 420 \pm 140 $ &   $ 320 \pm 120 $ &   $ 283 \pm 99 $ &   $ 267 \pm 96 $ \\ 
+Other  &   $ 168 \pm 56 $ &   $ 103 \pm 33 $ &   $ 8.9 \pm 2.5 $ &   $ 11.2 \pm 2.5 $ \\ 
+\hline
+Total background  &   $ 7260 \pm 730 $ &   $ 6770 \pm 880 $ &   $ 1120 \pm 120 $ &   $ 900 \pm 120 $ \\ 
+\hline
+Data  & 7259  & 6768  & 1119  & 894  \\
+\hline\hline    
+\end{tabular}
+%%\\
+%\vspace{0.2cm}
+
+%
+\end{center}
+%\vspace{-0.5cm}
+\caption{
+$\Htautau$ search: Predicted and observed yields in each of the analysis regions considered.
+The prediction is shown before the fit to data. Also shown are the signal expectations for 
+$\Hc$ and $\Hu$ assuming $\BR(t\to Hc)=1\%$ and $\BR(t\to Hu)=1\%$ respectively.
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
+a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
+$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
+The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
+excluding the normalisation uncertainty of the fake $\had$ background, which is determined via a likelihood fit to data.
+}
+\label{tab:Htautau_Prefit_Yields_Unblind}
+\end{table} 
+%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[htbp]
+\small
+\begin{center}
+\begin{tabular}{l*{4}{c}}
+\hline\hline
+ & $\lephad$ 3j & $\lephad$ $\geq$4j & $\hadhad$ 3j &  $\hadhad$ $\geq$4j \\
+\hline
+$\Hc$  &   $ -4.2 \pm 8.2 $ &   $ -11 \pm 21 $ &   $ -2.4 \pm 4.3 $ &   $ -10 \pm 11 $ \\ 
+\hline
+Fake $\had$  &   $ 2290 \pm 680 $ &   $ 2640 \pm 880 $ &   $ 640 \pm 110 $ &   $ 440 \pm 100 $ \\ 
+Top (real $\had$)  &   $ 4300 \pm 670 $ &   $ 3660 \pm 860 $ &   $ 147 \pm 84 $ &   $ 139 \pm 35 $ \\ 
+$Z \to \tau\tau$  &   $ 500 \pm 100 $ &   $ 359 \pm 90 $ &   $ 320 \pm 79 $ &   $ 306 \pm 76 $ \\ 
+Other  &   $ 178 \pm 45 $ &   $ 112 \pm 28 $ &   $ 9.6 \pm 2.6 $ &   $ 12.5 \pm 2.6 $ \\ 
+\hline
+Total  &   $ 7230 \pm 160 $ &   $ 6760 \pm 170 $ &   $ 1117 \pm 65 $ &   $ 893 \pm 45 $ \\
+\hline
+Data & 7259  & 6768  & 1119  & 894 \\ 
+\hline\hline    
+\end{tabular}
+%%\\
+%\vspace{0.2cm}
+
+%
+\end{center}
+%\vspace{-0.5cm}
+\caption{
+$\Htautau$ search: Predicted and observed yields in each of the analysis regions considered.
+The background prediction is shown after the fit to data under the signal-plus-background hypothesis 
+(assuming $\Hc$ as signal).
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
+a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
+$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
+The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
+computed taking into account correlations among nuisance parameters and among processes.
+}
+\label{tab:Htautau_Postfit_Yields_Unblind_Hc}
+\end{table} 
+%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[htbp]
+\small
+\begin{center}
+\begin{tabular}{l*{4}{c}}
+\hline\hline
+ & $\lephad$ 3j & $\lephad$ $\geq$4j & $\hadhad$ 3j &  $\hadhad$ $\geq$4j \\
+\hline
+$\Hu$  &   $ -5.7 \pm 8.6 $ &   $ -14 \pm 21 $ &   $ -2,0 \pm 2.8 $ &   $ -7.1 \pm 9.8 $ \\ 
+\hline
+Fake $\had$  &   $ 2270 \pm 680 $ &   $ 2620 \pm 880 $ &   $ 640 \pm 110 $ &   $ 440 \pm 100 $ \\
+Top (real $\had$)  &   $ 4320 \pm 660 $ &   $ 3680 \pm 860 $ &   $ 148 \pm 84 $ &   $ 140 \pm 35 $ \\ 
+$Z \to \tau\tau$  &   $ 470 \pm 100 $ &   $ 359 \pm 89 $ &   $ 321 \pm 79 $ &   $ 308 \pm 77 $ \\ 
+Other  &   $ 177 \pm 44 $ &   $ 111 \pm 27 $ &   $ 9.7 \pm 2.6 $ &   $ 12.5 \pm 2.6 $ \\ 
+\hline
+Total  &   $ 7230 \pm 160 $ &   $ 6760 \pm 160 $ &   $ 1118 \pm 66 $ &   $ 892 \pm 45 $ \\ 
+\hline
+Data  & 7259  & 6768  & 1119  & 894  \\ 
+\hline\hline    
+\end{tabular}
+%%\\
+%\vspace{0.2cm}
+
+%
+\end{center}
+%\vspace{-0.5cm}
+\caption{
+$\Htautau$ search: Predicted and observed yields in each of the analysis regions considered.
+The background prediction is shown after the fit to data under the signal-plus-background hypothesis 
+(assuming $\Hu$ as signal).
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
+a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
+$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
+The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
+computed taking into account correlations among nuisance parameters and among processes.
+}
+\label{tab:Htautau_Postfit_Yields_Unblind_Hu}
+\end{table} 
+%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2018-10-11 sections/objects.tex
extra language editor comments

@@
 with a total charge of $\pm 1$. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
-A boosted decision tree (BDT) discriminant using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject
+A boosted decision tree (BDT) discriminant~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject
 jet backgrounds. Three working points labelled loose, medium and tight are defined, and correspond to different $\had$ identification efficiency 
@@
 Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
-and muon candidates are removed. Clusters from identified electrons are not excluded during jet reconstruction. 
+and muon candidates are removed. Energy clusters from identified electrons are not excluded during jet reconstruction. 
 In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 

### 2018-10-11 ANA-TOPQ-2017-07-PAPER-metadata.tex
removed version number
sync local version with master

@@
 % Comment or remove in final version.
-\AtlasVersion{1.2}
+\AtlasVersion{1.3}
 % Abstract - % directly after { is important for correct indentation
@@
 and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, respectively.  
-The high multiplicity of $b$-quark jets, or the presence of hadronically decaying tau leptons, are exploited in the two analyses respectively. 
+The high multiplicity of $b$-quark jets, or the presence of hadronically decaying $\tau$-leptons, are exploited in the two analyses respectively. 
 Multivariate techniques are used to separate the signal from the background, which is dominated by top-quark pair production.
@@
 and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), respectively.
-The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055) respectively. 
-These are the most restrictive direct bounds on $tqH$ interactions measured so far.
+The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
+These are the most restrictive direct bounds on $tqH$ interactions obtained so far.
 }
@@
 %\AtlasRefCode{TOPQ-2017-07}
-\AtlasRefCode{ATLAS-CONF-2018-049}
+%\AtlasRefCode{ATLAS-CONF-2018-049}
 

### 2018-10-11 sections/conclusion.tex

@@
 In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
-are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$ respectively.
-In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
-are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$ respectively.
+are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$, respectively.
+In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios 
+are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$, respectively.
 The combination of these searches with ATLAS searches in diphoton and multilepton final states 
@@
 yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
-and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming that $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$ respectively.
-The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055) respectively. 
+and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming respectively $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$.
+The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
 %Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
-These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions measured so far.
+These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions obtained so far.

### 2018-10-11 sections/data_presel.tex

@@
 
-Both searches are based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ with 25 ns bunch spacing collected 
-with the ATLAS detector in 2015 and 2016, corresponding to an integrated luminosity of $36.1~\ifb$.
+Both searches are based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ with 25 ns bunch spacing collected in 2015 and 2016, corresponding to an integrated luminosity of $36.1~\ifb$.
 Only events recorded with a single-electron trigger, a single-muon trigger, or a ditau trigger under stable beam conditions 
@@
 
-The above requirements apply to the physics objects as defined in Section~\ref{sec:objects}.
+The above requirements apply to the reconstructed objects defined in Section~\ref{sec:objects}.
 %, which are in general different between both searches. 
 These requirements, which ensure a negligible overlap between the $\Hbb$ and $\Htautau$ searches,
-are referred to as the ``preselection'' and are summarised in Table~\ref{tab:preselection}.
+are referred to as the preselection and are summarised in Table~\ref{tab:preselection}.
 

### 2018-10-11 sections/introduction.tex

--- 2018-09-09 sections/introduction.tex
@@
 
-Following the observation of a Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
+Following the observation of the Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
 the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties is underway.
@@
 since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta}. 
-While other FCNC top couplings, $tq\gamma$, $tqZ$, $tqg$, are also enhanced relative to the SM prediction in these scenarios beyond the SM, 
+While other FCNC top couplings, $tq\gamma$, $tqZ$, $tqg$, are also enhanced in these scenarios beyond the SM, 
 the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling. 
@@
 and excellent diphoton mass re\-so\-lu\-tion. 
-Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as ``multileptons",
+Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as multileptons,
 are able to exploit a significantly larger branching ratio for the Higgs 
@@
 %so any excess would be hard to interpret as originating from $t \to Hq$ decays.
-Finally, searches have also been performed considering the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
+Finally, searches have also been performed exploiting the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
 of $\BR(H\to b\bar{b})\simeq 58\%$. Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, 
 as well as the larger integrated luminosity.
-Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% CL of  
+Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of  
 $\BR(t\to Hc)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, and of $\BR(t\to Hc)<0.16\%$ based on
@@
 assumption of $\BR(t\to Hc)=0$. The CMS Collaboration has performed a search using  
-$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} using 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
+$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} with 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
 in upper limits of $\BR(t\to Hc)<0.47\%$ and $\BR(t\to Hu)<0.47\%$, in each case neglecting the other decay mode.
@@
 The searches presented in this paper are focussed on fermionic decay modes.
-Therefore, they help to complete the programme of searches for $t \to Hq$ decays at the ATLAS experiment based on $pp$ collision 
+Therefore, they help to complete the programme of searches for $t \to Hq$ decays of the ATLAS experiment based on $pp$ collision 
 data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
-Two analyses are performed searching for $\ttbar \to WbHq$ production (i.e. $pp \to tH$ production is ignored), and targeting the 
-$H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which will be referred to as ``$\Hbb$ search" and ``$\Htautau$ search", respectively.
+Two analyses are performed searching for $\ttbar \to WbHq$ production (ignoring $pp \to tH$ production), and targeting the 
+$H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which will be referred to as ``$\Hbb$ search'' and ``$\Htautau$ search'', respectively.
 The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, several 
@@
 The $\Htautau$ search selects events with two $\tau$-lepton candidates of which at least one is decaying hadronically, as well as multiple jets. 
-The latter requirement is aimed at selecting events with a hadronically-decaying $W$ boson, since this allows an improved reconstruction of the
+The latter requirement is aimed at selecting events with a hadronically decaying $W$ boson, since this allows an improved reconstruction of the
 event kinematics.

### 2018-10-11 sections/signal_background_modeling.tex

@@
 Backgrounds with non-prompt electrons or muons, with photons or jets misidentified as electrons, or with jets misidentified as $\had$ candidates, 
-generically referred to as ``fake leptons'', are estimated using data-driven methods. 
+generically referred to as fake leptons, are estimated using data-driven methods. 
 The background prediction is further improved during the statistical analysis by performing a likelihood 
@@
 
-Samples of simulated $\ttbar \to WbHq$ events are generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
+Samples of simulated $\ttbar \to WbHq$ events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
 the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix element calculation 
@@
 The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
-initial and final state radiation, referred to as the ``tune'', is used.
+initial and final state radiation, referred to as the tune, was used.
 The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
 assuming an arbitrary branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
-The case of both top quarks decaying into $Hq$ is neglected in the analysis given existing upper limits on $\BR(t \to Hq)$ (see Section~\ref{sec:intro}).
+The case of both top quarks decaying into $Hq$ is neglected in the analysis given the existing upper limits on $\BR(t \to Hq)$ (Section~\ref{sec:intro}).
 
-The nominal sample used to model the $\ttbar$ background is generated with the NLO generator {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd} using the NNPDF3.0 NLO PDF set.
+The nominal sample used to model the $\ttbar$ background was generated with the NLO generator {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd} using the NNPDF3.0 NLO PDF set.
 The {\powheg} model parameter $h_{\textrm{damp}}$, which controls
-matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, is set to 1.5 times the top quark mass. 
-Parton shower, hadronisation, and underlying event are modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
+matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, was set to 1.5 times the top quark mass. 
+Parton shower, hadronisation, and underlying event were modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
 Alternative $\ttbar$ simulation samples used to derive systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
@@
 on the flavour content of additional particle jets not originating from the decay of the $\ttbar$ system.
-Events labelled as either \ttbin\ or \ttcin\ are generically referred to in the following as $\ttbar$+HF events, where HF stands for ``heavy flavour''.
+Events labelled as either \ttbin\ or \ttcin\ are generically referred to in the following as $\ttbar$+HF events, where HF stands for heavy flavour.
 The remaining events are labelled as $\ttbar$+light-jets events, including those with no additional jets. 
@@
 %This reweighting is applied to the alternative $\ttbar$ samples as well.
-This reweighting is also applied to the alternative $\ttbar$ samples that are used to study systematic uncertainties (see Section~\ref{sec:syst_bkgmodeling}).
+This reweighting is also applied to the alternative $\ttbar$ samples that are used to study systematic uncertainties.
 
-Samples of single-top-quark events corresponding to the $t$-channel production mechanism are generated with the 
-{\powheg}~v1~\cite{Frederix:2012dh} generator that uses the 4F scheme  for the NLO matrix element calculations
+Samples of single-top-quark events corresponding to the $t$-channel production mechanism were generated with the 
+{\powheg}~v1~\cite{Frederix:2012dh} generator that uses the 4F scheme  for the NLO matrix-element calculations
 and the fixed 4F \textsc{CT10}f\textsc{4}~\cite{Lai:2010vv} PDF set.
-Samples corresponding to the $tW$- and $s$-channel production mechanisms are generated 
+Samples corresponding to the $tW$- and $s$-channel production mechanisms were generated 
 with {\powheg}~v1 using the CT10 PDF set. Overlaps between the $\ttbar$ and $tW$ final states are avoided by using 
-the ``diagram removal'' scheme~\cite{Frixione:2005vw}.
-The parton shower, hadronisation and the underlying event are modelled using {\pythia}~6.428~\cite{Sjostrand:2006za} 
+the diagram removal scheme~\cite{Frixione:2005vw}.
+The parton shower, hadronisation and the underlying event were modelled using {\pythia}~6.428~\cite{Sjostrand:2006za} 
 with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set 
@@
 
-Samples of $W/Z$+jets events are generated with the {\sherpa}~2.2.1~\cite{Gleisberg:2008ta} generator. 
+Samples of $W/Z$+jets events were generated with the {\sherpa}~2.2.1~\cite{Gleisberg:2008ta} generator. 
 The matrix element is calculated for up to two partons at NLO and up to four partons at LO using 
-\textsc{Comix}~\cite{Gleisberg:2008fv} and \textsc{OpenLoops}~\cite{Cascioli:2011va}. The matrix element calculation 
+\textsc{Comix}~\cite{Gleisberg:2008fv} and \textsc{OpenLoops}~\cite{Cascioli:2011va}. The matrix-element calculation 
 is merged with the {\sherpa} parton shower~\cite{Schumann:2007mg} using the ME+PS@NLO prescription~\cite{Hoeche:2012yf}. 
 The PDF set used for the matrix-element calculation is NNPDF3.0 NNLO~\cite{Ball:2014uwa} with a dedicated parton shower tuning developed for {\sherpa}. 
-Separate samples are generated for different $W/Z$+jets categories using filters for a $b$-jet 
+Separate samples were generated for different $W/Z$+jets categories using filters for a $b$-jet 
 ($W/Z$+$\geq$1$b$+jets), a $c$-jet and no $b$-jet ($W/Z$+$\geq$1$c$+jets), and with a veto on $b$- and $c$-jets 
@@
 Both the $W$+jets and $Z$+jets samples are normalised to their respective inclusive NNLO theoretical 
-cross sections in QCD calculated with \textsc{FEWZ}~\cite{Anastasiou:2003ds}.
+cross sections calculated with \textsc{FEWZ}~\cite{Anastasiou:2003ds}.
 
-Samples of $WW/WZ/ZZ$+jets events are generated with {\sherpa}~2.1.1 using the CT10 PDF set
+Samples of $WW/WZ/ZZ$+jets events were generated with {\sherpa}~2.1.1 using the CT10 PDF set
 and include processes containing up to four electroweak vertices. 
@@
 
-Samples of $\ttbar V$ and $\ttbar H$ events are generated with {\amcatnlo}~2.2.1, using NLO matrix elements and the NNPDF3.0 NLO PDF set,
+Samples of $\ttbar V$ and $\ttbar H$ events were generated with {\amcatnlo}~2.2.1, using NLO matrix elements and the NNPDF3.0 NLO PDF set,
 and interfaced to {\pythia}~8.210 with the NNPDF2.3 LO PDF set and the A14 tune. 
-Instead, the $\ttbar V$ samples used by the $\Hbb$ search are based on LO matrix elements computed for up to two additional partons 
+Instead, the $\ttbar V$ samples used in the $\Hbb$ search are based on LO matrix elements computed for up to two additional partons 
 using the NNPDF3.0 NLO PDF set, and merged using the CKKW-L approach~\cite{Lonnblad:2001iq}.
@@
 utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
-To model the effects of pile-up, events from minimum-bias interactions are generated using {\pythia}~8.186~\cite{Sjostrand:2007gs}  
+To model the effects of pile-up, events from minimum-bias interactions were generated using {\pythia}~8.186~\cite{Sjostrand:2007gs}  
 in combination with the A2 tune~\cite{ATL-PHYS-PUB-2011-014}, 
 and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
-The generated events are processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
+The generated events were processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
 using \textsc{Geant4}~\cite{Agostinelli:2002hh}. A faster simulation, where the full \textsc{Geant4} simulation of
 the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
-is adopted for some of the samples used to estimate modelling systematic uncertainties.
-Simulated events are processed through the same reconstruction software as the data, and corrections are applied so that the object identification 
+was adopted for some of the samples used to estimate modelling systematic uncertainties.
+Simulated events were processed through the same reconstruction software as the data, and corrections were applied so that the object identification 
 efficiencies, energy scales and energy resolutions match those determined from data control samples.
@@
 \subsubsection{Fake electrons and muons}
-In the $\Hbb$ search, the background from multijet production (``multijet background'' in the following) contributes to the selected 
+In the $\Hbb$ search, the background from multijet production (multijet background in the following) contributes to the selected 
 data sample via several production and misreconstruction mechanisms.  
 In the electron channel, it consists of non-prompt electrons (from semileptonic $b$- or $c$-hadron decays) as well as 
-misidentified photons (e.g.~from a conversion of a photon into an $e^+e^-$ pair) or jets with a high fraction of 
+misidentified photons (from a conversion of a photon into an $e^+e^-$ pair) or jets with a high fraction of 
 their energy deposited in the EM calorimeter.  In the muon channel, the multijet background originates predominantly from 
-non-prompt muons.  The multijet background normalisation and shape are estimated directly from data by using the ``matrix method''
+non-prompt muons.  The multijet background normalisation and shape are estimated directly from data by using the matrix method
 technique~\cite{Aad:2010ey,ATLAS-CONF-2014-058}, which exploits differences in lepton identification and isolation properties between 
 prompt leptons and leptons that are either non-prompt or result from the misidentification of photons or jets. 
-Further details can be found in Ref.~\cite{Aaboud:2018mjh}.
+% Further details can be found in Ref.~\cite{Aaboud:2018mjh}.
 
-\subsubsection{Fake taus}
+\subsubsection{Fake tau candidates}
 \label{sec:faketaus}
@@
 The CR selection requirements are analogous to those used to define the different SRs, except that the leading (trailing) $\had$ candidate
-in the $\lephad$ ($\hadhad$) channel is required to fail the medium tau identification but pass the loose one, or the two tau candidates have the same charge.
+in the $\lephad$ ($\hadhad$) channel is required to fail the medium $\had$ identification but pass the loose identification, or the two $\had$ candidates have the same charge.
 
-The fake $\had$ background prediction in a given SR is modelled by the distribution (referred to as ``fake $\had$ template'') derived from data in the corresponding CR.
+The fake $\had$ background prediction in a given SR is modelled by the distribution (referred to as fake $\had$ template) derived from data in the corresponding CR.
 The fake $\had$ template is defined as the data distribution from which the contributions from the simulated backgrounds with real $\had$ candidates, originating primarily from
 $W(\to \tau\nu)$+jets and $Z(\to \tau\tau)$+jets, are subtracted.
-In the $\lephad$ channel, simulation studies indicate that the fake $\had$ background composition is consistent between the SR and the CR, and dominated by $\ttbar$.
+In the $\lephad$ channel, simulation studies indicate that the fake $\had$ background composition is consistent between the SR and the CR, and dominated by $\ttbar$ production.
 In the $\hadhad$ channel, the fake $\had$ background is expected to be dominated by multijet production.
@@
 In both the $\lephad$ and $\hadhad$ channels, the fake $\had$ template in each SR is initially normalised to the estimated fake $\had$ background yield, 
-defined as the data yield minus the contributions from the simulated backgrounds with real $\had$ candidates (i.e. assuming no signal contribution).
+defined as the data yield minus the contributions from the simulated backgrounds with real $\had$ candidates (assuming no signal contribution).
 During the statistical analysis, the normalisation of the fake $\had$ background in each SR is allowed to vary unconstrained in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.

### 2018-10-11 sections/statistical_analysis.tex

@@
 normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$,
-and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties in the signal and background expectations. 
+and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties of the signal and background expectations. 
 Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
@@
 %using kinematic variables other than the ones used in the fit. 
-Statistical uncertainties in each bin of the predicted final discriminant distributions due to the limited size of the simulated samples 
-are taken into account by dedicated parameters in the fit.     
+Statistical uncertainties in each bin of the predicted final discriminant distributions are taken into account by dedicated parameters in the fit.     
 The best-fit $\BR(t\to Hq)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
-hypothesis, i.e. maximising the likelihood function $L(\mu,\theta)$ over $\mu$ and $\theta$.
+hypothesis, maximising the likelihood function $L(\mu,\theta)$ over $\mu$ and $\theta$.
 
@@
 plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
-a signal contamination above 5\% are excluded (referred to as ``blinding cuts'').
+a signal contamination above 5\% are excluded (referred to as blinding cuts).
 In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
-when varying assumptions regarding some of the leading sources of uncertainty. At this point, the blinding cuts in data 
-are removed and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
+when varying assumptions on some of the leading sources of uncertainty. 
+After this, the blinding cuts
+are removed in the data and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
 nuisance parameters before and after removal of the blinding cuts, which are found to be consistent. In addition, it is verified that the 
@@
 
-The test statistic $q_\mu$ is defined as the profile likelihood ratio: 
+The test statistic $q_\mu$ is defined as the profile likelihood ratio, 
 $q_\mu = -2\ln({\cal L}(\mu,{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
@@
 The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
-A related statistic is used to determine the compatibility of the observed data with the background-only hypothesis (i.e.~the discovery test)  
+A related statistic is used to determine the compatibility of the observed data with the background-only hypothesis (the so-called discovery test)  
 by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
@@
 %the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
-the distribution of $q_0$ based on the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
+the distribution of $q_0$ based on the asymptotic formulae in Ref.~\cite{Cowan:2010js}, 
 above the observed value of $q_0$ in the data. 
 %The observed $p_0$-value is checked for each explored signal scenario.
-In the case of the data being compatible with the background expectation, upper limits on $\mu$, and thus on 
+In the case of the data being compatible with the background-only hypothesis, upper limits on $\mu$, and thus on 
 $\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.

### 2018-10-11 sections/strategy_Hbb.tex

@@
 at least four $b$-tagged jets are dominated by \ttbin. Intermediate compositions are found in regions with exactly three 
-$b$-tagged jets.  Most of the $\ttbar$+light-jets background in these regions have a charm jet from the hadronic $W$ boson 
+$b$-tagged jets.  Most of the $\ttbar$+light-jets background in these regions has a charm jet from the hadronic $W$ boson 
 decay  being $b$-tagged, in addition to the two $b$-jets from the top quark decays.
@@
 
-Figure~\ref{fig:LHD} compares the distribution of the LH discriminant between the $\Hc$ and $\Hu$ signals and the 
+Figure~\ref{fig:LHD} compares the shape of the LH discriminant distribution between the $\Hc$ and $\Hu$ signals and the 
 $t\bar{t}\to WbWb$ background in each of the analysis regions considered.
@@
 \subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep6jin4bin_FcncDiscriminant.eps}} \\
-\caption{$\Hbb$ search: Comparison of the distribution of the LH discriminant after preselection 
+\caption{$\Hbb$ search: Comparison of the shape of the LH discriminant distribution after preselection 
 between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 

### 2018-10-11 ANA-TOPQ-2017-07-PAPER-auxmat.tex
adding new tautau aux material

@@
 
+\clearpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\clearpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{center}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/met_centrality_lephad_3j_FR.eps}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/met_centrality_lephad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_lephad_3j_FR.eps}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_lephad_4j_FR.eps}} \\
+\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of some of the most
+discriminating BDT input variables in the $\lephad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
+$\met$ $\phi$ centrality in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
+$m_{Hq}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
+$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
+The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
+added to the background prediction.
+%The first and the last bins in all figures contain the underflow and overflow respectively.
+The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
+The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
+which is determined via a likelihood fit to data.}
+\label{fig:BDT_inputs_lephad_3}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\begin{center}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_perp_lephad_3j_FR.eps}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_perp_lephad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_lephad_3j_FR.eps}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_lephad_4j_FR.eps}} \\
+\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of some of the most
+discriminating BDT input variables in the $\lephad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
+$E_{\text{T},\perp}^{\text{miss}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
+$E_{\text{T},\parallel}^{\text{miss}}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
+$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
+The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
+added to the background prediction.
+%The first and the last bins in all figures contain the underflow and overflow respectively.
+The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
+The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
+which is determined via a likelihood fit to data.}
+\label{fig:BDT_inputs_lephad_4}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\begin{center}
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_hadhad_3j_FR.eps}}
@@
 \label{fig:BDT_inputs_hadhad_2}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\begin{center}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/met_centrality_hadhad_3j_FR.eps}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/met_centrality_hadhad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_hadhad_3j_FR.eps}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_hadhad_4j_FR.eps}} \\
+\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
+discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
+$\met$ $\phi$ centrality  in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
+$m_{Hq}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
+$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
+The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
+added to the background prediction.
+The first and the last bins in the figures in (c) and (d) contain the underflow and overflow respectively.
+The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
+The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
+which is determined via a likelihood fit to data.} 
+\label{fig:BDT_inputs_hadhad_3}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\begin{center}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_perp_hadhad_3j_FR.eps}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_perp_hadhad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_hadhad_3j_FR.eps}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_hadhad_4j_FR.eps}} \\
+\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
+discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
+$E_{\text{T},\perp}^{\text{miss}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
+$E_{\text{T},\parallel}^{\text{miss}}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
+$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
+The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
+added to the background prediction.
+The first and the last bins in the figures in (c) and (d) contain the underflow and overflow respectively.
+The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
+The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
+which is determined via a likelihood fit to data.} 
+\label{fig:BDT_inputs_hadhad_4}
 \end{center}

### 2018-10-12 ANA-TOPQ-2017-07-PAPER-auxmat.tex
adding ranking plots

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\begin{center}
+\includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_bb.eps} \\
+\caption{$\Hbb$ search: Ranking of the nuisance parameters included in the fit according to their impact on the measured branching ratio $\BR(t\to Hc)$. 
+Only the 10 most highly ranked parameters are shown. Nuisance parameters corresponding to MC statistical uncertainties are not included here. 
+The empty blue rectangles correspond to the pre-fit impact on $\BR(t\to Hc)$ and the filled blue ones to the post-fit impact on $\BR(t\to Hc)$, 
+both referring to the upper scale. The impact of each nuisance parameter, $\Delta\mu$, is computed by comparing the nominal best-fit value of $\BR(t\to Hc)$ 
+with the result of the fit when fixing the considered nuisance parameter to its best-fit value, $\hat{\theta}$, shifted by its pre-fit (post-fit) uncertainties 
+$\pm\Delta\theta$ ($\pm\Delta\hat{\theta}$). The black points show the pulls of the nuisance parameters relative to their nominal values, $\theta_{0}$. 
+These pulls and their relative post-fit errors, $\Delta\hat{\theta}/\Delta\theta$, refer to the lower scale.
+For experimental uncertainties that are decomposed into several independent sources, NP I corresponds to the first nuisance parameter, 
+ordered by its impact on $\BR(t\to Hc)$.} 
+\label{fig:ranking_bb}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\begin{center}
+\includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_tt.eps} \\
+\caption{$\Htautau$ search: Ranking of the nuisance parameters included in the fit according to their impact on the measured branching ratio $\BR(t\to Hc)$. 
+Only the 10 most highly ranked parameters are shown. Nuisance parameters corresponding to MC statistical uncertainties are not included here. 
+The empty blue rectangles correspond to the pre-fit impact on $\BR(t\to Hc)$ and the filled blue ones to the post-fit impact on $\BR(t\to Hc)$, 
+both referring to the upper scale. The impact of each nuisance parameter, $\Delta\mu$, is computed by comparing the nominal best-fit value of $\BR(t\to Hc)$ 
+with the result of the fit when fixing the considered nuisance parameter to its best-fit value, $\hat{\theta}$, shifted by its pre-fit (post-fit) uncertainties 
+$\pm\Delta\theta$ ($\pm\Delta\hat{\theta}$). The black points show the pulls of the nuisance parameters relative to their nominal values, $\theta_{0}$. 
+These pulls and their relative post-fit errors, $\Delta\hat{\theta}/\Delta\theta$, refer to the lower scale.
+For experimental uncertainties that are decomposed into several independent sources, NP I corresponds to the first nuisance parameter, 
+ordered by its impact on $\BR(t\to Hc)$.} 
+\label{fig:ranking_tautau}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %\begin{figure*}[t]

### 2018-10-12 sections/signal_background_modeling.tex
fixing sherpa version for VV

@@
 
-Samples of $WW/WZ/ZZ$+jets events were generated with {\sherpa}~2.1.1 using the CT10 PDF set
+Samples of $WW/WZ/ZZ$+jets events were generated with {\sherpa}~2.2.1 using the CT10 PDF set
 and include processes containing up to four electroweak vertices. 

### 2018-10-12 ANA-TOPQ-2017-07-PAPER-auxmat.tex
Implemented residual comments from Filippo

--- 2018-10-11 ANA-TOPQ-2017-07-PAPER-auxmat.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\begin{center}
+\includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_bb.eps} \\
+\caption{$\Hbb$ search: Ranking of the nuisance parameters included in the fit according to their impact on the measured signal strength $\mu$, in
+the case of the $\Hc$ search.
+Only the 10 most highly ranked parameters are shown. Nuisance parameters corresponding to MC statistical uncertainties are not included here. 
+The empty blue rectangles correspond to the pre-fit impact on $\mu$ and the filled blue ones to the post-fit impact on $\mu$, 
+both referring to the upper scale. The impact of each nuisance parameter, $\Delta\mu$, is computed by comparing the nominal best-fit value of $\mu$ 
+with the result of the fit when fixing the considered nuisance parameter to its best-fit value, $\hat{\theta}$, shifted by its pre-fit (post-fit) uncertainties 
+$\pm\Delta\theta$ ($\pm\Delta\hat{\theta}$). The black points show the pulls of the nuisance parameters relative to their nominal values, $\theta_{0}$. 
+These pulls and their relative post-fit errors, $\Delta\hat{\theta}/\Delta\theta$, refer to the lower scale.
+For experimental uncertainties that are decomposed into several independent sources, NP I corresponds to the first nuisance parameter, 
+ordered by its impact on $\mu$.} 
+\label{fig:ranking_bb}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[t]
+\begin{center}
+\includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_tt.eps} \\
+\caption{$\Htautau$ search: Ranking of the nuisance parameters included in the fit according to their impact on the measured signal strength $\mu$, in
+the case of the $\Hc$ search.
+Only the 10 most highly ranked parameters are shown. Nuisance parameters corresponding to MC statistical uncertainties are not included here. 
+The empty blue rectangles correspond to the pre-fit impact on $\mu$ and the filled blue ones to the post-fit impact on $\mu$, 
+both referring to the upper scale. The impact of each nuisance parameter, $\Delta\mu$, is computed by comparing the nominal best-fit value of $\mu$ 
+with the result of the fit when fixing the considered nuisance parameter to its best-fit value, $\hat{\theta}$, shifted by its pre-fit (post-fit) uncertainties 
+$\pm\Delta\theta$ ($\pm\Delta\hat{\theta}$). The black points show the pulls of the nuisance parameters relative to their nominal values, $\theta_{0}$. 
+These pulls and their relative post-fit errors, $\Delta\hat{\theta}/\Delta\theta$, refer to the lower scale.
+For experimental uncertainties that are decomposed into several independent sources, NP I and NP II correspond to the first and second nuisance parameters, 
+ordered by its impact on $\mu$.} 
+\label{fig:ranking_tautau}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %\begin{figure*}[t]

### 2018-10-12 sections/strategy_Hbb.tex
Implemented residual comments from Filippo

@@
 at least four $b$-tagged jets are dominated by \ttbin. Intermediate compositions are found in regions with exactly three 
-$b$-tagged jets.  Most of the $\ttbar$+light-jets background in these regions has a charm jet from the hadronic $W$ boson 
+$b$-tagged jets.  Most of the $\ttbar$+light-jets background events in these regions have a charm jet from the hadronic $W$ boson 
 decay  being $b$-tagged, in addition to the two $b$-jets from the top quark decays.
@@
 \subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep6jin4bin_FcncDiscriminant.eps}} \\
-\caption{$\Hbb$ search: Comparison of the shape of the LH discriminant distribution after preselection 
+\caption{$\Hbb$ search: Comparison of the distributions of the LH discriminant after preselection 
 between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 

### 2018-10-12 sections/strategy_Htautau.tex
extra language editor comments
Implemented residual comments from Filippo

--- 2018-10-03 sections/strategy_Htautau.tex
@@
 
-Boosted decision trees~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} are used in each SR to improve the separation between signal and background. 
+Boosted decision trees are used in each SR to improve the separation between signal and background. 
 %The separate training exploits differences in event kinematics across SRs.  
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh4j/canv_.eps}} \\
-\caption{$\Htautau$ search: Comparison of the distribution of the BDT discriminant after preselection between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
+\caption{$\Htautau$ search: Comparison of the distributions of the BDT discriminant after preselection between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
 and the total background (black solid) in the different search regions considered:

### 2018-10-22 ANA-TOPQ-2017-07-PAPER-auxmat.tex
updating captions of ranking plots

@@
 These pulls and their relative post-fit errors, $\Delta\hat{\theta}/\Delta\theta$, refer to the lower scale.
+The parameter $\mathrm{k}(\ttbin)$ refers to the floating normalisation of the $\ttbin$ background, for which the pre-fit impact on $\mu$ is not defined, 
+and for which both $\theta_{0}$ and $\Delta\theta$ are set to 1.
 For experimental uncertainties that are decomposed into several independent sources, NP I corresponds to the first nuisance parameter, 
@@
 These pulls and their relative post-fit errors, $\Delta\hat{\theta}/\Delta\theta$, refer to the lower scale.
+The parameter $\mathrm{k}($Fake $\had)$ refers to the floating normalisation of the fake $\had$ background, for which the pre-fit impact on $\mu$ is not defined, 
+and for which both $\theta_{0}$ and $\Delta\theta$ are set to 1.
 For experimental uncertainties that are decomposed into several independent sources, NP I and NP II correspond to the first and second nuisance parameters, 

### 2018-10-23 ANA-TOPQ-2017-07-PAPER-auxmat.tex
fixing the bb plots adding the overflow bin

--- 2018-10-12 ANA-TOPQ-2017-07-PAPER-auxmat.tex
@@
 These pulls and their relative post-fit errors, $\Delta\hat{\theta}/\Delta\theta$, refer to the lower scale.
+The parameter $\mathrm{k}($Fake~$\had)$ refers to the floating normalisation of the fake $\had$ background, for which the pre-fit impact on $\mu$ is not defined, 
+and for which both $\theta_{0}$ and $\Delta\theta$ are set to 1.
 For experimental uncertainties that are decomposed into several independent sources, NP I and NP II correspond to the first and second nuisance parameters, 

### 2018-11-14 ANA-TOPQ-2017-07-PAPER-auxmat.tex
Partly implemented D. Stoker's CDS comments

@@
 %-------------------------------------------------------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[htbp]
-\small
-\begin{center}
-\begin{tabular}{l*{3}{c}}
-\hline\hline
- & 4j, 2b & 4j, 3b & 4j, 4b \\
-\hline
-$\Hc$ & $ 1990 \pm 190 $ &   $ 1260 \pm 190 $ &   $ 24.8 \pm 9.5 $ \\
-$\Hu$ & $ 1950 \pm 190 $ &   $ 1110 \pm 170 $ &   $ 19 \pm 16 $ \\ 
-\hline
-$\ttbar$+light-jets & $ 87000 \pm 11000 $ &   $ 4300 \pm 1200 $ &   $ 10.2 \pm 9.6 $ \\ 
-$\ttcin$ & $ 8300 \pm 4300 $ &   $ 1050 \pm 640 $ &   $ 3.2 \pm 3.3 $ \\ 
-$\ttbin$ & $ 3620 \pm 440 $ &   $ 2900 \pm 580 $ &   $ 95 \pm 33 $ \\ 
-$t\bar{t}V$ & $ 176 \pm 31 $ &   $ 34.8 \pm 6.9 $ &   $ 2.84 \pm 0.74 $ \\ 
-$t\bar{t}H$ & $ 61.7 \pm 9.2 $ &   $ 48.7 \pm 8.3 $ &   $ 5.1 \pm 1.0 $ \\
-$W$+jets & $ 5400 \pm 2400 $ &   $ 280 \pm 130 $ &   $ 3.3 \pm 1.8 $ \\ 
-$Z$+jets & $ 2120 \pm 960 $ &   $ 115 \pm 55 $ &   $ 2.4 \pm 1.4 $ \\ 
-Single top & $ 7100 \pm 1300 $ &   $ 400 \pm 120 $ &   $ 7.8 \pm 6.0 $ \\ 
-Diboson & $ 267 \pm 97 $ &   $ 17.2 \pm 6.5 $ &   $ 0.58 \pm 0.27 $ \\ 
-Multijet & $ 7800 \pm 3400 $ &   $ 930 \pm 360 $ &   $ 31 \pm 17 $ \\
-\hline
-Total background & $ 120000 \pm 15000 $ &   $ 10000 \pm 2000 $ &   $ 162 \pm 44 $ \\ 
-\hline
-Data & 120572  & 11275  & 176  \\
-\hline\hline    
-\end{tabular}
-%%\\
-\vspace{0.2cm}
-
-\begin{tabular}{l*{3}{c}}
-\hline\hline
- & 5j, 2b & 5j, 3b & 5j, $\geq$4b \\
-\hline
-$\Hc$ & $ 1260 \pm 240 $ &   $ 1010 \pm 190 $ &   $ 26.2 \pm 8.8 $ \\ 
-$\Hu$ & $ 1160 \pm 240 $ &   $ 930 \pm 160 $ &   $ 23 \pm 12 $ \\ 
-\hline
-$\ttbar$+light-jets & $ 41300 \pm 9100 $ &   $ 3200 \pm 900 $ &   $ 13 \pm 11 $ \\ 
-$\ttcin$ & $ 5900 \pm 3100 $ &   $ 1320 \pm 760 $ &   $ 21 \pm 17 $ \\ 
-$\ttbin$ & $ 3040 \pm 250 $ &   $ 4300 \pm 760 $ &   $ 310 \pm 83 $ \\ 
-$t\bar{t}V$  &   $ 175 \pm 29 $ &   $ 67 \pm 12 $ &   $ 9.1 \pm 2.0 $ \\ 
-$t\bar{t}H$  &   $ 81.3 \pm 9.5 $ &   $ 103 \pm 15 $ &   $ 18.4 \pm 3.5 $ \\ 
-$W$+jets  &   $ 2400 \pm 1100 $ &   $ 186 \pm 89 $ &   $ 7.3 \pm 3.9 $ \\ 
-$Z$+jets  &   $ 780 \pm 350 $ &   $ 83 \pm 39 $ &   $ 6.1 \pm 3.8 $ \\ 
-Single top  &   $ 2990 \pm 780 $ &   $ 350 \pm 110 $ &   $ 16.6 \pm 7.6 $ \\ 
-Diboson  &   $ 125 \pm 56 $ &   $ 13.7 \pm 6.3 $ &   $ 0.89 \pm 0.47 $ \\ 
-Multijet  &   $ 3700 \pm 1500 $ &   $ 500 \pm 230 $ &   $ 3.8 \pm 4.9 $ \\ 
-\hline
-Total background &  $ 60000 \pm 11000 $ &   $ 10100 \pm 1900 $ &   $ 405 \pm 98 $ \\
-\hline
-Data & 58557  & 11707  & 466  \\ 
-\hline\hline    
-\end{tabular}
-%%\\
-\vspace{0.2cm}
-
-\begin{tabular}{l*{3}{c}}
-\hline\hline
- & $\geq$ 6j, 2b & $\geq$6j, 3b & $\geq$6j, $\geq$4b \\
-\hline
-$\Hc$ & $ 760 \pm 250 $ &   $ 690 \pm 210 $ &   $ 60 \pm 60 $ \\ 
-$\Hu$ & $ 680 \pm 240 $ &   $ 570 \pm 180 $ &   $ 36 \pm 40 $ \\ 
-\hline
-$\ttbar$+light-jets  &   $ 22900 \pm 8100 $ &   $ 2400 \pm 910 $ &   $ 14 \pm 18 $ \\ 
-$\ttcin$  &   $ 5300 \pm 3000 $ &   $ 1800 \pm 1100 $ &   $ 29 \pm 23 $ \\ 
-$\ttbin$  &   $ 3270 \pm 510 $ &   $ 7300 \pm 1300 $ &   $ 1100 \pm 240 $ \\ 
-$t\bar{t}V$  &   $ 229 \pm 41 $ &   $ 154 \pm 30 $ &   $ 30.8 \pm 6.9 $ \\ 
-$t\bar{t}H$  &   $ 140 \pm 18 $ &   $ 262 \pm 39 $ &   $ 71 \pm 14 $ \\ 
-$W$+jets  &   $ 1360 \pm 630 $ &   $ 200 \pm 100 $ &   $ 15.4 \pm 8.2 $ \\ 
-$Z$+jets  &   $ 410 \pm 200 $ &   $ 63 \pm 32 $ &   $ 5.1 \pm 4.0 $ \\ 
-Single top  &   $ 1510 \pm 560 $ &   $ 360 \pm 160 $ &   $ 34 \pm 20 $ \\ 
-Diboson  &   $ 93 \pm 47 $ &   $ 18.5 \pm 9.6 $ &   $ 2.1 \pm 1.2 $ \\ 
-Multijet  &   $ 1920 \pm 820 $ &   $ 780 \pm 360 $ &   $ 43 \pm 29 $ \\ 
-\hline
-Total background &  $ 37100 \pm 9600 $ &   $ 13400 \pm 2600 $ &   $ 1360 \pm 290 $ \\ 
-\hline
-Data & 35886  & 14877  & 1335  \\ 
-\hline\hline    
-\end{tabular}
-%%\\
-%\vspace{0.2cm}
-
-%
-\end{center}
-%\vspace{-0.5cm}
-\caption{
-$\Hbb$ search: Predicted and observed yields in each of the analysis regions considered.
-The prediction is shown before the fit to data. Also shown are the signal expectations for 
-$\Hc$ and $\Hu$ assuming $\BR(t\to Hc)=1\%$ and $\BR(t\to Hu)=1\%$ respectively.
-The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
-excluding the normalisation uncertainty of the $\ttbin$ background, which is determined via a likelihood fit to data.
-}
-\label{tab:Hbb_Prefit_Yields_Unblind}
-\end{table} 
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[htbp]
-\small
-\begin{center}
-\begin{tabular}{l*{3}{c}}
-\hline\hline
- & 4j, 2b & 4j, 3b & 4j, 4b \\
-\hline
-$\Hc$  &   $ -30 \pm 470 $ &   $ -20 \pm 300 $ &   $ -0.4 \pm 5.9 $ \\ 
-\hline
-$\ttbar$+light-jets  &    $ 82900 \pm 4200 $ &   $ 4900 \pm 500 $ &   $ 16 \pm 12 $ \\ 
-$\ttcin$  &   $ 11400 \pm 4800 $ &   $ 1360 \pm 550 $ &   $ 5.9 \pm 4.2 $ \\ 
-$\ttbin$  &   $ 4270 \pm 590 $ &   $ 3400 \pm 350 $ &   $ 110 \pm 17 $ \\ 
-$t\bar{t}V$  &    $ 174 \pm 28 $ &   $ 35.0 \pm 5.9 $ &   $ 2.69 \pm 0.55 $ \\ 
-$t\bar{t}H$  &   $ 62.6 \pm 7.8 $ &   $ 47.3 \pm 6.3 $ &   $ 4.68 \pm 0.69 $ \\ 
-$W$+jets  &   $ 4800 \pm 1800 $ &   $ 260 \pm 100 $ &   $ 2.9 \pm 1.3 $ \\ 
-$Z$+jets  &    $ 1870 \pm 730 $ &   $ 102 \pm 41 $ &   $ 1.9 \pm 1.0 $ \\ 
-Single-top  &  $ 6360 \pm 980 $ &   $ 393 \pm 96 $ &   $ 7.6 \pm 5.2 $ \\ 
-Diboson  &   $ 242 \pm 84 $ &   $ 16.3 \pm 5.7 $ &   $ 0.50 \pm 0.22 $ \\ 
-Multijet  &   $ 9000 \pm 3500 $ &   $ 820 \pm 240 $ &   $ 29 \pm 16 $ \\ 
-\hline
-Total & $ 121100 \pm 2200 $ &   $ 11290 \pm 280 $ &   $ 181 \pm 23 $ \\ 
-\hline
-Data & 120572  & 11275  & 176  \\ 
-\hline\hline      
-\end{tabular}
-%%\\
-\vspace{0.2cm}
-
-\begin{tabular}{l*{3}{c}}
-\hline\hline
- & 5j, 2b & 5j, 3b & 5j, $\geq$4b \\
-\hline
-$\Hc$  &   $ -20 \pm 300 $ &   $ -10 \pm 240 $ &   $ -0.4 \pm 6.2 $ \\ 
-\hline
-$\ttbar$+light-jets  &   $ 38000 \pm 3100 $ &   $ 3480 \pm 460 $ &   $ 15.8 \pm 9.5 $ \\ 
-$\ttcin$  &   $ 8300 \pm 3400 $ &   $ 2000 \pm 760 $ &   $ 39 \pm 18 $ \\ 
-$\ttbin$  &   $ 3410 \pm 470 $ &   $ 4900 \pm 460 $ &   $ 356 \pm 29 $ \\ 
-$t\bar{t}V$  &   $ 168 \pm 26 $ &   $ 65 \pm 10 $ &   $ 8.2 \pm 1.4 $ \\ 
-$t\bar{t}H$  &   $ 81.1 \pm 8.9 $ &   $ 99 \pm 12 $ &   $ 16.6 \pm 2.3 $ \\ 
-$W$+jets  &   $ 2080 \pm 820 $ &   $ 169 \pm 68 $ &   $ 6.0 \pm 2.8 $ \\ 
-$Z$+jets  &   $ 700 \pm 270 $ &   $ 74 \pm 30 $ &   $ 5.6 \pm 3.2 $ \\ 
-Single-top  &   $ 2560 \pm 590 $ &   $ 322 \pm 90 $ &   $ 13.3 \pm 5.8 $ \\ 
-Diboson  &   $ 111 \pm 48 $ &   $ 12.5 \pm 5.4 $ &   $ 0.76 \pm 0.39 $ \\ 
-Multijet  &   $ 3380 \pm 950 $ &   $ 560 \pm 230 $ &   $ 3.6 \pm 4.8 $ \\ 
-\hline
-Total & $ 58800 \pm 1400 $ &   $ 11690 \pm 360 $ &   $ 465 \pm 29 $ \\ 
-\hline
-Data & 58557  & 11707  & 466  \\ 
-\hline\hline      
-\end{tabular}
-%%\\
-\vspace{0.2cm}
-
-\begin{tabular}{l*{3}{c}}
-\hline\hline
- & $\geq$6j, 2b & $\geq$6j, 3b & $\geq$6j, $\geq$4b \\
-\hline
-$\Hc$  &   $ -10 \pm 180 $ &   $ -10 \pm 160 $ &   $ -1 \pm 14 $ \\ 
-\hline
-$\ttbar$+light-jets  &   $ 20100 \pm 2500 $ &   $ 2560 \pm 490 $ &   $ 21 \pm 23 $ \\ 
-$\ttcin$  &   $ 7800 \pm 3300 $ &   $ 3000 \pm 1100 $ &   $ 59 \pm 25 $ \\ 
-$\ttbin$  &   $ 3390 \pm 480 $ &   $ 7510 \pm 760 $ &   $ 1106 \pm 83 $ \\ 
-$t\bar{t}V$  &   $ 213 \pm 34 $ &   $ 145 \pm 24 $ &   $ 27.0 \pm 4.8 $ \\ 
-$t\bar{t}H$  &   $ 134 \pm 15 $ &   $ 240 \pm 30 $ &   $ 61.6 \pm 8.8 $ \\ 
-$W$+jets  &   $ 1200 \pm 470 $ &   $ 183 \pm 75 $ &   $ 12.5 \pm 5.7 $ \\ 
-$Z$+jets  &   $ 350 \pm 150 $ &   $ 56 \pm 24 $ &   $ 3.5 \pm 2.2 $ \\ 
-Single-top  &   $ 1220 \pm 400 $ &   $ 310 \pm 120 $ &   $ 27 \pm 14 $ \\ 
-Diboson  &   $ 82 \pm 40 $ &   $ 16.7 \pm 8.2 $ &   $ 1.70 \pm 0.90 $ \\ 
-Multijet  &   $ 1540 \pm 530 $ &   $ 860 \pm 340 $ &   $ 37 \pm 26 $ \\ 
-\hline
-Total &   $ 36000 \pm 1300 $ &   $ 14880 \pm 500 $ &   $ 1360 \pm 72 $ \\ 
-\hline
-Data & 35886  & 14877  & 1335  \\
-\hline\hline      
-\end{tabular}
-%%\\
-%\vspace{0.2cm}
-
-%
-\end{center}
-%\vspace{-0.5cm}
-\caption{
-$\Hbb$ search: Predicted and observed yields in each of the analysis regions considered.
-The background prediction is shown after the fit to data under the signal-plus-background hypothesis 
-(assuming $\Hc$ as signal).
-The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
-computed taking into account correlations among nuisance parameters and among processes.
-}
-\label{tab:Hbb_Postfit_Yields_Unblind_Hc}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[htbp]
-\small
-\begin{center}
-\begin{tabular}{l*{3}{c}}
-\hline\hline
- & 4j, 2b & 4j, 3b & 4j, 4b \\
-\hline
-$\Hu$  &   $ 40 \pm 550 $ &   $ 20 \pm 320 $ &   $ 0.4 \pm 5.3 $ \\
-\hline
-$\ttbar$+light-jets  &   $ 82700 \pm 4400 $ &   $ 4860 \pm 530 $ &   $ 15 \pm 12 $ \\ 
-$\ttcin$  &   $ 11500 \pm 5100 $ &   $ 1400 \pm 580 $ &   $ 5.8 \pm 4.2 $ \\ 
-$\ttbin$  &   $ 4260 \pm 590 $ &   $ 3400 \pm 350 $ &   $ 110 \pm 17 $ \\ 
-$t\bar{t}V$  &   $ 173 \pm 28 $ &   $ 34.8 \pm 5.8 $ &   $ 2.68 \pm 0.54 $ \\ 
-$t\bar{t}H$  &   $ 62.4 \pm 7.7 $ &   $ 47.1 \pm 6.2 $ &   $ 4.66 \pm 0.68 $ \\ 
-$W$+jets  &   $ 4800 \pm 1900 $ &   $ 260 \pm 100 $ &   $ 2.9 \pm 1.4 $ \\ 
-$Z$+jets  &   $ 1880 \pm 740 $ &   $ 103 \pm 42 $ &   $ 1.9 \pm 1.0 $ \\ 
-Single-top  &   $ 6380 \pm 990 $ &   $ 392 \pm 96 $ &   $ 7.5 \pm 5.2 $ \\ 
-Diboson  &   $ 243 \pm 85 $ &   $ 16.3 \pm 5.7 $ &   $ 0.50 \pm 0.22 $ \\ 
-Multijet  &   $ 9000 \pm 3500 $ &   $ 810 \pm 240 $ &   $ 29 \pm 16 $ \\ 
-\hline
-Total &   $ 121000 \pm 2300 $ &   $ 11290 \pm 290 $ &   $ 181 \pm 23 $ \\ 
-\hline
-Data & 120572  & 11275  & 176  \\ 
-\hline\hline      
-\end{tabular}
-%%\\
-\vspace{0.2cm}
-
-\begin{tabular}{l*{3}{c}}
-\hline\hline
- & 5j, 2b & 5j, 3b & 5j, $\geq$4b \\
-\hline
-$\Hu$  &   $ 20 \pm 330 $ &   $ 20 \pm 270 $ &   $ 0.4 \pm 6.6 $ \\ 
-\hline
-$\ttbar$+light-jets  &   $ 37800 \pm 3400 $ &   $ 3450 \pm 500 $ &   $ 15.8 \pm 9.7 $ \\ 
-$\ttcin$  &   $ 8400 \pm 3700 $ &   $ 2000 \pm 800 $ &   $ 39 \pm 19 $ \\ 
-$\ttbin$  &   $ 3400 \pm 470 $ &   $ 4920 \pm 460 $ &   $ 356 \pm 29 $ \\ 
-$t\bar{t}V$  &   $ 168 \pm 26 $ &   $ 65 \pm 10 $ &   $ 8.2 \pm 1.4 $ \\ 
-$t\bar{t}H$  &   $ 81.0 \pm 8.9 $ &   $ 99 \pm 12 $ &   $ 16.6 \pm 2.3 $ \\ 
-$W$+jets  &   $ 2100 \pm 840 $ &   $ 169 \pm 69 $ &   $ 6.0 \pm 2.8 $ \\ 
-$Z$+jets  &   $ 710 \pm 280 $ &   $ 74 \pm 30 $ &   $ 5.5 \pm 3.2 $ \\ 
-Single-top  &   $ 2570 \pm 600 $ &   $ 320 \pm 90 $ &   $ 13.4 \pm 5.8 $ \\ 
-Diboson  &   $ 112 \pm 48 $ &   $ 12.5 \pm 5.5 $ &   $ 0.77 \pm 0.39 $ \\ 
-Multijet  &   $ 3430 \pm 990 $ &   $ 560 \pm 230 $ &   $ 3.6 \pm 4.8 $ \\ 
-\hline
-Total &   $ 58800 \pm 1500 $ &   $ 11690 \pm 380 $ &   $ 465 \pm 29 $ \\ 
-\hline
-Data & 58557  & 11707  & 466  \\ 
-\hline\hline      
-\end{tabular}
-%%\\
-\vspace{0.2cm}
-
-\begin{tabular}{l*{3}{c}}
-\hline\hline
- & $\geq$6j, 2b & $\geq$6j, 3b & $\geq$6j, $\geq$4b \\
-\hline
-$\Hu$ &   $ 10 \pm 190 $ &   $ 10 \pm 160 $ &   $ 1 \pm 10 $ \\ 
-\hline
-$\ttbar$+light-jets  &   $ 20000 \pm 2700 $ &   $ 2530 \pm 520 $ &   $ 20 \pm 24 $ \\ 
-$\ttcin$  &   $ 7900 \pm 3600 $ &   $ 3000 \pm 1200 $ &   $ 58 \pm 26 $ \\ 
-$\ttbin$  &   $ 3390 \pm 480 $ &   $ 7520 \pm 760 $ &   $ 1106 \pm 83 $ \\ 
-$t\bar{t}V$  &   $ 213 \pm 34 $ &   $ 147 \pm 24 $ &   $ 27.0 \pm 4.8 $ \\ 
-$t\bar{t}H$  &   $ 135 \pm 16 $ &   $ 241 \pm 30 $ &   $ 61.9 \pm 9.0 $ \\ 
-$W$+jets  &   $ 1210 \pm 480 $ &   $ 184 \pm 76 $ &   $ 12.6 \pm 5.8 $ \\ 
-$Z$+jets  &   $ 360 \pm 150 $ &   $ 57 \pm 24 $ &   $ 3.6 \pm 2.2 $ \\ 
-Single-top  &   $ 1240 \pm 400 $ &   $ 320 \pm 120 $ &   $ 27 \pm 14 $ \\ 
-Diboson  &   $ 83 \pm 40 $ &   $ 16.8 \pm 8.3 $ &   $ 1.71 \pm 0.91 $ \\ 
-Multijet  &   $ 1530 \pm 530 $ &   $ 860 \pm 340 $ &   $ 37 \pm 26 $ \\ 
-\hline
-Total &   $ 36000 \pm 1400 $ &   $ 14880 \pm 530 $ &   $ 1360 \pm 73 $ \\ 
-\hline
-Data & 35886  & 14877  & 1335  \\
-\hline\hline      
-\end{tabular}
-%%\\
-%\vspace{0.2cm}
-
-%
-\end{center}
-%\vspace{-0.5cm}
-\caption{
-$\Hbb$ search: Predicted and observed yields in each of the analysis regions considered.
-The background prediction is shown after the fit to data under the signal-plus-background hypothesis (assuming $\Hu$ as signal).
-The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
-computed taking into account correlations among nuisance parameters and among processes.
-}
-\label{tab:Hbb_Postfit_Yields_Unblind_Hu}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[htbp]
-\small
-\begin{center}
-\begin{tabular}{l*{4}{c}}
-\hline\hline
- & $\lephad$ 3j & $\lephad$ $\geq$4j & $\hadhad$ 3j &  $\hadhad$ $\geq$4j \\
-\hline
-$\Hc$  &   $ 89 \pm 14 $ &   $ 226 \pm 43 $ &   $ 46 \pm 14 $ &   $ 122 \pm 32 $ \\ 
-$\Hu$  &   $ 100 \pm 17 $ &   $ 237 \pm 47 $ &   $ 32 \pm 10 $ &   $ 114 \pm 28 $ \\ 
-\hline
-Fake $\had$  &   $ 2828 \pm 78 $ &   $ 3200 \pm 100 $ &   $ 710 \pm 110 $ &   $ 500 \pm 62 $ \\
-Top (real $\had$)  &   $ 3840 \pm 720 $ &   $ 3160 \pm 890 $ &   $ 113 \pm 72 $ &   $ 117 \pm 35 $ \\  
-$Z \to \tau\tau$  &   $ 420 \pm 140 $ &   $ 320 \pm 120 $ &   $ 283 \pm 99 $ &   $ 267 \pm 96 $ \\ 
-Other  &   $ 168 \pm 56 $ &   $ 103 \pm 33 $ &   $ 8.9 \pm 2.5 $ &   $ 11.2 \pm 2.5 $ \\ 
-\hline
-Total background  &   $ 7260 \pm 730 $ &   $ 6770 \pm 880 $ &   $ 1120 \pm 120 $ &   $ 900 \pm 120 $ \\ 
-\hline
-Data  & 7259  & 6768  & 1119  & 894  \\
-\hline\hline    
-\end{tabular}
-%%\\
-%\vspace{0.2cm}
-
-%
-\end{center}
-%\vspace{-0.5cm}
-\caption{
-$\Htautau$ search: Predicted and observed yields in each of the analysis regions considered.
-The prediction is shown before the fit to data. Also shown are the signal expectations for 
-$\Hc$ and $\Hu$ assuming $\BR(t\to Hc)=1\%$ and $\BR(t\to Hu)=1\%$ respectively.
-The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
-a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
-$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
-The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
-excluding the normalisation uncertainty of the fake $\had$ background, which is determined via a likelihood fit to data.
-}
-\label{tab:Htautau_Prefit_Yields_Unblind}
-\end{table} 
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[htbp]
-\small
-\begin{center}
-\begin{tabular}{l*{4}{c}}
-\hline\hline
- & $\lephad$ 3j & $\lephad$ $\geq$4j & $\hadhad$ 3j &  $\hadhad$ $\geq$4j \\
-\hline
-$\Hc$  &   $ -4.2 \pm 8.2 $ &   $ -11 \pm 21 $ &   $ -2.4 \pm 4.3 $ &   $ -10 \pm 11 $ \\ 
-\hline
-Fake $\had$  &   $ 2290 \pm 680 $ &   $ 2640 \pm 880 $ &   $ 640 \pm 110 $ &   $ 440 \pm 100 $ \\ 
-Top (real $\had$)  &   $ 4300 \pm 670 $ &   $ 3660 \pm 860 $ &   $ 147 \pm 84 $ &   $ 139 \pm 35 $ \\ 
-$Z \to \tau\tau$  &   $ 500 \pm 100 $ &   $ 359 \pm 90 $ &   $ 320 \pm 79 $ &   $ 306 \pm 76 $ \\ 
-Other  &   $ 178 \pm 45 $ &   $ 112 \pm 28 $ &   $ 9.6 \pm 2.6 $ &   $ 12.5 \pm 2.6 $ \\ 
-\hline
-Total  &   $ 7230 \pm 160 $ &   $ 6760 \pm 170 $ &   $ 1117 \pm 65 $ &   $ 893 \pm 45 $ \\
-\hline
-Data & 7259  & 6768  & 1119  & 894 \\ 
-\hline\hline    
-\end{tabular}
-%%\\
-%\vspace{0.2cm}
-
-%
-\end{center}
-%\vspace{-0.5cm}
-\caption{
-$\Htautau$ search: Predicted and observed yields in each of the analysis regions considered.
-The background prediction is shown after the fit to data under the signal-plus-background hypothesis 
-(assuming $\Hc$ as signal).
-The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
-a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
-$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
-The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
-computed taking into account correlations among nuisance parameters and among processes.
-}
-\label{tab:Htautau_Postfit_Yields_Unblind_Hc}
-\end{table} 
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[htbp]
-\small
-\begin{center}
-\begin{tabular}{l*{4}{c}}
-\hline\hline
- & $\lephad$ 3j & $\lephad$ $\geq$4j & $\hadhad$ 3j &  $\hadhad$ $\geq$4j \\
-\hline
-$\Hu$  &   $ -5.7 \pm 8.6 $ &   $ -14 \pm 21 $ &   $ -2,0 \pm 2.8 $ &   $ -7.1 \pm 9.8 $ \\ 
-\hline
-Fake $\had$  &   $ 2270 \pm 680 $ &   $ 2620 \pm 880 $ &   $ 640 \pm 110 $ &   $ 440 \pm 100 $ \\
-Top (real $\had$)  &   $ 4320 \pm 660 $ &   $ 3680 \pm 860 $ &   $ 148 \pm 84 $ &   $ 140 \pm 35 $ \\ 
-$Z \to \tau\tau$  &   $ 470 \pm 100 $ &   $ 359 \pm 89 $ &   $ 321 \pm 79 $ &   $ 308 \pm 77 $ \\ 
-Other  &   $ 177 \pm 44 $ &   $ 111 \pm 27 $ &   $ 9.7 \pm 2.6 $ &   $ 12.5 \pm 2.6 $ \\ 
-\hline
-Total  &   $ 7230 \pm 160 $ &   $ 6760 \pm 160 $ &   $ 1118 \pm 66 $ &   $ 892 \pm 45 $ \\ 
-\hline
-Data  & 7259  & 6768  & 1119  & 894  \\ 
-\hline\hline    
-\end{tabular}
-%%\\
-%\vspace{0.2cm}
-
-%
-\end{center}
-%\vspace{-0.5cm}
-\caption{
-$\Htautau$ search: Predicted and observed yields in each of the analysis regions considered.
-The background prediction is shown after the fit to data under the signal-plus-background hypothesis 
-(assuming $\Hu$ as signal).
-The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
-a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
-$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
-The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
-computed taking into account correlations among nuisance parameters and among processes.
-}
-\label{tab:Htautau_Postfit_Yields_Unblind_Hu}
-\end{table} 
-%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
 
@@
 $\Delta R$ separation ($\mbb$).
-The small contributions from $\ttbar V$, $\ttbar H$, single top, $W/Z$+jets, diboson, and multijet backgrounds are combined 
+The small contributions from $\ttbar V$, $\ttbar H$, single-top-quark, $W/Z$+jets, diboson, and multijet backgrounds are combined 
 into a single background source referred to as ``Non-$\ttbar$''. 
@@
 %$\Delta R$ separation ($\mbb$).
-%The small contributions from $\ttbar V$, $\ttbar H$, single top, $W/Z$+jets, diboson, and multijet backgrounds are combined 
+%The small contributions from $\ttbar V$, $\ttbar H$, single-top-quark, $W/Z$+jets, diboson, and multijet backgrounds are combined 
 %into a single background source referred to as ``Non-$\ttbar$''. 
@@
 $x_{2}^{\text{fit}}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
-The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
 a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
@@
 $m_{Hq}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
-The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
 a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
@@
 $E_{\text{T},\parallel}^{\text{miss}}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
-The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
 a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
@@
 $p_{\text{T},2}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
-The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
 a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
@@
 $m_{Hq}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
-The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
 a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
@@
 $E_{\text{T},\parallel}^{\text{miss}}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
-The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
+The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
 a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure*}[t]
-%\begin{center}
-%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}}
-%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}} \\
-%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}}
-%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}} \\
-%\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
-%important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
-%$x_{2}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
-%$p_{\text{T},2}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
-%The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
-%a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
-%$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
-%The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
-%added on top of the background prediction.
-%The first and the last bins in the figures in (c) and (d) contain the underflow and overflow respectively.
-%The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
-%The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
-%which is determined via a likelihood fit to data.} 
-%\label{fig:BDT_inputs_hadhad_3}
-%\end{center}
-%\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure*}[t]
-%\begin{center}
-%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}}
-%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}} \\
-%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}}
-%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/placeholder8x8.eps}} \\
-%\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
-%important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
-%$x_{2}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
-%$p_{\text{T},2}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
-%The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
-%a single background source referred to as ``Top (real $\had$)", whereas the small contributions from 
-%$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
-%The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
-%added on top of the background prediction.
-%The first and the last bins in the figures in (c) and (d) contain the underflow and overflow respectively.
-%The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
-%The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
-%which is determined via a likelihood fit to data.} 
-%\label{fig:BDT_inputs_hadhad_3}
-%\end{center}
-%\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-11-14 sections/conclusion.tex
Partly implemented D. Stoker's CDS comments

@@
 
-A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
+A search for flavour-changing neutral-current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
-CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
-Two complementary analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
+CERN Large Hadron Collider and corresponding to an integrated luminosity of 36.1 fb$^{-1}$.
+Two complementary analyses are performed to search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
 and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  

### 2018-11-14 sections/detector.tex
Partly implemented D. Stoker's CDS comments

@@
 The calorimeters are surrounded by a muon spectrometer within a magnetic field provided by air-core toroid magnets 
-with a bending integral of about 2.5 Tm in the barrel and up to 6 Tm in the end-caps. 
+with a bending integral of about 2.5 Tm in the barrel and up to 6 Tm in the endcaps. 
 The muon spectrometer measures the trajectories of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking chambers,

### 2018-11-14 sections/strategy_Hbb.tex
Partly implemented D. Stoker's CDS comments

@@
 However, the use of the 60\% $b$-tagging efficiency operating point, characterised by a low mistag rate for
-charm and light jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity distribution,
+$c$- and light-jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity distribution,
 with a very small fraction of events having four or more $b$-tagged jets.
@@
 $b$-tagged jets.  Most of the $\ttbar$+light-jets background events in these regions have a charm jet from the hadronic $W$ boson 
-decay  being $b$-tagged, in addition to the two $b$-jets from the top quark decays.
+decay  being $b$-tagged, in addition to the two $b$-jets from the top-quark decays.
 
@@
 \begin{equation*}
-LH(\mathbf{x}) = \frac{P^\textrm{sig}(\mathbf{x}) }{P^\textrm{sig}(\mathbf{x}) +P^\textrm{bkg}(\mathbf{x}) },
+L(\mathbf{x}) = \frac{P^\textrm{sig}(\mathbf{x}) }{P^\textrm{sig}(\mathbf{x}) +P^\textrm{bkg}(\mathbf{x}) },
 \label{eq:D}
@@
 Combinations are weighted using information on the per-jet multivariate $b$-tagging discriminant value to suppress the impact from 
-parton--jet assignments that are inconsistent with the correct parton candidates flavour.
+parton--jet assignments that are inconsistent with the correct flavour of the parton candidates.
 

### 2018-11-14 sections/strategy_Htautau.tex
Partly implemented D. Stoker's CDS comments

@@
 %three additional jets. Therefore, at least four jets are typically expected in signal events.
-However, in a significant fraction of the events the lowest-$\pt$ jet from the $W$-boson decay fails the minimum $\pt$ requirement of $30~\gev$,
+However, in a significant fraction of the events the lowest-$\pt$ jet from the $W$ boson decay fails the minimum $\pt$ requirement of $30~\gev$,
 resulting in signal events with only three jets reconstructed.
@@
 This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
-of $\met$ in the event (larger in $\lephad$ events compared to $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
+of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
 is missing or not (events with exactly three jets or at least four jets).
@@
 \begin{table*}[t!]
+\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for each search region (denoted by $\times$). 
+The description of each variable is provided in the text.}}
 \begin{center}
@@
 \end{tabular}
-\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for each search region (denoted by $\times$). 
-The description of each variable is provided in the text.}}
 \label{tab:mva_var}
@@
 \item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\had$ candidate (denoted as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\had$ candidates (denoted as particles 1 and 2 respectively) in the $\hadhad$ channel.
-\item $\met$ $\phi$ centrality: a variable that quantifies the relative angular position of the $\mpt$ with respect to the 
-visible $\tau$-lepton decay products in the transverse plane. The transverse plane is transformed such that the direction of the $\tau$-lepton decay products are 
+\item $\met$ $\phi$ centrality: a variable that quantifies the angular position of the $\mpt$ relative to the 
+visible $\tau$-lepton decay products in the transverse plane. The transverse plane is transformed such that the directions of the $\tau$-lepton decay products are 
 orthogonal, and that the smaller angle between the $\tau$-lepton decay products defines the positive quadrant of the transformed plane. 

### 2018-11-14 sections/systematic_uncertainties.tex
Partly implemented D. Stoker's CDS comments

@@
 instead the $W$+$c$-jet scale factors.  
-In the case of the $\Hbb$ ($\Htautau$) search, the uncertainties on these scale factors include a total of six independent sources affecting $b$-jets, one (three) source(s) affecting $c$-jets, and 17 sources affecting light-jets.
+In the case of the $\Hbb$ ($\Htautau$) search, the uncertainties on these scale factors include 
+a total of 6 independent sources affecting $b$-jets, 1 (2) source(s) affecting $c$-jets, and 17 sources affecting light-jets. 
 These systematic uncertainties are taken as uncorrelated between $b$-jets, $c$-jets, and light-jets. 

### 2018-11-16 ANA-TOPQ-2017-07-PAPER-metadata.tex
preparing for second circulation

@@
 %\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
-\AtlasTitle{Search for top quark decays $t \to Hq$ with 36 fb$^{-1}$ of $pp$ collision data at $\sqrt{s}=13~\tev$ with the ATLAS detector}
+\AtlasTitle{Search for top-quark decays $t \to Hq$ with 36 fb$^{-1}$ of $pp$ collision data at $\sqrt{s}=13~\tev$ with the ATLAS detector}
 
@@
 % Comment or remove in final version.
-\AtlasVersion{1.3}
+\AtlasVersion{2.1}
 % Abstract - % directly after { is important for correct indentation
@@
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
-CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
-Two complementary analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
+CERN Large Hadron Collider and corresponding to an integrated luminosity of 36.1 fb$^{-1}$.
+Two complementary analyses are performed to search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
 and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, respectively.  
-The high multiplicity of $b$-quark jets, or the presence of hadronically decaying $\tau$-leptons, are exploited in the two analyses respectively. 
+The high multiplicity of $b$-quark jets, or the presence of hadronically decaying $\tau$-leptons, is exploited in the two analyses respectively. 
 Multivariate techniques are used to separate the signal from the background, which is dominated by top-quark pair production.
@@
 % ATLAS reference code, to help ATLAS members to locate the paper
-%\AtlasRefCode{TOPQ-2017-07}
+\AtlasRefCode{TOPQ-2017-07}
 %\AtlasRefCode{ATLAS-CONF-2018-049}
@@
 % Comment deadline
-\AtlasCoverCommentsDeadline{3 September 2018}
+\AtlasCoverCommentsDeadline{4 November 2018}
 

### 2018-11-16 sections/data_presel.tex

@@
 Both searches are based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ with 25 ns bunch spacing collected in 2015 and 2016, corresponding to an integrated luminosity of $36.1~\ifb$.
-Only events recorded with a single-electron trigger, a single-muon trigger, or a ditau trigger under stable beam conditions 
+Only events recorded with a single-electron trigger, a single-muon trigger, or a di-$\tau$ trigger under stable beam conditions 
 and for which all detector subsystems were operational are considered.
@@
 %For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
-For ditau triggers, the $\pt$ threshold of the leading (trailing) $\had$ candidate is 35 (25)~\gev.
+For di-$\tau$ triggers, the $\pt$ threshold of the leading (trailing) $\had$ candidate is 35 (25)~\gev.
 In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.
@@
 and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
-data taking conditions). In addition, its electric charge is required to be of opposite sign to that of the leading $\had$ candidate.
-Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\had$ candidates and 
+data-taking conditions). In addition, its electric charge is required to be of opposite sign to that of the leading $\had$ candidate.
+Events in the $\hadhad$ channel are recorded with a di-$\tau$ trigger, and are required to have at least two $\had$ candidates and 
 no selected electrons or muons. The two leading $\had$ candidates are required to have charges of opposite sign. 
@@
 \begin{table*}[t!]
+\caption{\small{Summary of preselection requirements for the $\Hbb$ and $\Htautau$ searches. 
+The leading and trailing $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
 \begin{center}
@@
 \midrule
-Trigger & single-lepton trigger & single-lepton trigger & ditau trigger  \\
+Trigger & single-lepton trigger & single-lepton trigger & di-$\tau$ trigger  \\
 Leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
@@
 \end{tabular}
-\caption{\small{Summary of preselection requirements for the $\Hbb$ and $\Htautau$ searches. 
-The leading and trailing $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
 \label{tab:preselection}

### 2018-11-16 sections/introduction.tex

@@
 %looking for deviations from the Standard Model (SM) predictions.  
-An interesting possibility is the presence of flavour-changing neutral current (FCNC) interactions 
+An interesting possibility is the presence of flavour-changing neutral-current (FCNC) interactions 
 between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$). Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl}, 
@@
 In the Standard Model (SM), such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
-interactions are forbidden at the tree level and even suppressed at higher orders in the perturbative expansion due to the 
+interactions are forbidden at the tree level and suppressed even at higher orders in the perturbative expansion due to the 
 Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.  As a result, the SM predictions for the $t \to Hq$ branching 
 ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
-In contrast, large enhancements in these branching ratios are possible in some beyond-SM scenarios.
+In contrast, large enhancements of these branching ratios are possible in some scenario beyond the SM.
 Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
@@
 Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as multileptons,
-are able to exploit a significantly larger branching ratio for the Higgs 
-boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, and are also characterised by relatively small backgrounds.
+are able to exploit a branching ratio that is significantly larger for the $H \rightarrow WW^*, \tau\tau$ decay modes than for the $H \rightarrow \gamma\gamma$ decay mode,
+%are able to exploit a significantly larger branching ratio for the Higgs boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, 
+and are also characterised by relatively small backgrounds.
 %However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
@@
 Finally, searches have also been performed exploiting the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
-of $\BR(H\to b\bar{b})\simeq 58\%$. Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, 
+of $\BR(H\to b\bar{b})\simeq 58\%$. Compared with Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, 
 as well as the larger integrated luminosity.
@@
 in upper limits of $\BR(t\to Hc)<0.47\%$ and $\BR(t\to Hu)<0.47\%$, in each case neglecting the other decay mode.
-Compared to previous searches, the search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
+Compared with previous searches, the search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
 $pp \to tH$ production~\cite{Greljo:2014dka}.
@@
 Two analyses are performed searching for $\ttbar \to WbHq$ production (ignoring $pp \to tH$ production), and targeting the 
-$H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which will be referred to as ``$\Hbb$ search'' and ``$\Htautau$ search'', respectively.
+$H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which this paper refers to as ``$\Hbb$ search'' and ``$\Htautau$ search'', respectively.
 The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, several 

### 2018-11-16 sections/objects.tex

@@
 Hadronically decaying $\tau$-lepton ($\had$) candidates are reconstructed from energy clusters in the calorimeters and
-associated inner detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
+associated inner-detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
 with a total charge of $\pm 1$. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
@@
 if a muon lies within $\Delta R = 0.2$ of the axis of a jet, the jet is removed if either it has fewer than three tracks originating from the 
-primary vertex or it has a small $\pt$ compared to that of the muon (the $\pt$ of the jet is less than 50\% of the $\pt$ of the muon,
-or the scalar sum of the $\pt$ of the tracks associated to the jet is less than 70\% of the $\pt$ of the muon).
+primary vertex or it has a small $\pt$ compared with that of the muon (the $\pt$ of the jet is less than 50\% of the $\pt$ of the muon,
+or the scalar sum of the $\pt$ of the tracks associated with the jet is less than 70\% of the $\pt$ of the muon).
 

### 2018-11-16 sections/signal_background_modeling.tex

@@
 are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
-In the simulation, the top quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
+In the simulation, the top-quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
 and the Higgs boson is allowed to decay into all SM particles with branching ratios calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
@@
 Samples of simulated $\ttbar \to WbHq$ events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
-the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix element calculation 
+the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element calculation 
 is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering, hadronisation, and the underlying event.
 The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
-initial and final state radiation, referred to as the tune, was used.
+initial- and final-state radiation, referred to as the tune, was used.
 The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
@@
 The {\powheg} model parameter $h_{\textrm{damp}}$, which controls
-matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, was set to 1.5 times the top quark mass. 
+matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, was set to 1.5 times the top-quark mass. 
 Parton shower, hadronisation, and underlying event were modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
@@
 Samples corresponding to the $tW$- and $s$-channel production mechanisms were generated 
-with {\powheg}~v1 using the CT10 PDF set. Overlaps between the $\ttbar$ and $tW$ final states are avoided by using 
+with {\powheg}~v1 using the CT10 PDF set. Overlaps between the $\ttbar$ and $tW$ final states were avoided by using 
 the diagram removal scheme~\cite{Frixione:2005vw}.
@@
 Samples of $W/Z$+jets events were generated with the {\sherpa}~2.2.1~\cite{Gleisberg:2008ta} generator. 
-The matrix element is calculated for up to two partons at NLO and up to four partons at LO using 
+The matrix element was calculated for up to two partons at NLO and up to four partons at LO using 
 \textsc{Comix}~\cite{Gleisberg:2008fv} and \textsc{OpenLoops}~\cite{Cascioli:2011va}. The matrix-element calculation 
@@
 and include processes containing up to four electroweak vertices. 
-In the case of $WW/WZ$+jets ($ZZ$+jets) the matrix element is calculated for zero (up to one) additional partons 
+In the case of $WW/WZ$+jets ($ZZ$+jets) the matrix element was calculated for zero (up to one) additional partons 
 at NLO and up to three partons at LO using the same procedure as for the $W/Z$+jets samples. 
@@
 
-\subsubsection{Fake tau candidates}
+\subsubsection{Fake $\tau$-lepton candidates}
 \label{sec:faketaus}

### 2018-11-16 sections/statistical_analysis.tex

@@
 The best-fit $\BR(t\to Hq)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
-hypothesis, maximising the likelihood function $L(\mu,\theta)$ over $\mu$ and $\theta$.
+hypothesis, maximising the likelihood function ${\cal L}(\mu,\theta)$ over $\mu$ and $\theta$.
 
@@
 plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
-a signal contamination above 5\% are excluded (referred to as blinding cuts).
+a signal contamination above 5\% are excluded (referred to as blinding requirements).
 In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
 when varying assumptions on some of the leading sources of uncertainty. 
-After this, the blinding cuts
+After this, the blinding requirements
 are removed in the data and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
-nuisance parameters before and after removal of the blinding cuts, which are found to be consistent. In addition, it is verified that the 
+nuisance parameters before and after removal of the blinding requirements, which are found to be consistent. In addition, it is verified that the 
 fit is able to correctly determine the strength of a simulated signal injected in the real data.

### 2018-11-21 sections/data_presel.tex
Implemented more CDS comments from David Stoker

@@
 and for which all detector subsystems were operational are considered.
-The number of $pp$ interactions per bunch crossing in this dataset ranges from about 8 to 45 interactions, with an average of 24.
+The number of $pp$ interactions per bunch crossing in this dataset ranges from about 8 to 45, with an average of 24.
 %The mean number of $pp$ interactions per bunch crossing in the dataset is 24.
@@
 %with looser identification criteria and no isolation requirements.
-Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
+Single-electron and single-muon triggers with low $\pt$ thresholds and lepton isolation requirements are combined in a logical OR 
 with higher-threshold triggers but with a looser identification criterion and without any isolation requirement.

### 2018-11-21 sections/detector.tex
Implemented more CDS comments from David Stoker

@@
 2~T axial magnetic field, electromagnetic and hadronic calorimeters, and a muon spectrometer
-incorporating three large toroid magnet assemblies. The inner detector consists of a high-granularity silicon pixel detector, 
+incorporating three large toroid magnet assemblies. The inner detector contains a high-granularity silicon pixel detector, 
 including the %newly-installed

### 2018-11-21 sections/introduction.tex
Implemented more CDS comments from David Stoker

@@
 In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{ 
-In the following $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
+In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
 $WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
@@
 $H \to WW^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically, or $H \to ZZ^*$~\cite{Aaboud:2018pob}.
-These upper limits are derived under the assumption of $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ under the
-assumption of $\BR(t\to Hc)=0$. The CMS Collaboration has performed a search using  
+These upper limits are derived assuming that $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ if $\BR(t\to Hc)=0$. 
+The CMS Collaboration has performed a search using  
 $H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} with 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
@@
 %The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
-The searches presented in this paper are focussed on fermionic decay modes.
-Therefore, they help to complete the programme of searches for $t \to Hq$ decays of the ATLAS experiment based on $pp$ collision 
+The searches presented in this paper are focussed on fermionic decay modes. Therefore, they help to complete the 
+ATLAS experiment's programme of searches for $t \to Hq$ decays based on $pp$ collision
+%programme of searches for $t \to Hq$ decays of the ATLAS experiment based on $pp$ collision 
 data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
-Two analyses are performed searching for $\ttbar \to WbHq$ production (ignoring $pp \to tH$ production), and targeting the 
+Two analyses are performed, searching for $\ttbar \to WbHq$ production (ignoring $pp \to tH$ production) and targeting the 
 $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which this paper refers to as ``$\Hbb$ search'' and ``$\Htautau$ search'', respectively.
@@
 %The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
-The $\Htautau$ search selects events with two $\tau$-lepton candidates of which at least one is decaying hadronically, as well as multiple jets. 
-The latter requirement is aimed at selecting events with a hadronically decaying $W$ boson, since this allows an improved reconstruction of the
+The $\Htautau$ search selects events with two $\tau$-lepton candidates, at least one of which decays hadronically, as well as multiple jets.
+The latter requirement aims to select events with a hadronically decaying $W$ boson, since this allows an improved reconstruction of the
 event kinematics.
@@
 %two of which originating from hadronic $W$ decays. 
-Both searches employ different multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
+Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
 These two searches are combined with previous ATLAS searches in the diphoton and multilepton final states using the same dataset~\cite{Aaboud:2017mfd,Aaboud:2018pob}, 

### 2018-11-21 sections/objects.tex
Implemented more CDS comments from David Stoker

@@
 different layers of the muon spectrometer to tracks found in the inner detector;
-the resulting muon candidates are refitted using the complete track information from both detector systems.
+the resulting muon candidates are re-fitted using the complete track information from both detector systems.
 In the $\Hbb$ ($\Htautau$) search, muon candidates are required to have $\pt>30~(10)~\gev$ and $|\eta|<2.5$ 
@@
 A track-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$, where
-the scalar sum includes all tracks (excluding the lepton candidate itself) within the cone defined by $\Delta R<R_{\textrm{cut}}$ about the %axis
+the scalar sum includes all tracks (excluding the lepton candidate itself) within the cone defined by $\Delta R<R_{\textrm{cut}}$ around the %axis
 direction of the lepton.  The value of $R_{\textrm{cut}}$ is the smaller of $r_{\textrm{min}}$ and $10~\gev/\pt^\ell$, where
@@
 makes $\pt$-dependent requirements on $I_R/\pt^\ell$. Additionally, the $\Htautau$ search requires leptons to
-satisfy a calorimeter-based isolation criterion: the sum of the transverse energy within a cone of
+satisfy a calorimeter-based isolation criterion: the sum of the transverse energy within a cone of size
 $\Delta R<0.2$ around the lepton, after subtracting the contributions
@@
 radius parameter $R=0.4$, as implemented in the \fastjet\ package~\cite{Cacciari:2011ma}.  
-Jet reconstruction in the calorimeter starts from topological clustering~\cite{Aad:2016upy} of individual calorimeter cells calibrated to the electromagnetic scale. 
+Jet reconstruction in the calorimeter starts from topological clustering~\cite{Aad:2016upy} of individual calorimeter cells calibrated to the electromagnetic energy scale. 
 The reconstructed jets are then calibrated to the particle level by the application of a jet energy scale 
@@
 or detector noise~\cite{ATLAS-CONF-2015-029}.  To reduce the contamination due to jets originating from pile-up interactions,
-additional requirements are made on the jet vertex tagger (JVT)~\cite{Aad:2015ina} output for jets with $\pt<60~\gev$ and $|\eta| < 2.4$,
+additional requirements are imposed on the jet vertex tagger (JVT)~\cite{Aad:2015ina} output for jets with $\pt<60~\gev$ and $|\eta| < 2.4$,
 or on the forward JVT~\cite{Aaboud:2017pou} output for jets with $\pt<50~\gev$ and $|\eta| > 2.5$.
@@
 working point for the nominal selection, while the loose working point is used for background estimation.
-The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\had$ 
+The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one-prong (three-prong) $\had$ 
 decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
@@
 first step is the removal of $\had$ candidates within $\Delta R=0.2$ of electrons or muons, and the last step is the
-removal of jets whose axis lies within $\Delta R=0.2$ of the highest-$\pt$ (leading) or the two leading $\had$ candidates (depending on the
+removal of jets whose axis lies within $\Delta R=0.2$ of the leading (highest-$\pt$) $\had$ candidate or the two leading $\had$ candidates (depending on the
 analysis channel). In addition, the muon--jet overlap removal is slightly different:

### 2018-11-21 sections/signal_background_modeling.tex
Implemented more CDS comments from David Stoker

@@
 production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
-with prompt leptons, i.e. those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
+with prompt leptons, i.e.\ those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
 are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
@@
 matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, was set to 1.5 times the top-quark mass. 
-Parton shower, hadronisation, and underlying event were modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
+The parton showers, hadronisation, and underlying event were modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
 Alternative $\ttbar$ simulation samples used to derive systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
@@
 The $\ttbar$ background selected by the $\Hbb$ search is enriched in $\ttbar$+heavy-flavour production, and thus requires a more sophisticated 
-treatment than provided by the nominal $\ttbar$ sample, which is briefly outlined below. A detailed discussion can be found in Ref.~\cite{Aaboud:2017rss}.
+treatment than provided by the nominal $\ttbar$ sample; this treatment is briefly outlined below. A detailed discussion can be found in Ref.~\cite{Aaboud:2017rss}.
 %The large and complex $\ttbar$ background selected by the $\Hbb$ search requires a more sophisticated treatment than provided by the nominal $\ttbar$ sample. 
@@
 Samples of single-top-quark events corresponding to the $t$-channel production mechanism were generated with the 
-{\powheg}~v1~\cite{Frederix:2012dh} generator that uses the 4F scheme  for the NLO matrix-element calculations
+{\powheg}~v1~\cite{Frederix:2012dh} generator, using the 4F scheme  for the NLO matrix-element calculations
 and the fixed 4F \textsc{CT10}f\textsc{4}~\cite{Lai:2010vv} PDF set.
@@
 the diagram removal scheme~\cite{Frixione:2005vw}.
-The parton shower, hadronisation and the underlying event were modelled using {\pythia}~6.428~\cite{Sjostrand:2006za} 
+The parton showers, hadronisation and the underlying event were modelled using {\pythia}~6.428~\cite{Sjostrand:2006za} 
 with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set 
@@
 the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
-was adopted for some of the samples used to estimate modelling systematic uncertainties.
+was adopted for some of the samples used to estimate systematic uncertainties in background modelling.
 Simulated events were processed through the same reconstruction software as the data, and corrections were applied so that the object identification 
@@
 misidentified photons (from a conversion of a photon into an $e^+e^-$ pair) or jets with a high fraction of 
-their energy deposited in the EM calorimeter.  In the muon channel, the multijet background originates predominantly from 
+their energy deposited in the EM calorimeter.  In the muon channel, the multijet background originates mainly from 
 non-prompt muons.  The multijet background normalisation and shape are estimated directly from data by using the matrix method
@@
 \label{sec:faketaus}
-In the $\Htautau$ search, the background with one or more fake $\had$ candidates is mainly arising from $\ttbar$ or
+In the $\Htautau$ search, the background with one or more fake $\had$ candidates mainly arises from $\ttbar$ or
 multijet production, depending on the analysis channel, with $W$+jets production contributing to a lesser extent. 
-Studies based on the simulation show that, for all above processes, fake $\had$ candidates primarily result from the 
+Studies based on the simulation show that, for all the above processes, fake $\had$ candidates primarily result from the 
 misidentification of light-quark jets, with the contribution from $b$-quarks and gluon jets playing a subdominant role.
-It is also found that the fake rate decreases as the $\had$ candidate $\pt$ increases for all jet flavours.
+It is also found that the fake rate decreases for all jet flavours as the $\had$ candidate $\pt$ increases.
 
@@
 
-The fake $\had$ background prediction in a given SR is modelled by the distribution (referred to as fake $\had$ template) derived from data in the corresponding CR.
+The fake $\had$ background prediction in a given SR is modelled by the distribution (referred to as the fake $\had$ template) derived from data in the corresponding CR.
 The fake $\had$ template is defined as the data distribution from which the contributions from the simulated backgrounds with real $\had$ candidates, originating primarily from
@@
 However, simulation studies indicate that the contribution of $\ttbar$ events to the fake $\had$ background is higher in the SR than in the CR.
-Therefore, an appropriate amount of simulated $\ttbar$ events with fake $\had$ candidates in the CR is added to the fake $\had$ template to match the fake $\had$ background composition in the SR.
+Therefore, an appropriate number of simulated $\ttbar$ events with fake $\had$ candidates in the CR is added to the fake $\had$ template to match the fake $\had$ background composition in the SR.
 In both the $\lephad$ and $\hadhad$ channels, the fake $\had$ template in each SR is initially normalised to the estimated fake $\had$ background yield, 
 defined as the data yield minus the contributions from the simulated backgrounds with real $\had$ candidates (assuming no signal contribution).
-During the statistical analysis, the normalisation of the fake $\had$ background in each SR is allowed to vary unconstrained in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.
+During the statistical analysis, the normalisation of the fake $\had$ background in each SR is allowed to vary freely in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.
 

### 2018-11-21 sections/strategy_Hbb.tex
Implemented more CDS comments from David Stoker

@@
 This section presents an overview of the analysis strategy adopted in the $\Hbb$ search, which
-follows closely that of the previous search performed on the Run 1 dataset~\cite{Aad:2015pja}.
+closely follows that of the previous search performed on the Run 1 dataset~\cite{Aad:2015pja}.
 
@@
 
-Given the choice of the $W\to\ell\nu$ and $H\to b\bar{b}$ decay modes, the $\ttbar \to WbHq$ signal 
+Given that the $W\to\ell\nu$ and $H\to b\bar{b}$ decay modes are chosen, the $\ttbar \to WbHq$ signal 
 is expected to have four jets in the final state, three of them originating from $b$-quarks, which 
@@
 However, the use of the 60\% $b$-tagging efficiency operating point, characterised by a low mistag rate for
-$c$- and light-jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity distribution,
+$c$- and light-jets, results in both the $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity distribution,
 with a very small fraction of events having four or more $b$-tagged jets.
@@
 at least four $b$-tagged jets are dominated by \ttbin. Intermediate compositions are found in regions with exactly three 
-$b$-tagged jets.  Most of the $\ttbar$+light-jets background events in these regions have a charm jet from the hadronic $W$ boson 
-decay  being $b$-tagged, in addition to the two $b$-jets from the top-quark decays.
+$b$-tagged jets.  Most of the $\ttbar$+light-jets background events in these regions have a $b$-tagged charm jet from the hadronic $W$ boson 
+decay, in addition to the two $b$-jets from the top-quark decays.
 
@@
 the selected signal events have a $H \to b\bar{b}$ decay in more than 97\% of the events.
-The other regions have significantly lower signal-to-background ratios, but they are used for the purpose of improving 
+The other regions have significantly lower signal-to-background ratios, but they are used to improve 
 the $\ttbar$+jets background prediction and constraining the related systematic uncertainties
 through a likelihood fit to data.  
-Because of somewhat larger fraction of $\Hc$ signal in the regions with exactly three $b$-tagged jets,
-this analysis is expected to have slightly better sensitivity for $\Hc$ than for $\Hu$ signal.
+Because of a somewhat larger fraction of $\Hc$ signal in the regions with exactly three $b$-tagged jets,
+this analysis is expected to have slightly better sensitivity to a $\Hc$ signal than to a $\Hu$ signal.
 
@@
 \includegraphics[width=0.55\textwidth]{figures/Hbb/fit/cH_plots/Summary.eps}
-\caption{$\Hbb$ search: Comparison between the data and background prediction for the event yields in each of the analysis regions considered 
+\caption{$\Hbb$ search: Comparison between the data and predicted background for the event yields in each of the analysis regions considered 
 before the fit to data (``Pre-Fit''). All events satisfy the preselection requirements, whereas those with exactly two $b$-tagged jets are
@@
 
-This search uses a similar likelihood (LH) discriminant as that developed in Ref.~\cite{Aad:2015pja}.
+This search uses a likelihood (LH) discriminant similar to that developed in Ref.~\cite{Aad:2015pja}.
 The LH variable for a given event is defined as:
@@
 As in Ref.~\cite{Aad:2015pja}, $P^\textrm{sig}$ and $P^\textrm{bkg}$ are approximated as a product of one-dimensional pdfs for
-each of the invariant masses considered, and averaged among all possible parton--jet matching combinations. 
-Combinations are weighted using information on the per-jet multivariate $b$-tagging discriminant value to suppress the impact from 
+each of the invariant masses considered, and averaged over all possible parton--jet matching combinations. 
+Combinations are weighted using the per-jet multivariate $b$-tagging discriminant value to suppress the impact from 
 parton--jet assignments that are inconsistent with the correct flavour of the parton candidates.
@@
 the analysis: $\ttbar$+light-jets and \ttbin. Thus, $P^\textrm{bkg}$ is computed as the average of
-the pdfs for both hypotheses, weighted by their relative fractions found in simulated $\ttbar$+jets events, which depend
+the pdfs for the two hypotheses, weighted by their relative fractions found in simulated $\ttbar$+jets events, which depend
 on the analysis region considered. Furthermore, in a significant fraction of $\Hq$ simulated events (about 40--50\% in regions with exactly three $b$-tagged jets), 
@@
 for several kinematic variables associated with the reconstructed lepton, jets, and missing transverse momentum. 
-The distributions shown correspond to the lepton $\pt$, $\met$, the scalar sum of the transverse momenta of 
+The distributions shown correspond to the lepton $\pt$, the $\met$, the scalar sum of the transverse momenta of 
 the jets, and the invariant mass distribution of the two $b$-tagged jets with lowest $\Delta R$ separation.
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_mbb_mindR.eps}} \\ 
-\caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
+\caption{\small{$\Hbb$ search: Comparison between the data and predicted background for several kinematic 
 distributions in the (4j, 3b) region before the fit to data (``Pre-Fit''). 
@@
 \caption{$\Hbb$ search: Comparison of the distributions of the LH discriminant after preselection 
-between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
+of the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
 and the $t\bar{t}\to WbWb$ background (black solid) in different regions considered in the analysis:
@@
 In the regions with $\geq$4 $b$-tagged jets, the signal acceptance is small, which translates
-into low statistics for the simulated samples. Therefore, only two bins are used for these distributions.} 
+into a small number of events for the simulated samples. Therefore, only two bins are used for these distributions.} 
 \label{fig:LHD}

### 2018-11-21 sections/systematic_uncertainties.tex
Implemented more CDS comments from David Stoker

@@
 
-Several sources of systematic uncertainty are considered that can affect the normalisation of signal 
-and background and/or the shape of their corresponding discriminant distributions.  
+Several sources of systematic uncertainty that can affect the normalisation of signal 
+and background and/or the shape of their corresponding discriminant distributions are considered.
 Each source is considered to be uncorrelated with the other sources.  
@@
 %from the fit to the data.
-%The total systematic uncertainty on the $\Hc$ signal normalisation in the (4 j, 4 b) channel is approximately 17\%, 
+%The total systematic uncertainty in the $\Hc$ signal normalisation in the (4 j, 4 b) channel is approximately 17\%, 
 %with similar contributions from uncertainties related to $b$-tagging and overall signal modelling. After the fit,
@@
 instead the $W$+$c$-jet scale factors.  
-In the case of the $\Hbb$ ($\Htautau$) search, the uncertainties on these scale factors include 
+In the case of the $\Hbb$ ($\Htautau$) search, the uncertainties in these scale factors include 
 a total of 6 independent sources affecting $b$-jets, 1 (2) source(s) affecting $c$-jets, and 17 sources affecting light-jets. 
@@
 and $\pt>750~\gev$ for light-jets); it is taken to be correlated among the three jet flavours. 
-%This uncertainty is evaluated in the simulation by comparing the tagging efficiencies while varying e.g. the fraction 
+%This uncertainty is evaluated in the simulation by comparing the tagging efficiencies while varying e.g.\ the fraction 
 %of tracks with shared hits in the silicon detectors or the fraction of fake tracks resulting from random combinations of hits, 
@@
 by comparing the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 
-The latter uses MMHT2014 LO~\cite{Harland-Lang:2014zoa} PDF set in combination with the H7UE tune~\cite{Bellm:2015jjp}.
-The uncertainty of the modelling of additional radiation is assessed with two alternative {\powheg}+{\pythiaeight} samples:
+The latter uses the MMHT2014 LO~\cite{Harland-Lang:2014zoa} PDF set in combination with the H7UE tune~\cite{Bellm:2015jjp}.
+The uncertainty in the modelling of additional radiation is assessed with two alternative {\powheg}+{\pythiaeight} samples:
 a sample with increased radiation (referred to as radHi) is obtained by decreasing the renormalisation and factorisation scales  
@@
 In the case of the $\Hbb$ search, where the $\ttbar$+HF background plays a prominent role, a more 
-detailed treatment of its associated systematic uncertainties is made. In particular, since several analysis 
-regions have a sufficiently large number of events of \ttbin\ background, its normalisation is 
+detailed treatment of its associated systematic uncertainties is used. In particular, since several analysis 
+regions have a sufficiently large number of \ttbin\ background events, its normalisation is 
 determined in the fit to data.
@@
 to precisely determine it, and the analysis has very limited sensitivity to this uncertainty.
-Since the diagrams that contribute to $\ttbar$+light-jets, \ttcin, \ttbin\
-production are different, all above uncertainties on $\ttbar$+jets
+Since the diagrams that contribute to $\ttbar$+light-jets, \ttcin, and \ttbin\
+production are different, all above uncertainties in $\ttbar$+jets
 background modelling (NLO generator, PS \& Had, and radHi/radLow), except the uncertainty of the inclusive cross section, are
@@
 the contributions to the \ttbin\ background originating from multiple parton interactions.
-Finally, an extra uncertainty on the \ttbin\ background is assigned by 
-comparing
+Finally, an additional uncertainty is assigned to the \ttbin\ background by comparing
 the predictions from {\powheg}+{\pythiaeight} and {\ShOL} 4F (5F vs 4F).
@@
 be the normalisation uncertainty, correlated across all $V$+jets subprocesses. 
-Since {\sherpa}~2.2 has been found to underestimate $V$+heavy-flavour by about a factor
+Since {\sherpa}~2.2 has been found to underestimate $V$+heavy-flavour production by about a factor
 of 1.3~\cite{Aaboud:2017xsd}, additional 30\% normalisation uncertainties are assumed for $V$+$\geq$1$c$+jets and $V$+$\geq$1$b$+jets
@@
 corresponding uncertainty of the $\ttbar$+jets background.
-An additional systematic uncertainty on $tW$-channel production concerning the separation 
+An additional systematic uncertainty in $tW$-channel production concerning the separation 
 between $t\bar{t}$ and $tW$ at NLO is assessed by comparing
@@
 contributions from the limited size of the data sample, particularly at high jet and $b$-tag multiplicities, as 
-well as from the uncertainty on the rate of fake leptons, estimated in 
-different control regions (e.g. selected with a requirement on either the maximum $\met$ or $\mtw$). 
+well as from the uncertainty in the rate of fake leptons, estimated in 
+different control regions (e.g.\ selected with a requirement on either the maximum $\met$ or $\mtw$). 
 A combined normalisation uncertainty of 50\% due 
@@
 
-Uncertainties on the data-driven fake $\had$ background in the $\Htautau$ search are obtained by using additional signal-depleted regions.
+Uncertainties of the data-driven fake $\had$ background in the $\Htautau$ search are obtained by using additional signal-depleted regions.
 The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\had$ identification criteria, and thus referred to as ``loose SR''  and ``loose CR''.
 %The shape difference between the fake $\tauhad$ background prediction in each loose SR and its associated loose CR
-%is applied as an uncertainty on the prediction in the nominal SR.
+%is assigned as an uncertainty in the prediction in the nominal SR.
 %In each loose SR, the shape difference between the data and the fake $\tauhad$ background estimate based on its associated loose CR,
 %in both cases having subtracted the small contribution from real $\tauhad$ candidates based on the simulation, 
-%is applied as an uncertainty on the prediction in the nominal SR. 
-%In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty on the prediction in the nominal SR. 
-In each loose SR, after subtracting the small contribution from real $\had$ candidates based on the simulation, 
+%is applied as an uncertainty in the prediction in the nominal SR. 
+%In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty in the prediction in the nominal SR. 
+In each loose SR, after subtracting the small simulation-predicted contribution from real $\had$ candidates, 
 the relative difference in the shape of the distribution between the remaining data and the fake $\had$ background estimate based on its associated loose CR 
-is applied as an uncertainty on the prediction in the nominal SR.
+is assigned as an uncertainty of the prediction in the nominal SR.
 In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\had$ candidate from the simulation that are added to the fake $\had$ template in the $\hadhad$ channel as part of the fake $\had$ background estimation procedure.
@@
 The same uncertainty is assigned to the selected signal events with fake $\had$ candidates.
-In addition, a systematic uncertainty is assigned to account for the different fractional composition of particles (various types of leptons and partons) originating the fake $\had$ candidates 
+In addition, a systematic uncertainty is assigned to account for the different fractional composition of particles (various types of leptons and partons) producing the fake $\had$ candidates 
 between each SR and its corresponding CR in the $\ttbar$ simulation. 

### 2018-11-21 sections/objects.tex
Implemented CDS comments by Tom LeCompte, Christian Johnson, and Jason Nielsen

@@
 This soft term is calculated from inner-detector tracks matched to the selected primary vertex to make it more resilient to
-contamination from pile-up interactions~\cite{run_2_met,ATL-PHYS-PUB-2015-027}.
+contamination from pile-up interactions~\cite{Aaboud:2018tkc}.

### 2018-11-21 sections/conclusion.tex

@@
 No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
-In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
+In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios 
 are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$, respectively.
@@
 yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
-and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming respectively $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$.
+and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$ respectively.
 The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 

### 2018-11-21 sections/detector.tex

@@
 including the %newly-installed
-insertable B-layer~\cite{IBL}, installed in 2014,
+insertable B-layer~\cite{IBL1,IBL2}, installed in 2014,
 and a silicon microstrip tracker,

### 2018-11-21 sections/statistical_analysis.tex

@@
 a product of Poisson probability terms over all bins considered in the search. This function depends
-on the signal-strength parameter $\mu$, defined as a multiplicative factor to the yield for $\Hq$ signal events
+on the signal-strength parameter $\mu$, defined as a factor multiplying the yield of $\Hq$ signal events
 normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$,
-and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties of the signal and background expectations. 
+and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations. 
 Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
 All nuisance parameters are subject to additional Gaussian or log-normal constraints in the likelihood, with the exception of a few parameters 
-that control the normalisation of some background components (e.g. the \ttbin\ background in the case of the $\Hbb$ search), which 
+that control the normalisation of some background components (e.g.\ the \ttbin\ background in the case of the $\Hbb$ search), which 
 are treated as free parameters in the fit.
@@
 
-The fitting procedure is initially validated through extensive studies using mock data, defined as the sum of all predicted backgrounds 
+The fitting procedure was initially validated through extensive studies using mock data, defined as the sum of all predicted backgrounds 
 plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
@@
 In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
-when varying assumptions on some of the leading sources of uncertainty. 
+when varying assumptions about some of the leading sources of uncertainty. 
 After this, the blinding requirements
 are removed in the data and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
-nuisance parameters before and after removal of the blinding requirements, which are found to be consistent. In addition, it is verified that the 
-fit is able to correctly determine the strength of a simulated signal injected in the real data.
+nuisance parameters before and after removal of the blinding requirements, and their values are found to be consistent. In addition, it is verified that the 
+fit is able to correctly determine the strength of a simulated signal injected into the real data.
 
@@
 The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
-A related statistic is used to determine the compatibility of the observed data with the background-only hypothesis (the so-called discovery test)  
+A related statistic is used to determine whether the observed data is compatible with the background-only hypothesis (the so-called discovery test)  
 by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.

### 2018-11-21 sections/strategy_Htautau.tex

@@
 
-The analysis strategy adopted in the $\Htautau$ search follows closely that developed in Ref.~\cite{Chen:2015nta} and is summarised in this section.
+The analysis strategy adopted in the $\Htautau$ search closely follows that developed in Ref.~\cite{Chen:2015nta} and is summarised in this section.
 
@@
 top quark ($t \to Wb \to qqb$) are rejected, as the $t \to Hq$ decay cannot be reconstructed due to the missing light-quark jet.
-This compatibility is assessed via a likelihood function that depens on the reconstructed mass of the three-jet 
+This compatibility is assessed via a likelihood function that depends on the reconstructed mass of the three-jet 
 system and the two non-$b$-tagged jets.
@@
 are estimated by minimising a $\chi^2$ function based on the probability density functions for the angular distance of the visible and invisible
-decay products in the $\tau$-lepton decay, and including Gaussian constraints on the $\tau$-lepton mass, the Higgs boson mass and the
-measured $\met$. After the $\chi^2$ minimisation, an improved resolution is obtained on the determination of the Higgs boson four-momentum, and hence
-its invariant mass, as well as on the four-momentum of the parent top quark. Following the event kinematic reconstruction, several kinematic variables
+products of the $\tau$-lepton decay, and including Gaussian constraints on the $\tau$-lepton mass, the Higgs boson mass and the
+measured $\met$. After the $\chi^2$ minimisation, the Higgs boson four-momentum, and hence its invariant mass, as well as the 
+four-momentum of the parent top quark, are determined with better resolution. Following the event kinematic reconstruction, several kinematic variables
 that discriminate between signal and background are defined. These variables are used in the multivariate analysis discussed in the next section.
@@
 
-A large set of potential variables was investigated in each SR separately, and only those variables that led to an improved discrimination
-performance of the BDT were kept.  The BDT input variables in each SR are listed in Table~\ref{tab:mva_var} and defined in the following:
+A large set of potential variables were investigated in each SR separately, and only those variables that led to better discrimination
+by the BDT were kept.  The BDT input variables in each SR are listed in Table~\ref{tab:mva_var} and defined in the following:
 
@@
 \item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\met$ in the $\lephad$ channel.
-\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\had$ candidate (denoted as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\had$ candidates (denoted as particles 1 and 2 respectively) in the $\hadhad$ channel.
+\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\had$ candidate (referred to as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\had$ candidates (referred to as particles 1 and 2 respectively) in the $\hadhad$ channel.
 \item $\met$ $\phi$ centrality: a variable that quantifies the angular position of the $\mpt$ relative to the 
@@
 Among these variables, the most discriminating are $m_{\tau\tau}^{\text{fit}}$, $p_{\text{T},2}$, $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$.
-A comparison between data and background prediction for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:BDT_inputs_lephad} and~\ref{fig:BDT_inputs_hadhad}.
+A comparison between data and the predicted background for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:BDT_inputs_lephad} and~\ref{fig:BDT_inputs_hadhad}.
 A good description of the data by the background model is observed in all cases.
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
-\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of some of the most
+\caption{$\Htautau$ search: Comparison between the data and predicted background after preselection for the distributions of two of the most
 discriminating BDT input variables in the $\lephad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_4j_FR.eps}} \\
-\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of two of the most 
+\caption{$\Htautau$ search: Comparison between the data and predicted background after preselection for the distributions of two of the most 
 discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh4j/canv_.eps}} \\
-\caption{$\Htautau$ search: Comparison of the distributions of the BDT discriminant after preselection between the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
+\caption{$\Htautau$ search: Comparison of the distributions of the BDT discriminant after preselection of the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
 and the total background (black solid) in the different search regions considered:

### 2018-11-26 sections/objects.tex
v2.1 after 2nd circulation

@@
 removal of jets whose axis lies within $\Delta R=0.2$ of the leading (highest-$\pt$) $\had$ candidate or the two leading $\had$ candidates (depending on the
-analysis channel). In addition, the muon--jet overlap removal is slightly different:
+search channel). In addition, the muon--jet overlap removal is slightly different:
 if a muon lies within $\Delta R = 0.2$ of the axis of a jet, the jet is removed if either it has fewer than three tracks originating from the 

### 2018-11-26 sections/statistical_analysis.tex
v2.1 after 2nd circulation

@@
 by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
-The $p$-value (referred to as $p_0$) representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
+The $p$-value (referred to as $p_0$), representing the level of agreement between the data and the background-only hypothesis, is estimated by integrating
+%representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
 %the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
@@
 %The observed $p_0$-value is checked for each explored signal scenario.
-In the case of the data being compatible with the background-only hypothesis, upper limits on $\mu$, and thus on 
+%In the case of the data being compatible with the background-only hypothesis, 
+Upper limits on $\mu$, and thus on 
 $\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.

### 2018-11-26 sections/strategy_Hbb.tex
v2.1 after 2nd circulation

@@
 Because of a somewhat larger fraction of $\Hc$ signal in the regions with exactly three $b$-tagged jets,
+resulting from the higher mistag rate for $c$-jets than for light-jets,
 this analysis is expected to have slightly better sensitivity to a $\Hc$ signal than to a $\Hu$ signal.
@@
 \end{equation*}
-where $P^\textrm{sig}(\mathbf{x}) $ and $P^\textrm{bkg}(\mathbf{x}) $ represent the probability density functions (pdf) of a given event under
+where $P^\textrm{sig}(\mathbf{x}) $ and $P^\textrm{bkg}(\mathbf{x})$ represent the probability density functions (pdf) of a given event under
 the signal hypothesis ($\ttbar \to WbHq$) and under the background hypothesis ($\ttbar \to WbWb$), respectively.
-Both $P^\textrm{sig}$ and $P^\textrm{bkg}$ are functions of $\mathbf{x}$, which denotes the set of two-body and three-body invariant masses 
-that correspond to the expected resonances in the event (the leptonically decaying $W$ boson, the Higgs boson or the hadronically 
-decaying $W$ boson, and the corresponding parent top quarks). These invariant masses are computed from the reconstructed 
-lepton, jets, and missing transverse momentum.
-As in Ref.~\cite{Aad:2015pja}, $P^\textrm{sig}$ and $P^\textrm{bkg}$ are approximated as a product of one-dimensional pdfs for
-each of the invariant masses considered, and averaged over all possible parton--jet matching combinations. 
+%Both $P^\textrm{sig}$ and $P^\textrm{bkg}$ are functions of $\mathbf{x}$, which denotes the set of two-body and three-body invariant masses 
+%that correspond to the expected resonances in the event (the leptonically decaying $W$ boson, the Higgs boson or the hadronically 
+%decaying $W$ boson, and the corresponding parent top quarks). These invariant masses are computed from the reconstructed 
+%lepton, jets, and missing transverse momentum.
+%As in Ref.~\cite{Aad:2015pja}, $P^\textrm{sig}$ and $P^\textrm{bkg}$ are approximated as a product of one-dimensional pdfs for
+%each of the invariant masses considered, and averaged over all possible parton--jet matching combinations. 
+%
+Both $P^\textrm{sig}$ and $P^\textrm{bkg}$ are functions of $\mathbf{x}$, representing the four-momentum vectors of all final-state particles at the reconstruction level:
+the lepton, the missing transverse momentum, and the selected jets in a given analysis region.
+The value of the multivariate $b$-tagging discriminant for each jet is also included in $\mathbf{x}$.
+As in Ref.~\cite{Aad:2015pja}, $P^\textrm{sig}$ and $P^\textrm{bkg}$ are approximated as a product of one-dimensional pdfs 
+over the set of two-body and three-body invariant masses that correspond to the expected resonances in the event (the leptonically decaying $W$ boson, 
+the Higgs boson or the hadronically decaying $W$ boson, and the corresponding parent top quarks) and averaged over all possible parton--jet matching combinations. 
+%
 Combinations are weighted using the per-jet multivariate $b$-tagging discriminant value to suppress the impact from 
 parton--jet assignments that are inconsistent with the correct flavour of the parton candidates.
+The invariant masses are computed from the reconstructed lepton, missing transverse momentum, and jets. After a suitable transformation of the three-body invariant masses 
+(see Ref.~\cite{Aad:2015pja}), all considered invariant mass variables are largely uncorrelated, thus making possible the factorisation of $P^\textrm{sig}$ and $P^\textrm{bkg}$
+as discussed above.
 
@@
 the jets, and the invariant mass distribution of the two $b$-tagged jets with lowest $\Delta R$ separation. 
-In general, a good description of the data by the background prediction is observed.
+The variables displayed do not correspond directly to those used internally in the evaluation the LH discriminant, as to build them it is necessary 
+to select a particular signal or background hypothesis and a jet permutation. Instead, these distributions are shown to demonstrate that
+a good description of the data by the background prediction is observed in several kinematic variables related to the information used in 
+the LH discriminant construction. 
+%In general, a good description of the data by the background prediction is observed.
 
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_mbb_mindR.eps}} \\ 
-\caption{\small{$\Hbb$ search: Comparison between the data and predicted background for several kinematic 
+\caption{\small{$\Hbb$ search: Comparison between the data and predicted background after preselection for several kinematic 
 distributions in the (4j, 3b) region before the fit to data (``Pre-Fit''). 

### 2018-11-26 sections/strategy_Htautau.tex
v2.1 after 2nd circulation

@@
 \item $m_{Hq}$: the invariant mass of the reconstructed Higgs boson and the associated light-quark jet in the $t \to Hq$ decay, corresponding to the reconstructed mass of the parent top quark.
-\item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\met$ in the $\lephad$ channel.
+\item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\mpt$ in the $\lephad$ channel.
 \item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\had$ candidate (referred to as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\had$ candidates (referred to as particles 1 and 2 respectively) in the $\hadhad$ channel.
-\item $\met$ $\phi$ centrality: a variable that quantifies the angular position of the $\mpt$ relative to the 
-visible $\tau$-lepton decay products in the transverse plane. The transverse plane is transformed such that the directions of the $\tau$-lepton decay products are 
-orthogonal, and that the smaller angle between the $\tau$-lepton decay products defines the positive quadrant of the transformed plane. 
-The $\met$ $\phi$ centrality is defined as the sum of the $x$ and $y$ components of the $\mpt$ unit vector in this transformed plane.
+\item $\met$ $\phi$ centrality: a variable that quantifies the angular position of $\mpt$ relative to the visible $\tau$-lepton decay products in the transverse plane. It is defined as:
+\begin{equation*}
+\met\; \phi\; \mathrm{centrality} = \frac{\sin(\phi_\mathrm{miss}-\phi_1)+\sin(\phi_\mathrm{miss}-\phi_2)}{\sqrt{\sin^2(\phi_\mathrm{miss}-\phi_1)+\sin^2(\phi_\mathrm{miss}-\phi_2)}}
+\end{equation*}
+\noindent where $\phi_\mathrm{miss}$ denotes the azimuthal angle of $\mpt$, and $\phi_1$ and $\phi_2$ denote the azimuthal angles the two $\tau$-lepton candidates 
+(the lepton and $\had$ candidate in the $\lephad$ channel, or the leading and trailing $\had$ candidates in the $\hadhad$ channel), referred to as particles 1 and 2 respectively.
+%The transverse plane is transformed such that the directions of the $\tau$-lepton decay products are 
+%rthogonal, and that the smaller angle between the $\tau$-lepton decay products defines the positive quadrant of the transformed plane. 
+%The $\met$ $\phi$ centrality is defined as the sum of the $x$ and $y$ components of the $\mpt$ unit vector in this transformed plane.
 %\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).

### 2018-11-26 sections/systematic_uncertainties.tex
v2.1 after 2nd circulation

@@
 
-In the case of the $\Hbb$ search, where the $\ttbar$+HF background plays a prominent role, a more 
+In the case of the $\Hbb$ search, where the $\ttbar$+HF background plays a prominent role (see Fig.~\ref{fig:Hbb_Summary}), a more 
 detailed treatment of its associated systematic uncertainties is used. In particular, since several analysis 

### 2018-12-18 sections/detector.tex
v2.2 implementing Lucia Di Ciaccio's CDS comments

--- 2018-11-21 sections/detector.tex
@@
 2~T axial magnetic field, electromagnetic and hadronic calorimeters, and a muon spectrometer
-incorporating three large toroid magnet assemblies. The inner detector contains a high-granularity silicon pixel detector, 
+incorporating three large toroid magnet assemblies with eight coils each. The inner detector contains a high-granularity silicon pixel detector, 
 including the %newly-installed
-insertable B-layer~\cite{IBL}, installed in 2014,
+insertable B-layer~\cite{Abbott:2018ikt}, installed in 2014,
 and a silicon microstrip tracker,

### 2018-12-18 sections/objects.tex
v2.2 implementing Lucia Di Ciaccio's CDS comments

@@
 
-Electron candidates~\cite{ATLAS-CONF-2016-024,ATL-PHYS-PUB-2016-015} are reconstructed from energy 
+Electron candidates~\cite{ATLAS-CONF-2016-024,Aaboud:2018ugz} are reconstructed from energy 
 clusters in the EM calorimeter that are matched to reconstructed tracks in the inner detector;

### 2018-12-18 sections/statistical_analysis.tex
v2.2 implementing Lucia Di Ciaccio's CDS comments

@@
 a product of Poisson probability terms over all bins considered in the search. This function depends
-on the signal-strength parameter $\mu$, defined as a factor multiplying the yield of $\Hq$ signal events
+on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $\Hq$ signal events
 normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$,
@@
 Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
-All nuisance parameters are subject to additional Gaussian or log-normal constraints in the likelihood, with the exception of a few parameters 
+All nuisance parameters are subject to Gaussian or log-normal constraints in the likelihood, with the exception of a few parameters 
 that control the normalisation of some background components (e.g.\ the \ttbin\ background in the case of the $\Hbb$ search), which 

### 2018-12-18 sections/strategy_Htautau.tex
v2.2 implementing Lucia Di Ciaccio's CDS comments

@@
 %The event reconstruction strategy used~\cite{Chen:2015nta} is summarised in the following.
-The event reconstruction is based on the strategy used in Ref.~\cite{Chen:2015nta}.
+The event kinematic reconstruction is based on the strategy used in Ref.~\cite{Chen:2015nta}, and is summarised below.
 
@@
 products of the $\tau$-lepton decay, and including Gaussian constraints on the $\tau$-lepton mass, the Higgs boson mass and the
-measured $\met$. After the $\chi^2$ minimisation, the Higgs boson four-momentum, and hence its invariant mass, as well as the 
+measured $\met$ within their expected resolutions. The resolution on the $\tau$-lepton mass and the Higgs boson mass are taken to be 
+$1.8~\gev$ and $20~\gev$, respectively, while the resolution on the measured $\met$ is parameterised as a linear function of 
+$\sqrt{\sum E_T}$, with $\sum E_T$ denoting the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
+After the $\chi^2$ minimisation, the Higgs boson four-momentum, and hence its invariant mass, as well as the 
 four-momentum of the parent top quark, are determined with better resolution. Following the event kinematic reconstruction, several kinematic variables
@@
 %draft 1 version
-%In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
-%whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
 In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\had$ contributions), 
-elsewhere the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account.
+whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
+%In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\had$ contributions),
+%elsewhere the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account.
 

### 2018-12-18 sections/systematic_uncertainties.tex
v2.2 implementing Lucia Di Ciaccio's CDS comments

@@
 
-The uncertainty in the integrated luminosity is 2.1\%, affecting the overall normalisation of
-all processes estimated from the simulation. It is derived, following a methodology similar to that detailed in Ref.~\cite{Aaboud:2016hhf}, 
-from a calibration of the luminosity scale using $x$--$y$ beam-separation scans performed in August 2015 and May 2016.
+The uncertainty in the integrated luminosity is 2.1\%, affecting the overall normalisation of all processes estimated from the simulation. 
+%It is derived, following a methodology similar to that detailed in Ref.~\cite{Aaboud:2016hhf}, 
+%from a calibration of the luminosity scale using $x$--$y$ beam-separation scans performed in August 2015 and May 2016.
+It is derived, following a methodology similar to that detailed in Ref.~\cite{Aaboud:2016hhf}, and using the LUCID-2 detector 
+for the baseline luminosity measurements \cite{Avoni:2018iuv}, from a calibration of the luminosity scale using $x$--$y$ beam-separation scans.
 
@@
 
-Efficiencies to tag jets from $b$- and $c$-quarks in the simulation are corrected to match the efficiencies in data by $\pt$-dependent factors,
+Efficiencies to tag $b$-jets and $c$-jets in the simulation are corrected to match the efficiencies in data by $\pt$-dependent factors,
 whereas the light-jet efficiency is scaled by $\pt$- and $\eta$-dependent factors.
@@
 
-Uncertainties of the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah},
+Uncertainties of the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah,Campbell:2011bn},
 as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
@@
 Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the selected jet multiplicity,  
-34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively.
+resulting in 34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively. 
 Recent comparisons between data and {\sherpa}~2.1.1 for $WZ(\to \ell\nu\ell\ell) + \geq$4 jets show
 agreement within the experimental uncertainty of approximately 40\%~\cite{Aaboud:2016yus}, which further justifies the above uncertainty.
+Given the very small contribution of this background to the total prediction, the final result is not affected by the assumed modelling
+uncertainties.
 
@@
 well as from the uncertainty in the rate of fake leptons, estimated in 
-different control regions (e.g.\ selected with a requirement on either the maximum $\met$ or $\mtw$). 
+different control regions (e.g.\ selected with a upper requirement on either $\met$ or $\mtw$). 
 A combined normalisation uncertainty of 50\% due 

### 2018-12-20 sections/systematic_uncertainties.tex
v2.2 again fixing two last Lucia Di Ciaccio's CDS comments

@@
 well as from the uncertainty in the rate of fake leptons, estimated in 
-different control regions (e.g.\ selected with a upper requirement on either $\met$ or $\mtw$). 
+different control regions (e.g.\ selected with an upper requirement on either $\met$ or $\mtw$). 
 A combined normalisation uncertainty of 50\% due 

### 2018-12-21 ANA-TOPQ-2017-07-PAPER-auxmat.tex

@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_mbb_mindR.eps}} \\ 
-\caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
+\caption{\small{$\Hbb$ search: Comparison between the data and predicted background for several kinematic 
 distributions in the (4j, 2b) region (prior to the application of the cut on the LH discriminant above 0.6) before  the fit to data (``Pre-Fit''). 
@@
 %\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_mbb_mindR.eps}} \\ 
-%\caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
+%\caption{\small{$\Hbb$ search: Comparison between the data and predicted background for several kinematic 
 %distributions in the (4j, 3b) region before performing the fit to data (``Pre-Fit''). 
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_mbb_mindR.eps}} \\ 
-\caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
+\caption{\small{$\Hbb$ search: Comparison between the data and predicted background for several kinematic 
 distributions in the (5j, 3b) region before the fit to data (``Pre-Fit''). 
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_lephad_4j_FR.eps}} \\
-\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of some of the most
+\caption{$\Htautau$ search: Comparison between the data and predicted background for the distribution of some of the most
 discriminating BDT input variables in the $\lephad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_lephad_4j_FR.eps}} \\
-\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of some of the most
+\caption{$\Htautau$ search: Comparison between the data and predicted background for the distribution of some of the most
 discriminating BDT input variables in the $\lephad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_lephad_4j_FR.eps}} \\
-\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of some of the most
+\caption{$\Htautau$ search: Comparison between the data and predicted background for the distribution of some of the most
 discriminating BDT input variables in the $\lephad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_hadhad_4j_FR.eps}} \\
-\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
+\caption{$\Htautau$ search: Comparison between the data and predicted background for the distribution of two of the most 
 discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_hadhad_4j_FR.eps}} \\
-\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
+\caption{$\Htautau$ search: Comparison between the data and predicted background for the distribution of two of the most 
 discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
@@
 \subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_hadhad_4j_FR.eps}} \\
-\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
+\caption{$\Htautau$ search: Comparison between the data and predicted background for the distribution of two of the most 
 discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for

### 2018-12-21 sections/detector.tex

@@
 including the %newly-installed
-insertable B-layer~\cite{Abbott:2018ikt}, installed in 2014,
+insertable B-layer~\cite{IBL1,IBL2,Abbott:2018ikt}, installed in 2014,
 and a silicon microstrip tracker,

### 2018-12-21 sections/introduction.tex

@@
 since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta}. 
-While other FCNC top couplings, $tq\gamma$, $tqZ$, $tqg$, are also enhanced in these scenarios beyond the SM, 
-the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling. 
-%See Ref.~\cite{Agashe:2013hma} for a review.
-%\textbf{Update a bit above paragraph mentioning more recent models.}
+While other FCNC top couplings ($tq\gamma$, $tqZ$, $tqg$) are also enhanced in these scenarios beyond the SM, 
+the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling~\cite{Agashe:2013hma}.
 
@@
 %The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
-The searches presented in this paper are focussed on fermionic decay modes. Therefore, they help to complete the 
+The searches presented in this paper are focussed on fermionic decay modes of the Higgs boson. Therefore, they help to complete the 
 ATLAS experiment's programme of searches for $t \to Hq$ decays based on $pp$ collision

### 2018-12-21 sections/signal_background_modeling.tex

@@
 In the $\Htautau$ search, the background with one or more fake $\had$ candidates mainly arises from $\ttbar$ or
-multijet production, depending on the analysis channel, with $W$+jets production contributing to a lesser extent. 
+multijet production, depending on the search channel, with $W$+jets production contributing to a lesser extent. 
 Studies based on the simulation show that, for all the above processes, fake $\had$ candidates primarily result from the 

### 2018-12-30 ANA-TOPQ-2017-07-PAPER-auxmat.tex
changing sections for pdf figures

@@
 \begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_lep0_pt.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_met.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_hthad.eps}} 
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_mbb_mindR.eps}} \\ 
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_lep0_pt.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_met.pdf}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_hthad.pdf}} 
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_mbb_mindR.pdf}} \\ 
 \caption{\small{$\Hbb$ search: Comparison between the data and predicted background for several kinematic 
@@
 \begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_lep0_pt.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_met.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_hthad.eps}} 
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_mbb_mindR.eps}} \\ 
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_lep0_pt.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_met.pdf}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_hthad.pdf}} 
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_mbb_mindR.pdf}} \\ 
 \caption{\small{$\Hbb$ search: Comparison between the data and predicted background for several kinematic 
@@
 \begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_lephad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_lephad_4j_FR.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_lephad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_lephad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_lephad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_lephad_4j_FR.pdf}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_lephad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_lephad_4j_FR.pdf}} \\
 \caption{$\Htautau$ search: Comparison between the data and predicted background for the distribution of some of the most
@@
 \begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/met_centrality_lephad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/met_centrality_lephad_4j_FR.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_lephad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_lephad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/met_centrality_lephad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/met_centrality_lephad_4j_FR.pdf}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_lephad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_lephad_4j_FR.pdf}} \\
 \caption{$\Htautau$ search: Comparison between the data and predicted background for the distribution of some of the most
@@
 \begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_perp_lephad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_perp_lephad_4j_FR.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_lephad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_lephad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_perp_lephad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_perp_lephad_4j_FR.pdf}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_lephad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_lephad_4j_FR.pdf}} \\
 \caption{$\Htautau$ search: Comparison between the data and predicted background for the distribution of some of the most
@@
 \begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_hadhad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_hadhad_4j_FR.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_hadhad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_hadhad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_hadhad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_hadhad_4j_FR.pdf}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_hadhad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_hadhad_4j_FR.pdf}} \\
 \caption{$\Htautau$ search: Comparison between the data and predicted background for the distribution of two of the most 
@@
 \begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/met_centrality_hadhad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/met_centrality_hadhad_4j_FR.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_hadhad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_hadhad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/met_centrality_hadhad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/met_centrality_hadhad_4j_FR.pdf}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_hadhad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/mtop_thc_hadhad_4j_FR.pdf}} \\
 \caption{$\Htautau$ search: Comparison between the data and predicted background for the distribution of two of the most 
@@
 \begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_perp_hadhad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_perp_hadhad_4j_FR.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_hadhad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_hadhad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_perp_hadhad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_perp_hadhad_4j_FR.pdf}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_hadhad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/MET_proj_hadhad_4j_FR.pdf}} \\
 \caption{$\Htautau$ search: Comparison between the data and predicted background for the distribution of two of the most 
@@
 \begin{center}
-\includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_bb.eps} \\
+\includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_bb.pdf} \\
 \caption{$\Hbb$ search: Ranking of the nuisance parameters included in the fit according to their impact on the measured signal strength $\mu$, in
@@
 \begin{center}
-\includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_tt.eps} \\
+\includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_tt.pdf} \\
 \caption{$\Htautau$ search: Ranking of the nuisance parameters included in the fit according to their impact on the measured signal strength $\mu$, in

### 2018-12-30 sections/strategy_Hbb.tex
changing sections for pdf figures

@@
 %\includegraphics[width=0.55\textwidth]{figures/Hbb/fit/base_ebv2_signal_cH_default_unblinded_splusb/Plots/Summary.png}
-\includegraphics[width=0.55\textwidth]{figures/Hbb/fit/cH_plots/Summary.eps}
+\includegraphics[width=0.55\textwidth]{figures/Hbb/fit/cH_plots/Summary.pdf}
 \caption{$\Hbb$ search: Comparison between the data and predicted background for the event yields in each of the analysis regions considered 
@@
 \begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_lep0_pt.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_met.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_hthad.eps}} 
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_mbb_mindR.eps}} \\ 
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_lep0_pt.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_met.pdf}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_hthad.pdf}} 
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_mbb_mindR.pdf}} \\ 
 \caption{\small{$\Hbb$ search: Comparison between the data and predicted background after preselection for several kinematic 
@@
 \begin{center}
-\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep4jex2bex_FcncDiscriminant.eps}} 
-\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep4jex3bex_FcncDiscriminant.eps}}
-\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep4jex4bin_FcncDiscriminant.eps}} \\
-\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep5jex2bex_FcncDiscriminant.eps}}
-\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep5jex3bex_FcncDiscriminant.eps}}
-\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep5jex4bin_FcncDiscriminant.eps}} \\
-\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep6jin2bex_FcncDiscriminant.eps}}
-\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep6jin3bex_FcncDiscriminant.eps}}
-\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep6jin4bin_FcncDiscriminant.eps}} \\
+\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep4jex2bex_FcncDiscriminant.pdf}} 
+\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep4jex3bex_FcncDiscriminant.pdf}}
+\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep4jex4bin_FcncDiscriminant.pdf}} \\
+\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep5jex2bex_FcncDiscriminant.pdf}}
+\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep5jex3bex_FcncDiscriminant.pdf}}
+\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep5jex4bin_FcncDiscriminant.pdf}} \\
+\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep6jin2bex_FcncDiscriminant.pdf}}
+\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep6jin3bex_FcncDiscriminant.pdf}}
+\subfloat[]{\includegraphics[width=0.33\textwidth]{figures/Hbb/discriminant_shape/canv_c1lep6jin4bin_FcncDiscriminant.pdf}} \\
 \caption{$\Hbb$ search: Comparison of the distributions of the LH discriminant after preselection 

### 2018-12-30 sections/strategy_Htautau.tex

@@
 \begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_4j_FR.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_4j_FR.pdf}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.pdf}} \\
 \caption{$\Htautau$ search: Comparison between the data and predicted background after preselection for the distributions of two of the most
@@
 \begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_4j_FR.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_4j_FR.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_4j_FR.pdf}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_4j_FR.pdf}} \\
 \caption{$\Htautau$ search: Comparison between the data and predicted background after preselection for the distributions of two of the most 
@@
 \begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl3j/canv_.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl4j/canv_.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh3j/canv_.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh4j/canv_.eps}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl3j/canv_.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl4j/canv_.pdf}} \\
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh3j/canv_.pdf}}
+\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh4j/canv_.pdf}} \\
 \caption{$\Htautau$ search: Comparison of the distributions of the BDT discriminant after preselection of the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 

### 2019-03-27 sections/introduction.tex

@@
 Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
-and of type II, such as the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk}, or supersymmetric models
-with R-parity violation~\cite{Eilam:2001dh}. In these scenarios, branching ratios can be as high as $\BR(t\to Hq) \sim 10^{-5}$. 
+and of type II, such as the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk,Cao:2014udj}, supersymmetric models
+with R-parity violation~\cite{Eilam:2001dh}, composite Higgs models with partial compositeness~\cite{Azatov:2014lha}, 
+or warped extra dimensions models with SM fermions in the bulk~\cite{Azatov:2009na}. 
+In these scenarios, branching ratios can be as high as $\BR(t\to Hq) \sim 10^{-5}$. 
 An even larger branching ratio of  $\BR(t\to Hc) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
-since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta}. 
+since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}. 
 While other FCNC top couplings ($tq\gamma$, $tqZ$, $tqg$) are also enhanced in these scenarios beyond the SM, 

### 2019-03-27 sections/systematic_uncertainties.tex

@@
 and $\pt>750~\gev$ for light-jets); it is taken to be correlated among the three jet flavours. 
+Since the fraction of signal and background in this kinematic regime is very small, these uncertainties have a negligible
+impact in the analyses.
 %This uncertainty is evaluated in the simulation by comparing the tagging efficiencies while varying e.g.\ the fraction 
@@
 Finally, an uncertainty related to the application of $c$-jet scale factors to $\tau$-jets is considered,
-but has a negligible impact in these analyses.
+which also has a negligible impact.
+%but has a negligible impact in these analyses.
 

### 2019-04-12 resubmission2/referee-replies.txt
Implemented referee replies (round 2)

Dear reviewer,

Thanks for your useful comments, which helped to improve the clarity of the paper.
Please find our replies below, starting by “——>”.

Best regards,

The ATLAS Collaboration

I reviewed the new draft and the responses provided by the authors. I am satisfied with the improvements in the draft and many of the answers offered by the authors. But there are still a few points that deserve further clarification:

- Concerning the answer to my first question, the authors explained very well that the SM-like assumption for the Higgs Branching Ratios is safe in the context of the considered simplified model. I would like this explanation to translate into a clarifying modification of the text, so that this fact is spelled out.

----> The following clarifying statements have been added in the 2nd paragraph of Sect. 1:

“The simplifying assumption of SM-like Higgs boson branching ratios is motivated by the fact that measurements of the flavour-diagonal Higgs boson couplings by the ATLAS and CMS collaborations are in agreement with the SM prediction within about 10\%~\cite{Khachatryan:2016vau,Sirunyan:2018koj}. Furthermore, typical beyond-the-SM scenarios that predict significant enhancements to $\BR(t\to Hq)$, also predict modifications to the Higgs boson branching ratios at the few percent level or below, well beyond the current experimental precision.”

- Once I take the answer to the previous comment for granted, I am puzzled by the answer to the following point. I was just convinced that the BRs of the Higgs in the considered scenario are SM-like and then, when I raise a question about the small impact of the presented measurement (I am trying to understand if this paper meets the JHEP standard or not, which is part of my referee role) I am told that every BR should be tested. I can agree with that, if one expects some final-state-related deviation. But I was told that this is not the case in the considered scenario. I see two options here: or the two provided answers are contradicting each other or (as I believe) it is interesting to perform these studies beyond the stringent assumptions of the considered simplified model. But then, if this is the case, the paper is missing to consider an alternative scenario where the predictions of Higgs BR values are broken and BSM effects are enhanced in the final states considered in this paper. To me, this is the most relevant point left.

----> There is no contradiction between the answers. As explained in the first set of replies, the assumption of SM-like Higgs boson branching ratios is well motivated and we would not consider it particularly stringent. The reason to perform the search for different Higgs boson decay modes is (we reproduce the original answer): “... to assess the overall consistency of the results obtained, as well as to improve the sensitivity through their combination. By combining all searches, the expected sensitivity is improved by about a factor of two relative to the most sensitive published individual searches.”  Leaving aside the improvement in sensitivity through the combination, the consistency check is important since the different searches have very different experimental signatures, and thus are affected by different backgrounds and systematic uncertainties. If a significant deviation is seen in one of the searches, one would like to know whether it’s also seen in the other searches, to determine its consistency with a FCNC signal interpretation. To make this clearer, the following sentences were added at the end of Sect. 1:

“The combination is performed after verifying the overall consistency of the results obtained by the different searches, which exploit very different experimental signatures and thus are affected by different backgrounds and related systematic uncertainties. By combining all searches, the expected sensitivity is improved by about a factor of two relative to the most sensitive individual results.”

- Concerning my question of the BDT, I agree with the authors that the final score of the BDT is well modelled. I disagree on their statement that BDT training is better when no cut on the quantities is applied. This is true when the input features and the correlations among them are correctly modelled. Here, we might have a hint of the opposite and the fact that the score distribution looks safe is not sufficient to make a statement in general. First of all, we are looking at an integrated projection across the full dataset, that could hide the effect. Or, it could just be that the incorrectly modelled feature has small impact/discrimination power (in which case, why was it added to start with?). To solve this point, I ask the authors to select the events in the [40, 80] slice of the feature under discussion and make a plot of the BDT score for data and Monte Carlo events.

----> As indicated in the previous set of replies, the discrepancy in the low mττ region was also observed in the dedicated control region for the fake τhad background (see attached Figs. 1a and 1b). The difference observed in this control region was assigned as a systematic uncertainty to the fake τhad background in the signal region. Since the incorrectly modelled feature affects a small fraction of the total number of events (<10%), is far from where the signal is expected, and a systematic uncertainty was assigned, we decided not to exclude those events from the analysis. Ultimately, the mismodeled events are expected to have a negligible impact on the result. This is demonstrated in the attached Figs. 2a and 2b which, as requested by the referee, display the BDT score of the subset of events with mττ<80 GeV. As it can be appreciated, they are all concentrated in the first bin of the BDT, where they represent ~20% of the total number of events in that bin. Since the discrepancy for this subset amounts to 30-40%, the total effect on the bin content is at the level of 6-8%, well within the assigned systematic uncertainty (see Figs. 10a and 10b in the paper).

To conclude, we would like to repeat again the statements made in the first reply:
“ As shown in Fig. 10, the BDT output distribution is well modeled both before and after the fit. Also, as indicated in Sect. 9, one of the tests performed was to verify that the fit is able to correctly determine the strength of a simulated signal injected into the real data. Therefore, no significant bias was expected nor observed. Since a possible bias due to this mismodelling is well under control there was no reason to apply a cut on the variable. “

Figure 1: The distributions of mττ in the fake τhad control regions comparing data to the background prediction (denoted nOS). (a) ττ, 3j channel. (b) ττ, 4j channel.

Figure 2: The distributions of BDT score for events with mττ<80 GeV, comparing data to the background prediction. (a) ττ, 3j channel. (b) ττ, 4j channel. Only statistical uncertainties in the background prediction are displayed.

- I raised a point about page 29 and the use of ”dominated by statistics” for the result. Now that the authors confirm that what they mean is that the uncertainty (not the result) is dominated by statistics, I would ask them to rephrase the sentence to make it clear while avoiding to use ”statistics dominated result” which is jargon. The word ”uncertainty” should appear somewhere. This is more to help non expert readers. I was giving for granted that the authors were going to change the text after my question. I should have been more explicit.

----> You are correct, it should have been changed. The 1st sentence in Sect. 10.3 has been rephrased to:

“Since all searches, with the exception of the $\Hbb$ search, are dominated by the data statistical uncertainty,...”

### 2019-04-18 resubmission2/referee-replies.txt

@@
 to assess the overall consistency of the results obtained, as well as to improve the sensitivity through their combination.
-By combining all searches, the expected sensitivity is improved by about a factor of two relative to the most sensitive published individual searches.”  Leaving aside the improvement in sensitivity through the combination, the consistency check is important since the different searches have very different experimental signatures, and thus are affected by different backgrounds and systematic uncertainties.
-If a significant deviation is seen in one of the searches, one would like to know whether it’s also seen in the other searches, to determine its consistency with a FCNC signal interpretation.
+By combining all searches, the expected sensitivity is improved by about a factor of two relative to the most sensitive published individual searches.”.
+The combined result reported in this paper is the most stringent limit available from the LHC to date, and thus we believe by itself already meets the JHEP standard.
+Leaving aside the improvement in sensitivity through the combination, the consistency check is important since the different searches have very different experimental signatures, and thus are affected by different backgrounds and systematic uncertainties.
+If a significant deviation is seen in one of the searches (again, this would be unrelated to the Higgs branching ratios, which are expected to be very SM-like), one would like to know whether it’s also seen in the other searches, to determine its consistency with a FCNC signal interpretation.
 To make this clearer, the following sentences were added at the end of Sect.

### 2019-04-18 sections/introduction.tex

@@
 $WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
-the SM. Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
+the SM.
+The simplifying assumption of SM-like Higgs boson branching ratios is motivated by the fact that measurements of the flavour-diagonal Higgs boson couplings by the ATLAS and CMS collaborations are in agreement with the SM prediction within about 10\%~\cite{Khachatryan:2016vau,Sirunyan:2018koj}.
+Furthermore, typical beyond-the-SM scenarios that predict significant enhancements to $\BR(t\to Hq)$, also predict modifications to the Higgs boson branching ratios at the few percent level or below, well beyond the current experimental precision.
+Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
 has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
@@
 Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
-These two searches are combined with previous ATLAS searches in the diphoton and multilepton final states using the same dataset~\cite{Aaboud:2017mfd,Aaboud:2018pob}, 
-and bounds are set on $\BR(t\to Hc)$ and $\BR(t\to Hu)$, as well as on the corresponding non-flavour-diagonal Yukawa couplings.
+These two searches are combined with previous ATLAS searches in the diphoton and multilepton final states using the same dataset~\cite{Aaboud:2017mfd,Aaboud:2018pob}, and bounds are set on $\BR(t\to Hc)$ and $\BR(t\to Hu)$, as well as on the corresponding non-flavour-diagonal Yukawa couplings.
+The combination is performed after verifying the overall consistency of the results obtained by the different searches, which exploit very different
+experimental signatures and thus are affected by different backgrounds and related systematic uncertainties. 
+By combining all searches, the expected sensitivity is improved by about a factor of two relative to the most sensitive individual results.

### 2021-06-03 sections/introduction.tex
update introduction

@@
 
-Following the observation of the Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
-the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties is underway.
-%looking for deviations from the Standard Model (SM) predictions.  
+It has been nearly a decade since the observation of Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
+the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties was conducted, by which no significant sign of deviation from Standard Model (SM) was observed until today.
+But there is still chance finding new physics with searches already attempted but with higher sensitivity.
 An interesting possibility is the presence of flavour-changing neutral-current (FCNC) interactions
@@
 ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
-In contrast, large enhancements of these branching ratios are possible in some scenario beyond the SM.
+In contrast, large enhancements of these branching ratios are possible in some scenarios beyond the SM.
 Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
@@
 Searches for $t \to Hq$ decays have been performed by the ATLAS and CMS collaborations, taking advantage of the large samples
-of top-quark pair ($\ttbar$) events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{Aaboud:2017mfd,Aaboud:2018pob,Sirunyan:2017uae} using early Run~2 data.
+of top-quark pair ($\ttbar$) events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{fcnc36} using early Run~2 data.
 In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{ 
@@
 Finally, searches have also been performed exploiting the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
-of $\BR(H\to b\bar{b})\simeq 58\%$. Compared with Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, 
-as well as the larger integrated luminosity.
+of $\BR(H\to b\bar{b})\simeq 58\%$. Compared with Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
 Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of  
@@
 These upper limits are derived assuming that $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ if $\BR(t\to Hc)=0$.
+The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
+Combining all of the ATLAS searches using 36fb$^{-1}$ Run~2 data, the limits at 95\% CL are set for  $\BR(t\to Hc)<0.11\%$ and $\BR(t\to Hc)<0.12\%$ respectively assuming the other one is 0.
 The CMS Collaboration has performed a search using  
@@
 %The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
-The searches presented in this paper are focussed on fermionic decay modes of the Higgs boson. Therefore, they help to complete the 
-ATLAS experiment's programme of searches for $t \to Hq$ decays based on $pp$ collision
-%programme of searches for $t \to Hq$ decays of the ATLAS experiment based on $pp$ collision 
-data at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016. The corresponding integrated luminosity is 36.1 fb$^{-1}$.
-Two analyses are performed, searching for $\ttbar \to WbHq$ production (ignoring $pp \to tH$ production) and targeting the 
-$H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, which this paper refers to as ``$\Hbb$ search'' and ``$\Htautau$ search'', respectively.
-The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, several 
-of which are identified with high purity as originating from the hadronisation of $b$-quarks. 
-%The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
-The $\Htautau$ search selects events with two $\tau$-lepton candidates, at least one of which decays hadronically, as well as multiple jets.
-The latter requirement aims to select events with a hadronically decaying $W$ boson, since this allows an improved reconstruction of the
-event kinematics.
+This paper is focussed on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
+The corresponding integrated luminosity is 139.6 fb$^{-1}$.
+Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted.
+Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) are selected for hadronic channels.
+Events with at least one \tauhad with an additional electron or muon are selected from leptonic channels, which exploits more regions compared to the search conducted using partial Run~2 data.
 
-%two of which originating from hadronic $W$ decays. 
-Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
-These two searches are combined with previous ATLAS searches in the diphoton and multilepton final states using the same dataset~\cite{Aaboud:2017mfd,Aaboud:2018pob}, and bounds are set on $\BR(t\to Hc)$ and $\BR(t\to Hu)$, as well as on the corresponding non-flavour-diagonal Yukawa couplings.
-The combination is performed after verifying the overall consistency of the results obtained by the different searches, which exploit very different
-experimental signatures and thus are affected by different backgrounds and related systematic uncertainties. 
-By combining all searches, the expected sensitivity is improved by about a factor of two relative to the most sensitive individual results.
+Multivariate technique is used to discriminate between the signal and the background on the basis of their different kinematics.
+
+The expected sensitivity is about a factor of two relative to the most sensitive results~\cite{fcnc36} up until now.

### 2021-06-03 generatePath.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+echo "\newcommand*{\FCNCFigures}{$FCNC_DIR/FCNCFigures}
+\newcommand*{\FCNCTables}{$FCNC_DIR/FCNCTables}
+\newcommand*{\FCNCAnalysis}{$FCNC_DIR/FCNCAnalysis}" > FCNCpaths.sty

### 2021-06-03 sections/introduction.tex
fix sentences

@@
 
-It has been nearly a decade since the observation of Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
-the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties was conducted, by which no significant sign of deviation from Standard Model (SM) was observed until today.
-But there is still chance finding new physics with searches already attempted but with higher sensitivity.
-An interesting possibility is the presence of flavour-changing neutral-current (FCNC) interactions
-between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$). Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl}, 
+Since the observation of Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
+the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties have been conducted for nearly a decade, by which no significant sign of deviation from Standard Model (SM) was observed until today.
+However there is still chance finding new physics with searches already attempted but with improved sensitivities.
+The presence of flavour-changing neutral-current (FCNC) interactions
+between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$) is still an active topic. Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl},
 %with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
@@
 %The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
-This paper is focussed on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
+This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
 The corresponding integrated luminosity is 139.6 fb$^{-1}$.
 Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted.
-Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) are selected for hadronic channels.
-Events with at least one \tauhad with an additional electron or muon are selected from leptonic channels, which exploits more regions compared to the search conducted using partial Run~2 data.
+Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected for hadronic channels.
+Events with at least one \tauhad with an additional electron or muon are selected from leptonic channels.
+More regions are exploited compared to the FCNC $\Htautau$ search conducted using partial Run~2 data.
 

### 2021-06-05 sections/data_presel.tex
update

@@
 
-Both searches are based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ with 25 ns bunch spacing collected in 2015 and 2016, corresponding to an integrated luminosity of $36.1~\ifb$.
+The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ with 25 ns bunch spacing collected from 2015 to 2018, corresponding to an integrated luminosity of $139.6~\ifb$.
 Only events recorded with a single-electron trigger, a single-muon trigger, or a di-$\tau$ trigger under stable beam conditions 
-and for which all detector subsystems were operational are considered.
+and for which all detector subsystems were operational are considered for signal regions.
+While the events recorded by di-lepton triggers fall into the control regions used for fake-tau background estimation.
 The number of $pp$ interactions per bunch crossing in this dataset ranges from about 8 to 45, with an average of 24.
-%The mean number of $pp$ interactions per bunch crossing in the dataset is 24.
 
-%Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
-%with higher-threshold triggers without isolation requirements to ensure maximum efficiency. 
-%For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
-%For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
-%along with triggers with a 60~\gev\ threshold and no isolation requirements, and with a 120 (140)~\gev\ threshold 
-%with looser identification criteria and no isolation requirements.
 Single-electron and single-muon triggers with low $\pt$ thresholds and lepton isolation requirements are combined in a logical OR 
 with higher-threshold triggers but with a looser identification criterion and without any isolation requirement.
-The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016), while for electrons the threshold is 24 (26)~\gev.
+The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016-2018), while for electrons the threshold is 24 (26)~\gev.
 %For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
 For di-$\tau$ triggers, the $\pt$ threshold of the leading (trailing) $\had$ candidate is 35 (25)~\gev.
-In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.
+Events satisfying the trigger selection are required to have at least one primary vertex candidate.
 
-Events selected by the $\Hbb$ search are recorded with a single-electron or single-muon trigger and 
-are required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger.  
-Furthermore, at least four jets are required, of which at least two must be $b$-tagged.
+The signal final state including an electron or muon or \lep are referred to as leptonic channel, otherwise hadronic channel.
 
-In the $\Htautau$ search, events are classified into $\lephad$ and $\hadhad$ channels depending on the 
-multiplicity of selected leptons. Events in the $\lephad$ channel are recorded with a single-electron or single-muon trigger 
-and are required to have exactly one selected electron or muon and at least one $\had$ candidate. 
-The selected electron or muon is required to match, with $\Delta R < 0.15$, the lepton reconstructed by the trigger 
-and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
-data-taking conditions). In addition, its electric charge is required to be of opposite sign to that of the leading $\had$ candidate.
-Events in the $\hadhad$ channel are recorded with a di-$\tau$ trigger, and are required to have at least two $\had$ candidates and 
-no selected electrons or muons. The two leading $\had$ candidates are required to have charges of opposite sign. 
-In addition, in both $\Htautau$ search channels, trigger matching for $\had$ candidates, at least three jets and exactly one $b$-tagged jet are required.
+The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger.
+Further requirement are defined targeting different signal decay mode:
+\begin{itemize}
+	\item $t_h\lephad$: Targeting $t(q)H\to bqq(q)\lephad$ decay mode.
+Exactly one additional $\had$ with charge opposite to the lepton is further required.
+At least 3 jets with exactly one $b$-tagged are required.
+	\item $t_l\hadhad$: Targeting $t(q)H\to bl\nu(q)\hadhad$ decay mode. At least two additional $\had$ with opposite charge are further required. At least 1 jet with exactly one $b$-tagged is required.
+	\item $t_l\had$: Targeting $t(q)H\to bl\nu(q)\hadhad$ decay mode when one of the \had fails the tau reconstruction or identificaiton so that there is only one reconstructed \had candidate.
+Exactly one additional $\had$ with charge same for the lepton is further required.
+At least 2 jets with exactly one $b$-tagged are required.
+\end{itemize}
+
+The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and trailing $\had$ matched to the $\had$'s reconstructed by the trigger.
+No selected electrons or muons is required.
+The two \had candidates are required to have charges of opposite sign.
 
@@
 %, which are in general different between both searches. 
-These requirements, which ensure a negligible overlap between the $\Hbb$ and $\Htautau$ searches,
-are referred to as the preselection and are summarised in Table~\ref{tab:preselection}.
+These requirements are referred to as the preselection and are summarised in Table~\ref{tab:preselection}.
 
@@
 \begin{table*}[t!]
-\caption{\small{Summary of preselection requirements for the $\Hbb$ and $\Htautau$ searches. 
+\caption{\small{Summary of preselection requirements. 
 The leading and trailing $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
 \begin{center}
-\begin{tabular}{l|c|cc}
+\begin{tabular}{c|ccc|c}
 \toprule\toprule
-\multicolumn{4}{c}{Preselection requirements} \\      
+\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multirow{2}{*}{hadronic channel} \\ 
+& $t_h\lephad$ & $t_l\hadhad$ &  $t_l\had$ & \\
 \midrule
-Requirement &  $\Hbb$ search & \multicolumn{2}{c}{$\Htautau$ search} \\      
-& & $\lephad$ channel & $\hadhad$ channel \\
-\midrule
-Trigger & single-lepton trigger & single-lepton trigger & di-$\tau$ trigger  \\
-Leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
-               & -- & $\geq$1 $\had$ & $\geq$2 $\had$ \\
-Electric charge ($q$) & -- & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
-Jets  &  $\geq$4 jets & $\geq$3 jets & $\geq$3 jets \\
-$b$-tagging & $\geq$2 $b$-tagged jets & =1 $b$-tagged jets & =1 $b$-tagged jets  \\
+Trigger & \multicolumn{3}{c|}{single-lepton trigger} & di-$\tau$ trigger  \\
+Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & no isolated $e$ or $\mu$ \\
+\had  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
+Electric charge ($q$) & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ & $q_\ell \times q_{\tau_{\mathrm{had,1}}} > 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
+Jets  &  $\geq$ 3 jets & $\geq$1 jets & $\geq$2 jets & $\geq$3 jets \\
+$b$-tagging & \multicolumn{3}{c|}{=1 $b$-tagged jets} & =1 $b$-tagged jets\\
 \bottomrule\bottomrule

### 2021-06-05 sections/objects.tex
update

@@
 ($1.37 < |\eta_{\textrm{cluster}}| < 1.52$) are excluded.
-In the $\Hbb$ ($\Htautau$) search, electron candidates are required to have $\pt>30~(15)~\gev$ and 
-$|\eta_{\textrm{cluster}}| < 2.47$, and to satisfy tight (medium) likelihood-based identification 
+Electron candidates are required to have $|\eta_{\textrm{cluster}}| < 2.47$, and to satisfy tight likelihood-based identification 
 criteria~\cite{ATLAS-CONF-2016-024} based on calorimeter, tracking and combined variables that provide 
@@
 the resulting muon candidates are re-fitted using the complete track information from both detector systems.
-In the $\Hbb$ ($\Htautau$) search, muon candidates are required to have $\pt>30~(10)~\gev$ and $|\eta|<2.5$ 
-and to satisfy medium identification criteria~\cite{Aad:2016jkr}.
+Muon candidates are required to satisfy medium identification criteria~\cite{Aad:2016jkr}.
 
@@
 and by requiring that their longitudinal impact parameter, $z_0$, satisfies $|z_0 \sin\theta|<0.5$~mm.
+To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have \pt 1~GeV above the threshold.
 To further reduce the background from non-prompt leptons, photon conversions and hadrons, lepton candidates are also required to be isolated 
 in the tracker and in the calorimeter.
-A track-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$, where
-the scalar sum includes all tracks (excluding the lepton candidate itself) within the cone defined by $\Delta R<R_{\textrm{cut}}$ around the %axis
-direction of the lepton.  The value of $R_{\textrm{cut}}$ is the smaller of $r_{\textrm{min}}$ and $10~\gev/\pt^\ell$, where
-$r_{\textrm{min}}$ is set to 0.2 (0.3) for electron (muon) candidates, and $\pt^\ell$ is the lepton $\pt$. 
-The $\Hbb$ search requires lepton candidates to satisfy $I_R/\pt^\ell < 0.06$, while the $\Htautau$ search 
-makes $\pt$-dependent requirements on $I_R/\pt^\ell$. Additionally, the $\Htautau$ search requires leptons to
-satisfy a calorimeter-based isolation criterion: the sum of the transverse energy within a cone of size
-$\Delta R<0.2$ around the lepton, after subtracting the contributions
-from pile-up and the energy deposit of the lepton itself, is required to be less than a $\pt$-dependent 
-fraction of the lepton energy. 
+A track-based lepton isolation criterion is defined by calculating the quantity $p_R = \sum \pt^{\textrm{trk}}$ and $E_R = \sum E^{\textrm{clst}}$, where
+the scalar sum includes all tracks and energy deposit (excluding the lepton candidate itself) within the cone defined by $\Delta R<0.2 (0.3)$ around the %axis
+direction of the electron (muon). The electron (muon) candidates are required satisfy both $I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$.
 %Additionally, the $\Htautau$ search requires leptons to
@@
 The reconstructed jets are then calibrated to the particle level by the application of a jet energy scale 
-derived from simulation and in situ corrections based on $\sqrt{s}=13~\tev$ data~\cite{Aaboud:2017jcu}.
-The calibrated jets used in the $\Hbb$ search are required to have $\pt > 25~\gev$ and $|\eta| < 2.5$,
-while the $\Htautau$ search uses jets with $\pt > 30~\gev$ and $|\eta| < 4.5$.
+derived from simulation and in situ corrections based on $\sqrt{s}=13~\tev$ data~\cite{Aaboud:2017jcu}. (TBD: check PFlow jets description)
+The calibrated jets used are required to have $\pt > 25~\gev$ and $|\eta| < 2.5$.
 Jet four-momenta are corrected for pile-up effects using the jet-area method~\cite{Cacciari:2008gn}.
@@
 or detector noise~\cite{ATLAS-CONF-2015-029}.  To reduce the contamination due to jets originating from pile-up interactions,
-additional requirements are imposed on the jet vertex tagger (JVT)~\cite{Aad:2015ina} output for jets with $\pt<60~\gev$ and $|\eta| < 2.4$,
-or on the forward JVT~\cite{Aaboud:2017pou} output for jets with $\pt<50~\gev$ and $|\eta| > 2.5$.
+additional requirements are imposed on the jet vertex tagger (JVT)~\cite{Aad:2015ina} output for jets with $\pt<60~\gev$ and $|\eta| < 2.4$.
 
@@
 of secondary and tertiary decay vertices reconstructed within the jet. For each jet, a value for the multivariate $b$-tagging discriminant is 
-calculated. In the $\Htautau$ search, a jet is considered $b$-tagged if this value is above the threshold corresponding to
+calculated. A jet is considered $b$-tagged if this value is above the threshold corresponding to
 an average 70\% efficiency to tag a $b$-quark jet, with a light-jet\footnote{Light-jet refers to a jet originating from the hadronisation of a light quark 
 ($u$, $d$, $s$) or a gluon.} rejection factor of about 380 and a charm-jet rejection factor of about 12, as determined for jets with
-$\pt >20~\gev$ and $|\eta|<2.5$ in simulated $\ttbar$ events. In contrast, the $\Hbb$ search employs a tighter $b$-tagging requirement, 
-corresponding to an average efficiency of 60\% to tag a $b$-quark jet, and light-jet and charm-jet rejection factors of about 1500 and 34, respectively.
+$\pt >20~\gev$ and $|\eta|<2.5$ in simulated $\ttbar$ events.  (TBD: check DL1r description)
 
@@
 associated inner-detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
-with a total charge of $\pm 1$. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
-A boosted decision tree (BDT) discriminant~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject
-jet backgrounds. Three working points labelled loose, medium and tight are defined, and correspond to different $\had$ identification efficiency 
-values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
+with a total charge of $\pm 1$. Candidates are required to have \pt 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
+A Recurrent Neural Network (RNN) ~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} (citation to be changed) using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject jet backgrounds.
+Three working points labelled loose, medium and tight are defined, and correspond to different $\had$ identification efficiency values, with the efficiency designed to be independent of $\pt$.
+The $\Htautau$ search uses the medium
 working point for the nominal selection, while the loose working point is used for background estimation.
@@
 Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
-Any $\had$ candidate that is also $b$-tagged is rejected.
+Any $\had$ candidate that is also $b$-tagged is rejected. (TBD: check RNN description and update then numbers)
 
@@
 
-Overlaps between reconstructed objects are removed sequentially. In the $\Hbb$ search, firstly, electron candidates that lie 
+Overlaps between reconstructed objects are removed sequentially. Firstly, electron candidates that lie 
 within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
@@
 if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
-The overlap removal procedure in the $\Htautau$ search is similar to that of the $\Hbb$ search, except that the
-first step is the removal of $\had$ candidates within $\Delta R=0.2$ of electrons or muons, and the last step is the
-removal of jets whose axis lies within $\Delta R=0.2$ of the leading (highest-$\pt$) $\had$ candidate or the two leading $\had$ candidates (depending on the
-search channel). In addition, the muon--jet overlap removal is slightly different:
-if a muon lies within $\Delta R = 0.2$ of the axis of a jet, the jet is removed if either it has fewer than three tracks originating from the 
-primary vertex or it has a small $\pt$ compared with that of the muon (the $\pt$ of the jet is less than 50\% of the $\pt$ of the muon,
-or the scalar sum of the $\pt$ of the tracks associated with the jet is less than 70\% of the $\pt$ of the muon).
 

### 2021-06-05 sections/signal_background_modeling.tex
update

@@
 The background prediction is further improved during the statistical analysis by performing a likelihood 
-fit to data using several signal-depleted analysis regions, as discussed in Sections~\ref{sec:strategy_Hbb} and~\ref{sec:strategy_Htautau}.
+fit to data using several signal-depleted analysis regions, as discussed in Sections~\ref{sec:strategy_Htautau}.
 
@@
 terms~\cite{Cacciari:2011hy,Baernreuther:2012ws,Czakon:2012zr,Czakon:2012pz,Czakon:2013goa}.
-%and using the MSTW 2008 NNLO~\cite{Martin:2009iq,Martin:2009bu} PDF set. 
-%The theoretical uncertainties result from variations of the factorisation and renormalisation scales, as well as from uncertainties in the
-%top quark mass, and in the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution to the overall theoretical uncertainty 
-%in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
-%with the MSTW 2008 68\% CL NNLO, CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3 5F FFN~\cite{Ball:2012cx} PDF sets.
-
-%The $\Hbb$ search requires a more sophisticated treatment of the $\ttbar$ background. 
-The $\ttbar$ background selected by the $\Hbb$ search is enriched in $\ttbar$+heavy-flavour production, and thus requires a more sophisticated 
-treatment than provided by the nominal $\ttbar$ sample; this treatment is briefly outlined below. A detailed discussion can be found in Ref.~\cite{Aaboud:2017rss}.
-%The large and complex $\ttbar$ background selected by the $\Hbb$ search requires a more sophisticated treatment than provided by the nominal $\ttbar$ sample. 
-The simulated $\ttbar$ events are categorised depending 
-on the flavour content of additional particle jets not originating from the decay of the $\ttbar$ system.
-Events labelled as either \ttbin\ or \ttcin\ are generically referred to in the following as $\ttbar$+HF events, where HF stands for heavy flavour.
-The remaining events are labelled as $\ttbar$+light-jets events, including those with no additional jets. 
-A finer categorisation of \ttbin\ events is considered for the purpose of applying further corrections and
-assigning systematic uncertainties associated with the modelling of heavy-flavour production in different event topologies~\cite{Aaboud:2017rss}.
-In particular, the \ttbin\ events are reweighted to an NLO prediction in the four-flavour (4F) scheme 
-of \ttbin\ production including parton showering~\cite{Cascioli:2013era}, based on {\ShOLlong}~\cite{Gleisberg:2008ta, Cascioli:2011va} (referred to as {\ShOL} 
-in the following) using the CT10 4F PDF set.  This reweighting is performed in such a way that the inter-normalisations of the \ttbin\ categories are at NLO accuracy, 
-while preserving the \ttbin\ cross section of the nominal $\ttbar$ sample. 
-%This reweighting is applied to the alternative $\ttbar$ samples as well.
-This reweighting is also applied to the alternative $\ttbar$ samples that are used to study systematic uncertainties.
 
@@
 the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.
-%Raitio:1978pt,Beenakker:2002nc,Dawson:2003zu,Yu:2014cka,Frixione:2015zaa}.
-
-%The production of four-top-quark events in the SM was simulated by samples generated at LO using {\amcatnlo}~2.2.2
-%and the NNPDF2.3 LO PDF set, interfaced to {\pythia}~8.186 in combination with the A14 tune. 
-%The sample was normalised to a cross section of 9.2 fb, computed at NLO~\cite{Alwall:2014hca}.
 
@@
 \subsubsection{Fake electrons and muons}
-In the $\Hbb$ search, the background from multijet production (multijet background in the following) contributes to the selected 
-data sample via several production and misreconstruction mechanisms.  
-In the electron channel, it consists of non-prompt electrons (from semileptonic $b$- or $c$-hadron decays) as well as 
-misidentified photons (from a conversion of a photon into an $e^+e^-$ pair) or jets with a high fraction of 
-their energy deposited in the EM calorimeter.  In the muon channel, the multijet background originates mainly from 
-non-prompt muons.  The multijet background normalisation and shape are estimated directly from data by using the matrix method
-technique~\cite{Aad:2010ey,ATLAS-CONF-2014-058}, which exploits differences in lepton identification and isolation properties between 
-prompt leptons and leptons that are either non-prompt or result from the misidentification of photons or jets. 
-% Further details can be found in Ref.~\cite{Aaboud:2018mjh}.
+Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one \had.
+Since the fake rate of \had candidate is much larger than electron or muon.
+So in the majority of the fake lepton events, the \had candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies.
+However the multi-jet background has large event rate and can contribute with both electron or muon and \had faked to $t_l\had$ where the fake-lepton dominates and the jet multiplicity is low.
+This kind of event is modelled by ABCD method widely used in ATLAS physics analyses.
 
@@
 \label{sec:faketaus}
-In the $\Htautau$ search, the background with one or more fake $\had$ candidates mainly arises from $\ttbar$ or
-multijet production, depending on the search channel, with $W$+jets production contributing to a lesser extent. 
+The background with one or more fake $\had$ candidates mainly arises from $\ttbar$ or
+multijet production, depending on the search channel. 
 Studies based on the simulation show that, for all the above processes, fake $\had$ candidates primarily result from the 
@@
 
-This background is estimated directly from data by defining control regions (CR) enriched in fake $\had$ candidates via loosened $\had$ requirements or flipped charge.
+In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$ candidates via loosened $\had$ requirements and partially from monte carlo.
 These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
-The CR selection requirements are analogous to those used to define the different SRs, except that the leading (trailing) $\had$ candidate
-in the $\lephad$ ($\hadhad$) channel is required to fail the medium $\had$ identification but pass the loose identification, or the two $\had$ candidates have the same charge.
+The CR selection requirements are analogous to those used to define the different SRs, except that the trailing $\had$ candidate is required to fail the medium $\had$ identification.
 
@@
 During the statistical analysis, the normalisation of the fake $\had$ background in each SR is allowed to vary freely in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.
-
-%In the $\Htautau$ search, the background events with real tau leptons are modelled by MC samples, including $t\bar{t}$, $t\bar{t}+H/V$, single top events with real taus, and $Z\to\tau\tau$+jets.
-The $Z\to ee,\mu\mu$ processes are included for lepton faking tau background.
-They are small compared to the other background components.
-The fake-tau background with one or more taus faked by jets consists of the top fake (with at least one fake tau from jets in the top events), QCD multijet and $W$+jets events.
-This background is estimated in a dedicated control region (fake-tau CR), which is shown in Fig.
-\ref{fig:region-definition}.
-The events in the fake-tau CR are required to pass mostly the same selection as fit region (FR, the region after the preselection and the cut in Eq.
-\ref{eq:chi2-3jet}; the tau candidates in FR are also required to have the same charge) except for the tau charge and identification requirement.
-The fake-tau CR consists of two kinds of events: 1.
-The $\tauhad$'s have medium ID and the tau candidates have the same charge; 2.
-The leading (sub-leading) $\tauhad$ in $\lephad$ ($\hadhad$) channel has loose ID but fails medium ID requirement and there is no charge requirement.
-So the fake-tau CR is orthogonal to the FR and dominated by fake $\tauhad$'s.
-%
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.45\textwidth]{figures/Htautau/fakes/fake-tau-control-region.eps}
-%\includegraphics[width=0.45\textwidth]{figures/Htautau/fakes/VR.eps}
-%
-%\caption{ The composition of the FR, fake-tau CR, and corresponding VRs defined for the analysis.
-The ``Loose'', ``Medium'', ``very loose'' are leading (sub-leading) tau ID in $\lephad$ ($\hadhad$) channel.
-OS and SS represent the charge requirements of the tau candidates, OS for opposite sign, SS for same sign.}
-%\label{fig:region-definition}
-%\end{figure}
-%
-%In the fake-tau CR, the MC contaminations from $Z$+jets, diboson, top events ($\ttbar$, single top, $\ttbar+H/V$) with two real taus are subtracted, with only the QCD, $W$+jets and top fake events left.
-%The fake taus are those $\tauhad$ candidates which cannot be matched to any real taus in the MC truth.
-%
-%In the $\lephad$ channel, the top fake is the dominant fake background, and the fractions of top fake in FR and fake-tau CR are consistent with those in FR VR and fake-tau VR.
-The same is true for the fractions of $W$+jets in FR and fake-tau CR.
-Therefore, after the subtraction, the events in fake-tau CR are transferred to FR with a transfer factor, which is defined as
-%
-%\begin{equation}
-%f_{\text{trans}} = \frac{N_{\text{data}}^{\text{FR}} - N_{\text{non-fake}}^{\text{FR}}}{N_{\text{fake}}^{\text{fake-tau-CR}}},
-%\label{eq:transfer-factor}
-%\end{equation}
-%
-%where $N_{\text{data}}^{\text{FR}}$ and $N_{\text{non-fake}}^{\text{FR}}$ are total event yields of data and non-fake MC background in FR, $N_{\text{fake}}^{\text{fake-tau-CR}}$ is the fake events from fake-tau CR, which is data-driven.
-Eq.
-\ref{eq:transfer-factor} gives a pre-fit normalization of the fake events to demonstrate the agreement of the data and total background prediction.
-After the fit, $f_{\text{trans}}$ will be modified by a new multiplicative factor (freely floating in the fit) replacting the final normalization of the fake.
-The fit untilizes the different distribution shapes of signal and background, as well as the background-enriched region in FR to determine the fake normalization.
-%  
-%In the $\hadhad$ channel, regarding that the QCD events have a considerable contribution to the fake-tau background and there is no guarentee that the fractions of top-fake-tau event in FR and fake-tau CR are the same.
-So a small amount of MC top-fake-tau events in fake-tau CR are added to the data-driven estimate to make them equal.
-The fractions of top-fake-tau events in both regions are simply computed by MC prediction.
-As a result, the fraction is also considered to have a systematic uncertainty (1-$\sigma$ deviation is around 30\%, which is measured in another top-enriched control region).
-So the transfer factor in the $\hadhad$ channel becomes:
-%
-%\begin{equation}
-%f_{\text{trans}} = \frac{N_{\text{data}}^{\text{FR}} - N_{\text{non-fake}}^{\text{FR}}}{N_{\text{fake}}^{\text{fake-tau-CR}} + \epsilon N_{\text{topFake}}^{\text{fake-tau-CR}}},
-%\label{eq:transfer-factor-hadhad}
-%\end{equation}
-%
-%where $N_{\text{topFake}}^{\text{fake-tau CR}}$ is the top-fake-tau MC yield in fake-tau CR, and $\epsilon$ is a scaling factor that makes the top fake fractions equal in fake-tau CR and FR.
-%
-%To check if the shape of the BDT discriminant of the fake-tau events in fake-tau CR and in the FR agree with each other, independent FR and fake-tau CR validation regions (VR, as shown in Fig.
-\ref{fig:region-definition}) are defined.
-The VRs are basically the same as the nominal regions, except that
-%
-%\begin{itemize}
-%\item The ``medium'' is downgraded to ``loose'', and ``loose'' downgraded to ``veryLoose'' for the subleading tau ID.
-%\item In $\hadhad$, the ID of the leading $\tauhad$ is downgraded from ``medium'' to ``loose'' as well, in order to suppress the signal contamination.
-%\end{itemize}
-%
-%The VRs are depleted of signals\footnote{The signal contamination is about $0.02\%$ and $0.15\%$ in the $\lephad$ 4-jet and $\hadhad$ 4-jet VRs, respectively, if assuming BR($t\to Hq$)=$1\%$.}, and the shape difference of the BDT discriminant of the fake-tau events between the FR VR and fake-tau VR (after subtracting on-fake MC backgrounds) are treated as one of the systematic uncertainty for the data-driven fake estimate.
-%
-%The different fractions of top fake, QCD and $W$+jets in fake-tau CR and FR can induce systematics in the fake estimation.
-In the $\lephad$ channel, relatively higher top fake fraction is seen in the FR than in the fake-tau CR.
-However, the top fake fractions in the FR and the FR VR are consistent with each other, and the same is true for the fractions in the fake-tau CR and the fake-tau VR.
-So the top fake fraction systematics is also covered by the VR samples comparisons.

### 2021-06-08 sections/signal_background_modeling.tex
first draft version

@@
 So in the majority of the fake lepton events, the \had candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies.
-However the multi-jet background has large event rate and can contribute with both electron or muon and \had faked to $t_l\had$ where the fake-lepton dominates and the jet multiplicity is low.
+However the multi-jet background has large event rate and can contribute with both electron or muon and \had faked, espcially to $t_l\had$ where the fake-lepton dominates and the jet multiplicity is low.
 This kind of event is modelled by ABCD method widely used in ATLAS physics analyses.
@@
 
-In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$ candidates via loosened $\had$ requirements and partially from monte carlo.
+In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$ candidates via loosened $\had$ requirements with proper fake factors and partially from monte carlo.
 These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
@@
 
-The fake $\had$ background prediction in a given SR is modelled by the distribution (referred to as the fake $\had$ template) derived from data in the corresponding CR.
-The fake $\had$ template is defined as the data distribution from which the contributions from the simulated backgrounds with real $\had$ candidates, originating primarily from
-$W(\to \tau\nu)$+jets and $Z(\to \tau\tau)$+jets, are subtracted.
-In the $\lephad$ channel, simulation studies indicate that the fake $\had$ background composition is consistent between the SR and the CR, and dominated by $\ttbar$ production.
-In the $\hadhad$ channel, the fake $\had$ background is expected to be dominated by multijet production.
-However, simulation studies indicate that the contribution of $\ttbar$ events to the fake $\had$ background is higher in the SR than in the CR.
-Therefore, an appropriate number of simulated $\ttbar$ events with fake $\had$ candidates in the CR is added to the fake $\had$ template to match the fake $\had$ background composition in the SR.
-In both the $\lephad$ and $\hadhad$ channels, the fake $\had$ template in each SR is initially normalised to the estimated fake $\had$ background yield, 
-defined as the data yield minus the contributions from the simulated backgrounds with real $\had$ candidates (assuming no signal contribution).
-During the statistical analysis, the normalisation of the fake $\had$ background in each SR is allowed to vary freely in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.
+In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrated monte carlo.
+The calibration is done depending on different source of the fake taus and \pt.
+The calibration factor are derived in the dedicated control regions discussed in Section~\ref{sec:strategy_Htautau}.

### 2021-06-08 sections/statistical_analysis.tex
first draft version

@@
 
-For each search, the final discriminant distributions across all analysis regions considered are jointly analysed to test for the 
+The final discriminant distributions across all analysis regions considered are jointly analysed to test for the 
 presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
@@
 on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $\Hq$ signal events
-normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$,
+normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=0.2\%$,
 and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations. 
 Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
-All nuisance parameters are subject to Gaussian or log-normal constraints in the likelihood, with the exception of a few parameters 
-that control the normalisation of some background components (e.g.\ the \ttbin\ background in the case of the $\Hbb$ search), which 
-are treated as free parameters in the fit.
-
+All nuisance parameters are subject to Gaussian constraints in the likelihood.
 For a given value of $\mu$, the nuisance parameters $\theta$ allow variations of the expectations for signal and background

### 2021-06-08 sections/strategy_Htautau.tex
Implemented referee comments
update
first draft version

--- 2018-11-26 sections/strategy_Htautau.tex
@@
 %-------------------------------------------------------------------------------
-\section{Strategy for the $\Htautau$ search}
+\section{Analysis strategy}
 \label{sec:strategy_Htautau}
@@
 
-The analysis strategy adopted in the $\Htautau$ search closely follows that developed in Ref.~\cite{Chen:2015nta} and is summarised in this section.
+The analysis strategy adopted in the $\Htautau$ search follows that developed in Ref.~\cite{Chen:2015nta} but improved to apply to more signal regions.
 
@@
 
-In the $\Htautau$ search, the $\ttbar \to WbHq$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
-the Higgs boson and at least four jets, only one of which originates from a $b$-quark.
-%In the $\Htautau$ search, the final state signature of interest is characterised by the presence of two $\tau$-leptons from the
-%decay of the Higgs boson as well as a light-quark jet, the latter two originating from the decay of one of the top quarks. 
+The $Wb(q)H\to q\bar{q}b(q)\tau\tau$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
+the Higgs boson and at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
 If one of the $\tau$-leptons decays leptonically, an isolated electron or muon and significant $\met$ is also expected.
-%The other top quark decays into a $W$ boson and a $b$-quark, with the $W$ boson in turn decaying hadronically, resulting in 
-%three additional jets. Therefore, at least four jets are typically expected in signal events.
-However, in a significant fraction of the events the lowest-$\pt$ jet from the $W$ boson decay fails the minimum $\pt$ requirement of $30~\gev$,
-resulting in signal events with only three jets reconstructed.
+In a significant fraction of the events, the lowest-$\pt$ jet from the $W$ boson decay fails the minimum $\pt$ requirement of $30~\gev$,
+resulting in some decay mode signal events mixed with production mode having only three jets reconstructed.
 In order to optimise the sensitivity of the search, the selected events are categorised into four SRs depending 
-on the number of $\taulep$ and $\had$ candidates, and on the number of jets:
-($\lephad$, 3j), ($\lephad$, $\geq$4j), ($\hadhad$, 3j), and ($\hadhad$, $\geq$4j).
+on the number of $\taulep$ and $\had$ candidates, and on the number of light flavored jets:
+($t_h\lephad$, 2j), ($t_h\lephad$, $\geq$4j), ($t_h\hadhad$, 3j), and ($t_h\hadhad$, $\geq$4j).
 
@@
 is missing or not (events with exactly three jets or at least four jets).
-%This analysis adopts the event reconstruction strategy developed in Ref.~\cite{Chen:2015nta}, which is briefly summarised in the following. 
-%The event reconstruction strategy used~\cite{Chen:2015nta} is summarised in the following.
-The event reconstruction is based on the strategy used in Ref.~\cite{Chen:2015nta}.
+The event kinematic reconstruction is based on the strategy used in Ref.~\cite{Chen:2015nta}, and is summarised below.
 
-Events with exactly three jets that are compatible with having a fully reconstructed hadronically decaying 
-top quark ($t \to Wb \to qqb$) are rejected, as the $t \to Hq$ decay cannot be reconstructed due to the missing light-quark jet.
-This compatibility is assessed via a likelihood function that depends on the reconstructed mass of the three-jet 
-system and the two non-$b$-tagged jets.
-For the remaining events, the selected jets are assigned to the different top-quark decay products via a criterion based on 
-minimising a sum of angular distances between objects. Finally, the four-momenta of the invisible decay products for each $\tau$-lepton decay 
-are estimated by minimising a $\chi^2$ function based on the probability density functions for the angular distance of the visible and invisible
-products of the $\tau$-lepton decay, and including Gaussian constraints on the $\tau$-lepton mass, the Higgs boson mass and the
-measured $\met$. After the $\chi^2$ minimisation, the Higgs boson four-momentum, and hence its invariant mass, as well as the 
-four-momentum of the parent top quark, are determined with better resolution. Following the event kinematic reconstruction, several kinematic variables
-that discriminate between signal and background are defined. These variables are used in the multivariate analysis discussed in the next section.
+For the decay mode events, the selected jets are assigned to the different top-quark decay products via a criterion based on 
+minimising the angular distances between light flavor jets and the visible decay product of the Higgs boson (the two tau candidates).
 
-%To comply with the signal topology, in each event, exactly one jet should be tagged as a $b$-jet.
-If all jets from the top hadronic decay and the jet from $t\to Hq$, denoted as the FCNC jet, pass the jet selection, there should be at least four jets.
-However, some jets have a $\pt$ less than 30 GeV and may fail to pass the jet selection.
-The most likely missing jet is the subleading jet from the $W$ decay.
-These 3-jet events are still kept if the FCNC jet can be found and matched with the Higgs to reconstruct the top.
-It is done as follows.
-In the 3-jet events, if the three jets, denoted by $j_1$, $j_2$, $b$, satisfy
-%\begin{equation}
-%\chi_{Wb}^2 \equiv \left(\frac{m_{j_1 j_2}-80.4}{20}\right)^2 + \left(\frac{m_{j_1 j_2 b}-172.5}{25}\right)^2 <5,
-%\label{eq:chi2-3jet}
-%\end{equation}
-%where the mass is in GeV, the event is discarded. In these events, a good hadronic top is reconstructed, but the FCNC jet from the other top is missing.
-%
-%If Eq.~(\ref{eq:chi2-3jet}) is not satisfied, the FCNC jet is identified by the least sum of angular distances, $\Delta R_{3j}$, expressed as 
-%\begin{equation}
-%\Delta R_{3j} \equiv \Delta R(j_c ,H) + \Delta R(j_W ,b) \: ,
-%\label{eq:deltaR-3jet}
-%\end{equation}
-%where the $j_W$ denotes the jet from the $W$ decay, and the event is kept.
-%
-%For the events with at least four jets (denoted as 4-jet events), the three leading ones other than the $b$-jet are considered.
-Out of the three possible combinations that form the two sets of top decay products, the one with the least sum of angular distances, $\Delta R_{4j}$, is chosen, which is defined as
-%\begin{equation}
-%\Delta R_{4j} \equiv \Delta R(j_c ,H) + \Delta R(j_{1} ,b) + \Delta R(j_{2} ,b) + \Delta R(j_{1} ,j_{2}),
-%\label{eq:deltaR-4jet}
-%\end{equation}
-%where $j_{1,2}$ are the jets from the $W$ decay. No explicit $c$-tagging is used, and as can be seen above, the FCNC jet is found through pure kinematic criteria such as $\Delta R$.
-%
-%The method introduced in \cite{Chen:2015nta} is used to recontruct the ditau mass and momentum by taking the tau decay kinematics into account.
-To determine the 4-momenta of the invisible decay products of the tau decays, the following $\chi^2$ in Eq.~\ref{eq:tautau-chi2}, based on the probability functions above and the constraints from the tau mass, the Higgs mass and the measured $\met$, is defined,
-%\begin{eqnarray}
-%\begin{array}{ll}
-%\chi^2 = & -2\ln \mathcal{P}_1 -2\ln \mathcal{P}_2 + \left( \frac{m_{\tau_1}^{\text{fit}} - 1.78}{\sigma_{\tau}} \right)^2 +  \left( \frac{m_{\tau_2}^{\text{fit}} - 1.78}{\sigma_{\tau}} \right)^2 +  \left( \frac{m_{H}^{\text{fit}} - 125}{\sigma_{\text{Higgs}}} \right)^2 + \\
-% & \left( \frac{E_{x,\text{miss}}^{\text{fit}} - E_{x,\text{miss}}}{\sigma_{\text{miss}}} \right)^2 + \left( \frac{E_{y,\text{miss}}^{\text{fit}} - E_{y,\text{miss}}}{\sigma_{\text{miss}}} \right)^2 ,
-%\end{array}
-%\label{eq:tautau-chi2}
-%\end{eqnarray}
-%where $\mathcal{P}_i(\Delta R)$ are the probability distributions of the angular distance of the visible and invisible decay products in the tau decay, parametrized as a function of the momentum of the tau lepton.
-In the $\taulep$ mode where two neutrinos are present, it is extended to be the joint probability distribution of $\Delta R$ and $m_{\text{mis}}$ with $m_{\text{mis}}$ being the invariant mass of the neutrinos, denoted by $\mathcal{P}(\Delta R, m_{\text{mis}})$.
-These probability density functions are obtained from the MC simulation.
-%
-%In the Eq.
-\ref{eq:tautau-chi2}, the free parameters scanned are the 4-momentum components of the invisible decay products for each tau decay.
-In the $\tauhad$ mode, only three momentum components are scanned since a single neutrino is massless.
-$m_{\tau_{1,2}}^{\text{fit}}$,  $m_{H}^{\text{fit}}$ and $E_{xy,\text{miss}}^{\text{fit}}$ are the calculated tau mass, Higgs mass, and missing transverse energy with the scanned parameters.
-The corresponding mass resolutions, $\sigma_{\tau}$ and $\sigma_{\text{Higgs}}$, are set to 1.8~GeV and 20~GeV respectively.
-The $\met$ resolution is parametrized as
-%\begin{equation}
-%\sigma_{\text{miss}}=13.1 + 0.50\sqrt{\Sigma E_\text{T}},
-%\label{eq:sigma-missing-E}
-%\end{equation}
-%where $\Sigma E_\text{T}$ (in GeV) is the scalar sum of transverse energy depositions of all objects and clusters.
-The invisible 4-momenta are obtained by minimizing the combined $\chi^2$ for each event.
-By adding the Higgs mass constraint term in the kinematic fit, not only is the Higgs mass resolution improved, but also the resolutions of the Higgs boson's four-momentum, and the mass of the top from which the Higgs comes.
+Finally, the four-momenta of the invisible decay products for each $\tau$-lepton decay 
+are estimated from kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the the Higgs boson mass and the
+measured $\met$ within their expected resolutions.
+The resolution on the Higgs boson mass is taken to be $20~\gev$, respectively, while the resolution on the measured $\met$ is parameterised as a linear function of
+$\sqrt{\sum E_T}$, with $\sum E_T$ denoting the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
+After the $\chi^2$ minimisation, the Higgs boson four-momentum, and hence its invariant mass, as well as the 
+four-momentum of the parent top quark in the decay mode signal events, are determined with better resolution.
+
+Following the event kinematic reconstruction, several kinematic variables that discriminate between signal and background are defined.
+These variables are used in the multivariate analysis discussed in the next section.
+
+The $Wb(q)H\to l\nu b(q)\tau\tau$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown.
+The kinematics fit is no longer feasible.
+The variables calculated from the visible objects are directly used in the multivariate analysis.
 
@@
 \begin{table*}[t!]
-\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for each search region (denoted by $\times$). 
+\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for hadronic channel. 
 The description of each variable is provided in the text.}}
-\begin{center}
-\begin{tabular}{ccccc}
-\toprule\toprule 
-& \multicolumn{2}{c}{$\lephad$} & \multicolumn{2}{c}{$\hadhad$} \\
-Variable & 3j & $\geq$4j & 3j & $\geq$4j  \\
-\midrule
-$m_{\tau\tau}^{\text{fit}}$                      	& $\times$  & $\times$  & $\times$  & $\times$ \\
-$m_{Hq}$                                	& $\times$  & $\times$  & $\times$  & $\times$ \\
-$m_{\text{T,lep}}$                              	& $\times$  & $\times$  &             & \\
-$p_{\text{T,1}}$                             	& $\times$  & $\times$ & $\times$  & $\times$ \\
-$p_{\text{T,2}}$                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
-$\met$ $\phi$ centrality                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
-$E_{\text{T},\parallel}^{\text{miss}}$          	& $\times$  & $\times$  & $\times$  & $\times$ \\
-$E_{\text{T},\perp}^{\text{miss}}$          	& $\times$  & $\times$  &             & \\
-$m_{b j_1}$                   		        & $\times$  & $\times$  & $\times$  & $\times$ \\
-$m_{\text{lep}j}$      			        & $\times$  & $\times$  &   	  & \\
-$m_{\tau j}$      			        & $\times$  & $\times$  &   	  & \\
-$x_1^{\text{fit}}$				& $\times$  &	$\times$  & $\times$  & $\times$ \\
-$x_2^{\text{fit}}$				& $\times$  & $\times$  & $\times$  & $\times$ \\
-$m_{b j_1 j_2 }$             	   		&             & $\times$  &             & $\times$ \\ 
-%\hline
-\bottomrule\bottomrule
-\end{tabular}
-\label{tab:mva_var}
-\end{center}
+\input{\FCNCTables/Importance/xTFW/Merged}
+\end{table*}
+
+\begin{table*}[t!]
+\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for leptonic channel. 
+The description of each variable is provided in the text.}}
+\input{\FCNCTables/Importance/tthML/Merged}
 \end{table*}
@@
 %draft 1 version
-%In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
-%whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
-In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\had$ contributions), 
-elsewhere the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account.
+In the training, All signal events ($tuH$ and $tcH$ signal are merged with a ratio of 1:1) are used against the total SM background (including both real and fake $\had$ contributions).
 
-A large set of potential variables were investigated in each SR separately, and only those variables that led to better discrimination
-by the BDT were kept.  The BDT input variables in each SR are listed in Table~\ref{tab:mva_var} and defined in the following:
-
+A large set of potential variables were investigated in each SR separately.
+The discrimination of a given variable was quantified by the ``separation" and ``importance" measures provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 1\% were kept.
+The BDT input variables in each SR and their importance are listed in Table~\ref{tab:mva_var} and defined in the following:
 \begin{itemize}
-\item $m_{\tau\tau}^{\text{fit}}$: the invariant mass of the two $\tau$-lepton candidates after the reconstruction of the neutrinos, indicating the reconstructed Higgs boson mass.
-\item $m_{Hq}$: the invariant mass of the reconstructed Higgs boson and the associated light-quark jet in the $t \to Hq$ decay, corresponding to the reconstructed mass of the parent top quark.
-\item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\mpt$ in the $\lephad$ channel.
-\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\had$ candidate (referred to as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\had$ candidates (referred to as particles 1 and 2 respectively) in the $\hadhad$ channel.
-\item $\met$ $\phi$ centrality: a variable that quantifies the angular position of $\mpt$ relative to the visible $\tau$-lepton decay products in the transverse plane. It is defined as:
-\begin{equation*}
-\met\; \phi\; \mathrm{centrality} = \frac{\sin(\phi_\mathrm{miss}-\phi_1)+\sin(\phi_\mathrm{miss}-\phi_2)}{\sqrt{\sin^2(\phi_\mathrm{miss}-\phi_1)+\sin^2(\phi_\mathrm{miss}-\phi_2)}}
-\end{equation*}
-\noindent where $\phi_\mathrm{miss}$ denotes the azimuthal angle of $\mpt$, and $\phi_1$ and $\phi_2$ denote the azimuthal angles the two $\tau$-lepton candidates 
-(the lepton and $\had$ candidate in the $\lephad$ channel, or the leading and trailing $\had$ candidates in the $\hadhad$ channel), referred to as particles 1 and 2 respectively.
-%The transverse plane is transformed such that the directions of the $\tau$-lepton decay products are 
-%rthogonal, and that the smaller angle between the $\tau$-lepton decay products defines the positive quadrant of the transformed plane. 
-%The $\met$ $\phi$ centrality is defined as the sum of the $x$ and $y$ components of the $\mpt$ unit vector in this transformed plane.
-%\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
-%\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the transverse direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
-\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector, minus 
-the magnitude of the fitted $\mpt$ vector.
-\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector perpendicular to the fitted $\mpt$ vector.
-\item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically decaying $W$ boson.
-\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance to the $\lep$ candidate.
-\item $m_{\tau j}$: the invariant mass of the  $\had$ candidate and the jet that has the smallest angular distance to the $\had$ candidate.
-\item $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$: the momentum fractions carried by the visible decay products from the two $\tau$-lepton candidates 
-(whether $\taulep$ or $\had$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
-\item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$ boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark.
-This variable is only defined for events with at least four jets.
+\item $E^{T}_{miss}$ is the missing transverse momentum.
+\item $p_{T,\tau}$ is the transverse momentum of the leading tau candidate.
+\item $p_{T,sub-\tau}$ is the transverse momentum of the sub-leading tau candidate.
+\item $p_{T,l}$ is the transverse momentum of the leading lepton.
+\item $\chi^2$ is derived from kinematic fitting for the neutrinos.
+\item $m_{t,SM}$ is the invariant mass of the $b$-jet and the two jets from the $W$ decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
+This variable is only defined for the 4-jet $t_hH$ and $t_ht(qH)$ events.
+\item $m^{T}_{W}$ is the transverse mass calculated from the lepton and $\met$ in the leptonic channels, defined as
+\begin{equation}
+m^{T}_{W} = \sqrt{2 p_{\text{T,lep}} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\text{lep,miss}} \right)}.  
+\end{equation}
+\item $m_{\tau,\tau}$ is the invariant mass of the tau candidates and reconstructed neutrinos in $t_hH$ and $t_ht(qH)$ channels. 
+\item $m_{W}$ is the reconstructed invariant mass of the hadronic $W$ boson from SM top quark.
+\item $m_{t,FCNC}$ is the visible invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, FCNC-jet and reconstructed neutrinos.
+\item $m_{\tau\tau,vis}$ is the visible invariant mass of the di-tau candidates
+\item $p_{T,\tau\tau,vis}$ is the $\pt$ of the di-tau candidates.
+\item $m_{t,FCNC,vis}$ is the reconstructed visible mass of the FCNC-decaying top quark.
+\item $m_{t,SM,vis}$ is the invariant mass of the lepton and the b-jet, which reflects the visible SM top mass.
+\item $M(\tau\tau qjet,min)$ is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative of variable $m_{t,FCNC,vis}$.
+\item $M(wjet1,wjet2,min)$ is the invariant mass of two light-flavor jet, minimized by choosing different jets, reflects the invariant mass of the W candidate, an alternative of $m_{W}$.
+\item $E^{T}_{miss}$ centrality is a measure of how central the $\met$ lies between the two tau candidates in the transverse plane, and is defined as
+\begin{eqnarray}
+\begin{array}{l}
+\met~\text{centrality} = {(x+y)}/{\sqrt{x^2+y^2}}, \\
+\text{with}~x=\frac{\sin(\phi_{\text{miss}}-\phi_{\tau_1})}{\sin(\phi_{\tau_2}-\phi_{\tau_1})},  y=\frac{\sin(\phi_{\tau_2}-\phi_{\text{miss}})}{\sin(\phi_{\tau_2}-\phi_{\tau_1})} ,
+\end{array}
+\label{eq:eq3}
+\end{eqnarray}
+\item $E_{\nu,i}/E_{\tau,i},i=1,2$ is the momentum fraction carried by the visible decay products from the tau mother.
+It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section.
+For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state, which is evident in the excess around 1 in Figure \ref{fig:x12_fit}.
+\item $\Delta R(l+bjet,\tau\tau)$ is the angular distance between the lepton+b-jet and di-tau candidates.
+\item $\Delta R(l,bjet)$ is the angular distance between the lepton and b-jet.
+\item $\Delta R(\tau,bjet)$ is the angular distance between the tau and b-jet. If there are two taus in the event, the leading one is selected for the calculation.
+\item $\eta_{\tau,max}$ is the maximum $\eta$ value among the tau candidates.
+\item $\Delta R(l,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
+\item $\Delta R(\tau,qjet)$ is the angular distance between the tau and the reconstructed fcnc jet.
+\item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(l,\tau)$.
+\item $\Delta\phi(\tau\tau,P^{T}_{miss})$ is the azimuthal angle between the $\met$ and di-tau $\pt$.
 \end{itemize}
-
-Among these variables, the most discriminating are $m_{\tau\tau}^{\text{fit}}$, $p_{\text{T},2}$, $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$.
-A comparison between data and the predicted background for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:BDT_inputs_lephad} and~\ref{fig:BDT_inputs_hadhad}.
+A comparison between data and the predicted background for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_lhadhad}.
+The comparison between the data and predicted background after preselection for the distributions of two of the most
+discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
+The expected signal (dashed red) corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.
+The first and the last bins in the figures contain the underflow and overflow respectively.
+The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
+The hashed area represents the total uncertainty of the background.
 A good description of the data by the background model is observed in all cases.
-The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:BDT}.
+The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[t]
-\begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_4j_FR.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
-\caption{$\Htautau$ search: Comparison between the data and predicted background after preselection for the distributions of two of the most
-discriminating BDT input variables in the $\lephad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
-$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
-$p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
-The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
-a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
-$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
-The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
-added to the background prediction.
-The first and the last bins in all figures contain the underflow and overflow respectively.
-The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
-The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
-which is determined via a likelihood fit to data.}
-\label{fig:BDT_inputs_lephad}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{\FCNCFigures/tex/BDTinput}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[t]
-\begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_4j_FR.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_4j_FR.eps}} \\
-\caption{$\Htautau$ search: Comparison between the data and predicted background after preselection for the distributions of two of the most 
-discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit''). The distributions are shown for
-$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
-$x_{1}^{\text{fit}}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
-The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
-a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
-$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
-The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
-added to the background prediction.
-The first and the last bins in the figures in (a) and (b) contain the underflow and overflow respectively.
-The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
-The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the fake $\had$ background, 
-which is determined via a likelihood fit to data.} 
-\label{fig:BDT_inputs_hadhad}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[t]
-\begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl3j/canv_.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hl4j/canv_.eps}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh3j/canv_.eps}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/discriminant_shape/shape_discriminant_hh4j/canv_.eps}} \\
-\caption{$\Htautau$ search: Comparison of the distributions of the BDT discriminant after preselection of the $\Hc$ (red dashed) and $\Hu$ (blue dotted) signals, 
-and the total background (black solid) in the different search regions considered:
-(a) ($\lephad$, 3j), (b) ($\lephad$, $\geq$4j), (c) ($\hadhad$, 3j), and (d) ($\hadhad$, $\geq$4j). }
-\label{fig:BDT}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{\FCNCFigures/tex/BDT}

### 2021-06-08 sections/systematic_uncertainties.tex
first draft version

--- 2018-12-18 sections/systematic_uncertainties.tex
@@
 
-%Table~\ref{tab:SystSummary} presents a list of all systematic uncertainties considered in the analysis 
-%and indicates whether they are taken to be normalisation-only, or to affect both shape and normalisation.
-%
-%%%%%%%%%%%%%%%
-%\begin{table*}[htbp]
-%\centering
-%\begin{tabular}{lcc}
-%\toprule\toprule
-%Systematic uncertainty & Type  & Components \\
-%\midrule
-%\textbf{Luminosity}                  &  N & 1\\\midrule
-%\textbf{Reconstructed Objects}                 &   & \\
-%Electron                  & SN & 5 \\
-%Muon                      &  SN & 6 \\
-%Jet reconstruction      & SN & 1\\ 
-%Jet vertex fraction         & SN    & 1\\
-%Jet energy scale            & SN & 22\\
-%Jet energy resolution       & SN & 1\\
-%Missing transverse momentum  & SN & 2\\ 
-%$b$-tagging efficiency      & SN & 6\\
-%$c$-tagging efficiency      & SN & 4\\
-%Light-jet tagging efficiency    & SN & 12\\ 
-%High-\pt\ tagging   & SN & 1 \\ \midrule
-%\textbf{Background Model}                 &   & \\
-%$t\bar{t}$ cross section    &  N & 1\\
-%$t\bar{t}$ modelling: $\pt$ reweighting   & SN & 9\\
-%$t\bar{t}$ modelling: parton shower & SN & 3\\
-%$t\bar{t}$+HF: normalisation & N & 2 \\
-%$t\bar{t}$+$c\bar{c}$: $\pt$ reweighting  & SN & 2 \\
-%$t\bar{t}$+$c\bar{c}$: generator & SN & 4 \\
-%$t\bar{t}$+$b\bar{b}$: NLO shape & SN & 8 \\
-%$W$+jets normalisation      &  N & 3\\
-%$W$ $\pt$ reweighting     &  SN & 1\\
-%$Z$+jets normalisation      &  N & 3\\
-%$Z$ $\pt$ reweighting     &  SN & 1\\
-%Single top normalisation    &  N & 3\\
-%Single top model            &  SN & 1\\
-%Diboson normalisation  &  N & 3\\
-%$t\bar{t}V$ cross section   &  N & 1\\
-%$t\bar{t}V$ model           &  SN & 1\\ 
-%$t\bar{t}H$ cross section & N & 1 \\
-%$t\bar{t}H$ model       & SN & 2 \\ 
-%Multijet normalisation  &  N & 4\\ \midrule
-%\textbf{Signal Model}                 &   & \\
-%$t\bar{t}$ cross section    &  N & 1\\
-%Higgs boson branching ratios & N & 3 \\
-%$t\bar{t}$ modelling: $\pt$ reweighting   & SN & 9\\
-%$t\bar{t}$ modelling: $\pt$ reweighting non-closure  & N & 1\\
-%$t\bar{t}$ modelling: parton shower & N & 1\\
-%\bottomrule\bottomrule
-%\end{tabular}
-%\caption{\label{tab:SystSummary} List of systematic uncertainties considered. 
-%An ``N'' means that the uncertainty is taken as affecting only the normalisation for all relevant 
-%processes and channels, whereas ``SN'' means that the uncertainty is 
-%taken on both shape and normalisation.
-%Some of the systematic uncertainties are split into several components for a more
-%accurate treatment.}
-%\end{table*}
-%%%%%%%%%%%%%%%
-%
-%The leading sources of systematic uncertainty vary depending on the analysis channel considered, but they 
-%typically originate from $\ttbar$+jets modelling (including $\ttbar$+HF) and $b$-tagging. 
-%For example, the total systematic uncertainty  in the background normalisation in the (4 j, 4 b) channel, 
-%which dominates the sensitivity in the case of the $\Hc$ search, is approximately 20\%, 
-%with the largest contributions originating from $\ttbar$+HF normalisation, $b$-tagging efficiency, 
-%$c$-tagging efficiency, light-jet tagging efficiency and $\ttbar$ cross section.
-%However, as shown in section~\ref{sec:result}, the fit to data in the nine analysis channels allows the overall background 
-%uncertainty to be reduced significantly, to approximately 4.4\%. 
-%The reduced uncertainty results from the significant constraints provided by the data on some
-%systematic uncertainties, as well as the anti-correlations among sources of systematic uncertainty resulting
-%from the fit to the data.
-%The total systematic uncertainty in the $\Hc$ signal normalisation in the (4 j, 4 b) channel is approximately 17\%, 
-%with similar contributions from uncertainties related to $b$-tagging and overall signal modelling. After the fit,
-%this uncertainty is reduced to 7.8\%.
-%Table~\ref{tab:SystSummary_WbHc} presents a summary of the sys\-te\-ma\-tic uncertainties for the $\Hc$ 
-%search and their impact on the normalisation of the signal and the main backgrounds in the (4 j, 4 b) channel.
-%
-%The following sections describe each of the systematic uncertainties considered in the analyses. 
-%
-%\begin{table*}[htbp]
-%\centering
-%\begin{tabular}{l | c c c c  | c c c c}
-%\toprule\toprule
-% & \multicolumn{4}{c|}{Pre-fit} & \multicolumn{4}{c}{Post-fit} \\ 
-% &  $WbHc$ & $t\bar{t}$+LJ & $t\bar{t}+c\bar{c}$ & $t\bar{t}+b\bar{b}$ &  $WbHc$ & $t\bar{t}$+LJ & $t\bar{t}+c\bar{c}$ & $t\bar{t}+b\bar{b}$ \\
-%\midrule
-%Luminosity  & $\pm 2.8 $  & $\pm 2.8 $  & $\pm 2.8 $  & $\pm 2.8 $  & $\pm 2.6$ & $\pm 2.6 $  & $\pm 2.6 $  & $\pm 2.6 $ \\ 
-%Lepton efficiencies  & $\pm 1.5 $  & $\pm 1.5 $  & $\pm 1.5 $  & $\pm 1.5 $  & $\pm 1.5$ &  $\pm 1.5 $  & $\pm 1.5 $  & $\pm 1.5 $ \\ 
-%Jet energy scale  & $\pm 3.3 $  & $\pm 2.9 $  & $\pm 2.3 $  & $\pm 5.8 $  & $\pm 1.4$ &  $\pm 1.2 $  & $\pm 1.8 $  & $\pm 4.1 $ \\ 
-%Jet efficiencies  & $\pm 1.2 $  & --  & $\pm 1.9 $  & $\pm 1.7 $  & $\pm 0.9$ &  --  & $\pm 1.4 $  & $\pm 1.2 $ \\
-%Jet energy resolution  & --  & $\pm 1.2 $  & $\pm 2.8 $  & $\pm 2.9 $  & -- &  -- & $\pm 1.0 $  & $\pm 1.1 $ \\ 
-%$b$-tagging eff.  & $\pm 7.9 $  & $\pm 5.5 $  & $\pm 5.2 $  & $\pm 10 $  & $\pm 5.7$ & $\pm 3.9 $  & $\pm 3.7 $  & $\pm 6.6 $ \\ 
-%$c$-tagging eff.  & $\pm 7.0 $  & $\pm 6.6 $  & $\pm 13 $  & $\pm 3.5 $  & $\pm 6.3$ &  $\pm 6.0 $  & $\pm 11 $  & $\pm 3.2 $ \\ 
-%Light-jet tagging eff.  & $\pm 0.8 $  & $\pm 18 $  & $\pm 3.2 $  & $\pm 1.5 $  & $\pm 0.6$ &  $\pm 13 $  & $\pm 2.3 $  & $\pm 1.1 $ \\
-%$t\bar{t}$: reweighting  & $\pm 5.9 $  & $\pm 2.7 $  & $\pm 4.2 $  & --  & $\pm 3.8$ &  $\pm 1.9 $  & $\pm 2.3 $  & -- \\ 
-%$t\bar{t}$: parton shower  & $\pm 5.4 $  & $\pm 4.8 $  & $\pm 10 $  & $\pm 4.9 $  & $\pm 1.7$ &  $\pm 1.5 $  & $\pm 6.5 $  & $\pm 3.1 $ \\ 
-%$t\bar{t}$+HF: normalisation  & --  & --  & $\pm 50 $  & $\pm 50 $  & -- &  --  & $\pm 32 $  & $\pm 16 $ \\ 
-%$t\bar{t}$+HF: modelling  & --  & --  & --  & $\pm 7.7 $  & -- &  --  & --  & $\pm 7.4 $ \\ 
-%Signal modelling  & $\pm 6.9 $  & --  & --  & --  & $\pm 6.9$ &  --  & --  & -- \\ 
-%Theor. cross sections  & $\pm 6.2 $  & $\pm 6.2 $  & $\pm 6.2 $  & $\pm 6.2 $  & $\pm 3.9$ &  $\pm 3.9 $  & $\pm 3.9 $  & $\pm 3.9 $ \\ 
-%\midrule                                                                                                                                                                                               
-%Total   & $\pm 17 $  & $\pm 22 $  & $\pm 54 $  & $\pm 53 $  & $\pm 7.8$ &  $\pm 14 $  & $\pm 28 $  & $\pm 15 $ \\ 
-%\bottomrule\bottomrule
-%\end{tabular}
-%\caption{$\Hcbb$ search: summary of the systematic uncertainties considered in the (4 j, 4 b) 
-%channel and their impact (in \%) on the normalisation of the signal and the main backgrounds, before and after the fit to data.
-%The $\Hc$ signal and the $t\bar{t}$+light-jets background are denoted by ``$WbHc$''  and ``$t\bar{t}$+LJ'' respectively.
-%Only sources of systematic uncertainty resulting in a normalisation change of at least 0.5\% are displayed.
-%The total post-fit uncertainty can differ from the sum in quadrature of individual sources due to the 
-%anti-correlations between them resulting from the fit to the data.}
-%\label{tab:SystSummary_WbHc}
-%\end{table*}
-%%%%%%%%%%%
-
 \subsection{Luminosity}
@@
 
-The uncertainty in the integrated luminosity is 2.1\%, affecting the overall normalisation of all processes estimated from the simulation. 
-%It is derived, following a methodology similar to that detailed in Ref.~\cite{Aaboud:2016hhf}, 
-%from a calibration of the luminosity scale using $x$--$y$ beam-separation scans performed in August 2015 and May 2016.
+The uncertainty in the integrated luminosity is 1.7\%, affecting the overall normalisation of all processes estimated from the simulation. 
 It is derived, following a methodology similar to that detailed in Ref.~\cite{Aaboud:2016hhf}, and using the LUCID-2 detector 
@@
 \label{sec:syst_objects}
-
-%Uncertainties associated with electrons and muons arise from the trigger, reconstruction, identification, and isolation
-%efficiencies, as well as the lepton momentum scale and resolution. These are measured in data using 
-%$Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events~\cite{ATLAS-CONF-2016-024,Aad:2016jkr}. 
-%The combined effect of all these uncertainties results in an overall normalisation 
-%uncertainty in signal and background of approximately 1\%.
 
@@
 The light-jet efficiency is measured in a multijet data sample enriched in light-flavour jets~\cite{ATLAS-CONF-2018-006}.
-Since the $\ttbar$ sample used to measure the $c$-jet tagging efficiency overlaps with the analysis sample, the $\Hbb$ search uses
-instead the $W$+$c$-jet scale factors.  
-In the case of the $\Hbb$ ($\Htautau$) search, the uncertainties in these scale factors include 
-a total of 6 independent sources affecting $b$-jets, 1 (2) source(s) affecting $c$-jets, and 17 sources affecting light-jets. 
+The uncertainties in these scale factors include a total of 44 independent sources affecting $b$-jets, 19 source affecting $c$-jets, and 19 sources affecting light-jets. 
 These systematic uncertainties are taken as uncorrelated between $b$-jets, $c$-jets, and light-jets.
-An additional uncertainty is included due to the extrapolation of these corrections to jets 
-with $\pt$ beyond the kinematic reach of the data calibration samples used ($\pt>300~\gev$ for $b$- and $c$-jets, 
-and $\pt>750~\gev$ for light-jets); it is taken to be correlated among the three jet flavours. 
-%This uncertainty is evaluated in the simulation by comparing the tagging efficiencies while varying e.g.\ the fraction 
-%of tracks with shared hits in the silicon detectors or the fraction of fake tracks resulting from random combinations of hits, 
-%both of which typically increase at high $\pt$ due to growing track multiplicity and density of hits within the jet. 
-Finally, an uncertainty related to the application of $c$-jet scale factors to $\tau$-jets is considered,
-but has a negligible impact in these analyses.
 
@@
 merged with the {\sherpa} parton shower using the ME+PS@NLO prescription.
-%either {\amcatnlo}+{\pythiaeight} (in the case of the $\Htautau$ search) or
-%\textsc{Sherpa} (in the case of the $\Hbb$ search). 
+
 The uncertainty due to the choice of parton shower and hadronisation (PS \& Had) model is derived 
@@
 and using the Var3c downward variation of the A14 set~\cite{ATL-PHYS-PUB-2016-004}.
-
-In the case of the $\Hbb$ search, where the $\ttbar$+HF background plays a prominent role (see Fig.~\ref{fig:Hbb_Summary}), a more 
-detailed treatment of its associated systematic uncertainties is used. In particular, since several analysis 
-regions have a sufficiently large number of \ttbin\ background events, its normalisation is 
-determined in the fit to data.
-%, with no prior uncertainty assumed. 
-In the case of the \ttcin\ normalisation, an uncertainty of 50\% is assumed, as the fit to the data is unable 
-to precisely determine it, and the analysis has very limited sensitivity to this uncertainty.
-Since the diagrams that contribute to $\ttbar$+light-jets, \ttcin, and \ttbin\
-production are different, all above uncertainties in $\ttbar$+jets
-background modelling (NLO generator, PS \& Had, and radHi/radLow), except the uncertainty of the inclusive cross section, are
-considered to be uncorrelated among these processes.
-Additional uncertainties of the \ttbin\ background are considered associated with the NLO prediction from {\ShOL}, 
-which is used for reweighting the nominal {\powheg}+{\pythiaeight} prediction. 
-These include three different scale variations, a different shower-recoil model scheme, and 
-two alternative PDF sets (MSTW 2008 NLO and NNPDF2.3 NLO). Additional uncertainties are assessed for
-the contributions to the \ttbin\ background originating from multiple parton interactions.
-Finally, an additional uncertainty is assigned to the \ttbin\ background by comparing
-the predictions from {\powheg}+{\pythiaeight} and {\ShOL} 4F (5F vs 4F).
-In the derivation of the above uncertainties, the overall normalisations of the \ttcin\ and \ttbin\ backgrounds 
-at the particle level are fixed to the nominal prediction. In order to maintain the inclusive $\ttbar$ cross section, 
-the normalisation of the $\ttbar$+light-jets background at the particle level is adjusted accordingly.
-% Further details are available in Ref.~\cite{Aaboud:2017rss}.
 
@@
 
-Uncertainties of the data-driven multijet background in the $\Hbb$ search include
-contributions from the limited size of the data sample, particularly at high jet and $b$-tag multiplicities, as 
-well as from the uncertainty in the rate of fake leptons, estimated in 
-different control regions (e.g.\ selected with a upper requirement on either $\met$ or $\mtw$). 
-A combined normalisation uncertainty of 50\% due 
-to all these effects is assigned, which is taken as correlated across jet
-and $b$-tag multiplicity bins, but uncorrelated between electron and muon channels. 
-No explicit shape uncertainty is assigned since the large statistical uncertainties associated with
-the multijet background prediction, which are uncorrelated 
-between bins in the final discriminant distribution, effectively cover all possible shape uncertainties.
+The statistical uncertainties of the fake $\had$ background calibration in the leptonic channel is applied with uncorrelated uncertainties for different fake $\had$ source and different $\pt$ slices.
+The uncertainties of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both statistical fluctuation and the differences between signal regions.
 
-Uncertainties of the data-driven fake $\had$ background in the $\Htautau$ search are obtained by using additional signal-depleted regions.
-The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\had$ identification criteria, and thus referred to as ``loose SR''  and ``loose CR''.
-%The shape difference between the fake $\tauhad$ background prediction in each loose SR and its associated loose CR
-%is assigned as an uncertainty in the prediction in the nominal SR.
-%In each loose SR, the shape difference between the data and the fake $\tauhad$ background estimate based on its associated loose CR,
-%in both cases having subtracted the small contribution from real $\tauhad$ candidates based on the simulation, 
-%is applied as an uncertainty in the prediction in the nominal SR. 
-%In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty in the prediction in the nominal SR. 
-In each loose SR, after subtracting the small simulation-predicted contribution from real $\had$ candidates, 
-the relative difference in the shape of the distribution between the remaining data and the fake $\had$ background estimate based on its associated loose CR 
-is assigned as an uncertainty of the prediction in the nominal SR.
-In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\had$ candidate from the simulation that are added to the fake $\had$ template in the $\hadhad$ channel as part of the fake $\had$ background estimation procedure.
-This uncertainty, associated with the modelling of the fake $\had$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\had$ candidate.
-The same uncertainty is assigned to the selected signal events with fake $\had$ candidates.
-In addition, a systematic uncertainty is assigned to account for the different fractional composition of particles (various types of leptons and partons) producing the fake $\had$ candidates 
-between each SR and its corresponding CR in the $\ttbar$ simulation. 
-Finally, the normalisation of the fake $\had$ background in each SR is determined in the fit to data. 
-%In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template.
-The MC studies shows that non-H-to-tautau signal with fake taus can contribute to the $\lephad$ channel.
-So a 30\% uncertainty is  applied to these signal-faking-tau events.
+The uncertainties of the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.
 
@@
 Several normalisation and shape uncertainties are taken into account for the $\Hq$ signal.
-The uncertainty of the $\ttbar$ cross section also applies to the $\Hq$ signal and is taken to be the same as, 
-and fully correlated with, the uncertainty assigned to the $\ttbar \to WbWb$ background.
 Uncertainties of the Higgs boson branching ratios are taken into account
 following the recommendation in Ref.~\cite{deFlorian:2016spz}.
-%: $\pm 1.1\%$ ($\Delta\alpha_\textrm{S}$),  $\pm 1.4\%$ ($\Delta m_b$) and $\pm 0.8\%$ (theory).
-Additional uncertainties associated with the modelling of additional radiation, with the choice of NLO generator, and
-with the choice of parton shower and hadronisation model, are estimated from the comparison of the nominal
-and alternative $\ttbar \to WbWb$ background samples (discussed in Section~\ref{sec:syst_bkgmodeling}) and applied to $\Hq$ signal. 
-These modelling uncertainties are taken to be uncorrelated with those affecting the $\ttbar \to WbWb$ background.
+The uncertainty of ISR, FSR and PDF are treated correlatedly with $\ttbar$ samples.
+The parton shower uncertainties is estimated by comparing the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}.

### 2021-06-11 ANA-TOPQ-2019-17-PAPER-auxmat.tex
rename fcnc-paper to ANA-TOPQ-2019-17-PAPER

--- 2018-12-30 ANA-TOPQ-2017-07-PAPER-auxmat.tex
@@
 %-------------------------------------------------------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[htbp]
-\begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_lep0_pt.pdf}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_met.pdf}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_hthad.pdf}} 
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex2bex_mbb_mindR.pdf}} \\ 
-\caption{\small{$\Hbb$ search: Comparison between the data and predicted background for several kinematic 
-distributions in the (4j, 2b) region (prior to the application of the cut on the LH discriminant above 0.6) before  the fit to data (``Pre-Fit''). 
-The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
-the jets ($\hthad$), and (d) the invariant mass of the two $b$-tagged jets with lowest 
-$\Delta R$ separation ($\mbb$).
-The small contributions from $\ttbar V$, $\ttbar H$, single-top-quark, $W/Z$+jets, diboson, and multijet backgrounds are combined 
-into a single background source referred to as ``Non-$\ttbar$''. 
-The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
-added to the background prediction.
-The last bin in all figures contains the overflow.
-The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
-The blue triangles indicate points that are outside the vertical range of the figure. 
-The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
-which is determined via a likelihood fit to data.}}
-\label{fig:Hbb_extravars_4j2b}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure*}[htbp]
-%\begin{center}
-%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_lep0_pt.eps}}
-%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_met.eps}} \\
-%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_hthad.eps}} 
-%\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_mbb_mindR.eps}} \\ 
-%\caption{\small{$\Hbb$ search: Comparison between the data and predicted background for several kinematic 
-%distributions in the (4j, 3b) region before performing the fit to data (``Pre-Fit''). 
-%The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
-%the jets ($\hthad$), and (d) the invariant mass distribution of the two $b$-tagged jets with lowest 
-%$\Delta R$ separation ($\mbb$).
-%The small contributions from $\ttbar V$, $\ttbar H$, single-top-quark, $W/Z$+jets, diboson, and multijet backgrounds are combined 
-%into a single background source referred to as ``Non-$\ttbar$''. 
-%The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
-%added on top of the background prediction.
-%The last bin in all figures contains the overflow.
-%The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
-%The blue triangles indicate points that are outside the vertical range of the figure. 
-%The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
-%which is determined via a likelihood fit to data.}}
-%\label{fig:Hbb_extravars_4j3b}
-%\end{center}
-%\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[htbp]
-\begin{center}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_lep0_pt.pdf}}
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_met.pdf}} \\
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_hthad.pdf}} 
-\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep5jex3bex_mbb_mindR.pdf}} \\ 
-\caption{\small{$\Hbb$ search: Comparison between the data and predicted background for several kinematic 
-distributions in the (5j, 3b) region before the fit to data (``Pre-Fit''). 
-The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
-the jets ($\hthad$), and (d) the invariant mass of the two $b$-tagged jets with lowest 
-$\Delta R$ separation ($\mbb$).
-The small contributions from $\ttbar V$, $\ttbar H$, single-top-quark, $W/Z$+jets, diboson, and multijet backgrounds are combined 
-into a single background source referred to as ``Non-$\ttbar$''. 
-The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
-added to the background prediction.
-The last bin in all figures contains the overflow.
-The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
-The blue triangles indicate points that are outside the vertical range of the figure. 
-The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
-which is determined via a likelihood fit to data.}}
-\label{fig:Hbb_extravars_5j3b}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{center}
-\includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_bb.pdf} \\
-\caption{$\Hbb$ search: Ranking of the nuisance parameters included in the fit according to their impact on the measured signal strength $\mu$, in
-the case of the $\Hc$ search.
-Only the 10 most highly ranked parameters are shown. Nuisance parameters corresponding to MC statistical uncertainties are not included here. 
-The empty blue rectangles correspond to the pre-fit impact on $\mu$ and the filled blue ones to the post-fit impact on $\mu$, 
-both referring to the upper scale. The impact of each nuisance parameter, $\Delta\mu$, is computed by comparing the nominal best-fit value of $\mu$ 
-with the result of the fit when fixing the considered nuisance parameter to its best-fit value, $\hat{\theta}$, shifted by its pre-fit (post-fit) uncertainties 
-$\pm\Delta\theta$ ($\pm\Delta\hat{\theta}$). The black points show the pulls of the nuisance parameters relative to their nominal values, $\theta_{0}$. 
-These pulls and their relative post-fit errors, $\Delta\hat{\theta}/\Delta\theta$, refer to the lower scale.
-The parameter $\mathrm{k}(\ttbin)$ refers to the floating normalisation of the $\ttbin$ background, for which the pre-fit impact on $\mu$ is not defined, 
-and for which both $\theta_{0}$ and $\Delta\theta$ are set to 1.
-For experimental uncertainties that are decomposed into several independent sources, NP I corresponds to the first nuisance parameter, 
-ordered by its impact on $\mu$.} 
-\label{fig:ranking_bb}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[t]
-\begin{center}
 \includegraphics[width=0.90\textwidth]{figures/Combo/ranking/Ranking_tt.pdf} \\

### 2021-06-11 ANA-TOPQ-2019-17-PAPER-metadata.tex
rename fcnc-paper to ANA-TOPQ-2019-17-PAPER

--- 2018-11-16 ANA-TOPQ-2017-07-PAPER-metadata.tex
@@
 %\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
-\AtlasTitle{Search for top-quark decays $t \to Hq$ with 36 fb$^{-1}$ of $pp$ collision data at $\sqrt{s}=13~\tev$ with the ATLAS detector}
+\AtlasTitle{Search for flavour-changing neutral current $tHq$ interections of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons
+                   with 139 fb$^{-1}$ of $pp$ collision data at $\sqrt{s}=13~\tev$ with the ATLAS detector}
 
@@
 % Comment or remove in final version.
-\AtlasVersion{2.1}
+%\AtlasVersion{2.2}
 % Abstract - % directly after { is important for correct indentation
 \AtlasAbstract{%
-A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the 
-Standard Model Higgs boson, $t\to Hq$, is presented. 
-The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
-CERN Large Hadron Collider and corresponding to an integrated luminosity of 36.1 fb$^{-1}$.
-Two complementary analyses are performed to search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
-and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, respectively.  
-The high multiplicity of $b$-quark jets, or the presence of hadronically decaying $\tau$-leptons, is exploited in the two analyses respectively. 
-Multivariate techniques are used to separate the signal from the background, which is dominated by top-quark pair production.
+
+A search for flavour-changing neutral current $tHq$ interections with a top quark, an up-type quark ($q=u, c$), and the
+Standard Model Higgs boson is presented. The Higgs boson decay to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
+The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
+CERN Large Hadron Collider and corresponding to an integrated luminosity of 139.6 fb$^{-1}$.
+Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
+which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow Hq$. 
+The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
+as well as multiple jets.  
+Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
 No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
-The combination of these searches with ATLAS searches in diphoton and multilepton final states 
-%significantly improves the sensitivity, 
-yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
-and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), respectively.
-The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
-These are the most restrictive direct bounds on $tqH$ interactions obtained so far.
+Observed (expected) 95\% CL upper limits are set on the $t\to Hc$ and $t\to Hu$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$) 
+and XXX ($0.034^{+0.014}_{-0.012}\%$), respectively.
+%The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
+%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.
 }
@@
 % ATLAS reference code, to help ATLAS members to locate the paper
-\AtlasRefCode{TOPQ-2017-07}
+\AtlasRefCode{TOPQ-2019-17}
 %\AtlasRefCode{ATLAS-CONF-2018-049}
@@
 % \AtlasJournal{Phys.\ Lett.\ B.}
-% \AtlasJournalRef{\PLB 789 (2017) 123}
-% \AtlasDOI{}
+%\AtlasJournalRef{JHEP 05 (2019) 123}
+%\AtlasDOI{10.1007/JHEP05(2019)123}
+
+% CERN preprint number ---> can be found in CDS entry for Draft 2!
+%\PreprintIdNumber{CERN-EP-2018-295}
 
@@
 % List of supporting notes  (leave as null \AtlasCoverSupportingNote{} if you want to skip this option)
-\AtlasCoverSupportingNote{Search for $\ttbar \to WbHq$, $H \to b\bar{b}$}{https://cds.cern.ch/record/2257631}
-\AtlasCoverSupportingNote{Search for $\ttbar \to WbHq$, $H \to \tau^+\tau^-$}{https://cds.cern.ch/record/2273683}
-\AtlasCoverSupportingNote{Combination of $\ttbar \to WbHq$ searches}{https://cds.cern.ch/record/2312520/}
+%\AtlasCoverSupportingNote{Search for $\ttbar \to WbHq$, $H \to b\bar{b}$}{https://cds.cern.ch/record/2257631}
+%\AtlasCoverSupportingNote{Search for $\ttbar \to WbHq$, $H \to \tau^+\tau^-$}{https://cds.cern.ch/record/2273683}
+%\AtlasCoverSupportingNote{Combination of $\ttbar \to WbHq$ searches}{https://cds.cern.ch/record/2312520/}
+\AtlasCoverSupportingNote{Search for flavor-changing neutral currents tHq interactions with, $H \to \tau^+\tau^-$}{https://cds.cern.ch/record/2687866}
 %
@@
 % Comment deadline
-\AtlasCoverCommentsDeadline{4 November 2018}
+\AtlasCoverCommentsDeadline{1 November 2021}
 
@@
 \AtlasCoverAnalysisTeam{
-$H \to b\bar{b}$: Trisha Farooque, Davide Gerbaudo, Aurelio Juste, Nicola Orlando,  \\ Cheng Peng,  Laura Pereira, 
-Yulia Rodina, Yanjun Tu,  Lo\"ic Val\'ery, \\ Tal Van Daalen, Jia-Shian Wang, Daiki Yamaguchi; \\
-$H \to \tau^+\tau^-$: Xin Chen, Antonio De Maria, Boyang Li, Ligang Xia, Gang Zhang; \\
-Combination: Peter Onyisi, Harish Potti}
+Xin Chen, Boyang Li, Mingming Xia, Wei-Ming Yao}
+%Combination: Peter Onyisi, Harish Potti}
 
@@
 % Give either all members at once (then they appear on one line), or separately
-\AtlasCoverEdBoardMember{Ketevi Assamagan~(chair), Garabed Halladjian, Fabrice Hubaut, Michele Weber~(chair)}
+\AtlasCoverEdBoardMember{Not assigned yet!}
 
@@
 % Editors egroup
-\AtlasCoverEgroupEditors{atlas-TOPQ-2017-07-editors@cern.ch}
+\AtlasCoverEgroupEditors{atlas-TOPQ-2019-17-editors@cern.ch}
 
 % EdBoard egroup
-\AtlasCoverEgroupEdBoard{atlas-TOPQ-2017-07-editorial-board@cern.ch}
+\AtlasCoverEgroupEdBoard{atlas-TOPQ-2019-17-editorial-board@cern.ch}

### 2021-06-11 sections/conclusion.tex
rename fcnc-paper to ANA-TOPQ-2019-17-PAPER

@@
 
-A search for flavour-changing neutral-current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
-The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
-CERN Large Hadron Collider and corresponding to an integrated luminosity of 36.1 fb$^{-1}$.
-Two complementary analyses are performed to search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
-and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
-The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, with several 
-of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
-The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
-Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
+A search for flavour-changing neutral current $tHq$ interections with a top quark,	an up-type quark ($q=u, c$), and the
+Standard Model Higgs boson is presented. The Higgs boson decay to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
+The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the
+CERN Large Hadron Collider and corresponding to an integrated luminosity of 139.6 fb$^{-1}$.
+Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
+which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow Hq$.
+The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
+as well as multiple jets.
+Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
 No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
-In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios 
-are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$, respectively.
-In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios 
-are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$, respectively.
-The combination of these searches with ATLAS searches in diphoton and multilepton final states 
-%significantly improves the sensitivity, 
-yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
-and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$ respectively.
-The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
-%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
-These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions obtained so far.
+Observed (expected) 95\% CL upper limits are set on the $t\to Hc$ and $t\to Hu$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$)
+and XXX ($0.034^{+0.014}_{-0.012}\%$), respectively.

### 2021-06-15 ANA-TOPQ-2019-17-PAPER-metadata.tex
updates on tau fakes and strategies

@@
 %\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
-\AtlasTitle{Search for flavour-changing neutral current $tHq$ interections of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons
-                   with 139 fb$^{-1}$ of $pp$ collision data at $\sqrt{s}=13~\tev$ with the ATLAS detector}
+\AtlasTitle{Search for flavour-changing neutral current $tHq$ ($q=u,c$) of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons
+                   in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector}
 

### 2021-06-15 sections/data_presel.tex
updates on tau fakes and strategies

@@
 \begin{itemize}
-	\item $t_h\lephad$: Targeting $t(q)H\to bqq(q)\lephad$ decay mode.
-Exactly one additional $\had$ with charge opposite to the lepton is further required.
-At least 3 jets with exactly one $b$-tagged are required.
-	\item $t_l\hadhad$: Targeting $t(q)H\to bl\nu(q)\hadhad$ decay mode. At least two additional $\had$ with opposite charge are further required. At least 1 jet with exactly one $b$-tagged is required.
-	\item $t_l\had$: Targeting $t(q)H\to bl\nu(q)\hadhad$ decay mode when one of the \had fails the tau reconstruction or identificaiton so that there is only one reconstructed \had candidate.
-Exactly one additional $\had$ with charge same for the lepton is further required.
-At least 2 jets with exactly one $b$-tagged are required.
+\item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\lephad$ decay.
+Exactly one $\had$ with opposite-side charge to $\tau_l$ is required, including at least three jets with exactly one $b$-tagged jet.
+\item $t_l\hadhad$: Targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-tagged jet.
+\item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the \had fails the tau reconstruction or identificaiton so that there is only
+  one \had candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-tagged jet.
 \end{itemize}
 
-The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and trailing $\had$ matched to the $\had$'s reconstructed by the trigger.
-No selected electrons or muons is required.
+The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and trailing $\had$ passed the trigger.
 The two \had candidates are required to have charges of opposite sign.
@@
 \had  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
-Electric charge ($q$) & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ & $q_\ell \times q_{\tau_{\mathrm{had,1}}} > 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
+Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} < 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} > 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ \\
 Jets  &  $\geq$ 3 jets & $\geq$1 jets & $\geq$2 jets & $\geq$3 jets \\

### 2021-06-15 sections/introduction.tex
updates on tau fakes and strategies

@@
 The corresponding integrated luminosity is 139.6 fb$^{-1}$.
-Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted.
+Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted and the signals are divided into several final states depending on the production modes and the
+decay of $W$ boson hadronically and leptonically from the $t\rightarrow wb$ decay referred as $t_h$ and $t_l$. The $H\rightarrow \tau\tau$ decay detected to be in
+either $\tlhad$ or $thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
 Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected for hadronic channels.
@@
 More regions are exploited compared to the FCNC $\Htautau$ search conducted using partial Run~2 data.
+The analysis also uses various $t\bar{t}$ control regions (CRtt) for calibration of tau fakes in Monte Carlo as well as
+data-driven fake estimations from QCD multi-jet background.
 

### 2021-06-15 sections/signal_background_modeling.tex
updates on tau fakes and strategies

@@
 the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element calculation 
-is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering, hadronisation, and the underlying event.
+is performed.} {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
+%{\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
+with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering, hadronisation, and the underlying event.
 The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
@@
 The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
-assuming an arbitrary branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
+assuming an arbitrary branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=0.2\%$.
 The case of both top quarks decaying into $Hq$ is neglected in the analysis given the existing upper limits on $\BR(t \to Hq)$ (Section~\ref{sec:intro}).
 
-The nominal sample used to model the $\ttbar$ background was generated with the NLO generator {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd} using the NNPDF3.0 NLO PDF set.
-The {\powheg} model parameter $h_{\textrm{damp}}$, which controls
+The $tH$ signal events were generated by {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
+with the NNPDF3.0 NLO parton distribution function (PDF) set and interfaced to {\pythia} 8.212 with the NNPDF2.3 LO PDF set for the modelling of parton showering,
+hadronisation, and the underlying event with the A14 tune.
+Depending on either up quark or charm quark involved in the FCNC decay, the effective Lagrangian of $tqH$ interaction are parametrised using
+dim-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 1.4218 pb and $\sigma(cg\to tH)$ = 0.206 pb using $\BR_{\mathrm{ref}}(t\to Hq)=0.2\%$ as benchmark.
+
+The nominal sample used to model the $\ttbar$ background was generated with the NLO generator {\powheg}~v2
+%\cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
+using the NNPDF3.0 NLO PDF set. The {\powheg} model parameter $h_{\textrm{damp}}$, which controls 
 matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, was set to 1.5 times the top-quark mass. 
@@
 \subsubsection{Fake electrons and muons}
-Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one \had.
-Since the fake rate of \had candidate is much larger than electron or muon.
-So in the majority of the fake lepton events, the \had candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies.
-However the multi-jet background has large event rate and can contribute with both electron or muon and \had faked, espcially to $t_l\had$ where the fake-lepton dominates and the jet multiplicity is low.
-This kind of event is modelled by ABCD method widely used in ATLAS physics analyses.
+Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one $\had$.
+Since the fake rate of $\had$ candidate is much larger than electron or muon.
+So in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies.
+However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, espcially to $t_l\had$ where the fake-lepton dominates and the jet multiplicity is low.
+This kind of event is modelled by data-driven ABCD method by cutting on $\met$ and the lepton isolation, which is widely used in ATLAS physics analyses.
+
+%\subsubsection{Fake $\tau$-lepton candidates}
+%\label{sec:faketaus}
+%The background with one or more fake $\had$ candidates mainly arises from $\ttbar$ or
+%multijet production, depending on the search channel. 
+%Studies based on the simulation show that, for all the above processes, fake $\had$ candidates primarily result from the 
+%misidentification of light-quark jets, with the contribution from $b$-quarks and gluon jets playing a subdominant role.
+%It is also found that the fake rate decreases for all jet flavours as the $\had$ candidate $\pt$ increases.
+
+%In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$ candidates via loosened $\had$ requirements with% proper fake factors and partially from monte carlo.
+These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
+The CR selection %requirements are analogous to those used to define the different SRs, except that the trailing $\had$ candidate is required to fail the medium $\had$ identification.
+
+%In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrated monte carlo with scale factors derived from the dedicated $t\bar t$
+%control regions ($CR_{tt}$) using the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events.
+%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated control regions discussed in Section~\ref{sec:st%rategy_Htautau}.
 
@@
 
-In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$ candidates via loosened $\had$ requirements with proper fake factors and partially from monte carlo.
+In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrated monte carlo with scale factors
+derived from the dedicated $t\bar t$
+control regions ($CR_{tt}$) using the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:crsr},
+aimed at fake taus from different origins. There are four kinds of fake taus that need to be calibrated: Type1) $\tau_{W}$'s with the opposite charge to the lepton;
+Type2) $\tau_{W}$'s with the same charge as the lepton; Type 3) the fake taus from b-jets; Type4) the fake taus from other origins (mainly radiations).
+These control regions are similar to the signal regions but with an additional b-jet or lepton defined as:
+$t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
+Where di-lepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The regions of
+$t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS are used to calibrate Type1 fake taus. Similarly for the Type2, the regions of $t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS are used.
+A simultaneous fit to data is made to derive the scale factors for the fake taus, which consists of total 24 parameters including 3 $\pt$ bins (25-35, 35-45, 45-)GeV for 1 and 3
+prong taus separately. The values of these scale factors range from 0.3 to 1.28 and are applied to the corresponding signal regions with single b-tagged jet.
+In $t_l\thadhad$ channel, both taus can be fake, so the calibration is applied to each tau separately, following the same procedure as $\tlhad$ channels using the
+lepton and fake tau charges, then the scale factors are multiplied together. The nominal value of the scale factors will vary along with other uncertainties from
+combined preformace (CP) recommendations and theory uncertainties in the final fit.
+%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
+%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
+%control regions discussed in Section~\ref{sec:strategy_Htautau}.
+
+In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$
+candidates via loosened $\had$ requirements with proper fake factors and partially from monte carlo.
 These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
-The CR selection requirements are analogous to those used to define the different SRs, except that the trailing $\had$ candidate is required to fail the medium $\had$ identification.
-
-In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrated monte carlo.
-The calibration is done depending on different source of the fake taus and \pt.
-The calibration factor are derived in the dedicated control regions discussed in Section~\ref{sec:strategy_Htautau}.
+The CR selection requirements are analogous to those used to define the different SRs, except
+that the trailing $\had$ candidate is required to fail the medium $\had$ identification.
+The events with fake trailing $\had$ candidate can be calculated by rescaling the templates of fake taus in the Fake-CR with proper fake factors (FF).
+The templates are aquired by subtracting all MC background contributions with real sub-leading taus from data. The FFs are computed as
+the ratio of the Data$-$MC$_\mathrm{real~tau}$ yields passing the medium tau ID to which failing the medium tau ID from different control regions and
+the differences are treated as part of systematics.

### 2021-06-15 sections/strategy_Htautau.tex
updates on tau fakes and strategies

@@
 
-The $Wb(q)H\to q\bar{q}b(q)\tau\tau$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
-the Higgs boson and at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
-If one of the $\tau$-leptons decays leptonically, an isolated electron or muon and significant $\met$ is also expected.
-In a significant fraction of the events, the lowest-$\pt$ jet from the $W$ boson decay fails the minimum $\pt$ requirement of $30~\gev$,
+The $tt(qH)$ and $tH$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
+the Higgs boson and the remaining $t\to Wb$ decay as well as an additional $q$-jet for $t\to qH$ decay. 
+%at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
+If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon and significant $\met$ is also expected.
+In a significant fraction of the events, the lowest-$\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
 resulting in some decay mode signal events mixed with production mode having only three jets reconstructed.
-In order to optimise the sensitivity of the search, the selected events are categorised into four SRs depending 
-on the number of $\taulep$ and $\had$ candidates, and on the number of light flavored jets:
-($t_h\lephad$, 2j), ($t_h\lephad$, $\geq$4j), ($t_h\hadhad$, 3j), and ($t_h\hadhad$, $\geq$4j).
+In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs depending on the number of leptons and
+$\had$ candidates, and on the number of light flavored jets:
+$t_l\hadhad$, $t_l\had$-1j, $t_l\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}.
+
+\begin{table}
+\centering
+\caption{Overview of the signal regions and the control regions used for fake tau scale factor derivation in leptonic channels.}
+\label{tab:srcr}
+\begin{tabular}[h]{c|c|c|c|c|c|c}
+\hline \hline
+\multicolumn{2}{c|}{Regions} & b-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
+\multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
+&$t_l\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
+&$t_l\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
+&$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
+&$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
+&$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
+&$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
+\multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
+&$t_lt_l2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
+&$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
+&$t_lt_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ OS\\ \cline{2-7}
+&$t_lt_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
+&$t_lt_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_l\tauhad$ OS\\ \hline
+\end{tabular}
+\end{table}
 
@@
 
-The $Wb(q)H\to l\nu b(q)\tau\tau$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown.
+In the  $t_lt(qH)$ and $t_lH$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown.
 The kinematics fit is no longer feasible.

### 2021-06-18 sections/introduction.tex
a few more changes up to systematics

@@
 decay of $W$ boson hadronically and leptonically from the $t\rightarrow wb$ decay referred as $t_h$ and $t_l$. The $H\rightarrow \tau\tau$ decay detected to be in
-either $\tlhad$ or $thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
+either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
 Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected for hadronic channels.

### 2021-06-18 sections/signal_background_modeling.tex
a few more changes up to systematics

@@
 derived from the dedicated $t\bar t$
-control regions ($CR_{tt}$) using the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:crsr},
+control regions ($CR_{tt}$) using the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
 aimed at fake taus from different origins. There are four kinds of fake taus that need to be calibrated: Type1) $\tau_{W}$'s with the opposite charge to the lepton;

### 2021-06-18 sections/strategy_Htautau.tex
a few more changes up to systematics

@@
 
-This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
-of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
-is missing or not (events with exactly three jets or at least four jets).
-The event kinematic reconstruction is based on the strategy used in Ref.~\cite{Chen:2015nta}, and is summarised below.
+%This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
+%of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
+%is missing or not (events with exactly three jets or at least four jets).
+This event categorisation is primarily motivated by optimizing the sensitivity in each signal region that targets both leptonic and hadronic top-quark
+decays as well as the Higgs decays into $\lephad$ or $\hadhad$ final state.   
+The event kinematic reconstruction is further applied to suppress the background based on the strategy used in Ref.~\cite{Chen:2015nta}, and is summarised below.
 
-For the decay mode events, the selected jets are assigned to the different top-quark decay products via a criterion based on 
-minimising the angular distances between light flavor jets and the visible decay product of the Higgs boson (the two tau candidates).
+For the $t_ht(qH)$ events, there should be at least four jets among which the one with the smallest angular distance to the visible decay product of the
+Higgs boson (the two tau candidates) is considered as $q$-jet since the top decay products are likely boosted closer together than other jets. 
+If there are more than 2 jets beside $q$-jet and $b$-jet, the jets from $W$ boson decay are chosen from the combination which have the invariant mass closest
+to W resonance. There is the chance that one of the jets fails the $\pt$ requirement and not reconstructed. The FCNC top resonance is still reconstructable
+given the big chance that the jet which is missing is from $W$ decay.
+
+In the $t_hH$ events, there are 3 jets coming from top hadronic decay including the b-jet. So a Higgs resonance formed by the taus and a top resonance formed by
+the jets are expected.
 
@@
 In the  $t_lt(qH)$ and $t_lH$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown.
-The kinematics fit is no longer feasible.
+The kinematics fit is no longer feasible in the $t_l\hadhad$ channel.
 The variables calculated from the visible objects are directly used in the multivariate analysis.
+However, the kinematics fit is still performed for the $t_l\had$ channels where the lepton and $\had$ are treated as di-tau candidate.
 
@@
     The description of each variable is provided in the text.}}
+\label{tab:importance_xTFW}
 \input{\FCNCTables/Importance/xTFW/Merged}
@@
     The description of each variable is provided in the text.}}
+\label{tab:importance_tthML}
 \input{\FCNCTables/Importance/tthML/Merged}
@@
 %draft 1 version
-In the training, All signal events ($tuH$ and $tcH$ signal are merged with a ratio of 1:1) are used against the total SM background (including both real and fake $\had$ contributions).
+In the training, All signal events ($tt(qH)$ and $tH$ signal are merged together) are used either for $tHu$ or $tHc$  $q=c,u$ against the total SM background (including both real and fake $\had$ contributions).
 
@@
 The discrimination of a given variable was quantified by the ``separation" and ``importance" measures provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 1\% were kept.
-The BDT input variables in each SR and their importance are listed in Table~\ref{tab:mva_var} and defined in the following:
+The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_tthML}-~\ref{tab:importance_xTFW} and defined in the following:
 \begin{itemize}
@@
 \end{equation}
-\item $m_{\tau,\tau}$ is the invariant mass of the tau candidates and reconstructed neutrinos in $t_hH$ and $t_ht(qH)$ channels. 
+\item $m_{\tau,\tau}$ is the invariant mass of the tau candidates and reconstructed neutrinos in $t_hH$, $t_ht(qH)$, and $t_l\had$ channels. 
 \item $m_{W}$ is the reconstructed invariant mass of the hadronic $W$ boson from SM top quark.
-\item $m_{t,FCNC}$ is the visible invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, FCNC-jet and reconstructed neutrinos.
-\item $m_{\tau\tau,vis}$ is the visible invariant mass of the di-tau candidates
+\item $m_{t,FCNC}$ is the visible invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
+\item $m_{\tau\tau,vis}$ is the visible invariant mass of the di-tau candidates or the lepton and $\had$ candidate when there is only one $\had$.
 \item $p_{T,\tau\tau,vis}$ is the $\pt$ of the di-tau candidates.
@@
 It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section.
-For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state, which is evident in the excess around 1 in Figure \ref{fig:x12_fit}.
+For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}.
 \item $\Delta R(l+bjet,\tau\tau)$ is the angular distance between the lepton+b-jet and di-tau candidates.
@@
 \item $\Delta R(l,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
-\item $\Delta R(\tau,qjet)$ is the angular distance between the tau and the reconstructed fcnc jet.
+\item $\Delta R(\tau,qjet)$ is the angular distance between the tau and the reconstructed $q$-jet.
 \item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(l,\tau)$.
@@
 \end{itemize}
-A comparison between data and the predicted background for some of these variables in each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_lhadhad}.
+A comparison between data and the predicted background for some of these variables in three main decay final states($t_l\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
+is shown in Figures~\ref{fig:mva_input_l2had_hadhad_lephad}.
+%each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_lhadhad}.
 The comparison between the data and predicted background after preselection for the distributions of two of the most 
 discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
-The expected signal (dashed red) corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.
+The expected signals (dashed red) are also shown after normalized to the total number of events un the predicted
+background for the shape comparison of the distributions.   
+%corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.
 The first and the last bins in the figures contain the underflow and overflow respectively.
@@
 A good description of the data by the background model is observed in all cases.
-The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
 
+The final observable used to extract signal events is defined as the BDT distribution in each SRs corresponding to either $tHu$ or $tHc$ signal training.
+Figure~\ref{fig:asimov_fitbdt_thu} and~\ref{fig:asimov_fitbdt_thc} show the fits to the data of BDT observable in each SRs with all background processes
+constrained to the SM expectation.
+%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{\FCNCFigures/tex/BDTinput}
+%\input{\FCNCFigures/tex/BDTinput}
 
-\input{\FCNCFigures/tex/BDT}
+%\input{\FCNCFigures/tex/BDT}

### 2021-06-23 sections/strategy_Htautau.tex
including latest plots and tables

@@
 
-The final observable used to extract signal events is defined as the BDT distribution in each SRs corresponding to either $tHu$ or $tHc$ signal training.
-Figure~\ref{fig:asimov_fitbdt_thu} and~\ref{fig:asimov_fitbdt_thc} show the fits to the data of BDT observable in each SRs with all background processes
+The final observable used to extract signal events is defined as the BDT distribution in each SRs corresponding to either $tHu$ or $tHc$ signal.
+Figure~\ref{fig:asimov_prefitbdt} show the prefits to the data of BDT observable in each SRs with all background processes
 constrained to the SM expectation.
@@
 %\input{\FCNCFigures/tex/BDTinput}
+\begin{figure}[H]
+\centering
+\includegraphics[page=6,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l2tau1bnj_os/ttvismass.pdf}
+\put(-130, 105){\small\textbf{(a1)}}
+%\put(-30, 80){\textbf{(a1)}}
+\includegraphics[page=6,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l2tau1bnj_os/drtautau.pdf}
+\put(-130, 105){\small\textbf{(a2)}}
+%\put(-30, 80){\textbf{(a2)}}
+\includegraphics[page=6,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l2tau1bnj_os/t2vismass.pdf}
+\put(-130, 105){\small\textbf{(a3)}} 
+%\put(-70, 70){\textbf{(a3)}}
+\\
+\includegraphics[page=6,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/tautaumass.pdf}
+\put(-130, 105){\small\textbf{(b1)}}
+\includegraphics[page=6,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/ttvismass.pdf}
+\put(-130, 105){\small\textbf{(b2)}}
+\includegraphics[page=6,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/drtautau.pdf}
+\put(-130, 105){\small\textbf{(b3)}}
+\\
+\includegraphics[page=6,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b3j_os_vetobtagwp70_highmet/ttvismass.pdf}
+\put(-130, 105){\small\textbf{(c1)}}
+\includegraphics[page=6,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b3j_os_vetobtagwp70_highmet/ttvismass.pdf}
+\put(-130, 105){\small\textbf{(c2)}}
+\includegraphics[page=6,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b3j_os_vetobtagwp70_highmet/drltau.pdf}
+\put(-130, 105){\small\textbf{(c3)}}
+\\
+\caption{ The BDT input distributions for the background and merged signal in the three main decay channels: $t_l\thadhad$ (a1-3), $t_h\thadhad$-3j (b1-3), and $t_h\tlhad$-3j (c1-3).
+}% The Kolmogorov Test values for the training and testing BDT distributions are also indicated.
+\label{fig:mva_input_l2had_hadhad_lephad}
+\end{figure}
 
 %\input{\FCNCFigures/tex/BDT}
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.33\textwidth]{\FCNCFigures/tthML/Limit/reg1l2tau1bnj_os.pdf}
+\put(-30, 110){\small\textbf{(a1)}}
+\includegraphics[width=0.33\textwidth]{\FCNCFigures/tthML/Limit/reg1l1tau1b1j_ss.pdf}
+\put(-30, 110){\small\textbf{(a2)}}
+\includegraphics[width=0.33\textwidth]{\FCNCFigures/tthML/Limit/reg1l1tau1b2j_ss.pdf}
+\put(-30, 110){\small\textbf{(a3)}}\\
+\includegraphics[width=0.33\textwidth]{\FCNCFigures/tthML/Limit/reg1l1tau1b2j_os.pdf}
+\put(-30, 110){\small\textbf{(b1)}}
+\includegraphics[width=0.33\textwidth]{\FCNCFigures/tthML/Limit/reg1l1tau1b3j_os.pdf}
+\put(-30, 110){\small\textbf{(b2)}}\\
+\includegraphics[width=0.33\textwidth]{\FCNCFigures/xTFW/Limit/tuH_reg2mtau1b2jos_vetobtagwp70_highmet.pdf}
+\put(-30, 110){\small\textbf{(c1)}}
+\includegraphics[width=0.33\textwidth]{\FCNCFigures/xTFW/Limit/tuH_reg2mtau1b3jos_vetobtagwp70_highmet.pdf}
+\put(-30, 110){\small\textbf{(c2)}}\\
+\caption{ The BDT output distributions are compared between the expected background and either $tHu$ or  $tHc$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),
+  $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2). }
+\label{fig:asimov_prefitbdt}
+\end{figure}

### 2021-09-21 ANA-TOPQ-2019-17-PAPER-metadata.tex
updating the paper draft V0.1

@@
 %\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
-\AtlasTitle{Search for flavour-changing neutral current $tHq$ ($q=u,c$) of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons
+\AtlasTitle{Search for flavour-changing neutral current $tqH$ ($q=u,c$) of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons
                    in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector}
@@
 % Comment or remove in final version.
-%\AtlasVersion{2.2}
+\AtlasVersion{0.1}
 % Abstract - % directly after { is important for correct indentation
@@
 
-A search for flavour-changing neutral current $tHq$ interections with a top quark, an up-type quark ($q=u, c$), and the
+A search for flavour-changing neutral current $tqH$ interections with a top quark, an up-type quark ($q=u, c$), and the
 Standard Model Higgs boson is presented. The Higgs boson decay to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
-CERN Large Hadron Collider and corresponding to an integrated luminosity of 139.6 fb$^{-1}$.
+CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
 Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
-which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow Hq$. 
+which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow qH$. 
 The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
@@
 Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
-No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
-Observed (expected) 95\% CL upper limits are set on the $t\to Hc$ and $t\to Hu$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$) 
+No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
+Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$) 
 and XXX ($0.034^{+0.014}_{-0.012}\%$), respectively.
@@
 % Give either all members at once (then they appear on one line), or separately
-\AtlasCoverEdBoardMember{Not assigned yet!}
+%\AtlasCoverEdBoardMember{Not assigned yet!}
 
-% \AtlasCoverEdBoardMember{EdBoard~Chair~(chair)}
-% \AtlasCoverEdBoardMember{EB~Member~1}
-% \AtlasCoverEdBoardMember{EB~Member~2}
-% \AtlasCoverEdBoardMember{EB~Member~3}
+ \AtlasCoverEdBoardMember{Luca Fiorini~(chair)}
+ \AtlasCoverEdBoardMember{Edson Carquin Lopez}
+ \AtlasCoverEdBoardMember{Luca Fiorini}
+ \AtlasCoverEdBoardMember{Michele Weber}
 

### 2021-09-21 sections/conclusion.tex
updating the paper draft V0.1

@@
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the
-CERN Large Hadron Collider and corresponding to an integrated luminosity of 139.6 fb$^{-1}$.
+CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
 Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in

### 2021-09-21 sections/data_presel.tex
updating the paper draft V0.1

@@
 
-The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ with 25 ns bunch spacing collected from 2015 to 2018, corresponding to an integrated luminosity of $139.6~\ifb$.
+The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ with 25 ns bunch spacing collected from 2015 to 2018, corresponding to an integrated luminosity of $139~\ifb$.
 Only events recorded with a single-electron trigger, a single-muon trigger, or a di-$\tau$ trigger under stable beam conditions 
-and for which all detector subsystems were operational are considered for signal regions.
+and for which all detector subsystems were operational are considered for analysis.
 While the events recorded by di-lepton triggers fall into the control regions used for fake-tau background estimation.
@@
 
-The signal final state including an electron or muon or \lep are referred to as leptonic channel, otherwise hadronic channel.
+The signal final state including an electron or muon or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
 
 The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger.
-Further requirement are defined targeting different signal decay mode:
+Further requirement are defined targeting different signal decay modes:
 \begin{itemize}
@@
 \item $t_l\hadhad$: Targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-tagged jet.
-\item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the \had fails the tau reconstruction or identificaiton so that there is only
-  one \had candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-tagged jet.
+\item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identificaiton so that there is only
+  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-tagged jet.
 \end{itemize}
@@
 The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and trailing $\had$ passed the trigger.
-The two \had candidates are required to have charges of opposite sign.
+The two $\had$ candidates are required to have charges of opposite sign.
 
@@
 Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & no isolated $e$ or $\mu$ \\
-\had  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
+$\had$  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
 Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} < 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} > 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ \\
-Jets  &  $\geq$ 3 jets & $\geq$1 jets & $\geq$2 jets & $\geq$3 jets \\
+Jets  &  3, $\geq$ 4 jets & $\geq$1 jets & 2, $\geq$3 jets & 3, $\geq$4 jets \\
 $b$-tagging & \multicolumn{3}{c|}{=1 $b$-tagged jets} & =1 $b$-tagged jets\\

### 2021-09-21 sections/introduction.tex
updating the paper draft V0.1

--- 2021-06-03 sections/introduction.tex
@@
 %with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
-such interactions would manifest themselves as FCNC top-quark decays~\cite{Agashe:2013hma}, $t\to H q$.  
-In the Standard Model (SM), such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
-interactions are forbidden at the tree level and suppressed even at higher orders in the perturbative expansion due to the 
-Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.  As a result, the SM predictions for the $t \to Hq$ branching 
-ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
+such interactions would manifest themselves as FCNC top-quark decays~\cite{Agashe:2013hma}, $t\to qH$.  
+In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
+The $t\to u/c+H$ branching fraction in the SM is calculated to be exceedingly small around $10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}.
+%such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
+%interactions are forbidden at the tree level and suppressed even at higher orders in the perturbative expansion due to the 
+%Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
+%As a result, the SM predictions for the $t \to Hq$ branching 
+%ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
 In contrast, large enhancements of these branching ratios are possible in some scenarios beyond the SM.
-Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) of type I, with explicit flavour conservation,
-and of type II, such as the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk,Cao:2014udj}, supersymmetric models
-with R-parity violation~\cite{Eilam:2001dh}, composite Higgs models with partial compositeness~\cite{Azatov:2014lha}, 
+Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) with or without the flavour violation,
+%of type I, with explicit flavour conservation,
+%and of type II, such as
+the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk,Cao:2014udj},
+supersymmetric models with R-parity violation~\cite{Eilam:2001dh}, composite Higgs models with partial compositeness~\cite{Azatov:2014lha}, 
 or warped extra dimensions models with SM fermions in the bulk~\cite{Azatov:2009na}. 
-In these scenarios, branching ratios can be as high as $\BR(t\to Hq) \sim 10^{-5}$. 
-An even larger branching ratio of  $\BR(t\to Hc) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
-since a tree-level FCNC coupling is not forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}. 
-While other FCNC top couplings ($tq\gamma$, $tqZ$, $tqg$) are also enhanced in these scenarios beyond the SM, 
-the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling~\cite{Agashe:2013hma}.
+In these scenarios, branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$. 
+An even larger branching ratio of  $\BR(t\to cH) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
+since a tree-level FCNC coupling is no longer forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}. 
+%While other FCNC top couplings ($tq\gamma$, $tqZ$, $tqg$) are also enhanced in these scenarios beyond the SM, 
+%the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling~\cite{Agashe:2013hma}.
+Therefore, an observation of this decay would be a clear evidence for new physics. The $tqH$ interaction could also potentially open up more
+Higgs decay channels, such as $H\rightarrow t^*q\rightarrow Wbq$, but they are likely suppressed due to the $t-H$ mass difference,
+which could be interesting for future studies.
+
+On the other hand, if the $tqH$ interaction exists, the single-top, Higgs associated production through this interaction should also be enhanced.
+The $tH$ associated production in the SM prediction is expected to be small at LHC~\cite{Greljo:2014dka}.
+So the study on this process will also contribute to the FCNC interaction searches.
 
@@
 of top-quark pair ($\ttbar$) events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{fcnc36} using early Run~2 data.
-In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{ 
-In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
+
+In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$.
+Similarly,
 $WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
 the SM.
-The simplifying assumption of SM-like Higgs boson branching ratios is motivated by the fact that measurements of the flavour-diagonal Higgs boson couplings by the ATLAS and CMS collaborations are in agreement with the SM prediction within about 10\%~\cite{Khachatryan:2016vau,Sirunyan:2018koj}.
-Furthermore, typical beyond-the-SM scenarios that predict significant enhancements to $\BR(t\to Hq)$, also predict modifications to the Higgs boson branching ratios at the few percent level or below, well beyond the current experimental precision.
-Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
-has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
-and excellent diphoton mass re\-so\-lu\-tion. 
-Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as multileptons,
-are able to exploit a branching ratio that is significantly larger for the $H \rightarrow WW^*, \tau\tau$ decay modes than for the $H \rightarrow \gamma\gamma$ decay mode,
+The assumption of using SM-like Higgs boson branching ratios is motivated by the fact that measurements of the flavour-diagonal Higgs boson couplings by the ATLAS and CMS collaborations are in agreement with the SM prediction within about 10\%~\cite{Khachatryan:2016vau,Sirunyan:2018koj}.
+%Furthermore, typical beyond-the-SM scenarios that predict significant enhancements to $\BR(t\to Hq)$, also predict modifications to the Higgs boson branching ratios at the few percent level or below, well beyond the current experimental precision.
+%Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
+%has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
+%and excellent diphoton mass re\-so\-lu\-tion. 
+%Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as multileptons,
+%are able to exploit a branching ratio that is significantly larger for the $H \rightarrow WW^*, \tau\tau$ decay modes than for the $H \rightarrow \gamma\gamma$ decay mode,
 %are able to exploit a significantly larger branching ratio for the Higgs boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, 
-and are also characterised by relatively small backgrounds.
+%and are also characterised by relatively small backgrounds.
 %However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
@@
 %so any excess would be hard to interpret as originating from $t \to Hq$ decays.
-Finally, searches have also been performed exploiting the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
-of $\BR(H\to b\bar{b})\simeq 58\%$. Compared with Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
+%Finally, searches have also been performed exploiting the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
+%of $\BR(H\to b\bar{b})\simeq 58\%$.
+Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
 Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of
-$\BR(t\to Hc)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, and of $\BR(t\to Hc)<0.16\%$ based on
+$\BR(t\to cH)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, $\BR(t\to cH)<0.16\%$ based on
 %signatures with two same-charge light leptons (electrons or muons) or three light leptons 
-multilepton signatures resulting from 
-$H \to WW^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically, or $H \to ZZ^*$~\cite{Aaboud:2018pob}.
-These upper limits are derived assuming that $\BR(t\to Hu)=0$. Similar upper limits are obtained for $\BR(t\to Hu)$ if $\BR(t\to Hc)=0$.
-The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
-Combining all of the ATLAS searches using 36fb$^{-1}$ Run~2 data, the limits at 95\% CL are set for  $\BR(t\to Hc)<0.11\%$ and $\BR(t\to Hc)<0.12\%$ respectively assuming the other one is 0.
+multilepton (electron or muon) signatures resulting from 
+$H \to  WW^*, ZZ^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically~\cite{Aaboud:2018pob},
+$\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36}, and of $\BR(t\to cH)<0.19\%$ using $H\to tau\bar{tau}$ decay in which at least
+one of $\tau$-leptons decays hadronically~\cite{fcnc36}.  
+These upper limits are derived assuming that $\BR(t\to uH)=0$. Similar upper limits are obtained for $\BR(t\to uH)$ if $\BR(t\to cH)=0$.
+%The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
+Combining all of the ATLAS searches using 36fb$^{-1}$ Run~2 data, the limits at 95\% CL are set for  $\BR(t\to cH)<0.11\%$ and $\BR(t\to uH)<0.12\%$ respectively assuming $\BR(t\to uH)=0$ and $\BR(t\to cH)=0$~\cite{fcnc36}.
+
 The CMS Collaboration has performed a search using  
@@
 This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
-The corresponding integrated luminosity is 139.6 fb$^{-1}$.
-Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted.
-Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected for hadronic channels.
-Events with at least one \tauhad with an additional electron or muon are selected from leptonic channels.
-More regions are exploited compared to the FCNC $\Htautau$ search conducted using partial Run~2 data.
+The corresponding integrated luminosity is 139.0 fb$^{-1}$.
+Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted and the signals are divided into several final states depending on the production modes and
+the  $W$ boson decay either hadronically or leptonically from the $t\rightarrow Wb$ decay referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
+$t_l$ when the $\tau$ decays into a light lepton(electron or muon) as $\tau_{lep}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
+The $H\rightarrow \tau\tau$ decay is detected to be in
+either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
+Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected as the hadronic channels.
+Events with at least one \tauhad with an additional electron or muon are selected as the leptonic channels.
+More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data as well as
+various $t\bar{t}$ control regions (CRtt) used for calibration of tau fakes in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
 
@@
 
-The expected sensitivity is about a factor of two relative to the most sensitive results~\cite{fcnc36} up until now.
+%The expected sensitivity is about a factor of two relative to the most sensitive results~\cite{fcnc36} up until now.

### 2021-09-21 sections/signal_background_modeling.tex
updating the paper draft V0.1

@@
 In the simulation, the top-quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
-and the Higgs boson is allowed to decay into all SM particles with branching ratios calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
+and the Higgs boson is forced to decay into $H\to \tau\tau$ with branching ratio calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
 Backgrounds with non-prompt electrons or muons, with photons or jets misidentified as electrons, or with jets misidentified as $\had$ candidates, 
@@
 The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
-assuming an arbitrary branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=0.2\%$.
+assuming an arbitrary branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=0.1\%$.
 The case of both top quarks decaying into $Hq$ is neglected in the analysis given the existing upper limits on $\BR(t \to Hq)$ (Section~\ref{sec:intro}).
@@
 hadronisation, and the underlying event with the A14 tune.
-Depending on either up quark or charm quark involved in the FCNC decay, the effective Lagrangian of $tqH$ interaction are parametrised using
-dim-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 1.4218 pb and $\sigma(cg\to tH)$ = 0.206 pb using $\BR_{\mathrm{ref}}(t\to Hq)=0.2\%$ as benchmark.
+Depending on either up quark or charm quark involved in the FCNC production, the effective Lagrangian of $tqH$ interaction are parametrised using
+dim-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 0.711 pb and $\sigma(cg\to tH)$ = 0.103 pb using $\BR_{\mathrm{ref}}(t\to Hq)=0.1\%$ as benchmark.
 
@@
 and interfaced to {\pythia}~8.210 with the NNPDF2.3 LO PDF set and the A14 tune. 
-Instead, the $\ttbar V$ samples used in the $\Hbb$ search are based on LO matrix elements computed for up to two additional partons 
-using the NNPDF3.0 NLO PDF set, and merged using the CKKW-L approach~\cite{Lonnblad:2001iq}.
+%Instead, the $\ttbar V$ samples used in the $\Hbb$ search are based on LO matrix elements computed for up to two additional partons 
+%using the NNPDF3.0 NLO PDF set, and merged using the CKKW-L approach~\cite{Lonnblad:2001iq}.
 The $\ttbar V$ samples are normalised to the NLO cross section computed with {\amcatnlo}, while the $\ttbar H$ sample is normalised using 
@@
 So in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies.
-However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, espcially to $t_l\had$ where the fake-lepton dominates and the jet multiplicity is low.
-This kind of event is modelled by data-driven ABCD method by cutting on $\met$ and the lepton isolation, which is widely used in ATLAS physics analyses.
+However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, espcially to $t_l\had$ where the fake-lepton dominates.
+%and the jet multiplicity is low.
+This kind of event is modelled by data-driven ABCD method by cutting on $\met$ and the tight lepton isolation using PLIV, which is widely used in ATLAS physics analyses.
 
@@
 The background with one or more fake $\had$ candidates mainly arises from $\ttbar$ or
-multijet production, depending on the search channel.
+multijet production, depending on the search channels.
 Studies based on the simulation show that, for all the above processes, fake $\had$ candidates primarily result from the
@@
 
-In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrated monte carlo with scale factors
+In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrating monte carlo with scale factors
 derived from the dedicated $t\bar t$
 control regions ($CR_{tt}$) using the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
-aimed at fake taus from different origins. There are four kinds of fake taus that need to be calibrated: Type1) $\tau_{W}$'s with the opposite charge to the lepton;
-Type2) $\tau_{W}$'s with the same charge as the lepton; Type 3) the fake taus from b-jets; Type4) the fake taus from other origins (mainly radiations).
-These control regions are similar to the signal regions but with an additional b-jet or lepton defined as:
+aimed at fake taus from different origins. There are four kinds of fake taus that need to be calibrated: Type1) the fake taus from $W$-jets ($\tau_{W}$)
+with the opposite charge to the lepton;
+Type2) $\tau_{W}$'s with the same charge as the lepton; Type 3) the fake taus from $b$-jets; Type4) the fake taus from other origins (mainly radiations).
+These control regions are similar to the signal regions but with an addition $b$-jet or lepton defined as following:
 $t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
-Where di-lepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The regions of
-$t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS are used to calibrate Type1 fake taus. Similarly for the Type2, the regions of $t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS are used.
-A simultaneous fit to data is made to derive the scale factors for the fake taus, which consists of total 24 parameters including 3 $\pt$ bins (25-35, 35-45, 45-)GeV for 1 and 3
-prong taus separately. The values of these scale factors range from 0.3 to 1.28 and are applied to the corresponding signal regions with single b-tagged jet.
-In $t_l\thadhad$ channel, both taus can be fake, so the calibration is applied to each tau separately, following the same procedure as $\tlhad$ channels using the
+The di-lepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The regions of
+$t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS are used to calibrate Type1 fake taus.
+Similarly for the Type2, the regions of $t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS are used.
+A simultaneous fit to data is made to derive the scale factors for the fake taus in MC, which consist of total 24 parameters
+including four types, 3 $\pt$ bins (25-35, 35-45, 45- GeV), 2 bins for 1 and 3 prong taus separately.
+The values of these scale factors range from 0.3 to 1.28 and are applied to the corresponding signal regions with single b-tagged jet.
+
+In the $t_l\thadhad$ channel, both taus can be fake, so the calibration is applied to each tau separately, following the same procedure as $\tlhad$ channels using the
 lepton and fake tau charges, then the scale factors are multiplied together. The nominal value of the scale factors will vary along with other uncertainties from
@@
 In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$
-candidates via loosened $\had$ requirements with proper fake factors and partially from monte carlo.
+candidates via loosened $\had$ requirements with proper fake factors and partially from monte carlo~\cite{ATLAS-CONF-2021-044}.
 These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.

### 2021-09-21 sections/statistical_analysis.tex
updating the paper draft V0.1

@@
 a product of Poisson probability terms over all bins considered in the search. This function depends
-on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $\Hq$ signal events
-normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=0.2\%$,
+on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $tH$ and $tt(Hq)$ signal events
+normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=0.1\%$,
 and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations. 
@@
 plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
-a signal contamination above 5\% are excluded (referred to as blinding requirements).
+a signal contamination above 10\% are excluded (referred to as blinding requirements).
 In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
@@
 The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
-A related statistic is used to determine whether the observed data is compatible with the background-only hypothesis (the so-called discovery test)  
-by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
-The $p$-value (referred to as $p_0$), representing the level of agreement between the data and the background-only hypothesis, is estimated by integrating
-%representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
-%the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
-the distribution of $q_0$ based on the asymptotic formulae in Ref.~\cite{Cowan:2010js}, 
-above the observed value of $q_0$ in the data. 
-%The observed $p_0$-value is checked for each explored signal scenario.
-%In the case of the data being compatible with the background-only hypothesis, 
-Upper limits on $\mu$, and thus on 
+%A related statistic is used to determine whether the observed data is compatible with the background-only hypothesis (the so-called discovery test)  
+%by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
+%The $p$-value (referred to as $p_0$), representing the level of agreement between the data and the background-only hypothesis, is estimated by integrating
+%%representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
+%%the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
+%the distribution of $q_0$ based on the asymptotic formulae in Ref.~\cite{Cowan:2010js}, 
+%above the observed value of $q_0$ in the data. 
+%%The observed $p_0$-value is checked for each explored signal scenario.
+%%In the case of the data being compatible with the background-only hypothesis, 
+%Upper limits on $\mu$, and thus on 
+%$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
+%For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
+%where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.
+
+In the absence of signal, exclusion limits are set on $\mu$ , and thus on
 $\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.

### 2021-09-21 sections/systematic_uncertainties.tex
a few more changes up to systematics
updating the paper draft V0.1

@@
 The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pile-up treatment, 
-is split into 21 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}.
+is split into 43 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}. The total JES uncertianty is
+below 5\% for most jets and below 1\% for central jets with pT between 300 GeV and 2 TeV. The difference between the JER
+in data and MC is represented by one NP. It is applied on the MC by smearing the jet pT within the prescribed uncertainty.
 
@@
 whereas the light-jet efficiency is scaled by $\pt$- and $\eta$-dependent factors.
-The $b$-jet efficiency is measured in a data sample enriched in $\ttbar$ events~\cite{Aaboud:2018xwy}, while the $c$-jet efficiency is measured
+The $b$-jet efficiency is measured in a data sample enriched in $\ttbar$ events~\cite{Aad:2019epj79}, %EPJ C79(2019)970 {Aaboud:2018xwy},
+  while the $c$-jet efficiency is measured
 using $\ttbar$ events~\cite{ATLAS-CONF-2018-001} or $W$+$c$-jet events~\cite{Aad:2015ydr}. 
@@
 These systematic uncertainties are taken as uncorrelated between $b$-jets, $c$-jets, and light-jets.
+
+The uncertainty on the pileup reweighting is evaluated by varying the pileup scale factors
+by 1$\sigma$ based on the reweighting of the average interactions per bunch crossing. However, this
+uncertainty is highly correlated with the luminosity uncertainty and may be an overestimate.
 
@@
 to the overall theoretical uncertainty in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
-with the MSTW 2008 68\% CL NNLO, CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3 5F FFN~\cite{Ball:2012cx} PDF sets.
-The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
-{\powheg}+{\pythiaeight} with a prediction from \textsc{Sherpa}~2.2.1. For the latter, the matrix-element calculation is performed 
-for up to two partons at NLO and up to four partons at LO using \textsc{Comix} and \textsc{OpenLoops}, and
-merged with the {\sherpa} parton shower using the ME+PS@NLO prescription.
+with the NNPDF3.0(NLO), CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3(LO) 5F FFN~\cite{Ball:2012cx} PDF sets.
+The hdamp parameter (which controls the amount of radiation produced by the parton shower in
+POWHEG-BOX v2) is set to 1.5$m_{top}$ in the nominal case. Alternative samples are generated with hdamp=3$m_{top}$. The
+difference between two samples is treated as one of the systematics as ``$t\bar{t}$ hdamp''. 
+%The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
+%{\powheg}+{\pythiaeight} with a prediction from \textsc{Sherpa}~2.2.1. For the latter, the matrix-element calculation is performed 
+%for up to two partons at NLO and up to four partons at LO using \textsc{Comix} and \textsc{OpenLoops}, and
+%merged with the {\sherpa} parton shower using the ME+PS@NLO prescription.
 
@@
 a sample with increased radiation (referred to as radHi) is obtained by decreasing the renormalisation and factorisation scales  
-by a factor of two, doubling the $h_{\textrm{damp}}$ parameter, and using the Var3c upward variation of the A14 parameter set;
+by a factor of two, %doubling the $h_{\textrm{damp}}$ parameter,
+and using the Var3c upward variation of the A14 parameter set;
 a sample with decreased radiation (referred to as radLow) is obtained by increasing the scales by a factor of two 
@@
 The total normalisation uncertainty of $V$+jets processes is estimated by comparing the data and total background prediction in 
-the different analysis regions considered, but requiring exactly zero $b$-tagged jets. Agreement between data and predicted background 
-in these modified regions, which are dominated by $V$+light-jets, is found to be within approximately 30\%. This bound is taken to 
-be the normalisation uncertainty, correlated across all $V$+jets subprocesses. 
-Since {\sherpa}~2.2 has been found to underestimate $V$+heavy-flavour production by about a factor
-of 1.3~\cite{Aaboud:2017xsd}, additional 30\% normalisation uncertainties are assumed for $V$+$\geq$1$c$+jets and $V$+$\geq$1$b$+jets
-subprocesses, considered uncorrelated between them.
+the different analysis regions considered, but requiring exactly zero $b$-tagged jets.
+%Agreement between data and predicted background 
+%in these modified regions, which are dominated by $V$+light-jets, is found to be within approximately 30\%. This bound is taken to 
+%be the normalisation uncertainty, correlated across all $V$+jets subprocesses. 
+%Since {\sherpa}~2.2 has been found to underestimate $V$+heavy-flavour production by about a factor
+%of 1.3~\cite{Aaboud:2017xsd}, additional 30\% normalisation uncertainties are assumed for $V$+$\geq$1$c$+jets and $V$+$\geq$1$b$+jets
+%subprocesses, considered uncorrelated between them.
 
@@
 For the $t$- and $tW$-channel processes, an uncertainty due to the choice of parton shower and hadronisation model is derived 
-by comparing events produced by {\powheg} interfaced to {\pythia}~6 or {\herwigpp}.
+by comparing events produced by {\powheg} interfaced to {\pythia}~8 or {\herwigpp}.
 These uncertainties are treated as fully correlated among single-top-quark production processes, but uncorrelated with the
@@
 
-Several normalisation and shape uncertainties are taken into account for the $\Hq$ signal.
+Several normalisation and shape uncertainties are taken into account for the $\Hq$ and $pp\to tH$ signals.
 Uncertainties of the Higgs boson branching ratios are taken into account

### 2021-09-21 sections/introduction.tex
modify introduction

--- 2021-06-18 sections/introduction.tex
@@
 Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted and the signals are divided into several final states depending on the production modes and the
-decay of $W$ boson hadronically and leptonically from the $t\rightarrow wb$ decay referred as $t_h$ and $t_l$. The $H\rightarrow \tau\tau$ decay detected to be in
+decay of $W$ boson hadronically and leptonically from the $t\rightarrow Wb$ decay, referred as $t_h$ and $t_l$ respectively. The $H\rightarrow \tau\tau$ decay detected to be in
 either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
-Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected for hadronic channels.
-Events with at least one \tauhad with an additional electron or muon are selected from leptonic channels.
-More regions are exploited compared to the FCNC $\Htautau$ search conducted using partial Run~2 data.
+Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected for hadronic channel.
+Events with at least one \tauhad with an additional electron or muon are selected from leptonic channel.
+More regions are exploited compared to the FCNC $\Htautau$ search conducted using early Run~2 data amounting to 36fb$^{-1}$.
 The analysis also uses various $t\bar{t}$ control regions (CRtt) for calibration of tau fakes in Monte Carlo as well as

### 2021-09-21 sections/objects.tex

@@
 in the tracker and in the calorimeter.
-A track-based lepton isolation criterion is defined by calculating the quantity $p_R = \sum \pt^{\textrm{trk}}$ and $E_R = \sum E^{\textrm{clst}}$, where
+A track-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$ and $E_R = \sum E^{\textrm{clst}}$, where
 the scalar sum includes all tracks and energy deposit (excluding the lepton candidate itself) within the cone defined by $\Delta R<0.2 (0.3)$ around the %axis
 direction of the electron (muon). The electron (muon) candidates are required satisfy both $I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$.
+
+Tight isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions based a trained isolation boosted decision tree \texttt{PromptLeptonVeto}(PLIV), which is to identify non-prompt light leptons using lifetime information associated with a track jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}.
+These additional reconstructed charged particle tracks inside the jet can be
+used to increase the precision of identifying the displaced decay vertex of heavy flavor (b, c) hadrons that produced non-prompt leptons.
+The tight working points are: \texttt{PLIV}$<-0.6734$ for high $\pt$ muons and \texttt{PLIV}$<-0.704$ for hight $\pt$ barrel electrons.
+The scale factors for the efficiencies of the tight \texttt{PLIV} working points are measured using the tag and probe method
+with $Z\rightarrow l^+l^-$ events. These scale factors are also checked applicable to the electron or muon from the tau decay
+using $Z\rightarrow\tau\tau\rightarrow e\mu$ samples, which is consistent with 1 at 2\% level. To be conservative, we assign
+additional $\pm 2\%$ systematic uncertainty for the PLIV efficiency for the tau-lepton in the lepton+$\thad$ channels.
 %Additionally, the $\Htautau$ search requires leptons to
@@
 %built from energy deposits in the calorimeters calibrated to the electromagnetic scale. 
-Candidate jets are reconstructed with the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq} with a
-radius parameter $R=0.4$, as implemented in the \fastjet\ package~\cite{Cacciari:2011ma}.  
-Jet reconstruction in the calorimeter starts from topological clustering~\cite{Aad:2016upy} of individual calorimeter cells calibrated to the electromagnetic energy scale. 
+Candidate jets are reconstructed using the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq} with a
+radius parameter $R=0.4$ applied to topological energy clusters~\cite{Aad:2016upy} and charged-particle tracks, processed using
+a particle-flow algorithm~\cite{Aad:2017epj77}. %newref Eur. Phys. J. C 77 (2017) 466
+%as implemented in the \fastjet\ package~\cite{Cacciari:2011ma}.  
+%Jet reconstruction in the calorimeter starts from topological clustering~\cite{Aad:2016upy} of individual calorimeter cells calibrated to the electromagnetic energy scale. 
 The reconstructed jets are then calibrated to the particle level by the application of a jet energy scale 
-derived from simulation and in situ corrections based on $\sqrt{s}=13~\tev$ data~\cite{Aaboud:2017jcu}. (TBD: check PFlow jets description)
+derived from simulation and in situ corrections based on $\sqrt{s}=13~\tev$ data~\cite{Aaboud:2017jcu}. %(TBD: check PFlow jets description)
 The calibrated jets used are required to have $\pt > 25~\gev$ and $|\eta| < 2.5$.
@@
 
-Jets containing $b$-hadrons are identified ($b$-tagged) via an algorithm~\cite{Aad:2015ydr,ATL-PHYS-PUB-2016-012} 
+Jets containing $b$-hadrons are identified ($b$-tagged) via the DL1r tagger~\cite{Aad:2019epj79,ATL-PHYS-PUB-2017-013} %newref
+%\cite{Aad:2015ydr,ATL-PHYS-PUB-2016-012} 
 that uses multivariate techniques to combine information about the impact parameters of displaced tracks and the  topological properties 
@@
 calculated. A jet is considered $b$-tagged if this value is above the threshold corresponding to
-an average 70\% efficiency to tag a $b$-quark jet, with a light-jet\footnote{Light-jet refers to a jet originating from the hadronisation of a light quark 
-($u$, $d$, $s$) or a gluon.} rejection factor of about 380 and a charm-jet rejection factor of about 12, as determined for jets with
-$\pt >20~\gev$ and $|\eta|<2.5$ in simulated $\ttbar$ events.  (TBD: check DL1r description)
+an average 70\% efficiency to tag a $b$-quark jet, with a light-jet\footnote{Light-jet refers to a jet originating from the hadronisation of a light quark ($u$, $d$, $s$) or a gluon.} rejection factor of about 385 and a charm-jet rejection factor of about 12, as determined for jets with
+$\pt >20~\gev$ and $|\eta|<2.5$ in simulated $\ttbar$ events.
 
 Hadronically decaying $\tau$-lepton ($\had$) candidates are reconstructed from energy clusters in the calorimeters and
-associated inner-detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
-with a total charge of $\pm 1$. Candidates are required to have \pt 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
-A Recurrent Neural Network (RNN) ~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} (citation to be changed) using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject jet backgrounds.
+associated inner-detector tracks~\cite{ATL-PHYS-PUB-2019-033}. %newref
+%~\cite{ATL-PHYS-PUB-2015-045}.
+Candidates are required to have either one or three associated tracks,
+with a total charge of $\pm 1$. Candidates are required to have \pt 5 GeV higher than the trigger threshold, and $|\eta|<2.5$,
+excluding the EM calorimeter's transition region.
+A Recurrent Neural Network (RNN)~\cite{Graves:2012SCI}
+%~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna}
+%A. Graves, Supervised Sequence Labelling with Recurrent Neural Networks, Studies in Computational Intelligence 385, Springer, 2012.
+using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject jet backgrounds.
 Three working points labelled loose, medium and tight are defined, and correspond to different $\had$ identification efficiency values, with the efficiency designed to be independent of $\pt$.
 The $\Htautau$ search uses the medium
-working point for the nominal selection, while the loose working point is used for background estimation.
-The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one-prong (three-prong) $\had$ 
-decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
+working point for the nominal selection.
+%, while the loose working point is used for background estimation.
+The medium working point has a combined reconstruction and identification efficiency of 75\% (60\%) for one-prong (three-prong) $\had$ 
+decays, and an expected rejection factor against light-jets of 35 (240)~\cite{ATL-PHYS-PUB-2019-033}. 
 Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
-Any $\had$ candidate that is also $b$-tagged is rejected. (TBD: check RNN description and update then numbers)
+Any $\had$ candidate that is also $b$-tagged is rejected.
+%(TBD: check RNN description and update then numbers)
 
@@
 In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
-is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
+is discarded if the jet is not $b$-tagged, otherwise the electron is remived.
+If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
 The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
@@
 and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
-few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
-if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
-
+few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.2$ are rejected
+if the jet is either $b$-tagged or has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
+The $\tauhad$ within a $\Delta R=0.2$ cone of an electron or muon are removed.
+In order to avoid double-counting of $\tauhad$ as jets, the closest jet whose axis is
+within ${\Delta}R = 0.2$ of a $\tauhad$ is discarded if the jet is not $b$-tagged, otherwise the $\tauhad$ is remived. 
 % TEXT FROM BOYANG. NEED TO RECHECK WHAT WE HAVE ABOVE IS ACCURATE

### 2021-09-21 sections/strategy_Htautau.tex

--- 2021-06-18 sections/strategy_Htautau.tex
@@
 
-The analysis strategy adopted in the $\Htautau$ search follows that developed in Ref.~\cite{Chen:2015nta} but improved to apply to more signal regions.
+The analysis strategy adopted in the $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more signal channels.
 
@@
 The $tt(qH)$ and $tH$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
-the Higgs boson and the remaining $t\to Wb$ decay as well as an additional $q$-jet for $t\to qH$ decay. 
+the Higgs boson and the remaining SM $t\to Wb$ decay. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
 %at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
-If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon and significant $\met$ is also expected.
-In a significant fraction of the events, the lowest-$\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
-resulting in some decay mode signal events mixed with production mode having only three jets reconstructed.
-In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs depending on the number of leptons and
+If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon with significant $\met$ is also expected.
+In a significant fraction of the events, the smaller jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
+resulting in some signal events mixed with production mode having only three reconstructed jets.
+In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs based on the number of light lepton and
 $\had$ candidates, and on the number of light flavored jets:
@@
 decays as well as the Higgs decays into $\lephad$ or $\hadhad$ final state.   
-The event kinematic reconstruction is further applied to suppress the background based on the strategy used in Ref.~\cite{Chen:2015nta}, and is summarised below.
+The event kinematic reconstruction is further applied in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the
+di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}. 
+%based on the strategy used in Ref.~\cite{Chen:2015nta}, and is summarised below.
 
-For the $t_ht(qH)$ events, there should be at least four jets among which the one with the smallest angular distance to the visible decay product of the
-Higgs boson (the two tau candidates) is considered as $q$-jet since the top decay products are likely boosted closer together than other jets. 
-If there are more than 2 jets beside $q$-jet and $b$-jet, the jets from $W$ boson decay are chosen from the combination which have the invariant mass closest
-to W resonance. There is the chance that one of the jets fails the $\pt$ requirement and not reconstructed. The FCNC top resonance is still reconstructable
-given the big chance that the jet which is missing is from $W$ decay.
+For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet, should be a hard narrow jet considering it's from the
+decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
+There should be at least four jets among which with the closest angular distance to the visible decay of the di-taus
+is considered as $q$-jet since the FCNC top decay products are likely boosted closer together than other jets. 
+If there are more than 2 jets beside $q$-jet and $b$-jet, the jets from $W$ boson decay are chosen from the combination
+with the invariant mass closest to W resonance. There is the chance that one of the jets fails the $\pt$ requirement and not reconstructed. This kind of events will fall
+into $t_hH$.
+%while the FCNC top resonance is
+%still reconstructable that the missing jet is likely from the decay of $W$ boson.
+%given the big chance that the jet which is missing is from $W$ decay.
 
@@
 
-Finally, the four-momenta of the invisible decay products for each $\tau$-lepton decay 
-are estimated from kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the the Higgs boson mass and the
+Finally, the four-momenta of the invisible decay products from the decay of di-taus 
+are estimated from a kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
 measured $\met$ within their expected resolutions.
 The resolution on the Higgs boson mass is taken to be $20~\gev$, respectively, while the resolution on the measured $\met$ is parameterised as a linear function of
-$\sqrt{\sum E_T}$, with $\sum E_T$ denoting the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
+$\sqrt{\sum E_T}$, where $\sum E_T$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
 After the $\chi^2$ minimisation, the Higgs boson four-momentum, and hence its invariant mass, as well as the 
-four-momentum of the parent top quark in the decay mode signal events, are determined with better resolution.
+four-momentum of the parent top quarks, are determined with better resolution in the signal events.
 
-Following the event kinematic reconstruction, several kinematic variables that discriminate between signal and background are defined.
-These variables are used in the multivariate analysis discussed in the next section.
+For the  $t_lt(qH)$ and $t_lH$ events where the $W$ boson from $t\to W b$ decays leptonically, there is a neutrino with large momentum and the flying direction is unknown.
+The kinematics fit is no longer feasible in the $t_l\hadhad$ and $t_l\had$ channels.
+The kinematic variables are calculated using the visible
+objects only.
 
-In the  $t_lt(qH)$ and $t_lH$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown.
+With the event topology reconstructed, a number of variables are defined for signal and background separation used in the multivariate analysis discussed below.
+
+%In the  $t_lt(qH)$ and $t_lH$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown.
 The kinematics fit is no longer feasible in the $t_l\hadhad$ channel.
@@
 %draft 1 version
-In the training, All signal events ($tt(qH)$ and $tH$ signal are merged together) are used either for $tHu$ or $tHc$  $q=c,u$ against the total SM background (including both real and fake $\had$ contributions).
+In the training, All signal events, $tt(qH)$ and $tH$ are merged together, are used for $tuH$ and $tcH$ against the total SM background (including both real and fake $\had$ contributions).
 
-A large set of potential variables were investigated in each SR separately.
-The discrimination of a given variable was quantified by the ``separation" and ``importance" measures provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 1\% were kept.
+A large set of potential variables are investigated in each SR separately.
+The discrimination of a given variable is quantified by the ``separation" and ``importance" measures provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 2\% were kept.
 The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_tthML}-~\ref{tab:importance_xTFW} and defined in the following:
@@
 \end{equation}
-\item $m_{\tau,\tau}$ is the invariant mass of the tau candidates and reconstructed neutrinos in $t_hH$, $t_ht(qH)$, and $t_l\had$ channels. 
+\item $m_{\tau,\tau}$ is the fitted invariant mass of the tau candidates and reconstructed neutrinos in the $t_hH$, $t_ht(qH)$ channels. 
 \item $m_{W}$ is the reconstructed invariant mass of the hadronic $W$ boson from SM top quark.
-\item $m_{t,FCNC}$ is the visible invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
-\item $m_{\tau\tau,vis}$ is the visible invariant mass of the di-tau candidates or the lepton and $\had$ candidate when there is only one $\had$.
+\item $m_{t,FCNC}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
+\item $m_{\tau\tau,vis}$ is the visible invariant mass of the di-tau candidates.
+  %or the lepton and $\had$ candidate when there is only one $\had$.
 \item $p_{T,\tau\tau,vis}$ is the $\pt$ of the di-tau candidates.
@@
 \end{itemize}
-A comparison between data and the predicted background for some of these variables in three main decay final states($t_l\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
-is shown in Figures~\ref{fig:mva_input_l2had_hadhad_lephad}.
+A comparison between data and the predicted background for the leading $\had$ $\pt$ in the SRs 
+%some of these variables in three main decay final states($t_l\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
+is shown in Figures~\ref{fig:taupt_postfit}.
 %each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_lhadhad}.
-The comparison between the data and predicted background after preselection for the distributions of two of the most 
-discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
-The expected signals (dashed red) are also shown after normalized to the total number of events un the predicted
+%The comparison between the data and predicted background after preselection for the distributions of two of the most 
+%discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
+The expected signals (dashed red) are also shown after normalized to the total number of events in the predicted
 background for the shape comparison of the distributions.   
@@
 
-The final observable used to extract signal events is defined as the BDT distribution in each SRs corresponding to either $tHu$ or $tHc$ signal training.
-Figure~\ref{fig:asimov_fitbdt_thu} and~\ref{fig:asimov_fitbdt_thc} show the fits to the data of BDT observable in each SRs with all background processes
+The final observable used to extract signal events is defined as the BDT distribution in each SRs corresponding to either $tuH$ or $tcH$ signal.
+Figure~\ref{fig:asimov_prefitbdt} show the prefits to the data of BDT observable in each SRs with all background processes
 constrained to the SM expectation.
@@
 %\input{\FCNCFigures/tex/BDTinput}
+\begin{figure}[H]
+\centering
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l2tau1bnj_os/tau_pt_0.pdf}
+\put(-130, 105){\small\textbf{(a1)}}
+%\put(-30, 80){\textbf{(a1)}}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
+\put(-130, 105){\small\textbf{(a2)}}
+%\put(-30, 80){\textbf{(a2)}}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
+\put(-130, 105){\small\textbf{(a3)}} 
+%\put(-70, 70){\textbf{(a3)}}
+\\
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
+\put(-30, 110){\small\textbf{(b1)}}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b3j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
+\put(-30, 110){\small\textbf{(b2)}}\\
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/tau_pt_0.pdf}
+\put(-30, 110){\small\textbf{(c1)}}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/tau_pt_0.pdf}
+\put(-30, 110){\small\textbf{(c2)}}\\
+\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),
+  $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2). Only statistical uncertainties are being shown (?). Underflow and overflow bins are included
+respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau
+contributions shown from ttbar and other MC including diboson, single top, and V+jets.}
+\label{fig:taupt_postfit}
+\end{figure}
 
 %\input{\FCNCFigures/tex/BDT}
+\begin{figure}[H]
+\centering
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l2tau1bnj_os/BDTG_test.pdf}
+\put(-30, 110){\small\textbf{(a1)}}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b1j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
+\put(-30, 110){\small\textbf{(a2)}}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
+\put(-30, 110){\small\textbf{(a3)}}\\
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf}
+\put(-30, 110){\small\textbf{(b1)}}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b3j_os_vetobtagwp70_highmet/BDTG_test.pdf}
+\put(-30, 110){\small\textbf{(b2)}}\\
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/BDTG_test.pdf}
+\put(-30, 110){\small\textbf{(c1)}}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/BDTG_test.pdf}
+\put(-30, 110){\small\textbf{(c2)}}\\
+\caption{ The BDT output distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),
+  $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2). Only statistical uncertainties are being shown (?). Underflow and overflow bins are included
+respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau
+contributions shown from ttbar and other MC including diboson, single top, and V+jets.}
+\label{fig:asimov_prefitbdt}
+\end{figure}

### 2021-11-08 sections/data_presel.tex
small typos

@@
 The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger.
-Further requirement are defined targeting different signal decay modes:
+Further requirements are defined targeting different signal decay modes:
 \begin{itemize}
@@
 
-The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and trailing $\had$ passed the trigger.
-The two $\had$ candidates are required to have charges of opposite sign.
+The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and trailing $\had$ passed the trigger. Further requirements are defined targeting signal decay modes:
+\begin{itemize}
+\item $t_h\hadhad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\hadhad$ decay. Exactly two $\had$ with opposite-sign charge are selected, including at least 3 jet with exactly one $b$-tagged jet.
+\end{itemize}
 

### 2021-11-08 sections/signal_background_modeling.tex

@@
 Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one $\had$.
-Since the fake rate of $\had$ candidate is much larger than electron or muon.
-So in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies.
+Since the fake rate of $\had$ candidate is much larger than electron or muon, in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies.
 However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, espcially to $t_l\had$ where the fake-lepton dominates.

### 2021-11-10 sections/signal_background_modeling.tex
modify the systematics and fix some typos

@@
 The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
-assuming an arbitrary branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=0.1\%$.
+assuming a benchmark branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=0.1\%$.
 The case of both top quarks decaying into $Hq$ is neglected in the analysis given the existing upper limits on $\BR(t \to Hq)$ (Section~\ref{sec:intro}).
@@
 The parton showers, hadronisation, and underlying event were modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
-Alternative $\ttbar$ simulation samples used to derive systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
+Alternative $\ttbar$ simulation samples used to derive parton shower systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
 The generated $\ttbar$ samples are normalised to a theoretical cross section of $832^{+46}_{-51}$~pb, 
@@
 Samples of single-top-quark events corresponding to the $t$-channel production mechanism were generated with the 
-{\powheg}~v1~\cite{Frederix:2012dh} generator, using the 4F scheme  for the NLO matrix-element calculations
-and the fixed 4F \textsc{CT10}f\textsc{4}~\cite{Lai:2010vv} PDF set.
+{\powheg}~v2~\cite{Frederix:2012dh} generator, using the 4F scheme  for the NLO matrix-element calculations
+and the corresponding NNPDF3.0 NLO set of PDFs.
 Samples corresponding to the $tW$- and $s$-channel production mechanisms were generated 
-with {\powheg}~v1 using the CT10 PDF set. Overlaps between the $\ttbar$ and $tW$ final states were avoided by using 
+with {\powheg}~v2 using the five-flavour scheme. Overlaps between the $\ttbar$ and $tW$ final states were avoided by using 
 the diagram removal scheme~\cite{Frixione:2005vw}.
-The parton showers, hadronisation and the underlying event were modelled using {\pythia}~6.428~\cite{Sjostrand:2006za} 
-with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set 
-in combination with the Perugia 2012 tune~\cite{Skands:2010ak}.
+The parton showers, hadronisation and the underlying event were modelled using {\pythia}~8.230~\cite{Sjostrand:2006za} using the A14 tune and the NNPDF2.3 LO PDF set.
+%with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set 
+%in combination with the Perugia 2012 tune~\cite{Skands:2010ak}.
 The single-top-quark samples are normalised to the approximate NNLO theoretical cross 

### 2021-11-10 sections/strategy_Htautau.tex
modify the systematics and fix some typos

@@
 The discrimination of a given variable is quantified by the ``separation" and ``importance" measures provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 2\% were kept.
-The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_tthML}-~\ref{tab:importance_xTFW} and defined in the following:
+The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_tthML} -~\ref{tab:importance_xTFW} and defined in the following:
 \begin{itemize}
@@
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l2tau1bnj_os/tau_pt_0.pdf}
-\put(-130, 105){\small\textbf{(a1)}}
+\put(-40, 90){\small\textbf{(a1)}}
 %\put(-30, 80){\textbf{(a1)}}
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
-\put(-130, 105){\small\textbf{(a2)}}
+\put(-40, 90){\small\textbf{(a2)}}
 %\put(-30, 80){\textbf{(a2)}}
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
-\put(-130, 105){\small\textbf{(a3)}} 
+\put(-40, 90){\small\textbf{(a3)}} 
 %\put(-70, 70){\textbf{(a3)}}
@@
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
-\put(-30, 110){\small\textbf{(b1)}}
+\put(-40, 90){\small\textbf{(b1)}}
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b3j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
-\put(-30, 110){\small\textbf{(b2)}}\\
+\put(-40, 90){\small\textbf{(b2)}}\\
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/tau_pt_0.pdf}
-\put(-30, 110){\small\textbf{(c1)}}
+\put(-40, 90){\small\textbf{(c1)}}
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/tau_pt_0.pdf}
-\put(-30, 110){\small\textbf{(c2)}}\\
+\put(-40, 90){\small\textbf{(c2)}}\\
 \caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),
@@
 respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau
-contributions shown from ttbar and other MC including diboson, single top, and V+jets.}
+contributions shown from $t\bar{t}$, Ztautau and other MC including diboson, single top, and V+jets.}
 \label{fig:taupt_postfit}
@@
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l2tau1bnj_os/BDTG_test.pdf}
-\put(-30, 110){\small\textbf{(a1)}}
+\put(-40, 90){\small\textbf{(a1)}}
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b1j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
-\put(-30, 110){\small\textbf{(a2)}}
+\put(-40, 90){\small\textbf{(a2)}}
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
-\put(-30, 110){\small\textbf{(a3)}}\\
+\put(-40, 90){\small\textbf{(a3)}}\\
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf}
-\put(-30, 110){\small\textbf{(b1)}}
+\put(-40, 90){\small\textbf{(b1)}}
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b3j_os_vetobtagwp70_highmet/BDTG_test.pdf}
-\put(-30, 110){\small\textbf{(b2)}}\\
+\put(-40, 90){\small\textbf{(b2)}}\\
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/BDTG_test.pdf}
-\put(-30, 110){\small\textbf{(c1)}}
+\put(-40, 90){\small\textbf{(c1)}}
 \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/BDTG_test.pdf}
-\put(-30, 110){\small\textbf{(c2)}}\\
+\put(-40, 90){\small\textbf{(c2)}}\\
 \caption{ The BDT output distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),
@@
 respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau
-contributions shown from ttbar and other MC including diboson, single top, and V+jets.}
+contributions shown from $t\bar{t}$ and other MC including diboson, single top, and V+jets.}
 \label{fig:asimov_prefitbdt}

### 2021-11-10 sections/systematic_uncertainties.tex
modify the systematics and fix some typos

@@
 
-A number of sources of systematic uncertainty affecting the modelling of $t\bar{t}$+jets are considered. 
-An uncertainty of  6\% is assigned to the inclusive $\ttbar$ production
-cross section~\cite{Czakon:2011xx}, including contributions from varying the factorisation and renormalisation 
-scales, as well as from the top-quark mass, the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution 
-to the overall theoretical uncertainty in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
-with the NNPDF3.0(NLO), CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3(LO) 5F FFN~\cite{Ball:2012cx} PDF sets.
+A number of sources of systematic uncertainty affecting the modelling of $t\bar{t}$+jets are considered: the choice of the renormalisation and factorisation scale in the matrix-element calculation, the choice of the matching scale when matching the matrix elements to the parton show generator, the uncertainty in the value of $\alpha_s$ when modeling intial-state radiation (ISR), the choice of the renormalisation scale when modeling final-state radiation (FSR).
+%%An uncertainty of  6\% is assigned to the inclusive $\ttbar$ production
+%%cross section~\cite{Czakon:2011xx}, including contributions from varying the factorisation and renormalisation 
+%%scales, as well as from the top-quark mass, the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution 
+%%to the overall theoretical uncertainty in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
+%%with the NNPDF3.0(NLO), CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3(LO) 5F FFN~\cite{Ball:2012cx} PDF sets.
+
 The hdamp parameter (which controls the amount of radiation produced by the parton shower in
@@
 
-Uncertainties affecting the normalisation of the $V$+jets background are estimated for the sum
-of $W$+jets and $Z$+jets, and separately for $V$+light-jets, $V$+$\geq$1$c$+jets, and $V$+$\geq$1$b$+jets subprocesses.
-The total normalisation uncertainty of $V$+jets processes is estimated by comparing the data and total background prediction in 
-the different analysis regions considered, but requiring exactly zero $b$-tagged jets.
+Another significancant background in hadronic channel stems from the ztautau samples, several sources of uncertainty are considered for these samples: 
+the PDF variation considering the standarnd deviation of the 100 NNPDF replicas event weights of NNPDF3.0nnlo PDF set used in Sherpa, renormalisation($\mu_{R}$) and factorisation scales($\mu_{F}$),jet-to-parton matching uncertainty,resummation scale uncertainty, variation in the choice of $\alpha_{S}$, alternative PDF variation evalatued comparing predictions from NNPDF3.0nnlo PDF set (nominal) with MMHT2014nnlo68cl and CT14nnlo PDF sets.
+
+%%Uncertainties affecting the normalisation of the $V$+jets background are estimated for the sum
+%%of $W$+jets and $Z$+jets, and separately for $V$+light-jets, $V$+$\geq$1$c$+jets, and $V$+$\geq$1$b$+jets subprocesses.
+%%The total normalisation uncertainty of $V$+jets processes is estimated by comparing the data and total background prediction in 
+%%the different analysis regions considered, but requiring exactly zero $b$-tagged jets.
 %Agreement between data and predicted background 
@@
 
-Uncertainties affecting the modelling of the single-top-quark background include a 
-$+5\%$/$-4\%$ uncertainty of the total cross section estimated as a weighted average 
-of the theoretical uncertainties in $t$-, $tW$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
-Additional uncertainties associated with the modelling of additional radiation are assessed by comparing the nominal
-samples with alternative samples where generator parameters are varied.
-For the $t$- and $tW$-channel processes, an uncertainty due to the choice of parton shower and hadronisation model is derived 
-by comparing events produced by {\powheg} interfaced to {\pythia}~8 or {\herwigpp}.
-These uncertainties are treated as fully correlated among single-top-quark production processes, but uncorrelated with the
-corresponding uncertainty of the $\ttbar$+jets background.
-An additional systematic uncertainty in $tW$-channel production concerning the separation 
-between $t\bar{t}$ and $tW$ at NLO is assessed by comparing
-the nominal sample, which uses the diagram removal scheme~\cite{Frixione:2008yi}, with an alternative sample
-using the diagram subtraction scheme~\cite{Frixione:2008yi}.
+To estimate the uncertainty originating from ISR modelling in the single top samples, the same procedure as $t\bar{t}$ is used.
+One NP reflects the symmetrised effect of the two shower variations Var3cDown and Var3cUp, and the other NP with name ``scale'' describe the symmetrised effect from the independent variations of the renormalisation and factorisation scale.
+The impact of the uncertainty from FSR modelling is estimated by reweighting the nominal single top sample.
+The two variations $\mu^{FSR}_{R} \times 0.5$ and $\mu^{FSR}_{R} \times 2$ are considered.
+The standard deviation of 100 NNPDF3.0nnlo variations is calculated Uncertainties on the PDF are evaluated following the recommended prescription in Ref.~\cite{ttRun2}.
 
-Uncertainties of the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah,Campbell:2011bn},
-as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
-comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}
-(it is assumed that two jets originate from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
-Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the selected jet multiplicity,  
-resulting in 34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively. 
-Recent comparisons between data and {\sherpa}~2.1.1 for $WZ(\to \ell\nu\ell\ell) + \geq$4 jets show
-agreement within the experimental uncertainty of approximately 40\%~\cite{Aaboud:2016yus}, which further justifies the above uncertainty.
-Given the very small contribution of this background to the total prediction, the final result is not affected by the assumed modelling
-uncertainties.
+The values of the scale-parameters $\mu_{f}$ and $\mu_{f}$ are varied by factors of 2.0 and 0.5 with respect to their default values to obtain the uncertainties related to the renormalization and factorization scales in ttV samples.
+Uncertainties on the PDF are evaluated following the same procedure in Ref.~\cite{ttZRun2}.
 
-Uncertainties of the $\ttbar V$ and $\ttbar H$ cross sections are 15\% and $+10\%$/$-13\%$, respectively,
-from the uncertainties of their respective NLO theoretical cross sections~\cite{Campbell:2012dh,Garzelli:2012bn,deFlorian:2016spz}.
+Following the recommendations of the PMG group, the uncertainties to be considered for diboson background include~\cite{dibosonRes} scale variations of the renormalization and factorization scale,
+PDF variations and $\alpha_{S}$ variations.
+
+A $+5.8\%-9.2\%$ normalization uncertainty is considered for the ttH background, corresponding to the scale and $\alpha_{S}$ uncertainties in the NLO cross-section computation.
+A constant PDF uncertainty of $\pm3.6$\% is assumed, as it was done for the previous measurement.
+Therefore, a overall sytematics with variation 9\% is entered in the final fit model~\cite{ttZRun2}.
+
+%%%Uncertainties affecting the modelling of the single-top-quark background include a 
+%%%$+5\%$/$-4\%$ uncertainty of the total cross section estimated as a weighted average 
+%%%of the theoretical uncertainties in $t$-, $tW$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
+%%%Additional uncertainties associated with the modelling of additional radiation are assessed by comparing the nominal
+%%%samples with alternative samples where generator parameters are varied.
+%%%For the $t$- and $tW$-channel processes, an uncertainty due to the choice of parton shower and hadronisation model is derived 
+%%%by comparing events produced by {\powheg} interfaced to {\pythia}~8 or {\herwigpp}.
+%%%These uncertainties are treated as fully correlated among single-top-quark production processes, but uncorrelated with the
+%%%corresponding uncertainty of the $\ttbar$+jets background.
+%%%An additional systematic uncertainty in $tW$-channel production concerning the separation 
+%%%between $t\bar{t}$ and $tW$ at NLO is assessed by comparing
+%%%the nominal sample, which uses the diagram removal scheme~\cite{Frixione:2008yi}, with an alternative sample
+%%%using the diagram subtraction scheme~\cite{Frixione:2008yi}.
+
+%%%%Uncertainties of the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah,Campbell:2011bn},
+%%%%as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
+%%%%comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}
+%%%%(it is assumed that two jets originate from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
+%%%%Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the selected jet multiplicity,  
+%%%%resulting in 34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively. 
+%%%%Recent comparisons between data and {\sherpa}~2.1.1 for $WZ(\to \ell\nu\ell\ell) + \geq$4 jets show
+%%%%agreement within the experimental uncertainty of approximately 40\%~\cite{Aaboud:2016yus}, which further justifies the above uncertainty.
+%%%%Given the very small contribution of this background to the total prediction, the final result is not affected by the assumed modelling
+%%%%uncertainties.
+%%%%
+%%%%Uncertainties of the $\ttbar V$ and $\ttbar H$ cross sections are 15\% and $+10\%$/$-13\%$, respectively,
+%%%%from the uncertainties of their respective NLO theoretical cross sections~\cite{Campbell:2012dh,Garzelli:2012bn,deFlorian:2016spz}.
 
@@
 following the recommendation in Ref.~\cite{deFlorian:2016spz}.
-The uncertainty of ISR, FSR and PDF are treated correlatedly with $\ttbar$ samples.
+The uncertainty of ISR, FSR, scale and PDF are considered in all SRs.
 The parton shower uncertainties is estimated by comparing the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}.
+%treated correlatedly with $\ttbar$ samples.

### 2021-11-11 sections/strategy_Htautau.tex
updating the limit of Wilson coefficients

@@
 
-The analysis strategy adopted in the $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more signal channels.
+The analysis strategy adopted in the $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more search channels.
 
@@
 resulting in some signal events mixed with production mode having only three reconstructed jets.
-In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs based on the number of light lepton and
+In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs based on the number of light leptons,
 $\had$ candidates, and on the number of light flavored jets:
@@
 Finally, the four-momenta of the invisible decay products from the decay of di-taus 
-are estimated from a kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
+are estimated using a kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
 measured $\met$ within their expected resolutions.
@@
 The discrimination of a given variable is quantified by the ``separation" and ``importance" measures provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 2\% were kept.
-The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_tthML} -~\ref{tab:importance_xTFW} and defined in the following:
+The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_tthML} and~\ref{tab:importance_xTFW} and defined in the following:
 \begin{itemize}
@@
 \item $\Delta R(l,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
-\item $\Delta R(\tau,qjet)$ is the angular distance between the tau and the reconstructed $q$-jet.
+\item $\Delta R(\tau,qjet)$ is the angular distance between the tau and the reconstructed $q$-jet. If there are two taus in the event, the leading one is used.
 \item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(l,\tau)$.
@@
 %discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
-The expected signals (dashed red) are also shown after normalized to the total number of events in the predicted
-background for the shape comparison of the distributions.   
+The expected signals (dashed) are also shown after scaled up for the shape comparison of the distributions.
+%by a large factor normalized to the total number of events in the predicted
+%background for the shape comparison.   
 %corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.

### 2021-11-11 sections/systematic_uncertainties.tex
updating the limit of Wilson coefficients

@@
 
-Another significancant background in hadronic channel stems from the ztautau samples, several sources of uncertainty are considered for these samples: 
-the PDF variation considering the standarnd deviation of the 100 NNPDF replicas event weights of NNPDF3.0nnlo PDF set used in Sherpa, renormalisation($\mu_{R}$) and factorisation scales($\mu_{F}$),jet-to-parton matching uncertainty,resummation scale uncertainty, variation in the choice of $\alpha_{S}$, alternative PDF variation evalatued comparing predictions from NNPDF3.0nnlo PDF set (nominal) with MMHT2014nnlo68cl and CT14nnlo PDF sets.
+Another significancant background in hadronic channel stems from the $Z\rightarrow \tau\tau$ samples, several sources of uncertainty are
+considered for these samples: the PDF variation considering the standarnd deviation of the 100 NNPDF replicas event weights of NNPDF3.0nnlo PDF
+set used in Sherpa, renormalisation($\mu_{R}$) and factorisation scales($\mu_{F}$),jet-to-parton matching uncertainty,resummation scale uncertainty,
+variation in the choice of $\alpha_{S}$, alternative PDF variation evalatued comparing predictions from NNPDF3.0nnlo PDF set (nominal)
+with MMHT2014nnlo68cl and CT14nnlo PDF sets.
 
-%%Uncertainties affecting the normalisation of the $V$+jets background are estimated for the sum
-%%of $W$+jets and $Z$+jets, and separately for $V$+light-jets, $V$+$\geq$1$c$+jets, and $V$+$\geq$1$b$+jets subprocesses.
-%%The total normalisation uncertainty of $V$+jets processes is estimated by comparing the data and total background prediction in 
-%%the different analysis regions considered, but requiring exactly zero $b$-tagged jets.
+Uncertainties affecting the normalisation of the $V$+jets background are estimated separately for $V$+light-jets, $V$+$\geq$1$c$+jets,
+and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated within approximately 30\% by comparing the
+data and total background prediction in the different analysis regions considered, but requiring exactly zero $b$-tagged jets.
 %Agreement between data and predicted background 
@@
 
-To estimate the uncertainty originating from ISR modelling in the single top samples, the same procedure as $t\bar{t}$ is used.
+%To estimate the uncertainty originating from ISR modelling in the single top samples, the same procedure as $t\bar{t}$ is used.
 One NP reflects the symmetrised effect of the two shower variations Var3cDown and Var3cUp, and the other NP with name ``scale'' describe the symmetrised effect from the independent variations of the renormalisation and factorisation scale.
@@
 
-The values of the scale-parameters $\mu_{f}$ and $\mu_{f}$ are varied by factors of 2.0 and 0.5 with respect to their default values to obtain the uncertainties related to the renormalization and factorization scales in ttV samples.
+%The values of the scale-parameters $\mu_{f}$ and $\mu_{f}$ are varied by factors of 2.0 and 0.5 with respect to their default values to obtain the uncertainties related to the renormalization and factorization scales in ttV samples.
 Uncertainties on the PDF are evaluated following the same procedure in Ref.~\cite{ttZRun2}.
 
-Following the recommendations of the PMG group, the uncertainties to be considered for diboson background include~\cite{dibosonRes} scale variations of the renormalization and factorization scale,
-PDF variations and $\alpha_{S}$ variations.
+%Following the recommendations of the PMG group, the uncertainties to be considered for diboson background include~\cite{dibosonRes} scale variations of the renormalization and factorization scale,
+%PDF variations and $\alpha_{S}$ variations.
 
-A $+5.8\%-9.2\%$ normalization uncertainty is considered for the ttH background, corresponding to the scale and $\alpha_{S}$ uncertainties in the NLO cross-section computation.
+%A $+5.8\%-9.2\%$ normalization uncertainty is considered for the ttH background, corresponding to the scale and $\alpha_{S}$ uncertainties in the NLO cross-section computation.
 A constant PDF uncertainty of $\pm3.6$\% is assumed, as it was done for the previous measurement.
@@
 
-%%%Uncertainties affecting the modelling of the single-top-quark background include a 
-%%%$+5\%$/$-4\%$ uncertainty of the total cross section estimated as a weighted average 
-%%%of the theoretical uncertainties in $t$-, $tW$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
-%%%Additional uncertainties associated with the modelling of additional radiation are assessed by comparing the nominal
+Uncertainties affecting the modelling of the single-top-quark background include a 
+$+5\%$/$-4\%$ uncertainty of the total cross section estimated as a weighted average 
+of the theoretical uncertainties in $t$-, $tW$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
+Additional uncertainties associated with the parton shower, hadronisation and ISR/FSR radiations are also considered using the same procedure
+as in $t\bar t$.
+%by comparing the nominal
 %%%samples with alternative samples where generator parameters are varied.
@@
 
-%%%%Uncertainties of the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah,Campbell:2011bn},
-%%%%as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
-%%%%comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}
+Uncertainties of the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah,Campbell:2011bn},
+as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
+comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}.
 %%%%(it is assumed that two jets originate from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
@@
 %%%%
-%%%%Uncertainties of the $\ttbar V$ and $\ttbar H$ cross sections are 15\% and $+10\%$/$-13\%$, respectively,
-%%%%from the uncertainties of their respective NLO theoretical cross sections~\cite{Campbell:2012dh,Garzelli:2012bn,deFlorian:2016spz}.
+Uncertainties of the $\ttbar V$ and $\ttbar H$ cross sections are 15\% and $+10\%$/$-13\%$, respectively,
+from the uncertainties of their respective NLO theoretical cross sections~\cite{Campbell:2012dh,Garzelli:2012bn,deFlorian:2016spz}.
 

### 2021-11-14 sections/strategy_Htautau.tex
modify some plots

--- 2021-11-10 sections/strategy_Htautau.tex
@@
 \centering
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l2tau1bnj_os/tau_pt_0.pdf}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf}
 \put(-40, 90){\small\textbf{(a1)}}
 %\put(-30, 80){\textbf{(a1)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
 \put(-40, 90){\small\textbf{(a2)}}
 %\put(-30, 80){\textbf{(a2)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
 \put(-40, 90){\small\textbf{(a3)}} 
@@
 \\
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
 \put(-40, 90){\small\textbf{(b1)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b3j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b3j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
 \put(-40, 90){\small\textbf{(b2)}}\\
@@
 \centering
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l2tau1bnj_os/BDTG_test.pdf}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/BDTG_test.pdf}
 \put(-40, 90){\small\textbf{(a1)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b1j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
 \put(-40, 90){\small\textbf{(a2)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
 \put(-40, 90){\small\textbf{(a3)}}\\
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf}
 \put(-40, 90){\small\textbf{(b1)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL/reg1l1tau1b3j_os_vetobtagwp70_highmet/BDTG_test.pdf}
+\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b3j_os_vetobtagwp70_highmet/BDTG_test.pdf}
 \put(-40, 90){\small\textbf{(b2)}}\\

### 2021-11-14 sections/introduction.tex

--- 2021-09-21 sections/introduction.tex
@@
 the SM.
-The assumption of using SM-like Higgs boson branching ratios is motivated by the fact that measurements of the flavour-diagonal Higgs boson couplings by the ATLAS and CMS collaborations are in agreement with the SM prediction within about 10\%~\cite{Khachatryan:2016vau,Sirunyan:2018koj}.
+%The assumption of using SM-like Higgs boson branching ratios is motivated by the fact that measurements of the flavour-diagonal Higgs boson couplings by the ATLAS and CMS collaborations are in agreement with the SM prediction within about 10\%~\cite{Khachatryan:2016vau,Sirunyan:2018koj}.
 %Furthermore, typical beyond-the-SM scenarios that predict significant enhancements to $\BR(t\to Hq)$, also predict modifications to the Higgs boson branching ratios at the few percent level or below, well beyond the current experimental precision.
@@
 $H \to  WW^*, ZZ^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically~\cite{Aaboud:2018pob},
-$\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36}, and of $\BR(t\to cH)<0.19\%$ using $H\to tau\bar{tau}$ decay in which at least
+$\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36}, and of $\BR(t\to cH)<0.19\%$ using $H\to \tau\bar{\tau}$ decay in which at least
 one of $\tau$-leptons decays hadronically~\cite{fcnc36}.  
@@
 %The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
+
 This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
@@
 Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted and the signals are divided into several final states depending on the production modes and
-the  $W$ boson decay either hadronically or leptonically from the $t\rightarrow Wb$ decay referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
+the  $W$ boson decay either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
 $t_l$ when the $\tau$ decays into a light lepton(electron or muon) as $\tau_{lep}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
-The $H\rightarrow \tau\tau$ decay is detected to be in
+The $H\rightarrow \tau\tau$ decay is detected in
 either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
@@
 Events with at least one \tauhad with an additional electron or muon are selected as the leptonic channels.
-More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data as well as
-various $t\bar{t}$ control regions (CRtt) used for calibration of tau fakes in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
+More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data and more
+$t\bar{t}$ control regions (CRtt) are used for calibration of tau fakes in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
 
-Multivariate technique is used to discriminate between the signal and the background on the basis of their different kinematics.
+Finally, multivariate technique is used to discriminate between the signal and the background on the basis of their different kinematics.
 

### 2021-11-14 sections/objects.tex

@@
 used to increase the precision of identifying the displaced decay vertex of heavy flavor (b, c) hadrons that produced non-prompt leptons.
-The tight working points are: \texttt{PLIV}$<-0.6734$ for high $\pt$ muons and \texttt{PLIV}$<-0.704$ for hight $\pt$ barrel electrons.
+The tight working points are used for high $\pt$ lepton.
 The scale factors for the efficiencies of the tight \texttt{PLIV} working points are measured using the tag and probe method
@@
 Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
-Any $\had$ candidate that is also $b$-tagged is rejected.
+Events with$\had$ candidate that is $b$-tagged are rejected.
 %(TBD: check RNN description and update then numbers)
@@
 In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
-is discarded if the jet is not $b$-tagged, otherwise the electron is remived.
+is discarded if the jet is not $b$-tagged, otherwise the electron is removed.
 If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.

### 2021-11-15 sections/systematic_uncertainties.tex
update sys cahpter

@@
 
-Uncertainties affecting the normalisation of the $V$+jets background are estimated separately for $V$+light-jets, $V$+$\geq$1$c$+jets,
-and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated within approximately 30\% by comparing the
-data and total background prediction in the different analysis regions considered, but requiring exactly zero $b$-tagged jets.
+%%Uncertainties affecting the normalisation of the $V$+jets background are estimated separately for $V$+light-jets, $V$+$\geq$1$c$+jets,
+%%and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated within approximately 30\% by comparing the
+%%data and total background prediction in the different analysis regions considered, but requiring exactly zero $b$-tagged jets.
 %Agreement between data and predicted background 
@@
 as in $t\bar t$.
+Uncertainties of the diboson background normalisation include variations of the renormalization and factorization scale, NNPDF3.0nnlo variations and $\alpha_{S}$ variations.
+Uncertainties of the $\ttbar V$ and $\ttbar H$ cross sections are 12\% and $+5.8\%-9.2\%$, respectively,
+from the uncertainties of their respective NLO theoretical cross sections~\cite{ttZRun2}.
+
 %by comparing the nominal
@@
 
-Uncertainties of the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah,Campbell:2011bn},
-as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
-comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}.
 %%%%(it is assumed that two jets originate from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
@@
 %%%%
-Uncertainties of the $\ttbar V$ and $\ttbar H$ cross sections are 15\% and $+10\%$/$-13\%$, respectively,
-from the uncertainties of their respective NLO theoretical cross sections~\cite{Campbell:2012dh,Garzelli:2012bn,deFlorian:2016spz}.
 

### 2021-11-15 sections/conclusion.tex
minor update

@@
 
-A search for flavour-changing neutral current $tHq$ interections with a top quark,	an up-type quark ($q=u, c$), and the
+A search for flavour-changing neutral current $tqH$ interections with a top quark,	an up-type quark ($q=u, c$), and the
 Standard Model Higgs boson is presented. The Higgs boson decay to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
@@
 Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
-which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow Hq$.
+which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow qH$.
 The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
@@
 Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
-No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
-Observed (expected) 95\% CL upper limits are set on the $t\to Hc$ and $t\to Hu$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$)
+No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
+Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$)
 and XXX ($0.034^{+0.014}_{-0.012}\%$), respectively.

### 2021-11-15 sections/signal_background_modeling.tex
minor update

@@
 The templates are aquired by subtracting all MC background contributions with real sub-leading taus from data. The FFs are computed as
-the ratio of the Data$-$MC$_\mathrm{real~tau}$ yields passing the medium tau ID to which failing the medium tau ID from different control regions and
+the ratio of the Data-MC($\mathrm{real~tau}$) yields passing the medium tau ID to which failing the medium tau ID from different control regions and
 the differences are treated as part of systematics.

### 2021-11-15 sections/systematic_uncertainties.tex
minor update

@@
 
-%%Uncertainties affecting the normalisation of the $V$+jets background are estimated separately for $V$+light-jets, $V$+$\geq$1$c$+jets,
-%%and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated within approximately 30\% by comparing the
-%%data and total background prediction in the different analysis regions considered, but requiring exactly zero $b$-tagged jets.
+Uncertainties affecting the normalisation of the $V$+jets background are estimated separately for $V$+light-jets, $V$+$\geq$1$c$+jets,
+and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated within approximately 30\% by comparing the
+data and total background prediction in the different analysis regions considered, but requiring exactly zero $b$-tagged jets.
 %Agreement between data and predicted background 

### 2021-11-16 ANA-TOPQ-2019-17-PAPER-metadata.tex
minor update
fix spelling

@@
 
-A search for flavour-changing neutral current $tqH$ interections with a top quark, an up-type quark ($q=u, c$), and the
-Standard Model Higgs boson is presented. The Higgs boson decay to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
+A search for flavour-changing neutral current $tqH$ interactions with a top quark, an up-type quark ($q=u, c$), and the
+Standard Model Higgs boson is presented. The Higgs boson decays to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
-CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
+CERN Large Hadron Collider and corresponds to an integrated luminosity of 139 fb$^{-1}$.
 Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
@@
 % Comment deadline
-\AtlasCoverCommentsDeadline{1 November 2021}
+\AtlasCoverCommentsDeadline{1 January 2022}
 

### 2021-11-16 sections/conclusion.tex
fix spelling

@@
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the
-CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
+CERN Large Hadron Collider and corresponds to an integrated luminosity of 139 fb$^{-1}$.
 Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in

### 2021-11-16 sections/data_presel.tex
fix spelling

@@
 \item $t_l\hadhad$: Targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-tagged jet.
-\item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identificaiton so that there is only
+\item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identification so that there is only
   one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-tagged jet.

### 2021-11-16 sections/signal_background_modeling.tex
fix spelling

@@
 Since the fake rate of $\had$ candidate is much larger than electron or muon, in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies.
-However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, espcially to $t_l\had$ where the fake-lepton dominates.
+However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, especially to $t_l\had$ where the fake-lepton dominates.
 %and the jet multiplicity is low.
@@
 lepton and fake tau charges, then the scale factors are multiplied together. The nominal value of the scale factors will vary along with other uncertainties from
-combined preformace (CP) recommendations and theory uncertainties in the final fit.
+combined performance (CP) recommendations and theory uncertainties in the final fit.
 %In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
@@
 The events with fake trailing $\had$ candidate can be calculated by rescaling the templates of fake taus in the Fake-CR with proper fake factors (FF).
-The templates are aquired by subtracting all MC background contributions with real sub-leading taus from data. The FFs are computed as
+The templates are acquired by subtracting all MC background contributions with real sub-leading taus from data. The FFs are computed as
 the ratio of the Data-MC($\mathrm{real~tau}$) yields passing the medium tau ID to which failing the medium tau ID from different control regions and

### 2021-11-16 sections/strategy_Htautau.tex
minor update
fix spelling

@@
 \begin{table*}[t!]
+\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for leptonic channel.
+    The description of each variable is provided in the text.}}
+\label{tab:importance_tthML}
+\input{\FCNCTables/Importance/tthML/Merged}
+\end{table*}
+
+\begin{table*}[t!]
 \caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for hadronic channel. 
@@
 
-\begin{table*}[t!]
-\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for leptonic channel. 
-    The description of each variable is provided in the text.}}
-\label{tab:importance_tthML}
-\input{\FCNCTables/Importance/tthML/Merged}
-\end{table*}
 %%%%%%%%%%%%%%%
@@
 \item $m_{t,SM,vis}$ is the invariant mass of the lepton and the b-jet, which reflects the visible SM top mass.
-\item $M(\tau\tau qjet,min)$ is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative of variable $m_{t,FCNC,vis}$.
+\item $M(\tau\tau qjet,min)$ is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant mass of the visible FCNC top decaying product, an alternative of variable $m_{t,FCNC,vis}$.
 \item $M(wjet1,wjet2,min)$ is the invariant mass of two light-flavor jet, minimized by choosing different jets, reflects the invariant mass of the W candidate, an alternative of $m_{W}$.

### 2021-11-16 sections/systematic_uncertainties.tex
fix spelling

@@
 The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pile-up treatment, 
-is split into 43 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}. The total JES uncertianty is
+is split into 43 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}. The total JES uncertainty is
 below 5\% for most jets and below 1\% for central jets with pT between 300 GeV and 2 TeV. The difference between the JER
@@
 
-A number of sources of systematic uncertainty affecting the modelling of $t\bar{t}$+jets are considered: the choice of the renormalisation and factorisation scale in the matrix-element calculation, the choice of the matching scale when matching the matrix elements to the parton show generator, the uncertainty in the value of $\alpha_s$ when modeling intial-state radiation (ISR), the choice of the renormalisation scale when modeling final-state radiation (FSR).
+A number of sources of systematic uncertainty affecting the modelling of $t\bar{t}$+jets are considered: the choice of the renormalisation and factorisation scale in the matrix-element calculation, the choice of the matching scale when matching the matrix elements to the parton show generator, the uncertainty in the value of $\alpha_s$ when modeling initial-state radiation (ISR), the choice of the renormalisation scale when modeling final-state radiation (FSR).
 %%An uncertainty of  6\% is assigned to the inclusive $\ttbar$ production
@@
 
-Another significancant background in hadronic channel stems from the $Z\rightarrow \tau\tau$ samples, several sources of uncertainty are
-considered for these samples: the PDF variation considering the standarnd deviation of the 100 NNPDF replicas event weights of NNPDF3.0nnlo PDF
+Another significant background in hadronic channel stems from the $Z\rightarrow \tau\tau$ samples, several sources of uncertainty are
+considered for these samples: the PDF variation considering the standard deviation of the 100 NNPDF replicas event weights of NNPDF3.0nnlo PDF
 set used in Sherpa, renormalisation($\mu_{R}$) and factorisation scales($\mu_{F}$),jet-to-parton matching uncertainty,resummation scale uncertainty,
-variation in the choice of $\alpha_{S}$, alternative PDF variation evalatued comparing predictions from NNPDF3.0nnlo PDF set (nominal)
+variation in the choice of $\alpha_{S}$, alternative PDF variation evaluated comparing predictions from NNPDF3.0nnlo PDF set (nominal)
 with MMHT2014nnlo68cl and CT14nnlo PDF sets.
@@
 A constant PDF uncertainty of $\pm3.6$\% is assumed, as it was done for the previous measurement.
-Therefore, a overall sytematics with variation 9\% is entered in the final fit model~\cite{ttZRun2}.
+Therefore, a overall systematics with variation 9\% is entered in the final fit model~\cite{ttZRun2}.
 

### 2022-01-19 ANA-TOPQ-2019-17-PAPER-metadata.tex
solve the commets

--- 2021-09-21 ANA-TOPQ-2019-17-PAPER-metadata.tex
@@
 % Comment or remove in final version.
-\AtlasVersion{0.1}
+\AtlasVersion{0.2}
 % Abstract - % directly after { is important for correct indentation
@@
 
-A search for flavour-changing neutral current $tqH$ interections with a top quark, an up-type quark ($q=u, c$), and the
-Standard Model Higgs boson is presented. The Higgs boson decay to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
+A search for flavour-changing neutral current $tqH$ interections with a top quark, an up-type quark ($q=u, c$), and a
+Standard Model Higgs boson is presented. The Higgs boson decays into a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
@@
 No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
-Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$) 
-and XXX ($0.034^{+0.014}_{-0.012}\%$), respectively.
+Observed (expected) 95\% CL upper limits are set on the $t\to Hc$ and $t\to Hu$ branching ratios of $0.099\%$ ($0.050^{+0.022}_{-0.014}\%$)
+and $0.072\%$ ($0.036^{+0.017}_{-0.010}\%$), respectively.}
 %The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
 %These are the most restrictive direct bounds on $tqH$ interactions obtained so far.
-}
+%}
 
@@
 % Submission journal and final reference
-\AtlasJournal{JHEP}
+
 % \AtlasJournal{Phys.\ Lett.\ B.}
@@
  \AtlasCoverEdBoardMember{Edson Carquin Lopez}
- \AtlasCoverEdBoardMember{Luca Fiorini}
  \AtlasCoverEdBoardMember{Michele Weber}
@@
 \AtlasCoverEgroupEdBoard{atlas-TOPQ-2019-17-editorial-board@cern.ch}
+
+\AtlasJournal{JHEP}

### 2022-01-19 sections/conclusion.tex
solve the commets

--- 2021-11-15 sections/conclusion.tex
@@
 
-A search for flavour-changing neutral current $tqH$ interections with a top quark,	an up-type quark ($q=u, c$), and the
-Standard Model Higgs boson is presented. The Higgs boson decay to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
-The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the
-CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
-Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
-which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow qH$.
-The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
-as well as multiple jets.
-Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
-No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
-Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$)
-and XXX ($0.034^{+0.014}_{-0.012}\%$), respectively.
+A search for flavour-changing neutral current process involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented.
+FCNC $tqH$ interaction is searched for both in $t\bar{t}$ decay mode, where one top quark decays following SM processes and the other one decays through $t\rightarrow Hq$, and in production mode($pp\rightarrow tH$) with a single top quark produced via FCNC interaction, while the decay according to SM.
+The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
+The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$), a b-tagged jet as well as multiple jets.Multivariate techniques based on BDT are used to distinguish the signal from the background on the basis of their different kinematics.
+
+Although no significant excess of events above the background expectation is found, about a factor of 2 improvement to 95\% CL upper limits on the $t\to Hq$ branching ratios are reported in Tab~\ref{tab:limits_summary}, along with the Wilson coefficients with respect to the previous partial run-2 results~\cite{Aaboud2019SearchFT}.
+Observed (expected) 95\% CL upper limits are set on the $t\to Hc$ and $t\to Hu$ branching ratios of $9.9\times10^{-4}$ ($5.0^{+2.2}_{-1.4}\times10^{-4}$) and $7.2\times10^{-4}$ ($3.6^{+1.7}_{-1.0}\times10^{-4}$).
+The observed (expected) upper limits on the D6 Wilson coefficients from the combination of the searches are $C_{c\phi}<1.38\,(0.97)$ and $C_{u\phi}<1.18\,(0.83)$, respectively.

### 2022-01-19 sections/detector.tex
solve the commets

@@
 terms of the polar angle $\theta$ as $\eta = - \ln \tan(\theta/2)$.
-Angular distance is measured in units of $\Delta R\equiv \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.} and
-consists of an inner tracking detector surrounded by a thin superconducting solenoid producing a
-2~T axial magnetic field, electromagnetic and hadronic calorimeters, and a muon spectrometer
-incorporating three large toroid magnet assemblies with eight coils each. The inner detector contains a high-granularity silicon pixel detector, 
-including the %newly-installed
-insertable B-layer~\cite{IBL1,IBL2,Abbott:2018ikt}, installed in 2014,
-and a silicon microstrip tracker,
-together providing a precise reconstruction of tracks of charged particles in the pseudorapidity range $|\eta|<2.5$.
+Angular distance is measured in units of $\Delta R\equiv \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.} and consists of an inner tracking detector surrounded by a thin superconducting solenoid producing a
+2~T axial magnetic field, electromagnetic and hadronic calorimeters, and a muon spectrometer incorporating three large toroid magnet assemblies with eight coils each.
+The inner detector contains a high-granularity silicon pixel detector, including the %newly-installed
+insertable B-layer~\cite{IBL1,IBL2,Abbott:2018ikt}, installed in 2014, and a silicon microstrip tracker, together providing a precise reconstruction of tracks of charged particles in the pseudorapidity range $|\eta|<2.5$.
 The inner detector also includes a transition radiation tracker that provides tracking and electron identification for $|\eta|<2.0$.
@@
 The calorimeter system covers the pseudorapidity range $|\eta| < 4.9$.
-Within the region $|\eta|< 3.2$, electromagnetic (EM) calorimetry is provided by barrel and 
-endcap high-granularity lead/liquid-argon (LAr) sampling calorimeters,
-with an additional thin LAr presampler covering $|\eta| < 1.8$,
-to correct for energy loss in material upstream of the calorimeters.
+Within the region $|\eta|< 3.2$, electromagnetic (EM) calorimetry is provided by barrel and endcap high-granularity lead/liquid-argon (LAr) sampling calorimeters, with an additional thin LAr presampler covering $|\eta| < 1.8$, to correct for energy loss in material upstream of the calorimeters.
 Hadronic calorimetry is provided by %the
-a steel/scintillator-tile calorimeter,
-segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
-The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
-optimised for electromagnetic and hadronic measurements, respectively.
-The calorimeters are surrounded by a muon spectrometer within a magnetic field provided by air-core toroid magnets 
-with a bending integral of about 2.5 Tm in the barrel and up to 6 Tm in the endcaps. 
-The muon spectrometer measures the trajectories of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking chambers,
-and is instrumented with separate trigger chambers covering $|\eta|<2.4$.
-A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based level-1 trigger followed by 
-a software-based high-level trigger, is used to reduce the event rate to a maximum of around 1 kHz for offline storage.
+a steel/scintillator-tile calorimeter, segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
+The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules optimised for electromagnetic and hadronic measurements, respectively.
+The calorimeters are surrounded by a muon spectrometer within a magnetic field provided by air-core toroid magnets with a bending integral of about \SI{2.5}{\tesla\metre} in the barrel and up to \SI{6.0}{\tesla\metre}in the endcaps.
+The muon spectrometer measures the trajectories of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking chambers, and is instrumented with separate trigger chambers covering $|\eta|<2.4$.
+A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based level-1 trigger followed by a software-based high-level trigger, is used to reduce the event rate to a maximum of around \SI{1}{\kHz} for offline storage.
+
+An extensive software suite~\cite{ATL-SOFT-PUB-2021-001} is used in the reconstruction and analysis of real and simulated data, in detector operations, and in the trigger and data acquisition systems of the experiment.

### 2022-01-19 sections/introduction.tex
solve the commets

@@
 the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties have been conducted for nearly a decade, by which no significant sign of deviation from Standard Model (SM) was observed until today.
-However there is still chance finding new physics with searches already attempted but with improved sensitivities.
+However there are still chances to find new physics improving the sensitivity of previous searches.
 The presence of flavour-changing neutral-current (FCNC) interactions
@@
 %with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
-such interactions would manifest themselves as FCNC top-quark decays~\cite{Agashe:2013hma}, $t\to qH$.  
+such interactions could manifest themselves as FCNC top-quark decays~\cite{Agashe:2013hma}, $t\to qH$.  
 In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
@@
 
-On the other hand, if the $tqH$ interaction exists, the single-top, Higgs associated production through this interaction should also be enhanced.
-The $tH$ associated production in the SM prediction is expected to be small at LHC~\cite{Greljo:2014dka}.
-So the study on this process will also contribute to the FCNC interaction searches.
+On the other hand, if the $tqH$ interaction exists, the single-top, Higgs associated production through this interaction should also be enhanced.So the study on this process will also contribute to the FCNC interaction searches.
+The $tH$ associated production in the SM is expected to have a small cross section at LHC centre of mass energy~\cite{Greljo:2014dka}.
 
@@
 $H \to  WW^*, ZZ^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically~\cite{Aaboud:2018pob},
-$\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36}, and of $\BR(t\to cH)<0.19\%$ using $H\to \tau\bar{\tau}$ decay in which at least
+$\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36}, and of $\BR(t\to cH)<0.19\%$ using $H\to \tau^+\tau^-$ decay in which at least
 one of $\tau$-leptons decays hadronically~\cite{fcnc36}.  
-These upper limits are derived assuming that $\BR(t\to uH)=0$. Similar upper limits are obtained for $\BR(t\to uH)$ if $\BR(t\to cH)=0$.
+These upper limits are derived assuming that $\BR(t\to uH)=0$. Similar upper limits are obtained for $\BR(t\to uH)$ assuming $\BR(t\to cH)=0$.
 %The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
@@
 
-The CMS Collaboration has performed a search using  
+The CMS Collaboration performed a similar search using  
 $H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} with 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
@@
 
-This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
+%This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
+This paper is focused on the decay mode of the Higgs boson into $\tau$-leptons with the complete Run~2 dataset collected in 2015-2018.
 The corresponding integrated luminosity is 139.0 fb$^{-1}$.
@@
 the  $W$ boson decay either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
-$t_l$ when the $\tau$ decays into a light lepton(electron or muon) as $\tau_{lep}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
+$t_l$ when the $\tau$ decays into a light lepton(electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
 The $H\rightarrow \tau\tau$ decay is detected in

### 2022-01-19 sections/signal_background_modeling.tex
solve the commets

--- 2021-11-10 sections/signal_background_modeling.tex
@@
 
+\begin{table}
+\footnotesize
+\centering
+\caption{Overview of the MC generators used for the main signal and background samples}
+\begin{tabular}[h]{l|c|c|c|c|c|c}
+\hline \hline
+\multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
+        &  ME   &  PS    &  ME  & PS &   &  \\\hline
+\textit{TT} Signal & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+\textit{ST} Signal & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+$W/Z$+jets & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline
+\ttbar & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+Single top & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+$t\bar{t}X$ & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+Diboson & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline\hline
+\end{tabular}
+\label{mob}
+\end{table}
+
 %-------------------------------------------------------------------------------

### 2022-01-19 sections/strategy_Htautau.tex
solve the commets

@@
 \begin{table*}[t!]
-\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for leptonic channel.
-    The description of each variable is provided in the text.}}
-\label{tab:importance_tthML}
-\input{\FCNCTables/Importance/tthML/Merged}
+\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for hadronic channel. 
+    The descriptions of each variable are provided in the following text.}}
+\label{tab:importance_xTFW}
+\input{tables/xTFW_Merged}
 \end{table*}
@@
 \begin{table*}[t!]
-\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for hadronic channel. 
-    The description of each variable is provided in the text.}}
-\label{tab:importance_xTFW}
-\input{\FCNCTables/Importance/xTFW/Merged}
+\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for leptonic channel. 
+    The descriptions of each variable are provided in the following text.}}
+\label{tab:importance_tthML}
+\input{tables/tthML_Merged}
 \end{table*}
-
-%%%%%%%%%%%%%%%
 
@@
 A large set of potential variables are investigated in each SR separately.
-The discrimination of a given variable is quantified by the ``separation" and ``importance" measures provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 2\% were kept.
+The discrimination of a given variable is quantified by the "separation"(measures the degree of overlap between background and signal shape) and "importance"(depicts the power of the variable to the classification of two distributions) provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 2\% were kept.
 The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_tthML} and~\ref{tab:importance_xTFW} and defined in the following:
 \begin{itemize}
-\item $E^{T}_{miss}$ is the missing transverse momentum.
-\item $p_{T,\tau}$ is the transverse momentum of the leading tau candidate.
-\item $p_{T,sub-\tau}$ is the transverse momentum of the sub-leading tau candidate.
-\item $p_{T,l}$ is the transverse momentum of the leading lepton.
+\item $\MET$ is the missing transverse momentum.
+\item $P_{\text{T,\tauhadvis}} $ is the transverse momentum of the leading tau candidate.
+\item $P_{\text{T,sub}-\tau}$ is the transverse momentum of the sub-leading tau candidate.
+\item $P_{\text{T},\ell}$ is the transverse momentum of the leading lepton.
 \item $\chi^2$ is derived from kinematic fitting for the neutrinos.
-\item $m_{t,SM}$ is the invariant mass of the $b$-jet and the two jets from the $W$ decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
+\item $m_{t,\text{SM}}$ is the invariant mass of the $b$-jet and the two jets from the $W$ decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
 This variable is only defined for the 4-jet $t_hH$ and $t_ht(qH)$ events.
-\item $m^{T}_{W}$ is the transverse mass calculated from the lepton and $\met$ in the leptonic channels, defined as
+\item $m^{T}_{\text{W}}$ is the transverse mass calculated from the lepton and $\met$ in the leptonic channels, defined as
 \begin{equation}
-m^{T}_{W} = \sqrt{2 p_{\text{T,lep}} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\text{lep,miss}} \right)}.  
+m^{T}_{\text{W}} = \sqrt{2 P_{T,\ell} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\ell,\text{miss}} \right)}.  
 \end{equation}
 \item $m_{\tau,\tau}$ is the fitted invariant mass of the tau candidates and reconstructed neutrinos in the $t_hH$, $t_ht(qH)$ channels. 
-\item $m_{W}$ is the reconstructed invariant mass of the hadronic $W$ boson from SM top quark.
-\item $m_{t,FCNC}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
-\item $m_{\tau\tau,vis}$ is the visible invariant mass of the di-tau candidates.
-  %or the lepton and $\had$ candidate when there is only one $\had$.
-\item $p_{T,\tau\tau,vis}$ is the $\pt$ of the di-tau candidates.
-\item $m_{t,FCNC,vis}$ is the reconstructed visible mass of the FCNC-decaying top quark.
-\item $m_{t,SM,vis}$ is the invariant mass of the lepton and the b-jet, which reflects the visible SM top mass.
-\item $M(\tau\tau qjet,min)$ is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant mass of the visible FCNC top decaying product, an alternative of variable $m_{t,FCNC,vis}$.
-\item $M(wjet1,wjet2,min)$ is the invariant mass of two light-flavor jet, minimized by choosing different jets, reflects the invariant mass of the W candidate, an alternative of $m_{W}$.
+\item $m_{\text{W}}$ is the reconstructed invariant mass of the hadronic $W$ boson from SM top quark.
+\item $m_{\text{t},\text{FCNC}}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
+\item $m_{\tau\tau,\text{vis}}$ is the visible invariant mass of the di-tau candidates. %or the lepton and $\had$ candidate when there is only one $\had$.
+\item $P_{\text{T},\tau\tau,\text{vis}}$ is the $\pT$ of the di-tau candidates.
+\item $m_{\text{t},\text{SM},\text{vis}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
+\item $m_{\text{t},\text{SM},\text{vis}}$ is the invariant mass of the lepton and the b-jet, which reflects the visible SM top mass.
+\item $M(\tau\tau \text{qjet},\text{min})$ is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative of variable $m_{\text{t},\text{FCNC},\text{vis}}$.
+\item $M(\text{wjet1},\text{wjet2},\text{min})$ is the invariant mass of two light-flavor jet, minimized by choosing different jets, reflects the invariant mass of the W candidate, an alternative of $m_{\text{W}}$.
 \item $E^{T}_{miss}$ centrality is a measure of how central the $\met$ lies between the two tau candidates in the transverse plane, and is defined as
@@
 \end{eqnarray}
-\item $E_{\nu,i}/E_{\tau,i},i=1,2$ is the momentum fraction carried by the visible decay products from the tau mother.
+\item $E_{\nu,\text{i}}/E_{\tau,\text{i}},\text{i}=1,2$ is the momentum fraction carried by the visible decay products from the tau mother.
 It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section.
 For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}.
-\item $\Delta R(l+bjet,\tau\tau)$ is the angular distance between the lepton+b-jet and di-tau candidates.
-\item $\Delta R(l,bjet)$ is the angular distance between the lepton and b-jet.
-\item $\Delta R(\tau,bjet)$ is the angular distance between the tau and b-jet. If there are two taus in the event, the leading one is selected for the calculation.
-\item $\eta_{\tau,max}$ is the maximum $\eta$ value among the tau candidates.
-\item $\Delta R(l,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
-\item $\Delta R(\tau,qjet)$ is the angular distance between the tau and the reconstructed $q$-jet. If there are two taus in the event, the leading one is used.
-\item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(l,\tau)$.
-\item $\Delta\phi(\tau\tau,P^{T}_{miss})$ is the azimuthal angle between the $\met$ and di-tau $\pt$.
+\item $\Delta R(\ell+\text{bjet},\tau\tau)$ is the angular distance between the lepton+b-jet and di-tau candidates.
+\item $\Delta R(\ell,\text{bjet})$ is the angular distance between the lepton and b-jet.
+\item $\Delta R(\tau,\text{bjet})$ is the angular distance between the tau and b-jet. If there are two taus in the event, the leading one is selected for the calculation.
+\item $\eta_{\tau,\text{max}}$ is the maximum $\eta$ value among the tau candidates.
+\item $\Delta R(\ell,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
+\item $\Delta R(\tau,\text{qjet})$ is the angular distance between the tau and the reconstructed $q$-jet. If there are two taus in the event, the leading one is used.
+\item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(\ell,\tau)$.
+\item $\Delta\phi(\tau\tau,P^{T}_{\text{miss}})$ is the azimuthal angle between the $\met$ and di-tau $\pT$.
 \end{itemize}
@@
 %some of these variables in three main decay final states($t_l\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
-is shown in Figures~\ref{fig:taupt_postfit}.
+is shown in Figures~\ref{fig:taupt_prefit}.
 %each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_lhadhad}.
@@
 %discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
-The expected signals (dashed) are also shown after scaled up for the shape comparison of the distributions.
+The expected signals are also shown after scaled up for the shape comparison of the distributions.
 %by a large factor normalized to the total number of events in the predicted
@@
 The first and the last bins in the figures contain the underflow and overflow respectively.
-The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
+The bottom panel displays the ratio of data to the background (``Bkg'') prediction.
 The hashed area represents the total uncertainty of the background.
@@
 The final observable used to extract signal events is defined as the BDT distribution in each SRs corresponding to either $tuH$ or $tcH$ signal.
-Figure~\ref{fig:asimov_prefitbdt} show the prefits to the data of BDT observable in each SRs with all background processes
-constrained to the SM expectation.
+%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
 %The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
@@
 \centering
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf}
-\put(-40, 90){\small\textbf{(a1)}}
-%\put(-30, 80){\textbf{(a1)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
-\put(-40, 90){\small\textbf{(a2)}}
-%\put(-30, 80){\textbf{(a2)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
-\put(-40, 90){\small\textbf{(a3)}} 
-%\put(-70, 70){\textbf{(a3)}}
-\\
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
-\put(-40, 90){\small\textbf{(b1)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b3j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
-\put(-40, 90){\small\textbf{(b2)}}\\
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/tau_pt_0.pdf}
-\put(-40, 90){\small\textbf{(c1)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/tau_pt_0.pdf}
-\put(-40, 90){\small\textbf{(c2)}}\\
-\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),
-  $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2). Only statistical uncertainties are being shown (?). Underflow and overflow bins are included
-respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau
-contributions shown from $t\bar{t}$, Ztautau and other MC including diboson, single top, and V+jets.}
-\label{fig:taupt_postfit}
+\begin{tabular}{@{}ccc@{}}
+%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
+%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
+%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l2tau1bnj_os.pdf} &
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b1j_ss.pdf}&
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b2j_ss.pdf}\\
+(a1) \pT(\tauhad) in $t_l\thadhad$ & (a2) \pT(\tauhad) in  $t_l\tauhad$-1j& (a3) \pT(\tauhad) in $t_l\tauhad$-2j\\
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b2j_os.pdf}&
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b3j_os.pdf}&
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
+(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
+(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
+\end{tabular}
+\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit').
+The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
+Underflow and overflow bins are included respectively in the first and last bins.
+Rare including single top, and V+jets and only subtau real refers to t$\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution.
+The lower panels show the ratios of the data ('Data') to the background prediction ('Bkg.')}
+\label{fig:taupt_prefit}
 \end{figure}
 
-%\input{\FCNCFigures/tex/BDT}
-\begin{figure}[H]
-\centering
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/BDTG_test.pdf}
-\put(-40, 90){\small\textbf{(a1)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
-\put(-40, 90){\small\textbf{(a2)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
-\put(-40, 90){\small\textbf{(a3)}}\\
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf}
-\put(-40, 90){\small\textbf{(b1)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b3j_os_vetobtagwp70_highmet/BDTG_test.pdf}
-\put(-40, 90){\small\textbf{(b2)}}\\
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/BDTG_test.pdf}
-\put(-40, 90){\small\textbf{(c1)}}
-\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/BDTG_test.pdf}
-\put(-40, 90){\small\textbf{(c2)}}\\
-\caption{ The BDT output distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),
-  $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2). Only statistical uncertainties are being shown (?). Underflow and overflow bins are included
-respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau
-contributions shown from $t\bar{t}$ and other MC including diboson, single top, and V+jets.}
-\label{fig:asimov_prefitbdt}
-\end{figure}
+% %\input{\FCNCFigures/tex/BDT}
+% \begin{figure}[H]
+% \centering
+% \begin{tabular}{@{}ccc@{}}
+% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/BDTG_test.pdf} &
+% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/BDTG_test.pdf}&
+% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}\\
+% (a1) BDT dicriminant in $t_l\thadhad$ & (a2) BDT dicriminant in  $t_l\tauhad$-1j& (a3) BDT dicriminant in $t_l\tauhad$-2j\\
+% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf} &
+% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b3j_os_vetobtagwp70_highmet/BDTG_test.pdf} &
+% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/BDTG_test.pdf} \\
+% (b1) BDT dicriminant in $t_h\tlhad$-2j & (b2) BDT dicriminant in  $t_h\tlhad$-3j & (b3) BDT dicriminant in $t_h\thadhad$-2j \\
+% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/BDTG_test.pdf} & \\
+% (c1) BDT dicriminant in$t_h\thadhad$-3j\\
+% \end{tabular}
+% \caption{ The BDT output distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),$t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1).
+Only statistical uncertainties are being shown (?).
+Underflow and overflow bins are included
+% respectively in the first and last bins.
+Empty data bins here are always blinded based on our strategy.
+The real tau contributions shown from $t\bar{t}$ and other MC including % diboson, single top, and V+jets.}
+% \label{fig:asimov_prefitbdt}
+% \end{figure}

### 2022-01-19 sections/systematic_uncertainties.tex
solve the commets

--- 2021-11-15 sections/systematic_uncertainties.tex
@@
 %treated correlatedly with $\ttbar$ samples.
+
+\begin{table}[htbp]
+\caption{List of relative uncertainties of the signal strength from the combined fit in hadronic channel.
+The uncertainties are symmetrised for presentation and grouped into the categories described in the text.
+%The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
+}
+\small
+\centering
+\begin{tabular}{cc} \toprule\toprule
+$\text{Uncertainty}    $   & $\Delta\mu/\mu[\%]$ \\\midrule
+$\text{Fake modelling} $   & $13.5$ \\
+$\text{Instrument}     $   & $2.6$  \\
+$\text{Jets}           $   & $1.7$   \\
+$\text{Met}            $   & $0.4$   \\
+$\tau                  $   & $7.2$    \\
+$\text{b-tagging}       $  & $0.3$    \\
+$\text{Signal Theory}  $   & $1.5$   \\
+$\text{Other MC theory} $  & $2.7$    \\
+$t\bar{t} \text{theory}$  & $7.6$     \\\midrule
+$\text{Statistics}      $  & $11.2$   \\
+$\text{Total systematic}$  & $24.2$  \\ \midrule
+$\text{Total}  $           & $26.7$ \\
+\bottomrule\bottomrule
+\end{tabular}
+\label{tab:had_sys_impact}
+\end{table}
+
+\begin{table}[htbp]
+\caption{List of relative uncertainties of the signal strength from the combined fit in leptonic channel.
+The uncertainties are symmetrised for presentation and grouped into  the categories described in the text.
+%The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
+}
+\small
+\centering
+\begin{tabular}{cc} \toprule\toprule
+$\text{Uncertainty}        $ & $  \Delta\mu/\mu[\%]  $\\\midrule
+$\text{Fake modelling}     $ & $       2.1             $\\
+$\text{Instrument}         $ & $       0.7             $\\
+$\text{Jets}               $ & $       2.8             $\\
+$\text{Met}                $ & $       1.2             $\\
+$\text{Lepton}             $ & $       0.7             $\\
+$\tau                      $ & $       2.3             $\\
+$\text{b-tagging}          $ & $       4.8             $\\
+$\text{Signal Theory}      $ & $       6.9             $\\
+$\text{Other MC theory}    $ & $       2.1             $\\
+$t\bar{t} \text{theory}    $ & $       3.7             $\\\midrule
+$\text{Statistics}         $ & $       5.9             $\\
+$\text{Total systematic}   $ & $       12.9            $\\\midrule
+$\text{Total}              $ & $       14.2            $\\
+\bottomrule\bottomrule
+\end{tabular}
+\label{tab:had_sys_impact}
+\end{table}

### 2022-01-19 ANA-TOPQ-2019-17-PAPER-metadata.tex

@@
 \AtlasAbstract{%
-
 A search for flavour-changing neutral current $tqH$ interections with a top quark, an up-type quark ($q=u, c$), and a
@@
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
-CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
+CERN Large Hadron Collider and corresponds to an integrated luminosity of 139 fb$^{-1}$.
 Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in

### 2022-01-19 sections/objects.tex

@@
 In order to avoid double-counting of $\tauhad$ as jets, the closest jet whose axis is
-within ${\Delta}R = 0.2$ of a $\tauhad$ is discarded if the jet is not $b$-tagged, otherwise the $\tauhad$ is remived. 
+within ${\Delta}R = 0.2$ of a $\tauhad$ is discarded if the jet is not $b$-tagged, otherwise the $\tauhad$ is removed. 
 % TEXT FROM BOYANG. NEED TO RECHECK WHAT WE HAVE ABOVE IS ACCURATE
-%In the $\Htautau$ search, the objects are removed with the following sequence: if two electrons have overlapping second-layer cluser, or shared tracks, the electron with lower $\pt$ is removed; $\tauhad$ within a $\Delta R=0.2$ cone of an electron or muon are removed; if a muon sharing an ID track with an electron and the muon is calo-tagged, the muon is removed, otherwise the electron is removed; jets within a $\Delta R=0.2$ cone of an electron are removed; electrons within a $\Delta R=0.4$ cone of a jet are removed; when a muon ID track is ghost associated to a jet or within a $\Delta R=0.2$ cone of a jet, the jet is removed if it has less than 3 tracks with $\pt>500$ MeV or has a relative small $\pt$ ($\pt^{\mu}>0.5\pt^{\text{jet}} \text{ and } \pt^{\mu}>0.7[\text{the scalar sum of the } \pt \text{'s of the jet tracks with } \pt>500$ MeV]); muons within a $\Delta R=0.4$ cone of a jet are removed; jets within a $\Delta R=0.2$ cone of the leading $\tauhad$ ($\lephad$), or with the two leading $\tauhad$'s ($\hadhad$), are removed.
+%In the $\Htautau$ search, the objects are removed with the following sequence: if two electrons have overlapping second-layer cluster, or shared tracks, the electron with lower $\pt$ is removed; $\tauhad$ within a $\Delta R=0.2$ cone of an electron or muon are removed; if a muon sharing an ID track with an electron and the muon is calo-tagged, the muon is removed, otherwise the electron is removed; jets within a $\Delta R=0.2$ cone of an electron are removed; electrons within a $\Delta R=0.4$ cone of a jet are removed; when a muon ID track is ghost associated to a jet or within a $\Delta R=0.2$ cone of a jet, the jet is removed if it has less than 3 tracks with $\pt>500$ MeV or has a relative small $\pt$ ($\pt^{\mu}>0.5\pt^{\text{jet}} \text{ and } \pt^{\mu}>0.7[\text{the scalar sum of the } \pt \text{'s of the jet tracks with } \pt>500$ MeV]); muons within a $\Delta R=0.4$ cone of a jet are removed; jets within a $\Delta R=0.2$ cone of the leading $\tauhad$ ($\lephad$), or with the two leading $\tauhad$'s ($\hadhad$), are removed.
 

### 2022-01-26 sections/conclusion.tex
updating EB comments

@@
 %-------------------------------------------------------------------------------
-
 A search for flavour-changing neutral current process involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented.
@@
 
-Although no significant excess of events above the background expectation is found, about a factor of 2 improvement to 95\% CL upper limits on the $t\to Hq$ branching ratios are reported in Tab~\ref{tab:limits_summary}, along with the Wilson coefficients with respect to the previous partial run-2 results~\cite{Aaboud2019SearchFT}.
+Although no significant excess of events above the background expectation is found, about a factor of 2 improvement to 95\% CL upper limits on the $t\to Hq$ branching ratios are reported in Table~\ref{tab:limits_summary}, along with the Wilson coefficients with respect to the previous partial run-2 results~\cite{Aaboud2019SearchFT}.
 Observed (expected) 95\% CL upper limits are set on the $t\to Hc$ and $t\to Hu$ branching ratios of $9.9\times10^{-4}$ ($5.0^{+2.2}_{-1.4}\times10^{-4}$) and $7.2\times10^{-4}$ ($3.6^{+1.7}_{-1.0}\times10^{-4}$).

### 2022-01-26 sections/introduction.tex
updating EB comments

@@
 %the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling~\cite{Agashe:2013hma}.
-Therefore, an observation of this decay would be a clear evidence for new physics. The $tqH$ interaction could also potentially open up more
-Higgs decay channels, such as $H\rightarrow t^*q\rightarrow Wbq$, but they are likely suppressed due to the $t-H$ mass difference,
-which could be interesting for future studies.
+Therefore, an observation of this decay would be a clear evidence for new physics.
+%The $tqH$ interaction could also potentially open up more
+%Higgs decay channels, such as $H\rightarrow t^*q\rightarrow Wbq$, but they are likely suppressed due to the $t-H$ mass difference,
+%which could be interesting for future studies.
 
@@
 
-In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$, yielding $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$.
+In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$ with a small $\BR(t\to Hq)$, yielding $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$.
 Similarly,

### 2022-01-26 sections/strategy_Htautau.tex
updating EB comments

@@
 The discrimination of a given variable is quantified by the "separation"(measures the degree of overlap between background and signal shape) and "importance"(depicts the power of the variable to the classification of two distributions) provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 2\% were kept.
-The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_tthML} and~\ref{tab:importance_xTFW} and defined in the following:
+The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_xTFW} and~\ref{tab:importance_tthML}, as defined in the following:
 \begin{itemize}

### 2022-01-28 ANA-TOPQ-2019-17-PAPER-metadata.tex
updating EB comments
fixing make error due to a wrong reference and other minor updates

@@
 No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
-Observed (expected) 95\% CL upper limits are set on the $t\to Hc$ and $t\to Hu$ branching ratios of $0.099\%$ ($0.050^{+0.022}_{-0.014}\%$)
-and $0.072\%$ ($0.036^{+0.017}_{-0.010}\%$), respectively.}
-%The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
+Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $0.099\%$ ($0.050^{+0.022}_{-0.014}\%$)
+and $0.072\%$ ($0.036^{+0.017}_{-0.010}\%$), respectively. The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
+the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.} 
+%$|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
 %These are the most restrictive direct bounds on $tqH$ interactions obtained so far.
@@
 \AtlasCoverAnalysisTeam{
-Xin Chen, Boyang Li, Mingming Xia, Wei-Ming Yao}
+Boyang Li, Mingming Xia, Wei-Ming Yao, Xin Chen}
 %Combination: Peter Onyisi, Harish Potti}

### 2022-01-28 sections/conclusion.tex
fixing make error due to a wrong reference and other minor updates

--- 2022-01-19 sections/conclusion.tex
@@
 %-------------------------------------------------------------------------------
-
 A search for flavour-changing neutral current process involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented.
-FCNC $tqH$ interaction is searched for both in $t\bar{t}$ decay mode, where one top quark decays following SM processes and the other one decays through $t\rightarrow Hq$, and in production mode($pp\rightarrow tH$) with a single top quark produced via FCNC interaction, while the decay according to SM.
+FCNC $tqH$ interaction is searched for both in $t\bar{t}$ decay mode, where one top quark decays following SM processes and the other one decays through $t\rightarrow Hq$, and in production mode($pp\rightarrow tH$) with a single top quark produced via FCNC interaction where $t\to Wb$.
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
 The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$), a b-tagged jet as well as multiple jets.Multivariate techniques based on BDT are used to distinguish the signal from the background on the basis of their different kinematics.
+The search sensitivities have been improved significantly compared to the previous analysis using 36$^{-1}$ of run-2 data~\cite{Aaboud2019SearchFT}.
 
-Although no significant excess of events above the background expectation is found, about a factor of 2 improvement to 95\% CL upper limits on the $t\to Hq$ branching ratios are reported in Tab~\ref{tab:limits_summary}, along with the Wilson coefficients with respect to the previous partial run-2 results~\cite{Aaboud2019SearchFT}.
-Observed (expected) 95\% CL upper limits are set on the $t\to Hc$ and $t\to Hu$ branching ratios of $9.9\times10^{-4}$ ($5.0^{+2.2}_{-1.4}\times10^{-4}$) and $7.2\times10^{-4}$ ($3.6^{+1.7}_{-1.0}\times10^{-4}$).
-The observed (expected) upper limits on the D6 Wilson coefficients from the combination of the searches are $C_{c\phi}<1.38\,(0.97)$ and $C_{u\phi}<1.18\,(0.83)$, respectively.
+No significant excess of events above the background expectation is found. We set 95\% CL upper limits on the $t\to Hq$ branching ratios and the corresponding
+dimension-6 operator Wilson coefficients in the effective $tqH$ coupling. 
+%about a factor of 2 improvement to 95\% CL upper limits on the $t\to Hq$ branching ratios are reported in Table~\ref{tab:limits_summary}, along with the Wilson coefficients with respect to the previous partial run-2 results~\cite{Aaboud2019SearchFT}.
+Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.9\times10^{-4}$ ($5.0^{+2.2}_{-1.4}\times10^{-4}$) and $7.2\times10^{-4}$ ($3.6^{+1.7}_{-1.0}\times10^{-4}$).
+%The observed (expected) upper limits on the D6 Wilson coefficients from the combination of the searches are set to $C_{c\phi}<1.38\,(0.97)$ and $C_{u\phi}<1.18\,(0.83)$, respectively.
+The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
+the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.

### 2022-01-28 sections/introduction.tex
fixing make error due to a wrong reference and other minor updates

@@
 the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties have been conducted for nearly a decade, by which no significant sign of deviation from Standard Model (SM) was observed until today.
-However there are still chances to find new physics improving the sensitivity of previous searches.
+However there are still chances to find new physics by improving the sensitivity of previous searches.
 The presence of flavour-changing neutral-current (FCNC) interactions
@@
 In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
-The $t\to u/c+H$ branching fraction in the SM is calculated to be exceedingly small around $10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}.
+The $t\to qH$ branching fraction in the SM is calculated to be exceedingly small around $10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}.
 %such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
@@
 
-On the other hand, if the $tqH$ interaction exists, the single-top, Higgs associated production through this interaction should also be enhanced.So the study on this process will also contribute to the FCNC interaction searches.
+On the other hand, if the $tqH$ interaction exists, the single-top, Higgs associated production through this interaction should also be enhanced.
+So the study on this process will also contribute to the FCNC interaction searches.
 The $tH$ associated production in the SM is expected to have a small cross section at LHC centre of mass energy~\cite{Greljo:2014dka}.
 
-Searches for $t \to Hq$ decays have been performed by the ATLAS and CMS collaborations, taking advantage of the large samples
+Searches for $t \to qH$ decays have been performed by the ATLAS and CMS collaborations, taking advantage of the large samples
 of top-quark pair ($\ttbar$) events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{fcnc36} using early Run~2 data.
 
-In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $Hq$ with a small $\BR(t\to Hq)$, yielding $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$.
+In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $qH$ with a small $\BR(t\to qH)$, yielding $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$.
 Similarly,
@@
 $H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} with 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
-in upper limits of $\BR(t\to Hc)<0.47\%$ and $\BR(t\to Hu)<0.47\%$, in each case neglecting the other decay mode.
+in upper limits of $\BR(t\to cH)<0.47\%$ and $\BR(t\to uH)<0.47\%$, in each case neglecting the other decay mode.
 Compared with previous searches, the search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 

### 2022-01-28 sections/statistical_analysis.tex
solve the commets
fixing make error due to a wrong reference and other minor updates

@@
 a product of Poisson probability terms over all bins considered in the search. This function depends
-on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $tH$ and $tt(Hq)$ signal events
-normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=0.1\%$,
+on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $tH$ and $tt(qH)$ signal events
+normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$,
 and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations. 
@@
 Statistical uncertainties in each bin of the predicted final discriminant distributions are taken into account by dedicated parameters in the fit.     
-The best-fit $\BR(t\to Hq)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
+The best-fit $\BR(t\to qH)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
 hypothesis, maximising the likelihood function ${\cal L}(\mu,\theta)$ over $\mu$ and $\theta$.
@@
 In the absence of signal, exclusion limits are set on $\mu$ , and thus on
-$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
-For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$,
+$\BR(t\to qH)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
+For a given signal scenario, values of the $\BR(t\to qH)$ yielding CL$_{\textrm{s}} < 0.05$,
 where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

### 2022-02-03 sections/systematic_uncertainties.tex
updating EB comments
typo fix

@@
 
-The uncertainty on the pileup reweighting is evaluated by varying the pileup scale factors
-by 1$\sigma$ based on the reweighting of the average interactions per bunch crossing. However, this
+The uncertainty on the pileup reweighing is evaluated by varying the pileup scale factors
+by 1$\sigma$ based on the reweighing of the average interactions per bunch crossing. However, this
 uncertainty is highly correlated with the luminosity uncertainty and may be an overestimate.
@@
 One NP reflects the symmetrised effect of the two shower variations Var3cDown and Var3cUp, and the other NP with name ``scale'' describe the symmetrised effect from the independent variations of the renormalisation and factorisation scale.
-The impact of the uncertainty from FSR modelling is estimated by reweighting the nominal single top sample.
+The impact of the uncertainty from FSR modelling is estimated by reweighing the nominal single top sample.
 The two variations $\mu^{FSR}_{R} \times 0.5$ and $\mu^{FSR}_{R} \times 2$ are considered.
@@
 \end{tabular}
-\label{tab:had_sys_impact}
+\label{tab:lep_sys_impact}
 \end{table}

### 2022-02-09 ANA-TOPQ-2019-17-PAPER-metadata.tex

@@
 \AtlasAbstract{%
-A search for flavour-changing neutral current $tqH$ interections with a top quark, an up-type quark ($q=u, c$), and a
+A search for flavour-changing neutral current $tqH$ interactions with a top quark, an up-type quark ($q=u, c$), and a
 Standard Model Higgs boson is presented. The Higgs boson decays into a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.

### 2022-02-09 sections/signal_background_modeling.tex
updating EB comments

@@
 
+An overview of the MC generators used for the main signal and background samples is summarized in Table~\ref{mob}.
+
 Samples of simulated $\ttbar \to WbHq$ events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
@@
 The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
-assuming a benchmark branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=0.1\%$.
-The case of both top quarks decaying into $Hq$ is neglected in the analysis given the existing upper limits on $\BR(t \to Hq)$ (Section~\ref{sec:intro}).
+assuming a benchmark branching ratio of $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$.
+The case of both top quarks decaying into $qH$ is neglected in the analysis given the existing upper limits on $\BR(t \to qH)$ (Section~\ref{sec:intro}).
 
@@
 Depending on either up quark or charm quark involved in the FCNC production, the effective Lagrangian of $tqH$ interaction are parametrised using
-dim-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 0.711 pb and $\sigma(cg\to tH)$ = 0.103 pb using $\BR_{\mathrm{ref}}(t\to Hq)=0.1\%$ as benchmark.
+dim-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 0.711 pb and $\sigma(cg\to tH)$ = 0.103 pb using $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$ as benchmark.
 

### 2022-02-16 sections/conclusion.tex
update the draft to V03 with comments

@@
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
-The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$), a b-tagged jet as well as multiple jets.Multivariate techniques based on BDT are used to distinguish the signal from the background on the basis of their different kinematics.
-The search sensitivities have been improved significantly compared to the previous analysis using 36$^{-1}$ of run-2 data~\cite{Aaboud2019SearchFT}.
-
-No significant excess of events above the background expectation is found. We set 95\% CL upper limits on the $t\to Hq$ branching ratios and the corresponding
+The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$), a b-tagged jet as well as multiple jets.
+Multivariate techniques based on BDT are used to distinguish the signal from the background on the basis of their different kinematics.
+%The search sensitivities have been improved significantly compared to the previous analysis using 36$^{-1}$ of run-2 data~\cite{Aaboud2019SearchFT}. 
+%No significant excess of events above the background expectation is found.
+There is an excess of data events observed above background with a significance of 2.6$\sigma$.  
+We set 95\% CL upper limits on the $t\to Hq$ branching ratios and the corresponding
 dimension-6 operator Wilson coefficients in the effective $tqH$ coupling. 
@@
 the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.
+These results improve significantly upon previous ATLAS and CMS limits on the $t\rightarrow Hq$ branching ratios..

### 2022-02-16 sections/introduction.tex
update the draft to V03 with comments

@@
 %-------------------------------------------------------------------------------
-
-Since the observation of Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
-the Large Hadron Collider (LHC), a comprehensive programme of measurements of its properties have been conducted for nearly a decade, by which no significant sign of deviation from Standard Model (SM) was observed until today.
-However there are still chances to find new physics by improving the sensitivity of previous searches.
-The presence of flavour-changing neutral-current (FCNC) interactions
-between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$) is still an active topic. Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl},
+After the discovery of the Higgs boson in 2012 by the ATLAS~\cite{Aad:2012tfa} and CMS~\cite{Chatrchyan:2012ufa} collaborations at 
+%Since the observation of Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
+the Large Hadron Collider (LHC), a comprehensive programme of measurements % of its properties
+has been conducted with increased precision and proved to be consistent with the Standard Model (SM) predictions. 
+%for nearly a decade, by which no significant sign of deviation from Standard Model (SM) was observed until today.
+However the LHC still provides an excellent opportunity to search for rare new physics processes beyond the Standard Model (BSM).  
+%there are still chances to find new physics by improving the sensitivity of previous searches.
+The flavour-changing neutral-current (FCNC) interactions 
+between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$) has been actively searched for by the ATLAS and CMS collaborations.
+%is still an active topic.
+Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl},
 %with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
@@
 In contrast, large enhancements of these branching ratios are possible in some scenarios beyond the SM.
-Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM) with or without the flavour violation,
+Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{Branco:2hdm2012} with or without the flavour violation,
 %of type I, with explicit flavour conservation,
@@
 %which could be interesting for future studies.
-
-On the other hand, if the $tqH$ interaction exists, the single-top, Higgs associated production through this interaction should also be enhanced.
-So the study on this process will also contribute to the FCNC interaction searches.
-The $tH$ associated production in the SM is expected to have a small cross section at LHC centre of mass energy~\cite{Greljo:2014dka}.
+On the other hand, if the $tqH$ interaction exists, the single-top, Higgs associated production process through this interaction becomes non-zero, enhancing the total
+production cross section of $pp\rightarrow tH$.
+So the study on this process will also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
+The $tH$ associated production in the SM is expected to have a small cross section of $92^{+7}_{-12}$ fb at LHC centre of mass energy~\cite{deFlorian:2016spz}.
 
@@
 Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
-Using 36.1 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of
+Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of
 $\BR(t\to cH)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, $\BR(t\to cH)<0.16\%$ based on
@@
 %The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
-Combining all of the ATLAS searches using 36fb$^{-1}$ Run~2 data, the limits at 95\% CL are set for  $\BR(t\to cH)<0.11\%$ and $\BR(t\to uH)<0.12\%$ respectively assuming $\BR(t\to uH)=0$ and $\BR(t\to cH)=0$~\cite{fcnc36}.
+Combining all of the ATLAS searches using 36.1~fb$^{-1}$ Run~2 data, the limits at 95\% CL are set for  $\BR(t\to cH)<0.11\%$ and $\BR(t\to uH)<0.12\%$ respectively assuming $\BR(t\to uH)=0$ and $\BR(t\to cH)=0$~\cite{fcnc36}.
 
@@
 %This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
-This paper is focused on the decay mode of the Higgs boson into $\tau$-leptons with the complete Run~2 dataset collected in 2015-2018.
+The analysis targets Higgs boson decays to 
+%This paper is focused on the decay mode of the Higgs boson into
+$\tau$-leptons with the complete Run~2 dataset collected in 2015-2018.
 The corresponding integrated luminosity is 139.0 fb$^{-1}$.
-Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted and the signals are divided into several final states depending on the production modes and
+Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted.
+The signals are divided into several final states depending on the production mode and
 the  $W$ boson decay either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
-$t_l$ when the $\tau$ decays into a light lepton(electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
+$t_l$ when the $\tau$ decays into a light lepton (electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
 The $H\rightarrow \tau\tau$ decay is detected in
@@
 More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data and more
-$t\bar{t}$ control regions (CRtt) are used for calibration of tau fakes in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
-
+$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
 Finally, multivariate technique is used to discriminate between the signal and the background on the basis of their different kinematics.

### 2022-02-16 sections/objects.tex
Updating Figure 2 with prefit plots for now
update the draft to V03 with comments

@@
 
-The event reconstruction is affected by multiple $pp$ collisions in a single bunch crossing and by collisions
-in neighbouring bunch crossings, referred to as pile-up. 
-Interaction vertices from the $pp$ collisions are reconstructed from at least two tracks 
-with transverse momentum ($\pt$) larger than $400~\mev$ that are consistent with originating from the 
+Events are selected from $pp$ collisions at $\sqrt(s)$=13 TeV recorded by the ATLAS detector during 2015-2018.
+Only events for which all relevant subsystems were operational are considered.
+Events are required to have at least one vertex with two or more tracks with transverse momentum
+%The event reconstruction is affected by multiple $pp$ collisions in a single bunch crossing and by collisions
+%in neighbouring bunch crossings, referred to as pile-up. 
+%Interaction vertices from the $pp$ collisions are reconstructed from at least two tracks with transverse momentum
+($\pt$) larger than $400~\mev$ that are consistent with originating from the 
 beam collision region in the $x$--$y$ plane. If more than one primary vertex candidate is found, the
@@
 and by requiring that their longitudinal impact parameter, $z_0$, satisfies $|z_0 \sin\theta|<0.5$~mm.
-To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have \pt 1~GeV above the threshold.
+%To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have \pt 1~GeV above the threshold.
 To further reduce the background from non-prompt leptons, photon conversions and hadrons, lepton candidates are also required to be isolated 
@@
 
-Tight isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions based a trained isolation boosted decision tree \texttt{PromptLeptonVeto}(PLIV), which is to identify non-prompt light leptons using lifetime information associated with a track jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}.
+Tight isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions based on a trained isolation boosted decision tree \texttt{PromptLeptonVeto}(PLIV), which is to identify non-prompt light leptons using lifetime information associated with a track jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}.
 These additional reconstructed charged particle tracks inside the jet can be
@@
 The scale factors for the efficiencies of the tight \texttt{PLIV} working points are measured using the tag and probe method
-with $Z\rightarrow l^+l^-$ events. These scale factors are also checked applicable to the electron or muon from the tau decay
-using $Z\rightarrow\tau\tau\rightarrow e\mu$ samples, which is consistent with 1 at 2\% level. To be conservative, we assign
-additional $\pm 2\%$ systematic uncertainty for the PLIV efficiency for the tau-lepton in the lepton+$\thad$ channels.
+with $Z\rightarrow l^+l^-$ ($l=e$ or $\mu$) events. These scale factors are also checked for the electron or muon from the tau decay
+using $Z\rightarrow\tau\tau\rightarrow e\mu4\nu$ samples, which is consistent at 2\% level. To be conservative, an
+additional uncertainty of $\pm 2\%$ is considered for the PLIV efficiency for the tau-lepton in the lepton+$\thad$ channels.
 %Additionally, the $\Htautau$ search requires leptons to
@@
 an average 70\% efficiency to tag a $b$-quark jet, with a light-jet\footnote{Light-jet refers to a jet originating from the hadronisation of a light quark ($u$, $d$, $s$) or a gluon.} rejection factor of about 385 and a charm-jet rejection factor of about 12, as determined for jets with
-$\pt >20~\gev$ and $|\eta|<2.5$ in simulated $\ttbar$ events.
+$\pt >20~\gev$ and $|\eta|<2.5$ in simulated $\ttbar$ events~\cite{Aad:2019epj79}.
 
@@
 Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
-Events with$\had$ candidate that is $b$-tagged are rejected.
+Events with $\had$ candidate that is $b$-tagged are rejected.
 %(TBD: check RNN description and update then numbers)
@@
 
-Overlaps between reconstructed objects are removed sequentially. Firstly, electron candidates that lie 
+To avoid double counting reconstructed objects, an overlap removal procedure is applied.
+%Overlaps between reconstructed objects are removed sequentially.
+Firstly, electron candidates that lie 
 within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 

### 2022-02-16 sections/strategy_Htautau.tex
fixing make error due to a wrong reference and other minor updates
typo fix
update the draft to V03 with comments

@@
 The $tt(qH)$ and $tH$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
-the Higgs boson and the remaining SM $t\to Wb$ decay. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
+the Higgs boson, where the remaining top quark decays into $Wb$. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
 %at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
-If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon with significant $\met$ is also expected.
-In a significant fraction of the events, the smaller jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
-resulting in some signal events mixed with production mode having only three reconstructed jets.
+If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon, together with significant $\met$ is also expected.
+In a significant fraction of the events, the lowest $\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
+resulting in only three reconstructed jets where the production mode is dominant. 
+%some signal events mixed with production mode having only three reconstructed jets.
 In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs based on the number of light leptons,
@@
 \hline \hline
-\multicolumn{2}{c|}{Regions} & b-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
+\multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
 \multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
@@
 %is missing or not (events with exactly three jets or at least four jets).
-This event categorisation is primarily motivated by optimizing the sensitivity in each signal region that targets both leptonic and hadronic top-quark
-decays as well as the Higgs decays into $\lephad$ or $\hadhad$ final state.   
+This event categorisation is primarily motivated by optimizing the sensitivity in each signal region that targets either leptonic or hadronic top-quark
+decays as well as the Higgs decays into either $\lephad$ or $\hadhad$ final state.   
 The event kinematic reconstruction is further applied in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the
@@
 
-For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet, should be a hard narrow jet considering it's from the
+For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a hard narrow jet from the
 decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
@@
 is considered as $q$-jet since the FCNC top decay products are likely boosted closer together than other jets. 
-If there are more than 2 jets beside $q$-jet and $b$-jet, the jets from $W$ boson decay are chosen from the combination
-with the invariant mass closest to W resonance. There is the chance that one of the jets fails the $\pt$ requirement and not reconstructed. This kind of events will fall
-into $t_hH$.
+If there are more than two jets beside $q$-jet and $b$-jet, the jets from $W$ boson decay are chosen from the combination
+with the invariant mass closest to W resonance. There is the chance that one of the jets fails the $\pt$ requirement and not reconstructed.
+This kind of events will fall into $t_hH$.
 %while the FCNC top resonance is
@@
 %given the big chance that the jet which is missing is from $W$ decay.
+In the $t_hH$ events, there are three jets coming from top hadronic decay including the $b$-jet and two opposite-sign $\had$ from the Higgs boson decay, where
+both $t_h$ and H can be reconstructed.  
+%. So a Higgs resonance formed by the taus and a top resonance formed by
+%the jets are expected.
 
-In the $t_hH$ events, there are 3 jets coming from top hadronic decay including the b-jet. So a Higgs resonance formed by the taus and a top resonance formed by
-the jets are expected.
-
-Finally, the four-momenta of the invisible decay products from the decay of di-taus 
+The four-momenta of the invisible decay products from the decay of the tau-leptons 
 are estimated using a kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
 measured $\met$ within their expected resolutions.
-The resolution on the Higgs boson mass is taken to be $20~\gev$, respectively, while the resolution on the measured $\met$ is parameterised as a linear function of
+The resolution on the Higgs boson mass is assumed to be $20~\gev$, respectively, while the resolution on the measured $\met$ is parameterised as a linear function of
 $\sqrt{\sum E_T}$, where $\sum E_T$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
@@
 
-For the  $t_lt(qH)$ and $t_lH$ events where the $W$ boson from $t\to W b$ decays leptonically, there is a neutrino with large momentum and the flying direction is unknown.
-The kinematics fit is no longer feasible in the $t_l\hadhad$ and $t_l\had$ channels.
-The kinematic variables are calculated using the visible
-objects only.
+For the  $t_lt(qH)$ and $t_lH$ events where the $W$ boson from $t\to W b$ decay decays leptonically,
+%has a large momentum and the flying direction is unknown.
+the kinematics fit is no longer feasible due to extra neutrino from $W\rightarrow \ell\nu$ decay. The kinematic variables are calculated using the visible
+objects only. After the event reconstruction, a number of variables are used to discriminate the signal from the background using a multivariate analysis described
+in Section~\ref{sec:tmva}.
 
-With the event topology reconstructed, a number of variables are defined for signal and background separation used in the multivariate analysis discussed below.
+%With the event topology reconstructed, a number of variables are defined for signal and background separation used in the multivariate analysis discussed below.
 
@@
 \subsection{Multivariate discriminant}
+\label{sec:tmva}
 
@@
 \begin{table*}[t!]
-\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for hadronic channel. 
+  \caption{\small{Discriminating variables used in the training of the BDT for hadronic channel.
+      The values in percent (\%) represent the separation and importance of each variable.
     The descriptions of each variable are provided in the following text.}}
@@
 \begin{table*}[t!]
-\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for leptonic channel. 
+  \caption{\small{Discriminating variables used in the training of the BDT for leptonic channel.
+      The values in percent (\%) represent the separation and importance of each variable.
     The descriptions of each variable are provided in the following text.}}
@@
 
-Boosted decision trees are used in each SR to improve the separation between signal and background. 
+Boosted decision trees (BDT)~\cite{Hocker:2007ht} are used in each SR to improve the separation between signal and background. 
 %The separate training exploits differences in event kinematics across SRs.  
 %draft 1 version
-In the training, All signal events, $tt(qH)$ and $tH$ are merged together, are used for $tuH$ and $tcH$ against the total SM background (including both real and fake $\had$ contributions).
+In the training, all signal events from $tt(qH)$ and $tH$ are merged together for $tuH$ and $tcH$. All background sources from SM processes
+(including both real and fake $\had$ contributions) are also used in the training.
 
@@
 The discrimination of a given variable is quantified by the "separation"(measures the degree of overlap between background and signal shape) and "importance"(depicts the power of the variable to the classification of two distributions) provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 2\% were kept.
-The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_xTFW} and~\ref{tab:importance_tthML}, as defined in the following:
+The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_xTFW} and~\ref{tab:importance_tthML}. The discriminating variables used are:
 \begin{itemize}
-\item $\MET$ is the missing transverse momentum.
+\item $\met$ is the missing transverse momentum.
 \item $P_{\text{T,\tauhadvis}} $ is the transverse momentum of the leading tau candidate.
 \item $P_{\text{T,sub}-\tau}$ is the transverse momentum of the sub-leading tau candidate.
-\item $P_{\text{T},\ell}$ is the transverse momentum of the leading lepton.
-\item $\chi^2$ is derived from kinematic fitting for the neutrinos.
+\item $P_{\text{T},\ell}$ is the transverse momentum of the leading light lepton.
+\item $\chi^2$ derived from the kinematic fit of the neutrino momentum.
 \item $m_{t,\text{SM}}$ is the invariant mass of the $b$-jet and the two jets from the $W$ decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
@@
 \item $m_{\tau,\tau}$ is the fitted invariant mass of the tau candidates and reconstructed neutrinos in the $t_hH$, $t_ht(qH)$ channels. 
-\item $m_{\text{W}}$ is the reconstructed invariant mass of the hadronic $W$ boson from SM top quark.
+\item $m_{\text{W}}$ is the reconstructed invariant mass of two light-jets from the $W$ decay with the mass closet to the $W$ mass.
 \item $m_{\text{t},\text{FCNC}}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
@@
 \item $P_{\text{T},\tau\tau,\text{vis}}$ is the $\pT$ of the di-tau candidates.
-\item $m_{\text{t},\text{SM},\text{vis}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
-\item $m_{\text{t},\text{SM},\text{vis}}$ is the invariant mass of the lepton and the b-jet, which reflects the visible SM top mass.
-\item $M(\tau\tau \text{qjet},\text{min})$ is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative of variable $m_{\text{t},\text{FCNC},\text{vis}}$.
-\item $M(\text{wjet1},\text{wjet2},\text{min})$ is the invariant mass of two light-flavor jet, minimized by choosing different jets, reflects the invariant mass of the W candidate, an alternative of $m_{\text{W}}$.
-\item $E^{T}_{miss}$ centrality is a measure of how central the $\met$ lies between the two tau candidates in the transverse plane, and is defined as
+\item $m_{\text{t},\text{FCNC},\text{vis}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
+\item $m_{\text{t},\text{SM},\text{vis}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible SM top mass.
+\item \text{Min}($M_{\tau\tau \text{q-jet}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative of variable $m_{\text{t},\text{FCNC},\text{vis}}$.
+\item \text{Min}($M_{\text{light-jet},\text{light-jet}}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.
+  %an alternative of $m_{\text{W}}$.
+\item $\met$ centrality is a measure of how central the $\met$ lies between the two tau candidates in the transverse plane, and is defined as
 \begin{eqnarray}
@@
 \met~\text{centrality} = {(x+y)}/{\sqrt{x^2+y^2}}, \\
-\text{with}~x=\frac{\sin(\phi_{\text{miss}}-\phi_{\tau_1})}{\sin(\phi_{\tau_2}-\phi_{\tau_1})},  y=\frac{\sin(\phi_{\tau_2}-\phi_{\text{miss}})}{\sin(\phi_{\tau_2}-\phi_{\tau_1})} ,
+\text{with}~x=\frac{\sin(\phi_{\text{miss}}-\phi_{\tau_1})}{\sin(\phi_{\tau_2}-\phi_{\tau_1})}, \quad  y=\frac{\sin(\phi_{\tau_2}-\phi_{\text{miss}})}{\sin(\phi_{\tau_2}-\phi_{\tau_1})} ,
 \end{array}
@@
 For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}.
-\item $\Delta R(\ell+\text{bjet},\tau\tau)$ is the angular distance between the lepton+b-jet and di-tau candidates.
-\item $\Delta R(\ell,\text{bjet})$ is the angular distance between the lepton and b-jet.
-\item $\Delta R(\tau,\text{bjet})$ is the angular distance between the tau and b-jet. If there are two taus in the event, the leading one is selected for the calculation.
-\item $\eta_{\tau,\text{max}}$ is the maximum $\eta$ value among the tau candidates.
+\item $\Delta R(\ell+\text{b-jet},\tau\tau)$ is the angular distance between the lepton+$b$-jet and di-tau candidates.
+\item $\Delta R(\ell,\text{b-jet})$ is the angular distance between the lepton and $b$-jet.
+\item $\Delta R(\tau,\text{b-jet})$ is the angular distance between the tau and $b$-jet. If there are two taus in the event, the leading one is selected for the calculation.
+\item \text{Max}($\eta_{\tau}$) is the maximum $\eta$ value among the tau candidates.
 \item $\Delta R(\ell,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
-\item $\Delta R(\tau,\text{qjet})$ is the angular distance between the tau and the reconstructed $q$-jet. If there are two taus in the event, the leading one is used.
+\item $\Delta R(\tau,\text{q-jet})$ is the angular distance between the tau and the reconstructed $q$-jet. If there are two taus in the event, the leading one is used.
 \item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(\ell,\tau)$.
-\item $\Delta\phi(\tau\tau,P^{T}_{\text{miss}})$ is the azimuthal angle between the $\met$ and di-tau $\pT$.
+\item $\Delta\phi(\tau\tau,\met)$ is the azimuthal angle between the $\met$ and di-tau $\pT$.
+\item $\Delta R(\tau,\text{light-jet})$ is the minimum angle distance between the tau and the light-jet. If there are two taus in the event, the leading one is used.
 \end{itemize}
-A comparison between data and the predicted background for the leading $\had$ $\pt$ in the SRs 
+A comparison between data and the predicted background for the leading $\had$ $\pt$ distribution in the SRs 
 %some of these variables in three main decay final states($t_l\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
-is shown in Figures~\ref{fig:taupt_prefit}.
+is shown in Figure~\ref{fig:taupt_prefit}.
 %each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_lhadhad}.
@@
 %discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
-The expected signals are also shown after scaled up for the shape comparison of the distributions.
+%The expected signals are also shown after scaled up for the shape comparison of the distributions.
 %by a large factor normalized to the total number of events in the predicted
@@
 
-The final observable used to extract signal events is defined as the BDT distribution in each SRs corresponding to either $tuH$ or $tcH$ signal.
+The final observable used to extract signal events is defined as the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.
 %Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
@@
 Underflow and overflow bins are included respectively in the first and last bins.
-Rare including single top, and V+jets and only subtau real refers to t$\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution.
+Rare including single top, and V+jets and only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution.
 The lower panels show the ratios of the data ('Data') to the background prediction ('Bkg.')}
@@
 % \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}\\
-% (a1) BDT dicriminant in $t_l\thadhad$ & (a2) BDT dicriminant in  $t_l\tauhad$-1j& (a3) BDT dicriminant in $t_l\tauhad$-2j\\
+% (a1) BDT discriminant in $t_l\thadhad$ & (a2) BDT discriminant in  $t_l\tauhad$-1j& (a3) BDT discriminant in $t_l\tauhad$-2j\\
 % \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf} &
@@
 % \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/BDTG_test.pdf} \\
-% (b1) BDT dicriminant in $t_h\tlhad$-2j & (b2) BDT dicriminant in  $t_h\tlhad$-3j & (b3) BDT dicriminant in $t_h\thadhad$-2j \\
+% (b1) BDT discriminant in $t_h\tlhad$-2j & (b2) BDT discriminant in  $t_h\tlhad$-3j & (b3) BDT discriminant in $t_h\thadhad$-2j \\
 % \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/BDTG_test.pdf} & \\
-% (c1) BDT dicriminant in$t_h\thadhad$-3j\\
+% (c1) BDT discriminant in$t_h\thadhad$-3j\\
 % \end{tabular}

### 2022-02-16 sections/systematic_uncertainties.tex
update the draft to V03 with comments

@@
 using $\ttbar$ events~\cite{ATLAS-CONF-2018-001} or $W$+$c$-jet events~\cite{Aad:2015ydr}. 
-The light-jet efficiency is measured in a multijet data sample enriched in light-flavour jets~\cite{ATLAS-CONF-2018-006}.
+The light-jet efficiency is measured in a multi-jet data sample enriched in light-flavour jets~\cite{ATLAS-CONF-2018-006}.
 The uncertainties in these scale factors include a total of 44 independent sources affecting $b$-jets, 19 source affecting $c$-jets, and 19 sources affecting light-jets. 
@@
 The latter uses the MMHT2014 LO~\cite{Harland-Lang:2014zoa} PDF set in combination with the H7UE tune~\cite{Bellm:2015jjp}.
-The uncertainty in the modelling of additional radiation is assessed with two alternative {\powheg}+{\pythiaeight} samples:
-a sample with increased radiation (referred to as radHi) is obtained by decreasing the renormalisation and factorisation scales  
-by a factor of two, %doubling the $h_{\textrm{damp}}$ parameter,
-and using the Var3c upward variation of the A14 parameter set;
-a sample with decreased radiation (referred to as radLow) is obtained by increasing the scales by a factor of two 
-and using the Var3c downward variation of the A14 set~\cite{ATL-PHYS-PUB-2016-004}.
+The uncertainty in the modelling of additional radiation from the PS are assessed by
+varying the corresponding parameter of the A14 set~\cite{ATL-PHYS-PUB-2016-004} and by varying the radiation renormalisation and factorisation scales
+by a factor of 2.0 and 0.5, respectively. 
+%The uncertainty in the modelling of additional radiation is assessed with two alternative {\powheg}+{\pythiaeight} samples:
+%a sample with increased radiation (referred to as radHi) is obtained by decreasing the renormalisation and factorisation scales  
+%by a factor of two, %doubling the $h_{\textrm{damp}}$ parameter,
+%and using the Var3c upward variation of the A14 parameter set;
+%a sample with decreased radiation (referred to as radLow) is obtained by increasing the scales by a factor of two 
+%and using the Var3c downward variation of the A14 set~\cite{ATL-PHYS-PUB-2016-004}.
 
@@
 considered for these samples: the PDF variation considering the standard deviation of the 100 NNPDF replicas event weights of NNPDF3.0nnlo PDF
-set used in Sherpa, renormalisation($\mu_{R}$) and factorisation scales($\mu_{F}$),jet-to-parton matching uncertainty,resummation scale uncertainty,
+set used in Sherpa, renormalisation ($\mu_{R}$) and factorisation scales ($\mu_{F}$), jet-to-parton matching uncertainty, resummation scale uncertainty,
 variation in the choice of $\alpha_{S}$, alternative PDF variation evaluated comparing predictions from NNPDF3.0nnlo PDF set (nominal)
@@
 Uncertainties affecting the normalisation of the $V$+jets background are estimated separately for $V$+light-jets, $V$+$\geq$1$c$+jets,
-and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated within approximately 30\% by comparing the
+and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated approximately 30\% by comparing the
 data and total background prediction in the different analysis regions considered, but requiring exactly zero $b$-tagged jets.
@@
 following the recommendation in Ref.~\cite{deFlorian:2016spz}.
-The uncertainty of ISR, FSR, scale and PDF are considered in all SRs.
-The parton shower uncertainties is estimated by comparing the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}.
+The uncertainty of ISR, FSR, scale and PDF are considered in all SRs. The parton shower uncertainties is estimated by comparing
+the nominal to an alternative sample interfaced with {\herwig7}.
+%the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 
 %treated correlatedly with $\ttbar$ samples.

### 2022-02-16 ANA-TOPQ-2019-17-PAPER-metadata.tex

@@
 %-------------------------------------------------------------------------------
-
 % Title
 %\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
-\AtlasTitle{Search for flavour-changing neutral current $tqH$ ($q=u,c$) of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons
-                   in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector}
+\AtlasTitle{Search for flavour-changing neutral current $tqH$ of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons
+                   in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.1em}}
 
@@
 % Comment or remove in final version.
-\AtlasVersion{0.2}
+\AtlasVersion{0.3}
 % Abstract - % directly after { is important for correct indentation
@@
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
-CERN Large Hadron Collider and corresponds to an integrated luminosity of 139 fb$^{-1}$.
+Large Hadron Collider and corresponds to an integrated luminosity of 139 fb$^{-1}$.
 Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
@@
 The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
-as well as multiple jets.  
-Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
-No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
+as well as multiple jets and event kinematics are used to separate signal from the background through a multivariate discriminant.  
+%Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
+%No significant excess of events above the background expectation is found,
+There is an excess of data events observed above background with a significance of 2.6$\sigma$,
+and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
 Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $0.099\%$ ($0.050^{+0.022}_{-0.014}\%$)
@@
 % Comment deadline
-\AtlasCoverCommentsDeadline{1 January 2022}
+\AtlasCoverCommentsDeadline{1 March 2022}
 

### 2022-02-16 sections/data_presel.tex

@@
 %For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
-For di-$\tau$ triggers, the $\pt$ threshold of the leading (trailing) $\had$ candidate is 35 (25)~\gev.
+For di-$\tau$ triggers, the $\pt$ threshold of the leading (subleading) $\had$ candidate is 35 (25)~\gev.
 Events satisfying the trigger selection are required to have at least one primary vertex candidate.
+To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have \pt 1~GeV above the threshold.
 
 The signal final state including an electron or muon or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
-
 The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger.
@@
 
-The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and trailing $\had$ passed the trigger. Further requirements are defined targeting signal decay modes:
+The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and subleading $\had$ passed the trigger.
+Further requirements are defined targeting signal decay modes:
 \begin{itemize}
@@
 \caption{\small{Summary of preselection requirements. 
-The leading and trailing $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
+The leading and subleading $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
 \begin{center}
@@
 \multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multirow{2}{*}{hadronic channel} \\ 
-& $t_h\lephad$ & $t_l\hadhad$ &  $t_l\had$ & \\
+& $t_h\lephad$ & $t_l\hadhad$ &  $t_l\had$ & $t_h\hadhad$\\
 \midrule

### 2022-02-16 sections/statistical_analysis.tex

@@
 
-In the absence of signal, exclusion limits are set on $\mu$ , and thus on
+%In the absence of signal,
+Exclusion limits are set on $\mu$ , and thus on
 $\BR(t\to qH)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.

### 2022-02-18 ANA-TOPQ-2019-17-PAPER-metadata.tex
major update v1.0

@@
 % Comment or remove in final version.
-\AtlasVersion{0.3}
+\AtlasVersion{1.0}
 % Abstract - % directly after { is important for correct indentation
 \AtlasAbstract{%
-A search for flavour-changing neutral current $tqH$ interactions with a top quark, an up-type quark ($q=u, c$), and a
-Standard Model Higgs boson is presented. The Higgs boson decays into a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
+A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, an up-type quark ($q=u, c$), and a
+Standard Model Higgs boson decaying into a $\tau$-lepton pair ($H\rightarrow \tau^+\tau^-$) is presented.
+%The Higgs boson decays into a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
@@
 Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
-which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow qH$. 
+which one of top quarks decays into $Wb$ and the other decays into $qH$ through the FCNC interactions.
+%top quark with FCNC decay of $t\rightarrow qH$. 
 The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
@@
 %No significant excess of events above the background expectation is found,
-There is an excess of data events observed above background with a significance of 2.6$\sigma$,
+A slight excess of data is observed above background with a significance of 2.6$\sigma$,
 and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.

### 2022-02-18 sections/conclusion.tex
major update v1.0

@@
 %-------------------------------------------------------------------------------
-A search for flavour-changing neutral current process involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented.
+A search for flavour-changing neutral current processes involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented.
 FCNC $tqH$ interaction is searched for both in $t\bar{t}$ decay mode, where one top quark decays following SM processes and the other one decays through $t\rightarrow Hq$, and in production mode($pp\rightarrow tH$) with a single top quark produced via FCNC interaction where $t\to Wb$.
@@
 %No significant excess of events above the background expectation is found.
-There is an excess of data events observed above background with a significance of 2.6$\sigma$.  
+A slight excess of data is observed above background with a significance of 2.6$\sigma$.  
 We set 95\% CL upper limits on the $t\to Hq$ branching ratios and the corresponding
-dimension-6 operator Wilson coefficients in the effective $tqH$ coupling. 
+dimension-6 operator Wilson coefficients in the effective $tqH$ couplings. 
 %about a factor of 2 improvement to 95\% CL upper limits on the $t\to Hq$ branching ratios are reported in Table~\ref{tab:limits_summary}, along with the Wilson coefficients with respect to the previous partial run-2 results~\cite{Aaboud2019SearchFT}.

### 2022-02-18 sections/introduction.tex
major update v1.0

@@
 In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
-The $t\to qH$ branching fraction in the SM is calculated to be exceedingly small around $10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}.
+The $t\to qH$ branching fraction in the SM is calculated to be exceedingly small, around $10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}.
 %such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
@@
 In contrast, large enhancements of these branching ratios are possible in some scenarios beyond the SM.
-Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{Branco:2hdm2012} with or without the flavour violation,
+Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{Branco:2hdm2012} with or without flavour violation,
 %of type I, with explicit flavour conservation,
@@
 production cross section of $pp\rightarrow tH$.
-So the study on this process will also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
+So the study of this process will also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
 The $tH$ associated production in the SM is expected to have a small cross section of $92^{+7}_{-12}$ fb at LHC centre of mass energy~\cite{deFlorian:2016spz}.
@@
 $t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
-Finally, multivariate technique is used to discriminate between the signal and the background on the basis of their different kinematics.
+Finally, a multivariate technique, boosted decision trees, is used to discriminate between the signal and the background on the basis of their different kinematics distributions.
 

### 2022-02-18 sections/strategy_Htautau.tex
major update v1.0

@@
 
-The $tt(qH)$ and $tH$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
+The $tt(qH)$ and $tH$ signal being probed are characterised by the presence of $\tau$-leptons from the decay of 
 the Higgs boson, where the remaining top quark decays into $Wb$. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
@@
 This event categorisation is primarily motivated by optimizing the sensitivity in each signal region that targets either leptonic or hadronic top-quark
-decays as well as the Higgs decays into either $\lephad$ or $\hadhad$ final state.   
-The event kinematic reconstruction is further applied in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the
+decays as well as the Higgs decays into either $\lephad$ or $\hadhad$ final states.   
+The event kinematic reconstruction is used in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the
 di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}. 
@@
 decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
-There should be at least four jets among which with the closest angular distance to the visible decay of the di-taus
-is considered as $q$-jet since the FCNC top decay products are likely boosted closer together than other jets. 
-If there are more than two jets beside $q$-jet and $b$-jet, the jets from $W$ boson decay are chosen from the combination
-with the invariant mass closest to W resonance. There is the chance that one of the jets fails the $\pt$ requirement and not reconstructed.
+There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
+is considered as the $q$-jet since the FCNC top decay products are likely boosted closer together than other jets. 
+If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
+with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and not reconstructed.
 This kind of events will fall into $t_hH$.
@@
 \item $m_{\tau\tau,\text{vis}}$ is the visible invariant mass of the di-tau candidates. %or the lepton and $\had$ candidate when there is only one $\had$.
-\item $P_{\text{T},\tau\tau,\text{vis}}$ is the $\pT$ of the di-tau candidates.
+\item $P_{\text{T},\tau\tau,\text{vis}}$ is the visible $\pT$ of the di-tau candidates.
 \item $m_{\text{t},\text{FCNC},\text{vis}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
-\item $m_{\text{t},\text{SM},\text{vis}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible SM top mass.
-\item \text{Min}($M_{\tau\tau \text{q-jet}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative of variable $m_{\text{t},\text{FCNC},\text{vis}}$.
+\item $m_{\text{t},\text{SM},\text{vis}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top quark mass.
+\item \text{Min}($M_{\tau\tau \text{q-jet}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\text{t},\text{FCNC},\text{vis}}$.
 \item \text{Min}($M_{\text{light-jet},\text{light-jet}}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.
@@
 \item $\Delta R(\ell,\text{b-jet})$ is the angular distance between the lepton and $b$-jet.
-\item $\Delta R(\tau,\text{b-jet})$ is the angular distance between the tau and $b$-jet. If there are two taus in the event, the leading one is selected for the calculation.
+\item $\Delta R(\tau,\text{b-jet})$ is the angular distance between the tau candidate and $b$-jet. If there are two taus in the event, the leading one is selected for the calculation.
 \item \text{Max}($\eta_{\tau}$) is the maximum $\eta$ value among the tau candidates.
 \item $\Delta R(\ell,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
-\item $\Delta R(\tau,\text{q-jet})$ is the angular distance between the tau and the reconstructed $q$-jet. If there are two taus in the event, the leading one is used.
+\item $\Delta R(\tau,\text{q-jet})$ is the angular distance between the tau candidate and the reconstructed $q$-jet. If there are two taus in the event, the leading one is used.
 \item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(\ell,\tau)$.
 \item $\Delta\phi(\tau\tau,\met)$ is the azimuthal angle between the $\met$ and di-tau $\pT$.
-\item $\Delta R(\tau,\text{light-jet})$ is the minimum angle distance between the tau and the light-jet. If there are two taus in the event, the leading one is used.
+\item $\Delta R(\tau,\text{light-jet})$ is the minimum angle distance between the tau candidate and the light-jet. If there are two taus in the event, the leading one is used.
 \end{itemize}
@@
 The first and the last bins in the figures contain the underflow and overflow respectively.
-The bottom panel displays the ratio of data to the background (``Bkg'') prediction.
+The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model} below.
 The hashed area represents the total uncertainty of the background.
 A good description of the data by the background model is observed in all cases.
-
 The final observable used to extract signal events is defined as the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.

### 2022-02-18 sections/systematic_uncertainties.tex
major update v1.0

@@
 Another significant background in hadronic channel stems from the $Z\rightarrow \tau\tau$ samples, several sources of uncertainty are
-considered for these samples: the PDF variation considering the standard deviation of the 100 NNPDF replicas event weights of NNPDF3.0nnlo PDF
+considered for these samples: the PDF variation considering the standard deviation of the 100 NNPDF replicas event weights
+of NNPDF3.0nnlo~\cite{Ball:2015NNPDF} PDF
 set used in Sherpa, renormalisation ($\mu_{R}$) and factorisation scales ($\mu_{F}$), jet-to-parton matching uncertainty, resummation scale uncertainty,
 variation in the choice of $\alpha_{S}$, alternative PDF variation evaluated comparing predictions from NNPDF3.0nnlo PDF set (nominal)
-with MMHT2014nnlo68cl and CT14nnlo PDF sets.
+with MMHT2014nnlo68cl and CT14nnlo~\cite{Lai:2010vv,Gao:2013xoa} PDF sets.
 
@@
 
-The statistical uncertainties of the fake $\had$ background calibration in the leptonic channel is applied with uncorrelated uncertainties for different fake $\had$ source and different $\pt$ slices.
-The uncertainties of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both statistical fluctuation and the differences between signal regions.
-
-The uncertainties of the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.
+The statistical uncertainties on the fake $\had$ background calibration in the leptonic channel are applied with uncorrelated uncertainties for different fake $\had$ sources and
+different $\pt$ slices. The uncertainty of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both,
+its statistical fluctuation and the differences between signal regions.
+The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.
 
@@
 following the recommendation in Ref.~\cite{deFlorian:2016spz}.
-The uncertainty of ISR, FSR, scale and PDF are considered in all SRs. The parton shower uncertainties is estimated by comparing
+The uncertainty of ISR, FSR, scale and PDF are considered in all SRs. The parton shower uncertainties are estimated by comparing
 the nominal to an alternative sample interfaced with {\herwig7}.
@@
 \begin{table}[htbp]
-\caption{List of relative uncertainties of the signal strength from the combined fit in hadronic channel.
+\caption{List of relative uncertainties of the signal strength from the combined fit in the hadronic channels.
 The uncertainties are symmetrised for presentation and grouped into the categories described in the text.
@@
 \begin{table}[htbp]
-\caption{List of relative uncertainties of the signal strength from the combined fit in leptonic channel.
+\caption{List of relative uncertainties of the signal strength from the combined fit in the leptonic channels.
 The uncertainties are symmetrised for presentation and grouped into  the categories described in the text.

### 2022-02-18 sections/introduction.tex
updates tables

--- 2022-02-16 sections/introduction.tex
@@
 %of $\BR(H\to b\bar{b})\simeq 58\%$.
-Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
+Compared to Run~1, the Run~2 searches(~\ref{tab:limits_summary}) benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
 Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of
@@
 $pp \to tH$ production~\cite{Greljo:2014dka}.
+
+\begin{table}[t!]
+\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$.}}
+\begin{center}
+\begin{tabular}{lcc}
+\toprule\toprule
+ & \multicolumn{1}{c}{95\% CL upper observed limits} & \multicolumn{1}{c}{95\% CL observed upper limits}  \\
+ & \multicolumn{1}{c}{on $\BR(t \to Hc)$} & \multicolumn{1}{c}{on $\BR(t \to Hu)$} \\
+\midrule\midrule
+ATLAS $H \to b\bar{b}$~\cite{fcnc36} & $4.2 \times 10^{-3}$ & $5.2 \times 10^{-3}$ \\
+ATLAS $H \to \tau\tau$ ($\lephad$, $\hadhad$)~\cite{fcnc36} & $1.9 \times 10^{-3}$  & $1.7 \times 10^{-3}$  \\ 
+ATLAS $H \to WW^*, \tau\tau, ZZ^*$ ($2\ell$SS, $3\ell$)~\cite{Aaboud:2018pob}  & $1.6 \times 10^{-3}$  & $1.9 \times 10^{-3}$  \\ 
+ATLAS $H \to \gamma\gamma$~\cite{Aaboud:2017mfd} & $2.2 \times 10^{-3}$  & $2.4 \times 10^{-3}$  \\
+CMS   $H\to b\bar{b}$~\cite{Sirunyan:2017uae} & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
+\midrule
+\bottomrule\bottomrule
+\end{tabular}
+\label{tab:limits_summary}
+\end{center}
+\end{table}
 

### 2022-02-18 sections/strategy_Htautau.tex
updates tables

--- 2022-02-16 sections/strategy_Htautau.tex
@@
 \begin{table*}[t!]
-  \caption{\small{Discriminating variables used in the training of the BDT for hadronic channel.
-      The values in percent (\%) represent the separation and importance of each variable.
+\caption{\small{Discriminating variables used in the training of the BDT.
+The values represent the importance rankings of each variable and cross($\times$) denotes the variable is not used in the training.
 The descriptions of each variable are provided in the following text.}}
-\label{tab:importance_xTFW}
-\input{tables/xTFW_Merged}
+\label{tab:importance}
+ \centering
+ \begin{tabular}{cccccccc} \toprule\toprule
+& $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_l\thadhad$     & $t_h\thadhad$-2j & $t_h\thadhad$-3j       \\\midrule 
+ $m_{\text{W}}$                                      & $\times$  &  $\times$           &  $\times$         & $9$      & $\times$      & $6$      & $7$\\
+ $\chi^{2}$                                          & $\times$  &  $\times$           &  $\times$         & $14$     & $\times$      & $\times$ & $\times$      \\
+ \text{max}($\eta_{\tau}$)                           & $4$       &  $\times$           &  $4$              & $\times$ & $10$          & $\times$ & $\times$       \\
+ $m^{\text{T}}_{\text{W}}$                           & $10$      &  $\times$           &  $8$              & $\times$ & $13$          & $\times$ & $\times$        \\
+ $m_{\tau,\tau}$                                     & $\times$  &  $2$                &  $\times$         & $3$      & $\times$      & $1$      & $1$          \\
+ $m_{\text{t},\text{SM}}$                            & $\times$  &  $1$                &  $\times$         & $2$      & $\times$      & $3$      & $4$          \\
+ $p_{\text{T},\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     & $\times$      & $\times$ & $\times$        \\
+ $m_{\text{t},\text{FCNC}}$                          &  $\times$ &  $\times$           &  $\times$         & $\times$ & $\times$      & $10$     & $6$\\
+ $m_{\text{t},\text{SM},\text{vis}}$                 & $3$       &  $\times$           &  $5$              & $\times$ & $4$           & $\times$ & $\times$        \\
+ $p_{\text{T},\tau}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
+ $\met$                                              & $5$       &  $11$               &  $10$             & $13$     & $6$           & $7$    & $13$          \\
+ $m_{\tau\tau,\text{vis}}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
+ $E_{\text{vis}~\tau,1}/E_{\tau,1}$                  & $\times$  &  $10$               &  $\times$         & $12$     & $\times$      & $8$    & $8$          \\
+ $E_{\text{vis}~\tau,2}/E_{\tau,2}$                  & $\times$  &  $7$                &  $\times$         & $4$      & $\times$      & $9$    & $11$         \\
+ $P_{\text{T,\tauhadvis}} $                          & $\times$  &  $\times$           &  $\times$         & $\times$ & $9$           & $\times$ & $\times$        \\
+ $m_{\text{t},\text{FCNC},\text{vis}}$               & $\times$  &  $\times$           &  $\times$         & $\times$ & $3$           & $\times$ & $\times$       \\
+ $\Delta\phi(\tau\tau,\met)$                         & $\times$  &  $6$    			   &  $\times$         & $16$     & $\times$      & $13$   & $12$         \\
+ $\met\text{centrality}$                             & $\times$  &  $13$               &  $\times$         & $15$     & $\times$      & $12$   & $9$         \\
+ \text{Min}($m_{\tau\tau \text{q-jet}}$)             & $9$       &  $\times$           &  $3$              & $\times$ & $14$          & $\times$ & $\times$        \\
+ $\Delta R(\ell,\tau)$                               & $8$       &  $9$                &  $9$              & $10$     & $15$          & $\times$ & $\times$        \\
+ $\Delta R(\tau,\tau)$                               & $\times$  &  $\times$           &  $\times$         & $\times$ & $2$           & $4$    & $3$             \\
+ $\Delta R(\ell,\text{b-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          & $\times$ & $\times$        \\
+ $\Delta R(\tau,\text{b-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          & $\times$ & $\times$       \\
+ $\Delta R(\ell+\text{b-jet},\tau\tau )$             & $\times$  &  $\times$           &  $\times$         & $\times$ & $7$           & $\times$ & $\times$        \\
+ $\Delta R(\tau,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
+ \text{Min}($m_{\text{light-jet},\text{light-jet}}$) & $\times$  &  $12$               &  $\times$         & $11$     & $\times$      & $\times$ & $\times$        \\
+ \bottomrule\bottomrule\\
+ \end{tabular}
 \end{table*}
 
-\begin{table*}[t!]
-  \caption{\small{Discriminating variables used in the training of the BDT for leptonic channel.
-      The values in percent (\%) represent the separation and importance of each variable.
-    The descriptions of each variable are provided in the following text.}}
-\label{tab:importance_tthML}
-\input{tables/tthML_Merged}
-\end{table*}
+%%%%%%%%%%%%%%%
+%%%  \begin{table*}[t!]
+%%%    \caption{\small{Discriminating variables used in the training of the BDT for hadronic channel.
+%%%        The values in percent (\%) represent the separation and importance of each variable.
+%%%      The descriptions of each variable are provided in the following text.}}
+%%%  \label{tab:importance_xTFW}
+%%%  \input{tables/xTFW_Merged}
+%%%  \end{table*}
+%%%  
+%%%  \begin{table*}[t!]
+%%%    \caption{\small{Discriminating variables used in the training of the BDT for leptonic channel.
+%%%        The values in percent (\%) represent the separation and importance of each variable.
+%%%      The descriptions of each variable are provided in the following text.}}
+%%%  \label{tab:importance_tthML}
+%%%  \input{tables/tthML_Merged}
+%%%  \end{table*}
 
@@
 The discrimination of a given variable is quantified by the "separation"(measures the degree of overlap between background and signal shape) and "importance"(depicts the power of the variable to the classification of two distributions) provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 2\% were kept.
-The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_xTFW} and~\ref{tab:importance_tthML}. The discriminating variables used are:
+The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance}. The discriminating variables used are:
 \begin{itemize}

### 2022-02-18 sections/systematic_uncertainties.tex
updates tables

--- 2022-02-16 sections/systematic_uncertainties.tex
@@
 
-\begin{table}[htbp]
-\caption{List of relative uncertainties of the signal strength from the combined fit in hadronic channel.
-The uncertainties are symmetrised for presentation and grouped into the categories described in the text.
-%The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
+\begin{table}[h!]
+\caption{List of relative uncertainties of the signal strength from the combined fit. The uncertainties are symmetrised for presentation and grouped into the categories described in the text.}
+\label{tab:had_sys_impact}
+\begin{center}
+\begin{tabular}{%
+@{}l%
+S%
+S%
+@{}%
 }
-\small
-\centering
-\begin{tabular}{cc} \toprule\toprule
-$\text{Uncertainty}    $   & $\Delta\mu/\mu[\%]$ \\\midrule
-$\text{Fake modelling} $   & $13.5$ \\
-$\text{Instrument}     $   & $2.6$  \\
-$\text{Jets}           $   & $1.7$   \\
-$\text{Met}            $   & $0.4$   \\
-$\tau                  $   & $7.2$    \\
-$\text{b-tagging}       $  & $0.3$    \\
-$\text{Signal Theory}  $   & $1.5$   \\
-$\text{Other MC theory} $  & $2.7$    \\
-$t\bar{t} \text{theory}$  & $7.6$     \\\midrule
-$\text{Statistics}      $  & $11.2$   \\
-$\text{Total systematic}$  & $24.2$  \\ \midrule
-$\text{Total}  $           & $26.7$ \\
-\bottomrule\bottomrule
+\toprule
+\multirow{2}{*}{Source of uncertainty}      & \multicolumn{2}{c}{$\Delta\mu/\mu [\%]$} \\
+                                            & \multicolumn{1}{c}{$t\rightarrow uH$} & \multicolumn{1}{c}{$t\rightarrow cH$} \\\midrule
+Lepton                                  & 0.6           &1.0         \\
+Met                                     & 0.7           &0.8         \\
+Luminosity and Pileup                   & 1.0           &1.3         \\
+Theoretical uncertainty in other MC     & 2.1           &2.9         \\
+Jets                                    & 2.4           &3.2         \\
+Flavour tagging                         & 2.7           &3.7         \\
+Misidentified $\tau$                    & 3.4           &4.8         \\
+Theoretical uncertainty in $t\bar{t}$   & 2.9           &4.3         \\
+Hadronic $\tau$ decays                  & 3.3           &4.4         \\
+Theoretical uncertainty in signal       & 5.3           &7.0         \\\midrule
+Total statistics uncertainty            & 5.1           &7.0         \\
+Total systematic uncertainty            & 11.2          &15.4        \\ \midrule
+Total                                   & 12.3          &16.9        \\
+\bottomrule
 \end{tabular} 
-\label{tab:had_sys_impact}
+\end{center}
 \end{table}
 
-\begin{table}[htbp]
-\caption{List of relative uncertainties of the signal strength from the combined fit in leptonic channel.
-The uncertainties are symmetrised for presentation and grouped into  the categories described in the text.
-%The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
-}
-\small
-\centering
-\begin{tabular}{cc} \toprule\toprule
-$\text{Uncertainty}        $ & $  \Delta\mu/\mu[\%]  $\\\midrule
-$\text{Fake modelling}     $ & $       2.1             $\\
-$\text{Instrument}         $ & $       0.7             $\\
-$\text{Jets}               $ & $       2.8             $\\
-$\text{Met}                $ & $       1.2             $\\
-$\text{Lepton}             $ & $       0.7             $\\
-$\tau                      $ & $       2.3             $\\
-$\text{b-tagging}          $ & $       4.8             $\\
-$\text{Signal Theory}      $ & $       6.9             $\\
-$\text{Other MC theory}    $ & $       2.1             $\\
-$t\bar{t} \text{theory}    $ & $       3.7             $\\\midrule
-$\text{Statistics}         $ & $       5.9             $\\
-$\text{Total systematic}   $ & $       12.9            $\\\midrule
-$\text{Total}              $ & $       14.2            $\\
-\bottomrule\bottomrule
-\end{tabular}
-\label{tab:lep_sys_impact}
-\end{table}
+%% Fake method    0.0476721  ( +0.0476721, -0.0476721 )
+%% FullSyst    0.154686  ( +0.154686, -0.154686 )
+%% Gammas    0.0700708  ( +0.0700708, -0.0700708 )
+%% Instrument    0.0131647  ( +0.0131647, -0.0131647 )
+%% JET    0.0320897  ( +0.0320897, -0.0320897 )
+%% Lepton    0.0104552  ( +0.0104552, -0.0104552 )
+%% MET    0.00841447  ( +0.00841447, -0.00841447 )
+%% SignalTheory    0.0699833  ( +0.0699833, -0.0699833 )
+%% TAU    0.0437292  ( +0.0437292, -0.0437292 )
+%% Theory    0.029182  ( +0.029182, -0.029182 )
+%% btag    0.0367613  ( +0.0367613, -0.0367613 )
+%% ttbarTheory    0.0427391  ( +0.0427391, -0.0427391 )
+
+%% Fake method   0.0341326  ( +0.0341326, -0.0341326 )
+%% FullSyst      0.112111      ( +0.112111, -0.112111 )
+%% Gammas        0.0509968       ( +0.0509968, -0.0509968 )
+%% Instrument    0.0093934  ( +0.0093934, -0.0093934 )
+%% JET           0.0235705  ( +0.0235705, -0.0235705 )
+%% Lepton        0.00568277  ( +0.00568277, -0.00568277 )
+%% MET           0.00704844  ( +0.00704844, -0.00704844 )
+%% SignalTheory  0.0526104  ( +0.0526104, -0.0526104 )
+%% TAU           0.032714  ( +0.032714, -0.032714 )
+%% Theory        0.0210686  ( +0.0210686, -0.0210686 )
+%% btag          0.027376  ( +0.027376, -0.027376 )
+%% ttbarTheory   0.0289194  ( +0.0289194, -0.0289194 )
+
+%\begin{table}[htbp]
+%\caption{List of relative uncertainties of the signal strength from the combined fit in hadronic channel.
+The uncertainties are symmetrised for presentation and %grouped into the categories described in the text.
+%The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations %introduced by the fit
+%}
+%\small
+%\centering
+%\begin{tabular}{cc} \toprule\toprule
+%$\text{Uncertainty}    $   & $\Delta\mu/\mu[\%]$ \\\midrule
+%$\text{Fake modelling} $   & $13.5$ \\
+%$\text{Instrument}     $   & $2.6$  \\
+%$\text{Jets}           $   & $1.7$   \\
+%$\text{Met}            $   & $0.4$   \\
+%$\tau                  $   & $7.2$    \\
+%$\text{b-tagging}       $  & $0.3$    \\
+%$\text{Signal Theory}  $   & $1.5$   \\
+%$\text{Other MC theory} $  & $2.7$    \\
+%$t\bar{t} \text{theory}$  & $7.6$     \\\midrule
+%$\text{Statistics}      $  & $11.2$   \\
+%$\text{Total systematic}$  & $24.2$  \\ \midrule
+%$\text{Total}  $           & $26.7$ \\
+%\bottomrule\bottomrule
+%\end{tabular}
+%\label{tab:had_sys_impact}
+%\end{table}
+
+%\begin{table}[htbp]
+%\caption{List of relative uncertainties of the signal strength from the combined fit in leptonic channel.
+The uncertainties are symmetrised for presentation and %grouped into  the categories described in the text.
+%The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations %introduced by the fit
+%}
+%\small
+%\centering
+%\begin{tabular}{cc} \toprule\toprule
+%$\text{Uncertainty}        $ & $  \Delta\mu/\mu[\%]  $\\\midrule
+%$\text{Fake modelling}     $ & $       2.1             $\\
+%$\text{Instrument}         $ & $       0.7             $\\
+%$\text{Jets}               $ & $       2.8             $\\
+%$\text{Met}                $ & $       1.2             $\\
+%$\text{Lepton}             $ & $       0.7             $\\
+%$\tau                      $ & $       2.3             $\\
+%$\text{b-tagging}          $ & $       4.8             $\\
+%$\text{Signal Theory}      $ & $       6.9             $\\
+%$\text{Other MC theory}    $ & $       2.1             $\\
+%$t\bar{t} \text{theory}    $ & $       3.7             $\\\midrule
+%$\text{Statistics}         $ & $       5.9             $\\
+%$\text{Total systematic}   $ & $       12.9            $\\\midrule
+%$\text{Total}              $ & $       14.2            $\\
+%\bottomrule\bottomrule
+%\end{tabular}
+%\label{tab:lep_sys_impact}
+%\end{table}

### 2022-02-18 sections/background_estimation.tex

%-------------------------------------------------------------------------------
\section{Background estimation}
\label{sec:background_model}
%-------------------------------------------------------------------------------

Most background processes are modelled using Monte Carlo (MC) simulation.
After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
Small contributions arise from single-top-quark, $W/Z$+jets, multi-jet and diboson ($WW,WZ,ZZ$) production, as well as from the associated 
production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
with prompt leptons, i.e.\ those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
In the simulation, the top-quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
and the Higgs boson is forced to decay into $H\to \tau\tau$ with branching ratio calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
Backgrounds with non-prompt light leptons (electron or muon), with photons or jets misidentified as electrons, or with jets misidentified as $\had$ candidates, 
generically referred to as \texttt{fake} leptons, are estimated using data-driven methods. 
The background prediction is further improved during the statistical analysis by performing a likelihood 
fit to data using several signal-depleted analysis regions, as discussed in Sections~\ref{sec:strategy_Htautau}.

%-------------------------------------------------------------------------------
%\subsection{Backgrounds with fake leptons}
%\label{sec:fakeleptons}
%-------------------------------------------------------------------------------
\subsection{Backgrounds with fake $\had$ leptons}
\label{sec:faketaus}
The background with one or more fake $\had$ candidates mainly arises from $\ttbar$ or
multi-jet production, depending on the search channels.
Studies based on simulation show that, for all the above processes, fake $\had$ candidates primarily result from the
misidentification of light jets and $b$-quark jets.
It is also found that the fake rate decreases for all jet flavours as the $\had$ candidate $\pt$ increases.

In the leptonic channels, the events with prompt electron or muon and fake taus are modelled by calibrating MC with scale factors (SF)
derived from the dedicated $t\bar t$
control regions ($CR_{tt}$) using dileptonic decays of $t\bar t$ events and semileptonic decays of $t\bar t$ events with two
$b$-tagged jets, summarized in Table~\ref{tab:srcr}. 	
%the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
%aimed at fake taus from different origins.
There are four kinds of fake taus that need to be calibrated: Type-1 fake taus from $W$-jets ($\tau_{W}$)
with opposite-sign (OS) of charge to the light lepton;
Type-2 $\tau_{W}$'s with same-sign (SS) charge to the light lepton; Type-3 fake taus originating from $b$-hadron decays; Type-4 fake taus from light-flavour hadron decays.
The control regions are defined similar to the signal regions but with an additional $b$-jet or light lepton.
%$t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
The dilepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate Type-3 and Type-4 fake taus. The semileptonic
regions ($t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS) where $\thad$ and light lepton have opposite charge are used to calibrate Type-1 fake taus.
Similarly for Type-2, the semileptonic regions ($t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS) where $\thad$ and light lepton have same charge are used.
A simultaneous fit to data is made to derive the scale factors for fake taus in MC, which consist of total of 24 parameters
depending on four types, three $\pt$ bins, two bins for 1- and 3-prong taus separately.
These scale factors are then used to correct the MC estimated fakes in the corresponding  signal regions with a single $b$-tagged jet.
In the $t_l\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the same procedure used in the $\tlhad$ channel.
%using the lepton and fake tau charges, then the scale factors are multiplied together.
The nominal value of scale factors will vary according to their uncertainties in the final fit.
%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
%control regions discussed in Section~\ref{sec:strategy_Htautau}.

In the hadronic channels, the contribution of fakes is estimated partially from data by defining control regions (CR)
enriched in misidentified
$\had$ candidates via loosened $\had$ requirements with proper fake factors and partially from MC~\cite{ATLAS-CONF-2021-044}.
These CRs do not overlap with the main signal regions, discussed in Section~\ref{sec:strategy_Htautau}.
The CR selection requirements are analogous to those used to define signal regions, except
that the subleading $\had$ candidate is required to fail the medium $\had$ identification (Loose).
The contribution of fakes with subleading $\had$ candidate can be calculated by rescaling the templates of Loose taus in the CR
with proper fake factors (FF).
The templates are produced by subtracting all MC background contributions with real sub-leading taus from data.
The FFs are computed as
the ratio of the Data-MC ($\mathrm{real~tau}$) yields passing to failing the medium tau ID in the $W$+jets control region. We have compared
FF obtained from the $W$+jets and the same-sign $\thadhad$ control regions and the differences are treated as a systematic uncertainty.

\subsection{Background with fake light leptons}
The background originating from non-prompt or misidentified light leptons is primarily from the QCD multi-jet production.
%Electrons and muons only appear in the leptonic channels where exactly one electron or muon and at least one $\had$ are required.
%Since the rate of $\had$ candidate is much larger than for electron or muon, in the majority of the fake lepton events, the $\had$ candidate is misidentified and
%the electron or muon is prompt based on MC studies.
%However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, especially to $t_l\had$ where the fake-lepton dominates.
%and the jet multiplicity is low.
The contribution from these events is estimated with a data-driven method called ABCD.
The estimate is based on the number of tight and loose light-leptons that passed and failed the PLIV cut in the low and high $\met$ regions. The number of
fake light leptons in the signal region is evaluated by scaling the number of loose leptons in the high $\met$ region by the ratio of tight and loose leptons in the
low $\met$ region. The contributions of prompt leptons and calibrated $\had$ fakes in the number of tight and loose leptons are subtracted using MC simulation.
A closure test is made for the background estimations in the signal depleted low BDT regions. The data are in good agreement with the background prediction in the
$t_l\had$ channels where the fake light leptons are important while negligible in other leptonic channels.

### 2022-02-18 sections/detector.tex
update the draft to V03 with comments

@@
 The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules optimised for electromagnetic and hadronic measurements, respectively.
-The calorimeters are surrounded by a muon spectrometer within a magnetic field provided by air-core toroid magnets with a bending integral of about \SI{2.5}{\tesla\metre} in the barrel and up to \SI{6.0}{\tesla\metre}in the endcaps.
+The calorimeters are surrounded by a muon spectrometer within a magnetic field provided by air-core toroid magnets with a bending integral of about \SI{2.5}{\tesla\metre} in the barrel and up to \SI{6.0}{\tesla\metre} in the endcaps.
 The muon spectrometer measures the trajectories of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking chambers, and is instrumented with separate trigger chambers covering $|\eta|<2.4$.
 A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based level-1 trigger followed by a software-based high-level trigger, is used to reduce the event rate to a maximum of around \SI{1}{\kHz} for offline storage.
-
 An extensive software suite~\cite{ATL-SOFT-PUB-2021-001} is used in the reconstruction and analysis of real and simulated data, in detector operations, and in the trigger and data acquisition systems of the experiment.

### 2022-02-18 sections/introduction.tex

--- 2022-02-18 sections/introduction.tex
@@
 %of $\BR(H\to b\bar{b})\simeq 58\%$.
-Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
+Compared to Run~1, the Run~2 searches (Table~\ref{tab:limits_summary_ref}) benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
 Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of
@@
 $pp \to tH$ production~\cite{Greljo:2014dka}.
+
+\begin{table}[t!]
+\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$.}}
+\begin{center}
+\tiny
+\begin{tabular}{ccccc}
+\toprule\toprule
+& &\multirow{2}{*}{$\mathcal{L}$ [fb$^{-1}$]} & \multicolumn{1}{c}{95\% CL observed upper limits} & \multicolumn{1}{c}{95\% CL observed upper limits}  \\
+& & 										    & \multicolumn{1}{c}{on $\BR(t \to Hc)$}            & \multicolumn{1}{c}{on $\BR(t \to Hu)$} \\
+\midrule
+\multirow{5}{*}{ATLAS}
+& $H \to b\bar{b}$~\cite{fcnc36}                                          & 36.1         & $4.2 \times 10^{-3}$ & $5.2 \times 10^{-3}$ \\
+& $H \to \gamma\gamma$~\cite{Aaboud:2017mfd}                              & 36.1         & $2.2 \times 10^{-3}$  & $2.4 \times 10^{-3}$  \\
+& $H \to \tau\tau$ ($\lephad$, $\hadhad$)~\cite{fcnc36}                   & 36.1         & $1.9 \times 10^{-3}$  & $1.7 \times 10^{-3}$  \\ 
+& $H \to WW^*, \tau\tau, ZZ^*$ ($2\ell$SS, $3\ell$)~\cite{Aaboud:2018pob} & 36.1         & $1.6 \times 10^{-3}$  & $1.9 \times 10^{-3}$\\ 
+& Combination~\cite{fcnc36}                                               & 36.1         & $1.1 \times 10^{-3}$  & $1.2 \times 10^{-3}$  \\\midrule
+\multirow{3}{*}{CMS} 
+& $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
+& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
+& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
+%
+
+\midrule
+\bottomrule\bottomrule
+\end{tabular}
+\label{tab:limits_summary_ref}
+\end{center}
+\end{table}
+
+% \begin{center}
+% \begin{tabular}{lccc}
+% \hline \hline
+% Analysis                           & Dataset & $\mathcal{L}$ [fb$^{-1}$] & Ref. \\
+% \hline
+% \Hyy\ (including \ttH, \Hyy)       & \multirow{4}{*}{2015--2017} & $79.8$ & (\cite{HIGG-2016-21}), \cite{HIGG-2018-13} \\
+% \hfourl\ (including \ttH, \hfourl) &                             & $79.8$ & (\cite{HIGG-2016-22}), \cite{HIGG-2018-13} \\
+% \VH, \hbb                          &                             & $79.8$ & \cite{HIGG-2018-04,HIGG-2018-50} \\
+% \hmm                               &                             & $79.8$ & (\cite{HIGG-2016-10}) \\
+% \hline
+% \hwwenmun                          & \multirow{6}{*}{2015--2016} & $36.1$ & \cite{HIGG-2016-07} \\
+% \htt                               &                             & $36.1$ & \cite{HIGG-2017-07} \\
+% \VBF, \hbb                         &                             & $24.5$ -- $30.6$ & \cite{HIGG-2016-30} \\
+% \ttH, \hbb\ and \ttH\ multilepton  &                             & $36.1$ & \cite{HIGG-2017-03,HIGG-2017-02,HIGG-2018-13}\\
+% \Hinv                              &                             & $36.1$ & \cite{EXOT-2016-37,HIGG-2016-28,EXOT-2016-23,HIGG-2018-54}\\
+% Off-shell \Hllll\ and \Hllvv\      &                             & $36.1$ & \cite{HIGG-2017-06} \\
+% \hline \hline
+% \end{tabular}
+% \end{center}
+% \label{tab:lumi}
+% \end{table}
 

### 2022-02-18 sections/objects.tex

@@
 A track-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$ and $E_R = \sum E^{\textrm{clst}}$, where
-the scalar sum includes all tracks and energy deposit (excluding the lepton candidate itself) within the cone defined by $\Delta R<0.2 (0.3)$ around the %axis
-direction of the electron (muon). The electron (muon) candidates are required satisfy both $I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$.
+the scalar sum includes all tracks and energy deposits (excluding the lepton candidate itself) within the cone defined by $\Delta R<0.2 (0.3)$ around the %axis
+direction of the electron (muon). The electron (muon) candidates are required to satisfy both $I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$.
 
@@
 These additional reconstructed charged particle tracks inside the jet can be
-used to increase the precision of identifying the displaced decay vertex of heavy flavor (b, c) hadrons that produced non-prompt leptons.
+used to increase the precision for identifying the displaced decay vertex of heavy flavor (b, c) hadrons that produced non-prompt leptons.
 The tight working points are used for high $\pt$ lepton.
 The scale factors for the efficiencies of the tight \texttt{PLIV} working points are measured using the tag and probe method
-with $Z\rightarrow l^+l^-$ ($l=e$ or $\mu$) events. These scale factors are also checked for the electron or muon from the tau decay
+with $Z\rightarrow l^+l^-$ ($l=e$ or $\mu$) events. These scale factors have also been checked for the electron or muon from the tau decay
 using $Z\rightarrow\tau\tau\rightarrow e\mu4\nu$ samples, which is consistent at 2\% level. To be conservative, an
@@
 Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
-Events with $\had$ candidate that is $b$-tagged are rejected.
+Events with a $b$-tagged $\had$ candidate are rejected.
 %(TBD: check RNN description and update then numbers)
@@
 %Overlaps between reconstructed objects are removed sequentially.
-Firstly, electron candidates that lie 
+%Firstly,
+Electron candidates that lie 
 within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
-Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
-and muon candidates are removed. Energy clusters from identified electrons are not excluded during jet reconstruction. 
+%Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
+%and muon candidates are removed.
+Energy clusters from identified electrons are not excluded during jet reconstruction. 
 In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 

### 2022-02-18 sections/simulated_samples.tex

--- 2022-02-09 sections/signal_background_modeling.tex
@@
 %-------------------------------------------------------------------------------
-\section{Signal and background modelling}
-\label{sec:signal_background_model}
 %-------------------------------------------------------------------------------
-
-Signal and most background processes are modelled using Monte Carlo (MC) simulation.
-After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
-Small contributions arise from single-top-quark, $W/Z$+jets, multijet and diboson ($WW,WZ,ZZ$) production, as well as from the associated 
-production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
-with prompt leptons, i.e.\ those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
-are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
-In the simulation, the top-quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
-and the Higgs boson is forced to decay into $H\to \tau\tau$ with branching ratio calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
-Backgrounds with non-prompt electrons or muons, with photons or jets misidentified as electrons, or with jets misidentified as $\had$ candidates, 
-generically referred to as fake leptons, are estimated using data-driven methods. 
-The background prediction is further improved during the statistical analysis by performing a likelihood 
-fit to data using several signal-depleted analysis regions, as discussed in Sections~\ref{sec:strategy_Htautau}.
-
-%-------------------------------------------------------------------------------
-\subsection{Simulated signal and background processes}
+\section{Simulated samples}
 \label{sec:simulations}
@@
 
-Samples of simulated $\ttbar \to WbHq$ events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
-the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element calculation 
+Samples of simulated $\ttbar \to WbHq$ ($tt(qH)$) events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
+the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element (ME) calculation 
 is performed.} {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
 %{\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
-with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering, hadronisation, and the underlying event.
+with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering (PS), hadronisation, and the underlying event.
 The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
@@
 
+Samples of $WH$ and $ZH$, collectively referred to as $VH$ are generated using {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
+and interfaced to {\pythia}~8.210 with the NNPDF2.3 LO PDF set and the A14 tune.
+The contribution of $tH$ associated production is also considered as part of SM Higgs background.
+The sample is generated using {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca} and interfaced with {\pythia}~8.210 with CT10PDF
+and A14 tune. The MC predictions are normalised using the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.
+
 All generated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
@@
         &  ME   &  PS    &  ME  & PS &   &  \\\hline
-\textit{TT} Signal & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-\textit{ST} Signal & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+$tt(qH)$ Signal & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+$tH$ Signal & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
 $W/Z$+jets & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline
@@
 Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one $\had$.
-Since the fake rate of $\had$ candidate is much larger than electron or muon, in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies.
+Since the fake rate of $\had$ candidate is much larger than for electron or muon, in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is prompt based on MC studies.
 However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, especially to $t_l\had$ where the fake-lepton dominates.
 %and the jet multiplicity is low.
-This kind of event is modelled by data-driven ABCD method by cutting on $\met$ and the tight lepton isolation using PLIV, which is widely used in ATLAS physics analyses.
+The contribution from these events is estimated with a data-driven method called ABCD.
+The estimate is based on the number of tight and loose leptons that passed and failed the PLIV cut in the low and high $\met$ regions. The number of
+fake leptons in the signal region is evaluated by rescaling the number of loose leptons in the high $\met$ region with the ratio of tight and loose leptons in the
+low $\met$ region. The contribution of prompt leptons in the number of loose leptons is subtracted using MC simulation.
+
+%This kind of event is modelled by data-driven ABCD method
+%by cutting on $\met$ and the tight lepton isolation using PLIV, which is widely used in ATLAS physics analyses.
 
@@
 %The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated control regions discussed in Section~\ref{sec:st%rategy_Htautau}.
-
-\subsubsection{Fake $\tau$-lepton candidates}
-\label{sec:faketaus}
-The background with one or more fake $\had$ candidates mainly arises from $\ttbar$ or
-multijet production, depending on the search channels.
-Studies based on the simulation show that, for all the above processes, fake $\had$ candidates primarily result from the
-misidentification of light-quark jets, with the contribution from $b$-quarks and gluon jets playing a subdominant role.
-It is also found that the fake rate decreases for all jet flavours as the $\had$ candidate $\pt$ increases.
-
-In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrating monte carlo with scale factors
-derived from the dedicated $t\bar t$
-control regions ($CR_{tt}$) using the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
-aimed at fake taus from different origins. There are four kinds of fake taus that need to be calibrated: Type1) the fake taus from $W$-jets ($\tau_{W}$)
-with the opposite charge to the lepton;
-Type2) $\tau_{W}$'s with the same charge as the lepton; Type 3) the fake taus from $b$-jets; Type4) the fake taus from other origins (mainly radiations).
-These control regions are similar to the signal regions but with an addition $b$-jet or lepton defined as following:
-$t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
-The di-lepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The regions of
-$t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS are used to calibrate Type1 fake taus.
-Similarly for the Type2, the regions of $t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS are used.
-A simultaneous fit to data is made to derive the scale factors for the fake taus in MC, which consist of total 24 parameters
-including four types, 3 $\pt$ bins (25-35, 35-45, 45- GeV), 2 bins for 1 and 3 prong taus separately.
-The values of these scale factors range from 0.3 to 1.28 and are applied to the corresponding signal regions with single b-tagged jet.
-
-In the $t_l\thadhad$ channel, both taus can be fake, so the calibration is applied to each tau separately, following the same procedure as $\tlhad$ channels using the
-lepton and fake tau charges, then the scale factors are multiplied together. The nominal value of the scale factors will vary along with other uncertainties from
-combined performance (CP) recommendations and theory uncertainties in the final fit.
-%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
-%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
-%control regions discussed in Section~\ref{sec:strategy_Htautau}.
-
-In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$
-candidates via loosened $\had$ requirements with proper fake factors and partially from monte carlo~\cite{ATLAS-CONF-2021-044}.
-These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
-The CR selection requirements are analogous to those used to define the different SRs, except
-that the trailing $\had$ candidate is required to fail the medium $\had$ identification.
-The events with fake trailing $\had$ candidate can be calculated by rescaling the templates of fake taus in the Fake-CR with proper fake factors (FF).
-The templates are acquired by subtracting all MC background contributions with real sub-leading taus from data. The FFs are computed as
-the ratio of the Data-MC($\mathrm{real~tau}$) yields passing the medium tau ID to which failing the medium tau ID from different control regions and
-the differences are treated as part of systematics.

### 2022-02-18 sections/strategy_Htautau.tex

--- 2022-02-18 sections/strategy_Htautau.tex
@@
 Underflow and overflow bins are included respectively in the first and last bins.
-Rare including single top, and V+jets and only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution.
-The lower panels show the ratios of the data ('Data') to the background prediction ('Bkg.')}
+Rare including single top, and $V$+jets and only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution.
+The lower panels show the ratios of the data to the background prediction.}
 \label{fig:taupt_prefit}

### 2022-02-18 sections/conclusion.tex
minor update

@@
 A search for flavour-changing neutral current processes involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented.
-FCNC $tqH$ interaction is searched for both in $t\bar{t}$ decay mode, where one top quark decays following SM processes and the other one decays through $t\rightarrow Hq$, and in production mode($pp\rightarrow tH$) with a single top quark produced via FCNC interaction where $t\to Wb$.
+FCNC $tqH$ interaction is searched for both in $t\bar{t}$ decay mode, where one top quark decays following SM processes and the other one decays through $t\rightarrow Hq$, and in production mode ($pp\rightarrow tH$) with a single top quark produced via FCNC interaction where $t\to Wb$.
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
@@
 the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.
-These results improve significantly upon previous ATLAS and CMS limits on the $t\rightarrow Hq$ branching ratios..
+These results improve significantly upon previous ATLAS and CMS limits on the $t\rightarrow Hq$ branching ratios.

### 2022-02-18 sections/introduction.tex
minor update

@@
 %of $\BR(H\to b\bar{b})\simeq 58\%$.
-Compared to Run~1, the Run~2 searches (Table~\ref{tab:limits_summary_ref}) benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
+Compared to Run~1, the Run~2 searches, summarised in Table~\ref{tab:limits_summary_ref}, benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
 Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of
@@
 Compared with previous searches, the search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
-$pp \to tH$ production~\cite{Greljo:2014dka}.
+$pp \to tH$ production~\cite{Greljo:2014dka}. CMS recently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
+their full Run-2 data and  set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $7.9\times10^{-4}(1.1\times10^{-3})$ and $\mathcal{B}(t\to Hc)$ of $9.4\times10^{-4}(8.6\times10^{-4})$~\cite{CMS:2021gfa}.
+CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.
 
@@
 %This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
-The analysis targets Higgs boson decays to 
+This analysis targets Higgs boson decays to 
 %This paper is focused on the decay mode of the Higgs boson into

### 2022-02-18 sections/statistical_analysis.tex
minor update

@@
 
-The final discriminant distributions across all analysis regions considered are jointly analysed to test for the 
+The final BDT discriminant distributions across all analysis regions considered are jointly analysed to test for the 
 presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
@@
 
-The fitting procedure was initially validated through extensive studies using mock data, defined as the sum of all predicted backgrounds 
+The fitting procedure was initially validated through extensive studies using pseudo data, defined as the sum of all predicted backgrounds 
 plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 

### 2022-02-18 sections/strategy_Htautau.tex
minor update

--- 2022-02-18 sections/strategy_Htautau.tex
@@
 \begin{table*}[t!]
-  \caption{\small{Discriminating variables used in the training of the BDT for hadronic channel.
-      The values in percent (\%) represent the separation and importance of each variable.
+  \caption{\small{The number of discriminating variables (n) used in the training of BDT in each SR. Variables are ranked from highest (1) to lowest (n) relative to one another by their
+      importance in the training. Variables which do not have a ranking are not included in the training. 
+      %The values represent their ra importance rankings of each variable and cross($\times$) denotes the variable is not used in the training.
       The descriptions of each variable are provided in the following text.}}
-\label{tab:importance_xTFW}
-\input{tables/xTFW_Merged}
+\label{tab:importance}
+ \centering
+ \begin{tabular}{cccccccc} \toprule\toprule
+   & $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_l\thadhad$     & $t_h\thadhad$-2j & $t_h\thadhad$-3j       \\\midrule
+   Total variables~(n)                           & $12$ & $15$ & $12$ & $17$ & $15$ & $12$ & $12$ \\\midrule 
+ $m_{\text{W}}$                                      &   &             &           & $9$      &       & $6$      & $7$\\
+ $\chi^{2}$                                          &   &             &           & $14$     &       &  &       \\
+ \text{max}($\eta_{\tau}$)                           & $4$       &             &  $4$              &  & $10$          &  &        \\
+ $m^{\text{T}}_{\text{W}}$                           & $11$      &             &  $8$              &  & $13$          &  &         \\
+ $m_{\tau,\tau}$                                     &   &  $2$                &           & $3$      &       & $1$      & $1$          \\
+ $m_{\text{t},\text{SM}}$                            &   &  $1$                &           & $2$      &       & $3$      & $4$          \\
+ $p_{\text{T},\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     &       &  &         \\
+ $m_{\text{t},\text{FCNC}}$                          &   &             &           &  &       & $10$     & $6$\\
+ $m_{\text{t},\text{SM},\text{vis}}$                 & $3$       &             &  $5$              &  & $4$           &  &         \\
+ $p_{\text{T},\tau}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
+ $\met$                                              & $5$       &  $11$               &  $10$             & $13$     & $6$           & $7$    & $13$          \\
+ $m_{\tau\tau,\text{vis}}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
+ $E_{\text{vis}~\tau,1}/E_{\tau,1}$                  &   &  $10$               &           & $12$     &       & $8$    & $8$          \\
+ $E_{\text{vis}~\tau,2}/E_{\tau,2}$                  &   &  $7$                &           & $4$      &       & $9$    & $11$         \\
+ $P_{\text{T,\tauhadvis}} $                          &   &             &           &  & $9$           &  &         \\
+ $m_{\text{t},\text{FCNC},\text{vis}}$               &   &             &           &  & $3$           &  &        \\
+ $\Delta\phi(\tau\tau,\met)$                         &   &  $6$                            &           & $16$     &       & $13$   & $12$         \\
+ $\met\text{centrality}$                             &   &  $13$               &           & $15$     &       & $12$   & $9$         \\
+ \text{Min}($m_{\tau\tau \text{q-jet}}$)             & $9$       &             &  $3$              &  & $14$          &  &         \\
+ $\Delta R(\ell,\tau)$                               & $8$       &  $9$                &  $9$              & $10$     & $15$          &  &         \\
+ $\Delta R(\tau,\tau)$                               &   &             &           &  & $2$           & $4$    & $3$             \\
+ $\Delta R(\ell,\text{b-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          &  &         \\
+ $\Delta R(\tau,\text{b-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          &  &        \\
+ $\Delta R(\ell+\text{b-jet},\tau\tau )$             &   &             &           &  & $7$           &  &         \\
+ $\Delta R(\tau,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
+ \text{Min}($m_{\text{light-jet},\text{light-jet}}$) &   &  $12$               &           & $11$     &       &  &         \\
+% $m_{\text{W}}$                                      & $\times$  &  $\times$           &  $\times$         & $9$      & $\times$      & $6$      & $7$\\
+% $\chi^{2}$                                          & $\times$  &  $\times$           &  $\times$         & $14$     & $\times$      & $\times$ & $\times$      \\
+% \text{max}($\eta_{\tau}$)                           & $4$       &  $\times$           &  $4$              & $\times$ & $10$          & $\times$ & $\times$       \\
+% $m^{\text{T}}_{\text{W}}$                           & $10$      &  $\times$           &  $8$              & $\times$ & $13$          & $\times$ & $\times$        \\
+% $m_{\tau,\tau}$                                     & $\times$  &  $2$                &  $\times$         & $3$      & $\times$      & $1$      & $1$          \\
+% $m_{\text{t},\text{SM}}$                            & $\times$  &  $1$                &  $\times$         & $2$      & $\times$      & $3$      & $4$          \\
+% $p_{\text{T},\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     & $\times$      & $\times$ & $\times$        \\
+% $m_{\text{t},\text{FCNC}}$                          &  $\times$ &  $\times$           &  $\times$         & $\times$ & $\times$      & $10$     & $6$\\
+% $m_{\text{t},\text{SM},\text{vis}}$                 & $3$       &  $\times$           &  $5$              & $\times$ & $4$           & $\times$ & $\times$        \\
+% $p_{\text{T},\tau}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
+% $\met$                                              & $5$       &  $11$               &  $10$             & $13$     & $6$           & $7$    & $13$          \\
+% $m_{\tau\tau,\text{vis}}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
+% $E_{\text{vis}~\tau,1}/E_{\tau,1}$                  & $\times$  &  $10$               &  $\times$         & $12$     & $\times$      & $8$    & $8$          \\
+% $E_{\text{vis}~\tau,2}/E_{\tau,2}$                  & $\times$  &  $7$                &  $\times$         & $4$      & $\times$      & $9$    & $11$         \\
+% $P_{\text{T,\tauhadvis}} $                          & $\times$  &  $\times$           &  $\times$         & $\times$ & $9$           & $\times$ & $\times$        \\
+% $m_{\text{t},\text{FCNC},\text{vis}}$               & $\times$  &  $\times$           &  $\times$         & $\times$ & $3$           & $\times$ & $\times$       \\
+% $\Delta\phi(\tau\tau,\met)$                         & $\times$  &  $6$    			   &  $\times$         & $16$     & $\times$      & $13$   & $12$         \\
+% $\met\text{centrality}$                             & $\times$  &  $13$               &  $\times$         & $15$     & $\times$      & $12$   & $9$         \\
+% \text{Min}($m_{\tau\tau \text{q-jet}}$)             & $9$       &  $\times$           &  $3$              & $\times$ & $14$          & $\times$ & $\times$        \\
+% $\Delta R(\ell,\tau)$                               & $8$       &  $9$                &  $9$              & $10$     & $15$          & $\times$ & $\times$        \\
+% $\Delta R(\tau,\tau)$                               & $\times$  &  $\times$           &  $\times$         & $\times$ & $2$           & $4$    & $3$             \\
+% $\Delta R(\ell,\text{b-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          & $\times$ & $\times$        \\
+% $\Delta R(\tau,\text{b-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          & $\times$ & $\times$       \\
+% $\Delta R(\ell+\text{b-jet},\tau\tau )$             & $\times$  &  $\times$           &  $\times$         & $\times$ & $7$           & $\times$ & $\times$        \\
+% $\Delta R(\tau,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
+% \text{Min}($m_{\text{light-jet},\text{light-jet}}$) & $\times$  &  $12$               &  $\times$         & $11$     & $\times$      & $\times$ & $\times$        \\
+ \bottomrule\bottomrule\\
+ \end{tabular}
 \end{table*}
 
-\begin{table*}[t!]
-  \caption{\small{Discriminating variables used in the training of the BDT for leptonic channel.
-      The values in percent (\%) represent the separation and importance of each variable.
-    The descriptions of each variable are provided in the following text.}}
-\label{tab:importance_tthML}
-\input{tables/tthML_Merged}
-\end{table*}
+%%%%%%%%%%%%%%%
+%%%  \begin{table*}[t!]
+%%%    \caption{\small{Discriminating variables used in the training of the BDT for hadronic channel.
+%%%        The values in percent (\%) represent the separation and importance of each variable.
+%%%      The descriptions of each variable are provided in the following text.}}
+%%%  \label{tab:importance_xTFW}
+%%%  \input{tables/xTFW_Merged}
+%%%  \end{table*}
+%%%  
+%%%  \begin{table*}[t!]
+%%%    \caption{\small{Discriminating variables used in the training of the BDT for leptonic channel.
+%%%        The values in percent (\%) represent the separation and importance of each variable.
+%%%      The descriptions of each variable are provided in the following text.}}
+%%%  \label{tab:importance_tthML}
+%%%  \input{tables/tthML_Merged}
+%%%  \end{table*}
 

### 2022-02-18 sections/systematic_uncertainties.tex
minor update

@@
 is split into 43 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}. The total JES uncertainty is
-below 5\% for most jets and below 1\% for central jets with pT between 300 GeV and 2 TeV. The difference between the JER
-in data and MC is represented by one NP. It is applied on the MC by smearing the jet pT within the prescribed uncertainty.
+below 5\% for most jets and below 1\% for central jets with $\pt$ between 300 GeV and 2 TeV. The difference between the JER
+in data and MC is represented by one NP. It is applied on the MC by smearing the jet $\pt$ within the prescribed uncertainty.
 
@@
 The hdamp parameter (which controls the amount of radiation produced by the parton shower in
-POWHEG-BOX v2) is set to 1.5$m_{top}$ in the nominal case. Alternative samples are generated with hdamp=3$m_{top}$. The
+POWHEG-BOX v2) is set to 1.5$m_t$ in the nominal case. Alternative samples are generated with hdamp=3$m_t$. The
 difference between two samples is treated as one of the systematics as ``$t\bar{t}$ hdamp''. 

### 2022-02-19 sections/simulated_samples.tex
minor update

@@
 
-%-------------------------------------------------------------------------------
-\subsection{Backgrounds with fake leptons}
-\label{sec:fakeleptons}
-%-------------------------------------------------------------------------------
-
-\subsubsection{Fake electrons and muons}
-Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one $\had$.
-Since the fake rate of $\had$ candidate is much larger than for electron or muon, in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is prompt based on MC studies.
-However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, especially to $t_l\had$ where the fake-lepton dominates.
-%and the jet multiplicity is low.
-The contribution from these events is estimated with a data-driven method called ABCD.
-The estimate is based on the number of tight and loose leptons that passed and failed the PLIV cut in the low and high $\met$ regions. The number of
-fake leptons in the signal region is evaluated by rescaling the number of loose leptons in the high $\met$ region with the ratio of tight and loose leptons in the
-low $\met$ region. The contribution of prompt leptons in the number of loose leptons is subtracted using MC simulation.
-
 %This kind of event is modelled by data-driven ABCD method

### 2022-02-22 ANA-TOPQ-2019-17-PAPER-metadata.tex
update and changing version back to 0.5 for now

@@
 %\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
-\AtlasTitle{Search for flavour-changing neutral current $tqH$ of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons
-                   in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.1em}}
+\AtlasTitle{Search for flavour-changing neutral current $tqH$ interactions of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.1em}}
 
@@
 % Comment or remove in final version.
-\AtlasVersion{1.0}
+\AtlasVersion{0.5}
 % Abstract - % directly after { is important for correct indentation
@@
 A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, an up-type quark ($q=u, c$), and a
-Standard Model Higgs boson decaying into a $\tau$-lepton pair ($H\rightarrow \tau^+\tau^-$) is presented.
+Standard Model (SM) Higgs boson decaying into a $\tau$-lepton pair ($H\rightarrow \tau^+\tau^-$) is presented.
 %The Higgs boson decays into a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
-Large Hadron Collider and corresponds to an integrated luminosity of 139 fb$^{-1}$.
-Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
+Large Hadron Collider that corresponds to an integrated luminosity of 139 fb$^{-1}$.
+Two processes are considered:  single top quark FCNC production in association with a Higgs boson ($pp\rightarrow tH$), and top quark pair production in
 which one of top quarks decays into $Wb$ and the other decays into $qH$ through the FCNC interactions.
 %top quark with FCNC decay of $t\rightarrow qH$. 
-The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
-as well as multiple jets and event kinematics are used to separate signal from the background through a multivariate discriminant.  
+The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ 
+with an additional lepton (e,$\mu$),
+as well as multiple jets. Event kinematics are used to separate signal from the background through a multivariate discriminant.  
 %Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
 %No significant excess of events above the background expectation is found,
-A slight excess of data is observed above background with a significance of 2.6$\sigma$,
+A slight excess of data is observed above the expected SM background with a significance of 2.6$\sigma$,
 and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
-Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $0.099\%$ ($0.050^{+0.022}_{-0.014}\%$)
-and $0.072\%$ ($0.036^{+0.017}_{-0.010}\%$), respectively. The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
+Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.9 \times 10^{-4}$ ($5.0^{+2.2}_{-1.4}\times 10^{-4}$) and $7.2\times 10^{-4}$ ($3.6^{+1.7}_{-1.0}\times 10^{-4}$), respectively.
+The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
 the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.} 

### 2022-02-22 sections/background_estimation.tex
update and changing version back to 0.5 for now

@@
 control regions ($CR_{tt}$) using dileptonic decays of $t\bar t$ events and semileptonic decays of $t\bar t$ events with two
-$b$-tagged jets, summarized in Table~\ref{tab:srcr}. 	
+$b$-jets, summarized in Table~\ref{tab:srcr}. 	
 %the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
@@
 depending on four types, three $\pt$ bins, two bins for 1- and 3-prong taus separately.
-These scale factors are then used to correct the MC estimated fakes in the corresponding  signal regions with a single $b$-tagged jet.
+These scale factors are then used to correct the MC estimated fakes in the corresponding  signal regions with a single $b$-jet.
 In the $t_l\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the same procedure used in the $\tlhad$ channel.

### 2022-02-22 sections/conclusion.tex
update and changing version back to 0.5 for now

@@
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
-The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$), a b-tagged jet as well as multiple jets.
+The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$), a $b$-jet as well as multiple jets.
 Multivariate techniques based on BDT are used to distinguish the signal from the background on the basis of their different kinematics.

### 2022-02-22 sections/data_presel.tex
update and changing version back to 0.5 for now

@@
 \item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\lephad$ decay.
-Exactly one $\had$ with opposite-side charge to $\tau_l$ is required, including at least three jets with exactly one $b$-tagged jet.
-\item $t_l\hadhad$: Targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-tagged jet.
+Exactly one $\had$ with opposite-side charge to $\tau_l$ is required, including at least three jets with exactly one $b$-jet.
+\item $t_l\hadhad$: Targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-jet.
 \item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identification so that there is only
-  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-tagged jet.
+  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-jet.
 \end{itemize}
@@
 \begin{itemize}
-\item $t_h\hadhad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\hadhad$ decay. Exactly two $\had$ with opposite-sign charge are selected, including at least 3 jet with exactly one $b$-tagged jet.
+\item $t_h\hadhad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\hadhad$ decay. Exactly two $\had$ with opposite-sign charge are selected, including at least 3 jet with exactly one $b$-jet.
 \end{itemize}
@@
 \toprule\toprule
-\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multirow{2}{*}{hadronic channel} \\ 
+\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & hadronic channel \\ 
 & $t_h\lephad$ & $t_l\hadhad$ &  $t_l\had$ & $t_h\hadhad$\\
@@
 Trigger & \multicolumn{3}{c|}{single-lepton trigger} & di-$\tau$ trigger  \\
-Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & no isolated $e$ or $\mu$ \\
+Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & =0 isolated $e$ or $\mu$ \\
 $\had$  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
@@
 Jets  &  3, $\geq$ 4 jets & $\geq$1 jets & 2, $\geq$3 jets & 3, $\geq$4 jets \\
-$b$-tagging & \multicolumn{3}{c|}{=1 $b$-tagged jets} & =1 $b$-tagged jets\\
+$b$-tagging & \multicolumn{3}{c|}{=1 $b$-jet} & =1 $b$-jet\\
 \bottomrule\bottomrule

### 2022-02-22 sections/introduction.tex
update and changing version back to 0.5 for now

--- 2022-02-18 sections/introduction.tex
@@
 %-------------------------------------------------------------------------------
-After the discovery of the Higgs boson in 2012 by the ATLAS~\cite{Aad:2012tfa} and CMS~\cite{Chatrchyan:2012ufa} collaborations at 
+After the discovery of the Higgs boson in 2012 at the Large Hadron Collider (LHC) by the ATLAS~\cite{Aad:2012tfa} and 
+CMS~\cite{Chatrchyan:2012ufa} collaborations, 
 %Since the observation of Higgs boson by the ATLAS and CMS experiments~\cite{Aad:2012tfa,Chatrchyan:2012ufa} at
-the Large Hadron Collider (LHC), a comprehensive programme of measurements % of its properties
-has been conducted with increased precision and proved to be consistent with the Standard Model (SM) predictions. 
+a comprehensive programme of measurements % of its properties
+has been conducted to explore this new particle. Measurements so far proved to be consistent with the Standard Model (SM) predictions. 
+However, the program is ongoing and precision measurements as well as searches for rare new physics processes beyond the Standar Model (BSM)
+are underway. One such possibility is flavour-changing neutral-current (FCNC) interactions between the Higgs boson, 
+the top quark, and an up-quark, $tqH$ ($q=u, c$), which has been actively searched for by the ATLAS and CMS collaborations.  
+%with increased precision and proved to be consistent with the Standard Model (SM) predictions. 
 %for nearly a decade, by which no significant sign of deviation from Standard Model (SM) was observed until today.
-However the LHC still provides an excellent opportunity to search for rare new physics processes beyond the Standard Model (BSM).  
+%However the LHC still provides an excellent opportunity to search for rare new physics processes beyond the Standard Model (BSM).  
 %there are still chances to find new physics by improving the sensitivity of previous searches.
-The flavour-changing neutral-current (FCNC) interactions 
-between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$) has been actively searched for by the ATLAS and CMS collaborations.
+%The flavour-changing neutral-current (FCNC) interactions 
+%between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$) has been actively searched for by the ATLAS and CMS collaborations.
 %is still an active topic.
@@
 In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
-The $t\to qH$ branching fraction in the SM is calculated to be exceedingly small, around $10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}.
+The $t\to qH$ branching fraction in the SM is calculated to be exceedingly small, $\BR(t\to qH)\approx10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}.
 %such decays are suppressed relative to the dominant $t\to Wb$ decay mode, since $tqH$ 
@@
 %the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling~\cite{Agashe:2013hma}.
-Therefore, an observation of this decay would be a clear evidence for new physics.
+Therefore, an observation of an enhanced rate of this decay would be a clear evidence for new physics.
 %The $tqH$ interaction could also potentially open up more
@@
 %which could be interesting for future studies.
-On the other hand, if the $tqH$ interaction exists, the single-top, Higgs associated production process through this interaction becomes non-zero, enhancing the total
+Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through this interaction would enhance 
+%becomes non-zero, enhancing 
+the total
 production cross section of $pp\rightarrow tH$.
-So the study of this process will also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
-The $tH$ associated production in the SM is expected to have a small cross section of $92^{+7}_{-12}$ fb at LHC centre of mass energy~\cite{deFlorian:2016spz}.
+The study of this process will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
+The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at LHC 13 TeV centre of mass energy~\cite{deFlorian:2016spz}.
 
@@
 of top-quark pair ($\ttbar$) events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{fcnc36} using early Run~2 data.
-
-In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $qH$ with a small $\BR(t\to qH)$, yielding $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$.
-Similarly,
+In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $qH$ with a small branching ratio 
+ $\BR(t\to qH)$, denoted as $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
 $WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
@@
 %of $\BR(H\to b\bar{b})\simeq 58\%$.
-Compared to Run~1, the Run~2 searches (Table~\ref{tab:limits_summary_ref}) benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
-Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of
+Compared to Run~1, the Run~2 searches, summarised in Table~\ref{tab:limits_summary_ref}, benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
+Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of branching ratio
 $\BR(t\to cH)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, $\BR(t\to cH)<0.16\%$ based on
@@
 one of $\tau$-leptons decays hadronically~\cite{fcnc36}.  
-These upper limits are derived assuming that $\BR(t\to uH)=0$. Similar upper limits are obtained for $\BR(t\to uH)$ assuming $\BR(t\to cH)=0$.
+These upper limits are derived assuming that the branching ratio $\BR(t\to uH)$ is null. Similar upper limits are obtained for $\BR(t\to uH)$ assuming $\BR(t\to cH)=0$.
 %The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
-Combining all of the ATLAS searches using 36.1~fb$^{-1}$ Run~2 data, the limits at 95\% CL are set for  $\BR(t\to cH)<0.11\%$ and $\BR(t\to uH)<0.12\%$ respectively assuming $\BR(t\to uH)=0$ and $\BR(t\to cH)=0$~\cite{fcnc36}.
+Combining all of the ATLAS searches using 36.1~fb$^{-1}$ Run~2 data, upper limits at 95\% CL on the branching fractions are 
+set at $\BR(t\to cH)<0.11\%$ assuming $\BR(t\to uH)=0$, and $\BR(t\to uH)<0.12\%$ assuming $\BR(t\to cH)=0$~\cite{fcnc36}.
 
@@
 $pp \to tH$ production~\cite{Greljo:2014dka}. 
+%CMS recently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
+%their full Run 2 data and  set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $7.9\times10^{-4}(1.1\times10^{-3})$ and $\mathcal{B}(t\to Hc)$ of $9.4\times10^{-4}(8.6\times10^{-4})$~\cite{CMS:2021gfa}.
+%CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.
 
@@
 & $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
-& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
-& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
+%& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
+%& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
 %
@@
 %This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
-The analysis targets Higgs boson decays to 
+The analysis reported here targets Higgs boson decays to 
 %This paper is focused on the decay mode of the Higgs boson into
@@
 Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted.
-The signals are divided into several final states depending on the production mode and
-the  $W$ boson decay either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
-$t_l$ when the $\tau$ decays into a light lepton (electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
+The dataset is divided into several final states depending on the production mode and
+the  $W$ decay. Top pair production events where the W boson decays hadronically (leptonicall) are referred to as $t_h$ ($t_l$). The contribution of 
+$W\rightarrow\tau\nu$ is included as $\tau_{\text{lep}}$ in $t_l$ when the $\tau$ decays into a light lepton (electron or muon) or as $\thad$ 
+in $t_h$ when the $\tau$ decays hadronically.
+%either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
+%$t_l$ when the $\tau$ decays into a light lepton (electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
 The $H\rightarrow \tau\tau$ decay is detected in
@@
 Events with at least one \tauhad with an additional electron or muon are selected as the leptonic channels.
-More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data and more
-$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
-Finally, a multivariate technique, boosted decision trees, is used to discriminate between the signal and the background on the basis of their different kinematics distributions.
+More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data.
+In addition, an improved treatment of misidentified $\tau$-leptons in simulation and data-driven
+fake estimations from QCD multi-jet background are implemented.
+% and more
+%$$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
+Finally, a multivariate technique based on boosted decision trees, is used to discriminate between the signal and the background on the basis of their different kinematics distributions.
 

### 2022-02-22 sections/signal_background_modeling.tex
update and changing version back to 0.5 for now

@@
 After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
-Small contributions arise from single-top-quark, $W/Z$+jets, multijet and diboson ($WW,WZ,ZZ$) production, as well as from the associated 
+Small contributions arise from single-top-quark, $W/Z$+jets, multi-jet and diboson ($WW,WZ,ZZ$) production, as well as from the associated 
 production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
@@
 The background with one or more fake $\had$ candidates mainly arises from $\ttbar$ or
-multijet production, depending on the search channels.
-Studies based on the simulation show that, for all the above processes, fake $\had$ candidates primarily result from the
+multi-jet production, depending on the search channels.
+Studies based on simulation show that, for all the above processes, fake $\had$ candidates primarily result from the
 misidentification of light-quark jets, with the contribution from $b$-quarks and gluon jets playing a subdominant role.
@@
 
-In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrating monte carlo with scale factors
+In the leptonic channels, the events with prompt electron or muon and fake taus are modelled by calibrating MC with scale factors
 derived from the dedicated $t\bar t$
-control regions ($CR_{tt}$) using the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
-aimed at fake taus from different origins. There are four kinds of fake taus that need to be calibrated: Type1) the fake taus from $W$-jets ($\tau_{W}$)
-with the opposite charge to the lepton;
-Type2) $\tau_{W}$'s with the same charge as the lepton; Type 3) the fake taus from $b$-jets; Type4) the fake taus from other origins (mainly radiations).
-These control regions are similar to the signal regions but with an addition $b$-jet or lepton defined as following:
-$t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
-The di-lepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The regions of
-$t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS are used to calibrate Type1 fake taus.
-Similarly for the Type2, the regions of $t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS are used.
-A simultaneous fit to data is made to derive the scale factors for the fake taus in MC, which consist of total 24 parameters
-including four types, 3 $\pt$ bins (25-35, 35-45, 45- GeV), 2 bins for 1 and 3 prong taus separately.
-The values of these scale factors range from 0.3 to 1.28 and are applied to the corresponding signal regions with single b-tagged jet.
+control regions ($CR_{tt}$) using dileptonic decays of $t\bar t$ events and semileptonic decays of $t\bar t$ events with two
+$b$-jets, summarized in Table~\ref{tab:srcr}. 	
+%the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
+%aimed at fake taus from different origins.
+There are four kinds of fake taus that need to be calibrated: Type1) fake taus from $W$-jets ($\tau_{W}$)
+with the opposite-sign (OS) of charge to the light lepton;
+Type2) $\tau_{W}$'s with the same-sign (SS) charge to the light lepton; Type 3) fake taus originating from $b$-hadron decays; Type4) fake taus from light-flavour hadron decays.
+The control regions are defined similar to the signal regions but with an additional $b$-jet or light lepton.
+%$t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
+The dilepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The semileptonic
+regions ($t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS) where $\thad$ and light lepton have opposite charge are used to calibrate Type1 fake taus.
+Similarly for the Type2, the semileptonic regions ($t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS) where $\thad$ and light lepton have same charge are used.
+A simultaneous fit to data is made to derive the scale factors for fake taus in MC, which consist of total of 24 parameters
+depending on four types, three $\pt$ bins, two bins for 1- and 3-prong taus separately.
+These scale factors are then used to correct the MC estimated fakes in the corresponding  signal regions with single $b$-jet.
 
-In the $t_l\thadhad$ channel, both taus can be fake, so the calibration is applied to each tau separately, following the same procedure as $\tlhad$ channels using the
-lepton and fake tau charges, then the scale factors are multiplied together. The nominal value of the scale factors will vary along with other uncertainties from
-combined performance (CP) recommendations and theory uncertainties in the final fit.
+In the $t_l\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the sameprocedure used in the $\tlhad$ channel.
+%using the lepton and fake tau charges, then the scale factors are multiplied together.
+The nominal value of scale factors will vary according to their uncertainties in the final fit.
 %In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
@@
 
-In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$
-candidates via loosened $\had$ requirements with proper fake factors and partially from monte carlo~\cite{ATLAS-CONF-2021-044}.
-These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
-The CR selection requirements are analogous to those used to define the different SRs, except
-that the trailing $\had$ candidate is required to fail the medium $\had$ identification.
-The events with fake trailing $\had$ candidate can be calculated by rescaling the templates of fake taus in the Fake-CR with proper fake factors (FF).
-The templates are acquired by subtracting all MC background contributions with real sub-leading taus from data. The FFs are computed as
-the ratio of the Data-MC($\mathrm{real~tau}$) yields passing the medium tau ID to which failing the medium tau ID from different control regions and
-the differences are treated as part of systematics.
+In the hadronic channels, the contribution of fakes is estimated partially from data by defining control regions (CR)
+enriched in misidentified
+$\had$ candidates via loosened $\had$ requirements with proper fake factors and partially from MC~\cite{ATLAS-CONF-2021-044}.
+These CRs do not overlap with the main signal regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
+The CR selection requirements are analogous to those used to define SRs, except
+that the subleading $\had$ candidate is required to fail the medium $\had$ identification (Loose).
+The contribution of fakes with subleading $\had$ candidate can be calculated by rescaling the templates of Loose taus in the CR
+with proper fake factors (FF).
+The templates are acquired by subtracting all MC background contributions with real sub-leading taus from data.
+The FFs are computed as
+the ratio of the Data-MC ($\mathrm{real~tau}$) yields passing to failing the medium tau ID in the $W$+jets control region. We have compared
+FF obtained from the $W$+jets and the same-sign $\thadhad$ control regions and the differences are treated as part of systematics.

### 2022-02-22 sections/simulated_samples.tex
update and changing version back to 0.5 for now

@@
 \centering
-\caption{Overview of the MC generators used for the main signal and background samples}
+\caption{Overview of the MC generators at which the matrix-element calculation (ME) at the leading or the next-leading order (Order), 
+the parton shower model (PS), and the parton distribution function set (PDF) used for the main signal and background samples.}
 \begin{tabular}[h]{l|c|c|c|c|c|c}
@@
         &  ME   &  PS    &  ME  & PS &   &  \\\hline
-$tt(qH)$ Signal & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-$tH$ Signal & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-$W/Z$+jets & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline
-\ttbar & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-Single top & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-$t\bar{t}X$ & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-Diboson & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline\hline
+$tt(qH)$ Signal & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+$tH$ Signal & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+$W/Z$+jets & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline
+\ttbar & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+Single top & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+$t\bar{t}X$ & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+Diboson & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline\hline
 \end{tabular}

### 2022-02-22 sections/strategy_Htautau.tex
update and changing version back to 0.5 for now

@@
 \centering
-\caption{Overview of the signal regions and the control regions used for fake tau scale factor derivation in leptonic channels.}
+\caption{Overview of the signal regions (SR) and the $t\bar{t}$ control regions (CRtt) used for fake tau scale factor derivation in leptonic channels.
+Leptons are required to have either same-sign (SS) or opposite-sign (OS) charges in each region.}
 \label{tab:srcr}
@@
 \multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
-\multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
+\multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
 &$t_l\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
@@
 &$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
-\multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
-&$t_lt_l2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
+\multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & $\ge0$                            & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
+&$t_lt_l2b\tauhad$      & 2     & $\ge0$                            & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
 &$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
@@
 \begin{table*}[t!]
-  \caption{\small{The number of discriminating variables (n) used in the training of BDT in each SR. Variables are ranked from highest (1) to lowest (n) relative to one another by their
-      importance in the training. Variables which do not have a ranking are not included in the training. 
+  \caption{\small{The number of discriminating variables (n) used in the training of BDT in each SR. 
+The rank of the discriminating variables relative to one another according to their importance in the training is reported from highest (1) to 
+lowest (n). Variables whose ranking is missing are not included in the training of the corresponding SR. The description of each variable is provided in the text.}}
+%Variables are ranked from highest (1) to lowest (n) relative to one another by their
+%      importance in the training. Variables which do not have a ranking are not included in the training. 
 %The values represent their ra importance rankings of each variable and cross($\times$) denotes the variable is not used in the training.
-      The descriptions of each variable are provided in the following text.}}
+%      The descriptions of each variable are provided in the following text.}}
 \label{tab:importance}
@@
  $m_{\text{t},\text{SM}}$                            &   &  $1$                &           & $2$      &       & $3$      & $4$          \\
- $p_{\text{T},\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     &       &  &         \\
+ ${\pt}_{\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     &       &  &         \\
  $m_{\text{t},\text{FCNC}}$                          &   &             &           &  &       & $10$     & $6$\\
  $m_{\text{t},\text{SM},\text{vis}}$                 & $3$       &             &  $5$              &  & $4$           &  &         \\
- $p_{\text{T},\tau}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
+ ${\pt}_{\tauhadvis}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
  $\met$                                              & $5$       &  $11$               &  $10$             & $13$     & $6$           & $7$    & $13$          \\
  $m_{\tau\tau,\text{vis}}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
- $E_{\text{vis}~\tau,1}/E_{\tau,1}$                  &   &  $10$               &           & $12$     &       & $8$    & $8$          \\
- $E_{\text{vis}~\tau,2}/E_{\tau,2}$                  &   &  $7$                &           & $4$      &       & $9$    & $11$         \\
+ $E_{\text{vis}~\tau1}/E_{\tau1}$                  &   &  $10$               &           & $12$     &       & $8$    & $8$          \\
+ $E_{\text{vis}~\tau2}/E_{\tau2}$                  &   &  $7$                &           & $4$      &       & $9$    & $11$         \\
  $P_{\text{T,\tauhadvis}} $                          &   &             &           &  & $9$           &  &         \\
@@
  \text{Min}($m_{\tau\tau \text{q-jet}}$)             & $9$       &             &  $3$              &  & $14$          &  &         \\
- $\Delta R(\ell,\tau)$                               & $8$       &  $9$                &  $9$              & $10$     & $15$          &  &         \\
+ \text{Min}($\Delta R(\ell,\tau)$)                               & $8$       &  $9$                &  $9$              & $10$     & $15$          &  &         \\
  $\Delta R(\tau,\tau)$                               &   &             &           &  & $2$           & $4$    & $3$             \\
  $\Delta R(\ell,\text{b-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          &  &         \\
- $\Delta R(\tau,\text{b-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          &  &        \\
+ $\Delta R(\tau1,\text{b-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          &  &        \\
  $\Delta R(\ell+\text{b-jet},\tau\tau )$             &   &             &           &  & $7$           &  &         \\
- $\Delta R(\tau,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
+ $\Delta R(\tau1,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
  \text{Min}($m_{\text{light-jet},\text{light-jet}}$) &   &  $12$               &           & $11$     &       &  &         \\
@@
 \item $\met$ is the missing transverse momentum.
-\item $P_{\text{T,\tauhadvis}} $ is the transverse momentum of the leading tau candidate.
-\item $P_{\text{T,sub}-\tau}$ is the transverse momentum of the sub-leading tau candidate.
-\item $P_{\text{T},\ell}$ is the transverse momentum of the leading light lepton.
+\item ${\pt}_{\tauhadvis} $ is the transverse momentum of the leading tau candidate.
+\item ${\pt}_{\text{sub}-\tau}$ is the transverse momentum of the sub-leading tau candidate.
+\item ${\pt}_{\ell}$ is the transverse momentum of the leading light lepton.
 \item $\chi^2$ derived from the kinematic fit of the neutrino momentum.
@@
 \begin{equation}
-m^{T}_{\text{W}} = \sqrt{2 P_{T,\ell} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\ell,\text{miss}} \right)}.  
+m^{T}_{\text{W}} = \sqrt{2 {\pt}_{\ell} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\ell,\text{miss}} \right)},  
 \end{equation}
+where $\Delta\phi_{\ell,\text{miss}}$ is the azimuth angle between the light-lepton and $\met$.  
 \item $m_{\tau,\tau}$ is the fitted invariant mass of the tau candidates and reconstructed neutrinos in the $t_hH$, $t_ht(qH)$ channels. 
@@
 \item $m_{\tau\tau,\text{vis}}$ is the visible invariant mass of the di-tau candidates. %or the lepton and $\had$ candidate when there is only one $\had$.
-\item $P_{\text{T},\tau\tau,\text{vis}}$ is the visible $\pT$ of the di-tau candidates.
+\item ${\pt}_{\tau\tau,\text{vis}}$ is the visible $\pT$ of the di-tau candidates.
 \item $m_{\text{t},\text{FCNC},\text{vis}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
@@
 \end{eqnarray}
-\item $E_{\nu,\text{i}}/E_{\tau,\text{i}},\text{i}=1,2$ is the momentum fraction carried by the visible decay products from the tau mother.
+\item $E_{\text{vis}~\tau\text{i}}/E_{\tau\text{i}},\text{i}=1,2$ is the momentum fraction carried by the visible decay products from the tau mother.
 It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section.
 For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}.
-\item $\Delta R(\ell+\text{b-jet},\tau\tau)$ is the angular distance between the lepton+$b$-jet and di-tau candidates.
-\item $\Delta R(\ell,\text{b-jet})$ is the angular distance between the lepton and $b$-jet.
-\item $\Delta R(\tau,\text{b-jet})$ is the angular distance between the tau candidate and $b$-jet. If there are two taus in the event, the leading one is selected for the calculation.
-\item \text{Max}($\eta_{\tau}$) is the maximum $\eta$ value among the tau candidates.
-\item $\Delta R(\ell,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
-\item $\Delta R(\tau,\text{q-jet})$ is the angular distance between the tau candidate and the reconstructed $q$-jet. If there are two taus in the event, the leading one is used.
-\item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(\ell,\tau)$.
+%\item $\Delta R(\ell+\text{b-jet},\tau\tau)$ is the angular distance between the lepton+$b$-jet and di-tau candidates.
+%\item $\Delta R(\ell,\text{b-jet})$ is the angular distance between the lepton and $b$-jet.
+%\item $\Delta R(\tau,\text{b-jet})$ is the angular distance between the tau candidate and $b$-jet. If there are two taus in the event, the leading one is selected for the calculation.
+%\item \text{Max}($\eta_{\tau}$) is the maximum $\eta$ value among the tau candidates.
+%\item $\Delta R(\ell,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
+%\item $\Delta R(\tau,\text{q-jet})$ is the angular distance between the tau candidate and the reconstructed $q$-jet. If there are two taus in the event, the leading one is used.
+%\item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(\ell,\tau)$.
 \item $\Delta\phi(\tau\tau,\met)$ is the azimuthal angle between the $\met$ and di-tau $\pT$.
-\item $\Delta R(\tau,\text{light-jet})$ is the minimum angle distance between the tau candidate and the light-jet. If there are two taus in the event, the leading one is used.
+\item $\Delta R(i,j)$ is the angular distance between \text{i} and \text{j} objects. 
+%\item $\Delta R(\tau1,\text{light-jet})$ is the minimum angle distance between the tau candidate and the light-jet. If there are two taus in the event, the leading one is used.
 \end{itemize}
@@
 The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
-Underflow and overflow bins are included respectively in the first and last bins.
-Rare including single top, and $V$+jets and only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution.
+Overflow bins are included respectively in the last bin.
+Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic)
+channels. 
+%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
 The lower panels show the ratios of the data to the background prediction.}

### 2022-02-22 sections/systematic_uncertainties.tex
update and changing version back to 0.5 for now

@@
 and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated approximately 30\% by comparing the
-data and total background prediction in the different analysis regions considered, but requiring exactly zero $b$-tagged jets.
+data and total background prediction in the different analysis regions considered, but requiring exactly zero $b$-jet.
 %Agreement between data and predicted background 
@@
 \begin{table}[h!]
-\caption{List of relative uncertainties of the signal strength from the combined fit. The uncertainties are symmetrised for presentation and grouped into the categories described in the text.}
+\caption{List of relative uncertainties on the upper limits of $\BR(t\to qH)$ ($q=u,c$) obtained from the combined fit.
+The uncertainties are symmetrised for presentation and grouped into the categories described in the text.}
 \label{tab:had_sys_impact}
@@
 \toprule
-\multirow{2}{*}{Source of uncertainty}      & \multicolumn{2}{c}{$\Delta\mu/\mu [\%]$} \\
+\multirow{2}{*}{Source of uncertainty}      & \multicolumn{2}{c}{$\Delta\BR/\BR [\%]$} \\
                                             & \multicolumn{1}{c}{$t\rightarrow uH$} & \multicolumn{1}{c}{$t\rightarrow cH$} \\\midrule

### 2022-02-22 sections/data_presel.tex
updates and change back the version to 0.5
update tables

--- 2022-02-16 sections/data_presel.tex
@@
 \toprule\toprule
-\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multirow{2}{*}{hadronic channel} \\ 
+\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multicolumn{1}{c}{hadronic channel} \\ 
 & $t_h\lephad$ & $t_l\hadhad$ &  $t_l\had$ & $t_h\hadhad$\\
@@
 Jets  &  3, $\geq$ 4 jets & $\geq$1 jets & 2, $\geq$3 jets & 3, $\geq$4 jets \\
-$b$-tagging & \multicolumn{3}{c|}{=1 $b$-tagged jets} & =1 $b$-tagged jets\\
+$b$-tagging & \multicolumn{3}{c|}{=1 $b$-jets} & =1 $b$-jets\\
 \bottomrule\bottomrule

### 2022-02-22 sections/introduction.tex
updates and change back the version to 0.5
update tables

--- 2022-02-18 sections/introduction.tex
@@
 \begin{table}[t!]
-\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$.}}
+\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$ obtained from ATLAS and CMS Collaborations with Run 2 data.}}
 \begin{center}
-\tiny
+\small 
 \begin{tabular}{ccccc}
@@
 & $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
-& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
+%& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
 % 
-
-\midrule
 \bottomrule\bottomrule

### 2022-02-22 sections/simulated_samples.tex
updates and change back the version to 0.5
update tables

--- 2022-02-19 sections/simulated_samples.tex
@@
 
+%  \begin{table}
+%  \footnotesize
+%  \centering
+%  \caption{Overview of the MC generators used for the main signal and background samples.}
+%  \begin{tabular}[h]{l|c|c|c|c|c|c}
+%  \hline \hline
+%  \multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
+%          &  ME   &  PS    &   ME  & PS &   &  \\\hline
+%  $tt(qH)$ Signal & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+%  $tH$ Signal & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+%  $W/Z$+jets & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline
+%  \ttbar & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+%  Single top & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+%  $t\bar{t}X$ & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+%  Diboson & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline\hline
+%  \end{tabular}
+%  \label{mob}
+%  \end{table}
+
 \begin{table}
@@
 \centering
-\caption{Overview of the MC generators used for the main signal and background samples}
+\caption{Overview of the MC generators used for the main signal and background samples.}
 \begin{tabular}[h]{l|c|c|c|c|c|c}
@@
         &  ME   &  PS    &   ME  & PS &   &  \\\hline
-$tt(qH)$ Signal & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-$tH$ Signal & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-$W/Z$+jets & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline
-\ttbar & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-Single top & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-$t\bar{t}X$ & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-Diboson & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline\hline
+$tt(qH)$ Signal & \powheg & \pythia~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+$tH$ Signal & \amcatnlolong & \pythia~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+$W/Z$+jets & \multicolumn{2}{c|}{\sherpa~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & \sherpa & NLO/LO \\ \hline
+\ttbar & \powheg & \pythia~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+Single top & \powheg & \pythia~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+$t\bar{t}X$ & \amcatnlolong & \pythia~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+Diboson & \multicolumn{2}{c|}{\sherpa~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & \sherpa & NLO/LO \\ \hline\hline
 \end{tabular}

### 2022-02-22 sections/strategy_Htautau.tex
updates and change back the version to 0.5
update tables

--- 2022-02-18 sections/strategy_Htautau.tex
@@
 
+%   \begin{table}
+%   \centering
+%   \caption{Overview of the signal regions and the control regions used for fake tau scale factor derivation in leptonic channels.}
+%   \label{tab:srcr}
+%   \begin{tabular}[h]{c|c|c|c|c|c|c}
+%   \hline \hline
+%   \multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
+%   \multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
+%   &$t_l\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
+%   &$t_l\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
+%   &$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
+%   &$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
+%   &$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
+%   &$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
+%   \multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
+%   &$t_lt_l2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
+%   &$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
+%   &$t_lt_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ OS\\ \cline{2-7}
+%   &$t_lt_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
+%   &$t_lt_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_l\tauhad$ OS\\ \hline
+%   \end{tabular}
+%   \end{table}
+
 \begin{table}
@@
 &$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
-\multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
-&$t_lt_l2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
+\multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & $\ge0$                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
+&$t_lt_l2b\tauhad$      & 2     & $\ge0$                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
 &$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}

### 2022-02-22 sections/systematic_uncertainties.tex
updates and change back the version to 0.5
update tables

--- 2022-02-18 sections/systematic_uncertainties.tex
@@
 }
-\toprule
+\toprule\toprule
 \multirow{2}{*}{Source of uncertainty}      & \multicolumn{2}{c}{$\Delta\mu/\mu [\%]$} \\
                                             & \multicolumn{1}{c}{$t\rightarrow uH$} & \multicolumn{1}{c}{$t\rightarrow cH$} \\\midrule
-Lepton                                  & 0.6           &1.0         \\
+%Lepton                                  & 0.6           &1.0         \\
+%Met                                     & 0.7           &0.8         \\
+%Luminosity and Pileup                   & 1.0           &1.3         \\
+%Theoretical uncertainty in other MC     & 2.1           &2.9         \\
+%Jets                                    & 2.4           &3.2         \\
+%Flavour tagging                         & 2.7           &3.7         \\
+%Misidentified $\tau$                    & 3.4           &4.8         \\
+%Theoretical uncertainty in $t\bar{t}$   & 2.9           &4.3         \\
+%Hadronic $\tau$ decays                  & 3.3           &4.4         \\
+%Theoretical uncertainty in signal       & 5.3           &7.0         \\\midrule
+%Total statistics uncertainty            & 5.1           &7.0         \\
+%Total systematic uncertainty            & 11.2          &15.4        \\ \midrule
+%Total                                   & 12.3          &16.9        \\
+
+Lepton ID                               & 0.6           &1.0         \\
 Met                                     & 0.7           &0.8         \\
-Luminosity and Pileup                   & 1.0           &1.3         \\
-Theoretical uncertainty in other MC     & 2.1           &2.9         \\
-Jets                                    & 2.4           &3.2         \\
+Fake lepton  modeling                   & 0.9           &1.1         \\
+Luminosity and Pileup                   & 0.9           &1.3         \\
+Other MC modeling                       & 2.1           &2.9         \\
+JES and JER                             & 2.4           &3.2         \\
 Flavour tagging                         & 2.7           &3.7         \\
-Misidentified $\tau$                    & 3.4           &4.8         \\
-Theoretical uncertainty in $t\bar{t}$   & 2.9           &4.3         \\
-Hadronic $\tau$ decays                  & 3.3           &4.4         \\
-Theoretical uncertainty in signal       & 5.3           &7.0         \\\midrule
-Total statistics uncertainty            & 5.1           &7.0         \\
-Total systematic uncertainty            & 11.2          &15.4        \\ \midrule
-Total                                   & 12.3          &16.9        \\
-\bottomrule
+$t\bar{t}$ modeling                     & 2.9           &4.3         \\
+Fake $\tau$ modeling                    & 3.2           &4.6         \\
+$\tau$ ID                               & 3.3           &4.4         \\
+Signal modeling including Br($H\to\tau\tau$)       & 5.3           &7.0         \\\midrule
+Total systematic uncertainty            & 11.2          &15.5        \\ 
+Total statistics uncertainty            & 5.1           &7.0         \\\midrule
+Total                                   & 12.3          &17.0        \\
+
+%tuH:
+%Fake LEP method    0.00919939  ( +0.00919939, -0.00919939 )
+%Fake method    0.0323159  ( +0.0323159, -0.0323159 )
+%FullSyst    0.112111  ( +0.112111, -0.112111 )
+%Gammas    0.0509968  ( +0.0509968, -0.0509968 )
+%Instrument    0.0093934  ( +0.0093934, -0.0093934 )
+%JET    0.0235705  ( +0.0235705, -0.0235705 )
+%Lepton    0.00568277  ( +0.00568277, -0.00568277 )
+%MET    0.00704844  ( +0.00704844, -0.00704844 )
+%SignalTheory    0.0526104  ( +0.0526104, -0.0526104 )
+%TAU    0.032714  ( +0.032714, -0.032714 )
+%Theory    0.0210686  ( +0.0210686, -0.0210686 )
+%btag    0.027376  ( +0.027376, -0.027376 )
+%ttbarTheory    0.0289194  ( +0.0289194, -0.0289194 )
+
+%tcH:
+%Fake LEP method    0.010914  ( +0.010914, -0.010914 )
+%Fake method    0.0455017  ( +0.0455017, -0.0455017 )
+%FullSyst    0.154686  ( +0.154686, -0.154686 )
+%Gammas    0.0700708  ( +0.0700708, -0.0700708 )
+%Instrument    0.0131647  ( +0.0131647, -0.0131647 )
+%JET    0.0320897  ( +0.0320897, -0.0320897 )
+%Lepton    0.0104552  ( +0.0104552, -0.0104552 )
+%MET    0.00841447  ( +0.00841447, -0.00841447 )
+%SignalTheory    0.0699833  ( +0.0699833, -0.0699833 )
+%TAU    0.0437292  ( +0.0437292, -0.0437292 )
+%Theory    0.029182  ( +0.029182, -0.029182 )
+%btag    0.0367613  ( +0.0367613, -0.0367613 )
+%ttbarTheory    0.0427391  ( +0.0427391, -0.0427391 )
+
+\bottomrule\bottomrule
 \end{tabular} 

### 2022-02-22 sections/data_presel.tex

@@
 \multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multicolumn{1}{c}{hadronic channel} \\ 
+%\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & hadronic channel \\ 
 & $t_h\lephad$ & $t_l\hadhad$ &  $t_l\had$ & $t_h\hadhad$\\

### 2022-02-22 sections/systematic_uncertainties.tex

@@
 %and using the Var3c upward variation of the A14 parameter set;
-%a sample with decreased radiation (referred to as radLow) is obtained by increasing the scales by a factor of two 
-%and using the Var3c downward variation of the A14 set~\cite{ATL-PHYS-PUB-2016-004}.
+%a sample with decreased radiation (referred to as radLow) is obtained by increasing the scales by a factor of two  %and using the Var3c downward variation of the A14 set~\cite{ATL-PHYS-PUB-2016-004}.
 
@@
 \toprule\toprule
-\multirow{2}{*}{Source of uncertainty}      & \multicolumn{2}{c}{$\Delta\mu/\mu [\%]$} \\
+\multirow{2}{*}{Source of uncertainty}      & \multicolumn{2}{c}{$\Delta\BR/\BR [\%]$} \\
                                             & \multicolumn{1}{c}{$t\rightarrow uH$} & \multicolumn{1}{c}{$t\rightarrow cH$} \\\midrule

### 2022-02-23 sections/strategy_Htautau.tex
update pt plots

--- 2022-02-22 sections/strategy_Htautau.tex
@@
 $t_l\hadhad$, $t_l\had$-1j, $t_l\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}.
+
+%   \begin{table}
+%   \centering
+%   \caption{Overview of the signal regions and the control regions used for fake tau scale factor derivation in leptonic channels.}
+%   \label{tab:srcr}
+%   \begin{tabular}[h]{c|c|c|c|c|c|c}
+%   \hline \hline
+%   \multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
+%   \multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
+%   &$t_l\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
+%   &$t_l\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
+%   &$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
+%   &$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
+%   &$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
+%   &$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
+%   \multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
+%   &$t_lt_l2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
+%   &$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
+%   &$t_lt_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ OS\\ \cline{2-7}
+%   &$t_lt_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
+%   &$t_lt_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_l\tauhad$ OS\\ \hline
+%   \end{tabular}
+%   \end{table}
 
@@
 %This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
-%of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
-%is missing or not (events with exactly three jets or at least four jets).
+%of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay %is missing or not (events with exactly three jets or at least four jets).
 This event categorisation is primarily motivated by optimizing the sensitivity in each signal region that targets either leptonic or hadronic top-quark
@@
 %\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
-\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l2tau1bnj_os.pdf} &
-\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b1j_ss.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b2j_ss.pdf}\\
+\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
+\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
+\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
 (a1) \pT(\tauhad) in $t_l\thadhad$ & (a2) \pT(\tauhad) in  $t_l\tauhad$-1j& (a3) \pT(\tauhad) in $t_l\tauhad$-2j\\
-\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b2j_os.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b3j_os.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
+\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
+\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}&
+\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
 (b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
-\includegraphics[page=1,width=0.33\textwidth]{figures/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
+\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
 (c1) \pT(\tauhad) in $t_h\thadhad$-3j\\

### 2022-02-23 ANA-TOPQ-2019-17-PAPER-metadata.tex
updates for more comments

@@
 %\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
-\AtlasTitle{Search for flavour-changing neutral current $tqH$ interactions of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.1em}}
+\AtlasTitle{Search for flavour-changing neutral current interactions of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.1em}}
 
@@
 \AtlasAbstract{%
+\vspace{0.1em}
 A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, an up-type quark ($q=u, c$), and a
@@
 The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
-the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.} 
+the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$ for the new physics scale $\Lambda$ at 1~TeV, respectively.} 
 %$|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
-%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.
-%}
-
+%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.%}
 % Author - this does not work with revtex (add it after \begin{document})

### 2022-02-23 sections/background_estimation.tex
updates and change back the version to 0.5
updates for more comments

@@
 derived from the dedicated $t\bar t$
-control regions ($CR_{tt}$) using dileptonic decays of $t\bar t$ events and semileptonic decays of $t\bar t$ events with two
+control regions (CRtt) using dileptonic decays of $t\bar t$ events and semileptonic decays of $t\bar t$ events with two
 $b$-jets, summarized in Table~\ref{tab:srcr}. 	
@@
 The FFs are computed as
-the ratio of the Data-MC ($\mathrm{real~tau}$) yields passing to failing the medium tau ID in the $W$+jets control region. We have compared
-FF obtained from the $W$+jets and the same-sign $\thadhad$ control regions and the differences are treated as a systematic uncertainty.
+the ratio of the Data-MC ($\mathrm{real~tau}$) yields in which the $\had$ candidate is passed or failed the medium tau ID selection
+in the $W$+jets control region.
+%passing to failing the medium tau ID in the $W$+jets control region.
+%We have compared
+FFs obtained from the $W$+jets and from the same-sign $\thadhad$ control regions are compared and the differences are treated as a systematic uncertainty.
 
@@
 %However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, especially to $t_l\had$ where the fake-lepton dominates.
-%and the jet multiplicity is low.
+and the jet multiplicity is low.
 The contribution from these events is estimated with a data-driven method called ABCD.

### 2022-02-23 sections/conclusion.tex
updates for more comments

@@
 A search for flavour-changing neutral current processes involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented.
-FCNC $tqH$ interaction is searched for both in $t\bar{t}$ decay mode, where one top quark decays following SM processes and the other one decays through $t\rightarrow Hq$, and in production mode ($pp\rightarrow tH$) with a single top quark produced via FCNC interaction where $t\to Wb$.
+FCNC $tqH$ interaction is searched for both in $t\bar{t}$ decay mode, where one top quark decays according to the SM processes and the other one decays through $t\rightarrow Hq$, and in production mode ($pp\rightarrow tH$) with a single top quark produced via FCNC interaction where $t\to Wb$.
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
@@
 %The search sensitivities have been improved significantly compared to the previous analysis using 36$^{-1}$ of run-2 data~\cite{Aaboud2019SearchFT}.
-%No significant excess of events above the background expectation is found.
+No significant excess of events above the background expectation is found.
 A slight excess of data is observed above background with a significance of 2.6$\sigma$.  
-We set 95\% CL upper limits on the $t\to Hq$ branching ratios and the corresponding
+95\% CL upper limits are set on the $t\to Hq$ branching ratios and the corresponding
 dimension-6 operator Wilson coefficients in the effective $tqH$ couplings. 
@@
 The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
-the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.
+the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$ for the new physics scale $\Lambda$ at 1~TeV, respectively.
 These results improve significantly upon previous ATLAS and CMS limits on the $t\rightarrow Hq$ branching ratios.

### 2022-02-23 sections/introduction.tex
updates for more comments

--- 2022-02-22 sections/introduction.tex
@@
 %The flavour-changing neutral-current (FCNC) interactions 
-%between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$) has been actively searched for by the ATLAS and CMS collaborations.
-%is still an active topic.
+%between the Higgs boson, the top quark, and a $u$- or $c$-quark, $tqH$ ($q=u,c$) has been actively searched for by the ATLAS and CMS collaborations. %is still an active topic.
 Since the Higgs boson is lighter than the top quark~\cite{Aad:2015zhl},
@@
 & Combination~\cite{fcnc36}                                               & 36.1         & $1.1 \times 10^{-3}$  & $1.2 \times 10^{-3}$  \\\midrule
-\multirow{3}{*}{CMS} 
+\multirow{1}{*}{CMS} 
 & $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
@@
 % 
-
-\midrule
 \bottomrule\bottomrule
@@
 Events with at least one \tauhad with an additional electron or muon are selected as the leptonic channels.
-More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data.
+More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data~\cite{fcnc36}.
 In addition, an improved treatment of misidentified $\tau$-leptons in simulation and data-driven

### 2022-02-23 sections/strategy_Htautau.tex
updates for more comments

@@
 $\sqrt{\sum E_T}$, where $\sum E_T$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
-After the $\chi^2$ minimisation, the Higgs boson four-momentum, and hence its invariant mass, as well as the 
-four-momentum of the parent top quarks, are determined with better resolution in the signal events.
+After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
+$\pt$ of the parent top quarks are determined with better resolution in the signal events.
 
@@
 
-Boosted decision trees (BDT)~\cite{Hocker:2007ht} are used in each SR to improve the separation between signal and background. 
+Boosted decision trees (BDT) implemented in the TMVA framework~\cite{Hocker:2007ht} are used in each SR to improve the separation between signal and background. 
 %The separate training exploits differences in event kinematics across SRs.  
@@
 %corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.
-The first and the last bins in the figures contain the underflow and overflow respectively.
+The last bin of each plot contains the overflow entries.
 The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model} below.
@@
 %\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l2tau1bnj_os.pdf} &
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b1j_ss.pdf}&
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b2j_ss.pdf}\\
 (a1) \pT(\tauhad) in $t_l\thadhad$ & (a2) \pT(\tauhad) in  $t_l\tauhad$-1j& (a3) \pT(\tauhad) in $t_l\tauhad$-2j\\
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b2j_os.pdf}&
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b3j_os.pdf}&
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
 (b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
+\includegraphics[page=1,width=0.33\textwidth]{figures/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
 (c1) \pT(\tauhad) in $t_h\thadhad$-3j\\

### 2022-02-23 sections/systematic_uncertainties.tex
updates for more comments

@@
 Several normalisation and shape uncertainties are taken into account for the $\Hq$ and $pp\to tH$ signals.
-Uncertainties of the Higgs boson branching ratios are taken into account
-following the recommendation in Ref.~\cite{deFlorian:2016spz}.
+Uncertainties of the Higgs boson branching ratios are taken from the measured values in Ref.~\cite{Zyla:2020zbs}.
+%into account following the recommendation in Ref.~\cite{deFlorian:2016spz}.
 The uncertainty of ISR, FSR, scale and PDF are considered in all SRs. The parton shower uncertainties are estimated by comparing
@@
 
-\begin{table}[h!]
-\caption{List of relative uncertainties on the upper limits of $\BR(t\to qH)$ ($q=u,c$) obtained from the combined fit.
+%\begin{table}[h!]
+%\caption{List of relative uncertainties on the upper limits of $\BR(t\to qH)$ ($q=u,c$) obtained from the combined fit.
 The uncertainties are symmetrised for presentation and grouped into the categories described in the text.}
-\label{tab:had_sys_impact}
-\begin{center}
-\begin{tabular}{%
-@{}l%
-S%
-S%
-@{}%
-}
-\toprule\toprule
-\multirow{2}{*}{Source of uncertainty}      & \multicolumn{2}{c}{$\Delta\BR/\BR [\%]$} \\
-                                            & \multicolumn{1}{c}{$t\rightarrow uH$} & \multicolumn{1}{c}{$t\rightarrow cH$} \\\midrule
+%\label{tab:had_sys_impact}
+%\begin{center}
+%\begin{tabular}{%
+%@{}l%
+%S%
+%S%
+%@{}%
+%}
+%\toprule\toprule
+%\multirow{2}{*}{Source of uncertainty}      & \multicolumn{2}{c}{$\Delta\BR/\BR [\%]$} \\
+%                                            & \multicolumn{1}{c}{$t\rightarrow uH$} & \multicolumn{1}{c}{$t\rightarrow cH$} \\\midrule
 %Lepton                                  & 0.6           &1.0         \\
@@
 
-Lepton ID                               & 0.6           &1.0         \\
-Met                                     & 0.7           &0.8         \\
-Fake lepton  modeling                   & 0.9           &1.1         \\
-Luminosity and Pileup                   & 0.9           &1.3         \\
-Other MC modeling                       & 2.1           &2.9         \\
-JES and JER                             & 2.4           &3.2         \\
-Flavour tagging                         & 2.7           &3.7         \\
-$t\bar{t}$ modeling                     & 2.9           &4.3         \\
-Fake $\tau$ modeling                    & 3.2           &4.6         \\
-$\tau$ ID                               & 3.3           &4.4         \\
-Signal modeling including Br($H\to\tau\tau$)       & 5.3           &7.0         \\\midrule
-Total systematic uncertainty            & 11.2          &15.5        \\ 
-Total statistics uncertainty            & 5.1           &7.0         \\\midrule
-Total                                   & 12.3          &17.0        \\
+%Lepton ID                               & 0.6           &1.0         \\
+%$\met$                                  & 0.7           &0.8         \\
+%Fake lepton  modeling                   & 0.9           &1.1         \\
+%Luminosity and Pileup                   & 0.9           &1.3         \\
+%Other MC modeling                       & 2.1           &2.9         \\
+%JES and JER                             & 2.4           &3.2         \\
+%Flavour tagging                         & 2.7           &3.7         \\
+%$t\bar{t}$ modeling                     & 2.9           &4.3         \\
+%Fake $\tau$ modeling                    & 3.2           &4.6         \\
+%$\tau$ ID                               & 3.3           &4.4         \\
+%Signal modeling including Br($H\to\tau\tau$)       & 5.3           &7.0         \\\midrule
+%Total systematic uncertainty            & 11.2          &15.5        \\ 
+%Total statistics uncertainty            & 5.1           &7.0         \\\midrule
+%Total                                   & 12.3          &17.0        \\
 
@@
 
-\bottomrule\bottomrule
-\end{tabular} 
-\end{center}
-\end{table}
+%\bottomrule\bottomrule
+%\end{tabular} 
+%\end{center}
+%\end{table}
 

### 2022-02-23 sections/introduction.tex
minor update table 1 and 5

@@
 \toprule\toprule
-& &\multirow{2}{*}{$\mathcal{L}$ [fb$^{-1}$]} & \multicolumn{1}{c}{95\% CL observed upper limits} & \multicolumn{1}{c}{95\% CL observed upper limits}  \\
+& &\multirow{2}{*}{$\mathcal{L}$ [fb$^{-1}$]} & \multicolumn{2}{c}{95\% CL observed upper limits}  \\
 & & 										    & \multicolumn{1}{c}{on $\BR(t \to Hc)$}            & \multicolumn{1}{c}{on $\BR(t \to Hu)$} \\

### 2022-02-23 sections/background_estimation.tex
add new limit plots

@@
 
-Most background processes are modelled using Monte Carlo (MC) simulation.
+Most background processes are modelled using MC simulation.
 After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
@@
 The CR selection requirements are analogous to those used to define signal regions, except
-that the subleading $\had$ candidate is required to fail the medium $\had$ identification (Loose).
-The contribution of fakes with subleading $\had$ candidate can be calculated by rescaling the templates of Loose taus in the CR
-with proper fake factors (FF).
+that the subleading $\had$ candidate is required to fail the medium $\had$ identification, but it still passes a loose requirement.
+The contribution of fakes with subleading $\had$ candidate can be calculated by rescaling the templates of loose taus in the CR
+with fake factors (FF).
 The templates are produced by subtracting all MC background contributions with real sub-leading taus from data.
@@
 \subsection{Background with fake light leptons}
-The background originating from non-prompt or misidentified light leptons is primarily from the QCD multi-jet production.
+The background originating from non-prompt or misidentified light leptons is primarily from the multi-jet production.
 %Electrons and muons only appear in the leptonic channels where exactly one electron or muon and at least one $\had$ are required.
@@
 A closure test is made for the background estimations in the signal depleted low BDT regions. The data are in good agreement with the background prediction in the
-$t_l\had$ channels where the fake light leptons are important while negligible in other leptonic channels.
+$t_l\had$ channels where the fake light leptons are important, while they are negligible in other leptonic channels.

### 2022-02-23 sections/introduction.tex
add new limit plots

@@
 $\tau$-leptons with the complete Run~2 dataset collected in 2015-2018.
-The corresponding integrated luminosity is 139.0 fb$^{-1}$.
+The corresponding integrated luminosity is 139 fb$^{-1}$.
 Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted.
@@
 either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
-Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected as the hadronic channels.
-Events with at least one \tauhad with an additional electron or muon are selected as the leptonic channels.
+Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are named hadronic channels.
+Events with at least one \tauhad with an additional electron or muon are named leptonic channels.
 More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data~\cite{fcnc36}.
 In addition, an improved treatment of misidentified $\tau$-leptons in simulation and data-driven
-fake estimations from QCD multi-jet background are implemented.
+fake estimations from multi-jet background are implemented.
 % and more

### 2022-02-23 sections/objects.tex
update and changing version back to 0.5 for now
updates and change back the version to 0.5
add new limit plots

@@
 
-Events are selected from $pp$ collisions at $\sqrt(s)$=13 TeV recorded by the ATLAS detector during 2015-2018.
+Events are selected from $pp$ collisions at $\sqrt{s}$=13 TeV recorded by the ATLAS detector during 2015-2018.
 Only events for which all relevant subsystems were operational are considered.
@@
 the scalar sum includes all tracks and energy deposits (excluding the lepton candidate itself) within the cone defined by $\Delta R<0.2 (0.3)$ around the %axis
-direction of the electron (muon). The electron (muon) candidates are required to satisfy both $I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$.
+direction of the electron (muon). The electron (muon) candidates are required to satisfy both $I_R/\pt^l < 0.2~(0.3)$ and $E_R/\pt^l < 0.2~(0.3)$.
+%$I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$.
 
@@
 %(TBD: check RNN description and update then numbers)
-
 %Overlaps between candidate objects are removed sequentially, following this order: muons, electrons,

### 2022-02-23 sections/strategy_Htautau.tex
add new limit plots

@@
 If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
-with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and not reconstructed.
+with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
 This kind of events will fall into $t_hH$.
@@
 In the $t_hH$ events, there are three jets coming from top hadronic decay including the $b$-jet and two opposite-sign $\had$ from the Higgs boson decay, where
-both $t_h$ and H can be reconstructed.  
+both $t_h$ and $H$ can be reconstructed.  
 %. So a Higgs resonance formed by the taus and a top resonance formed by
@@
 
-The four-momenta of the invisible decay products from the decay of the tau-leptons 
+The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
 are estimated using a kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
 measured $\met$ within their expected resolutions.
-The resolution on the Higgs boson mass is assumed to be $20~\gev$, respectively, while the resolution on the measured $\met$ is parameterised as a linear function of
-$\sqrt{\sum E_T}$, where $\sum E_T$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
+The resolution on the Higgs boson mass is assumed to be $20~\gev$, while the resolution on the measured $\met$ is parameterised as a linear function of
+$\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
 After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
@@
 %has a large momentum and the flying direction is unknown.
-the kinematics fit is no longer feasible due to extra neutrino from $W\rightarrow \ell\nu$ decay. The kinematic variables are calculated using the visible
+the kinematic fit is no longer feasible due to extra neutrino from $W\rightarrow \ell\nu$ decay. The kinematic variables are calculated using the visible
 objects only. After the event reconstruction, a number of variables are used to discriminate the signal from the background using a multivariate analysis described
@@
  \begin{tabular}{cccccccc} \toprule\toprule
-   & $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_l\thadhad$     & $t_h\thadhad$-2j & $t_h\thadhad$-3j       \\\midrule
+   & $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_l2\tauhad$     & $t_h2\tauhad$-2j & $t_h2\tauhad$-3j       \\\midrule
    Total variables~(n)                           & $12$ & $15$ & $12$ & $17$ & $15$ & $12$ & $12$ \\\midrule 
@@
  $\met\text{centrality}$                             &   &  $13$               &           & $15$     &       & $12$   & $9$         \\
- \text{Min}($m_{\tau\tau \text{q-jet}}$)             & $9$       &             &  $3$              &  & $14$          &  &         \\
- \text{Min}($\Delta R(\ell,\tau)$)                               & $8$       &  $9$                &  $9$              & $10$     & $15$          &  &         \\
+ \text{min}($m_{\tau\tau j/g}$)             & $9$       &             &  $3$              &  & $14$          &  &         \\
+ \text{min}($\Delta R(\ell,\tau)$)                               & $8$       &  $9$                &  $9$              & $10$     & $15$          &  &         \\
  $\Delta R(\tau,\tau)$                               &   &             &           &  & $2$           & $4$    & $3$             \\
- $\Delta R(\ell,\text{b-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          &  &         \\
- $\Delta R(\tau1,\text{b-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          &  &        \\
- $\Delta R(\ell+\text{b-jet},\tau\tau )$             &   &             &           &  & $7$           &  &         \\
+ $\Delta R(\ell,\text{$b$-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          &  &         \\
+ $\Delta R(\tau1,\text{$b$-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          &  &        \\
+ $\Delta R(\ell+\text{$b$-jet},\tau\tau )$             &   &             &           &  & $7$           &  &         \\
  $\Delta R(\tau1,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
- \text{Min}($m_{\text{light-jet},\text{light-jet}}$) &   &  $12$               &           & $11$     &       &  &         \\
+ \text{min}($m_{jj}$) &   &  $12$               &           & $11$     &       &  &         \\
 % $m_{\text{W}}$                                      & $\times$  &  $\times$           &  $\times$         & $9$      & $\times$      & $6$      & $7$\\
@@
 A large set of potential variables are investigated in each SR separately.
-The discrimination of a given variable is quantified by the "separation"(measures the degree of overlap between background and signal shape) and "importance"(depicts the power of the variable to the classification of two distributions) provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 2\% were kept.
+The discrimination of a given variable is quantified by the "separation"(measures the degree of overlap between background and signal shape) and "importance"(depicts the power of the variable to the classification of the events) provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is larger than 2\% were kept.
 The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance}. The discriminating variables used are:
@@
 \item $m_{\text{t},\text{SM},\text{vis}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top quark mass.
-\item \text{Min}($M_{\tau\tau \text{q-jet}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\text{t},\text{FCNC},\text{vis}}$.
-\item \text{Min}($M_{\text{light-jet},\text{light-jet}}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.
+\item \text{min}($m_{\tau\tau j/q}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\text{t},\text{FCNC},\text{vis}}$.
+\item \text{min}($m_{jj}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.
   %an alternative of $m_{\text{W}}$.
@@
 %\item $\Delta R(\tau,\text{b-jet})$ is the angular distance between the tau candidate and $b$-jet. If there are two taus in the event, the leading one is selected for the calculation.
-%\item \text{Max}($\eta_{\tau}$) is the maximum $\eta$ value among the tau candidates.
+%\item \text{max}($\eta_{\tau}$) is the maximum $\eta$ value among the tau candidates.
 %\item $\Delta R(\ell,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
@@
 The last bin of each plot contains the overflow entries.
-The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model} below.
+The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model}.
 The hashed area represents the total uncertainty of the background.
 A good description of the data by the background model is observed in all cases.
-The final observable used to extract signal events is defined as the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.
+The final observable used to extract the signal contribution is the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.
+
 %Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.

### 2022-02-23 sections/systematic_uncertainties.tex
add new limit plots

@@
 Uncertainties affecting the normalisation of the $V$+jets background are estimated separately for $V$+light-jets, $V$+$\geq$1$c$+jets,
-and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated approximately 30\% by comparing the
+and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated to be approximately 30\% by comparing the
 data and total background prediction in the different analysis regions considered, but requiring exactly zero $b$-jet.

### 2022-02-23 sections/introduction.tex
updates with EB comments

@@
 The dataset is divided into several final states depending on the production mode and
-the  $W$ decay. Top pair production events where the W boson decays hadronically (leptonicall) are referred to as $t_h$ ($t_l$). The contribution of 
-$W\rightarrow\tau\nu$ is included as $\tau_{\text{lep}}$ in $t_l$ when the $\tau$ decays into a light lepton (electron or muon) or as $\thad$ 
+the  $W$ decay. Top pair production events where the W boson decays hadronically (leptonicall) are referred to as $t_h$ ($t_{\ell}$). The contribution of 
+$W\rightarrow\tau\nu$ is included as $\lep$ in $t_{\ell}$ when the $\tau$ decays into a light lepton (electron or muon) or as $\thad$ 
 in $t_h$ when the $\tau$ decays hadronically.
@@
 The $H\rightarrow \tau\tau$ decay is detected in
-either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
+either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_{\ell}$). 
 Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are named hadronic channels.

### 2022-02-23 sections/strategy_Htautau.tex
updates with EB comments

@@
 $\had$ candidates, and on the number of light flavored jets:
-$t_l\hadhad$, $t_l\had$-1j, $t_l\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}.
+$t_{\ell}\hadhad$, $t_{\ell}\had$-1j, $t_{\ell}\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}.
 
@@
 %   \multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
-%   \multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
-%   &$t_l\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
-%   &$t_l\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
+%   \multirow{7}{*}{SR}&$t_{\ell}\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
+%   &$t_{\ell}\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
+%   &$t_{\ell}\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
 %   &$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
@@
 %   &$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
-%   \multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
-%   &$t_lt_l2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
-%   &$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
-%   &$t_lt_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ OS\\ \cline{2-7}
-%   &$t_lt_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
-%   &$t_lt_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_l\tauhad$ OS\\ \hline
+%   \multirow{6}{*}{CRtt}&$t_{\ell}t_{\ell}1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
+%   &$t_{\ell}t_{\ell}2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
+%   &$t_{\ell}t_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
+%   &$t_{\ell}t_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \cline{2-7}
+%   &$t_{\ell}t_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
+%   &$t_{\ell}t_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \hline
 %   \end{tabular}
@@
 \multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
-\multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
-&$t_l\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
-&$t_l\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
+\multirow{7}{*}{SR}&$t_{\ell}\thadhad$     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
+&$t_{\ell}\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
+&$t_{\ell}\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
 &$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
@@
 &$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
-\multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & $\ge0$                            & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
-&$t_lt_l2b\tauhad$      & 2     & $\ge0$                            & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
-&$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
-&$t_lt_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ OS\\ \cline{2-7}
-&$t_lt_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
-&$t_lt_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_l\tauhad$ OS\\ \hline
+\multirow{6}{*}{CRtt}&$t_{\ell}t_{\ell}1b\tauhad$ & 1     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
+&$t_{\ell}t_{\ell}2b\tauhad$      & 2     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
+&$t_{\ell}t_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
+&$t_{\ell}t_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \cline{2-7}
+&$t_{\ell}t_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
+&$t_{\ell}t_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \hline
 \end{tabular}
@@
 with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
-This kind of events will fall into $t_hH$.
+This kind of events will fall into $t_hH$ final state.
 %while the FCNC top resonance is
@@
 %given the big chance that the jet which is missing is from $W$ decay.
-In the $t_hH$ events, there are three jets coming from top hadronic decay including the $b$-jet and two opposite-sign $\had$ from the Higgs boson decay, where
+There are three jets coming from top hadronic decay including the $b$-jet and a pair of opposite-sign taus from the Higgs boson decay, where
 both $t_h$ and $H$ can be reconstructed.  
@@
 
-For the  $t_lt(qH)$ and $t_lH$ events where the $W$ boson from $t\to W b$ decay decays leptonically,
+For the  $t_{\ell}t(qH)$ and $t_{\ell}H$ events where $W$ boson from $t\to W b$ decay decays leptonically,
 %has a large momentum and the flying direction is unknown.
@@
 
-%In the  $t_lt(qH)$ and $t_lH$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown.
-The kinematics fit is no longer feasible in the $t_l\hadhad$ channel.
+%In the  $t_{\ell}t(qH)$ and $t_{\ell}H$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown.
+The kinematics fit is no longer feasible in the $t_{\ell}\hadhad$ channel.
 The variables calculated from the visible objects are directly used in the multivariate analysis.
-However, the kinematics fit is still performed for the $t_l\had$ channels where the lepton and $\had$ are treated as di-tau candidate.
+However, the kinematics fit is still performed for the $t_{\ell}\had$ channels where the lepton and $\had$ are treated as di-tau candidate.
 
@@
  \begin{tabular}{cccccccc} \toprule\toprule
-   & $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_l2\tauhad$     & $t_h2\tauhad$-2j & $t_h2\tauhad$-3j       \\\midrule
+   & $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_{\ell}2\tauhad$     & $t_h2\tauhad$-2j & $t_h2\tauhad$-3j       \\\midrule
    Total variables~(n)                           & $12$ & $15$ & $12$ & $17$ & $15$ & $12$ & $12$ \\\midrule 
- $m_{\text{W}}$                                      &   &             &           & $9$      &       & $6$      & $7$\\
+ $m_{\text{jj}}$                                      &   &             &           & $9$      &       & $6$      & $7$\\
  $\chi^{2}$                                          &   &             &           & $14$     &       &  &       \\
  \text{max}($\eta_{\tau}$)                           & $4$       &             &  $4$              &  & $10$          &  &        \\
- $m^{\text{T}}_{\text{W}}$                           & $11$      &             &  $8$              &  & $13$          &  &         \\
- $m_{\tau,\tau}$                                     &   &  $2$                &           & $3$      &       & $1$      & $1$          \\
- $m_{\text{t},\text{SM}}$                            &   &  $1$                &           & $2$      &       & $3$      & $4$          \\
+ $m^{W}_{\text{T}}$                           & $11$      &             &  $8$              &  & $13$          &  &         \\
+ $m_{\tau\tau,\text{fit}}$                                     &   &  $2$                &           & $3$      &       & $1$      & $1$          \\
+ $m_{\text{bjj},\text{fit}}$                            &   &  $1$                &           & $2$      &       & $3$      & $4$          \\
  ${\pt}_{\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     &       &  &         \\
- $m_{\text{t},\text{FCNC}}$                          &   &             &           &  &       & $10$     & $6$\\
- $m_{\text{t},\text{SM},\text{vis}}$                 & $3$       &             &  $5$              &  & $4$           &  &         \\
- ${\pt}_{\tauhadvis}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
+ $m_{\tau\tau\text{q},\text{fit}}$                          &   &             &           &  &       & $10$     & $6$\\
+ $m_{\text{bjj}}$                 & $3$       &             &  $5$              &  & $4$           &  &         \\
+ ${\pt}_{\tau1}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
  $\met$                                              & $5$       &  $11$               &  $10$             & $13$     & $6$           & $7$    & $13$          \\
- $m_{\tau\tau,\text{vis}}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
- $E_{\text{vis}~\tau1}/E_{\tau1}$                  &   &  $10$               &           & $12$     &       & $8$    & $8$          \\
- $E_{\text{vis}~\tau2}/E_{\tau2}$                  &   &  $7$                &           & $4$      &       & $9$    & $11$         \\
- $P_{\text{T,\tauhadvis}} $                          &   &             &           &  & $9$           &  &         \\
- $m_{\text{t},\text{FCNC},\text{vis}}$               &   &             &           &  & $3$           &  &        \\
+ $m_{\tau\tau}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
+ $E_{\tau1}/E_{\tau1,\text{fit}}$                  &   &  $10$               &           & $12$     &       & $8$    & $8$          \\
+ $E_{\tau2}/E_{\tau2,\text{fit}}$                  &   &  $7$                &           & $4$      &       & $9$    & $11$         \\
+ ${\pt}_{\tautau} $                          &   &             &           &  & $9$           &  &         \\
+ $m_{\tau\tau\text{q}}$               &   &             &           &  & $3$           &  &        \\
  $\Delta\phi(\tau\tau,\met)$                         &   &  $6$                            &           & $16$     &       & $13$   & $12$         \\
  $\met\text{centrality}$                             &   &  $13$               &           & $15$     &       & $12$   & $9$         \\
- \text{min}($m_{\tau\tau j/g}$)             & $9$       &             &  $3$              &  & $14$          &  &         \\
+ \text{min}($m_{\tau\tau \text{j}}$)             & $9$       &             &  $3$              &  & $14$          &  &         \\
  \text{min}($\Delta R(\ell,\tau)$)                               & $8$       &  $9$                &  $9$              & $10$     & $15$          &  &         \\
@@
 In the training, all signal events from $tt(qH)$ and $tH$ are merged together for $tuH$ and $tcH$. All background sources from SM processes
-(including both real and fake $\had$ contributions) are also used in the training.
+(including both real and fake tau contributions) are also used in the training.
 
@@
 \item $\met$ is the missing transverse momentum.
-\item ${\pt}_{\tauhadvis} $ is the transverse momentum of the leading tau candidate.
-\item ${\pt}_{\text{sub}-\tau}$ is the transverse momentum of the sub-leading tau candidate.
+\item ${\pt}_{\tau1} $ is the transverse momentum of the leading tau candidate.
+\item ${\pt}_{\tau2}$ is the transverse momentum of the sub-leading tau candidate.
 \item ${\pt}_{\ell}$ is the transverse momentum of the leading light lepton.
 \item $\chi^2$ derived from the kinematic fit of the neutrino momentum.
-\item $m_{t,\text{SM}}$ is the invariant mass of the $b$-jet and the two jets from the $W$ decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
+\item $m_{\text{bjj},\text{fit}}$ is the fitted invariant mass of the $b$-jet and the two jets from the $W$ decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
 This variable is only defined for the 4-jet $t_hH$ and $t_ht(qH)$ events.
-\item $m^{T}_{\text{W}}$ is the transverse mass calculated from the lepton and $\met$ in the leptonic channels, defined as
+\item $m^{W}_{\text{T}}$ is the transverse mass calculated from the lepton and $\met$ in the leptonic channels, defined as
 \begin{equation}
-m^{T}_{\text{W}} = \sqrt{2 {\pt}_{\ell} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\ell,\text{miss}} \right)},  
+m^{W}_{\text{T}} = \sqrt{2 {\pt}_{\ell} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\ell,\text{miss}} \right)},  
 \end{equation}
 where $\Delta\phi_{\ell,\text{miss}}$ is the azimuth angle between the light-lepton and $\met$.  
-\item $m_{\tau,\tau}$ is the fitted invariant mass of the tau candidates and reconstructed neutrinos in the $t_hH$, $t_ht(qH)$ channels. 
-\item $m_{\text{W}}$ is the reconstructed invariant mass of two light-jets from the $W$ decay with the mass closet to the $W$ mass.
-\item $m_{\text{t},\text{FCNC}}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
-\item $m_{\tau\tau,\text{vis}}$ is the visible invariant mass of the di-tau candidates. %or the lepton and $\had$ candidate when there is only one $\had$.
-\item ${\pt}_{\tau\tau,\text{vis}}$ is the visible $\pT$ of the di-tau candidates.
-\item $m_{\text{t},\text{FCNC},\text{vis}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
-\item $m_{\text{t},\text{SM},\text{vis}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top quark mass.
-\item \text{min}($m_{\tau\tau j/q}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\text{t},\text{FCNC},\text{vis}}$.
-\item \text{min}($m_{jj}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.
+\item $m_{\tau\tau,\text{fit}}$ is the fitted invariant mass of the tau candidates and reconstructed neutrinos for the $t_hH$ and $t_ht(qH)$ events. 
+\item $m_{\text{jj}}$ is the reconstructed invariant mass of two light-jets from the $W$ decay with the mass closet to the $W$ mass.
+\item $m_{\tau\tau\text{q},\text{fit}}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
+\item $m_{\tau\tau}$ is the visible invariant mass of the di-tau system. %or the lepton and $\had$ candidate when there is only one $\had$.
+\item ${\pt}_{\tau\tau}$ is the visible $\pT$ of the di-tau system.
+\item $m_{\tau\tau,\text{q}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
+\item $m_{\text{bjj}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top quark mass.
+\item \text{min}($m_{\tau\tau \text{j}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\tautau\text{q}}$.
+\item \text{min}($m_{\text{jj}}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.
   %an alternative of $m_{\text{W}}$.
@@
 \end{eqnarray}
-\item $E_{\text{vis}~\tau\text{i}}/E_{\tau\text{i}},\text{i}=1,2$ is the momentum fraction carried by the visible decay products from the tau mother.
+\item $E_{\tau\text{i}}/E_{\tau\text{i},\text{fit}}$, \text{i}=1,2 are the momentum fraction carried by the visible decay products from the leading and subleading tau decays.
 It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section.
@@
 %\item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(\ell,\tau)$.
-\item $\Delta\phi(\tau\tau,\met)$ is the azimuthal angle between the $\met$ and di-tau $\pT$.
+\item $\Delta\phi(\tau\tau,\met)$ is the azimuthal angle between the $\met$ and di-tau system $\pT$.
 \item $\Delta R(i,j)$ is the angular distance between \text{i} and \text{j} objects. 
@@
 \end{itemize}
-A comparison between data and the predicted background for the leading $\had$ $\pt$ distribution in the SRs 
-%some of these variables in three main decay final states($t_l\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
+
+A comparison between data and the predicted background for the leading tau $\pt$ distribution in the SRs 
+%some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
 is shown in Figure~\ref{fig:taupt_prefit}.
-%each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_lhadhad}.
+%each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_{\ell}hadhad}.
 %The comparison between the data and predicted background after preselection for the distributions of two of the most 
@@
 \includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
-(a1) \pT(\tauhad) in $t_l\thadhad$ & (a2) \pT(\tauhad) in  $t_l\tauhad$-1j& (a3) \pT(\tauhad) in $t_l\tauhad$-2j\\
+(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
 \includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
@@
 \end{tabular}
-\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit').
+\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit').
 The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
@@
 % \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}\\
-% (a1) BDT discriminant in $t_l\thadhad$ & (a2) BDT discriminant in  $t_l\tauhad$-1j& (a3) BDT discriminant in $t_l\tauhad$-2j\\
+% (a1) BDT discriminant in $t_{\ell}\thadhad$ & (a2) BDT discriminant in  $t_{\ell}\tauhad$-1j& (a3) BDT discriminant in $t_{\ell}\tauhad$-2j\\
 % \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf} &
@@
 % \end{tabular}
-% \caption{ The BDT output distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),$t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1).
+% \caption{ The BDT output distributions are compared between the expected background and $tqH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3),$t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1).
 Only statistical uncertainties are being shown (?).

### 2022-02-24 sections/background_estimation.tex

@@
 and the Higgs boson is forced to decay into $H\to \tau\tau$ with branching ratio calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
-Backgrounds with non-prompt light leptons (electron or muon), with photons or jets misidentified as electrons, or with jets misidentified as $\had$ candidates, 
+Backgrounds with non-prompt light leptons (electron or muon), with photons or jets misidentified as electrons, or with jets misidentified as tau candidates, 
 generically referred to as \texttt{fake} leptons, are estimated using data-driven methods. 
 The background prediction is further improved during the statistical analysis by performing a likelihood 
-fit to data using several signal-depleted analysis regions, as discussed in Sections~\ref{sec:strategy_Htautau}.
+fit to data using several signal-depleted control regions as discussed in Section~\ref{sec:strategy_Htautau}.
 
@@
 %-------------------------------------------------------------------------------
-\subsection{Backgrounds with fake $\had$ leptons}
+\subsection{Backgrounds with fake tau leptons}
 \label{sec:faketaus}
-The background with one or more fake $\had$ candidates mainly arises from $\ttbar$ or
+The background with one or more fake tau candidates mainly arises from $\ttbar$ or
 multi-jet production, depending on the search channels.
-Studies based on simulation show that, for all the above processes, fake $\had$ candidates primarily result from the
+Studies based on simulation show that, for all the above processes, fake tau candidates primarily result from the
 misidentification of light jets and $b$-quark jets.
-It is also found that the fake rate decreases for all jet flavours as the $\had$ candidate $\pt$ increases.
+It is also found that the fake rate decreases for all jet flavours as the tau candidate $\pt$ increases.
 
@@
 The control regions are defined similar to the signal regions but with an additional $b$-jet or light lepton.
-%$t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
-The dilepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate Type-3 and Type-4 fake taus. The semileptonic
-regions ($t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS) where $\thad$ and light lepton have opposite charge are used to calibrate Type-1 fake taus.
-Similarly for Type-2, the semileptonic regions ($t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS) where $\thad$ and light lepton have same charge are used.
+%$t_{\ell}t_{\ell}1b\thad$, $t_{\ell}t_{\ell}2b\thad$, $t_{\ell}t_h2b\thad$-2jSS, $t_{\ell}t_h2b\thad$-2jOS, $t_{\ell}t_h2b\thad$-3jSS, and $t_{\ell}t_h2b\thad$-3jOS.
+The dilepton regions ($t_{\ell}t_{\ell}1b\thad$ and $t_{\ell}t_{\ell}2b\thad$) are used to calibrate Type-3 and Type-4 fake taus. The semileptonic
+regions ($t_{\ell}t_h2b\thad$-2jOS and $t_{\ell}t_h2b\thad$-3jOS) where $\thad$ and light lepton have opposite charge are used to calibrate Type-1 fake taus.
+Similarly for Type-2, the semileptonic regions ($t_{\ell}t_h2b\thad$-2jSS and $t_{\ell}t_h2b\thad$-3jSS) where $\thad$ and light lepton have same charge are used.
 A simultaneous fit to data is made to derive the scale factors for fake taus in MC, which consist of total of 24 parameters
@@
 These scale factors are then used to correct the MC estimated fakes in the corresponding  signal regions with a single $b$-jet.
-In the $t_l\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the same procedure used in the $\tlhad$ channel.
+In the $t_{\ell}\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the same procedure used in the $\tlhad$ channel.
 %using the lepton and fake tau charges, then the scale factors are multiplied together.
@@
 enriched in misidentified
-$\had$ candidates via loosened $\had$ requirements with proper fake factors and partially from MC~\cite{ATLAS-CONF-2021-044}.
+tau candidates via loosened tau requirements with proper fake factors and partially from MC~\cite{ATLAS-CONF-2021-044}.
 These CRs do not overlap with the main signal regions, discussed in Section~\ref{sec:strategy_Htautau}.
 The CR selection requirements are analogous to those used to define signal regions, except
-that the subleading $\had$ candidate is required to fail the medium $\had$ identification, but it still passes a loose requirement.
-The contribution of fakes with subleading $\had$ candidate can be calculated by rescaling the templates of loose taus in the CR
+that the subleading tau candidate is required to fail the medium tau identification, but it still passes a loose requirement.
+The contribution of fakes with subleading tau candidate can be calculated by rescaling the templates of loose taus in the CR
 with fake factors (FF).
@@
 The FFs are computed as
-the ratio of the Data-MC ($\mathrm{real~tau}$) yields in which the $\had$ candidate is passed or failed the medium tau ID selection
+the ratio of the Data-MC ($\mathrm{real~tau}$) yields in which the tau candidate is passed or failed the medium tau ID selection
 in the $W$+jets control region.
@@
 %the electron or muon is prompt based on MC studies.
-%However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, especially to $t_l\had$ where the fake-lepton dominates.
+%However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, especially to $t_{\ell}\had$ where the fake-lepton dominates.
 and the jet multiplicity is low.
@@
 fake light leptons in the signal region is evaluated by scaling the number of loose leptons in the high $\met$ region by the ratio of tight and loose leptons in the
-low $\met$ region. The contributions of prompt leptons and calibrated $\had$ fakes in the number of tight and loose leptons are subtracted using MC simulation.
+low $\met$ region. The contributions of prompt leptons and calibrated fake taus in the number of tight and loose leptons are subtracted using MC simulation.
 A closure test is made for the background estimations in the signal depleted low BDT regions. The data are in good agreement with the background prediction in the
-$t_l\had$ channels where the fake light leptons are important, while they are negligible in other leptonic channels.
+$t_{\ell}\had$ channels where the fake light leptons are important, while they are negligible in other leptonic channels.

### 2022-02-24 sections/data_presel.tex

@@
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ with 25 ns bunch spacing collected from 2015 to 2018, corresponding to an integrated luminosity of $139~\ifb$.
-Only events recorded with a single-electron trigger, a single-muon trigger, or a di-$\tau$ trigger under stable beam conditions 
+Only events recorded with a single-electron trigger, a single-muon trigger, or a di-tau trigger under stable beam conditions 
 and for which all detector subsystems were operational are considered for analysis.
-While the events recorded by di-lepton triggers fall into the control regions used for fake-tau background estimation.
+While the events recorded by di-lepton triggers fall into the control regions used for fake tau background estimation.
 The number of $pp$ interactions per bunch crossing in this dataset ranges from about 8 to 45, with an average of 24.
@@
 %For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
-For di-$\tau$ triggers, the $\pt$ threshold of the leading (subleading) $\had$ candidate is 35 (25)~\gev.
+For di-tau triggers, the $\pt$ threshold of the leading (subleading) tau candidate is 35 (25)~\gev.
 Events satisfying the trigger selection are required to have at least one primary vertex candidate.
-To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have \pt 1~GeV above the threshold.
+To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have a \pt of 1~GeV above the threshold.
 
@@
 \begin{itemize}
-\item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\lephad$ decay.
-Exactly one $\had$ with opposite-side charge to $\tau_l$ is required, including at least three jets with exactly one $b$-jet.
-\item $t_l\hadhad$: Targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-jet.
-\item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identification so that there is only
+\item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ final states with $H\to\lephad$ decay.
+Exactly one $\had$ with opposite-side charge to $\lep$ is required, including at least three jets with exactly one $b$-jet.
+\item $t_{\ell}\hadhad$: Targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with $H\to\hadhad$ decay.
+Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-jet.
+\item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identification so that there is only
   one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-jet.
@@
 \begin{itemize}
-\item $t_h\hadhad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\hadhad$ decay. Exactly two $\had$ with opposite-sign charge are selected, including at least 3 jet with exactly one $b$-jet.
+\item $t_h\hadhad$: Targeting $t_hH$ and $t_ht(qH)$ final states with $H\to\hadhad$ decay. Exactly two $\had$ with opposite-sign charge are selected, including at least 3 jet with exactly one $b$-jet.
 \end{itemize}
@@
 %\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & hadronic channel \\ 
-& $t_h\lephad$ & $t_l\hadhad$ &  $t_l\had$ & $t_h\hadhad$\\
+& $t_h\lephad$ & $t_{\ell}\hadhad$ &  $t_{\ell}\had$ & $t_h\hadhad$\\
 \midrule

### 2022-02-24 sections/objects.tex

@@
 the scalar sum includes all tracks and energy deposits (excluding the lepton candidate itself) within the cone defined by $\Delta R<0.2 (0.3)$ around the %axis
-direction of the electron (muon). The electron (muon) candidates are required to satisfy both $I_R/\pt^l < 0.2~(0.3)$ and $E_R/\pt^l < 0.2~(0.3)$.
-%$I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$.
+direction of the electron (muon). The electron (muon) candidates ($\ell=e$ or $\mu$) are required to satisfy both
+%$I_R/\pt^l < 0.2~(0.3)$ and $E_R/\pt^l < 0.2~(0.3)$.
+$I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$.
 
@@
 The scale factors for the efficiencies of the tight \texttt{PLIV} working points are measured using the tag and probe method
-with $Z\rightarrow l^+l^-$ ($l=e$ or $\mu$) events. These scale factors have also been checked for the electron or muon from the tau decay
+with $Z\rightarrow \ell^+\ell^-$ events. These scale factors have also been checked for the electron or muon from the tau decay
 using $Z\rightarrow\tau\tau\rightarrow e\mu4\nu$ samples, which is consistent at 2\% level. To be conservative, an

### 2022-02-24 sections/signal_background_modeling.tex
updates and change back the version to 0.5

@@
 The parton showers, hadronisation and the underlying event were modelled using {\pythia}~8.230~\cite{Sjostrand:2006za} using the A14 tune and the NNPDF2.3 LO PDF set.
-%with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set 
-%in combination with the Perugia 2012 tune~\cite{Skands:2010ak}.
+%with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set %in combination with the Perugia 2012 tune~\cite{Skands:2010ak}.
 The single-top-quark samples are normalised to the approximate NNLO theoretical cross 
@@
 Since the fake rate of $\had$ candidate is much larger than for electron or muon, in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is prompt based on MC studies.
-However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, especially to $t_l\had$ where the fake-lepton dominates.
+However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, especially to $t_{\ell}\had$ where the fake-lepton dominates.
 %and the jet multiplicity is low.
@@
 The control regions are defined similar to the signal regions but with an additional $b$-jet or light lepton.
-%$t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
-The dilepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The semileptonic
-regions ($t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS) where $\thad$ and light lepton have opposite charge are used to calibrate Type1 fake taus.
-Similarly for the Type2, the semileptonic regions ($t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS) where $\thad$ and light lepton have same charge are used.
+%$t_{\ell}t_{\ell}1b\thad$, $t_{\ell}t_{\ell}2b\thad$, $t_{\ell}t_h2b\thad$-2jSS, $t_{\ell}t_h2b\thad$-2jOS, $t_{\ell}t_h2b\thad$-3jSS, and $t_{\ell}t_h2b\thad$-3jOS.
+The dilepton regions ($t_{\ell}t_{\ell}1b\thad$ and $t_{\ell}t_{\ell}2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The semileptonic
+regions ($t_{\ell}t_h2b\thad$-2jOS and $t_{\ell}t_h2b\thad$-3jOS) where $\thad$ and light lepton have opposite charge are used to calibrate Type1 fake taus.
+Similarly for the Type2, the semileptonic regions ($t_{\ell}t_h2b\thad$-2jSS and $t_{\ell}t_h2b\thad$-3jSS) where $\thad$ and light lepton have same charge are used.
 A simultaneous fit to data is made to derive the scale factors for fake taus in MC, which consist of total of 24 parameters
@@
 
-In the $t_l\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the sameprocedure used in the $\tlhad$ channel.
+In the $t_{\ell}\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the sameprocedure used in the $\tlhad$ channel.
 %using the lepton and fake tau charges, then the scale factors are multiplied together.

### 2022-02-24 sections/systematic_uncertainties.tex

@@
 
-The statistical uncertainties on the fake $\had$ background calibration in the leptonic channel are applied with uncorrelated uncertainties for different fake $\had$ sources and
+The statistical uncertainties on the fake tau background calibration in the leptonic channel are applied with uncorrelated uncertainties for different fake tau sources and
 different $\pt$ slices. The uncertainty of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both,

### 2022-02-24 ANA-TOPQ-2019-17-PAPER-metadata.tex
updating to V0.5

@@
 %\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
-\AtlasTitle{Search for flavour-changing neutral current interactions of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.1em}}
+\AtlasTitle{Search for flavour-changing neutral current interactions of the top quark and the Higgs
+boson which decays into a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.10em} }
 
@@
 \AtlasAbstract{%
-\vspace{0.1em}
+\vspace{0.10em}
 A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, an up-type quark ($q=u, c$), and a
 Standard Model (SM) Higgs boson decaying into a $\tau$-lepton pair ($H\rightarrow \tau^+\tau^-$) is presented.
-%The Higgs boson decays into a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
@@
 which one of top quarks decays into $Wb$ and the other decays into $qH$ through the FCNC interactions.
-%top quark with FCNC decay of $t\rightarrow qH$. 
 The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ 
@@
 as well as multiple jets. Event kinematics are used to separate signal from the background through a multivariate discriminant.  
-%Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
-%No significant excess of events above the background expectation is found,
-A slight excess of data is observed above the expected SM background with a significance of 2.6$\sigma$,
+A slight excess of data is observed above the expected SM background with a significance of 2.3$\sigma$,
 and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.

### 2022-02-24 sections/background_estimation.tex
updating to V0.5

@@
 The background prediction is further improved during the statistical analysis by performing a likelihood 
-fit to data using several signal-depleted control regions as discussed in Section~\ref{sec:strategy_Htautau}.
+fit to data using several signal-depleted control regions as shown in Table~\ref{tab:srcr}.
 
@@
 with fake factors (FF).
-The templates are produced by subtracting all MC background contributions with real sub-leading taus from data.
+The templates are produced by subtracting all MC background contributions with real subleading taus from data.
 The FFs are computed as

### 2022-02-24 sections/bdt_Htautau.tex
updating to V0.5

--- 2022-02-23 sections/strategy_Htautau.tex
@@
-%-------------------------------------------------------------------------------
-\section{Analysis strategy}
-\label{sec:strategy_Htautau}
-%-------------------------------------------------------------------------------
-
-The analysis strategy adopted in the $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more search channels.
-
-\subsection{Event categorisation and kinematic reconstruction}
-\label{sec:htautau_reco_cat}
-
-The $tt(qH)$ and $tH$ signal being probed are characterised by the presence of $\tau$-leptons from the decay of 
-the Higgs boson, where the remaining top quark decays into $Wb$. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
-%at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
-If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon, together with significant $\met$ is also expected.
-In a significant fraction of the events, the lowest $\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
-resulting in only three reconstructed jets where the production mode is dominant. 
-%some signal events mixed with production mode having only three reconstructed jets.
-In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs based on the number of light leptons,
-$\had$ candidates, and on the number of light flavored jets:
-$t_{\ell}\hadhad$, $t_{\ell}\had$-1j, $t_{\ell}\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}.
-
-%   \begin{table}
-%   \centering
-%   \caption{Overview of the signal regions and the control regions used for fake tau scale factor derivation in leptonic channels.}
-%   \label{tab:srcr}
-%   \begin{tabular}[h]{c|c|c|c|c|c|c}
-%   \hline \hline
-%   \multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
-%   \multirow{7}{*}{SR}&$t_{\ell}\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
-%   &$t_{\ell}\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
-%   &$t_{\ell}\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
-%   &$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
-%   &$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
-%   &$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
-%   &$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
-%   \multirow{6}{*}{CRtt}&$t_{\ell}t_{\ell}1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
-%   &$t_{\ell}t_{\ell}2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
-%   &$t_{\ell}t_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
-%   &$t_{\ell}t_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \cline{2-7}
-%   &$t_{\ell}t_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
-%   &$t_{\ell}t_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \hline
-%   \end{tabular}
-%   \end{table}
-
-\begin{table}
-\centering
-\caption{Overview of the signal regions (SR) and the $t\bar{t}$ control regions (CRtt) used for fake tau scale factor derivation in leptonic channels.
-Leptons are required to have either same-sign (SS) or opposite-sign (OS) charges in each region.}
-\label{tab:srcr}
-\begin{tabular}[h]{c|c|c|c|c|c|c}
-\hline \hline
-\multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
-\multirow{7}{*}{SR}&$t_{\ell}\thadhad$     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
-&$t_{\ell}\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
-&$t_{\ell}\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
-&$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
-&$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
-&$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
-&$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
-\multirow{6}{*}{CRtt}&$t_{\ell}t_{\ell}1b\tauhad$ & 1     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
-&$t_{\ell}t_{\ell}2b\tauhad$      & 2     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
-&$t_{\ell}t_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
-&$t_{\ell}t_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \cline{2-7}
-&$t_{\ell}t_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
-&$t_{\ell}t_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \hline
-\end{tabular}
-\end{table}
-
-%This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
-%of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay %is missing or not (events with exactly three jets or at least four jets).
-This event categorisation is primarily motivated by optimizing the sensitivity in each signal region that targets either leptonic or hadronic top-quark
-decays as well as the Higgs decays into either $\lephad$ or $\hadhad$ final states.   
-The event kinematic reconstruction is used in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the
-di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}. 
-%based on the strategy used in Ref.~\cite{Chen:2015nta}, and is summarised below.
-
-For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a hard narrow jet from the
-decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
-There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
-is considered as the $q$-jet since the FCNC top decay products are likely boosted closer together than other jets. 
-If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
-with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
-This kind of events will fall into $t_hH$ final state.
-%while the FCNC top resonance is
-%still reconstructable that the missing jet is likely from the decay of $W$ boson.
-%given the big chance that the jet which is missing is from $W$ decay.
-There are three jets coming from top hadronic decay including the $b$-jet and a pair of opposite-sign taus from the Higgs boson decay, where
-both $t_h$ and $H$ can be reconstructed.  
-%. So a Higgs resonance formed by the taus and a top resonance formed by
-%the jets are expected.
-
-The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
-are estimated using a kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
-measured $\met$ within their expected resolutions.
-The resolution on the Higgs boson mass is assumed to be $20~\gev$, while the resolution on the measured $\met$ is parameterised as a linear function of
-$\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
-After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
-$\pt$ of the parent top quarks are determined with better resolution in the signal events.
-
-For the  $t_{\ell}t(qH)$ and $t_{\ell}H$ events where $W$ boson from $t\to W b$ decay decays leptonically,
-%has a large momentum and the flying direction is unknown.
-the kinematic fit is no longer feasible due to extra neutrino from $W\rightarrow \ell\nu$ decay. The kinematic variables are calculated using the visible
-objects only. After the event reconstruction, a number of variables are used to discriminate the signal from the background using a multivariate analysis described
-in Section~\ref{sec:tmva}.
-
-%With the event topology reconstructed, a number of variables are defined for signal and background separation used in the multivariate analysis discussed below.
-
-%In the  $t_{\ell}t(qH)$ and $t_{\ell}H$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown.
-The kinematics fit is no longer feasible in the $t_{\ell}\hadhad$ channel.
-The variables calculated from the visible objects are directly used in the multivariate analysis.
-However, the kinematics fit is still performed for the $t_{\ell}\had$ channels where the lepton and $\had$ are treated as di-tau candidate.
-
-\subsection{Multivariate discriminant}
+\section{Multivariate discriminant}
 \label{sec:tmva}
@@
  $m_{\text{bjj},\text{fit}}$                            &   &  $1$                &           & $2$      &       & $3$      & $4$          \\
- ${\pt}_{\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     &       &  &         \\
+ ${\pt}^{\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     &       &  &         \\
  $m_{\tau\tau\text{q},\text{fit}}$                          &   &             &           &  &       & $10$     & $6$\\
@@
 \item ${\pt}_{\tau1} $ is the transverse momentum of the leading tau candidate.
-\item ${\pt}_{\tau2}$ is the transverse momentum of the sub-leading tau candidate.
-\item ${\pt}_{\ell}$ is the transverse momentum of the leading light lepton.
+\item ${\pt}_{\tau2}$ is the transverse momentum of the subleading tau candidate.
+\item ${\pt}^{\ell}$ is the transverse momentum of the leading light lepton.
 \item $\chi^2$ derived from the kinematic fit of the neutrino momentum.
@@
 \item $m_{\text{bjj}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top quark mass.
-\item \text{min}($m_{\tau\tau \text{j}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\tautau\text{q}}$.
-\item \text{min}($m_{\text{jj}}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.
+\item \text{min}($m_{\tau\tau \text{j}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\tau\tau\text{q}}$.
+\item \text{min}($m_{\text{jj}}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the $W$ candidate.
   %an alternative of $m_{\text{W}}$.
@@
 \end{eqnarray}
-\item $E_{\tau\text{i}}/E_{\tau\text{i},\text{fit}}$, \text{i}=1,2 are the momentum fraction carried by the visible decay products from the leading and subleading tau decays.
+\item $E_{\tau\text{i}}/E_{\tau\text{i},\text{fit}}$ (\text{i}=1,2) is the momentum fraction carried by the visible decay products from the leading and subleading tau decays.
 It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section.
@@
 \item $\Delta\phi(\tau\tau,\met)$ is the azimuthal angle between the $\met$ and di-tau system $\pT$.
-\item $\Delta R(i,j)$ is the angular distance between \text{i} and \text{j} objects. 
+\item $\Delta R(a,b)$ is the angular distance between \text{a} and \text{b} objects in the event. 
 %\item $\Delta R(\tau1,\text{light-jet})$ is the minimum angle distance between the tau candidate and the light-jet. If there are two taus in the event, the leading one is used.
@@
 \includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
-(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
+(a1) & (a2) & (a3) \\
+%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
 \includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
@@
 \includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
-(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
+(b1) & (b2) & (b3) \\
+%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
 \includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
-(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
+(c1) \\
+%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
 \end{tabular}

### 2022-02-24 sections/data_presel.tex
updating to V0.5

@@
 
-The signal final state including an electron or muon or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
+The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
 The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger.
@@
 \item $t_{\ell}\hadhad$: Targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with $H\to\hadhad$ decay.
-Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-jet.
+Exactly a light lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-jet.
 \item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identification so that there is only
-  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-jet.
+  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the light lepton is required, including at least 2 jets with exactly one $b$-jet.
 \end{itemize}

### 2022-02-24 sections/introduction.tex
updating to V0.5

@@
 %with a measured mass $m_H=125.09 \pm 0.24~\gev$~\cite{Aad:2015zhl}, 
-such interactions could manifest themselves as FCNC top-quark decays~\cite{Agashe:2013hma}, $t\to qH$.  
+such interactions could manifest themselves as FCNC top-quark decays~($t\to qH$)~\cite{Agashe:2013hma}.  
 In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
@@
 The dataset is divided into several final states depending on the production mode and
-the  $W$ decay. Top pair production events where the W boson decays hadronically (leptonicall) are referred to as $t_h$ ($t_{\ell}$). The contribution of 
+the  $W$ decay. Top pair production events where the $W$ boson decays hadronically (leptonicall) are referred to as $t_h$ ($t_{\ell}$). The contribution of 
 $W\rightarrow\tau\nu$ is included as $\lep$ in $t_{\ell}$ when the $\tau$ decays into a light lepton (electron or muon) or as $\thad$ 
@@
 either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_{\ell}$). 
-Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are named hadronic channels.
+Events with two hadronically decaying $\tau$-leptons without electron or muon are named hadronic channels.
 Events with at least one \tauhad with an additional electron or muon are named leptonic channels.

### 2022-02-24 sections/strategy_Htautau.tex
updating to V0.5

@@
 The analysis strategy adopted in the $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more search channels.
-
-\subsection{Event categorisation and kinematic reconstruction}
-\label{sec:htautau_reco_cat}
-
+%\subsection{Event categorisation and kinematic reconstruction}
+%\label{sec:htautau_reco_cat}
 The $tt(qH)$ and $tH$ signal being probed are characterised by the presence of $\tau$-leptons from the decay of 
@@
 di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.
+
 %based on the strategy used in Ref.~\cite{Chen:2015nta}, and is summarised below.
@@
 However, the kinematics fit is still performed for the $t_{\ell}\had$ channels where the lepton and $\had$ are treated as di-tau candidate.
-
-\subsection{Multivariate discriminant}
-\label{sec:tmva}
-
-%%%%%%%%%%%%%%%
-\begin{table*}[t!]
-  \caption{\small{The number of discriminating variables (n) used in the training of BDT in each SR. 
-The rank of the discriminating variables relative to one another according to their importance in the training is reported from highest (1) to 
-lowest (n). Variables whose ranking is missing are not included in the training of the corresponding SR. The description of each variable is provided in the text.}}
-%Variables are ranked from highest (1) to lowest (n) relative to one another by their
-%      importance in the training. Variables which do not have a ranking are not included in the training. 
-%The values represent their ra importance rankings of each variable and cross($\times$) denotes the variable is not used in the training.
-%      The descriptions of each variable are provided in the following text.}}
-\label{tab:importance}
- \centering
- \begin{tabular}{cccccccc} \toprule\toprule
-   & $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_{\ell}2\tauhad$     & $t_h2\tauhad$-2j & $t_h2\tauhad$-3j       \\\midrule
-   Total variables~(n)                           & $12$ & $15$ & $12$ & $17$ & $15$ & $12$ & $12$ \\\midrule 
- $m_{\text{jj}}$                                      &   &             &           & $9$      &       & $6$      & $7$\\
- $\chi^{2}$                                          &   &             &           & $14$     &       &  &       \\
- \text{max}($\eta_{\tau}$)                           & $4$       &             &  $4$              &  & $10$          &  &        \\
- $m^{W}_{\text{T}}$                           & $11$      &             &  $8$              &  & $13$          &  &         \\
- $m_{\tau\tau,\text{fit}}$                                     &   &  $2$                &           & $3$      &       & $1$      & $1$          \\
- $m_{\text{bjj},\text{fit}}$                            &   &  $1$                &           & $2$      &       & $3$      & $4$          \\
- ${\pt}_{\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     &       &  &         \\
- $m_{\tau\tau\text{q},\text{fit}}$                          &   &             &           &  &       & $10$     & $6$\\
- $m_{\text{bjj}}$                 & $3$       &             &  $5$              &  & $4$           &  &         \\
- ${\pt}_{\tau1}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
- $\met$                                              & $5$       &  $11$               &  $10$             & $13$     & $6$           & $7$    & $13$          \\
- $m_{\tau\tau}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
- $E_{\tau1}/E_{\tau1,\text{fit}}$                  &   &  $10$               &           & $12$     &       & $8$    & $8$          \\
- $E_{\tau2}/E_{\tau2,\text{fit}}$                  &   &  $7$                &           & $4$      &       & $9$    & $11$         \\
- ${\pt}_{\tautau} $                          &   &             &           &  & $9$           &  &         \\
- $m_{\tau\tau\text{q}}$               &   &             &           &  & $3$           &  &        \\
- $\Delta\phi(\tau\tau,\met)$                         &   &  $6$                            &           & $16$     &       & $13$   & $12$         \\
- $\met\text{centrality}$                             &   &  $13$               &           & $15$     &       & $12$   & $9$         \\
- \text{min}($m_{\tau\tau \text{j}}$)             & $9$       &             &  $3$              &  & $14$          &  &         \\
- \text{min}($\Delta R(\ell,\tau)$)                               & $8$       &  $9$                &  $9$              & $10$     & $15$          &  &         \\
- $\Delta R(\tau,\tau)$                               &   &             &           &  & $2$           & $4$    & $3$             \\
- $\Delta R(\ell,\text{$b$-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          &  &         \\
- $\Delta R(\tau1,\text{$b$-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          &  &        \\
- $\Delta R(\ell+\text{$b$-jet},\tau\tau )$             &   &             &           &  & $7$           &  &         \\
- $\Delta R(\tau1,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
- \text{min}($m_{jj}$) &   &  $12$               &           & $11$     &       &  &         \\
-% $m_{\text{W}}$                                      & $\times$  &  $\times$           &  $\times$         & $9$      & $\times$      & $6$      & $7$\\
-% $\chi^{2}$                                          & $\times$  &  $\times$           &  $\times$         & $14$     & $\times$      & $\times$ & $\times$      \\
-% \text{max}($\eta_{\tau}$)                           & $4$       &  $\times$           &  $4$              & $\times$ & $10$          & $\times$ & $\times$       \\
-% $m^{\text{T}}_{\text{W}}$                           & $10$      &  $\times$           &  $8$              & $\times$ & $13$          & $\times$ & $\times$        \\
-% $m_{\tau,\tau}$                                     & $\times$  &  $2$                &  $\times$         & $3$      & $\times$      & $1$      & $1$          \\
-% $m_{\text{t},\text{SM}}$                            & $\times$  &  $1$                &  $\times$         & $2$      & $\times$      & $3$      & $4$          \\
-% $p_{\text{T},\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     & $\times$      & $\times$ & $\times$        \\
-% $m_{\text{t},\text{FCNC}}$                          &  $\times$ &  $\times$           &  $\times$         & $\times$ & $\times$      & $10$     & $6$\\
-% $m_{\text{t},\text{SM},\text{vis}}$                 & $3$       &  $\times$           &  $5$              & $\times$ & $4$           & $\times$ & $\times$        \\
-% $p_{\text{T},\tau}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
-% $\met$                                              & $5$       &  $11$               &  $10$             & $13$     & $6$           & $7$    & $13$          \\
-% $m_{\tau\tau,\text{vis}}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
-% $E_{\text{vis}~\tau,1}/E_{\tau,1}$                  & $\times$  &  $10$               &  $\times$         & $12$     & $\times$      & $8$    & $8$          \\
-% $E_{\text{vis}~\tau,2}/E_{\tau,2}$                  & $\times$  &  $7$                &  $\times$         & $4$      & $\times$      & $9$    & $11$         \\
-% $P_{\text{T,\tauhadvis}} $                          & $\times$  &  $\times$           &  $\times$         & $\times$ & $9$           & $\times$ & $\times$        \\
-% $m_{\text{t},\text{FCNC},\text{vis}}$               & $\times$  &  $\times$           &  $\times$         & $\times$ & $3$           & $\times$ & $\times$       \\
-% $\Delta\phi(\tau\tau,\met)$                         & $\times$  &  $6$    			   &  $\times$         & $16$     & $\times$      & $13$   & $12$         \\
-% $\met\text{centrality}$                             & $\times$  &  $13$               &  $\times$         & $15$     & $\times$      & $12$   & $9$         \\
-% \text{Min}($m_{\tau\tau \text{q-jet}}$)             & $9$       &  $\times$           &  $3$              & $\times$ & $14$          & $\times$ & $\times$        \\
-% $\Delta R(\ell,\tau)$                               & $8$       &  $9$                &  $9$              & $10$     & $15$          & $\times$ & $\times$        \\
-% $\Delta R(\tau,\tau)$                               & $\times$  &  $\times$           &  $\times$         & $\times$ & $2$           & $4$    & $3$             \\
-% $\Delta R(\ell,\text{b-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          & $\times$ & $\times$        \\
-% $\Delta R(\tau,\text{b-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          & $\times$ & $\times$       \\
-% $\Delta R(\ell+\text{b-jet},\tau\tau )$             & $\times$  &  $\times$           &  $\times$         & $\times$ & $7$           & $\times$ & $\times$        \\
-% $\Delta R(\tau,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
-% \text{Min}($m_{\text{light-jet},\text{light-jet}}$) & $\times$  &  $12$               &  $\times$         & $11$     & $\times$      & $\times$ & $\times$        \\
- \bottomrule\bottomrule\\
- \end{tabular}
-\end{table*}
-
-%%%%%%%%%%%%%%%
-%%%  \begin{table*}[t!]
-%%%    \caption{\small{Discriminating variables used in the training of the BDT for hadronic channel.
-%%%        The values in percent (\%) represent the separation and importance of each variable.
-%%%      The descriptions of each variable are provided in the following text.}}
-%%%  \label{tab:importance_xTFW}
-%%%  \input{tables/xTFW_Merged}
-%%%  \end{table*}
-%%%  
-%%%  \begin{table*}[t!]
-%%%    \caption{\small{Discriminating variables used in the training of the BDT for leptonic channel.
-%%%        The values in percent (\%) represent the separation and importance of each variable.
-%%%      The descriptions of each variable are provided in the following text.}}
-%%%  \label{tab:importance_tthML}
-%%%  \input{tables/tthML_Merged}
-%%%  \end{table*}
-
-Boosted decision trees (BDT) implemented in the TMVA framework~\cite{Hocker:2007ht} are used in each SR to improve the separation between signal and background. 
-%The separate training exploits differences in event kinematics across SRs.  
-%draft 1 version
-In the training, all signal events from $tt(qH)$ and $tH$ are merged together for $tuH$ and $tcH$. All background sources from SM processes
-(including both real and fake tau contributions) are also used in the training.
-
-A large set of potential variables are investigated in each SR separately.
-The discrimination of a given variable is quantified by the "separation"(measures the degree of overlap between background and signal shape) and "importance"(depicts the power of the variable to the classification of the events) provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is larger than 2\% were kept.
-The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance}. The discriminating variables used are:
-\begin{itemize}
-\item $\met$ is the missing transverse momentum.
-\item ${\pt}_{\tau1} $ is the transverse momentum of the leading tau candidate.
-\item ${\pt}_{\tau2}$ is the transverse momentum of the sub-leading tau candidate.
-\item ${\pt}_{\ell}$ is the transverse momentum of the leading light lepton.
-\item $\chi^2$ derived from the kinematic fit of the neutrino momentum.
-\item $m_{\text{bjj},\text{fit}}$ is the fitted invariant mass of the $b$-jet and the two jets from the $W$ decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
-This variable is only defined for the 4-jet $t_hH$ and $t_ht(qH)$ events.
-\item $m^{W}_{\text{T}}$ is the transverse mass calculated from the lepton and $\met$ in the leptonic channels, defined as
-\begin{equation}
-m^{W}_{\text{T}} = \sqrt{2 {\pt}_{\ell} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\ell,\text{miss}} \right)},  
-\end{equation}
-where $\Delta\phi_{\ell,\text{miss}}$ is the azimuth angle between the light-lepton and $\met$.  
-\item $m_{\tau\tau,\text{fit}}$ is the fitted invariant mass of the tau candidates and reconstructed neutrinos for the $t_hH$ and $t_ht(qH)$ events. 
-\item $m_{\text{jj}}$ is the reconstructed invariant mass of two light-jets from the $W$ decay with the mass closet to the $W$ mass.
-\item $m_{\tau\tau\text{q},\text{fit}}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
-\item $m_{\tau\tau}$ is the visible invariant mass of the di-tau system. %or the lepton and $\had$ candidate when there is only one $\had$.
-\item ${\pt}_{\tau\tau}$ is the visible $\pT$ of the di-tau system.
-\item $m_{\tau\tau,\text{q}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
-\item $m_{\text{bjj}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top quark mass.
-\item \text{min}($m_{\tau\tau \text{j}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\tautau\text{q}}$.
-\item \text{min}($m_{\text{jj}}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.
-  %an alternative of $m_{\text{W}}$.
-\item $\met$ centrality is a measure of how central the $\met$ lies between the two tau candidates in the transverse plane, and is defined as
-\begin{eqnarray}
-\begin{array}{l}
-\met~\text{centrality} = {(x+y)}/{\sqrt{x^2+y^2}}, \\
-\text{with}~x=\frac{\sin(\phi_{\text{miss}}-\phi_{\tau_1})}{\sin(\phi_{\tau_2}-\phi_{\tau_1})}, \quad  y=\frac{\sin(\phi_{\tau_2}-\phi_{\text{miss}})}{\sin(\phi_{\tau_2}-\phi_{\tau_1})} ,
-\end{array}
-\label{eq:eq3}
-\end{eqnarray}
-\item $E_{\tau\text{i}}/E_{\tau\text{i},\text{fit}}$, \text{i}=1,2 are the momentum fraction carried by the visible decay products from the leading and subleading tau decays.
-It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section.
-For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}.
-%\item $\Delta R(\ell+\text{b-jet},\tau\tau)$ is the angular distance between the lepton+$b$-jet and di-tau candidates.
-%\item $\Delta R(\ell,\text{b-jet})$ is the angular distance between the lepton and $b$-jet.
-%\item $\Delta R(\tau,\text{b-jet})$ is the angular distance between the tau candidate and $b$-jet. If there are two taus in the event, the leading one is selected for the calculation.
-%\item \text{max}($\eta_{\tau}$) is the maximum $\eta$ value among the tau candidates.
-%\item $\Delta R(\ell,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
-%\item $\Delta R(\tau,\text{q-jet})$ is the angular distance between the tau candidate and the reconstructed $q$-jet. If there are two taus in the event, the leading one is used.
-%\item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(\ell,\tau)$.
-\item $\Delta\phi(\tau\tau,\met)$ is the azimuthal angle between the $\met$ and di-tau system $\pT$.
-\item $\Delta R(i,j)$ is the angular distance between \text{i} and \text{j} objects. 
-%\item $\Delta R(\tau1,\text{light-jet})$ is the minimum angle distance between the tau candidate and the light-jet. If there are two taus in the event, the leading one is used.
-\end{itemize}
-
-A comparison between data and the predicted background for the leading tau $\pt$ distribution in the SRs 
-%some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
-is shown in Figure~\ref{fig:taupt_prefit}.
-%each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_{\ell}hadhad}.
-%The comparison between the data and predicted background after preselection for the distributions of two of the most 
-%discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
-%The expected signals are also shown after scaled up for the shape comparison of the distributions.
-%by a large factor normalized to the total number of events in the predicted
-%background for the shape comparison.   
-%corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.
-The last bin of each plot contains the overflow entries.
-The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model}.
-The hashed area represents the total uncertainty of the background.
-A good description of the data by the background model is observed in all cases.
-The final observable used to extract the signal contribution is the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.
-
-%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
-%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{\FCNCFigures/tex/BDTinput}
-\begin{figure}[H]
-\centering
-\begin{tabular}{@{}ccc@{}}
-%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
-%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
-%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
-(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
-(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
-(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
-\end{tabular}
-\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit').
-The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
-Overflow bins are included respectively in the last bin.
-Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic)
-channels. 
-%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
-The lower panels show the ratios of the data to the background prediction.}
-\label{fig:taupt_prefit}
-\end{figure}
-
-% %\input{\FCNCFigures/tex/BDT}
-% \begin{figure}[H]
-% \centering
-% \begin{tabular}{@{}ccc@{}}
-% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/BDTG_test.pdf} &
-% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/BDTG_test.pdf}&
-% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}\\
-% (a1) BDT discriminant in $t_{\ell}\thadhad$ & (a2) BDT discriminant in  $t_{\ell}\tauhad$-1j& (a3) BDT discriminant in $t_{\ell}\tauhad$-2j\\
-% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf} &
-% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b3j_os_vetobtagwp70_highmet/BDTG_test.pdf} &
-% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/BDTG_test.pdf} \\
-% (b1) BDT discriminant in $t_h\tlhad$-2j & (b2) BDT discriminant in  $t_h\tlhad$-3j & (b3) BDT discriminant in $t_h\thadhad$-2j \\
-% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/BDTG_test.pdf} & \\
-% (c1) BDT discriminant in$t_h\thadhad$-3j\\
-% \end{tabular}
-% \caption{ The BDT output distributions are compared between the expected background and $tqH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3),$t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1).
-Only statistical uncertainties are being shown (?).
-Underflow and overflow bins are included
-% respectively in the first and last bins.
-Empty data bins here are always blinded based on our strategy.
-The real tau contributions shown from $t\bar{t}$ and other MC including % diboson, single top, and V+jets.}
-% \label{fig:asimov_prefitbdt}
-% \end{figure}

### 2022-02-24 sections/strategy_Htautau_oldversion.tex
updating to V0.5

--- 2022-02-23 sections/strategy_Htautau.tex
@@
 \item ${\pt}_{\tau2}$ is the transverse momentum of the sub-leading tau candidate.
-\item ${\pt}_{\ell}$ is the transverse momentum of the leading light lepton.
+\item ${\pt}^{\ell}$ is the transverse momentum of the leading light lepton.
 \item $\chi^2$ derived from the kinematic fit of the neutrino momentum.
@@
 \item $m_{\text{bjj}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top quark mass.
-\item \text{min}($m_{\tau\tau \text{j}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\tautau\text{q}}$.
+\item \text{min}($m_{\tau\tau \text{j}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\tau\tau\text{q}}$.
 \item \text{min}($m_{\text{jj}}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.

### 2022-02-24 ANA-TOPQ-2019-17-PAPER-metadata.tex
update new comments

@@
 \AtlasTitle{Search for flavour-changing neutral current interactions of the top quark and the Higgs
-boson which decays into a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.10em} }
+boson in events with a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.10em} }
 
@@
 The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
-the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$ for the new physics scale $\Lambda$ at 1~TeV, respectively.} 
+the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.}%for the new physics scale $\Lambda$ at 1~TeV, respectively.} 
 %$|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 

### 2022-02-24 sections/conclusion.tex
updating to V0.5
update new comments

@@
 No significant excess of events above the background expectation is found.
-A slight excess of data is observed above background with a significance of 2.6$\sigma$.  
+A slight excess of data is observed above background with a significance of 2.3$\sigma$.  
 95\% CL upper limits are set on the $t\to Hq$ branching ratios and the corresponding
@@
 The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
-the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$ for the new physics scale $\Lambda$ at 1~TeV, respectively.
+the effective $tqH$ couplings for a new physics scale $\Lambda$ of 1~TeV are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.
 These results improve significantly upon previous ATLAS and CMS limits on the $t\rightarrow Hq$ branching ratios.

### 2022-02-24 sections/data_presel.tex
update new comments

@@
 %For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
-For di-tau triggers, the $\pt$ threshold of the leading (subleading) tau candidate is 35 (25)~\gev.
+For di-tau triggers, the $\pt$ threshold of the leading (subleading) $\had$ candidate is 35 (25)~\gev.
 Events satisfying the trigger selection are required to have at least one primary vertex candidate.
@@
 \begin{itemize}
-\item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ final states with $H\to\lephad$ decay.
+\item $t_h\lephad$: Targeting into the $t_hH$ and $t_ht(qH)$ final states with $H\to\lephad$ decay.
 Exactly one $\had$ with opposite-side charge to $\lep$ is required, including at least three jets with exactly one $b$-jet.
@@
 \begin{itemize}
-\item $t_h\hadhad$: Targeting $t_hH$ and $t_ht(qH)$ final states with $H\to\hadhad$ decay. Exactly two $\had$ with opposite-sign charge are selected, including at least 3 jet with exactly one $b$-jet.
+\item $t_h\hadhad$: Targeting into the $t_hH$ and $t_ht(qH)$ final states with $H\to\hadhad$ decay.
+Exactly two $\had$ with opposite-sign charge are selected, including at least 3 jet with exactly one $b$-jet.
 \end{itemize}

### 2022-02-24 sections/introduction.tex
update new comments

@@
 such interactions could manifest themselves as FCNC top-quark decays~($t\to qH$)~\cite{Agashe:2013hma}.
+Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through this interaction would enhance
+%becomes non-zero, enhancing 
+the total
+production cross section of $pp\rightarrow tH$.
 In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
@@
 %which could be interesting for future studies.
-Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through this interaction would enhance 
-%becomes non-zero, enhancing 
-the total
-production cross section of $pp\rightarrow tH$.
+%Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through %this interaction would enhance 
+%%becomes non-zero, enhancing 
+%the total
+%production cross section of $pp\rightarrow tH$.
 The study of this process will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
-The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at LHC 13 TeV centre of mass energy~\cite{deFlorian:2016spz}.
+The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at 13 TeV centre of mass energy~\cite{deFlorian:2016spz}.
 
@@
 in upper limits of $\BR(t\to cH)<0.47\%$ and $\BR(t\to uH)<0.47\%$, in each case neglecting the other decay mode.
-Compared with previous searches, the search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
+%Compared with previous searches, 
+The search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
 $pp \to tH$ production~\cite{Greljo:2014dka}. 

### 2022-02-24 sections/strategy_Htautau.tex
update new comments

@@
 %given the big chance that the jet which is missing is from $W$ decay.
-There are three jets coming from top hadronic decay including the $b$-jet and a pair of opposite-sign taus from the Higgs boson decay, where
+There are three jets coming from top hadronic decay including the $b$-jet and a pair of opposite-sign $\had$ from the Higgs boson decay, where
 both $t_h$ and $H$ can be reconstructed.  

### 2022-02-24 ANA-TOPQ-2019-17-PAPER-metadata.tex
commented out author list that fixed the conflict

@@
 \AtlasAbstract{%
-\vspace{0.10em}
 A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, an up-type quark ($q=u, c$), and a
@@
 % Author - this does not work with revtex (add it after \begin{document})
-\author{The ATLAS Collaboration}
+%\author{The ATLAS Collaboration}
 

### 2022-02-24 sections/introduction.tex
minor updates

@@
 such interactions could manifest themselves as FCNC top-quark decays~($t\to qH$)~\cite{Agashe:2013hma}.
+%Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through this interaction would enhance 
+%becomes non-zero, enhancing 
+%the total
+%production cross section of $pp\rightarrow tH$.
+
+In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
+Therefore, an observation of an enhanced rate of this decay would be a clear evidence for new physics.
 Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through this interaction would enhance
 %becomes non-zero, enhancing
-the total
-production cross section of $pp\rightarrow tH$.
-In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
+the total production cross section of $pp\rightarrow tH$.
 The $t\to qH$ branching fraction in the SM is calculated to be exceedingly small, $\BR(t\to qH)\approx10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}. 
@@
 %the largest enhancements are typically found for the $tqH$ couplings, and in particular the $tcH$ coupling~\cite{Agashe:2013hma}.
-Therefore, an observation of an enhanced rate of this decay would be a clear evidence for new physics.
+%Therefore, an observation of an enhanced rate of this decay would be a clear evidence for new physics.
 %The $tqH$ interaction could also potentially open up more
@@
 %production cross section of $pp\rightarrow tH$.
-The study of this process will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
+The study of $pp\rightarrow tH$ process will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
 The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at 13 TeV centre of mass energy~\cite{deFlorian:2016spz}.
@@
 In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $qH$ with a small branching ratio 
- $\BR(t\to qH)$, denoted as $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
-$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
+ $\BR(t\to qH)$, denoted as $\ttbar \to WbHq$\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
+$WbWb$ is used to denote $W^+b W^- \bar{b}$.}.  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
 the SM.

### 2022-03-10 sections/background_estimation.tex
update most comments

@@
 %aimed at fake taus from different origins.
-There are four kinds of fake taus that need to be calibrated: Type-1 fake taus from $W$-jets ($\tau_{W}$)
+There are four kinds of fake taus that need to be calibrated: Type-1 fake taus from hadronically-decaying W-bosons ($\tau_{W}$) %$W$-jets ($\tau_{W}$)
 with opposite-sign (OS) of charge to the light lepton;
@@
 enriched in misidentified
-tau candidates via loosened tau requirements with proper fake factors and partially from MC~\cite{ATLAS-CONF-2021-044}.
+tau candidates via loosened tau requirements with fake factors and partially from MC~\cite{ATLAS-CONF-2021-044}.
 These CRs do not overlap with the main signal regions, discussed in Section~\ref{sec:strategy_Htautau}.

### 2022-03-10 sections/bdt_Htautau.tex
update new comments
update most comments

@@
 A large set of potential variables are investigated in each SR separately.
-The discrimination of a given variable is quantified by the "separation"(measures the degree of overlap between background and signal shape) and "importance"(depicts the power of the variable to the classification of the events) provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is larger than 2\% were kept.
+The discrimination of a given variable is quantified by the "separation" (measures the degree of overlap between background and signal shape) and "importance" (depicts the power of the variable to the classification of the events) provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is larger than 2\% were kept.
 The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance}. The discriminating variables used are:
@@
 \item $\chi^2$ derived from the kinematic fit of the neutrino momentum.
-\item $m_{\text{bjj},\text{fit}}$ is the fitted invariant mass of the $b$-jet and the two jets from the $W$ decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
+\item $m_{\text{bjj},\text{fit}}$ is the fitted invariant mass of the $b$-jet and the two jets from the $W$ boson decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
 This variable is only defined for the 4-jet $t_hH$ and $t_ht(qH)$ events.
@@
 
-A comparison between data and the predicted background for the leading tau $\pt$ distribution in the SRs 
+A comparison after fake calibration between data and the predicted background for the leading $\had$ $\pt$ distribution in the SRs 
 %some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)

### 2022-03-10 sections/data_presel.tex
update most comments

@@
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ with 25 ns bunch spacing collected from 2015 to 2018, corresponding to an integrated luminosity of $139~\ifb$.
-Only events recorded with a single-electron trigger, a single-muon trigger, or a di-tau trigger under stable beam conditions 
+Only events recorded with a single-electron trigger, a single-muon trigger, or a di-tau trigger~\cite{TRIG-2018-05,TRIG-2018-01,id_trigger,l1topo_trigger} under stable beam conditions 
 and for which all detector subsystems were operational are considered for analysis.
@@
 For di-tau triggers, the $\pt$ threshold of the leading (subleading) $\had$ candidate is 35 (25)~\gev.
-Events satisfying the trigger selection are required to have at least one primary vertex candidate.
+%Events satisfying the trigger selection are required to have at least one primary vertex candidate.
 To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have a \pt of 1~GeV above the threshold.
 
-The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
-The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger.
+%The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
+%The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger.
+Further requirements are defined targeting different signal decay modes:
+The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers.
 Further requirements are defined targeting different signal decay modes:
@@
 \item $t_{\ell}\hadhad$: Targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with $H\to\hadhad$ decay.
-Exactly a light lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-jet.
+Exactly one light lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-jet.
 \item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identification so that there is only

### 2022-03-10 sections/detector.tex
update most comments

@@
 terms of the polar angle $\theta$ as $\eta = - \ln \tan(\theta/2)$.
-Angular distance is measured in units of $\Delta R\equiv \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.} and consists of an inner tracking detector surrounded by a thin superconducting solenoid producing a
+Angular separation is measured in units of $\Delta R\equiv \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.} and consists of an inner tracking detector surrounded by a thin superconducting solenoid producing a
 2~T axial magnetic field, electromagnetic and hadronic calorimeters, and a muon spectrometer incorporating three large toroid magnet assemblies with eight coils each.
@@
 The calorimeter system covers the pseudorapidity range $|\eta| < 4.9$.
-Within the region $|\eta|< 3.2$, electromagnetic (EM) calorimetry is provided by barrel and endcap high-granularity lead/liquid-argon (LAr) sampling calorimeters, with an additional thin LAr presampler covering $|\eta| < 1.8$, to correct for energy loss in material upstream of the calorimeters.
+Within the region $|\eta|< 3.2$, electromagnetic (EM) calorimetry is provided by barrel and endcap high-granularity lead/liquid-argon (LAr) sampling calorimeters, with an additional thin LAr presampler covering $|\eta| < 1.8$ to correct for energy loss in material upstream of the calorimeters.
 Hadronic calorimetry is provided by %the

### 2022-03-10 sections/introduction.tex
update most comments

@@
 are underway. One such possibility is flavour-changing neutral-current (FCNC) interactions between the Higgs boson, 
-the top quark, and an up-quark, $tqH$ ($q=u, c$), which has been actively searched for by the ATLAS and CMS collaborations.  
+the top quark, and an up-type quark, $tqH$ ($q=u, c$), which has been actively searched for by the ATLAS and CMS collaborations.  
 %with increased precision and proved to be consistent with the Standard Model (SM) predictions. 
@@
 %ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
-In contrast, large enhancements of these branching ratios are possible in some scenarios beyond the SM.
-Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{Branco:2hdm2012} with or without flavour violation,
+However, these branching ratios can as high as $\BR(t\to qH) \sim 10^{-5}$ which incorporate beyond the SM processes.
+Examples of these include: quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{ Branco:2hdm2012} with or without flavour violation,
  %of type I, with explicit flavour conservation,
@@
 or warped extra dimensions models with SM fermions in the bulk~\cite{Azatov:2009na}. 
-In these scenarios, branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$. 
-An even larger branching ratio of  $\BR(t\to cH) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation (type III),
-since a tree-level FCNC coupling is no longer forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}. 
+% In contrast, large enhancements of these branching ratios are possible in some scenarios beyond the SM.
+% Examples include quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{ %Branco:2hdm2012} with or without flavour violation,
+% %of type I, with explicit flavour conservation,
+% %and of type II, such as
+% the minimal supersymmetric SM (MSSM)~\cite{Bejar:2000ub, Guasch:1999jp,Cao:2007dk,Cao:2014udj},
+% supersymmetric models with R-parity violation~\cite{Eilam:2001dh}, composite Higgs models with partial  %compositeness~\cite{Azatov:2014lha}, 
+% or warped extra dimensions models with SM fermions in the bulk~\cite{Azatov:2009na}. 
+% In these scenarios, branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$. 
+An even larger branching ratio of  $\BR(t\to cH) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation, since a tree-level FCNC coupling is no longer forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}.
 %While other FCNC top couplings ($tq\gamma$, $tqZ$, $tqg$) are also enhanced in these scenarios beyond the SM, 
@@
 The study of $pp\rightarrow tH$ process will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
-The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at 13 TeV centre of mass energy~\cite{deFlorian:2016spz}.
+The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at centre-of-mass energies of $\sqrt{s}= 13~\tev$ centre of mass energy~\cite{deFlorian:2016spz}.
 
@@
 \begin{table}[t!]
-\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$ obtained from ATLAS and CMS Collaborations with Run 2 data.}}
+\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$ obtained from ATLAS and CMS Collaborations with Run 2 data.
+Each limit is obtained assuming the other branching ratio is 0}}
 \begin{center}
@@
 & $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
-%& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
+& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
 %& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
@@
 The dataset is divided into several final states depending on the production mode and
-the  $W$ decay. Top pair production events where the $W$ boson decays hadronically (leptonicall) are referred to as $t_h$ ($t_{\ell}$). The contribution of 
+the  $W$ decay. Top quark pair production events where the $W$ boson decays hadronically (leptonically) are referred to as $t_h$ ($t_{\ell}$). The contribution of 
 $W\rightarrow\tau\nu$ is included as $\lep$ in $t_{\ell}$ when the $\tau$ decays into a light lepton (electron or muon) or as $\thad$ 
@@
 Events with at least one \tauhad with an additional electron or muon are named leptonic channels.
-More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data~\cite{fcnc36}.
+More signal regions (with top quark decay leptonically) are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data~\cite{fcnc36}.
 In addition, an improved treatment of misidentified $\tau$-leptons in simulation and data-driven

### 2022-03-10 sections/objects.tex
update most comments

@@
 
-Events are selected from $pp$ collisions at $\sqrt{s}$=13 TeV recorded by the ATLAS detector during 2015-2018.
+Events are selected from $pp$ collisions at $\sqrt{s}$=13 TeV recorded by the ATLAS detector during 2015-2018~\cite{DAPR-2018-01}.
 Only events for which all relevant subsystems were operational are considered.
-Events are required to have at least one vertex with two or more tracks with transverse momentum
+Events are required to have at least one primary vertex with two or more tracks with transverse momentum
 %The event reconstruction is affected by multiple $pp$ collisions in a single bunch crossing and by collisions
@@
 
-Electron candidates~\cite{ATLAS-CONF-2016-024,Aaboud:2018ugz} are reconstructed from energy 
+Electron candidates~\cite{EGAM-2018-01} are reconstructed from energy 
 clusters in the EM calorimeter that are matched to reconstructed tracks in the inner detector;
@@
 
-Muon candidates~\cite{Aad:2016jkr} are reconstructed by matching track segments in %the various
+Muon candidates~\cite{MUON-2018-03} are reconstructed by matching track segments in %the various
 different layers of the muon spectrometer to tracks found in the inner detector;
@@
 the scalar sum includes all tracks and energy deposits (excluding the lepton candidate itself) within the cone defined by $\Delta R<0.2 (0.3)$ around the %axis
-direction of the electron (muon). The electron (muon) candidates ($\ell=e$ or $\mu$) are required to satisfy both
+direction of the electron (muon). The electron (muon) candidates are required to satisfy both
 %$I_R/\pt^l < 0.2~(0.3)$ and $E_R/\pt^l < 0.2~(0.3)$.
-$I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$.
+$I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$ ($\ell=e$ or $\mu$).
 
-Tight isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions based on a trained isolation boosted decision tree \texttt{PromptLeptonVeto}(PLIV), which is to identify non-prompt light leptons using lifetime information associated with a track jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}.
+Tight isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions based on a trained isolation boosted decision tree \texttt{PromptLeptonVeto}(PLIV), which is used to identify non-prompt light leptons using lifetime information associated with a track jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}.
 These additional reconstructed charged particle tracks inside the jet can be
-used to increase the precision for identifying the displaced decay vertex of heavy flavor (b, c) hadrons that produced non-prompt leptons.
+used to increase the accuracy for identifying the displaced decay vertex of heavy flavor (b, c) hadrons that produced non-prompt leptons.
 The tight working points are used for high $\pt$ lepton.

### 2022-03-10 sections/simulated_samples.tex
updates for more comments
add new limit plots
update most comments

--- 2022-02-22 sections/simulated_samples.tex
@@
 
-An overview of the MC generators used for the main signal and background samples is summarized in Table~\ref{mob}.
-
+An overview of the Monte Carlo (MC) generators used for the main signal and background samples is summarized in Table~\ref{mob}.
 Samples of simulated $\ttbar \to WbHq$ ($tt(qH)$) events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
@@
 Samples of $WH$ and $ZH$, collectively referred to as $VH$ are generated using {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
-and interfaced to {\pythia}~8.210 with the NNPDF2.3 LO PDF set and the A14 tune.
+and interfaced to {\pythia}~8.210 with the PDF4LHC15 PDF set and the AZNLO tune.
 The contribution of $tH$ associated production is also considered as part of SM Higgs background.
@@
 utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
-To model the effects of pile-up, events from minimum-bias interactions were generated using {\pythia}~8.186~\cite{Sjostrand:2007gs}  
-in combination with the A2 tune~\cite{ATL-PHYS-PUB-2011-014}, 
-and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
+%To model the effects of pile-up, events from minimum-bias interactions were generated using {\pythia}~8.186~\cite{Sjostrand:2007gs}  
+%in combination with the A3 tune~\cite{ATL-PHYS-PUB-2011-014}, 
+The effects of multiple interactions in the same and nearby bunch crossings (pile-up) were modelled by overlaying minimum-bias events, simulated using the soft QCD processes of {\pythia}~8.186~\cite{Sjostrand:2006za} with the A3~\cite{ATL-PHYS-PUB-2016-017} set of tuned parameters and NNPDF2.3 LO PDF set~\cite{Ball:2012cx}.
+%parton distribution functions (PDF).
+
+%and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
 The generated events were processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
@@
 efficiencies, energy scales and energy resolutions match those determined from data control samples.
+
+%  \begin{table}
+%  \footnotesize
+%  \centering
+%  \caption{Overview of the MC generators used for the main signal and background samples.}
+%  \begin{tabular}[h]{l|c|c|c|c|c|c}
+%  \hline \hline
+%  \multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
+%          &  ME   &  PS    &   ME  & PS &   &  \\\hline
+%  $tt(qH)$ Signal & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+%  $tH$ Signal & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+%  $W/Z$+jets & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline
+%  \ttbar & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+%  Single top & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+%  $t\bar{t}X$ & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+%  Diboson & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline\hline
+%  \end{tabular}
+%  \label{mob}
+%  \end{table}
 
@@
 $t\bar{t}X$ & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
+
+%$VH$ & {\powheg} & {\pythia}~8 & \multicolumn{2}{c|}{PDF4LHC15} & AZNLO & NLO \\ \hline
+$VH$ & {\powheg} & {\pythia}~8 & PDF4LHC15&CTEQ6L1 & AZNLO & NLO \\ \hline
+$tH$ & {\amcatnlolong} & {\pythia}~8 & \multicolumn{2}{c|}{CT10PDF} & A14 & NLO \\ \hline
+
 Diboson & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline\hline

### 2022-03-10 sections/strategy_Htautau.tex
update most comments

@@
 %some signal events mixed with production mode having only three reconstructed jets.
-In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs based on the number of light leptons,
+In order to optimise the sensitivity of the search, the selected events are categorised into seven signal regions(SRs) based on the number of light leptons,
 $\had$ candidates, and on the number of light flavored jets:
-$t_{\ell}\hadhad$, $t_{\ell}\had$-1j, $t_{\ell}\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}.
+%$t_{\ell}\hadhad$, $t_{\ell}\had$(1j and 2j), $t_{\ell}\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}. 
+$t_{\ell}\hadhad$, $t_{\ell}\had$ (1j and 2j), $t_h\lephad$ (2j and 3j), $t_h\hadhad$ (2j and 3j), as shown in Table~\ref{tab:srcr}.
 
@@
 decays as well as the Higgs decays into either $\lephad$ or $\hadhad$ final states.   
-The event kinematic reconstruction is used in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the
-di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.
+%The event kinematic reconstruction is used in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.
+The contribution of background to the signal regions $t_h\hadhad$ and $t_h\lephad$ channels is reduced by having a kinematic constraints on the di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.
 
@@
 
-For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a hard narrow jet from the
+For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a high $\pt$ jet from the
 decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
-There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
-is considered as the $q$-jet since the FCNC top decay products are likely boosted closer together than other jets. 
+%There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
+%is considered as the $q$-jet 
+Events should contain 4 jets, with the one at the smallest angular distance to the visible decay of the di-tau being labelled as the q-jet since the FCNC top decay products are likely boosted closer together than other jets.
 If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
 with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
-This kind of events will fall into $t_hH$ final state.
+These kinds of events will fall into $t_hH$ final state.
 %while the FCNC top resonance is
@@
 The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
-are estimated using a kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
+are estimated using a kinematic fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
 measured $\met$ within their expected resolutions.

### 2022-03-10 sections/systematic_uncertainties.tex
updating to V0.5
update most comments

@@
 Correlations of a given systematic uncertainty are maintained across processes and channels 
-as appropriate.
-The following sections describe the systematic uncertainties considered.
+as appropriate. The following sections describe the systematic uncertainties considered.
+Table~\ref{tab:had_sys_impact} shows a summary of the dominant systematics uncertainties on the measured $\BR(H\to qH)$ branching ratio
+resulting from the fits to the data in the signal regions as described in Section~\ref{sec:result}.
 
@@
 
-The uncertainty on the pileup reweighing is evaluated by varying the pileup scale factors
-by 1$\sigma$ based on the reweighing of the average interactions per bunch crossing. However, this
-uncertainty is highly correlated with the luminosity uncertainty and may be an overestimate.
+%The uncertainty on the pileup reweighing is evaluated by varying the pileup scale factors by 1$\sigma$ based on the reweighing of the average interactions per bunch crossing.
+However, this uncertainty is highly correlated with the luminosity uncertainty and may be an overestimate.
+Scale factors are applied to reweight simulated events in order to obtain the pile-up distribution corresponding to data.
+An uncertainty on these reweighting scale factors is considered based on the disagreement between the instantaneous luminosity in data and in simulation.
 

### 2022-03-10 sections/bdt_Htautau.tex
update tables and plots

@@
 \includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
-(b1) & (b2) & (b3) \\
+\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}\\
+(b1) & (b2) \\
 %(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
-(c1) \\
+\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}&
+\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}\\
+(c1) & (c2) \\
 %(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
 \end{tabular}
-\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit').
+\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2) before the fit to data ('Pre-Fit').
 The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.

### 2022-03-12 sections/bdt_Htautau.tex
update plots
addressing comments from draft 1

@@
 A large set of potential variables are investigated in each SR separately.
-The discrimination of a given variable is quantified by the "separation" (measures the degree of overlap between background and signal shape) and "importance" (depicts the power of the variable to the classification of the events) provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is larger than 2\% were kept.
-The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance}. The discriminating variables used are:
+The discrimination of a given variable is quantified by the "separation" (measures the degree of overlap between background and signal shape) and "importance" (depicts the power of the variable to the classification of the events) provided by the TMVA package~\cite{Hocker:2007ht}.
+The BDT discriminant is trained for each SR starting from a large list of variables. Then the variables are removed one at time and retraining until the receive operating characteristic (ROC)
+score drops more than 2\%.
+%The final variables used in SRs are shown in Table 5 with their ranking. 
+%and only those variables whose importance is larger than 2\% were kept.
+The final BDT input variables in each SR and their importances are listed in Table~\ref{tab:importance}. The discriminating variables used are:
 \begin{itemize}
@@
 \item ${\pt}^{\ell}$ is the transverse momentum of the leading light lepton.
-\item $\chi^2$ derived from the kinematic fit of the neutrino momentum.
+\item $\chi^2$ of the kinematic fit of the neutrino momentum.
 \item $m_{\text{bjj},\text{fit}}$ is the fitted invariant mass of the $b$-jet and the two jets from the $W$ boson decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
@@
 \item $m_{\text{bjj}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top quark mass.
-\item \text{min}($m_{\tau\tau \text{j}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\tau\tau\text{q}}$.
-\item \text{min}($m_{\text{jj}}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the $W$ candidate.
+\item \text{min}($m_{\tau\tau \text{j}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavour jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\tau\tau\text{q}}$.
+\item \text{min}($m_{\text{jj}}$) is the invariant mass of two light-flavour jets, minimized by choosing different jets, reflects the invariant mass of the $W$ candidate.
   %an alternative of $m_{\text{W}}$.
@@
 
-A comparison after fake calibration between data and the predicted background for the leading $\had$ $\pt$ distribution in the SRs 
+A comparison between data and the predicted background for the leading $\had$ $\pt$ distribution in the SRs, after applying fake factors, 
 %some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
@@
 \includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
-(a1) & (a2) & (a3) \\
+(a) & (b) & (c) \\
 %(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
@@
 \includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}\\
-(b1) & (b2) \\
+(d) & (e) \\
 %(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
@@
 \includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}\\
-(c1) & (c2) \\
+(f) & (g) \\
 %(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
 \end{tabular}
-\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2) before the fit to data ('Pre-Fit').
+\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a),  $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_h\thadhad$-2j (f), and $t_h\thadhad$-3j (g) before the fit to data ('Pre-Fit') after applying fake factors.
 The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow bins are included respectively in the last bin.
-Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic)
-channels. 
+Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channels.
+The $tuH$ signal shapes are also compared using a normalization factor(2-50).
 %( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 

### 2022-03-12 sections/data_presel.tex
addressing comments from draft 1

@@
 Only events recorded with a single-electron trigger, a single-muon trigger, or a di-tau trigger~\cite{TRIG-2018-05,TRIG-2018-01,id_trigger,l1topo_trigger} under stable beam conditions 
-and for which all detector subsystems were operational are considered for analysis.
-While the events recorded by di-lepton triggers fall into the control regions used for fake tau background estimation.
-The number of $pp$ interactions per bunch crossing in this dataset ranges from about 8 to 45, with an average of 24.
+and for which all detector subsystems were operational are considered for analysis. The events recorded by di-lepton triggers fall into the control regions are used for fake tau background
+estimation. The number of $pp$ interactions per bunch crossing in this dataset ranges from about 8 to 45, with an average of 24.
 
@@
 To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have a \pt of 1~GeV above the threshold. 
-
+The taus are required to have \pt 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
 %The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
@@
 \item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identification so that there is only
-  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the light lepton is required, including at least 2 jets with exactly one $b$-jet.
+  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the light lepton is required, including at least 2 jets with exactly one $b$-jet, to
+  reduce the SM backgrounds as well as orthogonal to other channels.
 \end{itemize}
@@
 Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} < 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} > 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ \\
-Jets  &  3, $\geq$ 4 jets & $\geq$1 jets & 2, $\geq$3 jets & 3, $\geq$4 jets \\
+Jets  &   $\geq$ 3 jets & $\geq$1 jets & $\geq$2 jets & $\geq$3 jets \\
 $b$-tagging & \multicolumn{3}{c|}{=1 $b$-jets} & =1 $b$-jets\\

### 2022-03-12 sections/simulated_samples.tex
addressing comments from draft 1

@@
 %-------------------------------------------------------------------------------
-\section{Simulated samples}
+\section{Simulated events}
 \label{sec:simulations}
@@
 The $tH$ signal events were generated by {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
-with the NNPDF3.0 NLO parton distribution function (PDF) set and interfaced to {\pythia} 8.212 with the NNPDF2.3 LO PDF set for the modelling of parton showering,
-hadronisation, and the underlying event with the A14 tune.
+with the NNPDF3.0 NLO parton distribution function (PDF) set. The parton showers, hadronisation, and underlying event were modelled by {\pythia}~8.212 with the NNPDF2.3 LO PDF set
+in combination with the A14 tune.
+%and interfaced to {\pythia} 8.212 with the NNPDF2.3 LO PDF set for the modelling of parton showering,
+%hadronisation, and the underlying event with the A14 tune.
 Depending on either up quark or charm quark involved in the FCNC production, the effective Lagrangian of $tqH$ interaction are parametrised using
@@
 and A14 tune. The MC predictions are normalised using the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.
+The contribution of triboson production is found to be small and negligible.
 

### 2022-03-12 sections/systematic_uncertainties.tex
addressing comments from draft 1

@@
 Uncertainties affecting the normalisation of the $V$+jets background are estimated separately for $V$+light-jets, $V$+$\geq$1$c$+jets,
-and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated to be approximately 30\% by comparing the
-data and total background prediction in the different analysis regions considered, but requiring exactly zero $b$-jet.
+and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated to be approximately 30\% by taking the maximum
+difference between the data and total background prediction in the different analysis regions considered, but requiring exactly zero, one, and two $b$-jets.
+This is mainly limited by the LO MC simulation in the $V$+jets high multiplicity regions.  
 %Agreement between data and predicted background 
@@
 
-The statistical uncertainties on the fake tau background calibration in the leptonic channel are applied with uncorrelated uncertainties for different fake tau sources and
-different $\pt$ slices. The uncertainty of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both,
-its statistical fluctuation and the differences between signal regions.
+The statistical uncertainties on the fake tau background calibration in the leptonic channel are applied with uncorrelated uncertainties for
+different fake tau sources and different $\pt$ slices. The uncertainties on the MC modelling of the various processes that used for
+evaluating the fake factors in the CRs are considered and treated fully correlated.
+The uncertainty of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both,
+its statistical fluctuation and the differences between the leptonic channels.
 The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.
+The uncertainties on the MC modelling of the various processes that used for
+evaluating the fake factors in the CRs are treated fully correlated in the fit.
 
@@
 
-Several normalisation and shape uncertainties are taken into account for the $\Hq$ and $pp\to tH$ signals.
+Several normalisation and shape uncertainties are taken into account and are treated fully correlated for the $\Hq$ and $pp\to tH$ signals.
 Uncertainties of the Higgs boson branching ratios are taken from the measured values in Ref.~\cite{Zyla:2020zbs}.
 %into account following the recommendation in Ref.~\cite{deFlorian:2016spz}.
-The uncertainty of ISR, FSR, scale and PDF are considered in all SRs. The parton shower uncertainties are estimated by comparing
+The uncertainty of ISR, FSR, scale and PDF are considered and are treated fully correlated in all SRs. The parton shower uncertainties are estimated by comparing
 the nominal to an alternative sample interfaced with {\herwig7}.

### 2022-03-12 ANA-TOPQ-2019-17-PAPER-metadata.tex
changed version to 0.6
update for V1.0 for circulation

@@
 \AtlasTitle{Search for flavour-changing neutral current interactions of the top quark and the Higgs
-boson in events with a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.10em} }
-
+boson in events with a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.10em}}
 % Draft version:
@@
 % Comment or remove in final version.
-\AtlasVersion{0.5}
+\AtlasVersion{1.1}
 % Abstract - % directly after { is important for correct indentation
@@
 % Comment deadline
-\AtlasCoverCommentsDeadline{1 March 2022}
+\AtlasCoverCommentsDeadline{9 March 2022}
 

### 2022-03-12 sections/background_estimation.tex

@@
 fit to data using several signal-depleted control regions as shown in Table~\ref{tab:srcr}.
-
+The events with one light lepton, two same-sign $\had$, and one $b$-jet, are also selected as a validation region (VR) for the background estimation in the leptonic channels. 
 %-------------------------------------------------------------------------------
@@
 %aimed at fake taus from different origins.
-There are four kinds of fake taus that need to be calibrated: Type-1 fake taus from hadronically-decaying W-bosons ($\tau_{W}$) %$W$-jets ($\tau_{W}$)
+There are four kinds of fake taus that need to be calibrated: Type-1 fake taus from hadronic $W$ boson decay ($\tau_{W}$) %$W$-jets ($\tau_{W}$)
 with opposite-sign (OS) of charge to the light lepton;
@@
 depending on four types, three $\pt$ bins, two bins for 1- and 3-prong taus separately.
-These scale factors are then used to correct the MC estimated fakes in the corresponding  signal regions with a single $b$-jet.
+The values of these scale factors range from 0.3-1.28 are then used to correct the MC estimated fakes in the corresponding  signal regions with a single $b$-jet.
 In the $t_{\ell}\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the same procedure used in the $\tlhad$ channel.
 %using the lepton and fake tau charges, then the scale factors are multiplied together.
-The nominal value of scale factors will vary according to their uncertainties in the final fit.
+The nominal value of scale factors will vary according to their uncertainties in the final fit. A closure test is made for the fake tau estimations using the same procedure
+in the $t_{\ell}\thadhad$-SS validation region, which shows a good agreement between data and the background prediction. 
 %In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
@@
 the ratio of the Data-MC ($\mathrm{real~tau}$) yields in which the tau candidate is passed or failed the medium tau ID selection
-in the $W$+jets control region.
+in the $W$+jets samples~\cite{ATLAS-CONF-2021-044}.
 %passing to failing the medium tau ID in the $W$+jets control region.
@@
 The contribution from these events is estimated with a data-driven method called ABCD.
-The estimate is based on the number of tight and loose light-leptons that passed and failed the PLIV cut in the low and high $\met$ regions. The number of
+The estimate is based on the number of tight and loose light-leptons that passed and failed the PLIV cut in the low ($<25~\gev$) and high
+($>25~\gev$) $\met$ regions. The number of
 fake light leptons in the signal region is evaluated by scaling the number of loose leptons in the high $\met$ region by the ratio of tight and loose leptons in the
 low $\met$ region. The contributions of prompt leptons and calibrated fake taus in the number of tight and loose leptons are subtracted using MC simulation.
-A closure test is made for the background estimations in the signal depleted low BDT regions. The data are in good agreement with the background prediction in the
-$t_{\ell}\had$ channels where the fake light leptons are important, while they are negligible in other leptonic channels.
+A closure test is made for the background estimations in the signal depleted low BDT ($<-0.6$) regions.
+The data are in good agreement with the background prediction in the
+$t_{\ell}\had$ channels where the fake light leptons are important, while negligible in other leptonic channels.

### 2022-03-12 sections/introduction.tex

@@
 The $H\rightarrow \tau\tau$ decay is detected in
-either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_{\ell}$). 
+either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$), but only in $\thadhad$ final state when the top decay leptonically ($t_{\ell}$) in order to avoid overlap with
+multilepton analysis~\cite{Aaboud:2018pob}. 
 Events with two hadronically decaying $\tau$-leptons without electron or muon are named hadronic channels.

### 2022-03-12 sections/objects.tex

@@
 These additional reconstructed charged particle tracks inside the jet can be
-used to increase the accuracy for identifying the displaced decay vertex of heavy flavor (b, c) hadrons that produced non-prompt leptons.
-The tight working points are used for high $\pt$ lepton.
+used to increase the accuracy for identifying the displaced decay vertex of heavy flavour (b, c) hadrons that produced non-prompt leptons.
+The tight working points are used for high $\pt$ lepton ($>20~\GeV$).
 The scale factors for the efficiencies of the tight \texttt{PLIV} working points are measured using the tag and probe method
@@
 Candidates are required to have either one or three associated tracks,
-with a total charge of $\pm 1$. Candidates are required to have \pt 5 GeV higher than the trigger threshold, and $|\eta|<2.5$,
-excluding the EM calorimeter's transition region.
+with a total charge of $\pm 1$.
+%Candidates are required to have \pt 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
 A Recurrent Neural Network (RNN)~\cite{Graves:2012SCI}

### 2022-03-12 sections/statistical_analysis.tex
add new limit plots

@@
 
-The final BDT discriminant distributions across all analysis regions considered are jointly analysed to test for the 
-presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
+The final discriminant distributions are the BDT outputs of all the considered analysis regions. They are jointly analysed to test for the 
+presence of a signal. The BDT distributions are binned to maximize the signal sensitivity.
+The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
 a product of Poisson probability terms over all bins considered in the search. This function depends

### 2022-03-12 sections/strategy_Htautau.tex

@@
 
-The analysis strategy adopted in the $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more search channels.
+The analysis strategy adopted in this FCNC $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more search channels.
 %\subsection{Event categorisation and kinematic reconstruction}
@@
 In order to optimise the sensitivity of the search, the selected events are categorised into seven signal regions(SRs) based on the number of light leptons,
-$\had$ candidates, and on the number of light flavored jets:
+$\had$ candidates, and on the number of light flavoured jets:
 %$t_{\ell}\hadhad$, $t_{\ell}\had$(1j and 2j), $t_{\ell}\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}. 
@@
 \centering
-\caption{Overview of the signal regions (SR) and the $t\bar{t}$ control regions (CRtt) used for fake tau scale factor derivation in leptonic channels.
+\caption{Overview of the signal regions (SR), validation region (VR), and the $t\bar{t}$ control regions (CRtt) used for fake tau scale factor derivation in leptonic channels.
 Leptons are required to have either same-sign (SS) or opposite-sign (OS) charges in each region.}
@@
 \hline \hline
-\multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
+\multicolumn{2}{c|}{Regions} & $b$-jet & light flavour jets        & lepton & hadronic taus & charge\\ \hline
 \multirow{7}{*}{SR}&$t_{\ell}\thadhad$     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
@@
 &$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
+VR &$t_{\ell}\thadhad$-SS     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ SS\\ \hline
 \multirow{6}{*}{CRtt}&$t_{\ell}t_{\ell}1b\tauhad$ & 1     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
@@
 %The event kinematic reconstruction is used in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.
-The contribution of background to the signal regions $t_h\hadhad$ and $t_h\lephad$ channels is reduced by having a kinematic constraints on the di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.
+The contribution of background to the signal regions of the $t_h\hadhad$ and $t_h\lephad$ channels is reduced by having a kinematic constraints on the di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.
 
@@
 The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
-are estimated using a kinematic fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
-measured $\met$ within their expected resolutions.
-The resolution on the Higgs boson mass is assumed to be $20~\gev$, while the resolution on the measured $\met$ is parameterised as a linear function of
+are estimated using a kinematic fit and collinear approximation for the tau decay products.
+The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
+measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is estimated to be $20~\gev$ from the MC simulation
+of the $tqH$ signals, while the resolution on the measured $\met$ is parameterised as a linear function of 
 $\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.

### 2022-03-12 sections/strategy_Htautau_oldversion.tex

@@
 \end{tabular}
-\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit').
+\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit'), but after applying the fake factors derived from the CRs to correct the fake tau background contribution.
 The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
-Overflow bins are included respectively in the last bin.
-Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic)
-channels. 
+Overflow bins are included respectively
+  in the last bin. Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channels. 
 %( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 

### 2022-03-12 sections/introduction.tex
update to CONF

@@
 %ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
-However, these branching ratios can as high as $\BR(t\to qH) \sim 10^{-5}$ which incorporate beyond the SM processes.
+However, these branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$ which incorporate beyond the SM processes.
 Examples of these include: quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{ Branco:2hdm2012} with or without flavour violation,
@@
 $pp \to tH$ production~\cite{Greljo:2014dka}. 
-%CMS recently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
-%their full Run 2 data and  set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $7.9\times10^{-4}(1.1\times10^{-3})$ and $\mathcal{B}(t\to Hc)$ of $9.4\times10^{-4}(8.6\times10^{-4})$~\cite{CMS:2021gfa}.
+CMS recently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
+their full Run 2 data and  set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $7.9\times10^{-4}(1.1\times10^{-3})$ and $\mathcal{B}(t\to Hc)$ of $9.4\times10^{-4}(8.6\times10^{-4})$~\cite{CMS:2021gfa}.
 %CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.

### 2022-03-13 sections/systematic_uncertainties.tex

@@
 
-The hdamp parameter (which controls the amount of radiation produced by the parton shower in
-POWHEG-BOX v2) is set to 1.5$m_t$ in the nominal case. Alternative samples are generated with hdamp=3$m_t$. The
-difference between two samples is treated as one of the systematics as ``$t\bar{t}$ hdamp''. 
+The $h_{\mathrm{damp}}$ parameter (which controls the amount of radiation produced by the parton shower in
+POWHEG-BOX v2) is set to 1.5$m_t$ in the nominal case. Alternative samples are generated with $h_{\mathrm{damp}}$=3$m_t$. The
+difference between two samples is treated as one of the systematics as ``$t\bar{t}$ $h_{\mathrm{damp}}$''. 
 %The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from

### 2022-03-13 sections/introduction.tex
minor update

@@
 has been conducted to explore this new particle. Measurements so far proved to be consistent with the Standard Model (SM) predictions. 
-However, the program is ongoing and precision measurements as well as searches for rare new physics processes beyond the Standar Model (BSM)
+However, the program is ongoing and precision measurements as well as searches for rare new physics processes beyond the Standard Model (BSM)
 are underway. One such possibility is flavour-changing neutral-current (FCNC) interactions between the Higgs boson, 

### 2022-03-14 sections/background_estimation.tex
adding Attilio's comments for CONF note

@@
 The data are in good agreement with the background prediction in the
-$t_{\ell}\had$ channels where the fake light leptons are important, while negligible in other leptonic channels.
+$t_{\ell}\had$ channels where the amount of fake light leptons is significant. However, this background is negligible in other leptonic channels.

### 2022-03-14 sections/introduction.tex
adding Attilio's comments for CONF note

@@
 %ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
-However, these branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$ which incorporate beyond the SM processes.
+However, these branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$ if considering beyond the SM processes.
 Examples of these include: quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{ Branco:2hdm2012} with or without flavour violation,
@@
 The study of $pp\rightarrow tH$ process will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
-The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at centre-of-mass energies of $\sqrt{s}= 13~\tev$ centre of mass energy~\cite{deFlorian:2016spz}.
+The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at centre-of-mass energy of $\sqrt{s}= 13~\tev$~\cite{deFlorian:2016spz}.
 
@@
 CMS recently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
-their full Run 2 data and  set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $7.9\times10^{-4}(1.1\times10^{-3})$ and $\mathcal{B}(t\to Hc)$ of $9.4\times10^{-4}(8.6\times10^{-4})$~\cite{CMS:2021gfa}.
+their full Run 2 data and  set observed(expected) upper limits on  $\BR(t\to cH)$ of $9.4\times10^{-4}(8.6\times10^{-4})$
+and $\BR{B}(t\to uH)$ of $7.9\times10^{-4}(1.1\times10^{-3})$~\cite{CMS:2021gfa}.
 %CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.
@@
 The dataset is divided into several final states depending on the production mode and
-the  $W$ decay. Top quark pair production events where the $W$ boson decays hadronically (leptonically) are referred to as $t_h$ ($t_{\ell}$). The contribution of 
+the  $W$ and tau decays. Top quark pair production events where the $W$ boson decays hadronically (leptonically) are referred to as $t_h$ ($t_{\ell}$).
+The decays $\tau \to \ell \nu_{\ell} \nu_{\tau}$ are referred as $\lep$, while the decays $\tau \to hadrons \nu_{\tau}$ are referred as $\thad$.
+The contribution of 
 $W\rightarrow\tau\nu$ is included as $\lep$ in $t_{\ell}$ when the $\tau$ decays into a light lepton (electron or muon) or as $\thad$ 

### 2022-03-14 sections/objects.tex
adding Attilio's comments for CONF note

@@
 in the tracker and in the calorimeter.
-A track-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$ and $E_R = \sum E^{\textrm{clst}}$, where
+A track- and cluster-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$ and $E_R = \sum E^{\textrm{clst}}$, where
 the scalar sum includes all tracks and energy deposits (excluding the lepton candidate itself) within the cone defined by $\Delta R<0.2 (0.3)$ around the %axis

### 2022-03-16 sections/systematic_uncertainties.tex

@@
 The statistical uncertainties on the fake tau background calibration in the leptonic channel are applied with uncorrelated uncertainties for
-different fake tau sources and different $\pt$ slices. The uncertainties on the MC modelling of the various processes that used for
-evaluating the fake factors in the CRs are considered and treated fully correlated.
+different fake tau sources and different $\pt$ slices. The uncertainties on the MC modelling of the various processes used for
+evaluation of the fake factors in the CRtt's are considered and treated as fully correlated in the fit.
 The uncertainty of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both,
 its statistical fluctuation and the differences between the leptonic channels.
-The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.
-The uncertainties on the MC modelling of the various processes that used for
-evaluating the fake factors in the CRs are treated fully correlated in the fit.
+The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factorsderived from different signal depleted CRs.
+%The uncertainties on the MC modelling of the various processes used for
+%evaluation of the fake factors in the CRtt's are treated as fully correlated in the fit.
 
@@
 
-Several normalisation and shape uncertainties are taken into account and are treated fully correlated for the $\Hq$ and $pp\to tH$ signals.
+Several normalisation and shape uncertainties are taken into account and are treated as fully correlated for the $\Hq$ and $pp\to tH$ signals.
 Uncertainties of the Higgs boson branching ratios are taken from the measured values in Ref.~\cite{Zyla:2020zbs}.

### 2022-03-18 sections/background_estimation.tex
update Luca's comments

--- 2022-03-12 sections/background_estimation.tex
@@
 fit to data using several signal-depleted control regions as shown in Table~\ref{tab:srcr}.
-The events with one light lepton, two same-sign $\had$, and one $b$-jet, are also selected as a validation region (VR) for the background estimation in the leptonic channels. 
+The events with one light lepton, two same-sign $\had$, and one $b$-jet, are also selected, enter in a validation region (VR) for the background estimation in the leptonic channels. 
 %-------------------------------------------------------------------------------
@@
 The templates are produced by subtracting all MC background contributions with real subleading taus from data.
-The FFs are computed as
-the ratio of the Data-MC ($\mathrm{real~tau}$) yields in which the tau candidate is passed or failed the medium tau ID selection
-in the $W$+jets samples~\cite{ATLAS-CONF-2021-044}.
+The FFs are computed as the ratio of misidentified $\thad$ candidate that either pass or fail the medium tau ID selection in the
+$W$+jets processes~\cite{ATLAS-CONF-2021-044}. 
+%the Data-MC ($\mathrm{real~tau}$) ratio of the yields of events in which the tau candidate is passing or failing the medium tau ID selection
+%in the $W$+jets samples~\cite{ATLAS-CONF-2021-044}.
 %passing to failing the medium tau ID in the $W$+jets control region.
@@
 low $\met$ region. The contributions of prompt leptons and calibrated fake taus in the number of tight and loose leptons are subtracted using MC simulation.
-A closure test is made for the background estimations in the signal depleted low BDT ($<-0.6$) regions.
+A closure test is made for the background estimations in the signal depleted low BDT ($<-0.6$) regions, defined in Section~\ref{sec:tmva}.
 The data are in good agreement with the background prediction in the
-$t_{\ell}\had$ channels where the fake light leptons are important, while negligible in other leptonic channels.
+$t_{\ell}\had$ channels, while the fake light leptons are negligible in other leptonic channels.

### 2022-03-18 sections/bdt_Htautau.tex
update Luca's comments

@@
 \begin{table*}[t!]
-  \caption{\small{The number of discriminating variables (n) used in the training of BDT in each SR. 
-The rank of the discriminating variables relative to one another according to their importance in the training is reported from highest (1) to 
+  \caption{\small{Discriminating variables (n) used in the training of the BDT of each SR. 
+The ranking of the input variables according to their importance in the training is reported from highest (1) to 
 lowest (n). Variables whose ranking is missing are not included in the training of the corresponding SR. The description of each variable is provided in the text.}}
@@
 The discrimination of a given variable is quantified by the "separation" (measures the degree of overlap between background and signal shape) and "importance" (depicts the power of the variable to the classification of the events) provided by the TMVA package~\cite{Hocker:2007ht}.
-The BDT discriminant is trained for each SR starting from a large list of variables. Then the variables are removed one at time and retraining until the receive operating characteristic (ROC)
-score drops more than 2\%.
+The BDT discriminant is trained for each SR starting from a large list of variables. Then the variables are removed one at time and the BDT is retrained until the
+receive operating characteristic (ROC) score drops more than 2\%.
 %The final variables used in SRs are shown in Table 5 with their ranking. 
 %and only those variables whose importance is larger than 2\% were kept.
-The final BDT input variables in each SR and their importances are listed in Table~\ref{tab:importance}. The discriminating variables used are:
+The final BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance}. The discriminating variables used are:
 \begin{itemize}
@@
 \item ${\pt}^{\ell}$ is the transverse momentum of the leading light lepton.
-\item $\chi^2$ of the kinematic fit of the neutrino momentum.
+\item $\chi^2$ of the kinematic fit of the invisible decay products of the tau leptons.
 \item $m_{\text{bjj},\text{fit}}$ is the fitted invariant mass of the $b$-jet and the two jets from the $W$ boson decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
@@
 \end{tabular}
-\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a),  $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_h\thadhad$-2j (f), and $t_h\thadhad$-3j (g) before the fit to data ('Pre-Fit') after applying fake factors.
-The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
-Overflow bins are included respectively in the last bin.
-Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channels.
-The $tuH$ signal shapes are also compared using a normalization factor(2-50).
+\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data ('Pre-Fit') showing 
+  the expected background and $tuH$ signals after applying fake factors in the following SRs: $t_{\ell}\thadhad$ (a),
+  $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_h\thadhad$-2j (f), and $t_h\thadhad$-3j (g).
+ The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
+ %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
+ Overflow events are included in the last bin.
+``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel.
+The $tuH$ signal is scaled using a normalization factor of 2 to 50.
 %( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
-The lower panels show the ratios of the data to the background prediction.}
+The lower panels show the data to prediction ratio.}
 \label{fig:taupt_prefit}
 \end{figure}
+
+% \begin{figure}[H]
+% \centering
+% \includegraphics[width=0.31\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf}
+% \includegraphics[width=0.31\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}
+% \includegraphics[width=0.31\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
+% (a1)  (a2)  (a3) \\
+% \includegraphics[width=0.31\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}
+% \includegraphics[width=0.31\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf} \\ 
+% (a1)  (a2)  (a3) \\
+% \includegraphics[width=0.31\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}
+% \includegraphics[width=0.31\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf} \\ 
+% (a1)  (a2)  (a3) \\
+% \caption{ The BDT output distributions for the background and TT signal (a1, b1), background and ST signal (a2, b2), background and different types of signals (c1,c2) and % ROC curves (a3, b3) in the $t_h\thadhad$-2j (a1-3,c1), $t_h\thadhad$-3j (b1-3,c2) regions of leptonic channel.
+Only statistical uncertainties are being shown.
+Underflow % and overflow bins are included respectively in the first and last bins.
+The real tau contributions shown from various MC samples.}% The Kolmogorov Test values for the % training and testing BDT distributions are also indicated.
+% \label{fig:overtrain_hadhad}
+% \end{figure}
 

### 2022-03-18 sections/conclusion.tex
adding Attilio's comments for CONF note
update Luca's comments

@@
 A search for flavour-changing neutral current processes involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented.
-FCNC $tqH$ interaction is searched for both in $t\bar{t}$ decay mode, where one top quark decays according to the SM processes and the other one decays through $t\rightarrow Hq$, and in production mode ($pp\rightarrow tH$) with a single top quark produced via FCNC interaction where $t\to Wb$.
+FCNC $tqH$ interaction is searched for both in the $t\bar{t}$ decay mode, where one top quark decays according to the SM processes and the other one decays through $t\rightarrow Hq$, and in the production mode ($pp\rightarrow tH$) with a single top quark produced via FCNC interaction where $t\to Wb$.
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
-The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$), a $b$-jet as well as multiple jets.
+The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton (e,$\mu$), a $b$-jet as well as multiple jets.
 Multivariate techniques based on BDT are used to distinguish the signal from the background on the basis of their different kinematics.
@@
 the effective $tqH$ couplings for a new physics scale $\Lambda$ of 1~TeV are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.
-These results improve significantly upon previous ATLAS and CMS limits on the $t\rightarrow Hq$ branching ratios.
+%These results improve significantly upon previous ATLAS and CMS limits on the $t\rightarrow Hq$ branching ratios.
+These results improve significantly previously published ATLAS studies in this channel and provide more stringent limit than the ATLAS  $t\rightarrow Hq$ combination~\cite{fcnc36}.

### 2022-03-18 sections/data_presel.tex
adding Attilio's comments for CONF note
update Luca's comments

@@
 To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have a \pt of 1~GeV above the threshold. 
-The taus are required to have \pt 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
+The reconstructed taus are required to have a \pt of 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
 %The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
@@
 Further requirements are defined targeting different signal decay modes:
-The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers.
+The events in the leptonic channel are recorded by a single-electron or single-muon trigger, required to have exactly one electron or muon that matches, within $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers.
 Further requirements are defined targeting different signal decay modes:
 \begin{itemize}
-\item $t_h\lephad$: Targeting into the $t_hH$ and $t_ht(qH)$ final states with $H\to\lephad$ decay.
+\item $t_h\lephad$: Targeting into the $t_hH$ and $t_ht(qH)$ final states with a $H\to\lephad$ decay.
 Exactly one $\had$ with opposite-side charge to $\lep$ is required, including at least three jets with exactly one $b$-jet.
-\item $t_{\ell}\hadhad$: Targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with $H\to\hadhad$ decay.
-Exactly one light lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-jet.
-\item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identification so that there is only
-  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the light lepton is required, including at least 2 jets with exactly one $b$-jet, to
-  reduce the SM backgrounds as well as orthogonal to other channels.
+\item $t_{\ell}\hadhad$: Targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay.
+Exactly one light lepton and two opposite-sign $\had$ are selected, including at least one jet with exactly one $b$-jet.
+\item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay where one $\had$ fails the tau reconstruction or identification so that there is only one reconstructed $\had$ candidate.
+  To reduce the SM backgrounds and avoid overlaps with the other selections, exactly one $\had$ with same-sign charge to the light lepton is required.
+  In addition, at least two jets including exactly one $b$-jet are required.
 \end{itemize}
 
-The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and subleading $\had$ passed the trigger.
-Further requirements are defined targeting signal decay modes:
+The events in the hadronic channel are selected by s di-tau trigger. Further requirements are:
+%recorded by di-tau trigger, required to have both leading and subleading $\had$ passed the trigger. Further requirements are defined targeting signal decay modes:
 \begin{itemize}
-\item $t_h\hadhad$: Targeting into the $t_hH$ and $t_ht(qH)$ final states with $H\to\hadhad$ decay.
-Exactly two $\had$ with opposite-sign charge are selected, including at least 3 jet with exactly one $b$-jet.
+\item $t_h\hadhad$: Targeting the $t_hH$ and $t_ht(qH)$ final states with $H\to\hadhad$ decay.
+Exactly two $\had$ with opposite-sign charge and at least three jets, including exactly one $b$-jet, are required.
+  %are selected, including at least 3 jet with exactly one $b$-jet.
 \end{itemize}

### 2022-03-18 sections/introduction.tex
update Luca's comments

@@
 %ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
-However, these branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$ if considering beyond the SM processes.
-Examples of these include: quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{ Branco:2hdm2012} with or without flavour violation,
+However, these branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$ when considering beyond the SM processes.
+Examples of these processes include: quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{ Branco:2hdm2012} with or without flavour violation,
  %of type I, with explicit flavour conservation,
@@
 The study of $pp\rightarrow tH$ process will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
-The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at centre-of-mass energy of $\sqrt{s}= 13~\tev$~\cite{deFlorian:2016spz}.
+The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at a centre-of-mass energy of $\sqrt{s}= 13~\tev$~\cite{deFlorian:2016spz}.
 
@@
 CMS recently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
-their full Run 2 data and  set observed(expected) upper limits on  $\BR(t\to cH)$ of $9.4\times10^{-4}(8.6\times10^{-4})$
-and $\BR{B}(t\to uH)$ of $7.9\times10^{-4}(1.1\times10^{-3})$~\cite{CMS:2021gfa}.
+the full Run 2 data. The observed (expected) upper limits on  $\BR(t\to cH)$ are $9.4\times10^{-4}(8.6\times10^{-4})$
+and are $7.9\times10^{-4}(1.1\times10^{-3})$ for $\BR{B}(t\to uH)$~\cite{CMS:2021gfa}.
 %CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.
@@
 \caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$ obtained from ATLAS and CMS Collaborations with Run 2 data.
-Each limit is obtained assuming the other branching ratio is 0}}
+Each limit is obtained assuming the other branching ratio is null.}}
 \begin{center}
@@
 The $H\rightarrow \tau\tau$ decay is detected in
-either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$), but only in $\thadhad$ final state when the top decay leptonically ($t_{\ell}$) in order to avoid overlap with
-multilepton analysis~\cite{Aaboud:2018pob}. 
+either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$), but only the $\thadhad$ final state is considered
+when the top decay leptonically ($t_{\ell}$) in order to avoid overlaps with
+other ATLAS searches~\cite{Aaboud:2018pob}. 
 Events with two hadronically decaying $\tau$-leptons without electron or muon are named hadronic channels.
-Events with at least one \tauhad with an additional electron or muon are named leptonic channels.
+Events with at least one \tauhad with an additional electron or muon (corresponding to $t_{\ell}$ or $\lep$ events) are named leptonic channels.
 More signal regions (with top quark decay leptonically) are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data~\cite{fcnc36}.
 In addition, an improved treatment of misidentified $\tau$-leptons in simulation and data-driven
-fake estimations from multi-jet background are implemented.
+fake estimations from multi-jet background is implemented.
 % and more

### 2022-03-18 sections/simulated_samples.tex
adding Attilio's comments for CONF note
update Luca's comments

@@
 The $tH$ signal events were generated by {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
-with the NNPDF3.0 NLO parton distribution function (PDF) set. The parton showers, hadronisation, and underlying event were modelled by {\pythia}~8.212 with the NNPDF2.3 LO PDF set
+with the NNPDF3.0 NLO parton distribution function (PDF) set. The parton showers, hadronisation, and underlying event are modelled by {\pythia}~8.212 with the NNPDF2.3 LO PDF set
 in combination with the A14 tune.
@@
 and A14 tune. The MC predictions are normalised using the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.
-The contribution of triboson production is found to be small and negligible.
+The contribution of triboson production is found to be negligible.
 
@@
 \centering
-\caption{Overview of the MC generators at which the matrix-element calculation (ME) at the leading or the next-leading order (Order), 
-the parton shower model (PS), and the parton distribution function set (PDF) used for the main signal and background samples.}
+\caption{Overview of the MC generators used for the main signal and background samples. including the matrix element (ME),
+  %at the leading or the next-leading order (Order), 
+parton shower (PS), parton distribution function set (PDF), and cross-section calculation order (Order).}%  used for the main signal and background samples.}
 \begin{tabular}[h]{l|c|c|c|c|c|c}

### 2022-03-18 sections/strategy_Htautau.tex
update Luca's comments

@@
 \centering
-\caption{Overview of the signal regions (SR), validation region (VR), and the $t\bar{t}$ control regions (CRtt) used for fake tau scale factor derivation in leptonic channels.
-Leptons are required to have either same-sign (SS) or opposite-sign (OS) charges in each region.}
+\caption{Overview of the signal regions (SR), validation region (VR), and $t\bar{t}$ control regions (CRtt) used for the fake tau scale factor derivation in the leptonic channels.
+Leptons are required to have either same-sign (SS) or opposite-sign (OS) in each region.}
 \label{tab:srcr}
@@
 %is considered as the $q$-jet 
-Events should contain 4 jets, with the one at the smallest angular distance to the visible decay of the di-tau being labelled as the q-jet since the FCNC top decay products are likely boosted closer together than other jets.
+Events should contain 4 jets, with the one having the smallest angular separation with respect to the visible di-tau system being labelled as  q-jet since the FCNC top decay products are likely boosted closer together.
 If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
 with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
-These kinds of events will fall into $t_hH$ final state.
+These kinds of events will fall into the $t_hH$ final state.
 %while the FCNC top resonance is
@@
 The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
-are estimated using a kinematic fit and collinear approximation for the tau decay products.
+are estimated using a kinematic fit and assuming a collinear approximation for the tau decay products.
 The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
-measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is estimated to be $20~\gev$ from the MC simulation
-of the $tqH$ signals, while the resolution on the measured $\met$ is parameterised as a linear function of 
+measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is estimated to be $20~\gev$ from a fit of the mass
+distribution of the simulated  $tqH$ signal events, while the resolution on the measured $\met$ is parameterised as a linear function of 
 $\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.

### 2022-03-18 sections/systematic_uncertainties.tex
update Luca's comments

@@
 as appropriate. The following sections describe the systematic uncertainties considered.
-Table~\ref{tab:had_sys_impact} shows a summary of the dominant systematics uncertainties on the measured $\BR(H\to qH)$ branching ratio
+Table~\ref{tab:had_sys_impact} shows a summary of the dominant systematics uncertainties on the measured $\BR(t\to qH)$ branching ratio
 resulting from the fits to the data in the signal regions as described in Section~\ref{sec:result}.
@@
 These systematic uncertainties are taken as uncorrelated between $b$-jets, $c$-jets, and light-jets.
-
 %The uncertainty on the pileup reweighing is evaluated by varying the pileup scale factors by 1$\sigma$ based on the reweighing of the average interactions per bunch crossing.
@@
 Scale factors are applied to reweight simulated events in order to obtain the pile-up distribution corresponding to data.
-An uncertainty on these reweighting scale factors is considered based on the disagreement between the instantaneous luminosity in data and in simulation.
+An uncertainty on these reweighting scale factors is estimated by varying the reweighting to the profile in data within its uncertainties.
+%considered based on the disagreement between the instantaneous luminosity in data and in simulation.
 
@@
 difference between the data and total background prediction in the different analysis regions considered, but requiring exactly zero, one, and two $b$-jets.
-This is mainly limited by the LO MC simulation in the $V$+jets high multiplicity regions.  
+This is mainly driven by the disagreement between MC simulation in the $V$+jets regions with high multiplicity of jets.  
 %Agreement between data and predicted background 

### 2022-03-18 sections/bdt_Htautau.tex
update tqH

@@
 \end{tabular}
-\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data ('Pre-Fit') showing 
+\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (``Pre-Fit'') showing 
   the expected background and $tuH$ signals after applying fake factors in the following SRs: $t_{\ell}\thadhad$ (a),

### 2022-03-18 sections/introduction.tex
minor typo fixes

@@
 CMS recently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
-the full Run 2 data. The observed (expected) upper limits on  $\BR(t\to cH)$ are $9.4\times10^{-4}(8.6\times10^{-4})$
+the full Run 2 dataset. The observed (expected) upper limits on  $\BR(t\to cH)$ are $9.4\times10^{-4}(8.6\times10^{-4})$
 and are $7.9\times10^{-4}(1.1\times10^{-3})$ for $\BR{B}(t\to uH)$~\cite{CMS:2021gfa}.
@@
 the  $W$ and tau decays. Top quark pair production events where the $W$ boson decays hadronically (leptonically) are referred to as $t_h$ ($t_{\ell}$).
-The decays $\tau \to \ell \nu_{\ell} \nu_{\tau}$ are referred as $\lep$, while the decays $\tau \to hadrons \nu_{\tau}$ are referred as $\thad$.
+The decays $\tau \to \ell \nu_{\ell} \nu_{\tau}$ are referred as $\lep$, while the decays $\tau \to \text{hadrons} + \nu_{\tau}$ are referred as $\thad$.
 The contribution of 

### 2022-03-18 sections/systematic_uncertainties.tex
update tqH
minor typo fixes

@@
 its statistical fluctuation and the differences between the leptonic channels.
-The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factorsderived from different signal depleted CRs.
+The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.
 %The uncertainties on the MC modelling of the various processes used for

### 2022-03-18 sections/conclusion.tex
minor typo fixes

@@
 A search for flavour-changing neutral current processes involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented.
-FCNC $tqH$ interaction is searched for both in the $t\bar{t}$ decay mode, where one top quark decays according to the SM processes and the other one decays through $t\rightarrow Hq$, and in the production mode ($pp\rightarrow tH$) with a single top quark produced via FCNC interaction where $t\to Wb$.
+FCNC $tqH$ interaction is searched for both in the $t\bar{t}$ decay mode, where one top quark decays according to the SM processes and the other one decays through $t\rightarrow qH$, and in the production mode ($pp\rightarrow tH$) with a single top quark produced via FCNC interaction where $t\to Wb$.
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
@@
 A slight excess of data is observed above background with a significance of 2.3$\sigma$.  
-95\% CL upper limits are set on the $t\to Hq$ branching ratios and the corresponding
+95\% CL upper limits are set on the $t\to qH$ branching ratios and the corresponding
 dimension-6 operator Wilson coefficients in the effective $tqH$ couplings. 
@@
 %These results improve significantly upon previous ATLAS and CMS limits on the $t\rightarrow Hq$ branching ratios.
-These results improve significantly previously published ATLAS studies in this channel and provide more stringent limit than the ATLAS  $t\rightarrow Hq$ combination~\cite{fcnc36}.
+These results improve significantly previously published ATLAS studies in this channel and provide more stringent limit than the ATLAS  $t\rightarrow qH$ combination~\cite{fcnc36}.

### 2022-03-20 sections/simulated_samples.tex
for pubdata

@@
 
-%  \begin{table}
-%  \footnotesize
-%  \centering
-%  \caption{Overview of the MC generators used for the main signal and background samples.}
-%  \begin{tabular}[h]{l|c|c|c|c|c|c}
-%  \hline \hline
-%  \multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
-%          &  ME   &  PS    &   ME  & PS &   &  \\\hline
-%  $tt(qH)$ Signal & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-%  $tH$ Signal & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-%  $W/Z$+jets & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline
-%  \ttbar & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-%  Single top & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-%  $t\bar{t}X$ & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-%  Diboson & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline\hline
-%  \end{tabular}
-%  \label{mob}
-%  \end{table}
-
 \begin{table}
@@
 \centering
-\caption{Overview of the MC generators used for the main signal and background samples. including the matrix element (ME),
-  %at the leading or the next-leading order (Order), 
-parton shower (PS), parton distribution function set (PDF), and cross-section calculation order (Order).}%  used for the main signal and background samples.}
+\caption{Overview of the MC generators used for the main signal and background samples.
+including the matrix element (ME), parton shower (PS), parton distribution function set (PDF), and cross-section calculation order (Order).}
 \begin{tabular}[h]{l|c|c|c|c|c|c}
@@
 $t\bar{t}X$ & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-
-%$VH$ & {\powheg} & {\pythia}~8 & \multicolumn{2}{c|}{PDF4LHC15} & AZNLO & NLO \\ \hline
 $VH$ & {\powheg} & {\pythia}~8 & PDF4LHC15&CTEQ6L1 & AZNLO & NLO \\ \hline
 $tH$ & {\amcatnlolong} & {\pythia}~8 & \multicolumn{2}{c|}{CT10PDF} & A14 & NLO \\ \hline
-
 Diboson & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline\hline

### 2022-03-20 sections/background_estimation.tex

@@
 The templates are produced by subtracting all MC background contributions with real subleading taus from data.
-The FFs are computed as the ratio of misidentified $\thad$ candidate that either pass or fail the medium tau ID selection in the
+The FFs are computed as the ratio of misidentified $\thad$ candidates that either pass or fail the medium tau ID selection in regions enriched in events originating from 
 $W$+jets processes~\cite{ATLAS-CONF-2021-044}. 

### 2022-03-20 sections/bdt_Htautau.tex

@@
 The discrimination of a given variable is quantified by the "separation" (measures the degree of overlap between background and signal shape) and "importance" (depicts the power of the variable to the classification of the events) provided by the TMVA package~\cite{Hocker:2007ht}.
-The BDT discriminant is trained for each SR starting from a large list of variables. Then the variables are removed one at time and the BDT is retrained until the
+The BDT discriminant is trained for each SR starting from a large list of variables. Then the least important variable is removed one at a time and the BDT is retrained until the
 receive operating characteristic (ROC) score drops more than 2\%.
@@
 \item ${\pt}^{\ell}$ is the transverse momentum of the leading light lepton.
-\item $\chi^2$ of the kinematic fit of the invisible decay products of the tau leptons.
+\item $\chi^2$ of the kinematic fit of the momentum of the invisible decay products of the tau leptons.
 \item $m_{\text{bjj},\text{fit}}$ is the fitted invariant mass of the $b$-jet and the two jets from the $W$ boson decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.

### 2022-03-20 sections/introduction.tex

@@
 \begin{table}[t!]
-\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$ obtained from ATLAS and CMS Collaborations with Run 2 data.
+\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to cH)$ and $\BR(t \to uH)$ obtained from ATLAS and CMS Collaborations with Run 2 data.
 Each limit is obtained assuming the other branching ratio is null.}}
@@
 & &\multirow{2}{*}{$\mathcal{L}$ [fb$^{-1}$]} & \multicolumn{2}{c}{95\% CL observed upper limits}  \\
-& & 										    & \multicolumn{1}{c}{on $\BR(t \to Hc)$}            & \multicolumn{1}{c}{on $\BR(t \to Hu)$} \\
+& & 										    & \multicolumn{1}{c}{on $\BR(t \to cH)$}            & \multicolumn{1}{c}{on $\BR(t \to uH)$} \\
 \midrule

### 2022-03-20 sections/strategy_Htautau.tex

@@
 %is considered as the $q$-jet 
-Events should contain 4 jets, with the one having the smallest angular separation with respect to the visible di-tau system being labelled as  q-jet since the FCNC top decay products are likely boosted closer together.
+Events should contain 4 jets, with the one having the smallest angular separation with respect to the visible di-tau system being labelled as  $q$-jet since the FCNC top decay products are likely boosted closer together.
 If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination

### 2022-03-21 sections/background_estimation.tex
update figure 1 with log-scale

@@
 fit to data using several signal-depleted control regions as shown in Table~\ref{tab:srcr}.
-The events with one light lepton, two same-sign $\had$, and one $b$-jet, are also selected, enter in a validation region (VR) for the background estimation in the leptonic channels. 
+The events with one light lepton, two same-sign $\had$, and one $b$-jet, are also selected, providing a validation region (VR) for the background estimation in the leptonic channels. 
 %-------------------------------------------------------------------------------

### 2022-03-21 sections/bdt_Htautau.tex
update figure 1 with log-scale

@@
 %\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
+\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_os_log_.pdf} &
+\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b1j_ss_log_.pdf}&
+\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_ss_log_.pdf}\\
 (a) & (b) & (c) \\
 %(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}\\
+\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_os_log_.pdf}&
+\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b3j_os_log_.pdf}\\
 (d) & (e) \\
 %(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}\\
+\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b2jos_log_.pdf}&
+\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jos_log_.pdf}\\
 (f) & (g) \\

### 2022-03-22 sections/background_estimation.tex
answer comments

@@
 Backgrounds with non-prompt light leptons (electron or muon), with photons or jets misidentified as electrons, or with jets misidentified as tau candidates, 
-generically referred to as \texttt{fake} leptons, are estimated using data-driven methods. 
+generically referred to as fake leptons, are estimated using data-driven methods. 
+%\texttt{fake} 
 The background prediction is further improved during the statistical analysis by performing a likelihood 

### 2022-03-22 sections/strategy_Htautau.tex
answer comments

@@
 %The event kinematic reconstruction is used in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.
-The contribution of background to the signal regions of the $t_h\hadhad$ and $t_h\lephad$ channels is reduced by having a kinematic constraints on the di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.
+The contribution of background to the signal regions of the $t_h\hadhad$ and $t_h\lephad$ channels is reduced by having a kinematic constraints on the di-tau mass and the $\met$ in the event~\cite{Chen:2015nta}.
 
@@
 If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
-with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
+with the invariant mass closest to the $W$ boson mass. There is the possibility that one of the jets fails the $\pt$ requirement and is not reconstructed.
 These kinds of events will fall into the $t_hH$ final state.

### 2022-04-12 sections/bdt_Htautau.tex
change legend to ell
update BR label and CONF pub data
updatesn new plots and add CR plots

@@
 
-A comparison between data and the predicted background for the leading $\had$ $\pt$ distribution in the SRs, after applying fake factors, 
+A comparison between data and the predicted background for the leading $\had$ $\pt$  and visible di-tau mass distribution in the SRs, after applying fake factors, 
 %some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
-is shown in Figure~\ref{fig:taupt_prefit}.
+is shown in Figure~\ref{fig:taupt_prefit} and Figure~\ref{fig:mtt}, respectively.
 %each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_{\ell}hadhad}.
@@
 \includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_os_log_.pdf}&
-\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b3j_os_log_.pdf}\\
-(d) & (e) \\
+\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b3j_os_log_.pdf} &
+\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_ss_log_.pdf} \\
+(d) & (e) & (f)\\
 %(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
 \includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b2jos_log_.pdf}&
-\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jos_log_.pdf}\\
-(f) & (g) \\
+\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jos_log_.pdf}&
+\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jss_log_.pdf}\\
+(g) & (h) & (i)\\
 %(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
@@
   the expected background and $tuH$ signals after applying fake factors in the following SRs: $t_{\ell}\thadhad$ (a),
-  $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_h\thadhad$-2j (f), and $t_h\thadhad$-3j (g).
+ $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$ same sign CR (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j same sign CR (i).
  The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
@@
 
+\begin{figure}[H]
+\centering
+\begin{tabular}{@{}ccc@{}}
+%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
+%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
+%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
+\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_os_log_mtt.pdf} &
+\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg1l1tau1b1j_ss_log_mtt.pdf}&
+\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_ss_log_mtt.pdf}\\
+(a) & (b) & (c) \\
+%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
+\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_os_log_mtt.pdf}&
+\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg1l1tau1b3j_os_log_mtt.pdf}&
+\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_ss_log_mtt.pdf}\\
+(d) & (e) & (f)\\
+%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
+\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg2mtau1b2jos_log_mtt.pdf}&
+\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg2mtau1b3jos_log_mtt.pdf}&
+\includegraphics[page=1,width=0.29\textwidth]{figures/mtt/tuH_reg2mtau1b3jss_log_mtt.pdf}\\
+(g) & (h) & (i)\\
+%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
+\end{tabular}
+\caption{Visible di-tau mass  distributions obtained before the fit to data (``Pre-Fit'') showing 
+  the expected background and $tuH$ signals after applying fake factors in the following SRs: $t_{\ell}\thadhad$ (a),
+ $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$ same sign CR (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j same sign CR (i).
+ The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
+ %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
+ Overflow events are included in the last bin.
+``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel.
+The $tuH$ signal is scaled using a normalization factor of 2 to 50.
+%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
+The lower panels show the data to prediction ratio.}
+\label{fig:mtt}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\begin{tabular}{@{}ccc@{}}
+\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b2j_os_log_ttCR.pdf} &
+\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b2j_ss_log_ttCR.pdf}&
+\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b3j_os_log_ttCR.pdf}\\
+(a) & (b) & (c) \\
+\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b3j_ss_log_ttCR.pdf}&
+\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg2l1tau1bnj_log_ttCR.pdf}&
+\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg2l1tau2bnj_log_ttCR.pdf}\\
+(d) & (e) & (f)\\
+%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
+\end{tabular}
+\caption{Leading $\thad$ $\pt$  distributions obtained the fake $\thad$ calibration method after applying fake factors in the following CRs: 
+$t_{\ell}t_{h}$2b$\thad$-2j OS (a), $t_{\ell}t_{h}$2b$\thad$-2j SS (b), $t_{\ell}t_{h}$2b$\thad$-3j OS (c), $t_{\ell}t_{h}$2b$\thad$-3j SS (d), $t_{\ell}t_{\ell}$1b$\thad$-nj (e) and $t_{\ell}t_{\ell}$2b$\thad$-nj (f).
+ The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
+ %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
+ Overflow events are included in the last bin. 
+%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
+The lower panels show the data to prediction ratio.}
+\label{fig:ttCR_mtt}
+\end{figure}
+
 % %\input{\FCNCFigures/tex/BDT}

### 2022-04-16 sections/bdt_Htautau.tex
update to V1.3

--- 2022-03-20 sections/bdt_Htautau.tex
@@
 %and only those variables whose importance is larger than 2\% were kept.
-The final BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance}. The discriminating variables used are:
+The final BDT input variables in each SR and their importance ranking are listed in Table~\ref{tab:importance}. The discriminating variables used are:
 \begin{itemize}
@@
 
-A comparison between data and the predicted background for the leading $\had$ $\pt$ distribution in the SRs, after applying fake factors, 
+A comparison between data and the predicted background for the leading $\had$ $\pt$  and the visible invariant mass of the di-tau system ($m_{\tau\tau}$)
+distributions in the SRs, after applying fake factors, 
 %some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
-is shown in Figure~\ref{fig:taupt_prefit}.
+are shown in Figure~\ref{fig:taupt_prefit} and~\ref{fig:mtt}, respectively.
 %each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_{\ell}hadhad}.
@@
 %\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
+\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_os_log_.pdf} &
+\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b1j_ss_log_.pdf}&
+\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_ss_log_.pdf}\\
 (a) & (b) & (c) \\
 %(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}\\
-(d) & (e) \\
+\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_os_log_.pdf}&
+\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b3j_os_log_.pdf} &
+\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_ss_log_.pdf} \\
+(d) & (e) & (f)\\
 %(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}&
-\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}\\
-(f) & (g) \\
+\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b2jos_log_.pdf}&
+\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jos_log_.pdf}&
+\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jss_log_.pdf}\\
+(g) & (h) & (i)\\
 %(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
@@
   the expected background and $tuH$ signals after applying fake factors in the following SRs: $t_{\ell}\thadhad$ (a),
-  $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_h\thadhad$-2j (f), and $t_h\thadhad$-3j (g).
+ $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS  (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
  The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
@@
 
+\begin{figure}[H]
+\centering
+\begin{tabular}{@{}ccc@{}}
+%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
+%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
+%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
+\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_os_log_mtt.pdf} &
+\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b1j_ss_log_mtt.pdf}&
+\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_ss_log_mtt.pdf}\\
+(a) & (b) & (c) \\
+%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
+\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_os_log_mtt.pdf}&
+\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b3j_os_log_mtt.pdf}&
+\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_ss_log_mtt.pdf}\\
+(d) & (e) & (f)\\
+%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
+\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b2jos_log_mtt.pdf}&
+\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jos_log_mtt.pdf}&
+\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jss_log_mtt.pdf}\\
+(g) & (h) & (i)\\
+%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
+\end{tabular}
+\caption{Visible invariant mass of di-tau system ($m_{\tau\tau}$) distributions obtained before the fit to data (``Pre-Fit'') showing 
+  the expected background and $tuH$ signals after applying fake factors in the following SRs: $t_{\ell}\thadhad$ (a),
+ $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
+ The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
+ %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
+ Overflow events are included in the last bin.
+``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel.
+The $tuH$ signal is scaled using a normalization factor of 2 to 50.
+%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
+The lower panels show the data to prediction ratio.}
+\label{fig:mtt}
+\end{figure}
+
+%\begin{figure}[H]
+%\centering
+%\begin{tabular}{@{}ccc@{}}
+%\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b2j_os_log_ttCR.pdf} &
+%\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b2j_ss_log_ttCR.pdf}&
+%\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b3j_os_log_ttCR.pdf}\\
+%(a) & (b) & (c) \\
+%\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b3j_ss_log_ttCR.pdf}&
+%\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg2l1tau1bnj_log_ttCR.pdf}&
+%\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg2l1tau2bnj_log_ttCR.pdf}\\
+%(d) & (e) & (f)\\
+%\end{tabular}
+%\caption{Leading $\thad$ $\pt$  distributions obtained the fit to data (``Post-Fit'') for the fake $\thad$ fake factor calibration in the following ttCRs: 
+%$t_{\ell}t_{h}$2b$\thad$-2j OS (a), $t_{\ell}t_{h}$2b$\thad$-2j SS (b), $t_{\ell}t_{h}$2b$\thad$-3j OS (c), $t_{\ell}t_{h}$2b$\thad$-3j SS (d), $t_{\ell}t_{\ell}$1b$\thad$-nj (e) and $t_{\ell}t_{\ell}$2b$\thad$-nj (f).
+% The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
+% Overflow events are included in the last bin. 
+%The lower panels show the data to prediction ratio.}
+%\label{fig:ttCR_mtt}
+%\end{figure}
+
 % %\input{\FCNCFigures/tex/BDT}

### 2022-04-16 sections/conclusion.tex
update to V1.3

@@
 %about a factor of 2 improvement to 95\% CL upper limits on the $t\to Hq$ branching ratios are reported in Table~\ref{tab:limits_summary}, along with the Wilson coefficients with respect to the previous partial run-2 results~\cite{Aaboud2019SearchFT}.
-Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.9\times10^{-4}$ ($5.0^{+2.2}_{-1.4}\times10^{-4}$) and $7.2\times10^{-4}$ ($3.6^{+1.7}_{-1.0}\times10^{-4}$).
+Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.4\times10^{-4}$ ($4.8^{+2.2}_{-1.4}\times10^{-4}$) and $6.9\times10^{-4}$ ($3.5^{+1.5}_{-1.0}\times10^{-4}$).
 %The observed (expected) upper limits on the D6 Wilson coefficients from the combination of the searches are set to $C_{c\phi}<1.38\,(0.97)$ and $C_{u\phi}<1.18\,(0.83)$, respectively.
 The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
-the effective $tqH$ couplings for a new physics scale $\Lambda$ of 1~TeV are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.
+the effective $tqH$ couplings for a new physics scale $\Lambda$ of 1~TeV are $C_{c\phi} <1.35\, (0.97)$ and $C_{u\phi} <1.16\, (0.82)$, respectively.
 %These results improve significantly upon previous ATLAS and CMS limits on the $t\rightarrow Hq$ branching ratios.

### 2022-04-16 sections/introduction.tex
update to V1.3

@@
 CMS recently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
-the full Run 2 dataset. The observed (expected) upper limits on  $\BR(t\to cH)$ are $9.4\times10^{-4}(8.6\times10^{-4})$
-and are $7.9\times10^{-4}(1.1\times10^{-3})$ for $\BR{B}(t\to uH)$~\cite{CMS:2021gfa}.
+the full Run 2 dataset. The observed (expected) upper limits on  $\BR(t\to cH)$ are $9.4\times10^{-4}\, (8.6\times10^{-4})$
+and are $7.9\times10^{-4}\, (1.1\times10^{-3})$ for $\BR{B}(t\to uH)$~\cite{CMS:2021gfa}.
 %CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.

### 2022-04-16 sections/tau_FF_appendix.tex
update to V1.3

\section{Tau fake scale factor calibration in the ttCRs}
\label{sec:tauFF_appendix}

Figure~\ref{fig:ttCR_mtt} shows the post-fit of the leading $\thad$ $\pt$ in the ttCRs, which shows a good agreement between the data and the fitted background model.
Table~\ref{tab:ff1_summary} and~\ref{tab:ff2_summary} are summarized the fake scale factors of 1-prong and 3-prong taus
derived from the ttCRs including both statistical and systematic uncertainties.

\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b2j_os_log_ttCR.pdf} &
\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b2j_ss_log_ttCR.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b3j_os_log_ttCR.pdf}\\
(a) & (b) & (c) \\
\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg1l1tau2b3j_ss_log_ttCR.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg2l1tau1bnj_log_ttCR.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/ttCR/tuH_reg2l1tau2bnj_log_ttCR.pdf}\\
(d) & (e) & (f)\\
\end{tabular}
\caption{Leading $\thad$ $\pt$  distributions obtained after the fit to data (``Post-Fit'') for the $\thad$ fake scale factors in the following ttCRs:
  $t_{\ell}t_{h}$2b$\thad$-2j OS (a), $t_{\ell}t_{h}$2b$\thad$-2j SS (b), $t_{\ell}t_{h}$2b$\thad$-3j OS (c), $t_{\ell}t_{h}$2b$\thad$-3j SS (d),
  $t_{\ell}t_{\ell}$1b$\thad$-nj (e) and $t_{\ell}t_{\ell}$2b$\thad$-nj (f).
  The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
  Overflow events are included in the last bin. The lower panels show the data to prediction ratio.}
\label{fig:ttCR_mtt}
\end{figure}

\begin{table}
\caption{ Summary of fake tau (1-prong) scale factors derived in the ttCRs. The numbers are shown as: nominal values, statistical, and systematics erros. }
\begin{center}
\begin{tabular}{lcccccc}
\toprule\toprule

\multirow{2}{*}{Fake Factor Types} & \multicolumn{3}{c}{1 prong}  \\
$\thad$ $\pt$                                   &  $25-35$ GeV  & $35-45$ GeV  &  $45-$ GeV            \\
\midrule
Type-1                          &$0.71 \pm 0.01 \pm 0.03 $ &$0.61 \pm 0.02 \pm 0.04 $ &$0.38 \pm 0.02 \pm 0.05 $  \\
% W fake OS
Type-2                          &$0.76 \pm 0.06 \pm 0.04 $ & $0.37 \pm 0.08 \pm 0.02$ & $0.74 \pm 0.08 \pm 0.02 $ \\
% W fake SS
Type-3                          &$0.62 \pm 0.10 \pm 0.03 $ &$0.83 \pm 0.09 \pm 0.03 $ &$0.94 \pm 0.07 \pm 0.02 $  \\
%  b fake
Type-4                          &$1.20 \pm 0.02 \pm 0.01 $ & $1.01 \pm 0.04 \pm 0.02 $ &$0.76 \pm 0.03 \pm 0.03 $  \\
% other fake
\bottomrule\bottomrule
\end{tabular}
\label{tab:ff1_summary}
\end{center}
\end{table}

\begin{table}
\caption{ Summary of fake tau (3-prong) scale factors derived in the ttCRs. The numbers are shown as: nominal values, statistical, and systematics erros. }
\begin{center}
\begin{tabular}{lcccccc}
\toprule\toprule

\multirow{2}{*}{Fake Factor Types}        & \multicolumn{3}{c}{3 prong}  \\
$\thad$ $\pt$                             &  $25-35$ GeV  & $35-45$ GeV       &  $45-$ GeV  \\
\midrule
Type-1                                    & $1.01 \pm 0.03 \pm 0.04 $ & $1.09 \pm 0.04 \pm 0.05 $ & $0.30 \pm 0.05 \pm 0.07 $ \\
% W fake OS
Type-2                                    & $0.93 \pm 0.10 \pm 0.04 $ & $1.05 \pm 0.09 \pm 0.03 $ & $0.79 \pm 0.09 \pm 0.04 $ \\
% W fake SS
Type-3                                    & $1.07 \pm 0.13 \pm 0.03 $ &$1.39 \pm 0.12 \pm 0.03 $ &$1.26 \pm 0.10 \pm 0.04 $  \\
%  b fake
Type-4                                    &$1.28 \pm 0.07 \pm 0.02 $ &$0.66 \pm 0.08 \pm 0.01 $ & $0.71 \pm 0.07 \pm 0.02 $ \\
% other fake
\bottomrule\bottomrule
\end{tabular}
\label{tab:ff2_summary}
\end{center}
\end{table}

### 2022-04-16 sections/tau_FF_appendix.tex
minor fix

@@
 
-\multirow{2}{*}{Fake Factor Types} & \multicolumn{3}{c}{1 prong}  \\
+Fake tau types & \multicolumn{3}{c}{1-prong tau}  \\ \midrule
 $\thad$ $\pt$                                   &  $25-35$ GeV  & $35-45$ GeV  &  $45-$ GeV            \\
@@
 
-\multirow{2}{*}{Fake Factor Types}        & \multicolumn{3}{c}{3 prong}  \\
+Fake tau types        & \multicolumn{3}{c}{3-prong tau}  \\ \midrule
 $\thad$ $\pt$                             &  $25-35$ GeV  & $35-45$ GeV       &  $45-$ GeV  \\

### 2022-04-17 sections/bdt_Htautau.tex
minor fix

@@
 A comparison between data and the predicted background for the leading $\had$ $\pt$  and the visible invariant mass of the di-tau system ($m_{\tau\tau}$)
-distributions in the SRs, after applying fake factors, 
+distributions in SRs and VRs, after applying fake factors, 
 %some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
@@
 \caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (``Pre-Fit'') showing 
-  the expected background and $tuH$ signals after applying fake factors in the following SRs: $t_{\ell}\thadhad$ (a),
+  the expected background and $tuH$ signals after applying fake factors in the following: $t_{\ell}\thadhad$ (a),
  $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS  (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
@@
 \caption{Visible invariant mass of di-tau system ($m_{\tau\tau}$) distributions obtained before the fit to data (``Pre-Fit'') showing 
-  the expected background and $tuH$ signals after applying fake factors in the following SRs: $t_{\ell}\thadhad$ (a),
+  the expected background and $tuH$ signals after applying fake factors in the following: $t_{\ell}\thadhad$ (a),
  $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).

### 2022-05-08 sections/bdt_Htautau.tex
addressing Luca's comments to V1.4

@@
  $\Delta R(\tau1,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
- \text{min}($m_{jj}$) &   &  $12$               &           & $11$     &       &  &         \\
+ \text{min}($m_{\text{jj}}$) &   &  $12$               &           & $11$     &       &  &         \\
 % $m_{\text{W}}$                                      & $\times$  &  $\times$           &  $\times$         & $9$      & $\times$      & $6$      & $7$\\
@@
 \item ${\pt}^{\ell}$ is the transverse momentum of the leading light lepton.
-\item $\chi^2$ of the kinematic fit of the momentum of the invisible decay products of the tau leptons.
+\item $\chi^2$ of the kinematic fit of the momentum of the invisible decay products of the tau leptons as defined in eq.~(\ref{eq:eq1}).
 \item $m_{\text{bjj},\text{fit}}$ is the fitted invariant mass of the $b$-jet and the two jets from the $W$ boson decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
@@
 \item $m_{\text{bjj}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top quark mass.
-\item \text{min}($m_{\tau\tau \text{j}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavour jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\tau\tau\text{q}}$.
-\item \text{min}($m_{\text{jj}}$) is the invariant mass of two light-flavour jets, minimized by choosing different jets, reflects the invariant mass of the $W$ candidate.
+\item \text{min}($m_{\tau\tau \text{j}}$) is the minimum value of the visible mass of the di-tau candidates (include leptonic tau) and the light-flavour jet system, minimized by choosing different jet, reflecting the invariant masss of the visible FCNC top decaying products.
+\item \text{min}($m_{\text{jj}}$) is the minimum value of all the invariant mass of all the light-flavour jet pairs, reflecting the invariant mass of the $W$ boson candidate.
   %an alternative of $m_{\text{W}}$.
@@
 \item $E_{\tau\text{i}}/E_{\tau\text{i},\text{fit}}$ (\text{i}=1,2) is the momentum fraction carried by the visible decay products from the leading and subleading tau decays.
-It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section.
+It is based on the best-fit of the 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section.
 For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}.
@@
 %corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.
-The last bin of each plot contains the overflow entries.
-The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model}.
-The hashed area represents the total uncertainty of the background.
+%The last bin of each plot contains the overflow entries.
+%The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model}.
+%The hashed area represents the total uncertainty of the background.
 A good description of the data by the background model is observed in all cases.
@@
 \caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (``Pre-Fit'') showing 
-  the expected background and $tuH$ signals after applying fake factors in the following: $t_{\ell}\thadhad$ (a),
+  the expected background and $tuH$ signals after applying fake factors in the following regions: $t_{\ell}\thadhad$ (a),
  $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS  (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
@@
 \end{tabular}
-\caption{Visible invariant mass of di-tau system ($m_{\tau\tau}$) distributions obtained before the fit to data (``Pre-Fit'') showing 
-  the expected background and $tuH$ signals after applying fake factors in the following: $t_{\ell}\thadhad$ (a),
+\caption{Visible invariant mass of the di-tau system ($m_{\tau\tau}$) distributions obtained before the fit to data (``Pre-Fit'') showing 
+  the expected background and $tuH$ signals after applying fake factors in the following regions: $t_{\ell}\thadhad$ (a),
  $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).

### 2022-05-08 sections/data_presel.tex
addressing Luca's comments to V1.4

@@
 \item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay where one $\had$ fails the tau reconstruction or identification so that there is only one reconstructed $\had$ candidate.
-  To reduce the SM backgrounds and avoid overlaps with the other selections, exactly one $\had$ with same-sign charge to the light lepton is required.
+  To reduce the SM backgrounds and avoid overlaps with the other ATLAS searches, exactly one $\had$ with same-sign charge to the light lepton is required.
   In addition, at least two jets including exactly one $b$-jet are required.
@@
 \caption{\small{Summary of preselection requirements. 
-The leading and subleading $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
+The leading and subleading $\had$ candidates are denoted by $\tau_{\mathrm{had1}}$ and $\tau_{\mathrm{had2}}$ respectively.}}
 \begin{center}
@@
 $\had$  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
-Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} < 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} > 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ \\
+Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} < 0$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} > 0$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} < 0$ \\
 Jets  &   $\geq$ 3 jets & $\geq$1 jets & $\geq$2 jets & $\geq$3 jets \\

### 2022-05-08 sections/strategy_Htautau.tex
addressing Luca's comments to V1.4

@@
 
-The analysis strategy adopted in this FCNC $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more search channels.
+The analysis strategy adopted in this FCNC $\Htautau$ search is similar to the one used in Refs.~\cite{fcnc36,Chen:2015nta} but extended to more search channels.
 %\subsection{Event categorisation and kinematic reconstruction}
@@
 are estimated using a kinematic fit and assuming a collinear approximation for the tau decay products.
-The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
-measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is estimated to be $20~\gev$ from a fit of the mass
+The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass ($m_{\text{H}}=125~\gev$) and the
+measured $E_{\text{x,y}}^{\text{miss}}$  within their expected resolutions ($\sigma_{E_{\text{x,y}}^{\text{miss}}}$), defined as
+\begin{eqnarray}
+\begin{array}{ll}
+\chi^2 =
+\left( \frac{m_{\tau\tau,\text{fit}} - m_{\text{H}}}{\sigma_{\tau\tau}} \right)^2 +
+\left( \frac{E_{\text{x,fit}}^{\text{miss}} - E_{\text{x}}^{\text{miss}}}{\sigma_{E_{\text{x}}^{\text{miss}}}} \right)^2
+  +\left( \frac{E_{\text{y,fit}}^{\text{miss}} - E_{\text{y}}^{\text{miss}}}{\sigma_{E_{\text{y}}^{\text{miss}}}} \right)^2.
+\end{array}
+\label{eq:eq1}
+\end{eqnarray}
+
+The resolution on the Higgs boson mass ($\sigma_{\tau\tau}$) is estimated to be $20~\gev$ from a fit of the mass
 distribution of the simulated  $tqH$ signal events, while the resolution on the measured $\met$ is parameterised as a linear function of 

### 2022-05-08 sections/systematic_uncertainties.tex
update to V1.3
addressing Luca's comments to V1.4

@@
 POWHEG-BOX v2) is set to 1.5$m_t$ in the nominal case. Alternative samples are generated with $h_{\mathrm{damp}}$=3$m_t$. The
-difference between two samples is treated as one of the systematics as ``$t\bar{t}$ $h_{\mathrm{damp}}$''. 
+difference between two samples is treated as a systematic named as ``$t\bar{t}$ $h_{\mathrm{damp}}$''. 
 %The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
@@
 different fake tau sources and different $\pt$ slices. The uncertainties on the MC modelling of the various processes used for
-evaluation of the fake factors in the CRtt's are considered and treated as fully correlated in the fit.
-The uncertainty of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both,
-its statistical fluctuation and the differences between the leptonic channels.
+evaluation of the fake factors in the CRtt's are treated as fully correlated in the fit.
+The uncertainty of the ABCD method is applied on the normalisation factors for muon and electron respectively including both,
+its statistical fluctuation and the differences in the normalisation factors between the leptonic channels.
 The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.
@@
 Several normalisation and shape uncertainties are taken into account and are treated as fully correlated for the $\Hq$ and $pp\to tH$ signals.
-Uncertainties of the Higgs boson branching ratios are taken from the measured values in Ref.~\cite{Zyla:2020zbs}.
-%into account following the recommendation in Ref.~\cite{deFlorian:2016spz}.
+Uncertainties of the Higgs boson branching ratios are taken
+%from the measured values in Ref.~\cite{Zyla:2020zbs}.
+into account following the recommendation in Ref.~\cite{deFlorian:2016spz}.
 The uncertainty of ISR, FSR, scale and PDF are considered and are treated fully correlated in all SRs. The parton shower uncertainties are estimated by comparing

### 2022-05-08 ANA-TOPQ-2019-17-PAPER-metadata.tex
minor update
adding Attilio's comments for CONF note
update Luca's comments
update ATLAS-CONF-2022-014

@@
 % Comment or remove in final version.
-\AtlasVersion{1.1}
+\AtlasVersion{1.4}
 % Abstract - % directly after { is important for correct indentation
@@
 and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
-Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.9 \times 10^{-4}$ ($5.0^{+2.2}_{-1.4}\times 10^{-4}$) and $7.2\times 10^{-4}$ ($3.6^{+1.7}_{-1.0}\times 10^{-4}$), respectively.
+Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.4 \times 10^{-4}\, (4.8^{+2.2}_{-1.4}\times 10^{-4})$
+and $6.9\times 10^{-4}\, (3.5^{+1.5}_{-1.0}\times 10^{-4})$, respectively. 
 The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
-the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.}%for the new physics scale $\Lambda$ at 1~TeV, respectively.} 
+the effective $tqH$ couplings are $C_{c\phi} <1.35\, (0.97)$ and $C_{u\phi} <1.16\, (0.82)$, respectively.}%for the new physics scale $\Lambda$ at 1~TeV, respectively.} 
 %$|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
@@
 % ATLAS reference code, to help ATLAS members to locate the paper
+%\AtlasRefCode{CONF-TOPQ-2022-06}
 \AtlasRefCode{TOPQ-2019-17}
-%\AtlasRefCode{ATLAS-CONF-2018-049}
+%\AtlasRefCode{ATLAS-CONF-2022-014}
 
@@
 % Comment deadline
-\AtlasCoverCommentsDeadline{9 March 2022}
+\AtlasCoverCommentsDeadline{9 May 2022}
 

### 2022-05-08 sections/background_estimation.tex
update to V1.3

@@
 Similarly for Type-2, the semileptonic regions ($t_{\ell}t_h2b\thad$-2jSS and $t_{\ell}t_h2b\thad$-3jSS) where $\thad$ and light lepton have same charge are used.
-A simultaneous fit to data is made to derive the scale factors for fake taus in MC, which consist of total of 24 parameters
-depending on four types, three $\pt$ bins, two bins for 1- and 3-prong taus separately.
+A simultaneous fit to data is made to derive the scale factors for fake taus in MC, which consist of a total of 24 parameters
+depending on four types of fake taus, three $\pt$ bins, two bins for 1- and 3-prong taus separately. The post-fit distributions of the
+leading $\thad$ $\pt$ and measured tau scale factors are presented in Appendix~\ref{sec:tauFF_appendix}. 
 The values of these scale factors range from 0.3-1.28 are then used to correct the MC estimated fakes in the corresponding  signal regions with a single $b$-jet.

### 2022-05-08 sections/objects.tex

@@
 These additional reconstructed charged particle tracks inside the jet can be
-used to increase the accuracy for identifying the displaced decay vertex of heavy flavour (b, c) hadrons that produced non-prompt leptons.
+used to increase the accuracy for identifying the displaced decay vertex of heavy flavour ($b$, $c$) hadrons that produced non-prompt leptons.
 The tight working points are used for high $\pt$ lepton ($>20~\GeV$).
@@
 The calibrated jets used are required to have $\pt > 25~\gev$ and $|\eta| < 2.5$.
-Jet four-momenta are corrected for pile-up effects using the jet-area method~\cite{Cacciari:2008gn}.
+The four-momentum of the jets is corrected for pile-up effects using the jet-area method~\cite{Cacciari:2008gn}.
 
@@
 Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
-Events with a $b$-tagged $\had$ candidate are rejected.
+Events are rejected if the jet seeding the $\had$ candidate is $b$-tagged.
+%Events with a $b$-tagged  $\had$ candidate are rejected.
 %(TBD: check RNN description and update then numbers)

### 2022-05-08 sections/statistical_analysis.tex
minor update for the final confnote

@@
 and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations.
+The $pp\rightarrow tH$ production cross section is related to $\BR(t\rightarrow qH)$ based on their dimension-6 operators~\cite{fcnc_production_theory}.
 Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
@@
 %In the absence of signal,
-Exclusion limits are set on $\mu$ , and thus on
+Exclusion limits are set on $\mu$ and thus on
 $\BR(t\to qH)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.

### 2022-05-08 sections/tau_FF_appendix.tex

@@
 
-Figure~\ref{fig:ttCR_mtt} shows the post-fit of the leading $\thad$ $\pt$ in the ttCRs, which shows a good agreement between the data and the fitted background model.
-Table~\ref{tab:ff1_summary} and~\ref{tab:ff2_summary} are summarized the fake scale factors of 1-prong and 3-prong taus
+Figure~\ref{fig:ttCR_mtt} presents the post-fit distributions of the leading $\thad$ $\pt$ in the ttCRs, which shows a good agreement between the data and the fitted background model.
+Table~\ref{tab:ff1_summary} and~\ref{tab:ff2_summary} summarize the fake scale factors of 1-prong and 3-prong taus
 derived from the ttCRs including both statistical and systematic uncertainties.
@@
 \begin{table}
-\caption{ Summary of fake tau (1-prong) scale factors derived in the ttCRs. The numbers are shown as: nominal values, statistical, and systematics erros. }
+\caption{ Summary of fake tau (1-prong) scale factors derived in the ttCRs. The numbers are shown as: nominal values, statistical, and systematics uncertainties. }
 \begin{center}

### 2022-05-23 sections/bdt_Htautau.tex
minor update to V1.5

@@
 The BDT discriminant is trained for each SR starting from a large list of variables. Then the least important variable is removed one at a time and the BDT is retrained until the
-receive operating characteristic (ROC) score drops more than 2\%.
+received operating characteristic (ROC) score drops more than 2\%.
 %The final variables used in SRs are shown in Table 5 with their ranking. 
@@
 \item ${\pt}^{\ell}$ is the transverse momentum of the leading light lepton.
-\item $\chi^2$ of the kinematic fit of the momentum of the invisible decay products of the tau leptons as defined in eq.~(\ref{eq:eq1}).
+\item $\chi^2$ of the kinematic fit of the momentum of the invisible decay products of the tau leptons as defined in Eq.~(\ref{eq:eq1}).
 \item $m_{\text{bjj},\text{fit}}$ is the fitted invariant mass of the $b$-jet and the two jets from the $W$ boson decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
@@
 \item \text{min}($m_{\tau\tau \text{j}}$) is the minimum value of the visible mass of the di-tau candidates (include leptonic tau) and the light-flavour jet system, minimized by choosing different jet, reflecting the invariant masss of the visible FCNC top decaying products.
-\item \text{min}($m_{\text{jj}}$) is the minimum value of all the invariant mass of all the light-flavour jet pairs, reflecting the invariant mass of the $W$ boson candidate.
+\item \text{min}($m_{\text{jj}}$) is the minimum value of the invariant mass of all the light-flavour jet pairs, reflecting the invariant mass of the $W$ boson candidate.
   %an alternative of $m_{\text{W}}$.

### 2022-05-23 sections/data_presel.tex
minor update to V1.5

@@
 \item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay where one $\had$ fails the tau reconstruction or identification so that there is only one reconstructed $\had$ candidate.
-  To reduce the SM backgrounds and avoid overlaps with the other ATLAS searches, exactly one $\had$ with same-sign charge to the light lepton is required.
+  To reduce the SM backgrounds and avoid overlaps with the final states of other ATLAS searches, exactly one $\had$ with same-sign charge to the light lepton is required.
   In addition, at least two jets including exactly one $b$-jet are required.

### 2022-06-02 ANA-TOPQ-2019-17-PAPER-metadata.tex
minor update to V1.5
Fixing the language editorial comments and update to V1.6

@@
 % Comment or remove in final version.
-\AtlasVersion{1.4}
+\AtlasVersion{1.6}
 % Abstract - % directly after { is important for correct indentation
 \AtlasAbstract{%
-A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, an up-type quark ($q=u, c$), and a
+A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, another up-type quark ($q=u, c$), and a
 Standard Model (SM) Higgs boson decaying into a $\tau$-lepton pair ($H\rightarrow \tau^+\tau^-$) is presented.
-The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
-Large Hadron Collider that corresponds to an integrated luminosity of 139 fb$^{-1}$.
+The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ that corresponds to an integrated luminosity of 139 fb$^{-1}$ recorded with the ATLAS detector at the 
+Large Hadron Collider.
 Two processes are considered:  single top quark FCNC production in association with a Higgs boson ($pp\rightarrow tH$), and top quark pair production in
@@
 as well as multiple jets. Event kinematics are used to separate signal from the background through a multivariate discriminant.  
-A slight excess of data is observed above the expected SM background with a significance of 2.3$\sigma$,
+A slight excess of data is observed with a significance of 2.3$\sigma$ above the expected SM background,
 and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
@@
 % Comment deadline
-\AtlasCoverCommentsDeadline{9 May 2022}
+\AtlasCoverCommentsDeadline{9 June 2022}
 

### 2022-06-02 sections/background_estimation.tex
Fixing the language editorial comments and update to V1.6

@@
 with prompt leptons, i.e.\ those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
-are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
+are estimated using samples of simulated events and are initially normalised to their theoretical cross sections.
 In the simulation, the top-quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
-and the Higgs boson is forced to decay into $H\to \tau\tau$ with branching ratio calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
+and the Higgs boson is forced to decay via $H\to \tau\tau$ with branching ratio calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
 Backgrounds with non-prompt light leptons (electron or muon), with photons or jets misidentified as electrons, or with jets misidentified as tau candidates, 
@@
 
-In the leptonic channels, the events with prompt electron or muon and fake taus are modelled by calibrating MC with scale factors (SF)
+In the leptonic channels, the events with a prompt electron or muon and fake taus are modelled by calibrating the MC with scale factors (SF)
 derived from the dedicated $t\bar t$
 control regions (CRtt) using dileptonic decays of $t\bar t$ events and semileptonic decays of $t\bar t$ events with two
-$b$-jets, summarized in Table~\ref{tab:srcr}. 	
+$b$-jets, as is summarized in Table~\ref{tab:srcr}. The control regions are defined similarly to the signal regions but with an additional $b$-jet or light lepton. 	
 %the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
@@
 There are four kinds of fake taus that need to be calibrated: Type-1 fake taus from hadronic $W$ boson decay ($\tau_{W}$) %$W$-jets ($\tau_{W}$)
-with opposite-sign (OS) of charge to the light lepton;
-Type-2 $\tau_{W}$'s with same-sign (SS) charge to the light lepton; Type-3 fake taus originating from $b$-hadron decays; Type-4 fake taus from light-flavour hadron decays.
-The control regions are defined similar to the signal regions but with an additional $b$-jet or light lepton.
+with opposite-sign (OS) charge relative to the light lepton;
+Type-2 $\tau_{W}$'s with same-sign (SS) charge relative to the light lepton; Type-3 fake taus originating from $b$-hadron decays; Type-4 fake taus from light-flavour hadron decays.
+%The control regions are defined similar to the signal regions but with an additional $b$-jet or light lepton.
 %$t_{\ell}t_{\ell}1b\thad$, $t_{\ell}t_{\ell}2b\thad$, $t_{\ell}t_h2b\thad$-2jSS, $t_{\ell}t_h2b\thad$-2jOS, $t_{\ell}t_h2b\thad$-3jSS, and $t_{\ell}t_h2b\thad$-3jOS.
 The dilepton regions ($t_{\ell}t_{\ell}1b\thad$ and $t_{\ell}t_{\ell}2b\thad$) are used to calibrate Type-3 and Type-4 fake taus. The semileptonic
-regions ($t_{\ell}t_h2b\thad$-2jOS and $t_{\ell}t_h2b\thad$-3jOS) where $\thad$ and light lepton have opposite charge are used to calibrate Type-1 fake taus.
-Similarly for Type-2, the semileptonic regions ($t_{\ell}t_h2b\thad$-2jSS and $t_{\ell}t_h2b\thad$-3jSS) where $\thad$ and light lepton have same charge are used.
-A simultaneous fit to data is made to derive the scale factors for fake taus in MC, which consist of a total of 24 parameters
-depending on four types of fake taus, three $\pt$ bins, two bins for 1- and 3-prong taus separately. The post-fit distributions of the
+regions ($t_{\ell}t_h2b\thad$-2jOS and $t_{\ell}t_h2b\thad$-3jOS), where the $\thad$ and light lepton have opposite charges, are used to calibrate Type-1 fake taus.
+Similarly for Type-2, the semileptonic regions ($t_{\ell}t_h2b\thad$-2jSS and $t_{\ell}t_h2b\thad$-3jSS), where the $\thad$ and light lepton have same charges, are used.
+A simultaneous fit to data is made to derive the scale factors for fake taus in the MC. These consist of a total of 24 parameters
+depending on four types of fake taus, three $\pt$ bins, and two bins for 1- and 3-prong taus separately. The post-fit distributions of the
 leading $\thad$ $\pt$ and measured tau scale factors are presented in Appendix~\ref{sec:tauFF_appendix}. 
-The values of these scale factors range from 0.3-1.28 are then used to correct the MC estimated fakes in the corresponding  signal regions with a single $b$-jet.
+The values of these scale factors range from 0.3 to 1.28 and are then used to correct the MC-estimated fakes in the corresponding  signal regions with a single $b$-jet.
 In the $t_{\ell}\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the same procedure used in the $\tlhad$ channel.
 %using the lepton and fake tau charges, then the scale factors are multiplied together.
-The nominal value of scale factors will vary according to their uncertainties in the final fit. A closure test is made for the fake tau estimations using the same procedure
-in the $t_{\ell}\thadhad$-SS validation region, which shows a good agreement between data and the background prediction. 
+The central value of scale factors vary according to their uncertainties in the final fit. A closure test is made for the fake tau estimates using the same procedure
+in the $t_{\ell}\thadhad$-SS validation region, and it shows good agreement between data and the background prediction. 
 %In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
@@
 
-In the hadronic channels, the contribution of fakes is estimated partially from data by defining control regions (CR)
-enriched in misidentified
-tau candidates via loosened tau requirements with fake factors and partially from MC~\cite{ATLAS-CONF-2021-044}.
-These CRs do not overlap with the main signal regions, discussed in Section~\ref{sec:strategy_Htautau}.
+In the hadronic channels, the contribution of fakes is estimated from data using the fake-factor (FF) method to derive the transfer functions from the background enriched control
+regions (CR) to the SR~\cite{ATLAS-CONF-2021-044}.
+%by defining control regions (CR)
+%enriched in misidentified
+%tau candidates via loosened tau requirements with fake factors and partially from MC~\cite{ATLAS-CONF-2021-044}.
+These CRs do not overlap with the main signal regions discussed in Section~\ref{sec:strategy_Htautau}.
 The CR selection requirements are analogous to those used to define signal regions, except
-that the subleading tau candidate is required to fail the medium tau identification, but it still passes a loose requirement.
-The contribution of fakes with subleading tau candidate can be calculated by rescaling the templates of loose taus in the CR
-with fake factors (FF).
-The templates are produced by subtracting all MC background contributions with real subleading taus from data.
+that the subleading tau candidate is required to fail the medium tau identification while still passing a loose requirement.
+The contribution of fakes with subleading tau candidates can be calculated by rescaling the templates of loose taus in the CR
+with the FFs.
+The templates are produced by subtracting all MC background contributions with real subleading taus from the data.
 The FFs are computed as the ratio of misidentified $\thad$ candidates that either pass or fail the medium tau ID selection in regions enriched in events originating from 
@@
 %We have compared
-FFs obtained from the $W$+jets and from the same-sign $\thadhad$ control regions are compared and the differences are treated as a systematic uncertainty.
+FFs obtained from the $W$+jets and from the same-sign $\thadhad$ control regions are compared and the difference is treated as a systematic uncertainty.
 
@@
 fake light leptons in the signal region is evaluated by scaling the number of loose leptons in the high $\met$ region by the ratio of tight and loose leptons in the
-low $\met$ region. The contributions of prompt leptons and calibrated fake taus in the number of tight and loose leptons are subtracted using MC simulation.
-A closure test is made for the background estimations in the signal depleted low BDT ($<-0.6$) regions, defined in Section~\ref{sec:tmva}.
+low $\met$ region. The contributions of prompt leptons and calibrated fake taus to the number of tight and loose leptons are subtracted using MC simulation.
+A closure test is made for the background estimates in the signal depleted low BDT ($<-0.6$) regions, defined in Section~\ref{sec:tmva}.
 The data are in good agreement with the background prediction in the

### 2022-06-02 sections/bdt_Htautau.tex
Fixing the language editorial comments and update to V1.6

@@
 
-Boosted decision trees (BDT) implemented in the TMVA framework~\cite{Hocker:2007ht} are used in each SR to improve the separation between signal and background. 
+Boosted decision trees implemented in the TMVA framework~\cite{Hocker:2007ht} are used in each SR to improve the separation between signal and background. 
 %The separate training exploits differences in event kinematics across SRs.  
 %draft 1 version
-In the training, all signal events from $tt(qH)$ and $tH$ are merged together for $tuH$ and $tcH$. All background sources from SM processes
+In the training process, all signal events from $tt(qH)$ and $tH$ are merged together for $tuH$ and $tcH$. All background sources from SM processes
 (including both real and fake tau contributions) are also used in the training.
 
-A large set of potential variables are investigated in each SR separately.
-The discrimination of a given variable is quantified by the "separation" (measures the degree of overlap between background and signal shape) and "importance" (depicts the power of the variable to the classification of the events) provided by the TMVA package~\cite{Hocker:2007ht}.
-The BDT discriminant is trained for each SR starting from a large list of variables. Then the least important variable is removed one at a time and the BDT is retrained until the
-received operating characteristic (ROC) score drops more than 2\%.
+Many potential variables are investigated in each SR separately.
+The discrimination of a given variable is quantified by the "separation" (which measures the degree of overlap between background and signal shape) and "importance" (which depicts the power of the variable in the classification of the events) provided by the TMVA package.%~\cite{Hocker:2007ht}.
+The BDT discriminant is trained for each SR starting from a large list of variables; then the least important variables are removed sequentially, and the BDT is retrained until the
+receiver operating characteristic (ROC) score drops by more than 2\%.
 %The final variables used in SRs are shown in Table 5 with their ranking. 
 %and only those variables whose importance is larger than 2\% were kept.
-The final BDT input variables in each SR and their importance ranking are listed in Table~\ref{tab:importance}. The discriminating variables used are:
+The final BDT input variables in each SR and their importance ranking are listed in Table~\ref{tab:importance}. The discriminating variables are as follows.
 \begin{itemize}
@@
 \end{equation}
-where $\Delta\phi_{\ell,\text{miss}}$ is the azimuth angle between the light-lepton and $\met$.  
+where $\Delta\phi_{\ell,\text{miss}}$ is the azimuthal angle between the light-lepton and $\met$.  
 \item $m_{\tau\tau,\text{fit}}$ is the fitted invariant mass of the tau candidates and reconstructed neutrinos for the $t_hH$ and $t_ht(qH)$ events. 
-\item $m_{\text{jj}}$ is the reconstructed invariant mass of two light-jets from the $W$ decay with the mass closet to the $W$ mass.
-\item $m_{\tau\tau\text{q},\text{fit}}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
+\item $m_{\text{jj}}$ is the reconstructed invariant mass of two light-jets from the $W$ decay with the mass closest to the $W$ mass.
+\item $m_{\tau\tau\text{q},\text{fit}}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from the di-tau candidates, $q$-jet and reconstructed neutrinos.
 \item $m_{\tau\tau}$ is the visible invariant mass of the di-tau system. %or the lepton and $\had$ candidate when there is only one $\had$.
@@
 \item $m_{\text{bjj}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top quark mass.
-\item \text{min}($m_{\tau\tau \text{j}}$) is the minimum value of the visible mass of the di-tau candidates (include leptonic tau) and the light-flavour jet system, minimized by choosing different jet, reflecting the invariant masss of the visible FCNC top decaying products.
+\item \text{min}($m_{\tau\tau \text{j}}$) is the minimum value of the visible mass of the di-tau candidates (including leptonically decaying tau) and the light-flavour jet system,
+  reflecting the invariant mass of the visible FCNC top decaying products.
 \item \text{min}($m_{\text{jj}}$) is the minimum value of the invariant mass of all the light-flavour jet pairs, reflecting the invariant mass of the $W$ boson candidate.
   %an alternative of $m_{\text{W}}$.
-\item $\met$ centrality is a measure of how central the $\met$ lies between the two tau candidates in the transverse plane, and is defined as
+\item $\met$ centrality is a measure of how centrally the $\met$ lies between the two tau candidates in the transverse plane, and is defined as
 \begin{eqnarray}
@@
 \item $\Delta\phi(\tau\tau,\met)$ is the azimuthal angle between the $\met$ and di-tau system $\pT$.
-\item $\Delta R(a,b)$ is the angular distance between \text{a} and \text{b} objects in the event. 
+\item $\Delta R(a,b)$ is the angular distance between the \text{a} and \text{b} objects in the event. 
 %\item $\Delta R(\tau1,\text{light-jet})$ is the minimum angle distance between the tau candidate and the light-jet. If there are two taus in the event, the leading one is used.
@@
 
-A comparison between data and the predicted background for the leading $\had$ $\pt$  and the visible invariant mass of the di-tau system ($m_{\tau\tau}$)
+Comparisons between the data and the predicted background for the leading $\had$ $\pt$  and the visible invariant mass of the di-tau system ($m_{\tau\tau}$)
 distributions in SRs and VRs, after applying fake factors, 
 %some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
-are shown in Figure~\ref{fig:taupt_prefit} and~\ref{fig:mtt}, respectively.
+are shown in Figures~\ref{fig:taupt_prefit} and~\ref{fig:mtt}, respectively.
 %each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_{\ell}hadhad}.
@@
 A good description of the data by the background model is observed in all cases.
-The final observable used to extract the signal contribution is the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.
+The final observable used to extract the signal contribution is the BDT distribution in each SR corresponding to either the $tuH$ or the $tcH$ signal.
 
@@
  %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
- Overflow events are included in the last bin.
-``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel.
-The $tuH$ signal is scaled using a normalization factor of 2 to 50.
+ Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, $V$+jets, and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signals are scaled using
+ normalization factors of 2 to 50.   
 %( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 

### 2022-06-02 sections/conclusion.tex
Fixing the language editorial comments and update to V1.6

@@
 %-------------------------------------------------------------------------------
-A search for flavour-changing neutral current processes involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented.
-FCNC $tqH$ interaction is searched for both in the $t\bar{t}$ decay mode, where one top quark decays according to the SM processes and the other one decays through $t\rightarrow qH$, and in the production mode ($pp\rightarrow tH$) with a single top quark produced via FCNC interaction where $t\to Wb$.
-The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
+A search for flavour-changing neutral current processes involving a top quark, another up-type quark ($q=u, c$), and a SM Higgs boson is presented.
+FCNC $tqH$ interaction is sought both in the $t\bar{t}$ decay mode, where one top quark decays via SM processes and the other one decays through $t\rightarrow qH$, and in the production mode ($pp\rightarrow tH$) with a single top quark produced via the
+FCNC interaction where $t\to Wb$.
+%The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
 The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton (e,$\mu$), a $b$-jet as well as multiple jets.
@@
 No significant excess of events above the background expectation is found.
-A slight excess of data is observed above background with a significance of 2.3$\sigma$.  
-95\% CL upper limits are set on the $t\to qH$ branching ratios and the corresponding
+A slight excess of data is observed above background with a significance of 2.3$\sigma$. Upper limits at the
+95\% confidence level are set on the $t\to qH$ branching ratios and the corresponding
 dimension-6 operator Wilson coefficients in the effective $tqH$ couplings. 
@@
 %These results improve significantly upon previous ATLAS and CMS limits on the $t\rightarrow Hq$ branching ratios.
-These results improve significantly previously published ATLAS studies in this channel and provide more stringent limit than the ATLAS  $t\rightarrow qH$ combination~\cite{fcnc36}.
+These results improve significantly upon the previously published ATLAS studies in this channel and provide more stringent limits than the ATLAS  $t\rightarrow qH$ combination~\cite{fcnc36}.

### 2022-06-02 sections/data_presel.tex
Fixing the language editorial comments and update to V1.6

--- 2022-05-08 sections/data_presel.tex
@@
 Only events recorded with a single-electron trigger, a single-muon trigger, or a di-tau trigger~\cite{TRIG-2018-05,TRIG-2018-01,id_trigger,l1topo_trigger} under stable beam conditions 
-and for which all detector subsystems were operational are considered for analysis. The events recorded by di-lepton triggers fall into the control regions are used for fake tau background
-estimation. The number of $pp$ interactions per bunch crossing in this dataset ranges from about 8 to 45, with an average of 24.
+and for which all detector subsystems were operational are considered for analysis. The events recorded by di-lepton triggers that fall into the control regions are used for fake tau background
+estimation as discussed in Section~\ref{sec:background_model}. The number of $pp$ interactions per bunch crossing in this dataset ranges from about 8 to 45, with an average of 24.
 
@@
 Further requirements are defined targeting different signal decay modes:
-The events in the leptonic channel are recorded by a single-electron or single-muon trigger, required to have exactly one electron or muon that matches, within $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers.
-Further requirements are defined targeting different signal decay modes:
+The events in the leptonic channel are recorded by a single-electron or single-muon trigger, and are required to have exactly one electron or muon that matches, within $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers.
+Requirements are placed on the following additional quantities.
+%Further requirements are defined targeting different signal decay modes:  
 \begin{itemize}
-\item $t_h\lephad$: Targeting into the $t_hH$ and $t_ht(qH)$ final states with a $H\to\lephad$ decay.
-Exactly one $\had$ with opposite-side charge to $\lep$ is required, including at least three jets with exactly one $b$-jet.
-\item $t_{\ell}\hadhad$: Targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay.
-Exactly one light lepton and two opposite-sign $\had$ are selected, including at least one jet with exactly one $b$-jet.
-\item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay where one $\had$ fails the tau reconstruction or identification so that there is only one reconstructed $\had$ candidate.
-  To reduce the SM backgrounds and avoid overlaps with the other ATLAS searches, exactly one $\had$ with same-sign charge to the light lepton is required.
+\item $t_h\lephad$: To enhance selection of the $t_hH$ and $t_ht(qH)$ final states with a $H\to\lephad$ decay, exactly one $\had$ with opposite-side charge to $\lep$ is required, including at least three jets with exactly one $b$-jet.
+\item $t_{\ell}\hadhad$: To enhance selection of $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay, exactly one light lepton and two opposite-sign $\had$ are selected,
+  including jets with exactly one $b$-jet.
+\item $t_{\ell}\had$: This channel is also to enhance $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay where one $\had$ fails the tau reconstruction or identification
+  criterion so that there is only one reconstructed $\had$ candidate.
+  To reduce the SM backgrounds and avoid overlaps with the final states of other ATLAS searches, exactly one $\had$ with charge the same as that assigned to the light lepton is required.
   In addition, at least two jets including exactly one $b$-jet are required.
@@
 
-The events in the hadronic channel are selected by s di-tau trigger. Further requirements are:
+The events in the hadronic channel are selected by a di-tau trigger. Further requirements are:
 %recorded by di-tau trigger, required to have both leading and subleading $\had$ passed the trigger. Further requirements are defined targeting signal decay modes:

### 2022-06-02 sections/detector.tex
Fixing the language editorial comments and update to V1.6

@@
 terms of the polar angle $\theta$ as $\eta = - \ln \tan(\theta/2)$.
-Angular separation is measured in units of $\Delta R\equiv \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.} and consists of an inner tracking detector surrounded by a thin superconducting solenoid producing a
+Angular separation is measured in units of $\Delta R\equiv \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.} and it consists of an inner tracking detector surrounded by a thin superconducting solenoid producing a
 2~T axial magnetic field, electromagnetic and hadronic calorimeters, and a muon spectrometer incorporating three large toroid magnet assemblies with eight coils each.
@@
 The calorimeters are surrounded by a muon spectrometer within a magnetic field provided by air-core toroid magnets with a bending integral of about \SI{2.5}{\tesla\metre} in the barrel and up to \SI{6.0}{\tesla\metre} in the endcaps.
-The muon spectrometer measures the trajectories of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking chambers, and is instrumented with separate trigger chambers covering $|\eta|<2.4$.
+The muon spectrometer measures the trajectories of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking chambers, and it is instrumented with separate trigger chambers covering $|\eta|<2.4$.
 A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based level-1 trigger followed by a software-based high-level trigger, is used to reduce the event rate to a maximum of around \SI{1}{\kHz} for offline storage.

### 2022-06-02 sections/introduction.tex
addressing Luca's comments to V1.4
Fixing the language editorial comments and update to V1.6

--- 2022-03-20 sections/introduction.tex
@@
 a comprehensive programme of measurements % of its properties
-has been conducted to explore this new particle. Measurements so far proved to be consistent with the Standard Model (SM) predictions. 
+has been conducted to explore this particle. Measurements so far have proved to be consistent with the Standard Model (SM) predictions. 
 However, the program is ongoing and precision measurements as well as searches for rare new physics processes beyond the Standard Model (BSM)
 are underway. One such possibility is flavour-changing neutral-current (FCNC) interactions between the Higgs boson, 
-the top quark, and an up-type quark, $tqH$ ($q=u, c$), which has been actively searched for by the ATLAS and CMS collaborations.  
+the top quark, and an up-type quark, $tqH$ ($q=u, c$), which have been sought for by the ATLAS and CMS collaborations.  
 %with increased precision and proved to be consistent with the Standard Model (SM) predictions. 
@@
 In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
-Therefore, an observation of an enhanced rate of this decay would be a clear evidence for new physics.
+An observation of an enhanced rate of this decay would be clear evidence for new physics.
 Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through this interaction would enhance
@@
 %ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
-However, these branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$ when considering beyond the SM processes.
+However, these branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$ when processes beyond the SM are included.
 Examples of these processes include: quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{ Branco:2hdm2012} with or without flavour violation,
@@
 supersymmetric models with R-parity violation~\cite{Eilam:2001dh}, composite Higgs models with partial  compositeness~\cite{Azatov:2014lha}, 
-or warped extra dimensions models with SM fermions in the bulk~\cite{Azatov:2009na}. 
+and warped extra dimensions models with SM fermions in the bulk~\cite{Azatov:2009na}. 
 % In contrast, large enhancements of these branching ratios are possible in some scenarios beyond the SM.
@@
 % In these scenarios, branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$. 
-An even larger branching ratio of  $\BR(t\to cH) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation, since a tree-level FCNC coupling is no longer forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}.
+An even larger branching ratio of  $\BR(t\to cH) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation, since in them the tree-level FCNC coupling is no longer forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}.
 %While other FCNC top couplings ($tq\gamma$, $tqZ$, $tqg$) are also enhanced in these scenarios beyond the SM, 
@@
 %production cross section of $pp\rightarrow tH$.
-The study of $pp\rightarrow tH$ process will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
+The study of $pp\rightarrow tH$ processes will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
 The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at a centre-of-mass energy of $\sqrt{s}= 13~\tev$~\cite{deFlorian:2016spz}.
@@
 In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $qH$ with a small branching ratio 
- $\BR(t\to qH)$, denoted as $\ttbar \to WbHq$\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
-$WbWb$ is used to denote $W^+b W^- \bar{b}$.}.  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
+ $\BR(t\to qH)$, denoted~\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
+$WbWb$ is used to denote $W^+b W^- \bar{b}$.} as $\ttbar \to WbHq$.  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
 the SM.
@@
 Compared to Run~1, the Run~2 searches, summarised in Table~\ref{tab:limits_summary_ref}, benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
-Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of branching ratio
-$\BR(t\to cH)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, $\BR(t\to cH)<0.16\%$ based on
+Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) on the branching ratio
+$\BR(t\to cH)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd} and $\BR(t\to cH)<0.16\%$ based on
 %signatures with two same-charge light leptons (electrons or muons) or three light leptons 
 multilepton (electron or muon) signatures resulting from 
-$H \to  WW^*, ZZ^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically~\cite{Aaboud:2018pob},
-$\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36}, and of $\BR(t\to cH)<0.19\%$ using $H\to \tau^+\tau^-$ decay in which at least
-one of $\tau$-leptons decays hadronically~\cite{fcnc36}.  
+$H \to  WW^*, ZZ^*$, $\tau^+\tau^-$ in which both $\tau$-leptons decay leptonically~\cite{Aaboud:2018pob}.
+The upper limits are set on $\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36} and $\BR(t\to cH)<0.19\%$ using the $H\to \tau^+\tau^-$ decay in which at least
+one of the $\tau$-leptons decays hadronically~\cite{fcnc36}.  
 These upper limits are derived assuming that the branching ratio $\BR(t\to uH)$ is null. Similar upper limits are obtained for $\BR(t\to uH)$ assuming $\BR(t\to cH)=0$.
 %The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
-Combining all of the ATLAS searches using 36.1~fb$^{-1}$ Run~2 data, upper limits at 95\% CL on the branching fractions are 
-set at $\BR(t\to cH)<0.11\%$ assuming $\BR(t\to uH)=0$, and $\BR(t\to uH)<0.12\%$ assuming $\BR(t\to cH)=0$~\cite{fcnc36}.
+Combining all of the ATLAS searches using 36.1~fb$^{-1}$ of Run~2 data, upper limits at 95\% CL on the branching fractions are 
+set at $\BR(t\to cH)<0.11\%$ assuming $\BR(t\to uH)=0$, and at $\BR(t\to uH)<0.12\%$ assuming $\BR(t\to cH)=0$~\cite{fcnc36}.
 
@@
 $pp \to tH$ production~\cite{Greljo:2014dka}. 
-CMS recently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
-the full Run 2 dataset. The observed (expected) upper limits on  $\BR(t\to cH)$ are $9.4\times10^{-4}(8.6\times10^{-4})$
-and are $7.9\times10^{-4}(1.1\times10^{-3})$ for $\BR{B}(t\to uH)$~\cite{CMS:2021gfa}.
+CMS subsequently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
+the full Run 2 dataset; observing (expected) upper limits on  $\BR(t\to cH)$ of $9.4\times10^{-4}\, (8.6\times10^{-4})$
+and on $\BR{B}(t\to uH)$ of $7.9\times10^{-4}\, (1.1\times10^{-3})$~\cite{CMS:2021gfa}.
 %CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.
@@
 \begin{table}[t!]
-\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to cH)$ and $\BR(t \to uH)$ obtained from ATLAS and CMS Collaborations with Run 2 data.
+\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to cH)$ and $\BR(t \to uH)$ obtained by the ATLAS and CMS Collaborations with Run 2 data.
 Each limit is obtained assuming the other branching ratio is null.}}
@@
 & Combination~\cite{fcnc36}                                               & 36.1         & $1.1 \times 10^{-3}$  & $1.2 \times 10^{-3}$  \\\midrule
-\multirow{1}{*}{CMS} 
+\multirow{2}{*}{CMS} 
 & $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
@@
 %This paper is focused on the decay mode of the Higgs boson into
-$\tau$-leptons with the complete Run~2 dataset collected in 2015-2018.
+$\tau$-leptons in the complete Run~2 dataset collected in 2015-2018.
 The corresponding integrated luminosity is 139 fb$^{-1}$.
-Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted.
+Both $\ttbar \to WbHq$ decays and $pp \to tH$ production are sought.
 The dataset is divided into several final states depending on the production mode and
@@
 either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$), but only the $\thadhad$ final state is considered
-when the top decay leptonically ($t_{\ell}$) in order to avoid overlaps with
+when the top decays leptonically ($t_{\ell}$), in order to avoid overlaps with
 other ATLAS searches~\cite{Aaboud:2018pob}. 
-Events with two hadronically decaying $\tau$-leptons without electron or muon are named hadronic channels.
+Events with two hadronically decaying $\tau$-leptons without an electron or muon are named hadronic channels.
 Events with at least one \tauhad with an additional electron or muon (corresponding to $t_{\ell}$ or $\lep$ events) are named leptonic channels.
-More signal regions (with top quark decay leptonically) are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data~\cite{fcnc36}.
-In addition, an improved treatment of misidentified $\tau$-leptons in simulation and data-driven
+More signal regions (with the top quark decaying leptonically) are exploited here than in the previous FCNC $\Htautau$ search which was conducted using the partial Run~2 dataset~\cite{fcnc36}.
+In addition, an improved treatment of misidentified $\tau$-leptons (fake) in simulation and data-driven
 fake estimations from multi-jet background is implemented.
@@
 %$$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
-Finally, a multivariate technique based on boosted decision trees, is used to discriminate between the signal and the background on the basis of their different kinematics distributions.
+Finally, a multivariate technique based on boosted decision trees is used to discriminate between the signal and the background on the basis of their different kinematical distributions.
 

### 2022-06-02 sections/objects.tex
Fixing the language editorial comments and update to V1.6

@@
 %To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have \pt 1~GeV above the threshold.
-To further reduce the background from non-prompt leptons, photon conversions and hadrons, lepton candidates are also required to be isolated 
-in the tracker and in the calorimeter.
-A track- and cluster-based lepton isolation criterion is defined by calculating the quantity $I_R = \sum \pt^{\textrm{trk}}$ and $E_R = \sum E^{\textrm{clst}}$, where
-the scalar sum includes all tracks and energy deposits (excluding the lepton candidate itself) within the cone defined by $\Delta R<0.2 (0.3)$ around the %axis
+To further reduce the background from non-prompt leptons mostly originating from heavy-flavour hadron decays, photon conversions and misidentified hadrons,
+lepton candidates are also required to be isolated in the tracker and in the calorimeter.
+A track- and cluster-based lepton isolation criterion is defined by calculating the quantities $I_R = \sum \pt^{\textrm{trk}}$ and $E_R = \sum E^{\textrm{clst}}$, where
+the scalar sum includes all tracks $\pt^{\textrm{trk}}$ and cluster energy deposits $E^{\textrm{clst}}$ (excluding the lepton candidate itself)
+within the cone defined by $\Delta R<0.2~(0.3)$ around the %axis
 direction of the electron (muon). The electron (muon) candidates are required to satisfy both
@@
 
-Tight isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions based on a trained isolation boosted decision tree \texttt{PromptLeptonVeto}(PLIV), which is used to identify non-prompt light leptons using lifetime information associated with a track jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}.
+Tight isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions based on a trained isolation boosted decision tree (BDT)
+\texttt{PromptLeptonVeto} (PLIV), which is used to identify non-prompt light leptons using lifetime information associated with a track jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}.
 These additional reconstructed charged particle tracks inside the jet can be
-used to increase the accuracy for identifying the displaced decay vertex of heavy flavour ($b$, $c$) hadrons that produced non-prompt leptons.
-The tight working points are used for high $\pt$ lepton ($>20~\GeV$).
-The scale factors for the efficiencies of the tight \texttt{PLIV} working points are measured using the tag and probe method
+used to increase the efficiency for identifying the displaced decay vertex of heavy flavour ($b$, $c$) hadrons that produced non-prompt leptons.
+The tight working points are used for high $\pt$ leptons ($>20~\GeV$).
+The scale factors for the efficiencies of the tight \texttt{PLIV} working points are measured using the tag and probe method~\cite{PERF-2016-01}
 with $Z\rightarrow \ell^+\ell^-$ events. These scale factors have also been checked for the electron or muon from the tau decay
-using $Z\rightarrow\tau\tau\rightarrow e\mu4\nu$ samples, which is consistent at 2\% level. To be conservative, an
+using $Z\rightarrow\tau\tau\rightarrow e\mu4\nu$ samples, which are consistent at the 2\% level. To be conservative, an
 additional uncertainty of $\pm 2\%$ is considered for the PLIV efficiency for the tau-lepton in the lepton+$\thad$ channels.
@@
 using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject jet backgrounds.
-Three working points labelled loose, medium and tight are defined, and correspond to different $\had$ identification efficiency values, with the efficiency designed to be independent of $\pt$.
+Three working points, labelled loose, medium and tight, are defined and correspond to different $\had$ identification efficiency values, with the efficiency designed to be independent of $\pt$.
 The $\Htautau$ search uses the medium
-working point for the nominal selection.
+working point for the $\had$ selection.
 %, while the loose working point is used for background estimation.
@@
 In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
-is discarded if the jet is not $b$-tagged, otherwise the electron is removed.
+is discarded if the jet is not $b$-tagged; otherwise the electron is removed.
 If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
@@
 Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
-and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
+and in such cases the jet is removed and the muon retained. Such jets are characterised by having very 
 few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.2$ are rejected
@@
 In order to avoid double-counting of $\tauhad$ as jets, the closest jet whose axis is
-within ${\Delta}R = 0.2$ of a $\tauhad$ is discarded if the jet is not $b$-tagged, otherwise the $\tauhad$ is removed. 
+within ${\Delta}R = 0.2$ of a $\tauhad$ is discarded if the jet is not $b$-tagged; otherwise the $\tauhad$ is removed. 
 % TEXT FROM BOYANG. NEED TO RECHECK WHAT WE HAVE ABOVE IS ACCURATE

### 2022-06-02 sections/simulated_samples.tex
Fixing the language editorial comments and update to V1.6

@@
 An overview of the Monte Carlo (MC) generators used for the main signal and background samples is summarized in Table~\ref{mob}.
-Samples of simulated $\ttbar \to WbHq$ ($tt(qH)$) events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
+Samples of simulated $\ttbar \to WbHq$ ($tt(qH)$) events were generated with the next-to-leading order (NLO) generator\footnote{In the following, 
 the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element (ME) calculation 
@@
 initial- and final-state radiation, referred to as the tune, was used.
-The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
+The signal sample is normalised to the same total cross section as is used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below)
 assuming a benchmark branching ratio of $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$.
@@
 %hadronisation, and the underlying event with the A14 tune.
-Depending on either up quark or charm quark involved in the FCNC production, the effective Lagrangian of $tqH$ interaction are parametrised using
-dim-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 0.711 pb and $\sigma(cg\to tH)$ = 0.103 pb using $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$ as benchmark.
+Depending on whether the up quark or the charm quark is involved in the FCNC production, the effective Lagrangian of the $tqH$ interaction is parametrised using
+dimension-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 0.711 pb and $\sigma(cg\to tH)$ = 0.103 pb using $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$ as the benchmark.
 
-The nominal sample used to model the $\ttbar$ background was generated with the NLO generator {\powheg}~v2
+The sample used to model the $\ttbar$ background was generated with the NLO generator {\powheg}~v2
 %\cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
 using the NNPDF3.0 NLO PDF set. The {\powheg} model parameter $h_{\textrm{damp}}$, which controls 
-matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, was set to 1.5 times the top-quark mass. 
+matrix element to parton shower matching and regulates the high-$\pt$ radiation, was set to 1.5 times the top-quark mass. 
 The parton showers, hadronisation, and underlying event were modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
@@
 
-Samples of single-top-quark events corresponding to the $t$-channel production mechanism were generated with the 
-{\powheg}~v2~\cite{Frederix:2012dh} generator, using the 4F scheme  for the NLO matrix-element calculations
+Samples of single-top-quark events corresponding to the $t$-channel production mechanism were generated with a  
+{\powheg}~v2 generator~\cite{Frederix:2012dh}, using the 4F scheme  for the NLO matrix-element calculations
 and the corresponding NNPDF3.0 NLO set of PDFs.
@@
 the diagram removal scheme~\cite{Frixione:2005vw}.
-The parton showers, hadronisation and the underlying event were modelled using {\pythia}~8.230~\cite{Sjostrand:2006za} using the A14 tune and the NNPDF2.3 LO PDF set.
+The parton showers, hadronisation and underlying event were modelled using {\pythia}~8.230~\cite{Sjostrand:2006za} using the A14 tune and the NNPDF2.3 LO PDF set.
 %with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set %in combination with the Perugia 2012 tune~\cite{Skands:2010ak}.
@@
 at NLO and up to three partons at LO using the same procedure as for the $W/Z$+jets samples. 
-The final states simulated require one of the bosons to decay leptonically and the other hadronically.
+The final states that were simulated require one of the bosons to decay leptonically and the other hadronically.
 All diboson samples are normalised to their NLO theoretical cross sections provided by {\sherpa}.
 
-Samples of $\ttbar V$ and $\ttbar H$ events were generated with {\amcatnlo}~2.2.1, using NLO matrix elements and the NNPDF3.0 NLO PDF set,
+Samples of $\ttbar V$ ($V=W\, Z$ boson) and $\ttbar H$ events were generated with {\amcatnlo}~2.2.1, using NLO matrix elements and the NNPDF3.0 NLO PDF set,
 and interfaced to {\pythia}~8.210 with the NNPDF2.3 LO PDF set and the A14 tune. 
@@
 
-Samples of $WH$ and $ZH$, collectively referred to as $VH$ are generated using {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
+Samples of $WH$ and $ZH$, collectively referred to as $VH$, are generated using {\powheg}~v2\cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
 and interfaced to {\pythia}~8.210 with the PDF4LHC15 PDF set and the AZNLO tune.
-The contribution of $tH$ associated production is also considered as part of SM Higgs background.
+The contribution of $tH$ associated production is also considered as part of the SM Higgs background.
 The sample is generated using {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca} and interfaced with {\pythia}~8.210 with CT10PDF
-and A14 tune. The MC predictions are normalised using the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.
+and the A14 tune. The MC predictions are normalised using the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.
 The contribution of triboson production is found to be negligible.
@@
 \centering
-\caption{Overview of the MC generators used for the main signal and background samples.
-including the matrix element (ME), parton shower (PS), parton distribution function set (PDF), and cross-section calculation order (Order).}
+\caption{Overview of the MC generators used for the main signal and background samples, including the matrix element (ME), parton shower (PS), parton distribution function set (PDF), and cross-section calculation order (Order).}
 \begin{tabular}[h]{l|c|c|c|c|c|c}

### 2022-06-02 sections/statistical_analysis.tex
Fixing the language editorial comments and update to V1.6

--- 2022-03-12 sections/statistical_analysis.tex
@@
 
-The final discriminant distributions are the BDT outputs of all the considered analysis regions. They are jointly analysed to test for the 
-presence of a signal. The BDT distributions are binned to maximize the signal sensitivity.
+The final discriminant distributions are the BDT outputs of all the considered analysis regions. They are jointly analysed for the 
+presence of a signal. The BDT distributions are binned to maximize sensitivity to the signal.
 The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
@@
 on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $tH$ and $tt(qH)$ signal events
-normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$,
+normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$;
 and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations.
-Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
-All nuisance parameters are subject to Gaussian constraints in the likelihood.
+The $pp\rightarrow tH$ production cross section is related to $\BR(t\rightarrow qH)$ through their dimension-6 operators~\cite{fcnc_production_theory}.
+It follows that the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
+All nuisance parameters are subject to Gaussian constraints on the likelihood.
 For a given value of $\mu$, the nuisance parameters $\theta$ allow variations of the expectations for signal and background
-according to the corresponding systematic uncertainties, and their fitted values result in the deviations from
+consistent with the corresponding systematic uncertainties, and their fitted values result in the deviations from
 the nominal expectations that globally provide the best fit to the data.
 This procedure allows a reduction of the impact of systematic uncertainties on 
-the search sensitivity by taking advantage of the highly populated background-dominated bins included in the likelihood fit.
+the search's sensitivity by taking advantage of the highly populated background-dominated bins included in the likelihood fit.
 %To verify the improved background prediction, fits under the background-only hypothesis are performed, 
@@
 %using kinematic variables other than the ones used in the fit. 
-Statistical uncertainties in each bin of the predicted final discriminant distributions are taken into account by dedicated parameters in the fit.     
+Statistical uncertainties in each bin of the predicted final discriminant distributions are taken into account through dedicated parameters in the fit.     
 The best-fit $\BR(t\to qH)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
-hypothesis, maximising the likelihood function ${\cal L}(\mu,\theta)$ over $\mu$ and $\theta$.
+hypothesis, and maximising the likelihood function ${\cal L}(\mu,\theta)$ over $\mu$ and $\theta$.
 
-The fitting procedure was initially validated through extensive studies using pseudo data, defined as the sum of all predicted backgrounds 
-plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
+The fitting procedure was initially validated through extensive studies using pseudodata (which is defined as the sum of all predicted backgrounds 
+plus an injected signal of variable strength) as well as by performing fits to real data where bins of the final discriminant variable with 
 a signal contamination above 10\% are excluded (referred to as blinding requirements).
@@
 nuisance parameters before and after removal of the blinding requirements, and their values are found to be consistent. In addition, it is verified that the 
-fit is able to correctly determine the strength of a simulated signal injected into the real data.
+fit is able to determine the strength of a simulated signal injected into the real data.
 
@@
 where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
-maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and ${\hat{\theta}}_\mu$ are the values of the
+maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and the ${\hat{\theta}}_\mu$ are the values of the
 nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
@@
 %In the absence of signal,
-Exclusion limits are set on $\mu$ , and thus on
-$\BR(t\to qH)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
+Exclusion limits are set on $\mu$ and thus on
+$\BR(t\to qH)$, derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
 For a given signal scenario, values of the $\BR(t\to qH)$ yielding CL$_{\textrm{s}} < 0.05$,

### 2022-06-02 sections/strategy_Htautau.tex
Fixing the language editorial comments and update to V1.6

@@
 %at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
-If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon, together with significant $\met$ is also expected.
+If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon, together with significant $\met$, is also expected.
 In a significant fraction of the events, the lowest $\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
@@
 %some signal events mixed with production mode having only three reconstructed jets.
-In order to optimise the sensitivity of the search, the selected events are categorised into seven signal regions(SRs) based on the number of light leptons,
-$\had$ candidates, and on the number of light flavoured jets:
+In order to optimise the sensitivity of the search, the selected events are categorised into seven signal regions (SRs) based on the  number of light leptons,
+$\had$ candidates, and number of light flavoured jets:
 %$t_{\ell}\hadhad$, $t_{\ell}\had$(1j and 2j), $t_{\ell}\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}. 
@@
 \caption{Overview of the signal regions (SR), validation region (VR), and $t\bar{t}$ control regions (CRtt) used for the fake tau scale factor derivation in the leptonic channels.
-Leptons are required to have either same-sign (SS) or opposite-sign (OS) in each region.}
+Leptons are required to have either same sign (SS) or opposite sign (OS) in each region.}
 \label{tab:srcr}
@@
 %of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay %is missing or not (events with exactly three jets or at least four jets).
-This event categorisation is primarily motivated by optimizing the sensitivity in each signal region that targets either leptonic or hadronic top-quark
-decays as well as the Higgs decays into either $\lephad$ or $\hadhad$ final states.   
+This event categorisation is primarily used to optimize the sensitivity in each signal region that targets either leptonic or hadronic top-quark
+decays as well as the Higgs decays into either the $\lephad$ or $\hadhad$ final states.   
 %The event kinematic reconstruction is used in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.
-The contribution of background to the signal regions of the $t_h\hadhad$ and $t_h\lephad$ channels is reduced by having a kinematic constraints on the di-tau mass and the $\met$ in the event~\cite{Chen:2015nta}.
+The contribution of background to the signal regions of the $t_h\hadhad$ and $t_h\lephad$ channels is reduced by having kinematic constraints on the di-tau mass and the $\met$ in the event~\cite{Chen:2015nta}.
 
@@
 %is considered as the $q$-jet 
-Events should contain 4 jets, with the one having the smallest angular separation with respect to the visible di-tau system being labelled as  $q$-jet since the FCNC top decay products are likely boosted closer together.
-If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
+Events should contain 4 jets, with the one having the smallest angular separation with respect to the visible di-tau system being labelled the $q$-jet since the FCNC top decay products are likely boosted closer together.
+If there are more than two jets besides the $q$- and $b$-jet, the jets from the $W$ boson decay are chosen from the combination
 with the invariant mass closest to the $W$ boson mass. There is the possibility that one of the jets fails the $\pt$ requirement and is not reconstructed.
-These kinds of events will fall into the $t_hH$ final state.
+These kinds of events will produce the $t_hH$ final state.
 %while the FCNC top resonance is
@@
 There are three jets coming from top hadronic decay including the $b$-jet and a pair of opposite-sign $\had$ from the Higgs boson decay, where
-both $t_h$ and $H$ can be reconstructed.  
+both the $t_h$ and $H$ can be reconstructed.  
 %. So a Higgs resonance formed by the taus and a top resonance formed by
@@
 distribution of the simulated  $tqH$ signal events, while the resolution on the measured $\met$ is parameterised as a linear function of 
-$\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
+$\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $E_{\text{T}}$ values of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
 After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
-$\pt$ of the parent top quarks are determined with better resolution in the signal events.
+$\pt$ values of the parent top quarks are determined with better resolution in the signal events.
 
-For the  $t_{\ell}t(qH)$ and $t_{\ell}H$ events where $W$ boson from $t\to W b$ decay decays leptonically,
+For the  $t_{\ell}t(qH)$ and $t_{\ell}H$ events where the $W$ boson from $t\to W b$ decay decays leptonically,
 %has a large momentum and the flying direction is unknown.
-the kinematic fit is no longer feasible due to extra neutrino from $W\rightarrow \ell\nu$ decay. The kinematic variables are calculated using the visible
+the kinematic fit is no longer feasible due to the neutrino from the $W\rightarrow \ell\nu$ decay. The kinematic variables are calculated using the visible
 objects only. After the event reconstruction, a number of variables are used to discriminate the signal from the background using a multivariate analysis described

### 2022-06-02 sections/systematic_uncertainties.tex
Fixing the language editorial comments and update to V1.6

@@
 as appropriate. The following sections describe the systematic uncertainties considered.
-Table~\ref{tab:had_sys_impact} shows a summary of the dominant systematics uncertainties on the measured $\BR(t\to qH)$ branching ratio
-resulting from the fits to the data in the signal regions as described in Section~\ref{sec:result}.
+Table~\ref{tab:had_sys_impact} shows a summary of the dominant systematic uncertainties on the measured $\BR(t\to qH)$ branching ratio
+resulting from the fits to the data on the signal regions as described in Section~\ref{sec:result}.
 
@@
 Uncertainties associated with electrons, muons, and $\had$ candidates arise from the trigger, reconstruction,  
-identification and isolation (in the case of electrons and muons) efficiencies, as well as the momentum scale and resolution. 
+identification and, in the case of electrons and muons, isolation efficiencies, as well as the momentum scale and resolution. 
 These are measured using $Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events ($\ell =e, \mu$)~\cite{ATLAS-CONF-2016-024,Aad:2016jkr} 
@@
 
-Uncertainties associated with jets arise from the jet energy scale
-and resolution, and the efficiency to pass the JVT requirements. 
-The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pile-up treatment, 
+Uncertainties associated with jets arise from the jet energy scale (JES)
+and resolution (JER) and the efficiency to pass the JVT requirements. 
+The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pile-up treatment
 is split into 43 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}. The total JES uncertainty is
 below 5\% for most jets and below 1\% for central jets with $\pt$ between 300 GeV and 2 TeV. The difference between the JER
-in data and MC is represented by one NP. It is applied on the MC by smearing the jet $\pt$ within the prescribed uncertainty.
+in data and in MC is represented by one nuisance parameter (NP). It is applied to the MC by smearing the jet $\pt$ within the prescribed uncertainty.
 
@@
 Efficiencies to tag $b$-jets and $c$-jets in the simulation are corrected to match the efficiencies in data by $\pt$-dependent factors,
-whereas the light-jet efficiency is scaled by $\pt$- and $\eta$-dependent factors.
+while the light-jet efficiency is scaled by $\pt$- and $\eta$-dependent factors.
 The $b$-jet efficiency is measured in a data sample enriched in $\ttbar$ events~\cite{Aad:2019epj79}, %EPJ C79(2019)970 {Aaboud:2018xwy},
@@
 The light-jet efficiency is measured in a multi-jet data sample enriched in light-flavour jets~\cite{ATLAS-CONF-2018-006}.
-The uncertainties in these scale factors include a total of 44 independent sources affecting $b$-jets, 19 source affecting $c$-jets, and 19 sources affecting light-jets. 
+The uncertainties in these scale factors include a total of 44 independent sources affecting $b$-jets, 19 sources affecting $c$-jets, and 19 sources affecting light-jets. 
 These systematic uncertainties are taken as uncorrelated between $b$-jets, $c$-jets, and light-jets.
@@
 However, this uncertainty is highly correlated with the luminosity uncertainty and may be an overestimate.
-Scale factors are applied to reweight simulated events in order to obtain the pile-up distribution corresponding to data.
-An uncertainty on these reweighting scale factors is estimated by varying the reweighting to the profile in data within its uncertainties.
+Scale factors are applied to reweight simulated events in order to obtain the pile-up distribution corresponding to the data.
+An uncertainty on these reweighting scale factors is estimated by varying the reweighting upon the profile in data within its uncertainties.
 %considered based on the disagreement between the instantaneous luminosity in data and in simulation.
@@
 
-A number of sources of systematic uncertainty affecting the modelling of $t\bar{t}$+jets are considered: the choice of the renormalisation and factorisation scale in the matrix-element calculation, the choice of the matching scale when matching the matrix elements to the parton show generator, the uncertainty in the value of $\alpha_s$ when modeling initial-state radiation (ISR), the choice of the renormalisation scale when modeling final-state radiation (FSR).
+A number of sources of systematic uncertainty affecting the modelling of $t\bar{t}$+jets are considered: the choice of the renormalisation and factorisation scale in the matrix-element calculation, the choice of the matching scale when matching the matrix elements to the parton shower generator, the uncertainty on the value of $\alpha_s$ when modeling initial-state radiation (ISR), and
+the choice of the renormalisation scale when modeling final-state radiation (FSR).
 %%An uncertainty of  6\% is assigned to the inclusive $\ttbar$ production
@@
 
-The $h_{\mathrm{damp}}$ parameter (which controls the amount of radiation produced by the parton shower in
-POWHEG-BOX v2) is set to 1.5$m_t$ in the nominal case. Alternative samples are generated with $h_{\mathrm{damp}}$=3$m_t$. The
-difference between two samples is treated as a systematic named as ``$t\bar{t}$ $h_{\mathrm{damp}}$''. 
+The $h_{\mathrm{damp}}$ parameter, which controls the amount of radiation produced by the parton shower in
+\powheg~v2, is set to 1.5$m_t$ in the $t\bar t$ sample. Alternative sample is generated with $h_{\mathrm{damp}}$=3$m_t$. The
+difference between two samples is treated as a systematic called ``$t\bar{t}$ $h_{\mathrm{damp}}$''. 
 %The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
@@
 The latter uses the MMHT2014 LO~\cite{Harland-Lang:2014zoa} PDF set in combination with the H7UE tune~\cite{Bellm:2015jjp}.
-The uncertainty in the modelling of additional radiation from the PS are assessed by
+The uncertainty on the modelling of additional radiation from the PS is assessed by
 varying the corresponding parameter of the A14 set~\cite{ATL-PHYS-PUB-2016-004} and by varying the radiation renormalisation and factorisation scales
@@
 
-Another significant background in hadronic channel stems from the $Z\rightarrow \tau\tau$ samples, several sources of uncertainty are
-considered for these samples: the PDF variation considering the standard deviation of the 100 NNPDF replicas event weights
-of NNPDF3.0nnlo~\cite{Ball:2015NNPDF} PDF
-set used in Sherpa, renormalisation ($\mu_{R}$) and factorisation scales ($\mu_{F}$), jet-to-parton matching uncertainty, resummation scale uncertainty,
-variation in the choice of $\alpha_{S}$, alternative PDF variation evaluated comparing predictions from NNPDF3.0nnlo PDF set (nominal)
-with MMHT2014nnlo68cl and CT14nnlo~\cite{Lai:2010vv,Gao:2013xoa} PDF sets.
+Another significant background to the hadronic channel stems from the $Z\rightarrow \tau\tau$ samples. Several sources of uncertainty are
+considered for these samples: the PDF variation, which is evaluated by considering the standard deviation
+produced by 100 NNPDF replicas event weights of NNPDF3.0nnlo~\cite{Ball:2015NNPDF} PDF set used in Sherpa,
+renormalisation ($\mu_{R}$) and factorisation scales ($\mu_{F}$), jet-to-parton matching uncertainty, resummation scale uncertainty,
+variation in the choice of $\alpha_{S}$, and alternative PDF use, which is evaluated by comparing predictions from NNPDF3.0nnlo PDF set (nominal)
+with those of MMHT2014nnlo68cl and CT14nnlo~\cite{Lai:2010vv,Gao:2013xoa} PDF sets.
 
@@
 and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated to be approximately 30\% by taking the maximum
-difference between the data and total background prediction in the different analysis regions considered, but requiring exactly zero, one, and two $b$-jets.
-This is mainly driven by the disagreement between MC simulation in the $V$+jets regions with high multiplicity of jets.  
+difference between the data and the total background prediction in the different analysis regions considered, but requiring exactly zero, one, and two $b$-jets.
+This is mainly driven by the disagreement between MC simulations in the $V$+jets regions with a high multiplicity of jets.  
 %Agreement between data and predicted background 
@@
 Uncertainties affecting the modelling of the single-top-quark background include a 
-$+5\%$/$-4\%$ uncertainty of the total cross section estimated as a weighted average 
+$+5\%$/$-4\%$ uncertainty on the total cross section, which is estimated as a weighted average 
 of the theoretical uncertainties in $t$-, $tW$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
-Additional uncertainties associated with the parton shower, hadronisation and ISR/FSR radiations are also considered using the same procedure
-as in $t\bar t$.
-Uncertainties of the diboson background normalisation include variations of the renormalization and factorization scale, NNPDF3.0nnlo variations and $\alpha_{S}$ variations.
-Uncertainties of the $\ttbar V$ and $\ttbar H$ cross sections are 12\% and $+5.8\%-9.2\%$, respectively,
-from the uncertainties of their respective NLO theoretical cross sections~\cite{ttZRun2}.
+Additional uncertainties associated with the parton shower, hadronisation and ISR/FSR radiations are also considered by using the same procedure
+as for $t\bar t$.
+Uncertainties on the diboson background normalisation include variations of the renormalization and factorization scales, NNPDF3.0nnlo variations and $\alpha_{S}$ variations.
+Uncertainties of the $\ttbar V$ and $\ttbar H$ cross sections are 12\% and [$+5.8\%/-9.2\%$], respectively,
+from the uncertainties on their respective NLO theoretical cross sections~\cite{ttZRun2}.
 
@@
 different fake tau sources and different $\pt$ slices. The uncertainties on the MC modelling of the various processes used for
-evaluation of the fake factors in the CRtt's are treated as fully correlated in the fit.
-The uncertainty of the ABCD method is applied on the normalisation factors for muon and electron respectively including both,
+evaluation of the fake factors in the CRtt are treated as fully correlated in the fit.
+The uncertainty on the ABCD method is applied to the normalisation factors for muons and electrons,including both
 its statistical fluctuation and the differences in the normalisation factors between the leptonic channels.
-The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.
+The uncertainties on the fake factor method applied to the hadronic channel includes statistical uncertainties on each fake factor and
+different sets of fake factors derived from different signal-depleted CRs.
 %The uncertainties on the MC modelling of the various processes used for
@@
 Several normalisation and shape uncertainties are taken into account and are treated as fully correlated for the $\Hq$ and $pp\to tH$ signals.
-Uncertainties of the Higgs boson branching ratios are taken
+Uncertainties on the Higgs boson branching ratios are taken
 %from the measured values in Ref.~\cite{Zyla:2020zbs}.
-into account following the recommendation in Ref.~\cite{deFlorian:2016spz}.
-The uncertainty of ISR, FSR, scale and PDF are considered and are treated fully correlated in all SRs. The parton shower uncertainties are estimated by comparing
-the nominal to an alternative sample interfaced with {\herwig7}.
+into account by following the recommendation in Ref.~\cite{deFlorian:2016spz}.
+The uncertainty due to ISR, FSR, scale and PDF are considered and are treated as fully correlated in all SRs. The parton shower uncertainties are estimated by comparing
+the nominal sample to an alternative sample interfaced with {\herwig7}.
 %the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 

### 2022-06-02 sections/tau_FF_appendix.tex
Fixing the language editorial comments and update to V1.6

--- 2022-04-16 sections/tau_FF_appendix.tex
@@
-\section{Tau fake scale factor calibration in the ttCRs}
+\section{Tau fake scale factor calibration in the CRtt}
 \label{sec:tauFF_appendix}
 
-Figure~\ref{fig:ttCR_mtt} shows the post-fit of the leading $\thad$ $\pt$ in the ttCRs, which shows a good agreement between the data and the fitted background model.
-Table~\ref{tab:ff1_summary} and~\ref{tab:ff2_summary} are summarized the fake scale factors of 1-prong and 3-prong taus
-derived from the ttCRs including both statistical and systematic uncertainties.
+Figure~\ref{fig:ttCR_mtt} presents the post-fit distributions of the leading $\thad$ $\pt$ in the CRtt. These show good agreement between the data and the fitted background model.
+Tables~\ref{tab:ff1_summary} and~\ref{tab:ff2_summary} summarize the fake scale factors of 1-prong and 3-prong taus
+derived from the CRtt including both statistical and systematic uncertainties.
 
@@
 \end{tabular}
-\caption{Leading $\thad$ $\pt$  distributions obtained after the fit to data (``Post-Fit'') for the $\thad$ fake scale factors in the following ttCRs:
+\caption{Leading $\thad$ $\pt$  distributions obtained after the fit to data (``Post-Fit'') for the $\thad$ fake scale factors in the following CRtt:
   $t_{\ell}t_{h}$2b$\thad$-2j OS (a), $t_{\ell}t_{h}$2b$\thad$-2j SS (b), $t_{\ell}t_{h}$2b$\thad$-3j OS (c), $t_{\ell}t_{h}$2b$\thad$-3j SS (d),
@@
   The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
-  Overflow events are included in the last bin. The lower panels show the data to prediction ratio.}
+  Overflow events are included in the last bin. The lower panels show the data-to-prediction ratio.}
 \label{fig:ttCR_mtt}
@@
 \begin{table}
-\caption{ Summary of fake tau (1-prong) scale factors derived in the ttCRs. The numbers are shown as: nominal values, statistical, and systematics erros. }
+\caption{ Summary of fake tau (1-prong) scale factors derived in the CRtt. The numbers are shown as: central values, statistical uncertainties, and systematics uncertainties. }
 \begin{center}
@@
 \begin{table}
-\caption{ Summary of fake tau (3-prong) scale factors derived in the ttCRs. The numbers are shown as: nominal values, statistical, and systematics erros. }
+\caption{ Summary of fake tau (3-prong) scale factors derived in the CRtt. The numbers are shown as: central values, statistical uncertainties, and systematics uncertainties. }
 \begin{center}

### 2022-06-03 ANA-TOPQ-2019-17-PAPER-metadata.tex
preparing draft 2
minor update to V2.0

@@
 % Comment or remove in final version.
-\AtlasVersion{1.6}
+\AtlasVersion{2.0}
 % Abstract - % directly after { is important for correct indentation
 \AtlasAbstract{%
-A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, another up-type quark ($q=u, c$), and a
+A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, another up-type quark ($q=u,\, c$), and a
 Standard Model (SM) Higgs boson decaying into a $\tau$-lepton pair ($H\rightarrow \tau^+\tau^-$) is presented.
@@
 The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ 
-with an additional lepton (e,$\mu$),
+with an additional lepton (e, $\mu$),
 as well as multiple jets. Event kinematics are used to separate signal from the background through a multivariate discriminant.  
@@
 % Comment deadline
-\AtlasCoverCommentsDeadline{9 June 2022}
+\AtlasCoverCommentsDeadline{14 June 2022}
 

### 2022-06-06 hepdata/run.sh
add hepdata

@@ -1,0 +1,22 @@
+cp Wilson.png				             thumb_Wilson.png				                                        
+cp reg1l1tau1b2j_ss_BDT_post.png		 thumb_reg1l1tau1b2j_ss_BDT_post.png		                            
+cp reg1l2tau1bnj_os_pt_prefit.png		 thumb_reg1l2tau1bnj_os_pt_prefit.png		                            
+cp reg2mtau1b3jos_BDT_post.png		     thumb_reg2mtau1b3jos_BDT_post.png		                        
+cp tcH_tuH.png                           thumb_tcH_tuH.png  
+cp reg1l1tau1b1j_ss_BDT_post.png		 thumb_reg1l1tau1b1j_ss_BDT_post.png		                            
+cp reg1l1tau1b2j_ss_pt_prefit.png		 thumb_reg1l1tau1b2j_ss_pt_prefit.png		                            
+cp reg1l2tau1bnj_ss_BDT_post.png		 thumb_reg1l2tau1bnj_ss_BDT_post.png		                            
+cp reg2mtau1b3jos_pt_prefit.png		     thumb_reg2mtau1b3jos_pt_prefit.png		                                                 
+cp reg1l1tau1b1j_ss_pt_prefit.png		 thumb_reg1l1tau1b1j_ss_pt_prefit.png		                            
+cp reg1l1tau1b3j_os_BDT_post.png		 thumb_reg1l1tau1b3j_os_BDT_post.png		                            
+cp reg1l2tau1bnj_ss_pt_prefit.png		 thumb_reg1l2tau1bnj_ss_pt_prefit.png		                            
+cp reg2mtau1b3jss_BDT_post.png		     thumb_reg2mtau1b3jss_BDT_post.png		                        
+cp tuH_limit.png                         thumb_tuH_limit.png    
+cp reg1l1tau1b2j_os_BDT_post.png		 thumb_reg1l1tau1b2j_os_BDT_post.png		                            
+cp reg1l1tau1b3j_os_pt_prefit.png		 thumb_reg1l1tau1b3j_os_pt_prefit.png		                            
+cp reg2mtau1b2jos_BDT_post.png		     thumb_reg2mtau1b2jos_BDT_post.png		                        
+cp reg2mtau1b3jss_pt_prefit.png          thumb_reg2mtau1b3jss_pt_prefit.png                   
[…]

### 2022-06-29 ANA-TOPQ-2019-17-PAPER-metadata.tex
revised to V2.1

@@
 \AtlasTitle{Search for flavour-changing neutral current interactions of the top quark and the Higgs
-boson in events with a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.10em}}
+boson in events with a pair of $\tau$-leptons in $pp$ collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.10em}}
 % Draft version:
@@
 % Comment or remove in final version.
-\AtlasVersion{2.0}
+\AtlasVersion{2.1}
 % Abstract - % directly after { is important for correct indentation
@@
 The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ 
-with an additional lepton (e, $\mu$),
+with an additional lepton ($e$, $\mu$),
 as well as multiple jets. Event kinematics are used to separate signal from the background through a multivariate discriminant.  
@@
 and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
-Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.4 \times 10^{-4}\, (4.8^{+2.2}_{-1.4}\times 10^{-4})$
+The observed (expected) 95\% CL upper limits set on the $t\to cH$ and $t\to uH$ branching ratios are $9.4 \times 10^{-4}\, (4.8^{+2.2}_{-1.4}\times 10^{-4})$
 and $6.9\times 10^{-4}\, (3.5^{+1.5}_{-1.0}\times 10^{-4})$, respectively. 
 The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
-the effective $tqH$ couplings are $C_{c\phi} <1.35\, (0.97)$ and $C_{u\phi} <1.16\, (0.82)$, respectively.}%for the new physics scale $\Lambda$ at 1~TeV, respectively.} 
+the effective $tqH$ couplings are $C_{c\phi} <1.35\, (0.97)$ and $C_{u\phi} <1.16\, (0.82)$.}%for a new-physics scale $\Lambda$ of 1~$\tev$, respectively.} 
 %$|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
@@
 %\AtlasCoverSupportingNote{Combination of $\ttbar \to WbHq$ searches}{https://cds.cern.ch/record/2312520/}
-\AtlasCoverSupportingNote{Search for flavor-changing neutral currents tHq interactions with, $H \to \tau^+\tau^-$}{https://cds.cern.ch/record/2687866}
+\AtlasCoverSupportingNote{Search for flavor-changing neutral currents $tqH$ interactions with, $H \to \tau^+\tau^-$}{https://cds.cern.ch/record/2687866}
 %

### 2022-06-29 sections/conclusion.tex
revised to V2.1

@@
 A search for flavour-changing neutral current processes involving a top quark, another up-type quark ($q=u, c$), and a SM Higgs boson is presented. 
-FCNC $tqH$ interaction is sought both in the $t\bar{t}$ decay mode, where one top quark decays via SM processes and the other one decays through $t\rightarrow qH$, and in the production mode ($pp\rightarrow tH$) with a single top quark produced via the
-FCNC interaction where $t\to Wb$.
+The search uses 139 fb$^{-1}$ of 13~\TeV\ $pp$ collisions recorded by the ATLAS detector at the LHC.
+Evidence of FCNC $tqH$ interactions is sought in both the $t\bar{t}$ decay mode, where one top quark decays via SM processes and the other one decays through $t\rightarrow qH$, and the production mode ($pp\rightarrow tH$), where a single top quark produced via the
+FCNC interaction decays as $t\to Wb$.
 %The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$.
@@
 No significant excess of events above the background expectation is found.
-A slight excess of data is observed above background with a significance of 2.3$\sigma$. Upper limits at the
+A slight excess of data is observed above background, with a significance of 2.3$\sigma$. Upper limits at the
 95\% confidence level are set on the $t\to qH$ branching ratios and the corresponding
@@
 %about a factor of 2 improvement to 95\% CL upper limits on the $t\to Hq$ branching ratios are reported in Table~\ref{tab:limits_summary}, along with the Wilson coefficients with respect to the previous partial run-2 results~\cite{Aaboud2019SearchFT}.
-Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.4\times10^{-4}$ ($4.8^{+2.2}_{-1.4}\times10^{-4}$) and $6.9\times10^{-4}$ ($3.5^{+1.5}_{-1.0}\times10^{-4}$).
+The observed (expected) 95\% CL upper limits set on the $t\to cH$ and $t\to uH$ branching ratios are $9.4\times10^{-4}$ ($4.8^{+2.2}_{-1.4}\times10^{-4}$) and $6.9\times10^{-4}$ ($3.5^{+1.5}_{-1.0}\times10^{-4}$), respectively.
 %The observed (expected) upper limits on the D6 Wilson coefficients from the combination of the searches are set to $C_{c\phi}<1.38\,(0.97)$ and $C_{u\phi}<1.18\,(0.83)$, respectively.
 The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
-the effective $tqH$ couplings for a new physics scale $\Lambda$ of 1~TeV are $C_{c\phi} <1.35\, (0.97)$ and $C_{u\phi} <1.16\, (0.82)$, respectively.
+the effective $tqH$ couplings, for a new-physics scale $\Lambda$ of 1~\TeV, are $C_{c\phi} <1.35\, (0.97)$ and $C_{u\phi} <1.16\, (0.82)$.
 %These results improve significantly upon previous ATLAS and CMS limits on the $t\rightarrow Hq$ branching ratios.
-These results improve significantly upon the previously published ATLAS studies in this channel and provide more stringent limits than the ATLAS  $t\rightarrow qH$ combination~\cite{fcnc36}.
+These results improve significantly upon the previously published ATLAS studies in this channel and provide more stringent limits than the previous combination of ATLAS  $t\rightarrow qH$ results.

### 2022-06-29 sections/data_presel.tex
revised to V2.1

@@
 The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ with 25 ns bunch spacing collected from 2015 to 2018, corresponding to an integrated luminosity of $139~\ifb$.
-Only events recorded with a single-electron trigger, a single-muon trigger, or a di-tau trigger~\cite{TRIG-2018-05,TRIG-2018-01,id_trigger,l1topo_trigger} under stable beam conditions 
-and for which all detector subsystems were operational are considered for analysis. The events recorded by di-lepton triggers that fall into the control regions are used for fake tau background
+Only events recorded with a single-electron trigger, a single-muon trigger, or a di-$\tau$-lepton trigger~\cite{TRIG-2018-05,TRIG-2018-01,id_trigger,l1topo_trigger} under stable beam conditions 
+and for which all detector subsystems were operational are considered for analysis.
+The events recorded by dilepton triggers that fall into the control regions are used for fake-$\tau$-lepton background
 estimation as discussed in Section~\ref{sec:background_model}. The number of $pp$ interactions per bunch crossing in this dataset ranges from about 8 to 45, with an average of 24.
@@
 Single-electron and single-muon triggers with low $\pt$ thresholds and lepton isolation requirements are combined in a logical OR 
-with higher-threshold triggers but with a looser identification criterion and without any isolation requirement.
-The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016-2018), while for electrons the threshold is 24 (26)~\gev.
+with higher-threshold triggers that have a looser identification criterion and no isolation requirement.
+The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016--2018), while for electrons the threshold is 24 (26)~\gev.
 %For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
-For di-tau triggers, the $\pt$ threshold of the leading (subleading) $\had$ candidate is 35 (25)~\gev.
+For di-$\tau$ triggers, the $\pt$ threshold for the leading (subleading) $\had$ candidate is 35 (25)~\gev.
 %Events satisfying the trigger selection are required to have at least one primary vertex candidate.
-To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have a \pt of 1~GeV above the threshold. 
-The reconstructed taus are required to have a \pt of 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
+To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have a \pt that is at least 1~\GeV\ above the threshold. 
+The reconstructed $\tau$-leptons are required to have a \pt at least 5~\GeV\ higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
 %The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
@@
 Further requirements are defined targeting different signal decay modes:
-The events in the leptonic channel are recorded by a single-electron or single-muon trigger, and are required to have exactly one electron or muon that matches, within $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers.
+The events in the leptonic channels are recorded by a single-electron or single-muon trigger, and are required to have exactly one electron or muon that matches, within $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers.
 Requirements are placed on the following additional quantities.
@@
 \begin{itemize}
-\item $t_h\lephad$: To enhance selection of the $t_hH$ and $t_ht(qH)$ final states with a $H\to\lephad$ decay, exactly one $\had$ with opposite-side charge to $\lep$ is required, including at least three jets with exactly one $b$-jet.
-\item $t_{\ell}\hadhad$: To enhance selection of $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay, exactly one light lepton and two opposite-sign $\had$ are selected,
-  including jets with exactly one $b$-jet.
-\item $t_{\ell}\had$: This channel is also to enhance $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay where one $\had$ fails the tau reconstruction or identification
+\item $t_h\lephad$: To enhance selection of the $t_hH$ and $t_ht(qH)$ final states with a $H\to\lephad$ decay, exactly one $\had$ with opposite-sign charge to $\lep$ is required, plus at least three jets with exactly one $b$-jet.
+\item $t_{\ell}\hadhad$: To enhance selection of $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay, exactly one light lepton and two opposite-sign $\had$ are required,
+  plus jets with exactly one $b$-jet.
+\item $t_{\ell}\had$: This channel enhances the selection of $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay where one $\had$ fails the applied reconstruction or identification
   criterion so that there is only one reconstructed $\had$ candidate.
-  To reduce the SM backgrounds and avoid overlaps with the final states of other ATLAS searches, exactly one $\had$ with charge the same as that assigned to the light lepton is required.
+  To reduce the SM backgrounds and avoid overlaps with the final states used in other ATLAS searches, exactly one $\had$ with the same charge as that assigned to the light lepton is required.
   In addition, at least two jets including exactly one $b$-jet are required.
@@
 
-The events in the hadronic channel are selected by a di-tau trigger. Further requirements are:
+The events in the hadronic channel are selected by a di-$\tau$ trigger. Further requirements are:
 %recorded by di-tau trigger, required to have both leading and subleading $\had$ passed the trigger. Further requirements are defined targeting signal decay modes:
 \begin{itemize}
-\item $t_h\hadhad$: Targeting the $t_hH$ and $t_ht(qH)$ final states with $H\to\hadhad$ decay.
+\item $t_h\hadhad$: The $t_hH$ and $t_ht(qH)$ final states with $H\to\hadhad$ decay are targeted.
 Exactly two $\had$ with opposite-sign charge and at least three jets, including exactly one $b$-jet, are required.
@@
 \begin{table*}[t!]
-\caption{\small{Summary of preselection requirements. 
+\caption{\small{Summary of the preselection requirements. 
 The leading and subleading $\had$ candidates are denoted by $\tau_{\mathrm{had1}}$ and $\tau_{\mathrm{had2}}$ respectively.}}
@@
 \toprule\toprule
-\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multicolumn{1}{c}{hadronic channel} \\ 
+\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{Leptonic channels}  & \multicolumn{1}{c}{Hadronic channel} \\ 
 %\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & hadronic channel \\ 
@@
 Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & =0 isolated $e$ or $\mu$ \\
-$\had$  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
-Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} < 0$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} > 0$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} < 0$ \\
-Jets  &   $\geq$ 3 jets & $\geq$1 jets & $\geq$2 jets & $\geq$3 jets \\
+$\had$  & $=$1 $\had$ & $=$2 $\had$ & $=$1 $\had$ & $=$2 $\had$ \\
+Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} = -1$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} = -1$ & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} = 1$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} = -1$ \\
+Jets  &   $\geq$3 jets & $\geq$1 jets & $\geq$2 jets & $\geq$3 jets \\
 $b$-tagging & \multicolumn{3}{c|}{=1 $b$-jets} & =1 $b$-jets\\

### 2022-06-29 sections/introduction.tex
revised to V2.1

@@
 %-------------------------------------------------------------------------------
-After the discovery of the Higgs boson in 2012 at the Large Hadron Collider (LHC) by the ATLAS~\cite{Aad:2012tfa} and 
+Since the discovery of the Higgs boson in 2012 at the Large Hadron Collider (LHC) by the ATLAS~\cite{Aad:2012tfa} and 
 CMS~\cite{Chatrchyan:2012ufa} collaborations, 
@@
 has been conducted to explore this particle. Measurements so far have proved to be consistent with the Standard Model (SM) predictions. 
-However, the program is ongoing and precision measurements as well as searches for rare new physics processes beyond the Standard Model (BSM)
-are underway. One such possibility is flavour-changing neutral-current (FCNC) interactions between the Higgs boson, 
-the top quark, and an up-type quark, $tqH$ ($q=u, c$), which have been sought for by the ATLAS and CMS collaborations.  
+However, the programme is ongoing and precision measurements as well as searches for rare new-physics processes beyond the Standard Model (BSM)
+are underway. One such possibility is flavour-changing neutral current (FCNC) interactions between the Higgs boson, 
+the top quark, and an up-type quark, $tqH$ ($q=u, c$), which have been searched for by the ATLAS and CMS collaborations.  
 %with increased precision and proved to be consistent with the Standard Model (SM) predictions. 
@@
 
-In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders due to the Glashow-Iliopoulos-Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
-An observation of an enhanced rate of this decay would be clear evidence for new physics.
+In the Standard Model (SM), the FCNC interaction is forbidden at tree level and suppressed at higher orders through the Glashow--Iliopoulos--Maiani (GIM) mechanism~\cite{Glashow:1970gm}.
+An observation of an enhanced rate of this decay would be clear evidence of new physics.
 Furthermore, if the $tqH$ interaction exists, the associated single-top and  Higgs  production process through this interaction would enhance
@@
 However, these branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$ when processes beyond the SM are included.
-Examples of these processes include: quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDM)~\cite{ Branco:2hdm2012} with or without flavour violation,
+Examples of these processes include: quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDMs)~\cite{ Branco:2hdm2012} with or without flavour violation,
  %of type I, with explicit flavour conservation,
@@
 % In these scenarios, branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$. 
-An even larger branching ratio of  $\BR(t\to cH) \sim 10^{-3}$ can be reached in 2HDM without explicit flavour conservation, since in them the tree-level FCNC coupling is no longer forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}.
+An even larger branching ratio of  $\BR(t\to cH) \sim 10^{-3}$ can be reached in 2HDMs without explicit flavour conservation, since in these models the tree-level FCNC coupling is no longer forbidden by any symmetry~\cite{Cheng:1987rs,Baum:2008qm,Chen:2013qta,Chiang:2015cba,Crivellin:2015hha,Botella:2015hoa, Gori:2017tvg,Chiang:2017fjr}.
 %While other FCNC top couplings ($tq\gamma$, $tqZ$, $tqg$) are also enhanced in these scenarios beyond the SM, 
@@
 The study of $pp\rightarrow tH$ processes will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
-The $tH$ associated production in the SM is expected to have a cross section of $92^{+7}_{-12}$ fb at a centre-of-mass energy of $\sqrt{s}= 13~\tev$~\cite{deFlorian:2016spz}.
+In the SM, associated production of $tH$ in $pp$ collisions is expected to have a cross section of $\sigma_{tH}=92^{+7}_{-12}$ fb at a centre-of-mass energy of $\sqrt{s}= 13~\tev$~\cite{deFlorian:2016spz}.
 
 Searches for $t \to qH$ decays have been performed by the ATLAS and CMS collaborations, taking advantage of the large samples
-of top-quark pair ($\ttbar$) events collected in proton-proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{fcnc36} using early Run~2 data.
+of top-quark pair ($\ttbar$) events collected in proton--proton ($pp$) collisions at centre-of-mass energies of $\sqrt{s}=7~\tev$ and $8~\tev$~\cite{Aad:2014dya,Aad:2015pja,Khachatryan:2016atv} during Run~1 of the LHC, as well as at $\sqrt{s}=13~\tev$~\cite{fcnc36} using early Run~2 data.
 In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $qH$ with a small branching ratio 
- $\BR(t\to qH)$, denoted~\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
-$WbWb$ is used to denote $W^+b W^- \bar{b}$.} as $\ttbar \to WbHq$.  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
+ $\BR(t\to qH)$, a process denoted by $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
+$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
 the SM.
@@
 Compared to Run~1, the Run~2 searches, summarised in Table~\ref{tab:limits_summary_ref}, benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
-Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) on the branching ratio
-$\BR(t\to cH)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd} and $\BR(t\to cH)<0.16\%$ based on
+Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) on the 
+$t\to cH$ branching ratio: $\BR(t\to cH)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd} and $\BR(t\to cH)<0.16\%$ based on
 %signatures with two same-charge light leptons (electrons or muons) or three light leptons 
-multilepton (electron or muon) signatures resulting from 
+multi-lepton (electron or muon) signatures resulting from 
 $H \to  WW^*, ZZ^*$, $\tau^+\tau^-$ in which both $\tau$-leptons decay leptonically~\cite{Aaboud:2018pob}.
-The upper limits are set on $\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36} and $\BR(t\to cH)<0.19\%$ using the $H\to \tau^+\tau^-$ decay in which at least
+ATLAS also set upper limits of $\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36} and $\BR(t\to cH)<0.19\%$ using $H\to \tau^+\tau^-$ decays in which at least
 one of the $\tau$-leptons decays hadronically~\cite{fcnc36}.  
-These upper limits are derived assuming that the branching ratio $\BR(t\to uH)$ is null. Similar upper limits are obtained for $\BR(t\to uH)$ assuming $\BR(t\to cH)=0$.
+These upper limits are derived assuming that the branching ratio $\BR(t\to uH)=0$. Similar upper limits are obtained for $\BR(t\to uH)$ when assuming $\BR(t\to cH)=0$.
 %The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
@@
 %Compared with previous searches, 
-The search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
+The search in Ref.~\cite{Sirunyan:2017uae} also considers the contribution to the signal from 
 $pp \to tH$ production~\cite{Greljo:2014dka}. 
 CMS subsequently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
-the full Run 2 dataset; observing (expected) upper limits on  $\BR(t\to cH)$ of $9.4\times10^{-4}\, (8.6\times10^{-4})$
-and on $\BR{B}(t\to uH)$ of $7.9\times10^{-4}\, (1.1\times10^{-3})$~\cite{CMS:2021gfa}.
+the full Run~2 dataset, obtaining observed (expected) upper limits of  $\BR(t\to cH) < 9.4\times10^{-4}\, (8.6\times10^{-4})$
+and $\BR(t\to uH) < 7.9\times10^{-4}\, (1.1\times10^{-3})$~\cite{CMS:2021gfa}.
 %CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.
@@
 \begin{table}[t!]
-\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to cH)$ and $\BR(t \to uH)$ obtained by the ATLAS and CMS Collaborations with Run 2 data.
-Each limit is obtained assuming the other branching ratio is null.}}
+\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to cH)$ and $\BR(t \to uH)$ obtained by the ATLAS and CMS collaborations with Run~2 data.
+Each limit is obtained assuming the other branching ratio is zero.}}
 \begin{center}
@@
 & $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
-& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
+& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137~~~~~          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
 %& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
@@
 %This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
-The analysis reported here targets Higgs boson decays to 
+The analysis reported here targets Higgs boson decays into 
 %This paper is focused on the decay mode of the Higgs boson into
-$\tau$-leptons in the complete Run~2 dataset collected in 2015-2018.
+$\tau$-leptons in the complete Run~2 dataset collected by ATLAS in 2015--2018.
 The corresponding integrated luminosity is 139 fb$^{-1}$.
@@
 The dataset is divided into several final states depending on the production mode and
-the  $W$ and tau decays. Top quark pair production events where the $W$ boson decays hadronically (leptonically) are referred to as $t_h$ ($t_{\ell}$).
-The decays $\tau \to \ell \nu_{\ell} \nu_{\tau}$ are referred as $\lep$, while the decays $\tau \to \text{hadrons} + \nu_{\tau}$ are referred as $\thad$.
+the  $W$ boson and $\tau$-lepton decays. Top quark pair production events where the $W$ boson decays hadronically (leptonically) are denoted by $t_h$ ($t_{\ell}$).
+The decays $\tau \to \ell \nu_{\ell} \nu_{\tau}$ are denoted by $\lep$, while the decays $\tau \to \text{hadrons} + \nu_{\tau}$ are denoted by $\thad$.
 The contribution of 
-$W\rightarrow\tau\nu$ is included as $\lep$ in $t_{\ell}$ when the $\tau$ decays into a light lepton (electron or muon) or as $\thad$ 
-in $t_h$ when the $\tau$ decays hadronically.
+$W\rightarrow\tau\nu$ is included as $\lep$ in $t_{\ell}$ when the $\tau$-lepton decays into a light lepton (electron or muon) or as $\thad$ 
+in $t_h$ when the $\tau$-lepton decays hadronically.
 %either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
@@
 The $H\rightarrow \tau\tau$ decay is detected in
-either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$), but only the $\thadhad$ final state is considered
-when the top decays leptonically ($t_{\ell}$), in order to avoid overlaps with
+either the $\tlhad$ or $\thadhad$ final state when the top quark decays hadronically ($t_h$), but only the $\thadhad$ final state is considered
+when the top quark decays leptonically ($t_{\ell}$), in order to avoid overlaps with
 other ATLAS searches~\cite{Aaboud:2018pob}. 
-Events with two hadronically decaying $\tau$-leptons without an electron or muon are named hadronic channels.
-Events with at least one \tauhad with an additional electron or muon (corresponding to $t_{\ell}$ or $\lep$ events) are named leptonic channels.
-More signal regions (with the top quark decaying leptonically) are exploited here than in the previous FCNC $\Htautau$ search which was conducted using the partial Run~2 dataset~\cite{fcnc36}.
-In addition, an improved treatment of misidentified $\tau$-leptons (fake) in simulation and data-driven
-fake estimations from multi-jet background is implemented.
+In this search, events with two hadronically decaying $\tau$-leptons and no electron or muon define the hadronic channel.
+Events with at least one \tauhad and an additional electron or muon (corresponding to $t_{\ell}$ or $\lep$ events) are assigned to leptonic channels.
+More signal regions (with the top quark decaying leptonically) are exploited here than in the previous FCNC $\Htautau$ search, which was conducted using the partial Run~2 dataset~\cite{fcnc36}.
+In addition, an improved treatment of misidentified $\tau$-leptons (`fakes') in simulation and in data-driven
+estimations of fakes from multi-jet background is implemented.
 % and more

### 2022-06-29 sections/simulated_samples.tex
revised to V2.1

@@
 
-An overview of the Monte Carlo (MC) generators used for the main signal and background samples is summarized in Table~\ref{mob}.
-Samples of simulated $\ttbar \to WbHq$ ($tt(qH)$) events were generated with the next-to-leading order (NLO) generator\footnote{In the following, 
+An overview of the Monte Carlo (MC) generators used for the main signal and background samples is summarised in Table~\ref{mob}.
+Samples of simulated $\ttbar \to WbHq$ ($tt(qH)$) events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
 the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element (ME) calculation 
-is performed.} {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
+is performed.} {\powheg}\,v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
 %{\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
-with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering (PS), hadronisation, and the underlying event.
-The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
-initial- and final-state radiation, referred to as the tune, was used.
+with the \textsc{NNPDF3.0nlo}~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia}\,8.212~\cite{Sjostrand:2007gs} with the \textsc{NNPDF2.3lo}~\cite{Ball:2012cx} PDF set for the modelling of the parton showers (PS), hadronisation, and underlying event.
+A set of tuned parameters called the A14 tune~\cite{ATLASUETune4} was used in {\pythia} to control the modelling of multi-parton interactions and  
+initial- and final-state radiation.
 The signal sample is normalised to the same total cross section as is used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below)
@@
 
-The $tH$ signal events were generated by {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
-with the NNPDF3.0 NLO parton distribution function (PDF) set. The parton showers, hadronisation, and underlying event are modelled by {\pythia}~8.212 with the NNPDF2.3 LO PDF set
+The $tH$ signal events were generated by {\amcatnlolong}\,2.6.2~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
+with the \textsc{NNPDF3.0nlo} parton distribution function (PDF) set. The parton showers, hadronisation, and underlying event were modelled by {\pythia}\,8.212 with the \textsc{NNPDF2.3lo} PDF set
 in combination with the A14 tune.
@@
 %hadronisation, and the underlying event with the A14 tune.
-Depending on whether the up quark or the charm quark is involved in the FCNC production, the effective Lagrangian of the $tqH$ interaction is parametrised using
-dimension-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 0.711 pb and $\sigma(cg\to tH)$ = 0.103 pb using $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$ as the benchmark.
+Depending on whether the up quark or the charm quark is involved in the FCNC production process, the effective Lagrangian of the $tqH$ interaction is parameterised using
+dimension-6 operators~\cite{fcnc_production_theory}.
+The cross sections $\sigma(ug\to tH) = 0.711$~pb and $\sigma(cg\to tH) = 0.103$~pb were obtained using $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$ as the benchmark.
 
-The sample used to model the $\ttbar$ background was generated with the NLO generator {\powheg}~v2
+The sample used to model the $\ttbar$ background was generated with the NLO generator {\powheg}\,v2
 %\cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
-using the NNPDF3.0 NLO PDF set. The {\powheg} model parameter $h_{\textrm{damp}}$, which controls 
+using the \textsc{NNPDF3.0nlo} PDF set. The {\powheg} model parameter $h_{\textrm{damp}}$, which controls 
 matrix element to parton shower matching and regulates the high-$\pt$ radiation, was set to 1.5 times the top-quark mass. 
-The parton showers, hadronisation, and underlying event were modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
+The parton showers, hadronisation, and underlying event were modelled by {\pythia}\,8.210 with the \textsc{NNPDF2.3lo} PDF set in combination with the A14 tune.
 Alternative $\ttbar$ simulation samples used to derive parton shower systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
-The generated $\ttbar$ samples are normalised to a theoretical cross section of $832^{+46}_{-51}$~pb, 
-computed using \textsc{Top++}~v2.0~\cite{Czakon:2011xx} at next-to-next-to-leading order (NNLO), 
+The generated $\ttbar$ samples are normalised to a theoretical cross section of $\sigma_{\ttbar}=832^{+46}_{-51}$~pb, 
+computed using \textsc{Top++}\,2.0~\cite{Czakon:2011xx} at next-to-next-to-leading order (NNLO), 
 including resummation of next-to-next-to-leading logarithmic (NNLL) soft gluon 
@@
 
-Samples of single-top-quark events corresponding to the $t$-channel production mechanism were generated with a  
-{\powheg}~v2 generator~\cite{Frederix:2012dh}, using the 4F scheme  for the NLO matrix-element calculations
-and the corresponding NNPDF3.0 NLO set of PDFs.
+Samples of single-top-quark events corresponding to the $t$-channel production mechanism were generated with the  
+{\powheg}\,v2 generator~\cite{Frederix:2012dh}, using the four-flavour scheme  for the NLO matrix-element calculations
+and the corresponding \textsc{NNPDF3.0nlo} set of PDFs.
 Samples corresponding to the $tW$- and $s$-channel production mechanisms were generated 
-with {\powheg}~v2 using the five-flavour scheme. Overlaps between the $\ttbar$ and $tW$ final states were avoided by using 
+with {\powheg}\,v2 using the five-flavour scheme. Overlaps between the $\ttbar$ and $tW$ final states were avoided by using 
 the diagram removal scheme~\cite{Frixione:2005vw}.
-The parton showers, hadronisation and underlying event were modelled using {\pythia}~8.230~\cite{Sjostrand:2006za} using the A14 tune and the NNPDF2.3 LO PDF set.
+The parton showers, hadronisation and underlying event were modelled using {\pythia}\,8.230~\cite{Sjostrand:2006za} with the A14 tune and the \textsc{NNPDF2.3lo} PDF set.
 %with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set %in combination with the Perugia 2012 tune~\cite{Skands:2010ak}.
@@
 
-Samples of $W/Z$+jets events were generated with the {\sherpa}~2.2.1~\cite{Gleisberg:2008ta} generator. 
+Samples of $W/Z$+jets events were generated with the {\sherpa}\,2.2.1~\cite{Gleisberg:2008ta} generator. 
 The matrix element was calculated for up to two partons at NLO and up to four partons at LO using 
 \textsc{Comix}~\cite{Gleisberg:2008fv} and \textsc{OpenLoops}~\cite{Cascioli:2011va}. The matrix-element calculation 
-is merged with the {\sherpa} parton shower~\cite{Schumann:2007mg} using the ME+PS@NLO prescription~\cite{Hoeche:2012yf}. 
-The PDF set used for the matrix-element calculation is NNPDF3.0 NNLO~\cite{Ball:2014uwa} with a dedicated parton shower tuning developed for {\sherpa}. 
+was merged with the {\sherpa} parton shower~\cite{Schumann:2007mg} using the MEPS@NLO prescription~\cite{Hoeche:2012yf}. 
+The PDF set used for the matrix-element calculation is \textsc{NNPDF3.0nnlo}~\cite{Ball:2014uwa} with a dedicated parton shower tune developed for {\sherpa}. 
 Separate samples were generated for different $W/Z$+jets categories using filters for a $b$-jet 
 ($W/Z$+$\geq$1$b$+jets), a $c$-jet and no $b$-jet ($W/Z$+$\geq$1$c$+jets), and with a veto on $b$- and $c$-jets 
-($W/Z$+light-jets), which are combined into the inclusive $W/Z$+jets samples.
-Both the $W$+jets and $Z$+jets samples are normalised to their respective inclusive NNLO theoretical 
+($W/Z$+light-jets), and were combined into the inclusive $W/Z$+jets samples.
+The $W$+jets and $Z$+jets samples are normalised to their respective inclusive NNLO theoretical 
 cross sections calculated with \textsc{FEWZ}~\cite{Anastasiou:2003ds}.
 
-Samples of $WW/WZ/ZZ$+jets events were generated with {\sherpa}~2.2.1 using the CT10 PDF set
+Samples of $WW/WZ/ZZ$+jets events were generated with {\sherpa}\,2.2.1 using the CT10 PDF set
 and include processes containing up to four electroweak vertices. 
@@
 
-Samples of $\ttbar V$ ($V=W\, Z$ boson) and $\ttbar H$ events were generated with {\amcatnlo}~2.2.1, using NLO matrix elements and the NNPDF3.0 NLO PDF set,
-and interfaced to {\pythia}~8.210 with the NNPDF2.3 LO PDF set and the A14 tune. 
+Samples of $\ttbar V$ ($V=W, Z$ boson) and $\ttbar H$ events were generated with {\amcatnlo}\,2.2.1, using NLO matrix elements and the \textsc{NNPDF3.0nlo} PDF set,
+and interfaced to {\pythia}\,8.210 with the \textsc{NNPDF2.3lo} PDF set and the A14 tune. 
 %Instead, the $\ttbar V$ samples used in the $\Hbb$ search are based on LO matrix elements computed for up to two additional partons 
@@
 
-Samples of $WH$ and $ZH$, collectively referred to as $VH$, are generated using {\powheg}~v2\cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
-and interfaced to {\pythia}~8.210 with the PDF4LHC15 PDF set and the AZNLO tune.
+Samples of $WH$ and $ZH$, collectively referred to as $VH$, were generated using {\powheg}\,v2~\cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
+and interfaced to {\pythia}\,8.210 with the PDF4LHC15 PDF set and the AZNLO tune.
 The contribution of $tH$ associated production is also considered as part of the SM Higgs background.
-The sample is generated using {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca} and interfaced with {\pythia}~8.210 with CT10PDF
+The sample was generated using {\amcatnlolong}\,2.6.2~\cite{Alwall:2014hca} and interfaced to {\pythia}\,8.210 with the CT10 PDF set
 and the A14 tune. The MC predictions are normalised using the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.
@@
 All generated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
-utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
+utilise \textsc{EvtGen}\,1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
 %To model the effects of pile-up, events from minimum-bias interactions were generated using {\pythia}~8.186~\cite{Sjostrand:2007gs}  
 %in combination with the A3 tune~\cite{ATL-PHYS-PUB-2011-014}, 
-The effects of multiple interactions in the same and nearby bunch crossings (pile-up) were modelled by overlaying minimum-bias events, simulated using the soft QCD processes of {\pythia}~8.186~\cite{Sjostrand:2006za} with the A3~\cite{ATL-PHYS-PUB-2016-017} set of tuned parameters and NNPDF2.3 LO PDF set~\cite{Ball:2012cx}.
+The effects of multiple interactions in the same and nearby bunch crossings (pile-up) were modelled by overlaying minimum-bias events, simulated using the soft QCD processes of {\pythia}\,8.186~\cite{Sjostrand:2006za} with the A3 tune~\cite{ATL-PHYS-PUB-2016-017} and \textsc{NNPDF2.3lo} PDF set~\cite{Ball:2012cx}.
 %parton distribution functions (PDF).
@@
 \footnotesize
-\centering
+%\centering
 \caption{Overview of the MC generators used for the main signal and background samples, including the matrix element (ME), parton shower (PS), parton distribution function set (PDF), and cross-section calculation order (Order).}
+\begin{center}
 \begin{tabular}[h]{l|c|c|c|c|c|c}
@@
         &  ME   &  PS    &  ME  & PS &   &  \\\hline
-$tt(qH)$ Signal & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-$tH$ Signal & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-$W/Z$+jets & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline
-\ttbar & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-Single top & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-$t\bar{t}X$ & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
-$VH$ & {\powheg} & {\pythia}~8 & PDF4LHC15&CTEQ6L1 & AZNLO & NLO \\ \hline
-$tH$ & {\amcatnlolong} & {\pythia}~8 & \multicolumn{2}{c|}{CT10PDF} & A14 & NLO \\ \hline
-Diboson & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline\hline
+$tt(qH)$ signal & {\powheg} & {\pythia}\,8 & \textsc{NNPDF3.0nlo} & \textsc{NNPDF2.3lo} & A14 & NLO \\ \hline
+$tH$ signal & {\amcatnlolong} & {\pythia}~8 & \textsc{NNPDF3.0nlo} & \textsc{NNPDF2.3lo} & A14 & NLO \\ \hline
+$W/Z$+jets & \multicolumn{2}{c|}{{\sherpa}\,2.2.1} & \multicolumn{2}{c|}{\textsc{NNPDF3.0nnlo}} & {\sherpa} & NLO/LO \\ \hline
+\ttbar & {\powheg} & {\pythia}\,8 & \textsc{NNPDF3.0nlo} & \textsc{NNPDF2.3lo} & A14 & NLO \\ \hline
+Single top & {\powheg} & {\pythia}\,8 & \textsc{NNPDF3.0nlo} & \textsc{NNPDF2.3lo} & A14 & NLO \\ \hline
+$t\bar{t}X$ & {\amcatnlolong} & {\pythia}\,8 & \textsc{NNPDF3.0nlo} & \textsc{NNPDF2.3lo} & A14 & NLO \\ \hline
+$VH$ & {\powheg} & {\pythia}\,8 & PDF4LHC15&CTEQ6L1 & AZNLO & NLO \\ \hline
+$tH$ & {\amcatnlolong} & {\pythia}\,8 & \multicolumn{2}{c|}{CT10} & A14 & NLO \\ \hline
+Diboson & \multicolumn{2}{c|}{{\sherpa}\,2.2.1} & \multicolumn{2}{c|}{\textsc{NNPDF3.0nnlo}} & {\sherpa} & NLO/LO \\ \hline\hline
 \end{tabular}
+\end{center}
 \label{mob}

### 2022-06-29 sections/statistical_analysis.tex
revised to V2.1

@@
 
-The final discriminant distributions are the BDT outputs of all the considered analysis regions. They are jointly analysed for the 
-presence of a signal. The BDT distributions are binned to maximize sensitivity to the signal.
+The final discriminant distributions are the BDT outputs from all the considered analysis regions. They are jointly analysed for the 
+presence of a signal. The BDT distributions are binned to maximise sensitivity to the signal.
 The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
@@
 on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $tH$ and $tt(qH)$ signal events
-normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$;
-and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations.
+normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$,
+and on $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations.
 The $pp\rightarrow tH$ production cross section is related to $\BR(t\rightarrow qH)$ through their dimension-6 operators~\cite{fcnc_production_theory}.
 It follows that the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
-All nuisance parameters are subject to Gaussian constraints on the likelihood.
+All nuisance parameters are subject to Gaussian constraints in the likelihood function.
 For a given value of $\mu$, the nuisance parameters $\theta$ allow variations of the expectations for signal and background
@@
 the nominal expectations that globally provide the best fit to the data.
-This procedure allows a reduction of the impact of systematic uncertainties on 
+This procedure reduces the impact of systematic uncertainties on 
 the search's sensitivity by taking advantage of the highly populated background-dominated bins included in the likelihood fit.
@@
 
-The fitting procedure was initially validated through extensive studies using pseudodata (which is defined as the sum of all predicted backgrounds 
-plus an injected signal of variable strength) as well as by performing fits to real data where bins of the final discriminant variable with 
-a signal contamination above 10\% are excluded (referred to as blinding requirements).
-In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
+The fitting procedure was initially validated through extensive studies using pseudo-data (which is defined as the sum of all predicted backgrounds 
+plus an injected signal of variable strength) as well as by performing fits to real data where bins of the final discriminating variable with 
+a signal contamination above 10\% are excluded (referred to as `blinding' requirements).
+In both cases, the robustness of the model with respect to systematic uncertainties is established by verifying the stability of the fitted background 
 when varying assumptions about some of the leading sources of uncertainty. 
@@
 The test statistic $q_\mu$ is defined as the profile likelihood ratio, 
-$q_\mu = -2\ln({\cal L}(\mu,{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
+$q_\mu = -2\ln({\cal L}(\mu,{\hat{\hat{\theta}}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
 where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
-maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and the ${\hat{\theta}}_\mu$ are the values of the
+maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and the ${\hat{\hat{\theta}}}_\mu$ are the values of the
 nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
@@
 $\BR(t\to qH)$, derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
-For a given signal scenario, values of the $\BR(t\to qH)$ yielding CL$_{\textrm{s}} < 0.05$,
-where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.
+For a given signal scenario, values of $\BR(t\to qH)$ yielding CL$_{\textrm{s}} < 0.05$,
+where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded with at least 95\% confidence.

### 2022-06-29 sections/strategy_Htautau.tex
revised to V2.1

@@
 %\label{sec:htautau_reco_cat}
-The $tt(qH)$ and $tH$ signal being probed are characterised by the presence of $\tau$-leptons from the decay of 
+The $tt(qH)$ and $tH$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
 the Higgs boson, where the remaining top quark decays into $Wb$. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
@@
 If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon, together with significant $\met$, is also expected.
-In a significant fraction of the events, the lowest $\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
+In a significant fraction of the events, the lowest-$\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
 resulting in only three reconstructed jets where the production mode is dominant. 
 %some signal events mixed with production mode having only three reconstructed jets.
-In order to optimise the sensitivity of the search, the selected events are categorised into seven signal regions (SRs) based on the  number of light leptons,
-$\had$ candidates, and number of light flavoured jets:
+In order to optimise the sensitivity of the search, the selected events are categorised into seven signal regions (SRs) based on the  numbers of light leptons,
+$\had$ candidates, and light-flavour jets:
 %$t_{\ell}\hadhad$, $t_{\ell}\had$(1j and 2j), $t_{\ell}\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}. 
@@
 \begin{table}
-\centering
-\caption{Overview of the signal regions (SR), validation region (VR), and $t\bar{t}$ control regions (CRtt) used for the fake tau scale factor derivation in the leptonic channels.
-Leptons are required to have either same sign (SS) or opposite sign (OS) in each region.}
+%\centering
+\caption{Overview of the signal regions (SR), validation region (VR), and $t\bar{t}$ control regions (CRtt) used for the fake-$\tau$-lepton scale factor derivation in the leptonic channels.
+Leptons are required to have either same-sign (SS) or opposite-sign (OS) charges in each region.}
 \label{tab:srcr}
+\begin{center}
 \begin{tabular}[h]{c|c|c|c|c|c|c}
 \hline \hline
-\multicolumn{2}{c|}{Regions} & $b$-jet & light flavour jets        & lepton & hadronic taus & charge\\ \hline
-\multirow{7}{*}{SR}&$t_{\ell}\thadhad$     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
+\multicolumn{2}{c|}{Regions} & $b$-jets & Light-flavour jets        & Leptons & Hadronic $\tau$ decays & Charge\\ \hline
+\multirow{7}{*}{SR}&$t_{\ell}\thadhad$     & 1     & $\ge0$~~~~                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
 &$t_{\ell}\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
@@
 &$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
-&$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
+&$t_h\tlhad$-3j   & 1     & $\ge3$~~~~                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
 &$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
-&$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
-VR &$t_{\ell}\thadhad$-SS     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ SS\\ \hline
-\multirow{6}{*}{CRtt}&$t_{\ell}t_{\ell}1b\tauhad$ & 1     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
-&$t_{\ell}t_{\ell}2b\tauhad$      & 2     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
+&$t_h\thadhad$-3j & 1     & $\ge3$~~~~                       & 0      & 2             & $\thadhad$ OS\\ \hline
+\multirow{2}{*}{VR}&$t_{\ell}\thadhad$-SS     & 1     & $\ge0$~~~~                                & 1      & 2             & $\thadhad$ SS\\ \hline
+&$t_h\thadhad$-3j SS & 1     & $\ge3$~~~~                       & 0      & 2             & $\thadhad$ SS\\ \hline
+\multirow{6}{*}{CRtt}&$t_{\ell}t_{\ell}1b\tauhad$ & 1     & $\ge0$~~~~                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
+&$t_{\ell}t_{\ell}2b\tauhad$      & 2     & $\ge0$~~~~                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
 &$t_{\ell}t_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
 &$t_{\ell}t_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \cline{2-7}
-&$t_{\ell}t_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
-&$t_{\ell}t_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \hline
+&$t_{\ell}t_h2b\tauhad$-3jSS & 2     & $\ge3$~~~~                        & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
+&$t_{\ell}t_h2b\tauhad$-3jOS & 2     & $\ge3$~~~~                & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \hline
 \end{tabular}
+\end{center}
 \end{table}
@@
 %of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay %is missing or not (events with exactly three jets or at least four jets).
-This event categorisation is primarily used to optimize the sensitivity in each signal region that targets either leptonic or hadronic top-quark
-decays as well as the Higgs decays into either the $\lephad$ or $\hadhad$ final states.   
+This event categorisation is primarily used to optimise the sensitivity in each signal region that targets either leptonic or hadronic top-quark
+decays as well as the Higgs boson decays into either the $\lephad$ or $\hadhad$ final state.   
 %The event kinematic reconstruction is used in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.
-The contribution of background to the signal regions of the $t_h\hadhad$ and $t_h\lephad$ channels is reduced by having kinematic constraints on the di-tau mass and the $\met$ in the event~\cite{Chen:2015nta}.
+The contribution of background to the signal regions of the $t_h\hadhad$ and $t_h\lephad$ channels is reduced by placing kinematic constraints on the di-$\tau$ mass and the $\met$ in the event~\cite{Chen:2015nta}.
 
@@
 
-For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a high $\pt$ jet from the
-decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
+For the $t_ht(qH)$ events, the jet from $t\to qH$, referred to as the FCNC jet ($q$-jet), should be a high-$\pt$ jet from the
+decay chain $t\to qH\to q\tau\tau$, with $\tau$-leptons reconstructed as $\lephad$ or $\hadhad$.
 %There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
 %is considered as the $q$-jet 
-Events should contain 4 jets, with the one having the smallest angular separation with respect to the visible di-tau system being labelled the $q$-jet since the FCNC top decay products are likely boosted closer together.
-If there are more than two jets besides the $q$- and $b$-jet, the jets from the $W$ boson decay are chosen from the combination
-with the invariant mass closest to the $W$ boson mass. There is the possibility that one of the jets fails the $\pt$ requirement and is not reconstructed.
-These kinds of events will produce the $t_hH$ final state.
+Events should contain four jets, with the one having the smallest angular separation from the visible di-$\tau$ system being labelled the $q$-jet since the FCNC top-quark decay products are likely to be boosted closer together.
+If there are more than two jets besides the $q$-jet and $b$-jet, the jets from the $W$ boson decay are chosen to be those from the combination
+with an invariant mass closest to the $W$ boson mass. It is possible that one of the jets fails the $\pt$ requirement and is not reconstructed.
+Events of this kind produce the $t_hH$ final state.
 %while the FCNC top resonance is
@@
 %given the big chance that the jet which is missing is from $W$ decay.
-There are three jets coming from top hadronic decay including the $b$-jet and a pair of opposite-sign $\had$ from the Higgs boson decay, where
-both the $t_h$ and $H$ can be reconstructed.  
+When both the $t_h$ and $H$ can be reconstructed, three jets come from the top quark's hadronic decay, including a $b$-jet, and a pair of opposite-sign $\had$ come from the Higgs boson decay.  
 %. So a Higgs resonance formed by the taus and a top resonance formed by
@@
 The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
-are estimated using a kinematic fit and assuming a collinear approximation for the tau decay products.
-The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass ($m_{\text{H}}=125~\gev$) and the
-measured $E_{\text{x,y}}^{\text{miss}}$  within their expected resolutions ($\sigma_{E_{\text{x,y}}^{\text{miss}}}$), defined as
+are estimated using a kinematic fit and assuming a collinear approximation for the $\tau$ decay products.
+The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints placed on the Higgs boson mass ($m_H=125~\gev$) and the
+measured $E_{x,y}^{\text{miss}}$  within their expected resolutions ($\sigma_{E_{x,y}^{\text{miss}}}$), defined as
 \begin{eqnarray}
@@
 \chi^2 =
-\left( \frac{m_{\tau\tau,\text{fit}} - m_{\text{H}}}{\sigma_{\tau\tau}} \right)^2 +
-\left( \frac{E_{\text{x,fit}}^{\text{miss}} - E_{\text{x}}^{\text{miss}}}{\sigma_{E_{\text{x}}^{\text{miss}}}} \right)^2
-  +\left( \frac{E_{\text{y,fit}}^{\text{miss}} - E_{\text{y}}^{\text{miss}}}{\sigma_{E_{\text{y}}^{\text{miss}}}} \right)^2.
+\left( \frac{m_{\tau\tau,\text{fit}} - m_{H}}{\sigma_{\tau\tau}} \right)^2 +
+\left( \frac{E_{x,\text{fit}}^{\text{miss}} - E_{x}^{\text{miss}}}{\sigma_{E_{x}^{\text{miss}}}} \right)^2
+  +\left( \frac{E_{y,\text{fit}}^{\text{miss}} - E_{y}^{\text{miss}}}{\sigma_{E_{y}^{\text{miss}}}} \right)^2.
 \end{array}
@@
 
-The resolution on the Higgs boson mass ($\sigma_{\tau\tau}$) is estimated to be $20~\gev$ from a fit of the mass
-distribution of the simulated  $tqH$ signal events, while the resolution on the measured $\met$ is parameterised as a linear function of 
+The Higgs boson mass resolution ($\sigma_{\tau\tau}$) is estimated to be $20~\gev$ from a fit of the mass
+distribution of the simulated  $tqH$ signal events, while the $\met$ measurement's resolution is parameterised as a linear function of 
 $\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $E_{\text{T}}$ values of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
-After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
+After the $\chi^2$ minimisation, both the Higgs boson $\pt$ and the 
 $\pt$ values of the parent top quarks are determined with better resolution in the signal events.
@@
 the kinematic fit is no longer feasible due to the neutrino from the $W\rightarrow \ell\nu$ decay. The kinematic variables are calculated using the visible
-objects only. After the event reconstruction, a number of variables are used to discriminate the signal from the background using a multivariate analysis described
-in Section~\ref{sec:tmva}.
+objects only. After the event reconstruction, a number of these variables are used in a multivariate analysis to discriminate the signal from the background, as described in Section~\ref{sec:tmva}.
 

### 2022-06-29 sections/systematic_uncertainties.tex
revised to V2.1

@@
 as appropriate. The following sections describe the systematic uncertainties considered.
-Table~\ref{tab:had_sys_impact} shows a summary of the dominant systematic uncertainties on the measured $\BR(t\to qH)$ branching ratio
-resulting from the fits to the data on the signal regions as described in Section~\ref{sec:result}.
+Table~\ref{tab:had_sys_impact} shows a summary of the dominant systematic uncertainties in the measured $\BR(t\to qH)$ branching ratio
+resulting from the fits to the data in the signal regions as described in Section~\ref{sec:result}.
 
@@
 The uncertainty in the integrated luminosity is 1.7\%, affecting the overall normalisation of all processes estimated from the simulation. 
-It is derived, following a methodology similar to that detailed in Ref.~\cite{Aaboud:2016hhf}, and using the LUCID-2 detector 
+It is derived, following a methodology similar to that detailed in Ref.~\cite{Aaboud:2016hhf} and using the LUCID-2 detector 
 for the baseline luminosity measurements \cite{Avoni:2018iuv}, from a calibration of the luminosity scale using $x$--$y$ beam-separation scans.
@@
 Uncertainties associated with jets arise from the jet energy scale (JES)
-and resolution (JER) and the efficiency to pass the JVT requirements. 
-The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pile-up treatment
+and resolution (JER), and the efficiency to pass the JVT requirements. 
+The largest contribution comes from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pile-up treatment
 is split into 43 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}. The total JES uncertainty is
-below 5\% for most jets and below 1\% for central jets with $\pt$ between 300 GeV and 2 TeV. The difference between the JER
-in data and in MC is represented by one nuisance parameter (NP). It is applied to the MC by smearing the jet $\pt$ within the prescribed uncertainty.
+below 5\% for most jets and below 1\% for central jets with $\pt$ between 300~\GeV\ and 2~\TeV. The difference between the JER values
+in data and MC events is represented by one nuisance parameter (NP). It is applied to the MC events by smearing the jet $\pt$ within the prescribed uncertainty.
 
@@
 
-Efficiencies to tag $b$-jets and $c$-jets in the simulation are corrected to match the efficiencies in data by $\pt$-dependent factors,
+Efficiencies to tag $b$-jets and $c$-jets in the simulation are corrected by $\pt$-dependent factors to match the efficiencies in data,
 while the light-jet efficiency is scaled by $\pt$- and $\eta$-dependent factors.
@@
 The light-jet efficiency is measured in a multi-jet data sample enriched in light-flavour jets~\cite{ATLAS-CONF-2018-006}.
-The uncertainties in these scale factors include a total of 44 independent sources affecting $b$-jets, 19 sources affecting $c$-jets, and 19 sources affecting light-jets. 
-These systematic uncertainties are taken as uncorrelated between $b$-jets, $c$-jets, and light-jets.
+The uncertainties in these scale factors come from a total of 44 independent sources affecting $b$-jets, 19 sources affecting $c$-jets, and 19 sources affecting light jets. 
+These systematic uncertainties are taken to be uncorrelated between $b$-jets, $c$-jets, and light jets.
 %The uncertainty on the pileup reweighing is evaluated by varying the pileup scale factors by 1$\sigma$ based on the reweighing of the average interactions per bunch crossing.
@@
 Scale factors are applied to reweight simulated events in order to obtain the pile-up distribution corresponding to the data.
-An uncertainty on these reweighting scale factors is estimated by varying the reweighting upon the profile in data within its uncertainties.
+An uncertainty in these reweighting scale factors is estimated by reweighting the profile in data while keeping it within its uncertainties.
 %considered based on the disagreement between the instantaneous luminosity in data and in simulation.
@@
 
-A number of sources of systematic uncertainty affecting the modelling of $t\bar{t}$+jets are considered: the choice of the renormalisation and factorisation scale in the matrix-element calculation, the choice of the matching scale when matching the matrix elements to the parton shower generator, the uncertainty on the value of $\alpha_s$ when modeling initial-state radiation (ISR), and
-the choice of the renormalisation scale when modeling final-state radiation (FSR).
+A number of sources of systematic uncertainty affecting the modelling of $t\bar{t}$+jets are considered: the choice of renormalisation and factorisation scale in the matrix-element calculation, the choice of matching scale when matching the matrix elements to the parton shower generator, the uncertainty in the value of $\alpha_\text{s}$ when modelling initial-state radiation (ISR), and
+the choice of renormalisation scale when modelling final-state radiation (FSR).
 %%An uncertainty of  6\% is assigned to the inclusive $\ttbar$ production
@@
 The $h_{\mathrm{damp}}$ parameter, which controls the amount of radiation produced by the parton shower in
-\powheg~v2, is set to 1.5$m_t$ in the $t\bar t$ sample. Alternative sample is generated with $h_{\mathrm{damp}}$=3$m_t$. The
-difference between two samples is treated as a systematic called ``$t\bar{t}$ $h_{\mathrm{damp}}$''. 
+\powheg\,v2, is set to 1.5$m_t$ in the $t\bar t$ sample. An alternative sample was generated with $h_{\mathrm{damp}}=3m_t$. The
+difference between the two samples is treated as a systematic uncertainty called `$t\bar{t}$ $h_{\mathrm{damp}}$'. 
 %The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
@@
 The uncertainty due to the choice of parton shower and hadronisation (PS \& Had) model is derived 
-by comparing the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}.
-The latter uses the MMHT2014 LO~\cite{Harland-Lang:2014zoa} PDF set in combination with the H7UE tune~\cite{Bellm:2015jjp}.
-The uncertainty on the modelling of additional radiation from the PS is assessed by
+by comparing the predictions from {\powheg} interfaced either to \textsc{Pythia\,8} or \textsc{Herwig\,7}.
+The latter uses the \textsc{MMHT2014lo}~\cite{Harland-Lang:2014zoa} PDF set in combination with the H7UE tune~\cite{Bellm:2015jjp}.
+The uncertainty in the modelling of additional radiation from the PS is assessed by
 varying the corresponding parameter of the A14 set~\cite{ATL-PHYS-PUB-2016-004} and by varying the radiation renormalisation and factorisation scales
@@
 
-Another significant background to the hadronic channel stems from the $Z\rightarrow \tau\tau$ samples. Several sources of uncertainty are
+Another significant background in the hadronic channel stems from the $Z\rightarrow \tau\tau$ samples. Several sources of uncertainty are
 considered for these samples: the PDF variation, which is evaluated by considering the standard deviation
-produced by 100 NNPDF replicas event weights of NNPDF3.0nnlo~\cite{Ball:2015NNPDF} PDF set used in Sherpa,
-renormalisation ($\mu_{R}$) and factorisation scales ($\mu_{F}$), jet-to-parton matching uncertainty, resummation scale uncertainty,
-variation in the choice of $\alpha_{S}$, and alternative PDF use, which is evaluated by comparing predictions from NNPDF3.0nnlo PDF set (nominal)
-with those of MMHT2014nnlo68cl and CT14nnlo~\cite{Lai:2010vv,Gao:2013xoa} PDF sets.
+produced by the event weights from the 100 NNPDF replicas for the \textsc{NNPDF3.0nnlo}~\cite{Ball:2015NNPDF} PDF set used in \sherpa,
+the renormalisation ($\mu_\text{r}$) and factorisation ($\mu_\text{f}$) scales, the jet-to-parton matching uncertainty, the resummation scale uncertainty,
+the variation in the choice of $\alpha_\text{s}$, and the use of alternative PDFs, which is evaluated by comparing predictions from the \textsc{NNPDF3.0nnlo} PDF set (nominal)
+with those from the \textsc{MMHT2014nnlo68cl} and \textsc{CT14nnlo}~\cite{Lai:2010vv,Gao:2013xoa} PDF sets.
 
@@
 difference between the data and the total background prediction in the different analysis regions considered, but requiring exactly zero, one, and two $b$-jets.
-This is mainly driven by the disagreement between MC simulations in the $V$+jets regions with a high multiplicity of jets.  
+This is driven mainly by differences between MC simulations in the $V$+jets regions with a high multiplicity of jets.  
 %Agreement between data and predicted background 
@@
 Uncertainties affecting the modelling of the single-top-quark background include a 
-$+5\%$/$-4\%$ uncertainty on the total cross section, which is estimated as a weighted average 
+$+5\%$/$-4\%$ uncertainty in the total cross section, which is estimated as a weighted average 
 of the theoretical uncertainties in $t$-, $tW$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
-Additional uncertainties associated with the parton shower, hadronisation and ISR/FSR radiations are also considered by using the same procedure
+Additional uncertainties associated with the parton shower, hadronisation and ISR/FSR radiation are also considered by using the same procedure
 as for $t\bar t$.
-Uncertainties on the diboson background normalisation include variations of the renormalization and factorization scales, NNPDF3.0nnlo variations and $\alpha_{S}$ variations.
-Uncertainties of the $\ttbar V$ and $\ttbar H$ cross sections are 12\% and [$+5.8\%/-9.2\%$], respectively,
-from the uncertainties on their respective NLO theoretical cross sections~\cite{ttZRun2}.
+Uncertainties in the diboson background normalisation include those estimated from variations of the renormalisation and factorisation scales,  \textsc{NNPDF3.0nnlo} variations and $\alpha_\text{s}$ variations.
+Uncertainties in the $\ttbar V$ and $\ttbar H$ cross sections are estimated to be 12\% and [$+5.8\%/-9.2\%$], respectively,
+from the uncertainties in their respective NLO theoretical cross sections~\cite{ttZRun2}.
 
@@
 
-The statistical uncertainties on the fake tau background calibration in the leptonic channel are applied with uncorrelated uncertainties for
-different fake tau sources and different $\pt$ slices. The uncertainties on the MC modelling of the various processes used for
+The statistical uncertainties of the fake-$\tau$-background calibration in the leptonic channels are applied with uncorrelated uncertainties for
+different sources of fake $\tau$-leptons and different $\pt$ slices. The uncertainties in the MC modelling of the various processes used for
 evaluation of the fake factors in the CRtt are treated as fully correlated in the fit.
-The uncertainty on the ABCD method is applied to the normalisation factors for muons and electrons,including both
-its statistical fluctuation and the differences in the normalisation factors between the leptonic channels.
-The uncertainties on the fake factor method applied to the hadronic channel includes statistical uncertainties on each fake factor and
-different sets of fake factors derived from different signal-depleted CRs.
+The uncertainty in the ABCD method is applied to the normalisation factors for muons and electrons, including both
+its statistical fluctuation and the differences between the normalisation factors for the various leptonic channels.
+The uncertainties in the fake-factor method applied to the hadronic channel includes the statistical uncertainty of each fake factor and
+differences between the sets of fake factors derived from different signal-depleted CRs.
 %The uncertainties on the MC modelling of the various processes used for
@@
 Several normalisation and shape uncertainties are taken into account and are treated as fully correlated for the $\Hq$ and $pp\to tH$ signals.
-Uncertainties on the Higgs boson branching ratios are taken
+Uncertainties in the Higgs boson branching ratios are taken
 %from the measured values in Ref.~\cite{Zyla:2020zbs}.
 into account by following the recommendation in Ref.~\cite{deFlorian:2016spz}.
-The uncertainty due to ISR, FSR, scale and PDF are considered and are treated as fully correlated in all SRs. The parton shower uncertainties are estimated by comparing
-the nominal sample to an alternative sample interfaced with {\herwig7}.
+The uncertainties due to ISR, FSR, the scales, and the PDFs, are considered and are treated as fully correlated in all SRs. The parton shower uncertainties are estimated by comparing
+the nominal sample with an alternative sample interfaced with \textsc{Herwig\,7}.
 %the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 

### 2022-06-30 sections/background_estimation.tex

@@
 In the simulation, the top-quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
-and the Higgs boson is forced to decay via $H\to \tau\tau$ with branching ratio calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
-Backgrounds with non-prompt light leptons (electron or muon), with photons or jets misidentified as electrons, or with jets misidentified as tau candidates, 
+and the Higgs boson is forced to decay via $H\to \tau\tau$ with a branching ratio calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
+Backgrounds with non-prompt light leptons (electron or muon), with photons or jets misidentified as electrons, or with jets misidentified as $\tau$-lepton candidates, 
 generically referred to as fake leptons, are estimated using data-driven methods. 
 %\texttt{fake} 
-The background prediction is further improved during the statistical analysis by performing a likelihood 
+The background prediction is improved during the statistical analysis by performing a likelihood 
 fit to data using several signal-depleted control regions as shown in Table~\ref{tab:srcr}.
@@
 %-------------------------------------------------------------------------------
-\subsection{Backgrounds with fake tau leptons}
+\subsection{Backgrounds with fake $\tau$-leptons}
 \label{sec:faketaus}
-The background with one or more fake tau candidates mainly arises from $\ttbar$ or
-multi-jet production, depending on the search channels.
-Studies based on simulation show that, for all the above processes, fake tau candidates primarily result from the
+The background with one or more fake $\tau$ candidates arises mainly from $\ttbar$ or
+multi-jet production, depending on the search channel.
+Studies based on simulation show that, for all the above processes, fake $\tau$ candidates primarily result from the
 misidentification of light jets and $b$-quark jets.
-It is also found that the fake rate decreases for all jet flavours as the tau candidate $\pt$ increases.
+It is also found that the fake rate decreases for all jet flavours as the $\tau$ candidate's $\pt$ increases.
 
-In the leptonic channels, the events with a prompt electron or muon and fake taus are modelled by calibrating the MC with scale factors (SF)
+In the leptonic channels, the events with a prompt electron or muon and fake $\tau$-leptons are modelled by calibrating the MC samples with scale factors (SF)
 derived from the dedicated $t\bar t$
-control regions (CRtt) using dileptonic decays of $t\bar t$ events and semileptonic decays of $t\bar t$ events with two
-$b$-jets, as is summarized in Table~\ref{tab:srcr}. The control regions are defined similarly to the signal regions but with an additional $b$-jet or light lepton. 	
+control regions (CRtt) using dileptonic decays of $t\bar t$ pairs and semileptonic decays of $t\bar t$ pairs with two
+$b$-jets, as is summarised in Table~\ref{tab:srcr}. The control regions are defined similarly to the signal regions but with an additional $b$-jet or light lepton. 	
 %the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
 %aimed at fake taus from different origins.
-There are four kinds of fake taus that need to be calibrated: Type-1 fake taus from hadronic $W$ boson decay ($\tau_{W}$) %$W$-jets ($\tau_{W}$)
+There are four kinds of fake $\tau$-leptons that need to be calibrated: Type-1 fake $\tau$-leptons from hadronic $W$ boson decay ($\tau_{W}$) %$W$-jets ($\tau_{W}$)
 with opposite-sign (OS) charge relative to the light lepton;
-Type-2 $\tau_{W}$'s with same-sign (SS) charge relative to the light lepton; Type-3 fake taus originating from $b$-hadron decays; Type-4 fake taus from light-flavour hadron decays.
+Type-2 $\tau_{W}$'s with same-sign (SS) charge relative to the light lepton; Type-3 fake $\tau$-leptons originating from $b$-hadron decays; and Type-4 fake $\tau$-leptons from light-flavour hadron decays.
 %The control regions are defined similar to the signal regions but with an additional $b$-jet or light lepton.
 %$t_{\ell}t_{\ell}1b\thad$, $t_{\ell}t_{\ell}2b\thad$, $t_{\ell}t_h2b\thad$-2jSS, $t_{\ell}t_h2b\thad$-2jOS, $t_{\ell}t_h2b\thad$-3jSS, and $t_{\ell}t_h2b\thad$-3jOS.
-The dilepton regions ($t_{\ell}t_{\ell}1b\thad$ and $t_{\ell}t_{\ell}2b\thad$) are used to calibrate Type-3 and Type-4 fake taus. The semileptonic
-regions ($t_{\ell}t_h2b\thad$-2jOS and $t_{\ell}t_h2b\thad$-3jOS), where the $\thad$ and light lepton have opposite charges, are used to calibrate Type-1 fake taus.
+The dilepton regions ($t_{\ell}t_{\ell}1b\thad$ and $t_{\ell}t_{\ell}2b\thad$) are used to calibrate Type-3 and Type-4 fake $\tau$-leptons. The semileptonic
+regions ($t_{\ell}t_h2b\thad$-2jOS and $t_{\ell}t_h2b\thad$-3jOS), where the $\thad$ and light lepton have opposite charges, are used to calibrate Type-1 fake $\tau$-leptons.
 Similarly for Type-2, the semileptonic regions ($t_{\ell}t_h2b\thad$-2jSS and $t_{\ell}t_h2b\thad$-3jSS), where the $\thad$ and light lepton have same charges, are used.
-A simultaneous fit to data is made to derive the scale factors for fake taus in the MC. These consist of a total of 24 parameters
-depending on four types of fake taus, three $\pt$ bins, and two bins for 1- and 3-prong taus separately. The post-fit distributions of the
-leading $\thad$ $\pt$ and measured tau scale factors are presented in Appendix~\ref{sec:tauFF_appendix}. 
-The values of these scale factors range from 0.3 to 1.28 and are then used to correct the MC-estimated fakes in the corresponding  signal regions with a single $b$-jet.
-In the $t_{\ell}\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the same procedure used in the $\tlhad$ channel.
+A simultaneous fit to data is made to derive the scale factors for fake $\tau$-leptons in the MC samples. These consist of a total of 24 parameters
+depending on four types of fake $\tau$-leptons, three $\pt$ bins, and two bins for 1- and 3-prong $\tau$ decays separately. The post-fit distributions of the
+leading $\thad$ $\pt$ and measured $\tau$ scale factors are presented in Appendix~\ref{sec:tauFF_appendix}. 
+The values of these scale factors range from 0.3 to 1.28 and are used to correct the MC-estimated fakes in the corresponding  signal regions with a single $b$-jet.
+In the $t_{\ell}\thadhad$ channel, both $\tau$ candidates can be misidentified, so the calibration is applied to each $\tau$ candidate separately, following the same procedure used in the $\tlhad$ channel.
 %using the lepton and fake tau charges, then the scale factors are multiplied together.
-The central value of scale factors vary according to their uncertainties in the final fit. A closure test is made for the fake tau estimates using the same procedure
+The central values of the scale factors vary according to their uncertainties in the final fit. A closure test is made for the fake-$\tau$ estimates, using the same procedure as
 in the $t_{\ell}\thadhad$-SS validation region, and it shows good agreement between data and the background prediction. 
@@
 
-In the hadronic channels, the contribution of fakes is estimated from data using the fake-factor (FF) method to derive the transfer functions from the background enriched control
+In the hadronic channels, the contribution of fakes is estimated from data using the fake-factor (FF) method to derive the transfer functions from the background-enriched control
 regions (CR) to the SR~\cite{ATLAS-CONF-2021-044}.
@@
 The CR selection requirements are analogous to those used to define signal regions, except
-that the subleading tau candidate is required to fail the medium tau identification while still passing a loose requirement.
-The contribution of fakes with subleading tau candidates can be calculated by rescaling the templates of loose taus in the CR
+that the subleading $\tau$ candidate is required to fail the `medium' $\tau$ identification while still passing a loose requirement.
+The contribution of fakes with subleading $\tau$ candidates can be calculated by rescaling the templates for `loose' $\tau$ candidates in the CR
 with the FFs.
-The templates are produced by subtracting all MC background contributions with real subleading taus from the data.
-The FFs are computed as the ratio of misidentified $\thad$ candidates that either pass or fail the medium tau ID selection in regions enriched in events originating from 
+The templates are produced by subtracting all MC background contributions with real subleading $\tau$-leptons from the data.
+The FFs are computed as the ratio of misidentified $\thad$ candidates that either pass or fail the `medium' $\tau$ ID selection in regions enriched in events originating from 
 $W$+jets processes~\cite{ATLAS-CONF-2021-044}. 
@@
 %We have compared
-FFs obtained from the $W$+jets and from the same-sign $\thadhad$ control regions are compared and the difference is treated as a systematic uncertainty.
+FFs obtained from the $W$+jets events are compared with those from the same-sign $\thadhad$ control regions and the differences are treated as systematic uncertainties.
 
 \subsection{Background with fake light leptons}
-The background originating from non-prompt or misidentified light leptons is primarily from the multi-jet production.
+The background originating from non-prompt or misidentified light leptons is primarily from multi-jet production.
 %Electrons and muons only appear in the leptonic channels where exactly one electron or muon and at least one $\had$ are required.
@@
 The contribution from these events is estimated with a data-driven method called ABCD.
-The estimate is based on the number of tight and loose light-leptons that passed and failed the PLIV cut in the low ($<25~\gev$) and high
+The estimate is based on the numbers of `tight' and `loose' light leptons that passed and failed the PLIV cut in the low ($<25~\gev$) and high
 ($>25~\gev$) $\met$ regions. The number of
-fake light leptons in the signal region is evaluated by scaling the number of loose leptons in the high $\met$ region by the ratio of tight and loose leptons in the
-low $\met$ region. The contributions of prompt leptons and calibrated fake taus to the number of tight and loose leptons are subtracted using MC simulation.
-A closure test is made for the background estimates in the signal depleted low BDT ($<-0.6$) regions, defined in Section~\ref{sec:tmva}.
+fake light leptons in the signal region is evaluated by scaling the number of `loose' leptons in the high $\met$ region by the ratio of `tight' leptons to `loose' leptons in the
+low $\met$ region. The contributions of prompt leptons and calibrated fake $\tau$-leptons to the numbers of `tight' and `loose' leptons are subtracted using MC simulation.
+A closure test is made for the background estimates in the signal-depleted low-BDT-score ($<-0.6$) regions, defined in Section~\ref{sec:tmva}.
 The data are in good agreement with the background prediction in the

### 2022-06-30 sections/bdt_Htautau.tex

@@
 The ranking of the input variables according to their importance in the training is reported from highest (1) to 
-lowest (n). Variables whose ranking is missing are not included in the training of the corresponding SR. The description of each variable is provided in the text.}}
+lowest (n). Variables whose ranking is missing are not included in the training of that SR. The description of each variable is provided in the text.}}
 %Variables are ranked from highest (1) to lowest (n) relative to one another by their
@@
  \centering
+ \vspace{0.2cm}
  \begin{tabular}{cccccccc} \toprule\toprule
-   & $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_{\ell}2\tauhad$     & $t_h2\tauhad$-2j & $t_h2\tauhad$-3j       \\\midrule
-   Total variables~(n)                           & $12$ & $15$ & $12$ & $17$ & $15$ & $12$ & $12$ \\\midrule 
+   & $t_{\ell}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{\ell}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_{\ell}2\tauhad$     & $t_h2\tauhad$-2j & $t_h2\tauhad$-3j       \\\midrule
+   Total variables~(n)                           & $12$~~ & $15$~~ & $12$~~ & $17$~~ & $15$~~ & $12$~~ & $12$~~ \\\midrule 
  $m_{\text{jj}}$                                      &   &             &           & $9$      &       & $6$      & $7$\\
- $\chi^{2}$                                          &   &             &           & $14$     &       &  &       \\
- \text{max}($\eta_{\tau}$)                           & $4$       &             &  $4$              &  & $10$          &  &        \\
- $m^{W}_{\text{T}}$                           & $11$      &             &  $8$              &  & $13$          &  &         \\
+ $\chi^{2}$                                          &   &             &           & $14$~~     &       &  &       \\
+ \text{max}($\eta_{\tau}$)                           & $4$       &             &  $4$              &  & $10$~~          &  &        \\
+ $m^{W}_{\text{T}}$                           & $11$~~      &             &  $8$              &  & $13$~~          &  &         \\
  $m_{\tau\tau,\text{fit}}$                                     &   &  $2$                &           & $3$      &       & $1$      & $1$          \\
- $m_{\text{bjj},\text{fit}}$                            &   &  $1$                &           & $2$      &       & $3$      & $4$          \\
- ${\pt}^{\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     &       &  &         \\
- $m_{\tau\tau\text{q},\text{fit}}$                          &   &             &           &  &       & $10$     & $6$\\
- $m_{\text{bjj}}$                 & $3$       &             &  $5$              &  & $4$           &  &         \\
- ${\pt}_{\tau1}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
- $\met$                                              & $5$       &  $11$               &  $10$             & $13$     & $6$           & $7$    & $13$          \\
- $m_{\tau\tau}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
- $E_{\tau1}/E_{\tau1,\text{fit}}$                  &   &  $10$               &           & $12$     &       & $8$    & $8$          \\
- $E_{\tau2}/E_{\tau2,\text{fit}}$                  &   &  $7$                &           & $4$      &       & $9$    & $11$         \\
+ $m_{\text{bjj}}$                            &   &  $1$                &           & $2$      &       & $3$      & $4$          \\
+ ${\pt}^{\ell}$                                 & $12$~~      &  $15$~~               &  $12$~~             & $17$~~     &       &  &         \\
+ $m_{\tau\tau\text{q},\text{fit}}$                          &   &             &           &  &       & $10$~~     & $6$\\
+ $m_{\ell \text{b}}$                 & $3$       &             &  $5$              &  & $4$           &  &         \\
+ ${\pt}_{\tau1}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$~~   & $10$~~           \\
+ $\met$                                              & $5$       &  $11$~~               &  $10$~~             & $13$~~     & $6$           & $7$    & $13$~~          \\
+ $m_{\tau\tau}$                           & $10$~~      &  $14$~~               &  $11$~~             & $6$      & $1$           & $2$    & $2$          \\
+ $E_{\tau1}/E_{\tau1,\text{fit}}$                  &   &  $10$~~               &           & $12$~~     &       & $8$    & $8$          \\
+ $E_{\tau2}/E_{\tau2,\text{fit}}$                  &   &  $7$                &           & $4$      &       & $9$    & $11$~~         \\
  ${\pt}_{\tautau} $                          &   &             &           &  & $9$           &  &         \\
  $m_{\tau\tau\text{q}}$               &   &             &           &  & $3$           &  &        \\
- $\Delta\phi(\tau\tau,\met)$                         &   &  $6$                            &           & $16$     &       & $13$   & $12$         \\
- $\met\text{centrality}$                             &   &  $13$               &           & $15$     &       & $12$   & $9$         \\
- \text{min}($m_{\tau\tau \text{j}}$)             & $9$       &             &  $3$              &  & $14$          &  &         \\
- \text{min}($\Delta R(\ell,\tau)$)                               & $8$       &  $9$                &  $9$              & $10$     & $15$          &  &         \\
+ $\Delta\phi(\tau\tau,\met)$                         &   &  $6$                            &           & $16$~~     &       & $13$~~   & $12$~~         \\
+ $\met\text{\,centrality}$                             &   &  $13$~~               &           & $15$~~     &       & $12$~~   & $9$         \\
+ \text{min}($m_{\tau\tau \text{j}}$)             & $9$       &             &  $3$              &  & $14$~~          &  &         \\
+ \text{min}($\Delta R(\ell,\tau)$)                               & $8$       &  $9$                &  $9$              & $10$~~     & $15$~~          &  &         \\
  $\Delta R(\tau,\tau)$                               &   &             &           &  & $2$           & $4$    & $3$             \\
- $\Delta R(\ell,\text{$b$-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          &  &         \\
- $\Delta R(\tau1,\text{$b$-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          &  &        \\
+ $\Delta R(\ell,\text{$b$-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$~~          &  &         \\
+ $\Delta R(\tau1,\text{$b$-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$~~          &  &        \\
  $\Delta R(\ell+\text{$b$-jet},\tau\tau )$             &   &             &           &  & $7$           &  &         \\
  $\Delta R(\tau1,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
- \text{min}($m_{\text{jj}}$) &   &  $12$               &           & $11$     &       &  &         \\
+ \text{min}($m_{\text{jj}}$) &   &  $12$~~               &           & $11$~~     &       &  &         \\
 % $m_{\text{W}}$                                      & $\times$  &  $\times$           &  $\times$         & $9$      & $\times$      & $6$      & $7$\\
@@
 %draft 1 version
-In the training process, all signal events from $tt(qH)$ and $tH$ are merged together for $tuH$ and $tcH$. All background sources from SM processes
-(including both real and fake tau contributions) are also used in the training.
+In the training process, all signal events from $tt(qH)$ and $tH$ are combined for $tuH$ and $tcH$. All background sources from SM processes
+(including both the real and fake $\tau$ contributions) are also used in the training.
 
-Many potential variables are investigated in each SR separately.
-The discrimination of a given variable is quantified by the "separation" (which measures the degree of overlap between background and signal shape) and "importance" (which depicts the power of the variable in the classification of the events) provided by the TMVA package.%~\cite{Hocker:2007ht}.
+Many potential variables were investigated in each SR separately.
+The discrimination of a given variable is quantified by the `separation' (which measures the degree of overlap between background and signal distribution shape) and `importance' (which ranks the power of the variable in the classification of the events) provided by the TMVA package.
+%~\cite{Hocker:2007ht}.
 The BDT discriminant is trained for each SR starting from a large list of variables; then the least important variables are removed sequentially, and the BDT is retrained until the
@@
 %and only those variables whose importance is larger than 2\% were kept.
-The final BDT input variables in each SR and their importance ranking are listed in Table~\ref{tab:importance}. The discriminating variables are as follows.
+The final BDT input variables in each SR and their importance ranking are listed in Table~\ref{tab:importance}. The discriminating variables are as follows:
 \begin{itemize}
 \item $\met$ is the missing transverse momentum.
-\item ${\pt}_{\tau1} $ is the transverse momentum of the leading tau candidate.
-\item ${\pt}_{\tau2}$ is the transverse momentum of the subleading tau candidate.
+\item ${\pt}_{\tau1} $ is the transverse momentum of the leading $\tau$-lepton candidate.
+\item \text{max}($\eta_{\tau}$) is the maximum $\eta$ of the $\tauhad$ candidate(s). 
+%\item ${\pt}_{\tau2}$ is the transverse momentum of the subleading $\tau$-lepton candidate.
 \item ${\pt}^{\ell}$ is the transverse momentum of the leading light lepton.
-\item $\chi^2$ of the kinematic fit of the momentum of the invisible decay products of the tau leptons as defined in Eq.~(\ref{eq:eq1}).
-\item $m_{\text{bjj},\text{fit}}$ is the fitted invariant mass of the $b$-jet and the two jets from the $W$ boson decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$.
+\item $\chi^2$ of the kinematic fit of the momentum of the invisible decay products of the $\tau$-leptons as defined in Eq.~(\ref{eq:eq1}).
+\item $m_{\text{bjj}}$ is the invariant mass of the $b$-jet and the two jets from the $W$ boson decay, and reflects the top-quark mass in the decay $t\to Wb \to j_1j_2b$.
 This variable is only defined for the 4-jet $t_hH$ and $t_ht(qH)$ events.
 \item $m^{W}_{\text{T}}$ is the transverse mass calculated from the lepton and $\met$ in the leptonic channels, defined as
-\begin{equation}
+\begin{equation*}
 m^{W}_{\text{T}} = \sqrt{2 {\pt}_{\ell} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\ell,\text{miss}} \right)},  
-\end{equation}
-where $\Delta\phi_{\ell,\text{miss}}$ is the azimuthal angle between the light-lepton and $\met$.  
-\item $m_{\tau\tau,\text{fit}}$ is the fitted invariant mass of the tau candidates and reconstructed neutrinos for the $t_hH$ and $t_ht(qH)$ events. 
-\item $m_{\text{jj}}$ is the reconstructed invariant mass of two light-jets from the $W$ decay with the mass closest to the $W$ mass.
-\item $m_{\tau\tau\text{q},\text{fit}}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from the di-tau candidates, $q$-jet and reconstructed neutrinos.
-\item $m_{\tau\tau}$ is the visible invariant mass of the di-tau system. %or the lepton and $\had$ candidate when there is only one $\had$.
-\item ${\pt}_{\tau\tau}$ is the visible $\pT$ of the di-tau system.
+\end{equation*}
+where $\Delta\phi_{\ell,\text{miss}}$ is the azimuthal angle between the light lepton and $\met$.  
+\item $m_{\tau\tau,\text{fit}}$ is the fitted invariant mass of the $\tau$ candidates and reconstructed neutrinos for the $t_hH$ and $t_ht(qH)$ events. 
+\item $m_{\text{jj}}$ is the reconstructed invariant mass of two light jets from the $W$ decay with a mass closest to the known $W$ boson mass.
+\item $m_{\tau\tau\text{q},\text{fit}}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from the di-$\tau$ candidates, $q$-jet and reconstructed neutrinos.
+\item $m_{\tau\tau}$ is the visible invariant mass of the di-$\tau$ system (including the light lepton when there is only one $\had$ candidate).
+\item ${\pt}_{\tau\tau}$ is the visible $\pT$ of the di-$\tau$ system.
 \item $m_{\tau\tau,\text{q}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
-\item $m_{\text{bjj}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top quark mass.
-\item \text{min}($m_{\tau\tau \text{j}}$) is the minimum value of the visible mass of the di-tau candidates (including leptonically decaying tau) and the light-flavour jet system,
-  reflecting the invariant mass of the visible FCNC top decaying products.
+\item $m_{\ell \text{b}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top-quark mass.
+\item \text{min}($m_{\tau\tau \text{j}}$) is the minimum value of the visible mass of the di-$\tau$ candidates (including leptonically decaying $\tau$ candidates) and the light-flavour jet,
+  reflecting the invariant mass of the visible FCNC top-quark decay products.
 \item \text{min}($m_{\text{jj}}$) is the minimum value of the invariant mass of all the light-flavour jet pairs, reflecting the invariant mass of the $W$ boson candidate.
   %an alternative of $m_{\text{W}}$.
-\item $\met$ centrality is a measure of how centrally the $\met$ lies between the two tau candidates in the transverse plane, and is defined as
-\begin{eqnarray}
+\item $\met$ centrality is a measure of how centrally the $\met$ lies between the two $\tau$ candidates in the transverse plane, and is defined as
+\begin{eqnarray*}
 \begin{array}{l}
@@
 \label{eq:eq3}
-\end{eqnarray}
-\item $E_{\tau\text{i}}/E_{\tau\text{i},\text{fit}}$ (\text{i}=1,2) is the momentum fraction carried by the visible decay products from the leading and subleading tau decays.
-It is based on the best-fit of the 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section.
-For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}.
+\end{eqnarray*}
+\item $E_{\tau {i}}/E_{\tau {i},\text{fit}}$ $({i}=1,2)$ is the momentum fraction carried by the visible decay products from the leading and subleading $\tau$ decays.
+It is based on the best fit of the four-momentum of the neutrino(s) according to the event reconstruction algorithm in this section.
+For the $\tauhad$ decay mode, the visible decay products carry most of the $\tau$-lepton's energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}.
 %\item $\Delta R(\ell+\text{b-jet},\tau\tau)$ is the angular distance between the lepton+$b$-jet and di-tau candidates.
@@
 %\item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(\ell,\tau)$.
-\item $\Delta\phi(\tau\tau,\met)$ is the azimuthal angle between the $\met$ and di-tau system $\pT$.
-\item $\Delta R(a,b)$ is the angular distance between the \text{a} and \text{b} objects in the event. 
+\item $\Delta\phi(\tau\tau,\met)$ is the azimuthal angle between the $\met$ and di-$\tau$ system's $\pT$.
+\item $\Delta R(a,b)$ is the angular distance between the $a$ and $b$ objects in the event. 
 %\item $\Delta R(\tau1,\text{light-jet})$ is the minimum angle distance between the tau candidate and the light-jet. If there are two taus in the event, the leading one is used.
@@
 
-Comparisons between the data and the predicted background for the leading $\had$ $\pt$  and the visible invariant mass of the di-tau system ($m_{\tau\tau}$)
-distributions in SRs and VRs, after applying fake factors, 
+Comparisons between the data and the predicted background for the distributions of leading $\had$ $\pt$  and visible invariant mass of the di-$\tau$ system ($m_{\tau\tau}$)
+in SRs and VRs, after applying fake factors, 
 %some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
@@
 %The hashed area represents the total uncertainty of the background.
-A good description of the data by the background model is observed in all cases.
-The final observable used to extract the signal contribution is the BDT distribution in each SR corresponding to either the $tuH$ or the $tcH$ signal.
+The data are well described by the background model in all cases.
+The final observable used to extract the signal contribution is the BDT distribution in each SR corresponding to either the $tuH$ or $tcH$ signal.
 
@@
 \end{tabular}
-\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (``Pre-Fit'') showing 
-  the expected background and $tuH$ signals after applying fake factors in the following regions: $t_{\ell}\thadhad$ (a),
- $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS  (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
- The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
+\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (`Pre-Fit') showing 
+  the expected background and $tuH$ signals after applying fake factors in the following regions: (a) $t_{\ell}\thadhad$,
+ (b) $t_{\ell}\tauhad$-1j,  (c) $t_{\ell}\tauhad$-2j, (d) $t_h\tlhad$-2j, (e) $t_h\tlhad$-3j, (f) $t_{\ell}\thadhad$-SS, (g) $t_h\thadhad$-2j, (h) $t_h\thadhad$-3j and (i) $t_h\thadhad$-3j SS.
+ The total statistical and systematic uncertainty of the background prediction is indicated by the hatched band.
  %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
- Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, $V$+jets, and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signals are scaled using
- normalization factors of 2 to 50.   
+ Overflow events are included in the last bin. `Other MC' (`Rare') includes single-top, $V$+jets, and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled by a
+ normalisation factor of either 2, 10, or 50.   
 %( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
-The lower panels show the data to prediction ratio.}
+The lower panels show the ratio of data to prediction.}
 \label{fig:taupt_prefit}
@@
 \end{tabular}
-\caption{Visible invariant mass of the di-tau system ($m_{\tau\tau}$) distributions obtained before the fit to data (``Pre-Fit'') showing 
-  the expected background and $tuH$ signals after applying fake factors in the following regions: $t_{\ell}\thadhad$ (a),
- $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
- The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
+\caption{Distributions of the visible invariant mass of the di-$\tau$ system ($m_{\tau\tau}$) obtained before the fit to data (`Pre-Fit') showing 
+  the expected background and $tuH$ signals after applying fake factors in the following regions: (a) $t_{\ell}\thadhad$,
+ (b) $t_{\ell}\tauhad$-1j,  (c) $t_{\ell}\tauhad$-2j, (d) $t_h\tlhad$-2j, (e) $t_h\tlhad$-3j, (f) $t_{\ell}\thadhad$-SS, (g) $t_h\thadhad$-2j, (h) $t_h\thadhad$-3j and (i) $t_h\thadhad$-3j SS.
+ The total statistical and systematic uncertainty of the background prediction is indicated by the hatched band.
  %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
  Overflow events are included in the last bin.
-``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel.
-The $tuH$ signal is scaled using a normalization factor of 2 to 50.
+`Other MC' (`Rare') includes single-top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel.
+The $tuH$ signal is scaled by a normalisation factor of either 2, 10, or 50.
 %( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
-The lower panels show the data to prediction ratio.}
+The lower panels show the ratio of data to prediction.}
 \label{fig:mtt}

### 2022-06-30 sections/detector.tex

@@
 The inner detector contains a high-granularity silicon pixel detector, including the %newly-installed
-insertable B-layer~\cite{IBL1,IBL2,Abbott:2018ikt}, installed in 2014, and a silicon microstrip tracker, together providing a precise reconstruction of tracks of charged particles in the pseudorapidity range $|\eta|<2.5$.
+insertable B-layer~\cite{IBL1,IBL2,Abbott:2018ikt} added as a new innermost layer in 2014, and a silicon microstrip tracker, together providing precise reconstruction of tracks of charged particles in the pseudorapidity range $|\eta|<2.5$.
 The inner detector also includes a transition radiation tracker that provides tracking and electron identification for $|\eta|<2.0$.

### 2022-06-30 sections/objects.tex

@@
 
-Events are selected from $pp$ collisions at $\sqrt{s}$=13 TeV recorded by the ATLAS detector during 2015-2018~\cite{DAPR-2018-01}.
+Events are selected from $pp$ collisions at $\sqrt{s}=13$~\TeV\ recorded by the ATLAS detector during 2015--2018~\cite{DAPR-2018-01}.
 Only events for which all relevant subsystems were operational are considered.
@@
 ($1.37 < |\eta_{\textrm{cluster}}| < 1.52$) are excluded.
-Electron candidates are required to have $|\eta_{\textrm{cluster}}| < 2.47$, and to satisfy tight likelihood-based identification 
+Electron candidates are required to have $|\eta_{\textrm{cluster}}| < 2.47$, and to satisfy `tight' likelihood-based identification 
 criteria~\cite{ATLAS-CONF-2016-024} based on calorimeter, tracking and combined variables that provide 
@@
 the resulting muon candidates are re-fitted using the complete track information from both detector systems.
-Muon candidates are required to satisfy medium identification criteria~\cite{Aad:2016jkr}.
+Muon candidates are required to satisfy `medium' identification criteria~\cite{Aad:2016jkr}.
 
@@
 %To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have \pt 1~GeV above the threshold.
-To further reduce the background from non-prompt leptons mostly originating from heavy-flavour hadron decays, photon conversions and misidentified hadrons,
+To further reduce the background from non-prompt leptons, which originate mostly from heavy-flavour hadron decays, photon conversions and misidentified hadrons,
 lepton candidates are also required to be isolated in the tracker and in the calorimeter.
-A track- and cluster-based lepton isolation criterion is defined by calculating the quantities $I_R = \sum \pt^{\textrm{trk}}$ and $E_R = \sum E^{\textrm{clst}}$, where
-the scalar sum includes all tracks $\pt^{\textrm{trk}}$ and cluster energy deposits $E^{\textrm{clst}}$ (excluding the lepton candidate itself)
+A track- and cluster-based lepton isolation criterion is defined by placing requirements on the quantities $I_R = \sum \pt^{\textrm{trk}}$ and $E_R = \sum E^{\textrm{clst}}$, where
+the scalar sum includes all tracks' $\pt^{\textrm{trk}}$ or cluster energy deposits $E^{\textrm{clst}}$ (excluding the lepton candidate itself)
 within the cone defined by $\Delta R<0.2~(0.3)$ around the %axis
@@
 %$I_R/\pt^l < 0.2~(0.3)$ and $E_R/\pt^l < 0.2~(0.3)$.
-$I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$ ($\ell=e$ or $\mu$).
+$I_R/\pt^\ell < 0.2~(0.3)$ and $E_R/\pt^\ell < 0.2~(0.3)$, where $\ell=e$ or $\mu$.
 
-Tight isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions based on a trained isolation boosted decision tree (BDT)
-\texttt{PromptLeptonVeto} (PLIV), which is used to identify non-prompt light leptons using lifetime information associated with a track jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}.
-These additional reconstructed charged particle tracks inside the jet can be
-used to increase the efficiency for identifying the displaced decay vertex of heavy flavour ($b$, $c$) hadrons that produced non-prompt leptons.
-The tight working points are used for high $\pt$ leptons ($>20~\GeV$).
-The scale factors for the efficiencies of the tight \texttt{PLIV} working points are measured using the tag and probe method~\cite{PERF-2016-01}
-with $Z\rightarrow \ell^+\ell^-$ events. These scale factors have also been checked for the electron or muon from the tau decay
-using $Z\rightarrow\tau\tau\rightarrow e\mu4\nu$ samples, which are consistent at the 2\% level. To be conservative, an
-additional uncertainty of $\pm 2\%$ is considered for the PLIV efficiency for the tau-lepton in the lepton+$\thad$ channels.
+`Tight' isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions by using a trained isolation boosted decision tree (BDT)
+\texttt{PromptLeptonVeto} (PLIV), which identifies non-prompt light leptons by using lifetime information associated with a track-jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}.
+These additional reconstructed charged-particle tracks inside the jet can be
+used to increase the efficiency for identifying the displaced decay vertices of heavy-flavour ($b$, $c$) hadrons that produced non-prompt leptons.
+The `tight' working points are used for leptons with high $\pt$ ($>20~\GeV$).
+Simulation-to-data scale factors for the efficiencies of the `tight' PLIV working points are measured using the tag-and-probe method~\cite{PERF-2016-01}
+with $Z\rightarrow \ell^+\ell^-$ events. These scale factors were checked for electrons or muons from the $\tau$-lepton decays
+using $Z\rightarrow\tau\tau\rightarrow e\mu4\nu$ samples, and are consistent at the 2\% level. To be conservative, an
+additional uncertainty of $\pm 2\%$ is considered for the PLIV efficiency for the $\tau$-lepton in the lepton+$\thad$ channels.
 %Additionally, the $\Htautau$ search requires leptons to
@@
 derived from simulation and in situ corrections based on $\sqrt{s}=13~\tev$ data~\cite{Aaboud:2017jcu}. %(TBD: check PFlow jets description)
-The calibrated jets used are required to have $\pt > 25~\gev$ and $|\eta| < 2.5$.
-The four-momentum of the jets is corrected for pile-up effects using the jet-area method~\cite{Cacciari:2008gn}.
+After being calibrated, the jets are required to have $\pt > 25~\gev$ and $|\eta| < 2.5$.
+The four-momentum of each jet is corrected for pile-up effects using the jet-area method~\cite{Cacciari:2008gn}.
 
@@
 
-Jets containing $b$-hadrons are identified ($b$-tagged) via the DL1r tagger~\cite{Aad:2019epj79,ATL-PHYS-PUB-2017-013} %newref
+Jets containing $b$-hadrons are identified ($b$-tagged) via the DL1r tagger~\cite{Aad:2019epj79,ATL-PHYS-PUB-2017-013}, %newref
 %\cite{Aad:2015ydr,ATL-PHYS-PUB-2016-012} 
-that uses multivariate techniques to combine information about the impact parameters of displaced tracks and the  topological properties 
+which uses multivariate techniques to combine information about the impact parameters of displaced tracks and the  topological properties 
 of secondary and tertiary decay vertices reconstructed within the jet. For each jet, a value for the multivariate $b$-tagging discriminant is 
 calculated. A jet is considered $b$-tagged if this value is above the threshold corresponding to
-an average 70\% efficiency to tag a $b$-quark jet, with a light-jet\footnote{Light-jet refers to a jet originating from the hadronisation of a light quark ($u$, $d$, $s$) or a gluon.} rejection factor of about 385 and a charm-jet rejection factor of about 12, as determined for jets with
+an average 70\% efficiency to tag a $b$-quark jet, with a light-jet\footnote{A `light jet' refers to a jet originating from the hadronisation of a light quark ($u$, $d$, $s$) or a gluon.} rejection factor of about 385 and a charm-jet rejection factor of about 12, as determined for jets with
 $\pt >20~\gev$ and $|\eta|<2.5$ in simulated $\ttbar$ events~\cite{Aad:2019epj79}.
 
-Hadronically decaying $\tau$-lepton ($\had$) candidates are reconstructed from energy clusters in the calorimeters and
+Hadronically decaying $\tau$-lepton ($\had$) candidates are reconstructed from calorimeter energy clusters and
 associated inner-detector tracks~\cite{ATL-PHYS-PUB-2019-033}. %newref
@@
 %Candidates are required to have \pt 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
-A Recurrent Neural Network (RNN)~\cite{Graves:2012SCI}
+A recurrent neural network (RNN)~\cite{Graves:2012SCI}
 %~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna}
@@
 using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject jet backgrounds.
-Three working points, labelled loose, medium and tight, are defined and correspond to different $\had$ identification efficiency values, with the efficiency designed to be independent of $\pt$.
-The $\Htautau$ search uses the medium
+Three working points, labelled `loose', `medium' and `tight', are defined and correspond to different $\had$ identification efficiency values, with the efficiency designed to be independent of $\pt$.
+The $\Htautau$ search uses the `medium'
 working point for the $\had$ selection.
 %, while the loose working point is used for background estimation.
-The medium working point has a combined reconstruction and identification efficiency of 75\% (60\%) for one-prong (three-prong) $\had$ 
-decays, and an expected rejection factor against light-jets of 35 (240)~\cite{ATL-PHYS-PUB-2019-033}. 
+The `medium' working point has a combined reconstruction and identification efficiency of 75\% (60\%) for one-prong (three-prong) $\had$ 
+decays, and an expected rejection factor of 35 (240) against light jets~\cite{ATL-PHYS-PUB-2019-033}. 
 Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
@@
 
-To avoid double counting reconstructed objects, an overlap removal procedure is applied.
+To avoid double-counting of reconstructed objects, an overlap removal procedure is applied.
 %Overlaps between reconstructed objects are removed sequentially.
@@
 if the jet is either $b$-tagged or has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
-The $\tauhad$ within a $\Delta R=0.2$ cone of an electron or muon are removed.
+The $\tauhad$ within a $\Delta R=0.2$ cone around an electron or muon are removed.
 In order to avoid double-counting of $\tauhad$ as jets, the closest jet whose axis is

### 2022-06-30 sections/tau_FF_appendix.tex

@@
-\section{Tau fake scale factor calibration in the CRtt}
+\section{Fake-$\thad$ scale factor calibration in the CRtt}
 \label{sec:tauFF_appendix}
@@
 Figure~\ref{fig:ttCR_mtt} presents the post-fit distributions of the leading $\thad$ $\pt$ in the CRtt. These show good agreement between the data and the fitted background model.
-Tables~\ref{tab:ff1_summary} and~\ref{tab:ff2_summary} summarize the fake scale factors of 1-prong and 3-prong taus
-derived from the CRtt including both statistical and systematic uncertainties.
+Tables~\ref{tab:ff1_summary} and~\ref{tab:ff2_summary} summarise the scale factors for 1-prong and 3-prong fake $\tau$ decays
+derived from the CRtt including both the statistical and systematic uncertainties.
 
@@
 \end{tabular}
-\caption{Leading $\thad$ $\pt$  distributions obtained after the fit to data (``Post-Fit'') for the $\thad$ fake scale factors in the following CRtt:
-  $t_{\ell}t_{h}$2b$\thad$-2j OS (a), $t_{\ell}t_{h}$2b$\thad$-2j SS (b), $t_{\ell}t_{h}$2b$\thad$-3j OS (c), $t_{\ell}t_{h}$2b$\thad$-3j SS (d),
-  $t_{\ell}t_{\ell}$1b$\thad$-nj (e) and $t_{\ell}t_{\ell}$2b$\thad$-nj (f).
-  The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
-  Overflow events are included in the last bin. The lower panels show the data-to-prediction ratio.}
+\caption{Leading $\thad$ $\pt$  distributions obtained after the fit to data (`Post-Fit') for the fake-$\thad$ scale factors in the following CRtt:
+  (a) $t_{\ell}t_{h}$2b$\thad$-2j OS, (b) $t_{\ell}t_{h}$2b$\thad$-2j SS, (c) $t_{\ell}t_{h}$2b$\thad$-3j OS, (d) $t_{\ell}t_{h}$2b$\thad$-3j SS,
+  (e) $t_{\ell}t_{\ell}$1b$\thad$-nj and (f) $t_{\ell}t_{\ell}$2b$\thad$-nj.
+  The total statistical and systematic uncertainty of the background prediction is indicated by the hatched band.
+  Overflow events are included in the last bin. The lower panels show the ratio of data to prediction.}
 \label{fig:ttCR_mtt}
@@
 \begin{table}
-\caption{ Summary of fake tau (1-prong) scale factors derived in the CRtt. The numbers are shown as: central values, statistical uncertainties, and systematics uncertainties. }
+\caption{ Summary of fake-$\tau$ (1-prong) scale factors derived in the CRtt. The numbers are shown as central values, statistical uncertainties, and systematics uncertainties. }
 \begin{center}
@@
 
-Fake tau types & \multicolumn{3}{c}{1-prong tau}  \\ \midrule
-$\thad$ $\pt$                                   &  $25-35$ GeV  & $35-45$ GeV  &  $45-$ GeV            \\
+Fake-$\tau$ types & \multicolumn{3}{c}{1-prong $\tau$ decay}  \\ \midrule
+$\thad$ $\pt$                                   &  25--35~\GeV  & 35--45~\GeV  &  $>45$~\GeV            \\
 \midrule
@@
 \begin{table}
-\caption{ Summary of fake tau (3-prong) scale factors derived in the CRtt. The numbers are shown as: central values, statistical uncertainties, and systematics uncertainties. }
+\caption{ Summary of fake-$\tau$ (3-prong) scale factors derived in the CRtt. The numbers are shown as central values, statistical uncertainties, and systematics uncertainties. }
 \begin{center}
@@
 
-Fake tau types        & \multicolumn{3}{c}{3-prong tau}  \\ \midrule
-$\thad$ $\pt$                             &  $25-35$ GeV  & $35-45$ GeV       &  $45-$ GeV  \\
+Fake-$\tau$ types        & \multicolumn{3}{c}{3-prong $\tau$ decays}  \\ \midrule
+$\thad$ $\pt$                             &  25--35~\GeV  & 35--45~\GeV       &  $>45$~\GeV  \\
 \midrule

### 2022-07-04 sections/introduction.tex
revised to V2.2

@@
 has been conducted to explore this particle. Measurements so far have proved to be consistent with the Standard Model (SM) predictions. 
-However, the programme is ongoing and precision measurements as well as searches for rare new-physics processes beyond the Standard Model (BSM)
+The programme is ongoing and precision measurements as well as searches for rare new-physics processes beyond the Standard Model (BSM)
 are underway. One such possibility is flavour-changing neutral current (FCNC) interactions between the Higgs boson, 
@@
 %ratios ($\BR$) are exceedingly small, $\BR(t\to Hu) \sim 10^{-17} $ and $\BR(t\to Hc) \sim 10^{-15}$~\cite{Eilam:1990zc,Mele:1998ag,AguilarSaavedra:2004wm,Zhang:2013xya}, making them undetectable in the foreseeable future.
-However, these branching ratios can be as high as $\BR(t\to qH) \sim 10^{-5}$ when processes beyond the SM are included.
+However, these branching ratios can be large enough to be observed at LHC 
+%as high as $\BR(t\to qH) \sim 10^{-5}$
+when processes beyond the SM are included.
 Examples of these processes include: quark-singlet models~\cite{AguilarSaavedra:2002kr}, two-Higgs-doublet models (2HDMs)~\cite{ Branco:2hdm2012} with or without flavour violation,

### 2022-07-22 sections/data_presel.tex
update to atlaslatex-13.5.0

@@
 To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have a \pt that is at least 1~\GeV\ above the threshold. 
-The reconstructed $\tau$-leptons are required to have a \pt at least 5~\GeV\ higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
+The reconstructed $\tau$-leptons are required to have a \pt at least 5~\GeV\ higher than the trigger threshold.
+%and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
 %The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
@@
 The events in the leptonic channels are recorded by a single-electron or single-muon trigger, and are required to have exactly one electron or muon that matches, within $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers.
-Requirements are placed on the following additional quantities.
+The following additional requirements are applied.
+%Requirements are placed on the following additional quantities.
 %Further requirements are defined targeting different signal decay modes:  

### 2022-07-22 sections/objects.tex
update to atlaslatex-13.5.0

@@
 the resulting muon candidates are re-fitted using the complete track information from both detector systems.
-Muon candidates are required to satisfy `medium' identification criteria~\cite{Aad:2016jkr}.
+Muon candidates are required to have $|\eta|<2.5$, and to satisfy `medium' identification criteria~\cite{Aad:2016jkr}.
 
@@
 Candidates are required to have either one or three associated tracks,
-with a total charge of $\pm 1$.
+with a total charge of $\pm 1$, and to have $\pt>25$ GeV with $|\eta|<2.5$, excluding the EM calorimeter's transition region.
 %Candidates are required to have \pt 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.

### 2022-07-22 sections/statistical_analysis.tex
update to atlaslatex-13.5.0

@@
 plus an injected signal of variable strength) as well as by performing fits to real data where bins of the final discriminating variable with 
-a signal contamination above 10\% are excluded (referred to as `blinding' requirements).
+an expected signal contamination above 10\%, assuming $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$, are excluded (referred to as `blinding' requirements).
 In both cases, the robustness of the model with respect to systematic uncertainties is established by verifying the stability of the fitted background 

### 2022-07-22 scripts/atlaslatex_2020.sh

@@ -1,0 +1,66 @@
+#! /bin/bash
+# Script to adjust atlaslatex documents to use atlaslatexpath style file.
+
+# Copyright (C) 2002-2022 CERN for the benefit of the ATLAS collaboration.
+
+# Changes:
+# 2020-11-23 Ian Brock (ian.brock@cern.ch): First version to get round TeX Live 2020 problem with directories in \usepackage etc.
+
+function cf_files {
+    # echo "Compare ${afile} with ${lfile}"
+    cmp --silent "$1" "$2"
+    cmpStatus=$?
+    # echo "cmp status is $cmpStatus" 
+    if [ $cmpStatus -eq 0 ]; then
+        echo "No change to file $1"
+    else
+        echo "Running diff on $1 vs $2:"
+        diff "$1" "$2"
+        echo "Will try to copy $2 to $1:"
+        cp -i "$2" "$1"
+    fi
+}
+
+DIR=`basename "${PWD}"`
+echo $DIR
+
+# Check we are in the right directory
+if [ -e ${DIR}.tex ]; then
+    echo "We are in directory ${PWD}."
+else
+    echo "We do not appear to be in the main directory: ${PWD}."
+    echo "There should be a tex file with the same name as the directory."
+    exit 1
+fi
+
+# Save a copy of the main file
+for lfile in ${DIR}.tex; do
+    npath=$(grep -c ATLASLATEXPATH ${lfile})
+    echo "ATLASLATEXPATH occurs ${npath} times in ${lfile}."
+    if [ $npath -le 0 ]; then
+        echo "\\ATLASSLATEXPATH not used - no changes needed."
+        exit 0
+    fi
+    cp ${DIR}.tex ${DIR}.tex.bak
+    bfile=${DIR}.tex.bak 
+    ATLASLATEXPATHDEF=$(grep -E '^\\newcommand\*\{\\ATLASLATEXPATH\}' ${bfile})
+    echo "ATLASLATEXPATH definition: ${ATLASLATEXPATHDEF}"
+    if [ -n ${ATLASLATEXPATHDEF} ]; then
+        sed -E 's|^\\newcommand\*\{\\ATLASLATEXPATH\}.*|\\RequirePackage\{latex/atlaslatexpath\}|' ${bfile} >${lfile}.tmp1
+    else
+        echo "ATLASLATEXPATH definition not found in ${lfile}."
[…]

### 2022-07-22 scripts/atlaslatex_update.sh

@@ -1,17 +1,19 @@
 #! /bin/bash
-# Script to update atlaslatex version from the Git master
+# Script to update atlaslatex version from the Git master.
 
-# Copyright (C) 2002-2018 CERN for the benefit of the ATLAS collaboration
+# Copyright (C) 2002-2022 CERN for the benefit of the ATLAS collaboration.
 
 # Changes:
-# 2018-08-14: BASENAME should be set correctly if Makefile is overwritten.
-
-# Remove temporary directory if it exists
-test -d tmp-atlaslatex && rm -r tmp-atlaslatex
+# 2018-08-14 Ian Brock (ian.brock@cern.ch): BASENAME should be set correctly if Makefile is overwritten.
+# 2019-04-16 Ian Brock (ian.brock@cern.ch): Only overwrite "BASENAME = ..." and not occurences without a space (in help).
+# 2020-11-21 Ian Brock (ian.brock@cern.ch): Check for use of \ATLASLATEXPATH and say atlaslatex_2020.sh should be run.
+# 2022-02-07 Ian Brock (ian.brock@cern.ch): Check that standard style files are all there.
 
 # Decide how to clone atlaslatex - ssh is default
 ATLASLATEXGIT=ssh://git@gitlab.cern.ch:7999/atlas-physics-office/atlaslatex.git
-while getopts shk opt; do
+BRANCH=''
+CLONE=1
+while getopts shkcd opt; do
     case $opt in
         s)
             ATLASLATEXGIT=ssh://git@gitlab.cern.ch:7999/atlas-physics-office/atlaslatex.git
@@ -22,37 +24,125 @@ while getopts shk opt; do
         k)
             ATLASLATEXGIT=https://:@gitlab.cern.ch:8443/atlas-physics-office/atlaslatex.git
             ;;
+        c)
+            CLONE=0
+            ;;
+        d)
+            BRANCH=devel
+            ;;
         \?)
             echo "$0 [-h] [-k] [-s]"
             echo "  -h use https GitLab link"
             echo "  -k use krb5 GitLab link"
             echo "  -s use ssh GitLab link"
+            echo "  -d use devel branch instead of master"
+            echo "  -c Copy scripts from local directory (mainly for testing)"
             exit 1
             ;;
     esac
 done
 
[…]

### 2022-07-22 scripts/tex_dollars.py

@@ -1,8 +1,8 @@
-#! /usr/bin/env python
+#! /usr/bin/env python3
 # Script to replace $...$ and $$...$$ with \(...\) and \[...\]
 # Note that this only works if $...$ is on one line.
 
-# Copyright (C) 2002-2018 CERN for the benefit of the ATLAS collaboration
+# Copyright (C) 2002-2022 CERN for the benefit of the ATLAS collaboration
 
 # Changes:
 # 2018-10-30 Ian Brock (ian.brock@cern.ch): First version of script.

### 2022-07-22 setup.sh

@@ -1,0 +1,1 @@
+export PATH=/cvmfs/sft.cern.ch/lcg/external/texlive/2020/bin/x86_64-linux:$PATH

### 2022-07-23 sections/background_estimation.tex
fix George's comments for V2.4

@@
 In the hadronic channels, the contribution of fakes is estimated from data using the fake-factor (FF) method to derive the transfer functions from the background-enriched control
-regions (CR) to the SR~\cite{ATLAS-CONF-2021-044}.
+regions (CR) to the SR~\cite{HIGG-2018-14}.
 %by defining control regions (CR)
@@
 The FFs are computed as the ratio of misidentified $\thad$ candidates that either pass or fail the `medium' $\tau$ ID selection in regions enriched in events originating from 
-$W$+jets processes~\cite{ATLAS-CONF-2021-044}. 
+$W$+jets processes~\cite{HIGG-2018-14}. 
 %the Data-MC ($\mathrm{real~tau}$) ratio of the yields of events in which the tau candidate is passing or failing the medium tau ID selection

### 2022-07-23 sections/bdt_Htautau.tex
revised to V2.2
fix George's comments for V2.4

@@
 lowest (n). Variables whose ranking is missing are not included in the training of that SR. The description of each variable is provided in the text.}}
-%Variables are ranked from highest (1) to lowest (n) relative to one another by their
-%      importance in the training. Variables which do not have a ranking are not included in the training. 
-%The values represent their ra importance rankings of each variable and cross($\times$) denotes the variable is not used in the training.
-%      The descriptions of each variable are provided in the following text.}}
 \label{tab:importance}
@@
    Total variables~(n)                           & $12$~~ & $15$~~ & $12$~~ & $17$~~ & $15$~~ & $12$~~ & $12$~~ \\\midrule
- $m_{\text{jj}}$                                      &   &             &           & $9$      &       & $6$      & $7$\\
+   $\met$                                              & $5$       &  $11$~~               &  $10$~~             & $13$~~     & $6$           & $7$    & $13$~~          \\
+   ${\pt}_{\tau1}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$~~   & $10$~~           \\
+   \text{max}($\eta_{\tau}$)                           & $4$       &             &  $4$              &  & $10$~~          &  &        \\
+   ${\pt}^{\ell}$                                 & $12$~~      &  $15$~~               &  $12$~~             & $17$~~     &       &  &         \\
    $\chi^{2}$                                          &   &             &           & $14$~~     &       &  &       \\
- \text{max}($\eta_{\tau}$)                           & $4$       &             &  $4$              &  & $10$~~          &  &        \\
+   $m_{\text{bjj}}$                            &   &  $1$                &           & $2$      &       & $3$      & $4$          \\
    $m^{W}_{\text{T}}$                           & $11$~~      &             &  $8$              &  & $13$~~          &  &         \\
    $m_{\tau\tau,\text{fit}}$                                     &   &  $2$                &           & $3$      &       & $1$      & $1$          \\  
- $m_{\text{bjj}}$                            &   &  $1$                &           & $2$      &       & $3$      & $4$          \\
- ${\pt}^{\ell}$                                 & $12$~~      &  $15$~~               &  $12$~~             & $17$~~     &       &  &         \\
+   $m_{\text{jj}}$                                      &   &             &           & $9$      &       & $6$      & $7$\\
    $m_{\tau\tau\text{q},\text{fit}}$                          &   &             &           &  &       & $10$~~     & $6$\\
+   $m_{\tau\tau}$                           & $10$~~      &  $14$~~               &  $11$~~             & $6$      & $1$           & $2$    & $2$          \\
+   ${\pt}_{\tautau} $                          &   &             &           &  & $9$           &  &         \\
+   $m_{\tau\tau\text{q}}$               &   &             &           &  & $3$           &  &        \\   
    $m_{\ell \text{b}}$                 & $3$       &             &  $5$              &  & $4$           &  &         \\
- ${\pt}_{\tau1}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$~~   & $10$~~           \\
- $\met$                                              & $5$       &  $11$~~               &  $10$~~             & $13$~~     & $6$           & $7$    & $13$~~          \\
- $m_{\tau\tau}$                           & $10$~~      &  $14$~~               &  $11$~~             & $6$      & $1$           & $2$    & $2$          \\
+   \text{min}($m_{\tau\tau \text{j}}$)             & $9$       &             &  $3$              &  & $14$~~          &  &         \\   
+   \text{min}($m_{\text{jj}}$) &   &  $12$~~               &           & $11$~~     &       &  &         \\
+   $\met\text{\,centrality}$                             &   &  $13$~~               &           & $15$~~     &       & $12$~~   & $9$         \\
    $E_{\tau1}/E_{\tau1,\text{fit}}$                  &   &  $10$~~               &           & $12$~~     &       & $8$    & $8$          \\
    $E_{\tau2}/E_{\tau2,\text{fit}}$                  &   &  $7$                &           & $4$      &       & $9$    & $11$~~         \\
- ${\pt}_{\tautau} $                          &   &             &           &  & $9$           &  &         \\
- $m_{\tau\tau\text{q}}$               &   &             &           &  & $3$           &  &        \\
    $\Delta\phi(\tau\tau,\met)$                         &   &  $6$                            &           & $16$~~     &       & $13$~~   & $12$~~         \\
- $\met\text{\,centrality}$                             &   &  $13$~~               &           & $15$~~     &       & $12$~~   & $9$         \\
- \text{min}($m_{\tau\tau \text{j}}$)             & $9$       &             &  $3$              &  & $14$~~          &  &         \\
    \text{min}($\Delta R(\ell,\tau)$)                               & $8$       &  $9$                &  $9$              & $10$~~     & $15$~~          &  &         \\
@@
    $\Delta R(\tau1,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
- \text{min}($m_{\text{jj}}$) &   &  $12$~~               &           & $11$~~     &       &  &         \\
-% $m_{\text{W}}$                                      & $\times$  &  $\times$           &  $\times$         & $9$      & $\times$      & $6$      & $7$\\
-% $\chi^{2}$                                          & $\times$  &  $\times$           &  $\times$         & $14$     & $\times$      & $\times$ & $\times$      \\
-% \text{max}($\eta_{\tau}$)                           & $4$       &  $\times$           &  $4$              & $\times$ & $10$          & $\times$ & $\times$       \\
-% $m^{\text{T}}_{\text{W}}$                           & $10$      &  $\times$           &  $8$              & $\times$ & $13$          & $\times$ & $\times$        \\
-% $m_{\tau,\tau}$                                     & $\times$  &  $2$                &  $\times$         & $3$      & $\times$      & $1$      & $1$          \\
-% $m_{\text{t},\text{SM}}$                            & $\times$  &  $1$                &  $\times$         & $2$      & $\times$      & $3$      & $4$          \\
-% $p_{\text{T},\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     & $\times$      & $\times$ & $\times$        \\
-% $m_{\text{t},\text{FCNC}}$                          &  $\times$ &  $\times$           &  $\times$         & $\times$ & $\times$      & $10$     & $6$\\
-% $m_{\text{t},\text{SM},\text{vis}}$                 & $3$       &  $\times$           &  $5$              & $\times$ & $4$           & $\times$ & $\times$        \\
-% $p_{\text{T},\tau}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
-% $\met$                                              & $5$       &  $11$               &  $10$             & $13$     & $6$           & $7$    & $13$          \\
-% $m_{\tau\tau,\text{vis}}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
-% $E_{\text{vis}~\tau,1}/E_{\tau,1}$                  & $\times$  &  $10$               &  $\times$         & $12$     & $\times$      & $8$    & $8$          \\
-% $E_{\text{vis}~\tau,2}/E_{\tau,2}$                  & $\times$  &  $7$                &  $\times$         & $4$      & $\times$      & $9$    & $11$         \\
-% $P_{\text{T,\tauhadvis}} $                          & $\times$  &  $\times$           &  $\times$         & $\times$ & $9$           & $\times$ & $\times$        \\
-% $m_{\text{t},\text{FCNC},\text{vis}}$               & $\times$  &  $\times$           &  $\times$         & $\times$ & $3$           & $\times$ & $\times$       \\
-% $\Delta\phi(\tau\tau,\met)$                         & $\times$  &  $6$    			   &  $\times$         & $16$     & $\times$      & $13$   & $12$         \\
-% $\met\text{centrality}$                             & $\times$  &  $13$               &  $\times$         & $15$     & $\times$      & $12$   & $9$         \\
-% \text{Min}($m_{\tau\tau \text{q-jet}}$)             & $9$       &  $\times$           &  $3$              & $\times$ & $14$          & $\times$ & $\times$        \\
-% $\Delta R(\ell,\tau)$                               & $8$       &  $9$                &  $9$              & $10$     & $15$          & $\times$ & $\times$        \\
-% $\Delta R(\tau,\tau)$                               & $\times$  &  $\times$           &  $\times$         & $\times$ & $2$           & $4$    & $3$             \\
-% $\Delta R(\ell,\text{b-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          & $\times$ & $\times$        \\
-% $\Delta R(\tau,\text{b-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          & $\times$ & $\times$       \\
-% $\Delta R(\ell+\text{b-jet},\tau\tau )$             & $\times$  &  $\times$           &  $\times$         & $\times$ & $7$           & $\times$ & $\times$        \\
-% $\Delta R(\tau,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
-% \text{Min}($m_{\text{light-jet},\text{light-jet}}$) & $\times$  &  $12$               &  $\times$         & $11$     & $\times$      & $\times$ & $\times$        \\
  \bottomrule\bottomrule\\
@@
 The BDT discriminant is trained for each SR starting from a large list of variables; then the least important variables are removed sequentially, and the BDT is retrained until the
-receiver operating characteristic (ROC) score drops by more than 2\%.
+receiver operating characteristic (ROC) score, the area under the ROC curve, drops by more than 2\%.
 %The final variables used in SRs are shown in Table 5 with their ranking. 
@@
 \item ${\pt}_{\tau\tau}$ is the visible $\pT$ of the di-$\tau$ system.
-\item $m_{\tau\tau,\text{q}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
+\item $m_{\tau\tau\text{q}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
 \item $m_{\ell \text{b}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top-quark mass.

### 2022-07-23 sections/objects.tex
fix George's comments for V2.4

@@
 Electron candidates are required to have $|\eta_{\textrm{cluster}}| < 2.47$, and to satisfy `tight' likelihood-based identification 
-criteria~\cite{ATLAS-CONF-2016-024} based on calorimeter, tracking and combined variables that provide 
+criteria~\cite{PERF-2016-01}
+%~\cite{ATLAS-CONF-2016-024}
+based on calorimeter, tracking and combined variables that provide 
 separation between electrons and jets.
@@
 A track- and cluster-based lepton isolation criterion is defined by placing requirements on the quantities $I_R = \sum \pt^{\textrm{trk}}$ and $E_R = \sum E^{\textrm{clst}}$, where
-the scalar sum includes all tracks' $\pt^{\textrm{trk}}$ or cluster energy deposits $E^{\textrm{clst}}$ (excluding the lepton candidate itself)
+the scalar sum runs over all tracks $\pt^{\textrm{trk}}$ or cluster energy deposits $E^{\textrm{clst}}$ (excluding the lepton candidate itself)
 within the cone defined by $\Delta R<0.2~(0.3)$ around the %axis
@@
 `Tight' isolation working points are also applied in some channels to reduce fake and non-prompt lepton contributions by using a trained isolation boosted decision tree (BDT)
-\texttt{PromptLeptonVeto} (PLIV), which identifies non-prompt light leptons by using lifetime information associated with a track-jet that matches the selected light lepton~\cite{ATLAS-CONF-2019-045}.
+\texttt{PromptLeptonVeto} (PLIV), which identifies non-prompt light leptons by using lifetime information associated with a track-jet that matches the selected light lepton.
+%~\cite{ATLAS-CONF-2019-045}.
 These additional reconstructed charged-particle tracks inside the jet can be
@@
 %built from energy deposits in the calorimeters calibrated to the electromagnetic scale. 
-Candidate jets are reconstructed using the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq} with a
-radius parameter $R=0.4$ applied to topological energy clusters~\cite{Aad:2016upy} and charged-particle tracks, processed using
+Candidate jets are reconstructed using the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2011ma}
+%Cacciari:2005hq}
+with a radius parameter $R=0.4$ applied to topological energy clusters~\cite{Aad:2016upy} and charged-particle tracks, processed using
 a particle-flow algorithm~\cite{Aad:2017epj77}. %newref Eur. Phys. J. C 77 (2017) 466

### 2022-07-23 sections/systematic_uncertainties.tex
fix George's comments for V2.4

@@
 identification and, in the case of electrons and muons, isolation efficiencies, as well as the momentum scale and resolution. 
-These are measured using $Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events ($\ell =e, \mu$)~\cite{ATLAS-CONF-2016-024,Aad:2016jkr} 
+These are measured using $Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events ($\ell =e, \mu$)~\cite{PERF-2016-01,Aad:2016jkr} 
 in the case of electrons and muons, and using $Z\to \tau^+\tau^-$ events in the case of $\had$ candidates~\cite{ATLAS-CONF-2017-029}.
@@
 of the theoretical uncertainties in $t$-, $tW$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
-Additional uncertainties associated with the parton shower, hadronisation and ISR/FSR radiation are also considered by using the same procedure
+Additional uncertainties associated with the parton shower, hadronisation and ISR/FSR are also considered by using the same procedure
 as for $t\bar t$.
@@
 Uncertainties in the $\ttbar V$ and $\ttbar H$ cross sections are estimated to be 12\% and [$+5.8\%/-9.2\%$], respectively,
-from the uncertainties in their respective NLO theoretical cross sections~\cite{ttZRun2}.
+from the uncertainties in their respective NLO theoretical cross sections~\cite{TOPQ-2018-08}.
 

### 2022-07-23 sections/bdt_Htautau.tex
updates plots labels

--- 2022-06-02 sections/bdt_Htautau.tex
@@
 %\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
-\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_os_log_.pdf} &
-\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b1j_ss_log_.pdf}&
-\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_ss_log_.pdf}\\
+\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l2tau1bnj_os_log_.pdf} &
+\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l1tau1b1j_ss_log_.pdf}&
+\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l1tau1b2j_ss_log_.pdf}\\
 (a) & (b) & (c) \\
 %(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
-\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_os_log_.pdf}&
-\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b3j_os_log_.pdf} &
-\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_ss_log_.pdf} \\
+\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l1tau1b2j_os_log_.pdf}&
+\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l1tau1b3j_os_log_.pdf} &
+\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l2tau1bnj_ss_log_.pdf} \\
 (d) & (e) & (f)\\
-%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
-\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b2jos_log_.pdf}&
-\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jos_log_.pdf}&
-\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jss_log_.pdf}\\
+%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhan 3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
+\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg2mtau1b2jos_log_.pdf}&
+\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg2mtau1b3jos_log_.pdf}&
+\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg2mtau1b3jss_log_.pdf}\\
 (g) & (h) & (i)\\
@@
  %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
- Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, $V$+jets, and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signals are scaled using
+ Overflow events are included in the last bin. ``Other MC'' includes single top, $V$+jets, and other small backgrounds in the leptonic and hadronic channels. The $tuH$ signals are scaled using
  normalization factors of 2 to 50.   
@@
  Overflow events are included in the last bin.
-``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel.
+``Other MC''  includes single top, and $V$+jets and other small backgrounds in the leptonic and hadronic channels.
 The $tuH$ signal is scaled using a normalization factor of 2 to 50.

### 2022-07-23 sections/data_presel.tex
updates plots labels

--- 2022-06-02 sections/data_presel.tex
@@
 Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & =0 isolated $e$ or $\mu$ \\
-$\had$  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
+$\had$  & $=$1 $\had$ & $=$2 $\had$ & $=$1 $\had$ & $=$2 $\had$ \\
 Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} < 0$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} > 0$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} < 0$ \\

### 2022-07-23 figures/Hbb/fit/cH_plots/Summary.C

@@ -1,1022 +1,0 @@
-void Summary()
-{
-//=========Macro generated from canvas: base_ebv2_signal_cH_uH_default_summary/base_ebv2_signal_cH_uH_default_summary
-//=========  (Fri Jul 20 10:20:53 2018) by ROOT version6.04/14
-   TCanvas *base_ebv2_signal_cH_uH_default_summary = new TCanvas("base_ebv2_signal_cH_uH_default_summary", "base_ebv2_signal_cH_uH_default_summary",0,0,900,850);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   base_ebv2_signal_cH_uH_default_summary->SetHighLightColor(2);
-   base_ebv2_signal_cH_uH_default_summary->Range(0,0,1,1);
-   base_ebv2_signal_cH_uH_default_summary->SetFillColor(0);
-   base_ebv2_signal_cH_uH_default_summary->SetBorderMode(0);
-   base_ebv2_signal_cH_uH_default_summary->SetBorderSize(2);
-   base_ebv2_signal_cH_uH_default_summary->SetTickx(1);
-   base_ebv2_signal_cH_uH_default_summary->SetTicky(1);
-   base_ebv2_signal_cH_uH_default_summary->SetLeftMargin(0.16);
-   base_ebv2_signal_cH_uH_default_summary->SetRightMargin(0.05);
-   base_ebv2_signal_cH_uH_default_summary->SetTopMargin(0.05);
-   base_ebv2_signal_cH_uH_default_summary->SetBottomMargin(0.16);
-   base_ebv2_signal_cH_uH_default_summary->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-1.058824,-0.0873016,9.529412,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetRightMargin(0.05);
[…]

### 2022-07-23 figures/Hbb/fit/cH_plots/c1lep4jex2bex.C

@@ -1,687 +1,0 @@
-void c1lep4jex2bex()
-{
-//=========Macro generated from canvas: c_c1lep4jex2bex/c_c1lep4jex2bex
-//=========  (Fri Jul 20 18:09:25 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex2bex = new TCanvas("c_c1lep4jex2bex", "c_c1lep4jex2bex",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex2bex->SetHighLightColor(2);
-   c_c1lep4jex2bex->Range(0,0,1,1);
-   c_c1lep4jex2bex->SetFillColor(0);
-   c_c1lep4jex2bex->SetBorderMode(0);
-   c_c1lep4jex2bex->SetBorderSize(2);
-   c_c1lep4jex2bex->SetTickx(1);
-   c_c1lep4jex2bex->SetTicky(1);
-   c_c1lep4jex2bex->SetLeftMargin(0.16);
-   c_c1lep4jex2bex->SetRightMargin(0.05);
-   c_c1lep4jex2bex->SetTopMargin(0.05);
-   c_c1lep4jex2bex->SetBottomMargin(0.16);
-   c_c1lep4jex2bex->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0.5308642,-0.0873016,1.024691,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis1[2] = {0.6, 1}; 
-   
-   TH1D *h_dummy2__1 = new TH1D("h_dummy2__1","Data/MC",1, xAxis1);
-   h_dummy2__1->SetMinimum(0.5);
-   h_dummy2__1->SetMaximum(1.5);
-   h_dummy2__1->SetEntries(5042418);
[…]

### 2022-07-23 figures/Hbb/fit/cH_plots/c1lep4jex4bin_postFit.C

@@ -1,711 +1,0 @@
-void c1lep4jex4bin_postFit()
-{
-//=========Macro generated from canvas: c_c1lep4jex4bin_postFit/c_c1lep4jex4bin_postFit
-//=========  (Fri Jul 20 18:06:41 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep4jex4bin_postFit = new TCanvas("c_c1lep4jex4bin_postFit", "c_c1lep4jex4bin_postFit",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep4jex4bin_postFit->SetHighLightColor(2);
-   c_c1lep4jex4bin_postFit->Range(0,0,1,1);
-   c_c1lep4jex4bin_postFit->SetFillColor(0);
-   c_c1lep4jex4bin_postFit->SetBorderMode(0);
-   c_c1lep4jex4bin_postFit->SetBorderSize(2);
-   c_c1lep4jex4bin_postFit->SetTickx(1);
-   c_c1lep4jex4bin_postFit->SetTicky(1);
-   c_c1lep4jex4bin_postFit->SetLeftMargin(0.16);
-   c_c1lep4jex4bin_postFit->SetRightMargin(0.05);
-   c_c1lep4jex4bin_postFit->SetTopMargin(0.05);
-   c_c1lep4jex4bin_postFit->SetBottomMargin(0.16);
-   c_c1lep4jex4bin_postFit->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-0.1728395,-0.0873016,1.061728,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis21[3] = {0, 0.5, 1}; 
-   
[…]

### 2022-07-23 figures/Hbb/fit/cH_plots/c1lep5jex3bex_postFit.C

@@ -1,983 +1,0 @@
-void c1lep5jex3bex_postFit()
-{
-//=========Macro generated from canvas: c_c1lep5jex3bex_postFit/c_c1lep5jex3bex_postFit
-//=========  (Fri Jul 20 18:06:42 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep5jex3bex_postFit = new TCanvas("c_c1lep5jex3bex_postFit", "c_c1lep5jex3bex_postFit",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep5jex3bex_postFit->SetHighLightColor(2);
-   c_c1lep5jex3bex_postFit->Range(0,0,1,1);
-   c_c1lep5jex3bex_postFit->SetFillColor(0);
-   c_c1lep5jex3bex_postFit->SetBorderMode(0);
-   c_c1lep5jex3bex_postFit->SetBorderSize(2);
-   c_c1lep5jex3bex_postFit->SetTickx(1);
-   c_c1lep5jex3bex_postFit->SetTicky(1);
-   c_c1lep5jex3bex_postFit->SetLeftMargin(0.16);
-   c_c1lep5jex3bex_postFit->SetRightMargin(0.05);
-   c_c1lep5jex3bex_postFit->SetTopMargin(0.05);
-   c_c1lep5jex3bex_postFit->SetBottomMargin(0.16);
-   c_c1lep5jex3bex_postFit->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-0.1728395,-0.0873016,1.061728,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis41[11] = {0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1}; 
-   
[…]

### 2022-07-23 figures/Hbb/fit/cH_plots/c1lep6jin2bex_postFit.C

@@ -1,687 +1,0 @@
-void c1lep6jin2bex_postFit()
-{
-//=========Macro generated from canvas: c_c1lep6jin2bex_postFit/c_c1lep6jin2bex_postFit
-//=========  (Fri Jul 20 18:06:43 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin2bex_postFit = new TCanvas("c_c1lep6jin2bex_postFit", "c_c1lep6jin2bex_postFit",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin2bex_postFit->SetHighLightColor(2);
-   c_c1lep6jin2bex_postFit->Range(0,0,1,1);
-   c_c1lep6jin2bex_postFit->SetFillColor(0);
-   c_c1lep6jin2bex_postFit->SetBorderMode(0);
-   c_c1lep6jin2bex_postFit->SetBorderSize(2);
-   c_c1lep6jin2bex_postFit->SetTickx(1);
-   c_c1lep6jin2bex_postFit->SetTicky(1);
-   c_c1lep6jin2bex_postFit->SetLeftMargin(0.16);
-   c_c1lep6jin2bex_postFit->SetRightMargin(0.05);
-   c_c1lep6jin2bex_postFit->SetTopMargin(0.05);
-   c_c1lep6jin2bex_postFit->SetBottomMargin(0.16);
-   c_c1lep6jin2bex_postFit->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0.5308642,-0.0873016,1.024691,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis61[2] = {0.6, 1}; 
-   
[…]

### 2022-07-23 figures/Hbb/fit/cH_plots/c1lep6jin4bin.C

@@ -1,711 +1,0 @@
-void c1lep6jin4bin()
-{
-//=========Macro generated from canvas: c_c1lep6jin4bin/c_c1lep6jin4bin
-//=========  (Fri Jul 20 18:09:26 2018) by ROOT version6.04/14
-   TCanvas *c_c1lep6jin4bin = new TCanvas("c_c1lep6jin4bin", "c_c1lep6jin4bin",0,0,600,700);
-   gStyle->SetOptStat(0);
-   gStyle->SetOptTitle(0);
-   c_c1lep6jin4bin->SetHighLightColor(2);
-   c_c1lep6jin4bin->Range(0,0,1,1);
-   c_c1lep6jin4bin->SetFillColor(0);
-   c_c1lep6jin4bin->SetBorderMode(0);
-   c_c1lep6jin4bin->SetBorderSize(2);
-   c_c1lep6jin4bin->SetTickx(1);
-   c_c1lep6jin4bin->SetTicky(1);
-   c_c1lep6jin4bin->SetLeftMargin(0.16);
-   c_c1lep6jin4bin->SetRightMargin(0.05);
-   c_c1lep6jin4bin->SetTopMargin(0.05);
-   c_c1lep6jin4bin->SetBottomMargin(0.16);
-   c_c1lep6jin4bin->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,1,0.28);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(-0.1728395,-0.0873016,1.061728,1.5);
-   pad1->SetFillColor(0);
-   pad1->SetFillStyle(4000);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(0);
-   pad1->SetTickx(1);
-   pad1->SetTicky(1);
-   pad1->SetLeftMargin(0.14);
-   pad1->SetRightMargin(0.05);
-   pad1->SetTopMargin(0);
-   pad1->SetBottomMargin(0.37);
-   pad1->SetFrameBorderMode(0);
-   pad1->SetFrameBorderMode(0);
-   Double_t xAxis81[3] = {0, 0.5, 1}; 
-   
-   TH1D *h_dummy2__73 = new TH1D("h_dummy2__73","Data/MC",2, xAxis81);
-   h_dummy2__73->SetMinimum(0.5);
-   h_dummy2__73->SetMaximum(1.5);
-   h_dummy2__73->SetEntries(872895);
[…]

### 2022-07-25 sections/introduction.tex
updates plots labels
minor updates

@@
 %production cross section of $pp\rightarrow tH$.
-The study of $pp\rightarrow tH$ processes will therefore also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
+The study of $pp\rightarrow tH$ processes will also contribute to the FCNC interaction searches~\cite{Greljo:2014dka}.
 In the SM, associated production of $tH$ in $pp$ collisions is expected to have a cross section of $\sigma_{tH}=92^{+7}_{-12}$ fb at a centre-of-mass energy of $\sqrt{s}= 13~\tev$~\cite{deFlorian:2016spz}.
@@
 The $H\rightarrow \tau\tau$ decay is detected in
-either the $\tlhad$ or $\thadhad$ final state when the top quark decays hadronically ($t_h$), but only the $\thadhad$ final state is considered
+either the $\tlhad$ or $\thadhad$ final states when the top quark decays hadronically ($t_h$), but only the $\thadhad$ final state is considered
 when the top quark decays leptonically ($t_{\ell}$), in order to avoid overlaps with

### 2022-07-25 sections/objects.tex
minor updates

@@
 Electron candidates are required to have $|\eta_{\textrm{cluster}}| < 2.47$, and to satisfy `tight' likelihood-based identification 
-criteria~\cite{PERF-2016-01}
+criteria~\cite{PERF-2017-01}
 %~\cite{ATLAS-CONF-2016-024}
@@
 The `tight' working points are used for leptons with high $\pt$ ($>20~\GeV$).
-Simulation-to-data scale factors for the efficiencies of the `tight' PLIV working points are measured using the tag-and-probe method~\cite{PERF-2016-01}
+Simulation-to-data scale factors for the efficiencies of the `tight' PLIV working points are measured using the tag-and-probe method~\cite{PERF-2017-01}
 with $Z\rightarrow \ell^+\ell^-$ events. These scale factors were checked for electrons or muons from the $\tau$-lepton decays

### 2022-07-25 sections/systematic_uncertainties.tex
minor updates

@@
 identification and, in the case of electrons and muons, isolation efficiencies, as well as the momentum scale and resolution. 
-These are measured using $Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events ($\ell =e, \mu$)~\cite{PERF-2016-01,Aad:2016jkr} 
+These are measured using $Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events ($\ell =e, \mu$)~\cite{PERF-2017-01,Aad:2016jkr} 
 in the case of electrons and muons, and using $Z\to \tau^+\tau^-$ events in the case of $\had$ candidates~\cite{ATLAS-CONF-2017-029}.

### 2022-07-26 sections/background_estimation.tex

@@
 In the hadronic channels, the contribution of fakes is estimated from data using the fake-factor (FF) method to derive the transfer functions from the background-enriched control
-regions (CR) to the SR~\cite{HIGG-2018-14}.
+regions (CR) to the SR~\cite{HIGG-2019-09}.
 %by defining control regions (CR)
@@
 The FFs are computed as the ratio of misidentified $\thad$ candidates that either pass or fail the `medium' $\tau$ ID selection in regions enriched in events originating from 
-$W$+jets processes~\cite{HIGG-2018-14}. 
+$W$+jets processes~\cite{HIGG-2019-09}. 
 %the Data-MC ($\mathrm{real~tau}$) ratio of the yields of events in which the tau candidate is passing or failing the medium tau ID selection

### 2022-07-26 sections/statistical_analysis.tex

@@
 where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
-maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and the ${\hat{\hat{\theta}}}_\mu$ are the values of the
+maximise the likelihood function (subject to the constraint $\hat{\mu} \geq 0$), and the ${\hat{\hat{\theta}}}_\mu$ are the values of the
 nuisance parameters that maximise the likelihood function for a given value of $\mu$. 

### 2022-09-22 sections/bdt_Htautau.tex
uopdate referee's comments

--- 2022-07-23 sections/bdt_Htautau.tex
@@
  %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
- Overflow events are included in the last bin. `Other MC' (`Rare') includes single-top, $V$+jets, and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled by a
+ Overflow events are included in the last bin. `Other MC' includes single-top, $V$+jets, and other small backgrounds in the leptonic and hadronic channel. The $tuH$ signal is scaled by a
  normalisation factor of either 2, 10, or 50.   
 %( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
-The lower panels show the ratio of data to prediction.}
+The lower panels show the ratio of data to prediction. Arrows in the figures indicate zero entries in the bins.}
 \label{fig:taupt_prefit}
@@
  Overflow events are included in the last bin.
-`Other MC' (`Rare') includes single-top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel.
+`Other MC' includes single-top, and $V$+jets and other small backgrounds in the leptonic and hadronic channels.
 The $tuH$ signal is scaled by a normalisation factor of either 2, 10, or 50.

### 2022-09-29 sections/introduction.tex

@@
 and $\BR(t\to uH) < 7.9\times10^{-4}\, (1.1\times10^{-3})$~\cite{CMS:2021gfa}.
-%CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.
+CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.
 
@@
 & $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137~~~~~          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
-%& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
+& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
 % 

### 2022-10-05 sections/introduction.tex
minor update to V2.7

@@
 and $\BR(t\to uH) < 7.9\times10^{-4}\, (1.1\times10^{-3})$~\cite{CMS:2021gfa}.
-CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.
+CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run~2 data and set observed (expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}\, (3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}\, (5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.
 
@@
 & $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
-& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137~~~~~          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
+& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
 & $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
